### 2018-12-06 Draft/draft.tex
Honghao: started the draft

\documentclass[11pt,letterpaper]{article}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
                                      {1ex \@plus1ex \@minus.2ex}%
                                      {-1em}%
                                      {\normalfont\normalsize\bfseries}}
\makeatother

%%%%%%%%%%%%%%%%%%%%%
%  P A C K A G E S  %
%%%%%%%%%%%%%%%%%%%%%

% Authors
\usepackage{authblk}

% Page margins
\usepackage[margin=1in]{geometry}

% Nicer math font
\usepackage{mathpazo}

% More fancy lists
\usepackage{enumerate}

% Microtype
\usepackage{microtype}

% TikZ
\usepackage{tikz}
%\usetikzlibrary{calc,shapes.geometric}
\usetikzlibrary{backgrounds,fit,decorations.pathreplacing,calc}

% Highlights
\usepackage{soul}

% Young Tableaux
\usepackage{ytableau}

% Figure
\usepackage{float}

% Hypertext package
\usepackage[colorlinks = true]{hyperref}
% Title and authors
%\hypersetup{
%  pdftitle = {},
%  pdfauthor = {}
%}
% Color definitions
\definecolor{darkred}  {rgb}{0.5,0,0}
\definecolor{darkblue} {rgb}{0,0,0.5}
\definecolor{darkgreen}{rgb}{0,0.5,0}
% Color links
\hypersetup{
  urlcolor   = blue,         % color of external links
  linkcolor  = darkblue,     % color of internal links
  citecolor  = darkgreen,    % color of links to bibliography
  filecolor  = darkred       % color of file links
}

% AMS
\usepackage{amsmath,amssymb,amsfonts,amsthm,amstext}

%% Restating theorems
%\usepackage{thm-restate}

% Powerful macros
\usepackage{etoolbox}

% Fixes for amsmath
\usepackage{mathtools}
\mathtoolsset{centercolon}
\makeatletter
\protected\def\tikz@nonactivecolon{\ifmmode\mathrel{\mathop\ordinarycolon}\else:\fi}
\makeatother

% Daw boxes
\usepackage{tcolorbox}

% Code
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}

% Clever references
\usepackage{cleveref}%[nameinlink]
\crefname{lemma}{Lemma}{Lemmas}
\crefname{proposition}{Proposition}{Propositions}
\crefname{definition}{Definition}{Definitions}
\crefname{theorem}{Theorem}{Theorems}
\crefname{conjecture}{Conjecture}{Conjectures}
\crefname{corollary}{Corollary}{Corollaries}
\crefname{claim}{Claim}{Claims}
\crefname{section}{Section}{Sections}
\crefname{appendix}{Appendix}{Appendices}
\crefname{figure}{Fig.}{Figs.}
\crefname{table}{Table}{Tables}
% \crefname{algorithm}{Algorithm}{Algorithms}

% IEEE tools
\usepackage[retainorgcmds]{IEEEtrantools}

% table of contents
\usepackage{tocloft}

%%%%%%%%%%%%%%%%%%%%%%%%%
%  N E W C O M M A N D  %
%%%%%%%%%%%%%%%%%%%%%%%%%

% Standard quantum notation

\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\braket}[2]{\langle#1|#2\rangle}
\newcommand{\ketbra}[2]{|#1\rangle\langle#2|}
\newcommand{\proj}[1]{|#1\rangle\langle#1|}

\newcommand{\x}{\otimes}
\newcommand{\xp}[1]{^{\otimes #1}}
\newcommand{\op}{\oplus}

\newcommand{\ct}{^{\dagger}}
\newcommand{\tp}{^{\mathsf{T}}}

% Linear algebra

%\newcommand{\1}{\mathbb{1}} % identity matrix
%\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\End}{End}
%\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Lin}{L} % all linear maps
\newcommand{\Mat}[1]{\mathrm{M}(#1)} % all matrices
%\newcommand{\Mat}[1]{\mathrm{M}_{#1}(\C)}

% Paired delimiters

\DeclarePairedDelimiter{\set}{\lbrace}{\rbrace}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\DeclarePairedDelimiter{\of}{\lparen}{\rparen}
\DeclarePairedDelimiter{\sof}{\lbrack}{\rbrack}
\DeclarePairedDelimiter{\ip}{\langle}{\rangle}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

% Operators

\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\DeclareMathOperator{\vc}{vec}
\DeclareMathOperator{\spn}{span}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\spec}{spec}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\hook}{hook}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\supp}{supp}

% Matrices

\newcommand{\mx}[1]{\begin{pmatrix}#1\end{pmatrix}}
\newcommand{\smx}[1]{\bigl(\begin{smallmatrix}#1\end{smallmatrix}\bigr)}

% Sets

\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\calH}{\mathcal{H}}

% Identity operator
\newcommand{\1}{\mathbb{1}}

% Pauli Group
\newcommand{\Pg}{\mathcal{P}}
\newcommand{\J}{\mathcal{J}}

% Special notation

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}

% Commands for highlighting text and notes

\usepackage{color}
\newcommand{\marked}[1]{{\fboxsep0pt\colorbox{yellow}{#1}}}
\usepackage[
  bordercolor = white,
  backgroundcolor = gray!30,
  linecolor = black,
  colorinlistoftodos]{todonotes}

%%%%%%%%%%%%%%%%%%%%%%%%%
%  N E W T H E O R E M  %
%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{claim}[theorem]{Claim}
\newtheorem*{conjecture*}{Conjecture}
\newtheorem*{problem}{Problem}
\newtheorem*{example}{Example}

\theoremstyle{definition}
\newtheorem*{remark}{Remark}

%%%%%%%%%%%%%%%%%%%
%  F I G U R E S  %
%%%%%%%%%%%%%%%%%%%

%\input{Tableau.tex}

%%%%%%%%%%%%%%%%
%   Document   %
%%%%%%%%%%%%%%%%

\begin{document}

\title{Self-test EPR pair with constant alphabet}

\author[1]{Honghao Fu}
\author[1,2]{Carl Miller}

\renewcommand\Affilfont{\itshape\small}

\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

\end{document}

### 2018-12-07 Draft/draft.tex
Honghao: added preliminaries and started section 2

@@
 
-% Matrices
-
-\newcommand{\mx}[1]{\begin{pmatrix}#1\end{pmatrix}}
-\newcommand{\smx}[1]{\bigl(\begin{smallmatrix}#1\end{smallmatrix}\bigr)}
-
 % Sets
@@
 \newcommand{\SVT}{SVT}
+\newcommand{\EPR}[1]{EPR^{(#1)}}
+\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
+\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
+\newcommand{\G}[1]{G^{(#1)}}
+\newcommand{\LS}{LS}
 
-% Commands for highlighting text and notes
+% Probabilities
+\newcommand{\pr}[2]{P(#1|#2)}
+\newcommand{\pa}[2]{P_A(#1|#2)}
+\newcommand{\pb}[2]{P_B(#1|#2)}
 
-\usepackage{color}
-\newcommand{\marked}[1]{{\fboxsep0pt\colorbox{yellow}{#1}}}
-\usepackage[
-  bordercolor = white,
-  backgroundcolor = gray!30,
-  linecolor = black,
-  colorinlistoftodos]{todonotes}
+% Bell Ineqaulities
+\newcommand{\I}{\mathcal{I}}
 
@@
 
-%%%%%%%%%%%%%%%%%%%
-%  F I G U R E S  %
-%%%%%%%%%%%%%%%%%%%
-
-%\input{Tableau.tex}
-
 %%%%%%%%%%%%%%%%
@@
 \maketitle
+%========================================
+\section{Preliminaries and notations}
+%========================================
+We use $[n]$ to denote the set $\{0,1 \dots n-1\}$.
+We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.
 
+\textbf{The EPR pair.} Our goal is to self-test maximally entangled state of local dimension $d$, denoted by 
+\begin{align}
+\ket{\EPR{d}} = \frac{1}{\sqrt{d}} \sum_{i = 0}^{d-1} \ket{ii}.
+\end{align}
+The superscript $(d)$ is to stress the local dimension and we follow this convention through this paper.
+
+\textbf{The Pauli operators.} 
+We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators behave like 
+the $d$-dimensional Pauli operators which are defined by
+\begin{align}
+	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1}{i} \quad \pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i}
+\end{align}
+where $\omega_d = e^{i\pi/d}$ is the primitive $d$th root of unity and the addition is taken modulo $d$.
+
+\textbf{The weighted CHSH inequality \cite{acin2012}.}
+The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
+The weighted CHSH operator is defined as 
+\begin{align}
+	\label{eq:chsh_op}
+	\I_\alpha = \alpha(A_0B_0+A_0B_1) + A_1B_0 - A_1B_1,
+\end{align}
+where $A_x,B_y$ for $x,y = 0,1$ are Binary observables on Hilbert space $\calH_A$ and $\calH_B$ respcetively.
+If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, we have 
+\begin{align}
+	\bra{\phi} \I_\alpha \ket{\phi} \leq 2\alpha.
+\end{align}
+However, If they share entangled state $\ket{\psi}$, the maximal violation is 
+\begin{align}
+\label{eq:chsh_max}
+\bra{\psi} \I_\alpha \ket{\psi} \leq 2\sqrt{1+\alpha^2}.
+\end{align}
+\begin{definition}[Ideal strategy for $\I_\alpha$]
+	Define $\mu = \arctan(1/\alpha)$.
+	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation of \cref{eq:chsh_max})
+	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz{2}$, $A_1 = \paulix{2}$,
+	$B_0 = \cos(\mu) \pauliz{2} + \sin(\mu) \paulix{2}$ and $B_1 = \cos(\mu) \pauliz{2} - \sin(\mu) \paulix{2}$.
+\end{definition}
+We take an approach introduced in Ref.~\cite{bamps2015} and prove the following robust self-testing result.
+\begin{theorem}
+\label{thm:selftest}
+	Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ satisfies that
+	\begin{align}
+		\bra{\psi} \I_\alpha \ket{\psi} \geq 2\sqrt{1+\alpha^2} - \epsilon
+	\end{align}
+	for some $\alpha$, then
+	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
+	\begin{align}
+		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{aux} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O(\sqrt{\epsilon})
+	\end{align}
+	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and where $A_x, B_y$ are from the 
+	ideal strategy.
+\end{theorem}
+We defer the proof of \cref{thm:selftest} till Appendix~\ref{sec:selftest}.
+After proving the robust the self-testing result, we take one step further and observed some interesting behaviour of the 
+observable $\tilde{B}_0\tilde{B}_1$.
+\begin{proposition}
+\label{prop:2d-subspace}
+	Suppose a quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
+	value of  $\bra{\psi}\I_{-\cot(\pi/2d)} \ket{\psi}$, then there exists a $2$-dimensional Hilbert space which is spanned by eigenvectors of 
+	$\tilde{B}_0\tilde{B}_1$ of eigenvalue $\omega_d$ and $\omega_d^{-1}$.
+\end{proposition}
+\begin{proof}[Proof of \cref{prop:2d-subspace}]
+	By \cref{thm:selftest}, the condition that the strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
+	maximal value of $\bra{\psi}  \I_\alpha \ket{\psi} $ implies that there exists state $\ket{u_0}, \ket{u_1}$ such that 
+	\begin{align*}
+	&(\tilde{B}_0 + \tilde{B}_1) \ket{u_0} = 2\cos(\pi/2d) \ket{u_0} \\
+	&(\tilde{B}_0 + \tilde{B}_1) \ket{u_1} = -2\cos(\pi/2d) \ket{u_1}\\
+	&(\tilde{B}_0 - \tilde{B}_1) \ket{u_0} = -2\sin(\pi/2d) \ket{u_1} \\
+	&(\tilde{B}_0 - \tilde{B}_1) \ket{u_1} = -2\sin(\pi/2d) \ket{u_0}.
+	\end{align*}
+	It is straightforward to calculate that 
+	\begin{align}
+		\tilde{B}_0\tilde{B}_1 \ket{u_0} &= \cos(\pi/d) \ket{u_0} -\sin(\pi/d) \ket{u_1}\\
+		\tilde{B}_0\tilde{B}_1\ket{u_1} &= \sin(\pi/d)\ket{u_0} + \cos(\pi/d) \ket{u_1}.
+	\end{align}
+	We can conclude that 
+	\begin{align}
+		&\tilde{B}_0\tilde{B}_1(\ket{u_0} + i\ket{u_1}) = e^{i \frac{\pi}{d}} (\ket{u_0} + i\ket{u_1})\\
+		&\tilde{B}_0\tilde{B}_1(\ket{u_0} - i\ket{u_1}) = e^{-i \frac{\pi}{d}} (\ket{u_0} - i\ket{u_1}).
+	\end{align}
+\end{proof}
+
+\textbf{Nonlocal game}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
+to give answer for a chosen question. We denote Alice's question set by $X$ and answer set by $A$. Similarly,
+Bob's question set is denoted by $Y$ and his answer set is denoted by $B$. The nonlocal game also
+comes with two functions: $\pi: X \times Y \rightarrow [0,1]$, which is the probability distribution over the questions,
+and $V: A \times B \times X \times Y \rightarrow \R$, which is the scoring function. Such games are nonlocal
+because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
+the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
+pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
+to our new nonlocal game.
+
+The quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side and 
+$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. Then the behaviour of Alice and Bob is described 
+by the conditional probability
+\begin{align}
+	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for } (a,b,x,y) \in A \times B \times X \times Y,
+\end{align}
+where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
+The \emph{value} of a strategy is given by
+\begin{align}
+	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
+\end{align}
+
+The main contribution of our work is the construction of a nonlocal game $\G{d}$ that can be used to self-test $\ket{\EPR{d}}$where $d$ is an arbitrary odd prime number. 
+In fact, our nonlocal game self-tests $\paulix{d}$ and $\pauliz{d}$ too, just implicitly.
+The nonlocal game is a linear system game with modifications. 
+We introduce the definition of self-testing first and then the definition of linear system game, 
+which come from Ref.~\cite{coladan2017, slofstra2017}.
+\begin{definition}[Self-testing]
+	We say that a nonlocal game self-tests a quantum state $\ket{\Psi}$ if 
+	any quantum strategy $S$ that achieves the optimal quantum value uses a shared state equivalent up to local isometry to $\ket{\Psi}$.
+\end{definition}
+\begin{definition}[Linear system game]
+ Let $Ax = b$ be an $m \times n$ linear system over $\Z_d$. The associated linear system game has two
+ players Alice and Bob, where Alice is given a equation number $1 \leq x \leq m$ and replies with $a \in \Z_d^{\times n}$
+ ,and Bob is given a variable $y$ and replies with an assignment $y \in \Z_d$. The winning condition is 
+ \begin{align*}
+ 	a(y) &= b && \text{(Consistency)} \\
+	\sum_{y = 1}^n A_{xy} a(y) &\equiv b(x) \pmod d. &&\text{(Constraint satisfaction)}
+ \end{align*}
+\end{definition}
+The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
+so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
+$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
+
+The main tool to understand linear system game is through its solution group over $\Z_d$.
+\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
+	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
+	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
+	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
+	\begin{align}
+		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
+	\end{align}
+	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
+	\begin{align}
+		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
+	\end{align}
+	Then the solution group has presentation 
+	\begin{align}
+	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
+	\end{align}
+\end{definition}
+Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
+Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
+\begin{definition}[Operator solution]
+	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
+	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
+	representation mapping $\J$ to $\overline{\omega_d}\1$.
+\end{definition}
+What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
+linear system game from its operator solution and vice versa.
+%========================================
+\section{Components of $\G{d}$}
+%========================================
+%----------------------------------------------------------------
+\subsection{The linear system game}
+%----------------------------------------------------------------
+The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is an embedding of the qudit Pauli group,
+which is defined as
+\begin{align}
+	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
+\end{align}
+To construct $\LS$, we introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
+by the following relations
+\begin{align}
+\label{eq:sim}
+	u_x x u_x = x^2, \quad
+	u_z z u_z = z^2.
+\end{align}
+Such relations give us the freedom to use the same solution group to embed different $\Pg_d$.
+
+With constraints imposed by other components of the whole game, the two conditions above 
+imply that the eigenvalues of $x$ and $z$ are $\{\omega_d^k = e^{ik\pi/d}\}_{k=1}^d$ with $d$ odd, prime and
+$\Z/(d\Z)$ has primitive root $2$ and the eigenspaces for different eigenvalues are of the same dimension.
+\hl{Later we will set the exponent to be $a \in \{2, 3, 5\}$ which is the primitive root of infinitely many prime numbers and
+construct a nonlocal game that can self-test infinitely many maximally entangled state.}
+\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
+
+Secondly, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
+relation $xzx^{-1}z^{-1} = \J$.
+
+It can be easily checked that the qudit Pauli-x and Pauli-z operators of dimension $d$ satisfy the new relations 
+above, where Pauli-x and Pauli-z operators are defined by
+\begin{align}
+	\sigma_x = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
+	\sigma_z = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
+\end{align}
+Moreover, if $U_x\sigma_xU_x^\dagger = \sigma_x^2$ and $U_z\sigma_zU_z^\dagger = \sigma_z^2$,
+we can verify that 
+\begin{align}
+	U_xU_z = \1 = U_zU_x,
+\end{align}
+Hence, we define the new group by
+\begin{equation}
+\begin{aligned}
+	\Pg =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
+	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
+\end{aligned}
+\end{equation}
+\hl{Since $\Pg_d$'s relations satisfy the relations of $\Pg$, can we say $\Pg_d$ is a subgroup of $\Pg$?}
+This group will be embedded in a solution group, $\Gamma_\Pg$, following Slofstra's embedding techniques.
+See Appendix~\ref{sec:construct} for details.
+\bibliographystyle{alphaurl}
+\bibliography{quantum_correlation}
+\appendix
+%========================================
+\section{Proof of \cref{thm:selftest} }
+\label{sec:selftest}
+%========================================
+\begin{proof}
+Following the techniques developed in Ref.~\cite{bamps2015}, the first step is to find a sum-of-square decomposition of 
+\begin{align}
+	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
+	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_0B_0+A_0B_1) -  A_1B_0 + A_1B_1.
+\end{align} 
+With the following notation
+\begin{align*}
+	Z_A = A_0 &\quad X_A = A_1\\
+	Z_B = \frac{B_0+B_1}{2\cos(\mu)} &\quad X_B = \frac{B_0-B_1}{2\sin(\mu)},
+\end{align*}
+the two SOS decompositions that we use are
+\begin{align}
+	\label{eq:sos1}&\bar{\I}_\alpha = \frac{\sin(\mu)\bar{\I}_\alpha^2 + 4\sin(\mu)\cos(\mu)^2(Z_AX_B+X_AZ_B)^2}{4},\\
+	\label{eq:sos2}&\bar{\I}_\alpha = \frac{\cos^2(\mu)}{\sin(\mu)}(Z_A-Z_B)^2 + \sin(\mu) (X_A-X_B)^2.
+\end{align}
+The verification is omitted here.
+
+Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_{y in [2]}\}$ achieves that 
+$\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$.
+The second step is to establish bounds of the following form
+\begin{align}
+	&\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
+	&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\
+	&\|(\tilde{X}_A-\tilde{X}_B)\ket{\psi}\| \leq c_3 \sqrt{\epsilon}\\
+	&\|(\tilde{Z}_A\tilde{X}_A+\tilde{X}_A\tilde{Z}_A)\ket{\psi}\| \leq c_4 \sqrt{\epsilon}.
+\end{align}
+Now we write $s = \sin(\mu)$, $c = \cos(\mu)$ and define
+\begin{align*}
+	S_1 &= \frac{\sqrt{s}}{2} \bar{\I}_\alpha, \quad
+	S_2 = \sqrt{s}c(\tilde{Z}_A\tilde{X}_B+\tilde{X}_A\tilde{Z}_B),\\
+	S_3 &= \frac{c}{\sqrt{s}}(\tilde{Z}_A-\tilde{Z}_B),\quad
+	S_4 = \sqrt{s}(\tilde{X}_A-\tilde{X}_B)
+\end{align*}
+then $\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2$ and $\bra{\psi}\bar{\I}_\alpha \ket{\psi} \leq \epsilon$ implies that 
+$\bra{\psi}S^2_i \ket{\psi} \leq \epsilon$ and $\|S_i \ket{\psi} \| \leq \sqrt{\epsilon}$ for $i = 1,2,3,4$.
+We can easily check that 
+\begin{align*}
+	c_1 = \frac{\sqrt{s}}{c}, \quad
+	c_2 = \frac{1}{\sqrt{s}} + \frac{1}{c\sqrt{s}}, \quad
+	c_3 = \frac{1}{\sqrt{s}}.
+\end{align*}
+where we use the relation that $\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A) = S_4/s^{1/2} + S_2/(cs^{1/2})$.
+To calculate $c_4$, we use the relation
+\begin{align}
+	\tilde{Z}_A\tilde{X}_A + \tilde{X}_A\tilde{Z}_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}
+\end{align}
+and reach the conclusion that  
+\begin{align}
+	c_4 = \frac{1+c+s}{c\sqrt{s}}
+\end{align}
+where we use that fact that $\tilde{Z}_A, \tilde{X}_A$ are unitaries.
+
+With appropriate substitutions, the rest of the proof follows the same derivation as that in Appendix A of Ref.~\cite{bamps2015},
+so we omit it here.
+\end{proof}
 \end{document}

### 2018-12-11 Draft/draft.tex
Honghao: finished introducing components of the whole game

@@
 
+% Table with multi-row
+\usepackage{multirow}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\LS}{LS}
+\newcommand{\tA}{\tilde{A}}
+\newcommand{\tB}{\tilde{B}}
+\newcommand{\tpsi}{\tilde{\psi}}
 
@@
 %========================================
+Suppose we would like to self-test $\ket{\EPR{d}}$ with $\G{d}$, where $d$ is prime and has primitive root $2$.
+Later we will see how to deal with general prime numbers and why there are infinitely many prime dimensional EPR pairs 
+that can be self-tested by a variant of $\G{d}$.
 %----------------------------------------------------------------
@@
 %----------------------------------------------------------------
-The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is an embedding of the qudit Pauli group,
+The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the qudit Pauli group,
 which is defined as
@@
 \end{align}
-To construct $\LS$, we introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
+The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
+We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
 by the following relations
@@
 \end{align}
-Such relations give us the freedom to use the same solution group to embed different $\Pg_d$.
-
-With constraints imposed by other components of the whole game, the two conditions above 
-imply that the eigenvalues of $x$ and $z$ are $\{\omega_d^k = e^{ik\pi/d}\}_{k=1}^d$ with $d$ odd, prime and
-$\Z/(d\Z)$ has primitive root $2$ and the eigenspaces for different eigenvalues are of the same dimension.
-\hl{Later we will set the exponent to be $a \in \{2, 3, 5\}$ which is the primitive root of infinitely many prime numbers and
-construct a nonlocal game that can self-test infinitely many maximally entangled state.}
+Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
 \footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
-
-Secondly, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
+but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
+Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
 relation $xzx^{-1}z^{-1} = \J$.
 
-It can be easily checked that the qudit Pauli-x and Pauli-z operators of dimension $d$ satisfy the new relations 
-above, where Pauli-x and Pauli-z operators are defined by
+It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
+where  $\paulix{d}$ and $\pauliz{d}$ are defined by
 \begin{align}
-	\sigma_x = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
-	\sigma_z = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
+	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
+	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
 \end{align}
-Moreover, if $U_x\sigma_xU_x^\dagger = \sigma_x^2$ and $U_z\sigma_zU_z^\dagger = \sigma_z^2$,
+Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
 we can verify that 
@@
 \end{align}
-Hence, we define the new group by
+Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
+In the end, we define $\Pg_{\LS}$ by
 \begin{equation}
 \begin{aligned}
-	\Pg =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
+	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
 	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
@@
 \end{equation}
-\hl{Since $\Pg_d$'s relations satisfy the relations of $\Pg$, can we say $\Pg_d$ is a subgroup of $\Pg$?}
-This group will be embedded in a solution group, $\Gamma_\Pg$, following Slofstra's embedding techniques.
+This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
+The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
 See Appendix~\ref{sec:construct} for details.
+%------------------------------------------------------------------------
+\subsection{The extended weighted CHSH game}
+%------------------------------------------------------------------------
+The extended weighted CHSH game is added to make sure that some of Alice and Bob's observables have
+eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
+The notation for the extended weighted CHSH game that enforces the eigenvalues of the observable $U$ is 
+$\CHSH_U$, where the superscript $d$ means that the rules of this game depends on $d$.
+Intuitively, this is one step towards verifying Alice and Bob use $\paulix{d}$ and $\pauliz{d}$ in their operator solution.
+
+In this game, Alice and Bob each gets a question $x$,$y \in \{ 0, 1, \ast\}$ and 
+they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
+The scoring rules are
+\begin{itemize}
+	\item \textbf{Case 1:} $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
+	they score only if $a = b$;
+	\item \textbf{Case 2a:} $x,y \in \{0,1\}$ and they answer with $a,b \in \{0,1\}$, then
+	their answers are scored according to $I_{-\cot(\pi/2d)}$
+	\item \textbf{Case 2b:} $x,y \in \{0,1\}$ and Alice answer with $\perp$, then all possible outputs from Bob
+	are discarded;
+	\item \textbf{Case 3:} $x \in {0,1}, y = \ast$, when Bob answers $\diamond$, Alice should answer with $\{0.1\}$ but not $\perp$,
+	when Bob answers $\perp$ Alice should answer $\perp$ too;
+	\item \textbf{Case 4:} other combination of inputs are not scored.
+\end{itemize}
+In the ideal strategy, Alice and Bob share the state $\ket{\psi} =1/\sqrt{d} \sum_{i=0}^{d-1} \ket{u_i}\ket{u_i}$.
+We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ amd
+define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
+ maximaize $\langle I_{-\cot(\pi/2d)} \rangle$.
+
+We summarize the projectors of the ideal strategy and the ideal correlation in the following two charts.
+Note that we don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ because they are irrelevant
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{|c|c||c|c|}
+\hline
+\multicolumn{2}{|c|}{} &
+\multicolumn{2}{|c|}{$x=\ast$}\\
+\cline{3-4}
+\multicolumn{2}{|c|}{} &$a = \diamond$ & $a = \perp$ \\
+\hline
+\hline
+\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & 2/d & 0 \\
+\cline{2-4}
+&$b=\perp$ & 0 & (d-2)/d \\
+\hline
+\end{tabular}
+\caption{Alice and Bob's behaviour when $x=y=\ast$.}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{|c|c||c|c|c|c|c|c|}
+\hline
+\multicolumn{2}{|c|}{} &
+\multicolumn{3}{|c|}{$x=0$}&
+\multicolumn{3}{|c|}{$x=1$} \\
+\cline{3-8}
+\multicolumn{2}{|c|}{} &
+$a = 0$ & $a=1$ & $a=\perp$ &
+$a = 0$ & $a=1$ & $a=\perp$\\
+\hline
+\hline
+\multirow{2}{*}{$y = 0$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{\sin^2(\pi/4d)}{d}$ & \small $\pr{\perp0}{00}$ 
+& $\frac{1+\sin(\pi/2d)}{2d}$ & $\frac{1-\sin(\pi/2d)}{2d}$ & \small  $\pr{\perp0}{10}$ \\
+\cline{2-8}
+&$b=1$ & $\frac{\sin^2(\pi/4d)}{d}$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{d-2}{d}-\pr{\perp0}{00}$ 
+&  $\frac{1-\sin(\pi/2d)}{2d}$ & $\frac{1+\sin(\pi/2d)}{2d}$ & \small $\frac{d-2}{d} - \pr{\perp0}{10}$  \\
+\hline
+\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{\sin^2(\pi/4d)}{d}$ & \small $\pr{\perp0}{01}$ & 
+$ \frac{1-\sin(\pi/2d)}{2d}$ & $ \frac{1+\sin(\pi/2d)}{2d}$ & \small $\pr{\perp 0}{11}$  \\
+\cline{2-8}
+&$b=1$ & $\frac{\sin^2(\pi/4d)}{d}$ & $\frac{\cos^2(\pi/4d)}{d}$ & \small $\frac{d-2}{d}-\pr{\perp0}{01}$ &  
+$ \frac{1+\sin(\pi/2d)}{2d}$ & $ \frac{1-\sin(\pi/2d)}{2d}$ & \small $\frac{d-2}{d}- \pr{\perp 0}{11}$ \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Alice and Bob's behaviour when $x,y \in [2]$.}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{|c|c||c|c|c|c|c|c|}
+\hline
+\multicolumn{2}{|c|}{} &
+\multicolumn{3}{|c|}{$x=0$}&
+\multicolumn{3}{|c|}{$x=1$} \\
+\cline{3-8}
+\multicolumn{2}{|c|}{} &
+$a = 0$ & $a=1$ & $a=\perp$ &
+$a = 0$ & $a=1$ & $a=\perp$\\
+\hline
+\hline
+\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/d$ & $1/d$ & 0 
+& $1/d$ & $1/d$ & 0 \\
+\cline{2-8}
+&$b=\perp$ & 0 & 0 & $\frac{d-2}{d}$ 
+&  0 & 0 & \small $\frac{d-2}{d} $  \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Alice and Bob's behaviour when $x\in [2]$ and $y = \ast$.}
+\end{table}
+Alice's projectors are 
+\begin{align*}
+	&A_\ast^\diamond = \Pi_V, A_\ast^\perp = \Pi_V^\perp \\
+	&A_0^0 = \ketbra{u_1}{u_1}, A_0^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_0^\perp = \Pi_V^\perp\\
+	&A_1^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
+	A_0^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_0^\perp = \Pi_V^\perp
+\end{align*}
+Bob's projectors are 
+\begin{align*}
+	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
+	&B_0^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} + \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
+	\left( \cos(\frac{\pi}{4d})\bra{u_1} + \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
+	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} - \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
+	\left( \sin(\frac{\pi}{4d})\bra{u_1} - \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
+	&B_1^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} - \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
+	\left( \cos(\frac{\pi}{4d})\bra{u_1} - \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
+	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} + \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
+	\left( \sin(\frac{\pi}{4d})\bra{u_1} + \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right).
+\end{align*}
+About Bob's projectors for input $y \in [2]$, we are only interested in their actions when restricted 
+to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.
+
+The importance of this game is summarized in the following lemma.
+\begin{lemma}
+	\label{lm:chsh_comp}
+	Suppose a quantum strategy $\left(\{\{\tA_x^a\}_a\}_x, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}\right)$
+	achieves the optimal correlation of $\CHSH$, then there exists unitaries $U_A$ and $U_B$ 
+	such that 
+	\begin{align*}
+		&U_A\x U_B \left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) = \ket{\EPR{2}} \\
+		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 + \tB_1}{2\cos(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
+		=\1 \x \pauliz{2} \ket{\EPR{2}} \\
+		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 - \tB_1}{-2\sin(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
+		=\1 \x \paulix{2} \ket{\EPR{2}} 
+	\end{align*}
+	where $\tB_0 = \tB_0^0 - \tB_0^1$ and $\tB_1 = \tB_1^0 - \tB_1^1$.
+\end{lemma}
+\begin{proof}
+Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \x \tB_y^b$ in the following proof.
+
+From the marginal distribution $\pb{\diamond}{\ast} = \pa{0}{0}+\pa{1}{0} = 2/d$,
+we know $\| \tB_\ast^\diamond \ket{\tpsi} \| = \| (\tA_0^0+\tA_0^1) \ket{\tpsi}\| = \sqrt{2/d}$.
+Since $\pr{0\diamond}{0\ast} + \pr{1\diamond}{0\ast} = 2/d$, we find that 
+\begin{align*}
+	\frac{\bra{\tpsi}\tB_\ast^\diamond (\tA_0^0+\tA_0^1) \tB_\ast^\diamond\ket{\tpsi}}{ \| \tB_\ast^\diamond \ket{\tpsi} \|^2} = 1,
+\end{align*}
+which means that 
+\begin{align}
+	(\tA_0^0+\tA_0^1)\tB_\ast^\diamond \ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
+\end{align}
+Using the commutation relation between $(\tA_0^0+\tA_0^1)$ and $\tB_\ast^\diamond$, we get
+\begin{align*}
+	\frac{\bra{\tpsi} (\tA_0^0+\tA_0^1) \tB_\ast^\diamond(\tA_0^0+\tA_0^1)\ket{\tpsi}}{ \| (\tA_0^0+\tA_0^1) \ket{\tpsi} \|^2} = 1,
+\end{align*}
+Similar argument gives us that 
+\begin{align}
+	\tB_\ast^\diamond (\tA_0^0+\tA_0^1) \ket{\tpsi} = (\tA_0^0+\tA_0^1)\ket{\tpsi}.
+\end{align}
+The two equations above can be chained by commutativity to reach the conclusion that 
+\begin{align}
+	(\tA_0^0+\tA_0^1)\ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
+\end{align}
+Following the same line of argument, we can conclude that
+\begin{align}
+	\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi} = (\tA_0^0+\tA_0^1)\ket{\tpsi} = (\tA_1^0+\tA_1^1)\ket{\tpsi}.
+\end{align}
+Looking at the marginal distribution when Alice and Bob output $\perp$, we conclude that 
+\begin{align}
+	\tB_\ast^\perp \ket{\tpsi} = \tA_\ast^\perp \ket{\tpsi} = \tA_0^\perp \ket{\tpsi} = \tA_1^\perp \ket{\tpsi},
+\end{align}
+with similar arguments.
+
+Next we examine the CHSH-type correlation when $x,y \in [2]$,
+\begin{align*}
+	   \bra{\tpsi} \tA_0^0\tB_0^0 \ket{\tpsi} 
+	= &\bra{\tpsi}(\tA_\ast^\diamond + \tA_\ast^\perp) \tA_0^0\tB_0^0 (\tA_\ast^\diamond + \tA_\ast^\perp)\ket{\tpsi} \\
+	= & \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_\ast^\perp\ket{\tpsi} \\
+	&+\bra{\tpsi}\tA_\ast^\perp \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\perp \tA_0^0\tB_0^0 \tA_\ast^\perp\ket{\tpsi}\\
+	= & \bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_0^\perp\ket{\tpsi} \\
+	&+\bra{\tpsi}\tA_0^\perp \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_0^\perp \tA_0^0\tB_0^0 \tA_0^\perp\ket{\tpsi}\\
+	=&\bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi},
+\end{align*}
+where we use the facts that $\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi}$, $\tA_\ast^\perp \ket{\tpsi} = \tA_0^\perp \ket{\tpsi}$ and that 
+$\spn(\tA_0^0) \cap \spn(\tA_0^\perp) = \emptyset$. 
+This means that if Alice and Bob share the state $\tB_\ast^\diamond \ket{\tpsi}/\|\tB_\ast^\diamond \ket{\tpsi}\|$ and apply 
+$\tA_0^0\tB_0^0$, the conditional probability is
+\begin{align}
+	\frac{\bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi}}{\bra{\tpsi} \tB_\ast^\diamond \tB_\ast^\diamond \ket{\tpsi}} = \frac{\cos^2(\pi/4d)}{2}.
+\end{align} 
+We can re-normalize the other correlations of $a,b \in [2]$ when $x,y \in [2]$ similarly and get a new set of correlations 
+which achieves the maximal value of $\langle \1_{-\cot(\pi/2d)}\rangle$. 
+The conclusion of \cref{lm:chsh_comp} follows the application of \cref{thm:selftest} on the state $\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi}/\|\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi}\|$ as $\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}$.
+\end{proof}
+Note that the combination of \cref{lm:chsh_comp} with \cref{prop:2d-subspace} gives us that 
+$\tB_0\tB_1$ has eigenvalues $\omega_d$ and $\omega_d^{-1}$.
+
+%------------------------------------------------------------------------
+\subsection{The single value test}
+%------------------------------------------------------------------------
+By the following test, we want to make sure that some unitary $U$ has eigenvalue $1$.
+In this test $X = \{\ast\}$, $Y = \{0,1,\ast\}$, $A = \{\diamond, \perp\}$ and $B = \{0,1, \diamond, \perp\}$.
+The scoring rules are
+\begin{itemize}
+	\item \textbf{Case 1} $x = y = \ast$: Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
+	they score only if $a = b$;
+	\item \textbf{Case 2} $x =\ast$ and $y = 0$: when Alice answer $\diamond$, Bob should answer $0$, when 
+	Alice answer$\perp$ all answers of Bob are accepted;
+	\item \textbf{Case 3} $x = \ast$ and $y = 1$: when Alice answer $\diamond$, Bob should answer $0$, when 
+	Alice answer$\perp$ all answers of Bob are accepted.
+\end{itemize}
+
+Define the subspace $V = \spn\{ \ket{u_0} \}$.
+The ideal strategy has projective measurement 
+\begin{align*}
+&A_\ast^\diamond = B_\ast^\diamond= \ketbra{u_0}{u_0}, 
+&&A_\ast^\perp = B_\ast^\perp = \1 - \ketbra{u_0}{u_0},\\
+&B_0^0|_V = B_1^0|_V = \ketbra{u_0}{u_0}, 
+&&B_0^1|_V = B_1^1|_V = 0.
+\end{align*}
+The shared state is 
+\begin{align}
+	\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{i \in [d]} \ket{u_i}\ket{u_i}.
+\end{align}
+Note that the shared state is the same as the one used in the extended weighted CHSH game.
+So are the observables $B_0$ and $B_1$.
+
+It is easy to calculate the ideal correlation, which is
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{|c|c||c|c|c|c|c|c|}
+\hline
+\multicolumn{2}{|c|}{} &
+\multicolumn{2}{|c|}{$y=\ast$} &
+\multicolumn{2}{|c|}{$y=0$} &
+\multicolumn{2}{|c|}{$y=1$}\\
+\cline{3-8}
+\multicolumn{2}{|c|}{} &$b = \diamond$ & $b = \perp$ & $b = 0$ & $b = 1$ & $b = 0$ & $b = 1$\\
+\hline
+\hline
+\multirow{2}{*}{$x = \ast$} & $a=\diamond$ & $1/d$ & 0 & $1/d$ & 0 & $1/d$ & 0 \\
+\cline{2-8}
+&$a=\perp$ & 0 & $(d-1)/d$ & \small $\pr{\perp0}{\ast0}$ & \small $\frac{d-1}{d} -\pr{\perp0}{\ast0}$  
+& \small $\pr{\perp0}{\ast1}$ & \small $\frac{d-1}{d}- \pr{\perp0}{\ast0}$  \\
+\hline
+\end{tabular}
+\caption{Ideal correlation of the single value test.}
+\end{center}
+\end{table}
+The reason we have $y=0$ or $y=1$ is that we want Bob to reuse operators from $\LS$ and we want to
+conclude that $B_0B_1$ has eigenvalue $1$.
+
+\begin{lemma}
+	\label{lm:svt_comp}
+	If a quantum strategy$(\{\tA_\ast^a\}_a, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}$ has the same behaviour as
+	the optimal one, then $(\tB_0^0 - \tB_0^1)(\tB_1^0-\tB_1^1)$ has eigenvalue $1$.
+\end{lemma}
+\begin{proof}
+By the marginal distribution we know that $\| A_\ast^\diamond \ket{\psi}\| = \frac{1}{\sqrt{d}}$.
+From the condition that $P(\diamond 0|\ast 0) = 1/d$, we know
+\begin{align}
+	\frac{  \bra{\psi} \tA_\ast^\diamond  \tB_0^0 \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|^2} = 1,
+\end{align}
+which implies that 
+\begin{align}
+ \tB_0^0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
+\end{align}
+With similar reasoning, we get
+\begin{align}
+ \tB_1^0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
+\end{align}
+Hence $ \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} $ is in the intersection of $\supp(\tB_0^0)$ and $\supp(\tB_1^0)$.
+Since $\supp(\tB_y^0)$ and $\supp(\tB_y^1)$ are disjoint, we know
+\begin{align*}
+	(\tB_y^0 - \tB_y^1)  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}  =  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}
+\end{align*}
+for $y = 0,1$.
+Therefor, we know $ \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} $ is an eigenvector of $\tB_0\tB_1$ with eigenvalue $1$ because
+\begin{align}
+	\tB_0\tB_1 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \tB_0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} =  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
+\end{align}
+\end{proof}
+In the later section, when we apply this test to make sure some unitary $U$ has eigenvalue $1$, 
+we denote the test by $\SVT_U$.
+
 \bibliographystyle{alphaurl}
@@
 \end{proof}
+%=====================================
+\section{Construction of $\Gamma(\LS)$}
+\label{sec:construct}
+%=====================================
+In this section, we are going to embed the group $\Pg_{\LS}$ into a solution group $\Gamma(\LS)$ of a linear system game.
+What we do is to write any generator with arbitrary order as a product of new order-$2$ generators and rewrite all
+the relations with the new generators. In the end, we can get rid of the generators $y_i$ and $u$ and all 
+the remaining generators are order-$2$.
+
+We first embed the relation $xzx^{-1}z^{-1} = \J$ in a linear system game very similar to the Magic Square game.
+It has been shown that the following relations embeds $xzx^{-1}z^{-1} = \J$ \footnote{For example, Fig.~$11$ of Ref.~\cite{coladan2017}
+proves it in a group picture.}. Let $y_3 = z$ and $y_7 = x$ and the linear relations are 
+\begin{align*}
+	&y_1y_2y_3 = e,
+	&&y_4y_5y_6 = e,
+	&&y_7y_8y_9 = e,\\
+	&y_1^{-1}y_4^{-1}y_7^{-1} = e,
+	&&y_2^{-1}y_5^{-1}y_8^{-1} = \J,
+	&&y_3^{-1}y_6^{-1}y_9^{-1} = e.
+\end{align*}
+We refer to these set of linear relations as the $\MS_l$ relations.
+The magic square game also introduces some commutation relations:
+\begin{align*}
+	&[y_1, y_2] = [y_1, y_3] = [y_1, y_4] = [y_1,y_7] = e,\\
+	&[y_2, y_3] = [y_2, y_5] = [y_2, y_8] = e,\\
+	&[y_3, y_6] = [y_3, y_9] = e,\\
+	&[y_4, y_7] = [y_4,y_5] =  [y_4,y_6] = e, \\
+	& [y_5,y_6] =  [y_5,y_8] = e,\\
+	& [y_6,y_9] = e,\\
+	& [y_7,y_8] =  [y_7,y_9] = e,\\
+	&[y_8,y_9] = e.
+\end{align*}
+The set of the commutation relations above is denoted by $\MS_c$.
+So we redefine $\Pg_{\LS}$ as 
+\begin{align}
+	\Pg_{\LS} = \langle \{y_i\}_{i=1}^9,u,\J: \MS_l \cup \MS_c \cup \{ [\J, y_i] = [\J, u] = e,
+					uy_7u^{-1} = y_7^2, u^{-1}y_3u = y_3^2\}	 \rangle.
+\end{align}
+Then we can use a procedure similar to the one used in the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017} to 
+embed $\Pg_{\LS}$ into a group with only order-$2$ generators except for $\J$, whose order is implicit.
+
+We start by introducing $y_{3,1}$ and $y_{3,2}$ of order $2$ such that $y_3 = y_{3,1}y_{3,2}$ 
+and $y_{3,1}$ commutes with $u$, $\J$ and $y_i$ for $ i \neq 3$.
+Then the relation $uy_3u^{-1} = y_3^2$ is rewritten as $uy_{3,2}u^{-1} = y_{3,2}y_{3,1}y_{3,2}$ so we introduce $y_{3,3} = y_{3,2}y_{3,1}y_{3,2}$.
+The group $\Pg_{\LS}$ becomes
+\begin{equation}
+\begin{aligned}
+	\Pg_{\LS} = \langle y_{3,1}, y_{3,2}, y_{3,3}, u, \{y_i\}_{i \neq 3} \J: &y_{3,1}^2 = y_{3,2}^2 = y_{3,3}^2 =e,\\
+	&\J \text{ commute with  all the generators, } [y_i,y_{3,1}] = [u,y_{3,1}] =  e \text{ for } i \neq 3,\\
+	&\MS_c \text{ with $y_3$ replaced by $y_{3,2}$},
+	\MS_l \text{ with $y_3$ replaced by $y_{3,1}y_{3,2}$},\\
+	& u^{-1}y_7u = y_7^2, 
+	y_{3,3} = y_{3,2}y_{3,1}y_{3,2}, uy_{3,2}u^{-1} = y_{3,3}\rangle.
+\end{aligned}
+\end{equation}
+Next, we introduce $y_{7,1}$ and $y_{7,2}$ of order $2$ such that $y_7 = y_{7,1}y_{7,2}$ and 
+$y_{7,1}$ commutes with $u$, $\J$ and $y_i$ for $i \neq 3,7$.
+Then the relation $u^{-1}y_7u = y_7^2$ is rewritten as $u^{-1}y_{7,2}u = y_{7,2}y_{7,1}y_{7,2}$ so we introduce $y_{7,3} = y_{7,2}y_{7,1}y_{7,2}$.
+The relation $y_7y_{3,1}y_7^{-1} = y_{3,1}$ is rewritten as $y_{7,2}y_{3,1}y_{7,2} = y_{7,1}y_{3,1}y_{7,1}$ so we introduce $y_{7,4} = y_{7,1}y_{3,1}y_{7,1}$.
+The group $\Pg_{\LS}$ becomes
+\begin{equation}
+\begin{aligned}
+	\Pg_{\LS} = \langle \{y_{3,i}\}_{i=1}^3, \{ y_{7,i} \}_{i=1}^4, \{y_i\}_{i\neq 3, 7}, u, \J: &\{y_{3,i}\}_{i=1}^3 \{y_{7,i}\}_{i=1}^4 \text{ of order } 2;\\
+	&\J \text{ commutes with all the generators, } [u, y_{3,1}] = [u, y_{7,1}] = e,\\
+	&y_{3,1}, y_{7,1} \text{ commute with } y_i,\; i \neq 3,7,\\
+	& \MS_c \text{ with $y_3, y_7$ replaced by $y_{3,2}, y_{7,2}$},\\
+	& \MS_l \text{ with $y_3$, $y_7$ replaced by $y_{3,1}y_{3,2}$ and $y_{7,1}y_{7,2}$} \\
+	&y_{3,3} = y_{3,2}y_{3,1}y_{3,2}, uy_{3,2}u^{-1} = y_{3,3}, \\
+	&y_{7,3} = y_{7,2}y_{7,1}y_{7,2}, u^{-1}y_{7,2}u = y_{7,3},\\
+	&y_{7,4} = y_{7,1}y_{3,1}y_{7,1}, y_{7,2}y_{3,1}y_{7,2} = y_{7,4} \rangle
+\end{aligned}
+\end{equation}
+To replace $u$, we introduce $u_1, u_2$ of order $2$ such that $u = u_1u_2$ and $u_1$ commutes with
+$y_i$ for $i \neq 3,7$ and $\J$.
+The conjugacy relations involving $u$ are $uy_{3,2}u^{-1} = y_{3,3}$, $u^{-1}y_{7,2}u = y_{7,3}$,
+$uy_{3,1}u^{-1} = y_{3,1}$ and $uy_{7,1}u^{-1} = y_{7,1}$. So we need to introduce $u_3,u_4,u_5,u_6$ such that 
+\begin{align*}
+	u_3 = u_2y_{3,2}u_2 = u_1y_{3,3}u_1, \\
+	u_4 = u_1y_{7,2}u_1 = u_2y_{7,3}u_2,\\
+	u_5 = u_2y_{3,1}u_2 = u_1y_{3,1}u_1,\\
+	u_6 = u_2y_{7,1}u_2 = u_1y_{7,1}u_1.
+\end{align*}
+At this stage $\Pg_{\LS}$ has generators $\{y_{3,i}\}_{i=1}^3, \{ y_{7,i} \}_{i=1}^4, \{y_i\}_{i\neq 3, 7}, \{u_i\}_{i=1}^6$ with $6$ linear relations and $44$ conjugacy relations.
+
+For the remaining $y_i$'s, we use $y_1$ as an example and the same steps apply to the other $y_i$'s.
+The conjugacy relations involving $y_1$ are 
+\begin{align*}
+	y_{1}y_{3,1} y_1^{-1} = y_{3,1},
+	&&y_{1}y_{7,1}y_1^{-1} = y_{7,1}.
+\end{align*}
+and $4$ commutation relations from $\MS_c$.
+So we need to introduce $y_{1,i}$ for $i = 1, 2 \dots 8$ such that they all are of order $2$ and
+\begin{align*}
+&y_1= y_{1,1} y_{1,2}\\
+&y_{1,3} = y_{1,2} y_{3,1}y_{1,2} = y_{1,1} y_{3,1}y_{1,1},\\
+&y_{1,4} = y_{1,2} y_{7,1}y_{1,2} = y_{1,1} y_{7,1}y_{1,1},\\
+&y_{1,5} = y_{1,2} y_{2}y_{1,2} = y_{1,1} y_{2}y_{1,1},\\
+&y_{1,6} = y_{1,2} y_{3,2}y_{1,2} = y_{1,1} y_{3,2}y_{1,1},\\
+&y_{1,7} = y_{1,2} y_{4}y_{1,2} = y_{1,1} y_{4}y_{1,1},\\
+&y_{1,8} = y_{1,2} y_{7,2}y_{1,2} = y_{1,1} y_{7,2}y_{1,1}.
+\end{align*}
+The new commutation relations are $y_{1,1}$ commutes with all the remaining $y_j$'s
+and commutation relations from $\MS_c$ involving $y_1$ with $y_1$ replaced by $y_{1,2}$.
+Then we repeat this process with $y_2$.
+In summary, replacing $y_1,y_2,y_4,y_5,y_6,y_8,y_9$ introduces $8+9+10+11+12+13+14 = 77$ new variables 
+and $12+14+16+18+20+22+24 = 126$ new conjugacy relations. 
+In total $\Pg_{\LS}$ has $90$ variables excluding $\J$, $6$ linear relations and $170$ conjugacy relations.
+
+Then following the recipe given in the proofs of Proposition~$4.2$ and Lemma~$4.4$ in Ref.~\cite{slofstra2017}, 
+we embed $\Pg_{\LS}$ into the solution 
+group $\Gamma(\LS)$ with $2351$ variables and $1916$ linear relations. 
+Alice's output alphabet is of size $64$ and of size $2$ for Bob.
+
+Such linear system game has at the biggest size when $a = 5$ or the special relation is $uxu^{-1} = x^5$.
+The biggest game has $2465$ variables and $2006$ equations. We leave the derivation for curious readers.
+
 \end{document}

### 2018-12-15 Draft/draft.tex
Honghao: added my progress on the main proof

@@
 \newcommand{\tpsi}{\tilde{\psi}}
+\newcommand{\tri}{\Delta}
 
@@
 
-\title{Self-test EPR pair with constant alphabet}
+\title{Self-test prime dimensional EPR pairs with constant alphabet}
 
@@
 %----------------------------------------------------------------
-The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the qudit Pauli group,
-which is defined as
+The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the 
+following group
 \begin{align}
-	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
+	\Pg_{\LS} = \langle u, x : uxu^{-1} = x^2 \rangle.
 \end{align}
-The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
-We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
-by the following relations
-\begin{align}
-\label{eq:sim}
-	u_x x u_x = x^2, \quad
-	u_z z u_z = z^2.
-\end{align}
-Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
-\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
-but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
-Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
-relation $xzx^{-1}z^{-1} = \J$.
-
-It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
-where  $\paulix{d}$ and $\pauliz{d}$ are defined by
-\begin{align}
-	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
-	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
-\end{align}
-Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
-we can verify that 
-\begin{align}
-	U_xU_z = \1 = U_zU_x,
-\end{align}
-Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
-In the end, we define $\Pg_{\LS}$ by
-\begin{equation}
-\begin{aligned}
-	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
-	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
-\end{aligned}
-\end{equation}
-This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
-The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
+%\begin{align}
+%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
+%\end{align}
+%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
+%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
+%by the following relations
+%\begin{align}
+%\label{eq:sim}
+%	u_x x u_x = x^2, \quad
+%	u_z z u_z = z^2.
+%\end{align}
+%Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
+%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
+%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
+%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
+%relation $xzx^{-1}z^{-1} = \J$.
+%
+%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
+%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
+%\begin{align}
+%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
+%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
+%\end{align}
+%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
+%we can verify that 
+%\begin{align}
+%	U_xU_z = \1 = U_zU_x,
+%\end{align}
+%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
+%In the end, we define $\Pg_{\LS}$ by
+%\begin{equation}
+%\begin{aligned}
+%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
+%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
+%\end{aligned}
+%\end{equation}
+%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
+%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
 See Appendix~\ref{sec:construct} for details.
@@
 By the following test, we want to make sure that some unitary $U$ has eigenvalue $1$.
-In this test $X = \{\ast\}$, $Y = \{0,1,\ast\}$, $A = \{\diamond, \perp\}$ and $B = \{0,1, \diamond, \perp\}$.
+In this test $X = \{\tri \}$, $Y = \{0,1,\tri\}$, $A = \{\diamond, \perp\}$ and $B = \{0,1, \diamond, \perp\}$.
 The scoring rules are
 \begin{itemize}
-	\item \textbf{Case 1} $x = y = \ast$: Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
+	\item \textbf{Case 1} $x = y = \tri$: Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
 	they score only if $a = b$;
-	\item \textbf{Case 2} $x =\ast$ and $y = 0$: when Alice answer $\diamond$, Bob should answer $0$, when 
+	\item \textbf{Case 2} $x =\tri$ and $y = 0$: when Alice answer $\diamond$, Bob should answer $0$, when 
 	Alice answer$\perp$ all answers of Bob are accepted;
-	\item \textbf{Case 3} $x = \ast$ and $y = 1$: when Alice answer $\diamond$, Bob should answer $0$, when 
+	\item \textbf{Case 3} $x = \tri$ and $y = 1$: when Alice answer $\diamond$, Bob should answer $0$, when 
 	Alice answer$\perp$ all answers of Bob are accepted.
@@
 \begin{align*}
-&A_\ast^\diamond = B_\ast^\diamond= \ketbra{u_0}{u_0}, 
-&&A_\ast^\perp = B_\ast^\perp = \1 - \ketbra{u_0}{u_0},\\
+&A_\tri^\diamond = B_\tri^\diamond= \ketbra{u_0}{u_0}, 
+&&A_\tri^\perp = B_\tri^\perp = \1 - \ketbra{u_0}{u_0},\\
 &B_0^0|_V = B_1^0|_V = \ketbra{u_0}{u_0}, 
@@
 \multicolumn{2}{|c|}{} &
-\multicolumn{2}{|c|}{$y=\ast$} &
+\multicolumn{2}{|c|}{$y=\tri$} &
 \multicolumn{2}{|c|}{$y=0$} &
@@
 \hline
-\multirow{2}{*}{$x = \ast$} & $a=\diamond$ & $1/d$ & 0 & $1/d$ & 0 & $1/d$ & 0 \\
+\multirow{2}{*}{$x = \tri$} & $a=\diamond$ & $1/d$ & 0 & $1/d$ & 0 & $1/d$ & 0 \\
 \cline{2-8}
-&$a=\perp$ & 0 & $(d-1)/d$ & \small $\pr{\perp0}{\ast0}$ & \small $\frac{d-1}{d} -\pr{\perp0}{\ast0}$  
-& \small $\pr{\perp0}{\ast1}$ & \small $\frac{d-1}{d}- \pr{\perp0}{\ast0}$  \\
+&$a=\perp$ & 0 & $(d-1)/d$ & \small $\pr{\perp0}{\tri0}$ & \small $\frac{d-1}{d} -\pr{\perp0}{\tri0}$  
+& \small $\pr{\perp0}{\tri1}$ & \small $\frac{d-1}{d}- \pr{\perp0}{\tri0}$  \\
 \hline
@@
 	\label{lm:svt_comp}
-	If a quantum strategy$(\{\tA_\ast^a\}_a, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}$ has the same behaviour as
+	If a quantum strategy$(\{\tA_\tri^a\}_a, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}$ has the same behaviour as
 	the optimal one, then $(\tB_0^0 - \tB_0^1)(\tB_1^0-\tB_1^1)$ has eigenvalue $1$.
@@
 \begin{proof}
-By the marginal distribution we know that $\| A_\ast^\diamond \ket{\psi}\| = \frac{1}{\sqrt{d}}$.
-From the condition that $P(\diamond 0|\ast 0) = 1/d$, we know
+By the marginal distribution we know that $\| A_\tri^\diamond \ket{\psi}\| = \frac{1}{\sqrt{d}}$.
+From the condition that $P(\diamond 0|\tri 0) = 1/d$, we know
 \begin{align}
-	\frac{  \bra{\psi} \tA_\ast^\diamond  \tB_0^0 \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|^2} = 1,
+	\frac{  \bra{\psi} \tA_\tri^\diamond  \tB_0^0 \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|^2} = 1,
 \end{align}
@@
 \begin{align}
- \tB_0^0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
+ \tB_0^0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
 \end{align}
@@
 \begin{align}
- \tB_1^0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
+ \tB_1^0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
 \end{align}
-Hence $ \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} $ is in the intersection of $\supp(\tB_0^0)$ and $\supp(\tB_1^0)$.
+Hence $ \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} $ is in the intersection of $\supp(\tB_0^0)$ and $\supp(\tB_1^0)$.
 Since $\supp(\tB_y^0)$ and $\supp(\tB_y^1)$ are disjoint, we know
 \begin{align*}
-	(\tB_y^0 - \tB_y^1)  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}  =  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}
+	(\tB_y^0 - \tB_y^1)  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}  =  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}
 \end{align*}
 for $y = 0,1$.
-Therefor, we know $ \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} $ is an eigenvector of $\tB_0\tB_1$ with eigenvalue $1$ because
+Therefor, we know $ \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} $ is an eigenvector of $\tB_0\tB_1$ with eigenvalue $1$ because
 \begin{align}
-	\tB_0\tB_1 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \tB_0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} =  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
+	\tB_0\tB_1 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \tB_0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} =  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
 \end{align}
@@
 we denote the test by $\SVT_U$.
+
+%=====================================
+\section{Main result}
+\label{sec:main}
+%=====================================
+%-----------------------------------------------------------------
+\subsection{The game $\G{d}$}
+%-----------------------------------------------------------------
+Assume the linear system game has $n$ variables and $m$ equations.
+Alice receives $x \in \{1,\dots m+4 \}$ and Bob receives
+$y \in \{1,\dots,n+2\}$. The scoring rules are the following:
+\begin{itemize}
+	\item when $x \in \{1,\dots m\}$ and $y \in \{1, \dots n\}$, they are scored according to the 
+	linear system game, $\LS$;
+	\item when $x \in \{m+1, m+2, m+3\}$ and $y \in \{1, 2, n+1\}$, they are scored according to $\CHSH_X$,
+	where 
+	\begin{align}
+		&\ast_A = m+1, \quad 0_A = m+2,\quad 1_A = m+3,\\
+		&\ast_B = n+1,\quad 0_B = 1, \quad 1_A = 2,
+	\end{align}
+	are the inputs for the game $\CHSH_X$
+	(The intuition behind is that $B_1B_2 = X$.);
+	\item when $x = m+4$ and  $y \in \{1,2,n+2\}$, they are scored according to $\SVT_X$, where
+	\begin{align}
+		& \tri_A = m+4 \\
+		& \tri_B = n+2, \quad 1_B = 1,\quad 2_B = 2
+	\end{align}
+	are the inputs for the game $\SVT_X$;
+	\item otherwise, they score $0$.
+\end{itemize}
+Note that the dimension $d$ is defined in the rules of $\CHSH_X$.
+Next we are going to prove that the strategy winning this game optimally can self-test $d$-dimensional EPR pair.
+
+%-----------------------------------------------------------------
+\subsection{Proof}
+%-----------------------------------------------------------------
+\hl{This subsection needs to be formalized.}
+By Lemma~$4.3$ of \cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
+of the linear system game: 
+For each variable $\{ x_i \}_{i=1}^n$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
+The condition that they agree with assignment to variables means that 
+\begin{align}
+	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
+\end{align}
+and the condition that Alice's assignments satisfy the constraint means that 
+\begin{align}
+	\Tr(\rho_A \Pi_{j: A_{ij} \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m
+\end{align}
+where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$, so for  any $\ket{v} \in \supp(\rho_A)$,
+we have 
+\begin{align}
+\Pi_{j:A_{ij} \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m.
+\end{align}
+Since the relation $u^{-1}xu = x^2$ is embedded in this linear system game, we know
+\begin{align}
+	\sigma_A(u)^\dagger A_1A_2 \sigma_A(u) \ket{v}= (A_1A_2)^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
+\end{align}
+For simplicity, we define $X = A_1A_2$ and $U = \sigma_A(u)$.
+For simplicity, we define $X = A_1A_2$ and $U = \sigma_A(u)$.
+The condition becomes
+\begin{align}
+	UXU^\dagger \ket{v} = X^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
+\end{align}
+On the subspace $\supp(\rho_A)$, we have the equality
+\begin{align}
+	\label{eq:sim}
+	UXU^\dagger X^{-2} = \1.
+\end{align}
+We will come back to the implication of this condition later.
+
+Suppose the support of $\tA_\ast^\diamond$ is spanned by $\ket{u_0}$ and $\ket{u_1}$ and 
+define $\ket{x_1} = 1/\sqrt{2}(\ket{u_0} + i\ket{u_1})$. 
+The test $\CHSH_X$ tells that $\ket{x_1}$ is the eigenvector of $X$ with eigenvalue $e^{i\pi/d} = \omega_d$.
+Similarly, define $\ket{x_{d-1}} = 1/\sqrt{2}(\ket{u_0} - i\ket{u_1})$ such that $X \ket{x_{d-1}} = \omega_d^{d-1}\ket{x_{d-1}}$.
+We know 
+\begin{align}
+	\tA_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi} = \frac{1}{\sqrt{d}} (\ket{u_0}\ket{u_0} + \ket{u_1}\ket{u_1}).
+\end{align}
+If we restrict to Alice's system, we get 
+\begin{align}
+	\Tr_B(\tA_\ast^\diamond \ketbra{\tpsi}{\tpsi} \tA_\ast^\diamond) =\tA_\ast^\diamond \rho_A \tA_\ast^\diamond = 
+ \frac{1}{d} \ketbra{u_0}{u_0} + \ketbra{u_1}{u_1} = \frac{1}{d} \tA_\ast^\diamond.
+\end{align}
+Hence $\rho_A$ acts as $\1$ on $\supp(\tA_\ast^\diamond)$.
+We also know that there exists local unitary $U_A$ such that 
+\begin{align}
+U_A \tA_\ast^\diamond U_A^\dagger = \ketbra{x_1}{x_1}+\ketbra{x_{d-1}}{x_{d-1}}
+\end{align}
+and 
+\begin{align}
+\Tr(\ketbra{x_1}{x_1} \rho_A)
+=\Tr(U_A \ketbra{u_0}{u_0} U_A^\dagger \rho_A) 
+= \frac{1}{d} \Tr(U_A\ketbra{u_0}{u_0} U_A^\dagger) 
+= \frac{1}{d},
+\end{align}
+and similarly $\Tr( \ketbra{x_{d-1}}{x_{d-1}}\rho_A) = 1/d$.
+
+Next, we calculate the eigen-decomposition of $X$ in $\supp(\rho_A)$.
+Based on \cref{eq:sim}, we know
+\begin{align}
+\label{eq:ladder}
+ XU^\dagger \ket{x_1} = U^\dagger X^2 \ket{x_1} = \omega_d^2 U^\dagger \ket{x_1},
+\end{align}
+so $U^\dagger \ket{x_1}$ is an eigenvector of $X$ with eigenvalue $\omega_d^2$.
+By induction, we know $X (U^\dagger)^i \ket{x_1} = \omega_d^{2^i} (U^\dagger)^i\ket{x_1}$. 
+From the set $\{(U^\dagger)^i \ket{x_1}\}_{i=0}^{d-2}$, we can identify $\ket{x_i}$ for $i = 1 \dots  d-1$
+such that $X \ket{x_i} = \omega_d^i \ket{x_i}$.
+From the single value test, we know 
+\begin{align}
+	\tA_\triangle^\diamond \ket{\tpsi} = \tA_\triangle^\diamond \x \tB_\triangle^\diamond \ket{\tpsi} = \frac{1}{\sqrt{d}}
+	\ket{x_0}\ket{x_0}
+\end{align}
+where $X \ket{x_0} = \ket{x_0}$. 
+The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
+\begin{align}
+	X \ket{x_i} = \omega_d^i \ket{x_i}.
+\end{align}
+The other effect of $\SVT_X$ is that we know 
+\begin{align}
+	\tA_\triangle^\diamond \rho_A \tA_\triangle^\diamond = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^\diamond.
+\end{align}
+\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
 
@@
 %=====================================
-In this section, we are going to embed the group $\Pg_{\LS}$ into a solution group $\Gamma(\LS)$ of a linear system game.
-What we do is to write any generator with arbitrary order as a product of new order-$2$ generators and rewrite all
-the relations with the new generators. In the end, we can get rid of the generators $y_i$ and $u$ and all 
-the remaining generators are order-$2$.
-
-We first embed the relation $xzx^{-1}z^{-1} = \J$ in a linear system game very similar to the Magic Square game.
-It has been shown that the following relations embeds $xzx^{-1}z^{-1} = \J$ \footnote{For example, Fig.~$11$ of Ref.~\cite{coladan2017}
-proves it in a group picture.}. Let $y_3 = z$ and $y_7 = x$ and the linear relations are 
-\begin{align*}
-	&y_1y_2y_3 = e,
-	&&y_4y_5y_6 = e,
-	&&y_7y_8y_9 = e,\\
-	&y_1^{-1}y_4^{-1}y_7^{-1} = e,
-	&&y_2^{-1}y_5^{-1}y_8^{-1} = \J,
-	&&y_3^{-1}y_6^{-1}y_9^{-1} = e.
-\end{align*}
-We refer to these set of linear relations as the $\MS_l$ relations.
-The magic square game also introduces some commutation relations:
-\begin{align*}
-	&[y_1, y_2] = [y_1, y_3] = [y_1, y_4] = [y_1,y_7] = e,\\
-	&[y_2, y_3] = [y_2, y_5] = [y_2, y_8] = e,\\
-	&[y_3, y_6] = [y_3, y_9] = e,\\
-	&[y_4, y_7] = [y_4,y_5] =  [y_4,y_6] = e, \\
-	& [y_5,y_6] =  [y_5,y_8] = e,\\
-	& [y_6,y_9] = e,\\
-	& [y_7,y_8] =  [y_7,y_9] = e,\\
-	&[y_8,y_9] = e.
-\end{align*}
-The set of the commutation relations above is denoted by $\MS_c$.
-So we redefine $\Pg_{\LS}$ as 
-\begin{align}
-	\Pg_{\LS} = \langle \{y_i\}_{i=1}^9,u,\J: \MS_l \cup \MS_c \cup \{ [\J, y_i] = [\J, u] = e,
-					uy_7u^{-1} = y_7^2, u^{-1}y_3u = y_3^2\}	 \rangle.
-\end{align}
-Then we can use a procedure similar to the one used in the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017} to 
-embed $\Pg_{\LS}$ into a group with only order-$2$ generators except for $\J$, whose order is implicit.
-
-We start by introducing $y_{3,1}$ and $y_{3,2}$ of order $2$ such that $y_3 = y_{3,1}y_{3,2}$ 
-and $y_{3,1}$ commutes with $u$, $\J$ and $y_i$ for $ i \neq 3$.
-Then the relation $uy_3u^{-1} = y_3^2$ is rewritten as $uy_{3,2}u^{-1} = y_{3,2}y_{3,1}y_{3,2}$ so we introduce $y_{3,3} = y_{3,2}y_{3,1}y_{3,2}$.
-The group $\Pg_{\LS}$ becomes
-\begin{equation}
-\begin{aligned}
-	\Pg_{\LS} = \langle y_{3,1}, y_{3,2}, y_{3,3}, u, \{y_i\}_{i \neq 3} \J: &y_{3,1}^2 = y_{3,2}^2 = y_{3,3}^2 =e,\\
-	&\J \text{ commute with  all the generators, } [y_i,y_{3,1}] = [u,y_{3,1}] =  e \text{ for } i \neq 3,\\
-	&\MS_c \text{ with $y_3$ replaced by $y_{3,2}$},
-	\MS_l \text{ with $y_3$ replaced by $y_{3,1}y_{3,2}$},\\
-	& u^{-1}y_7u = y_7^2, 
-	y_{3,3} = y_{3,2}y_{3,1}y_{3,2}, uy_{3,2}u^{-1} = y_{3,3}\rangle.
-\end{aligned}
-\end{equation}
-Next, we introduce $y_{7,1}$ and $y_{7,2}$ of order $2$ such that $y_7 = y_{7,1}y_{7,2}$ and 
-$y_{7,1}$ commutes with $u$, $\J$ and $y_i$ for $i \neq 3,7$.
-Then the relation $u^{-1}y_7u = y_7^2$ is rewritten as $u^{-1}y_{7,2}u = y_{7,2}y_{7,1}y_{7,2}$ so we introduce $y_{7,3} = y_{7,2}y_{7,1}y_{7,2}$.
-The relation $y_7y_{3,1}y_7^{-1} = y_{3,1}$ is rewritten as $y_{7,2}y_{3,1}y_{7,2} = y_{7,1}y_{3,1}y_{7,1}$ so we introduce $y_{7,4} = y_{7,1}y_{3,1}y_{7,1}$.
-The group $\Pg_{\LS}$ becomes
-\begin{equation}
-\begin{aligned}
-	\Pg_{\LS} = \langle \{y_{3,i}\}_{i=1}^3, \{ y_{7,i} \}_{i=1}^4, \{y_i\}_{i\neq 3, 7}, u, \J: &\{y_{3,i}\}_{i=1}^3 \{y_{7,i}\}_{i=1}^4 \text{ of order } 2;\\
-	&\J \text{ commutes with all the generators, } [u, y_{3,1}] = [u, y_{7,1}] = e,\\
-	&y_{3,1}, y_{7,1} \text{ commute with } y_i,\; i \neq 3,7,\\
-	& \MS_c \text{ with $y_3, y_7$ replaced by $y_{3,2}, y_{7,2}$},\\
-	& \MS_l \text{ with $y_3$, $y_7$ replaced by $y_{3,1}y_{3,2}$ and $y_{7,1}y_{7,2}$} \\
-	&y_{3,3} = y_{3,2}y_{3,1}y_{3,2}, uy_{3,2}u^{-1} = y_{3,3}, \\
-	&y_{7,3} = y_{7,2}y_{7,1}y_{7,2}, u^{-1}y_{7,2}u = y_{7,3},\\
-	&y_{7,4} = y_{7,1}y_{3,1}y_{7,1}, y_{7,2}y_{3,1}y_{7,2} = y_{7,4} \rangle
-\end{aligned}
-\end{equation}
-To replace $u$, we introduce $u_1, u_2$ of order $2$ such that $u = u_1u_2$ and $u_1$ commutes with
-$y_i$ for $i \neq 3,7$ and $\J$.
-The conjugacy relations involving $u$ are $uy_{3,2}u^{-1} = y_{3,3}$, $u^{-1}y_{7,2}u = y_{7,3}$,
-$uy_{3,1}u^{-1} = y_{3,1}$ and $uy_{7,1}u^{-1} = y_{7,1}$. So we need to introduce $u_3,u_4,u_5,u_6$ such that 
-\begin{align*}
-	u_3 = u_2y_{3,2}u_2 = u_1y_{3,3}u_1, \\
-	u_4 = u_1y_{7,2}u_1 = u_2y_{7,3}u_2,\\
-	u_5 = u_2y_{3,1}u_2 = u_1y_{3,1}u_1,\\
-	u_6 = u_2y_{7,1}u_2 = u_1y_{7,1}u_1.
-\end{align*}
-At this stage $\Pg_{\LS}$ has generators $\{y_{3,i}\}_{i=1}^3, \{ y_{7,i} \}_{i=1}^4, \{y_i\}_{i\neq 3, 7}, \{u_i\}_{i=1}^6$ with $6$ linear relations and $44$ conjugacy relations.
-
-For the remaining $y_i$'s, we use $y_1$ as an example and the same steps apply to the other $y_i$'s.
-The conjugacy relations involving $y_1$ are 
-\begin{align*}
-	y_{1}y_{3,1} y_1^{-1} = y_{3,1},
-	&&y_{1}y_{7,1}y_1^{-1} = y_{7,1}.
-\end{align*}
-and $4$ commutation relations from $\MS_c$.
-So we need to introduce $y_{1,i}$ for $i = 1, 2 \dots 8$ such that they all are of order $2$ and
-\begin{align*}
-&y_1= y_{1,1} y_{1,2}\\
-&y_{1,3} = y_{1,2} y_{3,1}y_{1,2} = y_{1,1} y_{3,1}y_{1,1},\\
-&y_{1,4} = y_{1,2} y_{7,1}y_{1,2} = y_{1,1} y_{7,1}y_{1,1},\\
-&y_{1,5} = y_{1,2} y_{2}y_{1,2} = y_{1,1} y_{2}y_{1,1},\\
-&y_{1,6} = y_{1,2} y_{3,2}y_{1,2} = y_{1,1} y_{3,2}y_{1,1},\\
-&y_{1,7} = y_{1,2} y_{4}y_{1,2} = y_{1,1} y_{4}y_{1,1},\\
-&y_{1,8} = y_{1,2} y_{7,2}y_{1,2} = y_{1,1} y_{7,2}y_{1,1}.
-\end{align*}
-The new commutation relations are $y_{1,1}$ commutes with all the remaining $y_j$'s
-and commutation relations from $\MS_c$ involving $y_1$ with $y_1$ replaced by $y_{1,2}$.
-Then we repeat this process with $y_2$.
-In summary, replacing $y_1,y_2,y_4,y_5,y_6,y_8,y_9$ introduces $8+9+10+11+12+13+14 = 77$ new variables 
-and $12+14+16+18+20+22+24 = 126$ new conjugacy relations. 
-In total $\Pg_{\LS}$ has $90$ variables excluding $\J$, $6$ linear relations and $170$ conjugacy relations.
-
-Then following the recipe given in the proofs of Proposition~$4.2$ and Lemma~$4.4$ in Ref.~\cite{slofstra2017}, 
-we embed $\Pg_{\LS}$ into the solution 
-group $\Gamma(\LS)$ with $2351$ variables and $1916$ linear relations. 
-Alice's output alphabet is of size $64$ and of size $2$ for Bob.
-
-Such linear system game has at the biggest size when $a = 5$ or the special relation is $uxu^{-1} = x^5$.
-The biggest game has $2465$ variables and $2006$ equations. We leave the derivation for curious readers.
+%In this section, we are going to embed the group $\Pg_{\LS}$ into a solution group $\Gamma(\LS)$ of a linear system game.
+%What we do is to write any generator with arbitrary order as a product of new order-$2$ generators and rewrite all
+%the relations with the new generators. In the end, we can get rid of the generators $y_i$ and $u$ and all 
+%the remaining generators are order-$2$.
+%
+%We first embed the relation $xzx^{-1}z^{-1} = \J$ in a linear system game very similar to the Magic Square game.
+%It has been shown that the following relations embeds $xzx^{-1}z^{-1} = \J$ \footnote{For example, Fig.~$11$ of Ref.~\cite{coladan2017}
+%proves it in a group picture.}. Let $y_3 = z$ and $y_7 = x$ and the linear relations are 
+%\begin{align*}
+%	&y_1y_2y_3 = e,
+%	&&y_4y_5y_6 = e,
+%	&&y_7y_8y_9 = e,\\
+%	&y_1^{-1}y_4^{-1}y_7^{-1} = e,
+%	&&y_2^{-1}y_5^{-1}y_8^{-1} = \J,
+%	&&y_3^{-1}y_6^{-1}y_9^{-1} = e.
+%\end{align*}
+%We refer to these set of linear relations as the $\MS_l$ relations.
+%The magic square game also introduces some commutation relations:
+%\begin{align*}
+%	&[y_1, y_2] = [y_1, y_3] = [y_1, y_4] = [y_1,y_7] = e,\\
+%	&[y_2, y_3] = [y_2, y_5] = [y_2, y_8] = e,\\
+%	&[y_3, y_6] = [y_3, y_9] = e,\\
+%	&[y_4, y_7] = [y_4,y_5] =  [y_4,y_6] = e, \\
+%	& [y_5,y_6] =  [y_5,y_8] = e,\\
+%	& [y_6,y_9] = e,\\
+%	& [y_7,y_8] =  [y_7,y_9] = e,\\
+%	&[y_8,y_9] = e.
+%\end{align*}
+%The set of the commutation relations above is denoted by $\MS_c$.
+%So we redefine $\Pg_{\LS}$ as 
+%\begin{align}
+%	\Pg_{\LS} = \langle \{y_i\}_{i=1}^9,u,\J: \MS_l \cup \MS_c \cup \{ [\J, y_i] = [\J, u] = e,
+%					uy_7u^{-1} = y_7^2, u^{-1}y_3u = y_3^2\}	 \rangle.
+%\end{align}
+%Then we can use a procedure similar to the one used in the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017} to 
+%embed $\Pg_{\LS}$ into a group with only order-$2$ generators except for $\J$, whose order is implicit.
+%
+%We start by introducing $y_{3,1}$ and $y_{3,2}$ of order $2$ such that $y_3 = y_{3,1}y_{3,2}$ 
+%and $y_{3,1}$ commutes with $u$, $\J$ and $y_i$ for $ i \neq 3$.
+%Then the relation $uy_3u^{-1} = y_3^2$ is rewritten as $uy_{3,2}u^{-1} = y_{3,2}y_{3,1}y_{3,2}$ so we introduce $y_{3,3} = y_{3,2}y_{3,1}y_{3,2}$.
+%The group $\Pg_{\LS}$ becomes
+%\begin{equation}
+%\begin{aligned}
+%	\Pg_{\LS} = \langle y_{3,1}, y_{3,2}, y_{3,3}, u, \{y_i\}_{i \neq 3} \J: &y_{3,1}^2 = y_{3,2}^2 = y_{3,3}^2 =e,\\
+%	&\J \text{ commute with  all the generators, } [y_i,y_{3,1}] = [u,y_{3,1}] =  e \text{ for } i \neq 3,\\
+%	&\MS_c \text{ with $y_3$ replaced by $y_{3,2}$},
+%	\MS_l \text{ with $y_3$ replaced by $y_{3,1}y_{3,2}$},\\
+%	& u^{-1}y_7u = y_7^2, 
+%	y_{3,3} = y_{3,2}y_{3,1}y_{3,2}, uy_{3,2}u^{-1} = y_{3,3}\rangle.
+%\end{aligned}
+%\end{equation}
+%Next, we introduce $y_{7,1}$ and $y_{7,2}$ of order $2$ such that $y_7 = y_{7,1}y_{7,2}$ and 
+%$y_{7,1}$ commutes with $u$, $\J$ and $y_i$ for $i \neq 3,7$.
+%Then the relation $u^{-1}y_7u = y_7^2$ is rewritten as $u^{-1}y_{7,2}u = y_{7,2}y_{7,1}y_{7,2}$ so we introduce $y_{7,3} = y_{7,2}y_{7,1}y_{7,2}$.
+%The relation $y_7y_{3,1}y_7^{-1} = y_{3,1}$ is rewritten as $y_{7,2}y_{3,1}y_{7,2} = y_{7,1}y_{3,1}y_{7,1}$ so we introduce $y_{7,4} = y_{7,1}y_{3,1}y_{7,1}$.
+%The group $\Pg_{\LS}$ becomes
+%\begin{equation}
+%\begin{aligned}
+%	\Pg_{\LS} = \langle \{y_{3,i}\}_{i=1}^3, \{ y_{7,i} \}_{i=1}^4, \{y_i\}_{i\neq 3, 7}, u, \J: &\{y_{3,i}\}_{i=1}^3 \{y_{7,i}\}_{i=1}^4 \text{ of order } 2;\\
+%	&\J \text{ commutes with all the generators, } [u, y_{3,1}] = [u, y_{7,1}] = e,\\
+%	&y_{3,1}, y_{7,1} \text{ commute with } y_i,\; i \neq 3,7,\\
+%	& \MS_c \text{ with $y_3, y_7$ replaced by $y_{3,2}, y_{7,2}$},\\
+%	& \MS_l \text{ with $y_3$, $y_7$ replaced by $y_{3,1}y_{3,2}$ and $y_{7,1}y_{7,2}$} \\
+%	&y_{3,3} = y_{3,2}y_{3,1}y_{3,2}, uy_{3,2}u^{-1} = y_{3,3}, \\
+%	&y_{7,3} = y_{7,2}y_{7,1}y_{7,2}, u^{-1}y_{7,2}u = y_{7,3},\\
+%	&y_{7,4} = y_{7,1}y_{3,1}y_{7,1}, y_{7,2}y_{3,1}y_{7,2} = y_{7,4} \rangle
+%\end{aligned}
+%\end{equation}
+%To replace $u$, we introduce $u_1, u_2$ of order $2$ such that $u = u_1u_2$ and $u_1$ commutes with
+%$y_i$ for $i \neq 3,7$ and $\J$.
+%The conjugacy relations involving $u$ are $uy_{3,2}u^{-1} = y_{3,3}$, $u^{-1}y_{7,2}u = y_{7,3}$,
+%$uy_{3,1}u^{-1} = y_{3,1}$ and $uy_{7,1}u^{-1} = y_{7,1}$. So we need to introduce $u_3,u_4,u_5,u_6$ such that 
+%\begin{align*}
+%	u_3 = u_2y_{3,2}u_2 = u_1y_{3,3}u_1, \\
+%	u_4 = u_1y_{7,2}u_1 = u_2y_{7,3}u_2,\\
+%	u_5 = u_2y_{3,1}u_2 = u_1y_{3,1}u_1,\\
+%	u_6 = u_2y_{7,1}u_2 = u_1y_{7,1}u_1.
+%\end{align*}
+%At this stage $\Pg_{\LS}$ has generators $\{y_{3,i}\}_{i=1}^3, \{ y_{7,i} \}_{i=1}^4, \{y_i\}_{i\neq 3, 7}, \{u_i\}_{i=1}^6$ with $6$ linear relations and $44$ conjugacy relations. 
+%
+%For the remaining $y_i$'s, we use $y_1$ as an example and the same steps apply to the other $y_i$'s.
+%The conjugacy relations involving $y_1$ are 
+%\begin{align*}
+%	y_{1}y_{3,1} y_1^{-1} = y_{3,1},
+%	&&y_{1}y_{7,1}y_1^{-1} = y_{7,1}.
+%\end{align*}
+%and $4$ commutation relations from $\MS_c$.
+%So we need to introduce $y_{1,i}$ for $i = 1, 2 \dots 8$ such that they all are of order $2$ and
+%\begin{align*}
+%&y_1= y_{1,1} y_{1,2}\\
+%&y_{1,3} = y_{1,2} y_{3,1}y_{1,2} = y_{1,1} y_{3,1}y_{1,1},\\
+%&y_{1,4} = y_{1,2} y_{7,1}y_{1,2} = y_{1,1} y_{7,1}y_{1,1},\\
+%&y_{1,5} = y_{1,2} y_{2}y_{1,2} = y_{1,1} y_{2}y_{1,1},\\
+%&y_{1,6} = y_{1,2} y_{3,2}y_{1,2} = y_{1,1} y_{3,2}y_{1,1},\\
+%&y_{1,7} = y_{1,2} y_{4}y_{1,2} = y_{1,1} y_{4}y_{1,1},\\
+%&y_{1,8} = y_{1,2} y_{7,2}y_{1,2} = y_{1,1} y_{7,2}y_{1,1}.
+%\end{align*}
+%The new commutation relations are $y_{1,1}$ commutes with all the remaining $y_j$'s
+%and commutation relations from $\MS_c$ involving $y_1$ with $y_1$ replaced by $y_{1,2}$.
+%Then we repeat this process with $y_2$.
+%In summary, replacing $y_1,y_2,y_4,y_5,y_6,y_8,y_9$ introduces $8+9+10+11+12+13+14 = 77$ new variables 
+%and $12+14+16+18+20+22+24 = 126$ new conjugacy relations. 
+%In total $\Pg_{\LS}$ has $90$ variables excluding $\J$, $6$ linear relations and $170$ conjugacy relations.
+%
+%Then following the recipe given in the proofs of Proposition~$4.2$ and Lemma~$4.4$ in Ref.~\cite{slofstra2017}, 
+%we embed $\Pg_{\LS}$ into the solution 
+%group $\Gamma(\LS)$ with $2351$ variables and $1916$ linear relations. 
+%Alice's output alphabet is of size $64$ and of size $2$ for Bob.
+%
+%Such linear system game has at the biggest size when $a = 5$ or the special relation is $uxu^{-1} = x^5$.
+%The biggest game has $2465$ variables and $2006$ equations. We leave the derivation for curious readers.
 

### 2019-01-09 Draft/draft.tex
a more formal self-test proof

@@
 \newcommand{\tB}{\tilde{B}}
+\newcommand{\tW}{\tilde{W}}
+\newcommand{\tx}{\tilde{x}}
 \newcommand{\tpsi}{\tilde{\psi}}
@@
 \end{align}
-where $\omega_d = e^{i\pi/d}$ is the primitive $d$th root of unity and the addition is taken modulo $d$.
+where $\omega_d = e^{i\pi/d}$ is the primitive $d$th root of unity.
+Through out this paper, any operation on the label of the eigenvector $i$ is taken modulo $d$,
+for example, the addition above.
 
@@
 
-The main tool to understand linear system game is through its solution group over $\Z_d$.
-\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
-	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
-	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
-	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
-	\begin{align}
-		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
-	\end{align}
-	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
-	\begin{align}
-		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
-	\end{align}
-	Then the solution group has presentation 
-	\begin{align}
-	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
-	\end{align}
-\end{definition}
-Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
-Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
-\begin{definition}[Operator solution]
-	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
-	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
-	representation mapping $\J$ to $\overline{\omega_d}\1$.
-\end{definition}
-What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
-linear system game from its operator solution and vice versa.
+%The main tool to understand linear system game is through its solution group over $\Z_d$.
+%\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
+%	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
+%	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
+%	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
+%	\begin{align}
+%		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
+%	\end{align}
+%	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
+%	\begin{align}
+%		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
+%	\end{align}
+%	Then the solution group has presentation 
+%	\begin{align}
+%	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
+%	\end{align}
+%\end{definition}
+%Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
+%Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
+%\begin{definition}[Operator solution]
+%	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
+%	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
+%	representation mapping $\J$ to $\overline{\omega_d}\1$.
+%\end{definition}
+%What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
+%linear system game from its operator solution and vice versa.
 %========================================
@@
 \end{align}
+See Appendix~\ref{sec:construct} for details about how to construct $\LS$.
+
+The special property of $\Pg_{\LS}$ is summarized in the following lemma. 
+\begin{lemma}
+	\label{lm:ux_independ}
+	Suppose there exist unitaries $U$ and $X$ which have the following forms
+	\begin{align}
+		U = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && X = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
+	\end{align}
+	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
+	the ring of $(d-1)\times (d-1)$ matrices.
+\end{lemma}
+Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
+In the self-test proof, this lemma will be a critical step.
+\begin{proof}
+We are going to show the $(d-1)^2$ matrices of the set $\{U^k X^l\}_{k \in[d-1]-1, l \in [d-1]}$ are linearly independent.
+Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1]-1, l \in [d-1]}$
+such that 
+\begin{align}
+	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
+\end{align}
+We further assume that there exists integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
+The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
+Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
+where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
+Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.
+
+Starting with $\ket{x_{k_1}}$.
+Let's look at the entry $\bra{1}M\ket{1}$ where 
+\begin{align}
+	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/2^k}\braket{i}{1}.
+\end{align}
+For the term $\braket{1}{i/2^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $2^k \equiv 1 \pmod{d}$, or equivalently,
+$k = k_1$. Hence, we can conclude that 
+\begin{align}
+	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
+\end{align}
+Similarly we can determine that for all $j = 1,2\dots d-1$,
+\begin{align}
+	\bra{j}M\ket{j} 
+	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/2^k}\braket{i}{j} 
+	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
+\end{align}
+Hence we get $d-1$ equations with $d-1$ variables, and the linear system
+can be represented by 
+\begin{align}
+	W \ket{x_{k_1}} = 0,
+\end{align}
+where $W_{m,n} = \omega_d^{mn}$. Then we define
+\begin{align}
+	\tW = 
+	\begin{pmatrix}
+	1 & 1 \\
+	1 & W
+	\end{pmatrix}.
+\end{align}
+First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
+Now we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
+and prove that it satisfies the condition
+that 
+\begin{align}
+	\tW \ket{\tx_{k_1}} = 0,
+\end{align}
+which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
+We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which comes from the first row of $\tW$.
+It can be proved by summing the known $d-1$ equations as follows
+\begin{align}
+	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
+	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
+	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
+	= \sum_{l = 1}^{d-1}- x_{k_1,l}
+\end{align}
+where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
+Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.
+
+For $\ket{x_{k_a}}$, we look at entries $\{\bra{j}M\ket{aj}\}_{j=1}^{d-1}$ for $a = 2 \dots d-1$ and get equations
+of the form
+\begin{align}
+	0 = \bra{j}M\ket{aj} = \sum_{l=1}^{d-1} x_{k_a, l} \omega_d^{ajl} 
+\end{align}
+The corresponding coefficient matrix has value $\omega_d^{amn}$ at coordinate $m,n$,
+so it is also a submatrix of a Vandermonde matrix. Similar argument gives us that $\ket{x_{k_a}} = 0$.
+
+To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
+$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices.
+\end{proof}
 %\begin{align}
@@
 %The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
-See Appendix~\ref{sec:construct} for details.
+
 %------------------------------------------------------------------------
@@
 $\CHSH_U$, where the superscript $d$ means that the rules of this game depends on $d$.
-Intuitively, this is one step towards verifying Alice and Bob use $\paulix{d}$ and $\pauliz{d}$ in their operator solution.
+Intuitively, this is one step towards verifying Alice and Bob use some operator $X$ with eigenvalues
+$\{\omega_d^i\}_{i \in [d]}$ in their operator solution of $\LS$.
 
@@
 
-We summarize the projectors of the ideal strategy and the ideal correlation in the following two charts.
+For completeness, we show the ideal correlation in the following three charts and then give the projectors. 
 Note that we don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ because they are irrelevant
@@
 	&A_1^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
-	A_0^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_0^\perp = \Pi_V^\perp
+	A_0^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_0^\perp = \Pi_V^\perp.
 \end{align*}
@@
 
-The importance of this game is summarized in the following lemma.
+The robustness of this game is summarized in the following lemma.
 \begin{lemma}
@@
 	achieves the optimal correlation of $\CHSH$, then there exists unitaries $U_A$ and $U_B$ 
+	and a quantum state $\ket{junk}$
 	such that 
 	\begin{align*}
-		&U_A\x U_B \left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) = \ket{\EPR{2}} \\
+		&U_A\x U_B \left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) = \ket{\EPR{2}}\x \ket{junk} \\
 		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 + \tB_1}{2\cos(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
-		=\1 \x \pauliz{2} \ket{\EPR{2}} \\
+		=(\1 \x \pauliz{2} \ket{\EPR{2}}) \x \ket{junk} \\
 		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 - \tB_1}{-2\sin(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
-		=\1 \x \paulix{2} \ket{\EPR{2}} 
+		=(\1 \x \paulix{2} \ket{\EPR{2}}) \x \ket{junk} 
 	\end{align*}
@@
 \end{align}
-Since the relation $u^{-1}xu = x^2$ is embedded in this linear system game, we know
-\begin{align}
-	\sigma_A(u)^\dagger A_1A_2 \sigma_A(u) \ket{v}= (A_1A_2)^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
-\end{align}
-For simplicity, we define $X = A_1A_2$ and $U = \sigma_A(u)$.
-For simplicity, we define $X = A_1A_2$ and $U = \sigma_A(u)$.
-The condition becomes
-\begin{align}
+Since the relation $uxu^\dagger = x^2$ is embedded in this linear system game, we know
+\begin{align}
+	A_3A_4 A_1A_2 (A_3A_4)^\dagger \ket{v}= (A_1A_2)^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
+\end{align}
+How $u$ and $x$ are splitted into order-$2$ generators can be found in Appendix~\ref{sec:construct}.
+For simplicity, we define $X = A_1A_2$ and $U=A_3A_4$ such that
+the condition is equivalent to
+\begin{align}
+	\label{eq:ux_relation}
 	UXU^\dagger \ket{v} = X^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
 \end{align}
-On the subspace $\supp(\rho_A)$, we have the equality
-\begin{align}
-	\label{eq:sim}
-	UXU^\dagger X^{-2} = \1.
-\end{align}
 We will come back to the implication of this condition later.
 
-Suppose the support of $\tA_\ast^\diamond$ is spanned by $\ket{u_0}$ and $\ket{u_1}$ and 
-define $\ket{x_1} = 1/\sqrt{2}(\ket{u_0} + i\ket{u_1})$. 
-The test $\CHSH_X$ tells that $\ket{x_1}$ is the eigenvector of $X$ with eigenvalue $e^{i\pi/d} = \omega_d$.
+By \cref{lm:chsh_comp}, we can extract states $\ket{u_0}$ and $\ket{u_1}$ from the support of $\tA_\ast^\diamond$,   
+and define $\ket{x_1} = 1/\sqrt{2}(\ket{u_0} + i\ket{u_1})$. 
+\cref{prop:2d-subspace} implies that $\ket{x_1}$ is the eigenvector of $X$ with eigenvalue $e^{i\pi/d} = \omega_d$.
 Similarly, define $\ket{x_{d-1}} = 1/\sqrt{2}(\ket{u_0} - i\ket{u_1})$ such that $X \ket{x_{d-1}} = \omega_d^{d-1}\ket{x_{d-1}}$.
-We know 
-\begin{align}
-	\tA_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi} = \frac{1}{\sqrt{d}} (\ket{u_0}\ket{u_0} + \ket{u_1}\ket{u_1}).
-\end{align}
-If we restrict to Alice's system, we get 
-\begin{align}
-	\Tr_B(\tA_\ast^\diamond \ketbra{\tpsi}{\tpsi} \tA_\ast^\diamond) =\tA_\ast^\diamond \rho_A \tA_\ast^\diamond = 
- \frac{1}{d} \ketbra{u_0}{u_0} + \ketbra{u_1}{u_1} = \frac{1}{d} \tA_\ast^\diamond.
-\end{align}
-Hence $\rho_A$ acts as $\1$ on $\supp(\tA_\ast^\diamond)$.
-We also know that there exists local unitary $U_A$ such that 
-\begin{align}
-U_A \tA_\ast^\diamond U_A^\dagger = \ketbra{x_1}{x_1}+\ketbra{x_{d-1}}{x_{d-1}}
-\end{align}
-and 
-\begin{align}
-\Tr(\ketbra{x_1}{x_1} \rho_A)
-=\Tr(U_A \ketbra{u_0}{u_0} U_A^\dagger \rho_A) 
-= \frac{1}{d} \Tr(U_A\ketbra{u_0}{u_0} U_A^\dagger) 
-= \frac{1}{d},
-\end{align}
-and similarly $\Tr( \ketbra{x_{d-1}}{x_{d-1}}\rho_A) = 1/d$.
-
-Next, we calculate the eigen-decomposition of $X$ in $\supp(\rho_A)$.
-Based on \cref{eq:sim}, we know
+Hence, by \cref{eq:ux_relation} we can calculate the eigen-decomposition of $X$ in $\supp(\rho_A)$.
+as follows
 \begin{align}
@@
 From the set $\{(U^\dagger)^i \ket{x_1}\}_{i=0}^{d-2}$, we can identify $\ket{x_i}$ for $i = 1 \dots  d-1$
-such that $X \ket{x_i} = \omega_d^i \ket{x_i}$.
-From the single value test, we know 
-\begin{align}
-	\tA_\triangle^\diamond \ket{\tpsi} = \tA_\triangle^\diamond \x \tB_\triangle^\diamond \ket{\tpsi} = \frac{1}{\sqrt{d}}
+such that $X \ket{x_i} = \omega_d^i \ket{x_i}$ and 
+\begin{align}
+S = \{ \ket{x_1}, \ket{x_2} \dots  \ket{x_{d-1}} \} \subset \supp(\rho_A).
+\end{align}
+On the other hand, we also know that $U \ket{x_i} = \ket{x_{i/2}}$ for $i = 1,2 \dots d-1$.
+Note that $U$ and $X$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
+restricted to $\spn(S)$.
+
+\hl{Assume $\supp(\rho_A) = \supp(\rho_B)$ and $\ket{\psi} = \vc(\sqrt{\rho})$.} 
+The consistency condition is equivalent to
+\begin{align}
+	A_i \sqrt{\rho} B_i^\dagger = \sqrt{\rho}.
+\end{align}
+\hl{We further assume that $A_i = B_i$,} and define $\rho_S = \Pi_S \sqrt{rho} \Pi_S$
+where $\Pi_S = \sum_{i=1}^{d-1} \ketbra{x_i}{x_i}$. 
+Then we can conclude that 
+\begin{align}
+	U \rho_S U^{\dagger} = \rho_S && X \rho_S X^\dagger = \rho_S.
+\end{align}
+For any $k \in [d-1]$ and $l \in \{1,2\dots d-1\}$, the equation above tells us that 
+\begin{align}
+	U^kX^l \rho_S (U^kX^l)^\dagger = \rho_S.
+\end{align}
+By \cref{lm:ux_independ}, $\rho_S$ commutes with all the $(d-1) \times (d-1)$ matrices, which means that 
+\begin{align}
+	\rho_S \propto \Pi_S
+\end{align}
+
+In the end, we turn our attention back to the single value test. 
+The implication of the single value test is that
+\begin{align}
+	A_\triangle^\diamond \ket{\psi} = A_\triangle^\diamond \x B_\triangle^\diamond \ket{\psi} = \frac{1}{\sqrt{d}}
 	\ket{x_0}\ket{x_0}
 \end{align}
-where $X \ket{x_0} = \ket{x_0}$. 
-The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
-\begin{align}
-	X \ket{x_i} = \omega_d^i \ket{x_i}.
-\end{align}
-The other effect of $\SVT_X$ is that we know 
-\begin{align}
-	\tA_\triangle^\diamond \rho_A \tA_\triangle^\diamond = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^\diamond.
-\end{align}
-\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
+where $X \ket{x_0} = \ket{x_0}$ and $\ket{x_0} \in \supp(\rho_A)$. 
+Define $S^\perp = \{ \ket{x_0}\}$, then we know $\Pi_S^\perp \rho_A \Pi_S^\perp \propto \Pi_S$.
+Hence we know $\rho_A$ acts as $\1$ on $S \cup S^\perp$, which yields that there exists i
+sometries $V_A$ and $V_B$ such that
+\begin{align}
+	V_A \x V_B \ket{\psi} = \ket{\EPR{d}}.
+\end{align}
+
+%The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
+%\begin{align}
+%	X \ket{x_i} = \omega_d^i \ket{x_i}.
+%\end{align}
+%The other effect of $\SVT_X$ is that we know 
+%\begin{align}
+%	\tA_\triangle^\diamond \rho_A \tA_\triangle^\diamond = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^\diamond.
+%\end{align}
+%\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
 

### 2019-01-10 Draft/draft.tex
Honghao: the main proof should be more rigorous now.

@@
 \newcommand{\tri}{\Delta}
+\newcommand{\lB}{\overline{B}}
 
@@
 \end{align}
-where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$, so for  any $\ket{v} \in \supp(\rho_A)$,
+where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$. 
+Similarly we define $\rho_B = \Tr_A(\ketbra{\psi}{\psi})$.
+For any $\ket{v} \in \supp(\rho_A)$,
 we have 
@@
 How $u$ and $x$ are splitted into order-$2$ generators can be found in Appendix~\ref{sec:construct}.
-For simplicity, we define $X = A_1A_2$ and $U=A_3A_4$ such that
+For simplicity, we define $X_A = A_1A_2$ and $U_A=A_3A_4$ such that
 the condition is equivalent to
@@
 	\label{eq:ux_relation}
-	UXU^\dagger \ket{v} = X^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
+	U_AX_AU_A^\dagger \ket{v} = X_A^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
 \end{align}
@@
 
-By \cref{lm:chsh_comp}, we can extract states $\ket{u_0}$ and $\ket{u_1}$ from the support of $\tA_\ast^\diamond$,   
+By \cref{lm:chsh_comp}, we can extract states $\ket{u_0}$ and $\ket{u_1}$ from the support of $A_\ast^\diamond$,   
 and define $\ket{x_1} = 1/\sqrt{2}(\ket{u_0} + i\ket{u_1})$. 
-\cref{prop:2d-subspace} implies that $\ket{x_1}$ is the eigenvector of $X$ with eigenvalue $e^{i\pi/d} = \omega_d$.
-Similarly, define $\ket{x_{d-1}} = 1/\sqrt{2}(\ket{u_0} - i\ket{u_1})$ such that $X \ket{x_{d-1}} = \omega_d^{d-1}\ket{x_{d-1}}$.
-Hence, by \cref{eq:ux_relation} we can calculate the eigen-decomposition of $X$ in $\supp(\rho_A)$.
+\cref{prop:2d-subspace} implies that $\ket{x_{A,1}}$ is the eigenvector of $X_A$ with eigenvalue $\omega_d$.
+Similarly, define $\ket{x_{A,d-1}} = 1/\sqrt{2}(\ket{u_0} - i\ket{u_1})$ such that $X_A \ket{x_{A,d-1}} = \omega_d^{d-1}\ket{x_{A,d-1}}$.
+Hence, by \cref{eq:ux_relation} we can calculate the eigen-decomposition of $X_A$ in $\supp(\rho_A)$.
 as follows
@@
 \label{eq:ladder}
- XU^\dagger \ket{x_1} = U^\dagger X^2 \ket{x_1} = \omega_d^2 U^\dagger \ket{x_1},
-\end{align}
-so $U^\dagger \ket{x_1}$ is an eigenvector of $X$ with eigenvalue $\omega_d^2$.
-By induction, we know $X (U^\dagger)^i \ket{x_1} = \omega_d^{2^i} (U^\dagger)^i\ket{x_1}$. 
-From the set $\{(U^\dagger)^i \ket{x_1}\}_{i=0}^{d-2}$, we can identify $\ket{x_i}$ for $i = 1 \dots  d-1$
-such that $X \ket{x_i} = \omega_d^i \ket{x_i}$ and 
-\begin{align}
-S = \{ \ket{x_1}, \ket{x_2} \dots  \ket{x_{d-1}} \} \subset \supp(\rho_A).
-\end{align}
-On the other hand, we also know that $U \ket{x_i} = \ket{x_{i/2}}$ for $i = 1,2 \dots d-1$.
-Note that $U$ and $X$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
-restricted to $\spn(S)$.
-
-\hl{Assume $\supp(\rho_A) = \supp(\rho_B)$ and $\ket{\psi} = \vc(\sqrt{\rho})$.} 
+ X_AU_A^\dagger \ket{x_{A,1}} = U_A^\dagger X_A^2 \ket{x_{A,1}} = \omega_d^2 U_A^\dagger \ket{x_{A,1}},
+\end{align}
+so $U_A^\dagger \ket{x_{A,1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^2$.
+By induction, we know $X_A (U_A^\dagger)^i \ket{x_{A,1}} = \omega_d^{2^i} (U_A^\dagger)^i\ket{x_{A,1}}$. 
+From the set $\{(U_A^\dagger)^i \ket{x_{A,1}}\}_{i=0}^{d-2}$, we can identify $\ket{x_{A,i}}$ for $i = 1 \dots  d-1$
+such that $X_A \ket{x_{A,i}} = \omega_d^i \ket{x_{A,i}}$ and 
+\begin{align}
+S_A = \spn \{ \ket{x_{A,1}}, \ket{x_{A,2}} \dots  \ket{x_{A,d-1}} \} \subset \supp(\rho_A).
+\end{align}
+On the other hand, we also know that $U_A \ket{x_{A,i}} = \ket{x_{A,i/2}}$ for $i = 1,2 \dots d-1$.
+Note that $U_A$ and $X_A$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
+restricted to $\spn(S_A)$.
+
+Similar argument applies to Bob's operators. We can identify $X_B = B_1B_2$, 
+$U_B=B_3B_4$ and a vector space $S_B =\spn\{ \ket{x_{B,1}}, \ket{x_{B,2}} \dots  \ket{x_{B,d-1}} \} \subset \supp(\rho_B)$,
+such that 
+\begin{align}
+	X_B = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_{B,i}}{x_{B,i}} && U_B = \sum_{i=1}^{d-1} \ketbra{x_{B,i/2}}{x_{B,i}},
+\end{align}
+when their actions are restricted to $S_B$. Moreover, we can define a unitary $V: \supp{\rho_B} \to \supp(\rho_A)$,
+which maps $\ket{x_{B,i}}$ to $\ket{x_{A,i}}$.
+
+%and projectors $\Pi_{S_A}$ and $\Pi_{S_B}$ to be the projectors onto $S_A$ and $S_B$ respectively.
+%From now on, we focus on the state $\ket{\psi_S}$ which is defined as
+%\begin{align}
+%	\ket{\psi_S} = (\Pi_{S_A} \x (V\Pi_{S_B}))\ket{\psi} = \vc(\tau) 
+%\end{align}
+%for some $\tau \in L(S_A)$.
+Assume that $\ket{\psi} = \vc(\tau)$ for some $\tau \in L(\supp(\rho_B) \to \supp(\rho_A))$
 The consistency condition is equivalent to
 \begin{align}
-	A_i \sqrt{\rho} B_i^\dagger = \sqrt{\rho}.
-\end{align}
-\hl{We further assume that $A_i = B_i$,} and define $\rho_S = \Pi_S \sqrt{rho} \Pi_S$
-where $\Pi_S = \sum_{i=1}^{d-1} \ketbra{x_i}{x_i}$. 
-Then we can conclude that 
-\begin{align}
-	U \rho_S U^{\dagger} = \rho_S && X \rho_S X^\dagger = \rho_S.
-\end{align}
-For any $k \in [d-1]$ and $l \in \{1,2\dots d-1\}$, the equation above tells us that 
-\begin{align}
-	U^kX^l \rho_S (U^kX^l)^\dagger = \rho_S.
-\end{align}
-By \cref{lm:ux_independ}, $\rho_S$ commutes with all the $(d-1) \times (d-1)$ matrices, which means that 
-\begin{align}
-	\rho_S \propto \Pi_S
+\label{eq:con_tau}
+	A_i \tau B_i^\dagger = \tau.
+\end{align}
+Substituting $i=1,2$ into \cref{eq:con_tau}, we get 
+\begin{align}
+	X_A \tau X_B^\dagger = A_1A_2\tau B_2^\dagger B_1^\dagger = A_1\tau B_1^\dagger = \tau.
+\end{align}
+Inserting $V^\dagger V$ between $\tau$ and $X_B$ and multiplying $V^\dagger$ to the right on both sides yield that 
+\begin{align}
+	X_A \tau V^\dagger X_A^\dagger = X_A \tau V^\dagger VX_B^\dagger V^\dagger = \tau V^\dagger,
+\end{align}
+where we use the relation $VX_B^\dagger V^\dagger = X_A$.
+Similar argument gives us that 
+\begin{align}
+	U_A \tau V^\dagger  U_A^\dagger = \tau V^\dagger.
+\end{align}
+Then we can conclude that for any $k \in \{0,1 \dots d-2\}$ and $l \in \{1,2\dots d-1\}$
+\begin{align}
+	U_A^kX_A^l \tau V^\dagger (U_A^kX_A^l)^\dagger = \tau V^\dagger.
+\end{align}
+By \cref{lm:ux_independ}, $\tau V^\dagger$ projected onto $L(S_A)$ commutes with all the $(d-1) \times (d-1)$ matrices, which means that 
+\begin{align}
+	\label{eq:d-1}
+	\tau V^\dagger|_{S_A}  \propto \1_{S_A}.
 \end{align}
@@
 	A_\triangle^\diamond \ket{\psi} = A_\triangle^\diamond \x B_\triangle^\diamond \ket{\psi} = \frac{1}{\sqrt{d}}
-	\ket{x_0}\ket{x_0}
-\end{align}
-where $X \ket{x_0} = \ket{x_0}$ and $\ket{x_0} \in \supp(\rho_A)$. 
-Define $S^\perp = \{ \ket{x_0}\}$, then we know $\Pi_S^\perp \rho_A \Pi_S^\perp \propto \Pi_S$.
-Hence we know $\rho_A$ acts as $\1$ on $S \cup S^\perp$, which yields that there exists i
-sometries $V_A$ and $V_B$ such that
+	\ket{x_{A,0}}\ket{x_{B,0}}
+\end{align}
+where $X_C \ket{x_{C,0}} = \ket{x_{C,0}}$ and $\ket{x_{C,0}} \in \supp(\rho_C)$ for $C = A$ or $B$. 
+Recalling \cref{eq:d-1}, we can conclude that there exists local isometries 
+$V_A$ and $V_B$ such that
 \begin{align}

### 2019-01-23 Draft/draft.tex
Honghao: more completed draft

@@
 \newcommand{\ct}{^{\dagger}}
-\newcommand{\tp}{^{\mathsf{T}}}
+\newcommand{\tp}{^\intercal}
 
@@
 \newcommand{\calH}{\mathcal{H}}
+\newcommand{\calX}{\mathcal{X}}
+\newcommand{\calY}{\mathcal{Y}}
+\newcommand{\calA}{\mathcal{A}}
+\newcommand{\calB}{\mathcal{B}}
 
@@
 \newcommand{\EPR}[1]{EPR^{(#1)}}
-\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
-\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
+\newcommand{\paulix}{\sigma_x}
+\newcommand{\pauliz}{\sigma_z}
 \newcommand{\G}[1]{G^{(#1)}}
@@
 \maketitle
+
+%========================================
+\section{Introduction}
+\label{sec:intro}
+%========================================
+Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
+delegated computation \cite{ruv2013,cgsv2017} and device independent quantum cryptography
+\cite{qkd2011,qkd2014,miller2016,fu2018,eat2018}.
+
+The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
+one copy of it by the CHSH inequality \cite{bamps2015}. Many copies of the $2$-dimensional EPR
+pair can be self-tested in parallel \cite{mckague2016, coladan2017parallel}. 
+Self-testing general $d$-dimensional EPR pairs is a harder task.
+Recently, a remarkable result by Coladangelo \textit{et al}.\cite{cgs2017} 
+has shown that the maximally entangled state with arbitrary local dimension 
+can be self-tested with constant question alphabet but answer alphabet growing with
+the local dimension. 
+Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
+of the generalized Magic Square game and Magic Pentagram game, one can self-test
+$N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
+Both the Magic Square game and the Magic Pentagram game have constant question alphabet
+but growing answer alphabet.
+
+So far, general $d$-dimensional maximally entangled states are self-tested by
+modifying the correlation and enlarging the size of the correlation.
+A natural question to ask is whether maximally entangled state with large local dimension
+can be self-tested with fixed-sized correlation. 
+An equivalent question to ask is whether it is possible to self-test maximally
+entangled state more efficiently, with constant question and answer set. 
+In this report, we give an affirmative answer to this question by proving the following theorem.
+\begin{theorem}
+\label{thm:inf}
+	There exists a set $D$ of odd prime numbers such that for any $d \in D$, 
+	the maximally entangled state of local dimension $d$ can be self-tested 
+	with constant question and answer sets.
+\end{theorem}
+
+The set $D$ is easily characterizable as it contains all the odd prime numbers with 
+primitive root $2$, $3$ or $5$. To prove \cref{thm:inf}, we give explicit self-testing proof of 
+the maximally entangled state with local dimension $d$ whose primitive root is $2$ by explicitly giving the 
+correlation that achieves this goal. Then the self-testing property of this correlation is 
+given in the following theorem.
+\begin{theorem}
+\label{thm:pr_2}
+	All maximally entangled state with local dimension $d$, where $d$ is prime and has
+	primitive root $2$, can be self-tested by a constant-sized correlation.
+\end{theorem}
+Note that although the sizes of the question and answer
+sets do not depend on $d$, the optimal correlation does.
+This correlation can be easily converted to work for dimensions with primitive $3$ or $5$.
+
+\textbf{Structure of the paper}.
+We start with notations and background information in \cref{sec:prelim}.
+Since the game we designed consists of several sub-tests, we introduce the individual
+sub-tests and their implications in \cref{sec:comp}. Our main result is based the combination
+of the sub-tests and presented in \cref{sec:main}. In \cref{sec:extend}, we show how to adapt
+our nonlocal game to self-test maximally entangled state of different dimensions.
+
 %========================================
 \section{Preliminaries and notations}
+\label{sec:prelim}
 %========================================
-We use $[n]$ to denote the set $\{0,1 \dots n-1\}$.
-We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.
-
-\textbf{The EPR pair.} Our goal is to self-test maximally entangled state of local dimension $d$, denoted by 
+We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
+%We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.
+
+\textbf{The EPR pair.} Our goal is to self-test maximally entangled state of local dimension $d$, 
 \begin{align}
@@
 \end{align}
-The superscript $(d)$ is to stress the local dimension and we follow this convention through this paper.
-
-\textbf{The Pauli operators.} 
-We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators behave like 
-the $d$-dimensional Pauli operators which are defined by
-\begin{align}
-	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1}{i} \quad \pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i}
-\end{align}
-where $\omega_d = e^{i\pi/d}$ is the primitive $d$th root of unity.
-Through out this paper, any operation on the label of the eigenvector $i$ is taken modulo $d$,
-for example, the addition above.
+The superscript $(d)$ stresses the local dimension and we follow this convention through this paper.
+
+We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators 
+which have operators of the similar form
+\begin{align}
+	X = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i} && U = \sum_{i=0}^{d-1} \ketbra{i/2}{i},
+\end{align}
+where $\omega_d = e^{i2\pi/d}$ is the primitive $d$th root of unity.
+Through out this paper, any operation on the label of the eigenvector $i$ is taken modulo $d$.
+for example, the $i/2$ above.
 
@@
 The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
-The weighted CHSH operator is defined as 
+The weighted CHSH inequality is given below 
 \begin{align}
 	\label{eq:chsh_op}
-	\I_\alpha = \alpha(A_0B_0+A_0B_1) + A_1B_0 - A_1B_1,
-\end{align}
-where $A_x,B_y$ for $x,y = 0,1$ are Binary observables on Hilbert space $\calH_A$ and $\calH_B$ respcetively.
-If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, we have 
-\begin{align}
-	\bra{\phi} \I_\alpha \ket{\phi} \leq 2\alpha.
-\end{align}
+	\I_\alpha = \alpha\ip{A_0B_0}+\alpha\ip{A_0B_1} + \ip{A_1B_0} - \ip{A_1B_1}\leq 2\alpha,
+\end{align}
+where $A_x,B_y$ for $x,y = 0,1$ are Binary observables on Hilbert space $\calH_A$ and $\calH_B$ respectively.
+If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
+the weighted CHSH inequality.
 However, If they share entangled state $\ket{\psi}$, the maximal violation is 
@@
 \label{eq:chsh_max}
-\bra{\psi} \I_\alpha \ket{\psi} \leq 2\sqrt{1+\alpha^2}.
+ \I_\alpha \leq 2\sqrt{1+\alpha^2}.
 \end{align}
 \begin{definition}[Ideal strategy for $\I_\alpha$]
+	\label{def:ideal}
 	Define $\mu = \arctan(1/\alpha)$.
-	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation of \cref{eq:chsh_max})
-	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz{2}$, $A_1 = \paulix{2}$,
-	$B_0 = \cos(\mu) \pauliz{2} + \sin(\mu) \paulix{2}$ and $B_1 = \cos(\mu) \pauliz{2} - \sin(\mu) \paulix{2}$.
+	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
+	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz$, $A_1 = \paulix$,
+	$B_0 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_1 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
 \end{definition}
@@
 \label{thm:selftest}
-	Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ satisfies that
-	\begin{align}
-		\bra{\psi} \I_\alpha \ket{\psi} \geq 2\sqrt{1+\alpha^2} - \epsilon
-	\end{align}
+	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the violation
+	at least $2\sqrt{1+\alpha^2} - \epsilon$
 	for some $\alpha$, then
@@
 	\end{align}
-	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and where $A_x, B_y$ are from the 
-	ideal strategy.
+	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and $A_x, B_y$ are 
+	defined in \cref{def:ideal}.
 \end{theorem}
 We defer the proof of \cref{thm:selftest} till Appendix~\ref{sec:selftest}.
-After proving the robust the self-testing result, we take one step further and observed some interesting behaviour of the 
+After proving the robust the self-testing result, we take one step further and observe some interesting behaviour of the 
 observable $\tilde{B}_0\tilde{B}_1$.
@@
 \label{prop:2d-subspace}
-	Suppose a quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
-	value of  $\bra{\psi}\I_{-\cot(\pi/2d)} \ket{\psi}$, then there exists a $2$-dimensional Hilbert space which is spanned by eigenvectors of 
+	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
+	violation of  $\I_{\cot(-\pi/2d)}$, then there exists a $2$-dimensional Hilbert space which is spanned by eigenvectors of 
 	$\tilde{B}_0\tilde{B}_1$ of eigenvalue $\omega_d$ and $\omega_d^{-1}$.
@@
 \begin{proof}[Proof of \cref{prop:2d-subspace}]
-	By \cref{thm:selftest}, the condition that the strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
-	maximal value of $\bra{\psi}  \I_\alpha \ket{\psi} $ implies that there exists state $\ket{u_0}, \ket{u_1}$ such that 
-	\begin{align*}
-	&(\tilde{B}_0 + \tilde{B}_1) \ket{u_0} = 2\cos(\pi/2d) \ket{u_0} \\
-	&(\tilde{B}_0 + \tilde{B}_1) \ket{u_1} = -2\cos(\pi/2d) \ket{u_1}\\
-	&(\tilde{B}_0 - \tilde{B}_1) \ket{u_0} = -2\sin(\pi/2d) \ket{u_1} \\
-	&(\tilde{B}_0 - \tilde{B}_1) \ket{u_1} = -2\sin(\pi/2d) \ket{u_0}.
+	By \cref{thm:selftest}, the condition that the strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
+	maximal value of $\I_{\cot(-\pi/2d)} $ implies that there exist states $\ket{u_0}, \ket{u_1} \in \supp(\Tr_B(\ketbra{\tpsi}{\tpsi}))$ such that 
+	\begin{align*}
+	(\tilde{B}_0 + \tilde{B}_1) \ket{u_0} = 2\cos(-\pi/2d) \ket{u_0} 
+	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_1} = -2\cos(-\pi/2d) \ket{u_1}\\
+	(\tilde{B}_0 - \tilde{B}_1) \ket{u_0} = 2\sin(-\pi/2d) \ket{u_1} 
+	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_1} = 2\sin(-\pi/2d) \ket{u_0}.
 	\end{align*}
 	It is straightforward to calculate that 
-	\begin{align}
-		\tilde{B}_0\tilde{B}_1 \ket{u_0} &= \cos(\pi/d) \ket{u_0} -\sin(\pi/d) \ket{u_1}\\
-		\tilde{B}_0\tilde{B}_1\ket{u_1} &= \sin(\pi/d)\ket{u_0} + \cos(\pi/d) \ket{u_1}.
-	\end{align}
-	We can conclude that 
-	\begin{align}
-		&\tilde{B}_0\tilde{B}_1(\ket{u_0} + i\ket{u_1}) = e^{i \frac{\pi}{d}} (\ket{u_0} + i\ket{u_1})\\
+	\begin{align*}
+		\tilde{B}_0\tilde{B}_1 \ket{u_0} = \cos(\pi/d) \ket{u_0} -\sin(\pi/d) \ket{u_1},&&
+		\tilde{B}_0\tilde{B}_1\ket{u_1} = \sin(\pi/d)\ket{u_0} + \cos(\pi/d) \ket{u_1},
+	\end{align*}
+	so we can conclude that 
+	\begin{align*}
+		&\tilde{B}_0\tilde{B}_1(\ket{u_0} + i\ket{u_1}) = e^{i \frac{\pi}{d}} (\ket{u_0} + i\ket{u_1}), &&
 		&\tilde{B}_0\tilde{B}_1(\ket{u_0} - i\ket{u_1}) = e^{-i \frac{\pi}{d}} (\ket{u_0} - i\ket{u_1}).
-	\end{align}
+	\end{align*}
+	The actual eigenbasis we use is 
+	\begin{align}
+		\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{u_0} + i\ket{u_1}), &&
+		\ket{x_{d-1}} = \frac{-e^{i\pi/2d}}{\sqrt{2}}(\ket{u_0} - i\ket{u_1})
+	\end{align}
+	so that 
+	\begin{align}
+		&B_0 = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
+		&B_1 =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1},
+	\end{align}
+	which is important for the whole embedding argument to work in \cref{sec:comp}.
 \end{proof}
@@
 \textbf{Nonlocal game}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
-to give answer for a chosen question. We denote Alice's question set by $X$ and answer set by $A$. Similarly,
-Bob's question set is denoted by $Y$ and his answer set is denoted by $B$. The nonlocal game also
-comes with two functions: $\pi: X \times Y \rightarrow [0,1]$, which is the probability distribution over the questions,
-and $V: A \times B \times X \times Y \rightarrow \R$, which is the scoring function. Such games are nonlocal
+to give ananswer for a chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
+Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
+comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
+and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
 because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
@@
 \begin{align}
-	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for } (a,b,x,y) \in A \times B \times X \times Y,
+	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
 \end{align}
@@
 
-The main contribution of our work is the construction of a nonlocal game $\G{d}$ that can be used to self-test $\ket{\EPR{d}}$where $d$ is an arbitrary odd prime number. 
-In fact, our nonlocal game self-tests $\paulix{d}$ and $\pauliz{d}$ too, just implicitly.
-The nonlocal game is a linear system game with modifications. 
+The main contribution of our work is the construction of a nonlocal game $\G{d}$ with constant-sized $X$,$Y$,$A$ and $B$
+that can be used to self-test $\ket{\EPR{d}}$ for arbitrary odd prime $d$. 
+The nonlocal game is a linear system game with modifications or further enforcements. 
 We introduce the definition of self-testing first and then the definition of linear system game, 
@@
 \begin{definition}[Linear system game]
- Let $Ax = b$ be an $m \times n$ linear system over $\Z_d$. The associated linear system game has two
- players Alice and Bob, where Alice is given a equation number $1 \leq x \leq m$ and replies with $a \in \Z_d^{\times n}$
- ,and Bob is given a variable $y$ and replies with an assignment $y \in \Z_d$. The winning condition is 
+ Let $Hx = b$ be an $m \times n$ linear system over $\Z_2$. The associated linear system game involves two
+ players Alice and Bob, where Alice is given an equation number $1 \leq x \leq m$ and replies with $a \in \Z_2^{\times n}$,
+ and Bob is given a variable number $y$ and replies with an assignment $b \in \Z_2$. The winning condition is 
  \begin{align*}
  	a(y) &= b && \text{(Consistency)} \\
-	\sum_{y = 1}^n A_{xy} a(y) &\equiv b(x) \pmod d. &&\text{(Constraint satisfaction)}
+	\sum_{y = 1}^n H_{xy} a(y) &\equiv b(x) \pmod 2. &&\text{(Constraint satisfaction)}
  \end{align*}
@@
 \section{Components of $\G{d}$}
+\label{sec:comp}
 %========================================
-Suppose we would like to self-test $\ket{\EPR{d}}$ with $\G{d}$, where $d$ is prime and has primitive root $2$.
-Later we will see how to deal with general prime numbers and why there are infinitely many prime dimensional EPR pairs 
-that can be self-tested by a variant of $\G{d}$.
+The goal of this section and the next section is to 
+present a nonlocal game that can self-test $\ket{\EPR{d}}$, 
+where $d$ is prime and has primitive root $2$\footnote{By $d$ has primitive root $2$,
+we mean that $2$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$.
+When $d$ is prime, $\Z_d^\times = \{1,2\dots d-1\}$.}
+The game we constructed is denoted by $\G{d}$, which is the combination of several tasks.
+In this section, we introduce such tests and their implications.
+In \cref{sec:main}, we show how the implications can be combined to give a full self-test of $\ket{\EPR{d}}$. 
 %----------------------------------------------------------------
@@
 %----------------------------------------------------------------
-The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the 
+Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$, which
+is included in the group $K$.
+The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is the embedding of the 
 following group
 \begin{align}
-	\Pg_{\LS} = \langle u, x : uxu^{-1} = x^2 \rangle.
-\end{align}
-See Appendix~\ref{sec:construct} for details about how to construct $\LS$.
-
-The special property of $\Pg_{\LS}$ is summarized in the following lemma. 
+	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
+\end{align}
+
+\begin{proposition}
+	\label{prop:embed}
+	The group $\Pg$ can be embedded into a linear system game, $\LS$, over $\Z_2$,
+	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
+\end{proposition}
+The process of embedding $\Pg$
+into the solution group of $\LS$ follows the recipe given in the proofs of
+Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
+The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}..
+\begin{proof}
+The first step is to embed $\Pg$ into a linear-plus-conjugacy group $\Pg''$ where
+all the generators are of order $2$, following the instructions given in the proof of  
+Proposition~$4.8$ of the Ref.~\cite{slofstra2017}.
+We first introduce $x_1,x_2$ such that $x_1^2=x_2^2=e$, $x=x_1x_2$ and $u x_2 u^{-1}=x_2$.
+We also introduce $x' = ux_1u^{-1}$, 
+then we embed $\Pg$ in $\Pg'$ as
+\begin{align}
+	\Pg' = \langle x_1,x_2,x',u: x_1^2=x_2^2=x'^2=e,
+	x_1x_2x_1=x', ux_1u^{-1}=x', ux_2u^{-1} =x_2 \rangle.
+\end{align}
+Next, we introduce $u_1,u_2$ such that $u_1^2=u_2^2=e$ and $u=u_1u_2$, 
+and also $u_3.u_4$ of order $2$ such that the conjugacy relations involving them are 
+\begin{align*}
+u_2x_2u_2 = u_3, && u_1u_3u_1 = x_2\\
+u_2x_1u_2 = u_4, && u_1u_4u_1 = x',
+\end{align*}
+then
+$\Pg'$ is further embedded in $\Pg''$ as
+\begin{equation}
+\begin{aligned}
+	\Pg'' =  \langle &x_1,x_2,x',u_1,u_2,u_3,u_4: \text{all elements are of order $2$},\notag\\
+	 &u_2x_2u_2 = u_3, u_1u_3u_1 = x_2,
+u_2x_1u_2 = u_4, u_1u_4u_1 = x',x_1x_2x_1=x' \rangle.
+\end{aligned}
+\end{equation}	
+To represent the conjugacy relations by a tuple, we relabel the some of the generators as
+\begin{align*}
+	u_1 = x_3, && u_2 = x_4, && x' = x_5, && u_3 = x_6, && u_4 = x_7,
+\end{align*}
+so that a simpler form of the group $\Pg''$ is 
+\begin{equation}
+\begin{aligned}
+	\Pg'' = \langle \{x_i\}_{i=1}^7 : x_i^2 = e \; \forall i, 
+	x_1x_2x_1=x_5, x_4x_2x_4 = x_6,
+	 x_4x_1x_4=x_7, x_3x_2x_3 = x_6, x_3x_5x_3=x_7\rangle
+\end{aligned}
+\end{equation}
+We collect the subscript of $x_i$'s in the conjugacy relations and define
+\begin{align}
+	C= \{ &(1,2,5), (3,5,7), (4,1,7), (4,2,6), (3,2,6)\},
+\end{align}
+so that $(i,j,k) \in C$ if and only if $x_ix_jx_i = x_k$ in $\Pg''$.
+
+Next we embed $\Pg''$ into $\Pg_{NLC}$ to make $x_j$ and $x_k$ commute if $(i,j,k) \in C$,
+where $\Pg_{NLS}$ is a nice linear-plus-conjugacy group.
+This steps are given in the proof of Lemma~$4.4$ of the Ref.~\cite{slofstra2017}.
+The group $\Pg_{NLS}$ is defined as 
+\begin{equation}
+\begin{split}
+\Pg_{NLS} = \langle \{x_i, w_i, y_i, j_i\}_{i=1}^{7},f : &f^2 = x_i^2 =w_i^2=y_i^2=j_i^2= e, \\
+	&x_i = y_iz_i = fw_i,\; fy_if =z_i \quad\text{where } 1 \leq i \leq 7 \\
+	&y_j z_k = z_ky_j,\; w_iy_jw_i = z_k \quad\text{for all } (i,j,k)\in C \rangle.
+\end{split}
+\end{equation}
+To summarize the linear relations, we first introduce generator $g_{jk} = y_j z_k$ for all $(i,j,k) \in C$
+such that $g_{jk}^2 = e$. Now the group has $34$ generator.
+The $19$ linear relations are
+\begin{align*}
+	&x_i y_i z_i = e \quad \text{for} \quad i =1\dots 7 \\
+	&x_i f w_i = e  \quad \text{for} \quad i =1\dots 7\\
+	&g_{jk}y_jz_k =e \quad \text{for all}\quad (i,j,k) \in C.
+\end{align*}
+The $12$ conjugacy relations are 
+\begin{align*}
+	&fy_if = z_i\quad \text{for} \quad i =1\dots 7\\
+	&w_iy_j w_i = z_k \quad\text{for all } (i,j,k)\in C.
+\end{align*}
+We can standardise the generators by relabeling the generators all as $x_i$.
+There are $29$ generators in $\Pg_{NLS}$.
+
+The last step is given in the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}, which
+embeds all the conjugacy relations in linear relations.
+This is done by introduce $7$ new variables and $6$ linear relations for each
+conjugacy relations. For example, If $I = (i,j,k)$ is a conjugacy relation, then we introduce
+generators $y_{Ii}$ for $i=1 \dots 6$. Note that $y_{Ii}$ shall not be confused with the $y_i$'s
+in the previous step. The new linear relations are
+\begin{align*}
+	x_i y_{I1} y_{I2} = e && x_j y_{I2} y_{I3} = e && y_{I3}y_{I4}y_{I5} = e\\
+	x_i y_{I5} y_{I6} = e && x_k y_{I6} y_{I7} = e && y_{I1}y_{I4}y_{I7} = e.
+\end{align*}
+In the end, the solution group of $\LS$, $\Pg_{\LS}$,  
+has $118$ variables and $91$ equations.
+\end{proof}
+In the later parts of the paper, we use $n = 118$ and $m = 91$ to refer to the size of $\LS$.
+The key feature of this embedding is that $\LS$ has constant-sized input-output alphabet
+even if the generators $u$ and $x$ can have arbitrary order.
+
+We denote the special operators in the operator solution of $\LS$ that correpsond to generators 
+$u = x_3x_4$ and $x = x_1x_2$ by $U$ and $S$.
+The special property of $U$ and $S$ is summarized in the following lemma. 
 \begin{lemma}
@@
 	\begin{align}
-		U = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && X = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
+		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
 	\end{align}
 	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
-	the ring of $(d-1)\times (d-1)$ matrices.
+	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
 \end{lemma}
@@
 \begin{proof}
-We are going to show the $(d-1)^2$ matrices of the set $\{U^k X^l\}_{k \in[d-1]-1, l \in [d-1]}$ are linearly independent.
-Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1]-1, l \in [d-1]}$
+We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
+Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
 such that 
@@
 \end{align}
-We further assume that there exists integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
+We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
 The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
@@
 
-Starting with $\ket{x_{k_1}}$.
-Let's look at the entry $\bra{1}M\ket{1}$ where 
+We start with proving that $\ket{x_{k_1}} = 0$.
+Proving $\ket{x_{k_i}} = 0$ for other $i$ follows a similar argument, so we briefly
+discuss about it in the end.
+The entry $\bra{1}M\ket{1}$ can be expressed as  
 \begin{align}
@@
 \end{align}
-Hence we get $d-1$ equations with $d-1$ variables, and the linear system
-can be represented by 
+Hence we get $d-1$ equations with $d-1$ variables, and the linear system is
 \begin{align}
@@
 First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
-Now we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
+Next, we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
 and prove that it satisfies the condition
@@
 which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
-We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which comes from the first row of $\tW$.
+We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which is required by the first row of $\tW$.
 It can be proved by summing the known $d-1$ equations as follows
@@
 \end{align}
-The corresponding coefficient matrix has value $\omega_d^{amn}$ at coordinate $m,n$,
+The corresponding coefficient matrix has value $\omega_d^{amn}$ at coordinate $(m,n)$,
 so it is also a submatrix of a Vandermonde matrix. Similar argument gives us that $\ket{x_{k_a}} = 0$.
@@
 To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
-$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices.
+$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
 \end{proof}
@@
 %------------------------------------------------------------------------
-The extended weighted CHSH game is added to make sure that some of Alice and Bob's observables have
-eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
-The notation for the extended weighted CHSH game that enforces the eigenvalues of the observable $U$ is 
-$\CHSH_U$, where the superscript $d$ means that the rules of this game depends on $d$.
-Intuitively, this is one step towards verifying Alice and Bob use some operator $X$ with eigenvalues
-$\{\omega_d^i\}_{i \in [d]}$ in their operator solution of $\LS$.
+The extended weighted CHSH game is added to make sure that the operator $X$ extracted from 
+Alice and Bob's operator solution have eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
+In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
+$U$ and $X$ has the eigen-structure required by \cref{lm:ux_independ}.
+We denote this game that enforces the eigenvalues of the observable $U$ by
+$\CHSH_U$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
 
@@
 they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
-The scoring rules are
+Our self-test result follows the optimal behaviour in this game,
+Before presenting the optimal correlation, we give intuitions about how the players should behave.
 \begin{itemize}
-	\item \textbf{Case 1:} $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
-	they score only if $a = b$;
-	\item \textbf{Case 2a:} $x,y \in \{0,1\}$ and they answer with $a,b \in \{0,1\}$, then
-	their answers are scored according to $I_{-\cot(\pi/2d)}$
-	\item \textbf{Case 2b:} $x,y \in \{0,1\}$ and Alice answer with $\perp$, then all possible outputs from Bob
-	are discarded;
-	\item \textbf{Case 3:} $x \in {0,1}, y = \ast$, when Bob answers $\diamond$, Alice should answer with $\{0.1\}$ but not $\perp$,
-	when Bob answers $\perp$ Alice should answer $\perp$ too;
-	\item \textbf{Case 4:} other combination of inputs are not scored.
+	\item \textbf{Case 1:} when $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
+	their answer should agree;
+	\item \textbf{Case 2a:} when $x,y \in \{0,1\}$ and if they answer with $a,b \in \{0,1\}$, then
+	their answers are scored according to $I_{-\cot(\pi/2d)}$;
+	\item \textbf{Case 2b:} when $x,y \in \{0,1\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
+	\item \textbf{Case 3:} when $x \in {0,1}, y = \ast$, if Bob answers $\diamond$, 
+	Alice should answer with $\{0.1\}$ but not $\perp$,
+	if Bob answers $\perp$, Alice should answer $\perp$ too.
 \end{itemize}
-In the ideal strategy, Alice and Bob share the state $\ket{\psi} =1/\sqrt{d} \sum_{i=0}^{d-1} \ket{u_i}\ket{u_i}$.
-We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ amd
+\textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d}} \sum_{i=0}^{d-1} \ket{u_i}\ket{u_i}
+\sim \ket{\EPR{d}}$.
+We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and
 define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
- maximaize $\langle I_{-\cot(\pi/2d)} \rangle$.
+maximize $\langle I_{-\cot(\pi/2d)} \rangle$.
 
 For completeness, we show the ideal correlation in the following three charts and then give the projectors. 
-Note that we don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ because they are irrelevant
+Note that we don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ for all possible $x$,$y$ 
+because they are irrelevant.
 \begin{table}[H]
@@
 
-The robustness of this game is summarized in the following lemma.
+The self-testing property of this correlation is summarized in the following lemma.
 \begin{lemma}
@@
 	Suppose a quantum strategy $\left(\{\{\tA_x^a\}_a\}_x, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}\right)$
-	achieves the optimal correlation of $\CHSH$, then there exists unitaries $U_A$ and $U_B$ 
+	achieves the optimal correlation of $\CHSH$, 
+	and let $\ket{\tpsi'} = \tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}/\norm{\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}}^2$,
+	then there exists unitaries $U_A$ and $U_B$ 
 	and a quantum state $\ket{junk}$
@@
 	\begin{align*}
-		&U_A\x U_B \left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) = \ket{\EPR{2}}\x \ket{junk} \\
-		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 + \tB_1}{2\cos(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
-		=(\1 \x \pauliz{2} \ket{\EPR{2}}) \x \ket{junk} \\
-		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 - \tB_1}{-2\sin(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
-		=(\1 \x \paulix{2} \ket{\EPR{2}}) \x \ket{junk} 
+		&U_A\x U_B \left( \ket{\tpsi'}\right) = \ket{\EPR{2}}\x \ket{junk} \\
+		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 + \tB_1}{2\cos(\pi/2d)}\right)\ket{\tpsi'}\right]
+		=[(\1 \x \pauliz) \ket{\EPR{2}}] \x \ket{junk} \\
+		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 - \tB_1}{-2\sin(\pi/2d)}\right)\ket{\tpsi'} \right]
+		=[(\1 \x \paulix) \ket{\EPR{2}}] \x \ket{junk} 
 	\end{align*}
@@
 \begin{proof}
-Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \x \tB_y^b$ in the following proof.
+Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \tB_y^b$ in the following proof.
 
@@
 \end{align} 
-We can re-normalize the other correlations of $a,b \in [2]$ when $x,y \in [2]$ similarly and get a new set of correlations 
+We can re-normalize the other correlations of $a,b \in [2]$ when $x,y \in [2]$ similarly, and get a new set of correlations 
 which achieves the maximal value of $\langle \1_{-\cot(\pi/2d)}\rangle$. 
@@
 %------------------------------------------------------------------------
-By the following test, we want to make sure that some unitary $U$ has eigenvalue $1$.
-In this test $X = \{\tri \}$, $Y = \{0,1,\tri\}$, $A = \{\diamond, \perp\}$ and $B = \{0,1, \diamond, \perp\}$.
-The scoring rules are
+By the following test, we want to make sure that the operator $X$ has eigenvalue $1$.
+In this test $\calX = \{\tri \}$, $\calY = \{0,1,\tri\}$, $\calA = \{\diamond, \perp\}$ and $\calB = \{0,1, \diamond, \perp\}$.
+As before, we first give intuitions about how Alice and Bob should behave to achieve the optimal correlation, then
+we give the optimal correlation and the corresponding optimal strategy.
 \begin{itemize}
-	\item \textbf{Case 1} $x = y = \tri$: Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
-	they score only if $a = b$;
-	\item \textbf{Case 2} $x =\tri$ and $y = 0$: when Alice answer $\diamond$, Bob should answer $0$, when 
-	Alice answer$\perp$ all answers of Bob are accepted;
-	\item \textbf{Case 3} $x = \tri$ and $y = 1$: when Alice answer $\diamond$, Bob should answer $0$, when 
-	Alice answer$\perp$ all answers of Bob are accepted.
+	\item \textbf{Case 1}: when $x = y = \tri$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
+	their answers should agree;
+	\item \textbf{Case 2}: when $x =\tri$ and $y = 0$, if Alice answers with $\diamond$, Bob should answer $0$, and if 
+	Alice answers $\perp$, Bob can answer with any $b \in \calB$;
+	\item \textbf{Case 3}: when $x = \tri$ and $y = 1$, if Alice answers with $\diamond$, Bob should answer $0$, and if  
+	Alice answers with $\perp$, Bob can answer with any $b \in \calB$.
 \end{itemize}
 
+\textbf{The optimal correlation and strategy}.
+As in the previous test, Alice and Bob should share the entangled state
+$\ket{\psi} = \frac{1}{\sqrt{d}}\sum_{i=0}^{d-1} \ket{u_i}\ket{u_i} \sim \ket{\EPR{d}}$.
 Define the subspace $V = \spn\{ \ket{u_0} \}$.
@@
 \end{align*}
-The shared state is 
-\begin{align}
-	\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{i \in [d]} \ket{u_i}\ket{u_i}.
-\end{align}
-Note that the shared state is the same as the one used in the extended weighted CHSH game.
-So are the observables $B_0$ and $B_1$.
+Note that it is possible to construct observables $B_0$ and $B_1$ from $\LS$
+that can be used in both the extended weighted CHSH test and the single value test.
+Then we can conclude that $B_0B_1$ has eigenvalue $1$.
 
@@
 \end{table}
-The reason we have $y=0$ or $y=1$ is that we want Bob to reuse operators from $\LS$ and we want to
-conclude that $B_0B_1$ has eigenvalue $1$.
-
+
+The enforcement imposed by the single value test is summarized in the following lemma.
 \begin{lemma}
@@
 Hence $ \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} $ is in the intersection of $\supp(\tB_0^0)$ and $\supp(\tB_1^0)$.
-Since $\supp(\tB_y^0)$ and $\supp(\tB_y^1)$ are disjoint, we know
-\begin{align*}
-	(\tB_y^0 - \tB_y^1)  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}  =  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}
-\end{align*}
-for $y = 0,1$.
+Since for any $y \in [2]$, $\supp(\tB_y^0)$ and $\supp(\tB_y^1)$ are disjoint, we know
+\begin{align*}
+	(\tB_y^0 - \tB_y^1)  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}  =  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
+\end{align*}
 Therefor, we know $ \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} $ is an eigenvector of $\tB_0\tB_1$ with eigenvalue $1$ because
@@
 \end{proof}
-In the later section, when we apply this test to make sure some unitary $U$ has eigenvalue $1$, 
-we denote the test by $\SVT_U$.
+In the next section, when we apply this test to make sure the operator $X$ has eigenvalue $1$, and 
+we denote the test by $\SVT_X$.
 
@@
 %=====================================
+In this section, we introduce the combined game $\G{d}$ and then
+prove that it can self-test the state $\ket{\EPR{d}}$.
+
 %-----------------------------------------------------------------
@@
 %-----------------------------------------------------------------
-Assume the linear system game has $n$ variables and $m$ equations.
+Assume the linear system game has $n=118$ variables and $m=91$ equations.
 Alice receives $x \in \{1,\dots m+4 \}$ and Bob receives
-$y \in \{1,\dots,n+2\}$. The scoring rules are the following:
+$y \in \{1,\dots,n+2\}$. We follow the previous structure by first give intuition about how they should
+behave in this game. The correlation can be easily extracted from the behaviour list below.
 \begin{itemize}
-	\item when $x \in \{1,\dots m\}$ and $y \in \{1, \dots n\}$, they are scored according to the 
-	linear system game, $\LS$;
-	\item when $x \in \{m+1, m+2, m+3\}$ and $y \in \{1, 2, n+1\}$, they are scored according to $\CHSH_X$,
-	where 
+	\item When $x \in \{1,\dots m\}$ and $y \in \{1, \dots n\}$, they should win the 
+	linear system game $\LS$ perfectly;
+	\item when $x \in \{m+1, m+2, m+3\}$ and $y \in \{1, 2, n+1\}$, they should follow the
+	optimal correlation of the test $\CHSH_X$, where 
 	\begin{align}
@@
 	(The intuition behind is that $B_1B_2 = X$.);
-	\item when $x = m+4$ and  $y \in \{1,2,n+2\}$, they are scored according to $\SVT_X$, where
+	\item when $x = m+4$ and  $y \in \{1,2,n+2\}$, they should follow the optimal behaviour 
+	of the test $\SVT_X$, where
 	\begin{align}
@@
 	are the inputs for the game $\SVT_X$;
-	\item otherwise, they score $0$.
+	\item otherwise, their behaviour is irrelavent.
 \end{itemize}
 Note that the dimension $d$ is defined in the rules of $\CHSH_X$.
+
+\begin{proposition}
+	The game $\G{d}$ can be won perfectly by a quantum strategy.
+\end{proposition}
+We prove this proposition by giving the optimal strategy.
+\begin{proof}
+We determine the operator solution first and then we determine the shared state.
+Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
+the observables $B_1$ and $B_2$ are extended from the formulation given in the proof
+of \cref{prop:2d-subspace},
+%\begin{align}
+%	B_1 = \ketbra{x_0}{x_0} + 
+%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/2d}\ketbra{x_{d-k}}{x_k}\right)\\
+%	B_2 = \ketbra{x_0}{x_0} + 
+%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_{d-k}}{x_k} + e^{-ik\pi/2d}\ketbra{x_{k}}{x_{d-k}}\right)
+%\end{align}
+\begin{align}
+	B_1 &= \ketbra{x_0}{x_0} + 
+	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/d}\ketbra{x_{d-k}}{x_k}\right)\\
+	B_2 &= \ketbra{x_0}{x_0} + 
+	\sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
+\end{align}
+It can be checked that $B_1B_2 = \sum_{i=0}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ and the operator $U$ is
+\begin{align}
+	U = \sum_{i=0}^{d-1} \ketbra{x_{i/2 \pmod{d}}}{x_i}.
+\end{align}
+The first step of the embedding procedure in the proof of \cref{prop:embed} requires
+the commutativity between $U$ and $B_2$, which can be verified as follows,
+\begin{align}
+	UB_2U\ct = U\ketbra{x_0}{x_0}U\ct + \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct 
+	= \ketbra{x_0}{x_0} + \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct.
+\end{align}
+There are two cases to consider which are the index is even or odd.
+Note that in the following calculation, the division is not with respect to the modulo $d$.
+When the index $i$ is even, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{i/2}}{x_{d-i/2}}$, and
+when the index $i$ is odd, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{(d+i)/2}}{x_{(d-i)/2}}$,
+so we can calculate that 
+\begin{align}
+	\sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct 
+	=& \sum_{i=1}^{(d-1)/2}U\ketbra{x_{2i}}{x_{d-2i}}U\ct 
+	+ \sum_{i=0}^{(d-1)/2-1} U\ketbra{x_{2i+1}}{x_{d-(2i+1)}}U\ct\\
+	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=0}^{(d-1)/2-1} \ketbra{x_{(d+1)/2+i}}{x_{(d-1)/2-i}}\\
+	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=(d+1)/2}^{d-1} \ketbra{x_i}{x_{d-i}}\\
+	=&\sum_{i=1}^{d-1} \ketbra{x_i}{x_{d-i}}.
+\end{align}
+The decomposition of $U$ into $B_3$ and $B_4$ is similar to the decomposition of $X$ and we leave it to the curious 
+readers.
+
+In the next step of embedding, for each $x_i$, we find $y_i$ ,$z_i$, $w_i$ and $f$ such that
+$x_i = y_iz_i = fw_i$. We demonstrate how this splitting is done by pick $x_1$ as an example, 
+which is mapped to $B_1$ in the previous step. Now we map $x_1$ to $B_1'$ which is
+\begin{align}
+	B_1' = \begin{pmatrix}
+	B_1 & 0 \\
+	0 & B_1
+	\end{pmatrix},
+\end{align}
+then $y_1$, $z_1$, $w_1$ and $f$ are mapped to
+\begin{align}
+y_1 \to 
+\begin{pmatrix}
+B_1 & 0\\
+0 & \1
+\end{pmatrix},
+&&
+z_1 \to
+\begin{pmatrix}
+\1 & 0\\
+0 & B_1
+\end{pmatrix},
+\\
+w_1 \to 
+\begin{pmatrix}
+0 & B_1\\
+B_1 & 0
+\end{pmatrix},
+&&
+f \to
+\begin{pmatrix}
+0 & \1\\
+\1 & 0
+\end{pmatrix}.
+\end{align}
+
+The last step of embedding follows the same manner as we double the dimension of the operators again.
+For example, $y_1$ is mapped to $B_1 \oplus \1 \oplus B_1 \oplus \1$ and $z_1$ is mapped to 
+$\1 \oplus B_1 \oplus \1 \oplus B_1$, so effectively, $x_1$ is mapped to $B_1^{\oplus 4}$.
+\footnote{Details of this step of embedding can be found in proof of Proposition~$4.2$ in Ref.~\cite{slofstra2017}.}
+
+In the end, we determine the shared state.
+The optimal strategies for $\CHSH_X$ and $\SVT_X$ use state 
+$\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{i=0}^{d-1} \ket{u_i}\ket{u_i}$, 
+so the shared state for $\G{d}$ is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$.
+\end{proof}
 Next we are going to prove that the strategy winning this game optimally can self-test $d$-dimensional EPR pair.
@@
 %-----------------------------------------------------------------
-\subsection{Proof}
+\subsection{Proof of \cref{thm:pr_2}}
 %-----------------------------------------------------------------
 \hl{This subsection needs to be formalized.}
-By Lemma~$4.3$ of \cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
-of the linear system game: 
+
+Suppose Alice and Bob achieve the optimal correlation with the quantum strategy $(\ket{\psi}, \{A_x\}, \{B_y\})$
+for all $x,y \in \calX \times \calY$ .
+The observables $A_x$ and $B_y$ and the shared state $\ket{\psi}$ shall not be confused with the ones used in the optimal strategy.
+By Lemma~$4.3$ of Ref.~\cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
+of the linear system game $\LS$. 
 For each variable $\{ x_i \}_{i=1}^n$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
@@
 \begin{align}
-	\Tr(\rho_A \Pi_{j: A_{ij} \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m
+	\Tr(\rho_A \Pi_{j: H_{ij} \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m
 \end{align}
@@
 \begin{align}
-\Pi_{j:A_{ij} \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m.
-\end{align}
-Since the relation $uxu^\dagger = x^2$ is embedded in this linear system game, we know
+\Pi_{j:H_{ij} \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m.
+\end{align}
+Since the relation $uxu^{-1} = x^2$ is embedded in this linear system game, we know
 \begin{align}
@@
 
-By \cref{lm:chsh_comp}, we can extract states $\ket{u_0}$ and $\ket{u_1}$ from the support of $A_\ast^\diamond$,   
-and define $\ket{x_1} = 1/\sqrt{2}(\ket{u_0} + i\ket{u_1})$. 
+By \cref{lm:chsh_comp}, we can extract states $\ket{u_0}$ and $\ket{u_1}$ from the support $+1$-eigenspace of 
+$A_{m+1} = A_\ast^\diamond- A_\ast^\perp$,   
+and define $\ket{x_{A,1}} = 1/\sqrt{2}(\ket{u_0} + i\ket{u_1})$. 
 \cref{prop:2d-subspace} implies that $\ket{x_{A,1}}$ is the eigenvector of $X_A$ with eigenvalue $\omega_d$.
@@
 \end{align}
-On the other hand, we also know that $U_A \ket{x_{A,i}} = \ket{x_{A,i/2}}$ for $i = 1,2 \dots d-1$.
-Note that $U_A$ and $X_A$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
+On the other hand, by \cref{eq:ux_relation} we also know that $U_A \ket{x_{A,i}} = \ket{x_{A,i/2}}$ for $i = 1,2 \dots d-1$.
+Now we get $U_A$ and $X_A$ that satisfy the condition of \cref{lm:ux_independ} when their actions are 
 restricted to $\spn(S_A)$.
@@
 when their actions are restricted to $S_B$. Moreover, we can define a unitary $V: \supp{\rho_B} \to \supp(\rho_A)$,
-which maps $\ket{x_{B,i}}$ to $\ket{x_{A,i}}$.
+which maps $\ket{x_{B,i}}$ to $\ket{x_{A,i}}$ for $i=1\dots d-1$.
 
@@
 %for some $\tau \in L(S_A)$.
-Assume that $\ket{\psi} = \vc(\tau)$ for some $\tau \in L(\supp(\rho_B) \to \supp(\rho_A))$
+Assume that $\ket{\psi} = \vc(\tau)$ for some $\tau \in L(\supp(\rho_B), \supp(\rho_A))$
 The consistency condition is equivalent to
@@
 In the end, we turn our attention back to the single value test. 
-The implication of the single value test is that
-\begin{align}
-	A_\triangle^\diamond \ket{\psi} = A_\triangle^\diamond \x B_\triangle^\diamond \ket{\psi} = \frac{1}{\sqrt{d}}
-	\ket{x_{A,0}}\ket{x_{B,0}}
-\end{align}
-where $X_C \ket{x_{C,0}} = \ket{x_{C,0}}$ and $\ket{x_{C,0}} \in \supp(\rho_C)$ for $C = A$ or $B$. 
-Recalling \cref{eq:d-1}, we can conclude that there exists local isometries 
+The implication of the single value test is that there
+exists $\ket{x_{B,0}} \in \supp(\rho_B)$ such that $X_B \ket{x_{B,0}} = \ket{x_{B,0}}$,
+and similarly, there exists $\ket{x_{A,0}} \in supp(\rho_A)$ such that $X_A \ket{x_{A,0}} = \ket{x_{A,0}}$.
+We can further restrict $V$ so that $V\ket{x_{B,0}} = \ket{x_{A,0}}$.
+Define $S_A^\perp = \{ \ket{x_{A,0}}\}$.
+Since 
+\begin{align}
+	A_\triangle^\diamond \tau B_\triangle^\diamond =A_\triangle^\diamond \tau = \tau B_\triangle^\diamond,
+\end{align}
+and $\ket{x_{A,0}} \in \supp(A_\triangle^\diamond)$, $\ket{x_{B,0}} \in \supp(B_\triangle^\diamond)$, 
+we know that 
+\begin{align}
+\tau V^\dagger|_{S_A^\perp}  \propto \1_{S_A^\perp}.
+\end{align}
+%\begin{align}
+%	A_\triangle^\diamond \ket{\psi} = A_\triangle^\diamond \x B_\triangle^\diamond \ket{\psi} = \frac{1}{\sqrt{d}}
+%	\ket{x_{A,0}}\ket{x_{B,0}}
+%\end{align}
+By the orthogonality between $S_A$ and $S_A^\perp$, we can conclude that there exists local isometries 
 $V_A$ and $V_B$ such that
@@
 %\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
+%========================================
+\section{Extending $\G{d}$ for general prime numbers }
+\label{sec:extend}
+%========================================
 
@@
 \end{proof}
-%=====================================
-\section{Construction of $\Gamma(\LS)$}
-\label{sec:construct}
-%=====================================
-%In this section, we are going to embed the group $\Pg_{\LS}$ into a solution group $\Gamma(\LS)$ of a linear system game.
-%What we do is to write any generator with arbitrary order as a product of new order-$2$ generators and rewrite all
-%the relations with the new generators. In the end, we can get rid of the generators $y_i$ and $u$ and all 
-%the remaining generators are order-$2$.
-%
-%We first embed the relation $xzx^{-1}z^{-1} = \J$ in a linear system game very similar to the Magic Square game.
-%It has been shown that the following relations embeds $xzx^{-1}z^{-1} = \J$ \footnote{For example, Fig.~$11$ of Ref.~\cite{coladan2017}
-%proves it in a group picture.}. Let $y_3 = z$ and $y_7 = x$ and the linear relations are 
-%\begin{align*}
-%	&y_1y_2y_3 = e,
-%	&&y_4y_5y_6 = e,
-%	&&y_7y_8y_9 = e,\\
-%	&y_1^{-1}y_4^{-1}y_7^{-1} = e,
-%	&&y_2^{-1}y_5^{-1}y_8^{-1} = \J,
-%	&&y_3^{-1}y_6^{-1}y_9^{-1} = e.
-%\end{align*}
-%We refer to these set of linear relations as the $\MS_l$ relations.
-%The magic square game also introduces some commutation relations:
-%\begin{align*}
-%	&[y_1, y_2] = [y_1, y_3] = [y_1, y_4] = [y_1,y_7] = e,\\
-%	&[y_2, y_3] = [y_2, y_5] = [y_2, y_8] = e,\\
-%	&[y_3, y_6] = [y_3, y_9] = e,\\
-%	&[y_4, y_7] = [y_4,y_5] =  [y_4,y_6] = e, \\
-%	& [y_5,y_6] =  [y_5,y_8] = e,\\
-%	& [y_6,y_9] = e,\\
-%	& [y_7,y_8] =  [y_7,y_9] = e,\\
-%	&[y_8,y_9] = e.
-%\end{align*}
-%The set of the commutation relations above is denoted by $\MS_c$.
-%So we redefine $\Pg_{\LS}$ as 
-%\begin{align}
-%	\Pg_{\LS} = \langle \{y_i\}_{i=1}^9,u,\J: \MS_l \cup \MS_c \cup \{ [\J, y_i] = [\J, u] = e,
-%					uy_7u^{-1} = y_7^2, u^{-1}y_3u = y_3^2\}	 \rangle.
-%\end{align}
-%Then we can use a procedure similar to the one used in the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017} to 
-%embed $\Pg_{\LS}$ into a group with only order-$2$ generators except for $\J$, whose order is implicit.
-%
-%We start by introducing $y_{3,1}$ and $y_{3,2}$ of order $2$ such that $y_3 = y_{3,1}y_{3,2}$ 
-%and $y_{3,1}$ commutes with $u$, $\J$ and $y_i$ for $ i \neq 3$.
-%Then the relation $uy_3u^{-1} = y_3^2$ is rewritten as $uy_{3,2}u^{-1} = y_{3,2}y_{3,1}y_{3,2}$ so we introduce $y_{3,3} = y_{3,2}y_{3,1}y_{3,2}$.
-%The group $\Pg_{\LS}$ becomes
-%\begin{equation}
-%\begin{aligned}
-%	\Pg_{\LS} = \langle y_{3,1}, y_{3,2}, y_{3,3}, u, \{y_i\}_{i \neq 3} \J: &y_{3,1}^2 = y_{3,2}^2 = y_{3,3}^2 =e,\\
-%	&\J \text{ commute with  all the generators, } [y_i,y_{3,1}] = [u,y_{3,1}] =  e \text{ for } i \neq 3,\\
-%	&\MS_c \text{ with $y_3$ replaced by $y_{3,2}$},
-%	\MS_l \text{ with $y_3$ replaced by $y_{3,1}y_{3,2}$},\\
-%	& u^{-1}y_7u = y_7^2, 
-%	y_{3,3} = y_{3,2}y_{3,1}y_{3,2}, uy_{3,2}u^{-1} = y_{3,3}\rangle.
-%\end{aligned}
-%\end{equation}
-%Next, we introduce $y_{7,1}$ and $y_{7,2}$ of order $2$ such that $y_7 = y_{7,1}y_{7,2}$ and 
-%$y_{7,1}$ commutes with $u$, $\J$ and $y_i$ for $i \neq 3,7$.
-%Then the relation $u^{-1}y_7u = y_7^2$ is rewritten as $u^{-1}y_{7,2}u = y_{7,2}y_{7,1}y_{7,2}$ so we introduce $y_{7,3} = y_{7,2}y_{7,1}y_{7,2}$.
-%The relation $y_7y_{3,1}y_7^{-1} = y_{3,1}$ is rewritten as $y_{7,2}y_{3,1}y_{7,2} = y_{7,1}y_{3,1}y_{7,1}$ so we introduce $y_{7,4} = y_{7,1}y_{3,1}y_{7,1}$.
-%The group $\Pg_{\LS}$ becomes
-%\begin{equation}
-%\begin{aligned}
-%	\Pg_{\LS} = \langle \{y_{3,i}\}_{i=1}^3, \{ y_{7,i} \}_{i=1}^4, \{y_i\}_{i\neq 3, 7}, u, \J: &\{y_{3,i}\}_{i=1}^3 \{y_{7,i}\}_{i=1}^4 \text{ of order } 2;\\
-%	&\J \text{ commutes with all the generators, } [u, y_{3,1}] = [u, y_{7,1}] = e,\\
-%	&y_{3,1}, y_{7,1} \text{ commute with } y_i,\; i \neq 3,7,\\
-%	& \MS_c \text{ with $y_3, y_7$ replaced by $y_{3,2}, y_{7,2}$},\\
-%	& \MS_l \text{ with $y_3$, $y_7$ replaced by $y_{3,1}y_{3,2}$ and $y_{7,1}y_{7,2}$} \\
-%	&y_{3,3} = y_{3,2}y_{3,1}y_{3,2}, uy_{3,2}u^{-1} = y_{3,3}, \\
-%	&y_{7,3} = y_{7,2}y_{7,1}y_{7,2}, u^{-1}y_{7,2}u = y_{7,3},\\
-%	&y_{7,4} = y_{7,1}y_{3,1}y_{7,1}, y_{7,2}y_{3,1}y_{7,2} = y_{7,4} \rangle
-%\end{aligned}
-%\end{equation}
-%To replace $u$, we introduce $u_1, u_2$ of order $2$ such that $u = u_1u_2$ and $u_1$ commutes with
-%$y_i$ for $i \neq 3,7$ and $\J$.
-%The conjugacy relations involving $u$ are $uy_{3,2}u^{-1} = y_{3,3}$, $u^{-1}y_{7,2}u = y_{7,3}$,
-%$uy_{3,1}u^{-1} = y_{3,1}$ and $uy_{7,1}u^{-1} = y_{7,1}$. So we need to introduce $u_3,u_4,u_5,u_6$ such that 
-%\begin{align*}
-%	u_3 = u_2y_{3,2}u_2 = u_1y_{3,3}u_1, \\
-%	u_4 = u_1y_{7,2}u_1 = u_2y_{7,3}u_2,\\
-%	u_5 = u_2y_{3,1}u_2 = u_1y_{3,1}u_1,\\
-%	u_6 = u_2y_{7,1}u_2 = u_1y_{7,1}u_1.
-%\end{align*}
-%At this stage $\Pg_{\LS}$ has generators $\{y_{3,i}\}_{i=1}^3, \{ y_{7,i} \}_{i=1}^4, \{y_i\}_{i\neq 3, 7}, \{u_i\}_{i=1}^6$ with $6$ linear relations and $44$ conjugacy relations. 
-%
-%For the remaining $y_i$'s, we use $y_1$ as an example and the same steps apply to the other $y_i$'s.
-%The conjugacy relations involving $y_1$ are 
-%\begin{align*}
-%	y_{1}y_{3,1} y_1^{-1} = y_{3,1},
-%	&&y_{1}y_{7,1}y_1^{-1} = y_{7,1}.
-%\end{align*}
-%and $4$ commutation relations from $\MS_c$.
-%So we need to introduce $y_{1,i}$ for $i = 1, 2 \dots 8$ such that they all are of order $2$ and
-%\begin{align*}
-%&y_1= y_{1,1} y_{1,2}\\
-%&y_{1,3} = y_{1,2} y_{3,1}y_{1,2} = y_{1,1} y_{3,1}y_{1,1},\\
-%&y_{1,4} = y_{1,2} y_{7,1}y_{1,2} = y_{1,1} y_{7,1}y_{1,1},\\
-%&y_{1,5} = y_{1,2} y_{2}y_{1,2} = y_{1,1} y_{2}y_{1,1},\\
-%&y_{1,6} = y_{1,2} y_{3,2}y_{1,2} = y_{1,1} y_{3,2}y_{1,1},\\
-%&y_{1,7} = y_{1,2} y_{4}y_{1,2} = y_{1,1} y_{4}y_{1,1},\\
-%&y_{1,8} = y_{1,2} y_{7,2}y_{1,2} = y_{1,1} y_{7,2}y_{1,1}.
-%\end{align*}
-%The new commutation relations are $y_{1,1}$ commutes with all the remaining $y_j$'s
-%and commutation relations from $\MS_c$ involving $y_1$ with $y_1$ replaced by $y_{1,2}$.
-%Then we repeat this process with $y_2$.
-%In summary, replacing $y_1,y_2,y_4,y_5,y_6,y_8,y_9$ introduces $8+9+10+11+12+13+14 = 77$ new variables 
-%and $12+14+16+18+20+22+24 = 126$ new conjugacy relations. 
-%In total $\Pg_{\LS}$ has $90$ variables excluding $\J$, $6$ linear relations and $170$ conjugacy relations.
-%
-%Then following the recipe given in the proofs of Proposition~$4.2$ and Lemma~$4.4$ in Ref.~\cite{slofstra2017}, 
-%we embed $\Pg_{\LS}$ into the solution 
-%group $\Gamma(\LS)$ with $2351$ variables and $1916$ linear relations. 
-%Alice's output alphabet is of size $64$ and of size $2$ for Bob.
-%
-%Such linear system game has at the biggest size when $a = 5$ or the special relation is $uxu^{-1} = x^5$.
-%The biggest game has $2465$ variables and $2006$ equations. We leave the derivation for curious readers.
+%%=====================================
+%\section{Construction of $\Gamma(\LS)$}
+%\label{sec:construct}
+%%=====================================
 

### 2019-01-27 Draft/draft.tex
Honghao: completed self-testing proof, rescaled weighted CHSH test, removed single value test and added equations for the linear system game

@@
 \newcommand{\pauliz}{\sigma_z}
-\newcommand{\G}[1]{G^{(#1)}}
+\newcommand{\G}{G}
 \newcommand{\LS}{LS}
@@
 The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
-one copy of it by the CHSH inequality \cite{bamps2015}. Many copies of the $2$-dimensional EPR
-pair can be self-tested in parallel \cite{mckague2016, coladan2017parallel}. 
+one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
+pair in parallel \cite{mckague2016, coladan2017parallel}. 
 Self-testing general $d$-dimensional EPR pairs is a harder task.
@@
 
-So far, general $d$-dimensional maximally entangled states are self-tested by
+In summary, general $d$-dimensional maximally entangled states are self-tested by
 modifying the correlation and enlarging the size of the correlation.
@@
 \label{thm:inf}
-	There exists a set $D$ of odd prime numbers such that for any $d \in D$, 
-	the maximally entangled state of local dimension $d$ can be self-tested 
-	with constant question and answer sets.
+	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
+	the maximally entangled state of local dimension $d-1$ can be self-tested 
+	with constant-sized question and answer alphabets.
 \end{theorem}
@@
 The set $D$ is easily characterizable as it contains all the odd prime numbers with 
-primitive root $2$, $3$ or $5$. To prove \cref{thm:inf}, we give explicit self-testing proof of 
-the maximally entangled state with local dimension $d$ whose primitive root is $2$ by explicitly giving the 
+primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
+with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
+To prove \cref{thm:inf}, we give explicit self-testing proof of 
+the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$ by explicitly giving the 
 correlation that achieves this goal. Then the self-testing property of this correlation is 
@@
 \label{thm:pr_2}
-	All maximally entangled state with local dimension $d$, where $d$ is prime and has
+	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
 	primitive root $2$, can be self-tested by a constant-sized correlation.
@@
 
+In order to accomplish our goal, we introduce new techniques for self-testing.
+First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
+some unknown operator which is decomposed into two binary observables, which is not done before.
+Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintain
+certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
+Intuitively, such decomposition can be seen as the inverse of the decomposition used in the proof of Jordan's lemma.
+The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
+which is the core idea in all the previous self-testing results. 
+Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.
+
 \textbf{Structure of the paper}.
 We start with notations and background information in \cref{sec:prelim}.
-Since the game we designed consists of several sub-tests, we introduce the individual
-sub-tests and their implications in \cref{sec:comp}. Our main result is based the combination
+Since the game we designed consists of two sub-tests, we introduce one test
+in \cref{sec:lsg} and one in \cref{sec:chsh}. Our main result is based the combination
 of the sub-tests and presented in \cref{sec:main}. In \cref{sec:extend}, we show how to adapt
@@
 %We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.
-
-\textbf{The EPR pair.} Our goal is to self-test maximally entangled state of local dimension $d$, 
+The EPR pair of local dimension $d$ for $d \geq 2$ is the maximally entangled state and is denoted by
 \begin{align}
@@
 \begin{align}
-	X = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i} && U = \sum_{i=0}^{d-1} \ketbra{i/2}{i},
+	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/2}{k},
 \end{align}
 where $\omega_d = e^{i2\pi/d}$ is the primitive $d$th root of unity.
-Through out this paper, any operation on the label of the eigenvector $i$ is taken modulo $d$.
-for example, the $i/2$ above.
+Through out this paper, any operation on the label of the eigenvector $k$ is taken modulo $d$,
+unless otherwise specified, for example, the $i/2$ above.
 
@@
 	at least $2\sqrt{1+\alpha^2} - \epsilon$
-	for some $\alpha$, then
+	for some $\epsilon$, then
 	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
@@
 We defer the proof of \cref{thm:selftest} till Appendix~\ref{sec:selftest}.
-After proving the robust the self-testing result, we take one step further and observe some interesting behaviour of the 
+After proving the robust self-testing result, we take one step further and observe an interesting property of the 
 observable $\tilde{B}_0\tilde{B}_1$.
@@
 	By \cref{thm:selftest}, the condition that the strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
-	maximal value of $\I_{\cot(-\pi/2d)} $ implies that there exist states $\ket{u_0}, \ket{u_1} \in \supp(\Tr_B(\ketbra{\tpsi}{\tpsi}))$ such that 
+	maximal value of $\I_{\cot(-\pi/2d)} $ implies that there exist states $\ket{u_0}, \ket{u_1} \in \supp(\Tr_A(\ketbra{\tpsi}{\tpsi}))$ such that 
 	\begin{align*}
@@
 
-\textbf{Nonlocal game}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
-to give ananswer for a chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
+\textbf{Nonlocal games}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
+to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
 Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
@@
 
-The main contribution of our work is the construction of a nonlocal game $\G{d}$ with constant-sized $X$,$Y$,$A$ and $B$
-that can be used to self-test $\ket{\EPR{d}}$ for arbitrary odd prime $d$. 
-The nonlocal game is a linear system game with modifications or further enforcements. 
+The main contribution of our work is the construction of a nonlocal game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
+such that its optimal correlation can self-test $\ket{\EPR{d}}$ for arbitrary $d \in D$. 
+The nonlocal game is a linear system game with modifications and strict enforcements. 
 We introduce the definition of self-testing first and then the definition of linear system game, 
-which come from Ref.~\cite{coladan2017, slofstra2017}.
+following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
 \begin{definition}[Self-testing]
@@
 %linear system game from its operator solution and vice versa.
-%========================================
-\section{Components of $\G{d}$}
-\label{sec:comp}
-%========================================
-The goal of this section and the next section is to 
-present a nonlocal game that can self-test $\ket{\EPR{d}}$, 
-where $d$ is prime and has primitive root $2$\footnote{By $d$ has primitive root $2$,
-we mean that $2$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$.
-When $d$ is prime, $\Z_d^\times = \{1,2\dots d-1\}$.}
-The game we constructed is denoted by $\G{d}$, which is the combination of several tasks.
-In this section, we introduce such tests and their implications.
-In \cref{sec:main}, we show how the implications can be combined to give a full self-test of $\ket{\EPR{d}}$. 
-%----------------------------------------------------------------
-\subsection{The linear system game}
-%----------------------------------------------------------------
+
+%=======================================
+\section{The linear system game}
+\label{sec:lsg}
+%=======================================
+The goal of this section and the following two sections is to 
+present a correlation that can self-test $\ket{\EPR{d-1}}$, 
+where $d$ is prime and has primitive root $2$. 
+If $d$ has primitive root $2$,
+then $2$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$.
+When $d$ is prime, $\Z_d^\times = \{1,2\dots d-1\}$.
+The correlation we constructed is the optimal correlation for a game $\G$, which is the combination of two tests.
+In this section, we introduce the linear system game which tests a relation that should be satisfied by 
+Alice and Bob's observables.
+
 Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$, which
-is included in the group $K$.
-The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is the embedding of the 
+is included in the group $K$, which has presentation
+\begin{align*}
+	K = \langle a,b,c,x,y: a^2=b^2=c^2 = e, c=ab, yay^{-1} = a, yby^{-1}= c, xyx^{-1} = y^2\rangle.
+\end{align*}
+The main component of $\G$ is a linear system game $\LS$, whose solution group is the embedding of the 
 following group
@@
 \begin{align}
-	C= \{ &(1,2,5), (3,5,7), (4,1,7), (4,2,6), (3,2,6)\},
+	C= \{ (1,2,5), (3,5,7), (4,1,7), (4,2,6), (3,2,6)\},
 \end{align}
@@
 %\end{align}
-%Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
+%Consequently, the $d$ dependency of $\G$ comes from constraints imposed by other components of the game,
 %\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
@@
 
-%------------------------------------------------------------------------
-\subsection{The extended weighted CHSH game}
-%------------------------------------------------------------------------
+%======================================
+\section{The extended weighted CHSH game}
+\label{sec:chsh}
+%======================================
 The extended weighted CHSH game is added to make sure that the operator $X$ extracted from 
@@
 	\item \textbf{Case 2a:} when $x,y \in \{0,1\}$ and if they answer with $a,b \in \{0,1\}$, then
-	their answers are scored according to $I_{-\cot(\pi/2d)}$;
+	their answers are scored according to $I_{\cot(-\pi/2d)}$;
 	\item \textbf{Case 2b:} when $x,y \in \{0,1\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
@@
 \end{itemize}
-\textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d}} \sum_{i=0}^{d-1} \ket{u_i}\ket{u_i}
-\sim \ket{\EPR{d}}$.
+\textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$.
 We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and
 define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
-maximize $\langle I_{-\cot(\pi/2d)} \rangle$.
+maximize $\langle I_{\cot(-\pi/2d)} \rangle$.
 
@@
 \hline
-\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & 2/d & 0 \\
+\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & 2/(d-1) & 0 \\
 \cline{2-4}
-&$b=\perp$ & 0 & (d-2)/d \\
+&$b=\perp$ & 0 & (d-3)/(d-1) \\
 \hline
@@
 \hline
-\multirow{2}{*}{$y = 0$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{\sin^2(\pi/4d)}{d}$ & \small $\pr{\perp0}{00}$ 
-& $\frac{1+\sin(\pi/2d)}{2d}$ & $\frac{1-\sin(\pi/2d)}{2d}$ & \small  $\pr{\perp0}{10}$ \\
+\multirow{2}{*}{$y = 0$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d-1}$ & $\frac{\sin^2(\pi/4d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
+& $\frac{1+\sin(\pi/2d)}{2(d-1)}$ & $\frac{1-\sin(\pi/2d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/4d)}{d}$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{d-2}{d}-\pr{\perp0}{00}$ 
-&  $\frac{1-\sin(\pi/2d)}{2d}$ & $\frac{1+\sin(\pi/2d)}{2d}$ & \small $\frac{d-2}{d} - \pr{\perp0}{10}$  \\
+&$b=1$ & $\frac{\sin^2(\pi/4d)}{d-1}$ & $\frac{\cos^2(\pi/4d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
+&  $\frac{1-\sin(\pi/2d)}{2(d-1)}$ & $\frac{1+\sin(\pi/2d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
 \hline
-\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{\sin^2(\pi/4d)}{d}$ & \small $\pr{\perp0}{01}$ & 
-$ \frac{1-\sin(\pi/2d)}{2d}$ & $ \frac{1+\sin(\pi/2d)}{2d}$ & \small $\pr{\perp 0}{11}$  \\
+\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d-1}$ & $\frac{\sin^2(\pi/4d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
+$ \frac{1-\sin(\pi/2d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/2d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/4d)}{d}$ & $\frac{\cos^2(\pi/4d)}{d}$ & \small $\frac{d-2}{d}-\pr{\perp0}{01}$ &  
-$ \frac{1+\sin(\pi/2d)}{2d}$ & $ \frac{1-\sin(\pi/2d)}{2d}$ & \small $\frac{d-2}{d}- \pr{\perp 0}{11}$ \\
+&$b=1$ & $\frac{\sin^2(\pi/4d)}{d-1}$ & $\frac{\cos^2(\pi/4d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
+$ \frac{1+\sin(\pi/2d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/2d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
 \hline
@@
 \hline
-\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/d$ & $1/d$ & 0 
-& $1/d$ & $1/d$ & 0 \\
+\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/(d-1)$ & $1/(d-1)$ & 0 
+& $1/(d-1)$ & $1/(d-1)$ & 0 \\
 \cline{2-8}
-&$b=\perp$ & 0 & 0 & $\frac{d-2}{d}$ 
-&  0 & 0 & \small $\frac{d-2}{d} $  \\
+&$b=\perp$ & 0 & 0 & $\frac{d-3}{d-1}$ 
+&  0 & 0 & \small $\frac{d-3}{d-1} $  \\
 \hline
@@
 \begin{proof}
-Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \tB_y^b$ in the following proof.
-
-From the marginal distribution $\pb{\diamond}{\ast} = \pa{0}{0}+\pa{1}{0} = 2/d$,
-we know $\| \tB_\ast^\diamond \ket{\tpsi} \| = \| (\tA_0^0+\tA_0^1) \ket{\tpsi}\| = \sqrt{2/d}$.
-Since $\pr{0\diamond}{0\ast} + \pr{1\diamond}{0\ast} = 2/d$, we find that 
+Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \x\tB_y^b$ in the following proof.
+
+From the marginal distribution $\pb{\diamond}{\ast} = \pa{0}{0}+\pa{1}{0} = 2/d-1$,
+we know $\| \tB_\ast^\diamond \ket{\tpsi} \| = \| (\tA_0^0+\tA_0^1) \ket{\tpsi}\| = \sqrt{2/d-1}$.
+Since $\pr{0\diamond}{0\ast} + \pr{1\diamond}{0\ast} = 2/d-1$, we find that 
 \begin{align*}
@@
 
-%------------------------------------------------------------------------
-\subsection{The single value test}
-%------------------------------------------------------------------------
-By the following test, we want to make sure that the operator $X$ has eigenvalue $1$.
-In this test $\calX = \{\tri \}$, $\calY = \{0,1,\tri\}$, $\calA = \{\diamond, \perp\}$ and $\calB = \{0,1, \diamond, \perp\}$.
-As before, we first give intuitions about how Alice and Bob should behave to achieve the optimal correlation, then
-we give the optimal correlation and the corresponding optimal strategy.
-\begin{itemize}
-	\item \textbf{Case 1}: when $x = y = \tri$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
-	their answers should agree;
-	\item \textbf{Case 2}: when $x =\tri$ and $y = 0$, if Alice answers with $\diamond$, Bob should answer $0$, and if 
-	Alice answers $\perp$, Bob can answer with any $b \in \calB$;
-	\item \textbf{Case 3}: when $x = \tri$ and $y = 1$, if Alice answers with $\diamond$, Bob should answer $0$, and if  
-	Alice answers with $\perp$, Bob can answer with any $b \in \calB$.
-\end{itemize}
-
-\textbf{The optimal correlation and strategy}.
-As in the previous test, Alice and Bob should share the entangled state
-$\ket{\psi} = \frac{1}{\sqrt{d}}\sum_{i=0}^{d-1} \ket{u_i}\ket{u_i} \sim \ket{\EPR{d}}$.
-Define the subspace $V = \spn\{ \ket{u_0} \}$.
-The ideal strategy has projective measurement 
-\begin{align*}
-&A_\tri^\diamond = B_\tri^\diamond= \ketbra{u_0}{u_0}, 
-&&A_\tri^\perp = B_\tri^\perp = \1 - \ketbra{u_0}{u_0},\\
-&B_0^0|_V = B_1^0|_V = \ketbra{u_0}{u_0}, 
-&&B_0^1|_V = B_1^1|_V = 0.
-\end{align*}
-Note that it is possible to construct observables $B_0$ and $B_1$ from $\LS$
-that can be used in both the extended weighted CHSH test and the single value test.
-Then we can conclude that $B_0B_1$ has eigenvalue $1$.
-
-It is easy to calculate the ideal correlation, which is
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{|c|c||c|c|c|c|c|c|}
-\hline
-\multicolumn{2}{|c|}{} &
-\multicolumn{2}{|c|}{$y=\tri$} &
-\multicolumn{2}{|c|}{$y=0$} &
-\multicolumn{2}{|c|}{$y=1$}\\
-\cline{3-8}
-\multicolumn{2}{|c|}{} &$b = \diamond$ & $b = \perp$ & $b = 0$ & $b = 1$ & $b = 0$ & $b = 1$\\
-\hline
-\hline
-\multirow{2}{*}{$x = \tri$} & $a=\diamond$ & $1/d$ & 0 & $1/d$ & 0 & $1/d$ & 0 \\
-\cline{2-8}
-&$a=\perp$ & 0 & $(d-1)/d$ & \small $\pr{\perp0}{\tri0}$ & \small $\frac{d-1}{d} -\pr{\perp0}{\tri0}$  
-& \small $\pr{\perp0}{\tri1}$ & \small $\frac{d-1}{d}- \pr{\perp0}{\tri0}$  \\
-\hline
-\end{tabular}
-\caption{Ideal correlation of the single value test.}
-\end{center}
-\end{table}
-
-The enforcement imposed by the single value test is summarized in the following lemma.
-\begin{lemma}
-	\label{lm:svt_comp}
-	If a quantum strategy$(\{\tA_\tri^a\}_a, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}$ has the same behaviour as
-	the optimal one, then $(\tB_0^0 - \tB_0^1)(\tB_1^0-\tB_1^1)$ has eigenvalue $1$.
-\end{lemma}
-\begin{proof}
-By the marginal distribution we know that $\| A_\tri^\diamond \ket{\psi}\| = \frac{1}{\sqrt{d}}$.
-From the condition that $P(\diamond 0|\tri 0) = 1/d$, we know
-\begin{align}
-	\frac{  \bra{\psi} \tA_\tri^\diamond  \tB_0^0 \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|^2} = 1,
-\end{align}
-which implies that 
-\begin{align}
- \tB_0^0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
-\end{align}
-With similar reasoning, we get
-\begin{align}
- \tB_1^0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
-\end{align}
-Hence $ \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} $ is in the intersection of $\supp(\tB_0^0)$ and $\supp(\tB_1^0)$.
-Since for any $y \in [2]$, $\supp(\tB_y^0)$ and $\supp(\tB_y^1)$ are disjoint, we know
-\begin{align*}
-	(\tB_y^0 - \tB_y^1)  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}  =  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
-\end{align*}
-Therefor, we know $ \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} $ is an eigenvector of $\tB_0\tB_1$ with eigenvalue $1$ because
-\begin{align}
-	\tB_0\tB_1 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \tB_0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} =  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
-\end{align}
-\end{proof}
-In the next section, when we apply this test to make sure the operator $X$ has eigenvalue $1$, and 
-we denote the test by $\SVT_X$.
-
 %=====================================
@@
 %=====================================
-In this section, we introduce the combined game $\G{d}$ and then
-prove that it can self-test the state $\ket{\EPR{d}}$.
+In this section, we introduce the combined game $\G{d-1}$ and then
+prove that it can self-test the state $\ket{\EPR{d-1}}$.
 
 %-----------------------------------------------------------------
-\subsection{The game $\G{d}$}
+\subsection{The correlation for the game $\G$}
 %-----------------------------------------------------------------
 Assume the linear system game has $n=118$ variables and $m=91$ equations.
-Alice receives $x \in \{1,\dots m+4 \}$ and Bob receives
-$y \in \{1,\dots,n+2\}$. We follow the previous structure by first give intuition about how they should
+Alice receives $x \in \{1,\dots m+3 \}$ and Bob receives
+$y \in \{1,\dots,n+1\}$. We follow the previous structure by first give intuition about how they should
 behave in this game. The correlation can be easily extracted from the behaviour list below.
@@
 	(The intuition behind is that $B_1B_2 = X$.);
-	\item when $x = m+4$ and  $y \in \{1,2,n+2\}$, they should follow the optimal behaviour 
-	of the test $\SVT_X$, where
-	\begin{align}
-		& \tri_A = m+4 \\
-		& \tri_B = n+2, \quad 1_B = 1,\quad 2_B = 2
-	\end{align}
-	are the inputs for the game $\SVT_X$;
-	\item otherwise, their behaviour is irrelavent.
+	\item otherwise, their behaviour is irrelavant.
 \end{itemize}
@@
 \begin{proposition}
-	The game $\G{d}$ can be won perfectly by a quantum strategy.
+	The game $\G{d-1}$ can be won perfectly by a quantum strategy.
 \end{proposition}
@@
 In the end, we determine the shared state.
-The optimal strategies for $\CHSH_X$ and $\SVT_X$ use state 
-$\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{i=0}^{d-1} \ket{u_i}\ket{u_i}$, 
-so the shared state for $\G{d}$ is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$.
+The optimal correlation for $\CHSH_X$ uses state 
+$\ket{\psi} = \frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$, 
+so the shared state for $\G$ is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$.
 \end{proof}
-Next we are going to prove that the strategy winning this game optimally can self-test $d$-dimensional EPR pair.
+Next we are going to prove that the strategy winning this game optimally can self-test $d-1$-dimensional EPR pair.
 
@@
 	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
+	\text{ for } 1 \leq i \leq n
 \end{align}
@@
 
-By \cref{lm:chsh_comp}, we can extract states $\ket{u_0}$ and $\ket{u_1}$ from the support $+1$-eigenspace of 
-$A_{m+1} = A_\ast^\diamond- A_\ast^\perp$,   
-and define $\ket{x_{A,1}} = 1/\sqrt{2}(\ket{u_0} + i\ket{u_1})$. 
-\cref{prop:2d-subspace} implies that $\ket{x_{A,1}}$ is the eigenvector of $X_A$ with eigenvalue $\omega_d$.
-Similarly, define $\ket{x_{A,d-1}} = 1/\sqrt{2}(\ket{u_0} - i\ket{u_1})$ such that $X_A \ket{x_{A,d-1}} = \omega_d^{d-1}\ket{x_{A,d-1}}$.
+Suppose $A_{m+1} = A_\ast^\diamond- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
+$2m$-dimensional vector space and $\Pi_{V_A}$ is the projector onto it. The reason why it has dimension $2m$
+will be clear shortly. On Bob's side, we also have $B_{n+1} = B_\ast^\diamond- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
+Recall that from the extended weighted CHSH test, we know
+\begin{align}
+	A_\ast^\diamond \ket{\psi} = B_\ast^\diamond \ket{\psi} = A_\ast^\diamond \x B_\ast^\diamond \ket{\psi},
+\end{align}
+which implies that with an appropriate change of basis, we can get $V_A = V_B$, so in the rest of the proof
+we drop the subscript of $V$.
+By \cref{lm:chsh_comp} and \cref{prop:2d-subspace}, we know $V$ consists of $\omega_d$-eigenvectors and $\omega_d^{-1}$ eigenvectors of 
+$X_A$, so we can write 
+\begin{align}
+	\Pi_{V} = \Pi_{V_1} + \Pi_{V_{d-1}},
+\end{align}
+where $\Pi_{V_{1}}$ is the projector onto the $\omega_d$-eigenspace of $X_A$ and $\Pi_{V_{d-1}}$ is the projector 
+onto the $\omega_d^{-1}$-eigenspace of $X_A$.
+Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.
 Hence, by \cref{eq:ux_relation} we can calculate the eigen-decomposition of $X_A$ in $\supp(\rho_A)$.
@@
 \label{eq:ladder}
- X_AU_A^\dagger \ket{x_{A,1}} = U_A^\dagger X_A^2 \ket{x_{A,1}} = \omega_d^2 U_A^\dagger \ket{x_{A,1}},
-\end{align}
-so $U_A^\dagger \ket{x_{A,1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^2$.
-By induction, we know $X_A (U_A^\dagger)^i \ket{x_{A,1}} = \omega_d^{2^i} (U_A^\dagger)^i\ket{x_{A,1}}$. 
-From the set $\{(U_A^\dagger)^i \ket{x_{A,1}}\}_{i=0}^{d-2}$, we can identify $\ket{x_{A,i}}$ for $i = 1 \dots  d-1$
-such that $X_A \ket{x_{A,i}} = \omega_d^i \ket{x_{A,i}}$ and 
-\begin{align}
-S_A = \spn \{ \ket{x_{A,1}}, \ket{x_{A,2}} \dots  \ket{x_{A,d-1}} \} \subset \supp(\rho_A).
-\end{align}
-On the other hand, by \cref{eq:ux_relation} we also know that $U_A \ket{x_{A,i}} = \ket{x_{A,i/2}}$ for $i = 1,2 \dots d-1$.
-Now we get $U_A$ and $X_A$ that satisfy the condition of \cref{lm:ux_independ} when their actions are 
-restricted to $\spn(S_A)$.
-
-Similar argument applies to Bob's operators. We can identify $X_B = B_1B_2$, 
-$U_B=B_3B_4$ and a vector space $S_B =\spn\{ \ket{x_{B,1}}, \ket{x_{B,2}} \dots  \ket{x_{B,d-1}} \} \subset \supp(\rho_B)$,
-such that 
-\begin{align}
-	X_B = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_{B,i}}{x_{B,i}} && U_B = \sum_{i=1}^{d-1} \ketbra{x_{B,i/2}}{x_{B,i}},
-\end{align}
-when their actions are restricted to $S_B$. Moreover, we can define a unitary $V: \supp{\rho_B} \to \supp(\rho_A)$,
-which maps $\ket{x_{B,i}}$ to $\ket{x_{A,i}}$ for $i=1\dots d-1$.
+ X_AU_A^\dagger \ket{x_{1}} = U_A^\dagger X_A^2 \ket{x_{1}} = \omega_d^2 U_A^\dagger \ket{x_{1}},
+\end{align}
+so $U_A^\dagger \ket{x_{1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^2$.
+By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{2^i} (U_A^\dagger)^i\ket{x_{A,1}}$. 
+From the set $\{(U_A^\dagger)^i \Pi_{V_1} (U_A)^i \}_{i=0}^{d-2}$, we can identify $\Pi_{V_i}$ for $i = 1 \dots  d-1$
+such that $\Pi_{V_i}$ is the projector onto the $\omega_d^i$-eigenspace of $X_A$,
+and 
+\begin{align}
+ \cup_{i \in [d-1]+1} V_i \subset \supp(\rho_A).
+\end{align}
+Since unitary transformation does not change the rank of a matrix, we know $\rank(\Pi_{V_1}) = \rank(\Pi_{V_{i}}) =m$
+for $ i =1 \dots d-1$,
+and we assume 
+\begin{align}
+ \Pi_{V_i} = \sum_{j=1}^m \ketbra{x_{i,j}}{x_{i,j}}.
+\end{align}
+By \cref{eq:ux_relation} we also know that $U_A \ket{x_{i,j}} = \ket{x_{i/2,j}}$ for $i = 1,2 \dots d-1$.
+In order to apply \cref{lm:ux_independ}, we construct $m$ subspaces $\{W_j\}_{j=1}^m$ where 
+\begin{align}
+	W_j = \spn( \{ \ket{x_{i,j}} \}_{i=1}^{d-1} )
+\end{align}
+The subspace $W_j$ is orthogonal to $W_{j'}$ for $j \neq j'$, and
+$U_A$ and $X_A$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
+restricted to each $W_j$.
+Similar argument also applies to operator $X_B$ and $U_B$ on Bob's side.
+
+%Similar argument applies to Bob's operators. We can identify $X_B = B_1B_2$, 
+%$U_B=B_3B_4$ and a vector space $S_B =\spn\{ \ket{x_{B,1}}, \ket{x_{B,2}} \dots  \ket{x_{B,d-1}} \} \subset \supp(\rho_B)$,
+%such that 
+%\begin{align}
+%	X_B = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_{B,i}}{x_{B,i}} && U_B = \sum_{i=1}^{d-1} \ketbra{x_{B,i/2}}{x_{B,i}},
+%\end{align}
+%when their actions are restricted to $S_B$. Moreover, we can define a unitary $V: \supp{\rho_B} \to \supp(\rho_A)$,
+%which maps $\ket{x_{B,i}}$ to $\ket{x_{A,i}}$ for $i=1\dots d-1$.
 
@@
 %for some $\tau \in L(S_A)$.
-Assume that $\ket{\psi} = \vc(\tau)$ for some $\tau \in L(\supp(\rho_B), \supp(\rho_A))$
+With an appropriate change of basis, we 
+assume that $\ket{\psi} = \vc(\tau)$ for some $\tau \in L(\supp(\rho_A))$
 The consistency condition is equivalent to
@@
 \begin{align}
-	X_A \tau X_B^\dagger = A_1A_2\tau B_2^\dagger B_1^\dagger = A_1\tau B_1^\dagger = \tau.
-\end{align}
-Inserting $V^\dagger V$ between $\tau$ and $X_B$ and multiplying $V^\dagger$ to the right on both sides yield that 
-\begin{align}
-	X_A \tau V^\dagger X_A^\dagger = X_A \tau V^\dagger VX_B^\dagger V^\dagger = \tau V^\dagger,
-\end{align}
-where we use the relation $VX_B^\dagger V^\dagger = X_A$.
+	X_A \tau X_A^\dagger = A_1A_2\tau B_2^\dagger B_1^\dagger = A_1\tau B_1^\dagger = \tau.
+\end{align}
 Similar argument gives us that 
 \begin{align}
-	U_A \tau V^\dagger  U_A^\dagger = \tau V^\dagger.
+	U_A \tau U_A^\dagger = \tau.
 \end{align}
@@
 \begin{align}
-	U_A^kX_A^l \tau V^\dagger (U_A^kX_A^l)^\dagger = \tau V^\dagger.
-\end{align}
-By \cref{lm:ux_independ}, $\tau V^\dagger$ projected onto $L(S_A)$ commutes with all the $(d-1) \times (d-1)$ matrices, which means that 
+	U_A^kX_A^l \tau (U_A^kX_A^l)^\dagger = \tau.
+\end{align}
+Let $\Pi_{W_j}$ be the projector onto $W_j$. 
+By \cref{lm:ux_independ}, $\Pi_{W_j} \tau \Pi_{W_j}$ commutes with all the $(d-1) \times (d-1)$ matrices, which means that 
 \begin{align}
 	\label{eq:d-1}
-	\tau V^\dagger|_{S_A}  \propto \1_{S_A}.
-\end{align}
-
-In the end, we turn our attention back to the single value test. 
-The implication of the single value test is that there
-exists $\ket{x_{B,0}} \in \supp(\rho_B)$ such that $X_B \ket{x_{B,0}} = \ket{x_{B,0}}$,
-and similarly, there exists $\ket{x_{A,0}} \in supp(\rho_A)$ such that $X_A \ket{x_{A,0}} = \ket{x_{A,0}}$.
-We can further restrict $V$ so that $V\ket{x_{B,0}} = \ket{x_{A,0}}$.
-Define $S_A^\perp = \{ \ket{x_{A,0}}\}$.
-Since 
-\begin{align}
-	A_\triangle^\diamond \tau B_\triangle^\diamond =A_\triangle^\diamond \tau = \tau B_\triangle^\diamond,
-\end{align}
-and $\ket{x_{A,0}} \in \supp(A_\triangle^\diamond)$, $\ket{x_{B,0}} \in \supp(B_\triangle^\diamond)$, 
-we know that 
-\begin{align}
-\tau V^\dagger|_{S_A^\perp}  \propto \1_{S_A^\perp}.
-\end{align}
-%\begin{align}
-%	A_\triangle^\diamond \ket{\psi} = A_\triangle^\diamond \x B_\triangle^\diamond \ket{\psi} = \frac{1}{\sqrt{d}}
-%	\ket{x_{A,0}}\ket{x_{B,0}}
-%\end{align}
-By the orthogonality between $S_A$ and $S_A^\perp$, we can conclude that there exists local isometries 
-$V_A$ and $V_B$ such that
-\begin{align}
-	V_A \x V_B \ket{\psi} = \ket{\EPR{d}}.
+	\Pi_{W_j} \tau \Pi_{W_j}  = c_j \1_{S_A} \text{ for } j = 1\dots m.
+\end{align}
+In the vector form, we know
+\begin{align}
+	\sum_{j =1}^m \Pi_{W_j} \ket{\psi} =\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}. 
+\end{align}
+Recalling the fact that 
+\begin{align}
+\norm{ \Pi_{V_1} + \Pi_{V_{d-1}} \ket{\psi}}^2 = \norm{\Pi_{V_1} \ket{\psi}}^2 + \norm{\Pi_{V_{d-1}} \ket{\psi}}^2 = \frac{2}{d-1},
+ \end{align}
+ it means that 
+ \begin{align}
+ 	2 \sum_{j=1}^m \norm{c_j}^2 = \frac{2}{d-1}.
+ \end{align}
+ Then we can calculate the norm of $\sum_{j =1}^m \Pi_{W_j} \ket{\psi}$, which is
+ \begin{align}
+ \norm{\sum_{j =1}^m \Pi_{W_j} \ket{\psi}}^2 = \sum_{i=1}^{d-1} \sum_{j=1}^m \norm{c_j}^2 = 1 = \norm{\ket{\psi}}^2.
+ \end{align}
+ In the end, we can conclude that $\supp{\rho_A} = \cup_{i=1}^{d-1} V_i$ and there exist local isometries $\Phi_A$ and $\Phi_B$
+ such that 
+ \begin{align}
+ 	\Phi_A\x\Phi_B  \ket{\psi} =  (\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{ii}) \x \ket{junk}.
  \end{align}
@@
 %========================================
-\section{Extending $\G{d}$ for general prime numbers }
+\section{Extending $\G$ for general prime numbers }
 \label{sec:extend}
@@
 
-Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_{y in [2]}\}$ achieves that 
+Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_{y \in [2]}\}$ achieves that 
 $\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$.
@@
 %%=====================================
-%\section{Construction of $\Gamma(\LS)$}
-%\label{sec:construct}
+\section{Equations to embed $uxu^{-1} = x^2$}
+\label{sec:power2}
 %%=====================================
+\input{power2_equations}
+
+%%=====================================
+\section{Equations to embed $uxu^{-1} = x^3$}
+\label{sec:power3}
+%%=====================================
+\input{power3_equations}
+
+%%=====================================
+\section{Equations to embed $uxu^{-1} = x^5$}
+\label{sec:power5}
+%%=====================================
+\input{power5_equations}
 

### 2019-01-27 Draft/power2_equations.tex
Honghao: completed self-testing proof, rescaled weighted CHSH test, removed single value test and added equations for the linear system game

We have order-$2$ generators $\{x_i, w_i, y_i, j_i\}_{i=1}^{7} \cup \{f\} \cup \{g_{I_i}\}_{i=1}^5$,
where each $I_i$ represent a tuple of the form $(i,j,k)$ and it means that $x_ix_jx_i = x_k$.
We have 
\begin{align}
	I_1 = (1,2,5), 
	&&I_2 = (3,5,7), 
	&&I_3 = (4,1,7), 
	&&I_4 = (4,2,6), 
	&&I_5 = (3,2,6)
\end{align} 
and we denote $C = \{I_i\}_{i=1}^5$.
The linear relations involving the generators listed above are
\begin{align}
	\label{eq:xyz} &x_i y_i z_i = e  &&\text{for} \quad i =1\dots 7 \\
	\label{eq:xfw} &x_i f w_i = e   &&\text{for} \quad i =1\dots 7 \\
	&g_{I_1} y_2z_5 =e \\
	&g_{I_2} y_5z_7 =e \\
	&g_{I_3} y_1z_7 =e \\
	&g_{I_4} y_2z_6 =e \\
	&g_{I_5} y_2z_6 =e 
\end{align}

For $j =1 \dots 7$ we introduce a set of order-$2$ generators 
$\{ y_{F_j,k}\}_{k=1}^6$ and
a group of linear relations of the form
\begin{align}
	f y_{F_j,1} y _{F_j,2} = e, && f y_{F_j,5} y_{F_j,6} = e \\
	y_j y_{F_j,2} y _{F_j,3} = e, && z_j y_{F_j,6} y_{F_j,7} = e \\
	y_{F_j,1} y_{F_j,4} y _{F_j,7} = e, && y_{F_j,3} y_{F_j,4} y_{F_j,5} = e.
\end{align}
We refer to each group of linear relations of the from above as $(F_j)$.

In the end, for each $K \in C$, 
we introduce a set of order-$2$ generators $\{y_{K,k}\}_{k=1}^6$ and
linear relations.
Suppose $K = (k_1,k_2,k_3)$, then the group of linear relations are
\begin{align}
	w_{k_1} y_{K,1} y _{K,2} = e, && w_{k_1} y_{K,5} y_{K,6} = e \\
	y_{k_2} y_{K,2} y _{K,3} = e, && z_{k_3} y_{K,6} y_{K,7} = e \\
	y_{K,1} y_{K,4} y _{K,7} = e, && y_{K,3} y_{K,4} y_{K,5} = e,
\end{align}
We refer to each group of linear relations as $(K)$.
In summary, we have $118$ binary generators, which are
\begin{align}
\{x_i, w_i, y_i, j_i\}_{i=1}^{7} \cup \{f\} \cup \{g_{I_i}\}_{i=1}^5\cup\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^7
\cup \{\{y_{K,k}\}_{k=1}^6\}_{K \in C}.
\end{align}
In total, there are $91$ linear relations.
Converting a linear relation to a linear equation is trivial, so we omit it here.

From the group of linear relations $(F_j)$, we can deduce that for $j = 1 \dots 7$
\begin{align}
	f y_j f =& (y_{F_j,1} y _{F_j,2})(y_{F_j,2} y _{F_j,3})(y_{F_j,5} y_{F_j,6}) \\
	=&y_{F_j,1} (y_{F_j,3} y_{F_j,5}) y_{F_j,6} \\
	=& (y_{F_j,1} y_{F_j,4}) y_{F_j,6} \\
	=& y_{F_j,7} y_{F_j,6}\\
	=&z_j.
\end{align}
The immediate implication of the group of linear relations $(K)$ is that 
\begin{align}
	w_{k_1} y_{k_2} w_{k_1} =& (y_{K,1} y _{K,2})(y_{K,2} y _{K,3})(y_{K,5} y_{K,6}) \\
	=&y_{K,1} (y_{K,3} y_{K,5}) y_{K,6} \\
	=& (y_{K,1} y_{K,4}) y_{K,6} \\
	=& y_{K,7} y_{K,6}\\
	=&z_{k_3}.
\end{align}
From the conjugacy relation above, we can first deduce that 
\begin{align}
	w_{k_1}z_{k_2}w_{k_1} = w_{k_1}(f y_{k_2} f) w_{k_1} = f(w_{k_1}y_{k_2}w_{k_1}) f = fz_{k_3}f = y_{k_3}
\end{align}
where we use the fact that $(fw_{k_1})^2 = x_{k_1}^2 = e$ from \cref{eq:xfw}.
Then we can reason the relation between $x_{k_1}$, $x_{k_2}$ and $x_{k_3}$ as
follows
\begin{align}
	x_{k_1}x_{k_2}x_{k_1} = fw_{k_1}y_{k_2}z_{k_2}fw_{k_1} = (fw_{k_1}y_{k_2}w_{k_1}f)(fw_{k_1}z_{k_2}w_{k_1}f)
	=(fz_{k_3}f)(fy_{k_3}f) = y_{k_3}z_{k_3} = x_{k_3},
\end{align}
where we repeated use \cref{eq:xyz} and \cref{eq:xfw}.
In the end, we show why $I_1$,$I_2$,$I_3$,$I_4$ and $I_5$ imply that 
\begin{align}
	x_3 x_4 x_1x_2 x_4 x_3 =& x_3 (x_4 x_1x_4) (x_4x_2 x_4) x_3 \\
	=& (x_3 x_7 x_3) (x_3 x_6 x_3)\\
	=& x_5 x_2\\
	=& x_1x_2x_1 x_2
\end{align}
where we used the fact that $x_i$'s are of order-$2$.
If we treat $x_3x_4$ as $u$ and $x_1x_2$ as $x$, then we have derived that $uxu^{-1} = x^2$.

### 2019-01-27 Draft/power3_equations.tex
Honghao: completed self-testing proof, rescaled weighted CHSH test, removed single value test and added equations for the linear system game

We have order-$2$ generators $\{x_i, w_i, y_i, j_i\}_{i=1}^{8} \cup \{f\} \cup \{g_{I_i}\}_{i=1}^6$,
where each $I_i$ represent a tuple of the form $(i,j,k)$ and it means that $x_ix_jx_i = x_k$.
We have 
\begin{align*}
	&I_1 = (2,1,5), 
	&&I_2 = (1,3,6), 
	&&I_3 = (4,2,7), \\
	&I_4 = (3,2,7), 
	&&I_5 = (4,1,8),
	&&I_6 = (3,6,8)
\end{align*}
and we collect them in a set $C = \{ I_i \}_{i=1}^6$. 
The linear relations involving the generators listed above are
\begin{align}
	\label{eq:xyz} &x_i y_i z_i = e  &&\text{for} \quad i =1\dots 8 \\
	\label{eq:xfw} &x_i f w_i = e   &&\text{for} \quad i =1\dots 8 \\
	&g_{I_1} y_1z_5 =e \\
	&g_{I_2} y_3z_6 =e \\
	&g_{I_3} y_2z_7 =e \\
	&g_{I_4} y_2z_7 =e \\
	&g_{I_5} y_1z_8 =e \\
	&g_{I_6} y_6z_8 = e
\end{align}

To introduce the following linear relations, we introduce another set of 
generators $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^8$.
For $j =1 \dots 8$ we have a group of linear relations of the form
\begin{align}
	f y_{F_j,1} y _{F_j,2} = e, && f y_{F_j,5} y_{F_j,6} = e \\
	y_j y_{F_j,2} y _{F_j,3} = e, && z_j y_{F_j,6} y_{F_j,7} = e \\
	y_{F_j,1} y_{F_j,4} y _{F_j,7} = e, && y_{F_j,3} y_{F_j,4} y_{F_j,5} = e,
\end{align}
We refer to each group of linear relations of the from above as $(F_j)$.

The last set of linear relations comes from each $K \in C$, 
so we introduce another set of generators $\{\{y_{K,k}\}_{k=1}^6\}_{K \in C}$.
We have a group of linear relations for each $K \in C$.
Suppose $K = (k_1,k_2,k_3)$, then the group of linear relations are
\begin{align}
	w_{k_1} y_{K,1} y _{K,2} = e, && w_{k_1} y_{K,5} y_{K,6} = e \\
	y_{k_2} y_{K,2} y _{K,3} = e, && z_{k_3} y_{K,6} y_{K,7} = e \\
	y_{K,1} y_{K,4} y _{K,7} = e, && y_{K,3} y_{K,4} y_{K,5} = e,
\end{align}
We refer to each group of linear relations as $(K)$.
In summary, we have $123$ binary generators, which are
\begin{align}
\{x_i, w_i, y_i, j_i\}_{i=1}^{8} \cup \{f\} \cup \{g_{I_i}\}_{i=1}^6\cup\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^8
\cup \{\{y_{K,k}\}_{k=1}^6\}_{K \in C}.
\end{align}
There are $106$ linear relations.
Converting a linear relation to a linear equation is trivial, so we omit it here.

The derivation of $fy_jf=z_j$ from the group of linear relations $(F_j)$for $j = 1 \dots 8$
is the same as the previous case, so we omit it here.
We also omit the derivation of $x_{k_1} x_{k_2} x_{k_1} = x_{k_3}$, 
from the group of linear relations $(K)$,
for each $K \in C$.
In the end, we show the implication of the conjugacy relations in $C$ as follows 
\begin{align*}
	x_3 x_4 x_1x_2 x_4 x_3 =& x_3 (x_4 x_1x_4) (x_4x_2 x_4) x_3 \\
	=& (x_3 x_8 x_3) (x_3 x_7 x_3)\\
	=& x_6 x_2\\
	=& x_1x_5x_1 x_2\\
	=&x_1x_2x_1x_2x_1x_2
\end{align*}
where we used the fact that $x_i$'s are of order-$2$.
If we treat $x_3x_4$ as $u$ and $x_1x_2$ as $x$, then we have derived that $uxu^{-1} = x^3$.

### 2019-01-27 Draft/power5_equations.tex
Honghao: completed self-testing proof, rescaled weighted CHSH test, removed single value test and added equations for the linear system game

--- 2019-01-27 Draft/power3_equations.tex
@@
-We have order-$2$ generators $\{x_i, w_i, y_i, j_i\}_{i=1}^{8} \cup \{f\} \cup \{g_{I_i}\}_{i=1}^6$,
+We have order-$2$ generators $\{x_i, w_i, y_i, j_i\}_{i=1}^{10} \cup \{f\} \cup \{g_{I_i}\}_{i=1}^8$,
 where each $I_i$ represent a tuple of the form $(i,j,k)$ and it means that $x_ix_jx_i = x_k$.
@@
 	&&I_2 = (1,3,6), 
-	&&I_3 = (4,2,7), \\
-	&I_4 = (3,2,7), 
-	&&I_5 = (4,1,8),
-	&&I_6 = (3,6,8)
+	&&I_3 = (2,6,7), 
+	&&I_4 = (1,7,8), \\
+	&I_5 = (4,1,9),
+	&&I_6 = (3,8,9),
+	&&I_7 = (4,2,10)
+	&&I_8 = (3,2,10)
 \end{align*}
-and we collect them in a set $C = \{ I_i \}_{i=1}^6$. 
+and we collect them in a set $C = \{ I_i \}_{i=1}^8$. 
 The linear relations involving the generators listed above are
 \begin{align}
-	\label{eq:xyz} &x_i y_i z_i = e  &&\text{for} \quad i =1\dots 8 \\
-	\label{eq:xfw} &x_i f w_i = e   &&\text{for} \quad i =1\dots 8 \\
+	\label{eq:xyz} &x_i y_i z_i = e  &&\text{for} \quad i =1\dots 10 \\
+	\label{eq:xfw} &x_i f w_i = e   &&\text{for} \quad i =1\dots 10 \\
 	&g_{I_1} y_1z_5 =e \\
 	&g_{I_2} y_3z_6 =e \\
-	&g_{I_3} y_2z_7 =e \\
-	&g_{I_4} y_2z_7 =e \\
-	&g_{I_5} y_1z_8 =e \\
-	&g_{I_6} y_6z_8 = e
+	&g_{I_3} y_6z_7 =e \\
+	&g_{I_4} y_7z_8 =e \\
+	&g_{I_5} y_1z_9 =e \\
+	&g_{I_6} y_8z_9 = e\\
+	&g_{I_7} y_2z_{10} =e \\
+	&g_{I_8} y_2z_{10} = e
 \end{align}
@@
 To introduce the following linear relations, we introduce another set of 
-generators $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^8$.
-For $j =1 \dots 8$ we have a group of linear relations of the form
+generators $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{10}$.
+For $j =1 \dots 10$ we have a group of linear relations of the form
 \begin{align}
@@
 We refer to each group of linear relations as $(K)$.
-In summary, we have $123$ binary generators, which are
+In summary, we have $157$ binary generators, which are
 \begin{align}
-\{x_i, w_i, y_i, j_i\}_{i=1}^{8} \cup \{f\} \cup \{g_{I_i}\}_{i=1}^6\cup\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^8
+\{x_i, w_i, y_i, j_i\}_{i=1}^{10} \cup \{f\} \cup \{g_{I_i}\}_{i=1}^8\cup\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{10}
 \cup \{\{y_{K,k}\}_{k=1}^6\}_{K \in C}.
 \end{align}
-There are $106$ linear relations.
+There are $136$ linear relations.
 Converting a linear relation to a linear equation is trivial, so we omit it here.
 
-The derivation of $fy_jf=z_j$ from the group of linear relations $(F_j)$for $j = 1 \dots 8$
+The derivation of $fy_jf=z_j$ from the group of linear relations $(F_j)$for $j = 1 \dots 10$
 is the same as the previous case, so we omit it here.
@@
 	x_3 x_4 x_1x_2 x_4 x_3 =& x_3 (x_4 x_1x_4) (x_4x_2 x_4) x_3 \\
-	=& (x_3 x_8 x_3) (x_3 x_7 x_3)\\
-	=& x_6 x_2\\
-	=& x_1x_5x_1 x_2\\
-	=&x_1x_2x_1x_2x_1x_2
+	=& (x_3 x_9 x_3) (x_3 x_{10} x_3)\\
+	=& x_8 x_2\\
+	=& (x_1x_7x_1) x_2\\
+	=&x_1(x_2 x_6 x_2)x_1x_2\\
+	=& x_1x_2(x_1x_5x_1)x_2x_1x_2\\
+	=&x_1x_2x_1(x_2x_1x_2)x_1x_2x_1x_2
 \end{align*}
 where we used the fact that $x_i$'s are of order-$2$.
-If we treat $x_3x_4$ as $u$ and $x_1x_2$ as $x$, then we have derived that $uxu^{-1} = x^3$.
+If we treat $x_3x_4$ as $u$ and $x_1x_2$ as $x$, then we have derived that $uxu^{-1} = x^5$.

### 2019-01-29 Draft/draft.tex
Honghao: added definitions and strengthened proposition 12

@@
 %We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.
-The EPR pair of local dimension $d$ for $d \geq 2$ is the maximally entangled state and is denoted by
-\begin{align}
-\ket{\EPR{d}} = \frac{1}{\sqrt{d}} \sum_{i = 0}^{d-1} \ket{ii}.
-\end{align}
-The superscript $(d)$ stresses the local dimension and we follow this convention through this paper.
-
-We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators 
-which have operators of the similar form
+
+We use some basic number theory concepts in our work. A primitive root of a prime number
+$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
+$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
+$\Z_d^\times = \{1,2\dots d-1\}$.
+The EPR pair of local dimension $d-1$ for some prime $d$, which has primitive root $2$, 
+is denoted by
+\begin{align}
+\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{i = 0}^{d-2} \ket{ii}.
+\end{align}
+The superscript $(d-1)$ stresses the local dimension and we follow this convention through this paper.
+
+We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
 \begin{align}
@@
 \end{align}
-where $\omega_d = e^{i2\pi/d}$ is the primitive $d$th root of unity.
-Through out this paper, any operation on the label of the eigenvector $k$ is taken modulo $d$,
+where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity.
+Through out this paper, any operation on the label of the eigenvector $\ket{i}$ is taken modulo $d$,
 unless otherwise specified, for example, the $i/2$ above.
@@
 The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
-The weighted CHSH inequality is given below 
+In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 0,1$ 
+on Hilbert space $\calH_A$ and $\calH_B$ respectively.
+A binary observable is a Hermitian matrix whose eigenvalues are either $+1$ or $-1$.
+The weighted CHSH inequality is given by 
 \begin{align}
@@
 \end{align}
-where $A_x,B_y$ for $x,y = 0,1$ are Binary observables on Hilbert space $\calH_A$ and $\calH_B$ respectively.
+where $\ip{A_xB_y}$ is the expectation value of of the observables.
 If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
@@
 \end{definition}
-We take an approach introduced in Ref.~\cite{bamps2015} and prove the following robust self-testing result.
-\begin{theorem}
-\label{thm:selftest}
-	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the violation
-	at least $2\sqrt{1+\alpha^2} - \epsilon$
-	for some $\epsilon$, then
-	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
-	\begin{align}
-		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{aux} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O(\sqrt{\epsilon})
-	\end{align}
-	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and $A_x, B_y$ are 
-	defined in \cref{def:ideal}.
-\end{theorem}
-We defer the proof of \cref{thm:selftest} till Appendix~\ref{sec:selftest}.
-After proving the robust self-testing result, we take one step further and observe an interesting property of the 
-observable $\tilde{B}_0\tilde{B}_1$.
-\begin{proposition}
-\label{prop:2d-subspace}
-	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
-	violation of  $\I_{\cot(-\pi/2d)}$, then there exists a $2$-dimensional Hilbert space which is spanned by eigenvectors of 
-	$\tilde{B}_0\tilde{B}_1$ of eigenvalue $\omega_d$ and $\omega_d^{-1}$.
-\end{proposition}
-\begin{proof}[Proof of \cref{prop:2d-subspace}]
-	By \cref{thm:selftest}, the condition that the strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
-	maximal value of $\I_{\cot(-\pi/2d)} $ implies that there exist states $\ket{u_0}, \ket{u_1} \in \supp(\Tr_A(\ketbra{\tpsi}{\tpsi}))$ such that 
-	\begin{align*}
-	(\tilde{B}_0 + \tilde{B}_1) \ket{u_0} = 2\cos(-\pi/2d) \ket{u_0} 
-	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_1} = -2\cos(-\pi/2d) \ket{u_1}\\
-	(\tilde{B}_0 - \tilde{B}_1) \ket{u_0} = 2\sin(-\pi/2d) \ket{u_1} 
-	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_1} = 2\sin(-\pi/2d) \ket{u_0}.
-	\end{align*}
-	It is straightforward to calculate that 
-	\begin{align*}
-		\tilde{B}_0\tilde{B}_1 \ket{u_0} = \cos(\pi/d) \ket{u_0} -\sin(\pi/d) \ket{u_1},&&
-		\tilde{B}_0\tilde{B}_1\ket{u_1} = \sin(\pi/d)\ket{u_0} + \cos(\pi/d) \ket{u_1},
-	\end{align*}
-	so we can conclude that 
-	\begin{align*}
-		&\tilde{B}_0\tilde{B}_1(\ket{u_0} + i\ket{u_1}) = e^{i \frac{\pi}{d}} (\ket{u_0} + i\ket{u_1}), &&
-		&\tilde{B}_0\tilde{B}_1(\ket{u_0} - i\ket{u_1}) = e^{-i \frac{\pi}{d}} (\ket{u_0} - i\ket{u_1}).
-	\end{align*}
-	The actual eigenbasis we use is 
-	\begin{align}
-		\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{u_0} + i\ket{u_1}), &&
-		\ket{x_{d-1}} = \frac{-e^{i\pi/2d}}{\sqrt{2}}(\ket{u_0} - i\ket{u_1})
-	\end{align}
-	so that 
-	\begin{align}
-		&B_0 = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
-		&B_1 =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1},
-	\end{align}
-	which is important for the whole embedding argument to work in \cref{sec:comp}.
-\end{proof}
+An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
+measurements, which is the phenomenon of self-test. We give formal statement of this self-test result in \cref{sec:chsh}.
 
@@
 where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
+Note that we may use the term behaviour and correlation interchangeably.
 The \emph{value} of a strategy is given by
@@
 
-The main contribution of our work is the construction of a nonlocal game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
-such that its optimal correlation can self-test $\ket{\EPR{d}}$ for arbitrary $d \in D$. 
-The nonlocal game is a linear system game with modifications and strict enforcements. 
-We introduce the definition of self-testing first and then the definition of linear system game, 
+The main contribution of our work is the construction of a correlation, which is the optimal correlation of a game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
+such that this correlation can self-test $\ket{\EPR{d-1}}$ for arbitrary $d \in D$. 
+The nonlocal game $\G$ is a linear system game with strict enforcements. 
+We introduce the definition of self-testing first, the definition of linear system game, 
+and its operator solution, 
 following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
 \begin{definition}[Self-testing]
-	We say that a nonlocal game self-tests a quantum state $\ket{\Psi}$ if 
-	any quantum strategy $S$ that achieves the optimal quantum value uses a shared state equivalent up to local isometry to $\ket{\Psi}$.
+	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
+	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
+	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
+	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
+	such that 	
+	\begin{align*}
+		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
+	\end{align*}
 \end{definition}
 \begin{definition}[Linear system game]
- Let $Hx = b$ be an $m \times n$ linear system over $\Z_2$. The associated linear system game involves two
- players Alice and Bob, where Alice is given an equation number $1 \leq x \leq m$ and replies with $a \in \Z_2^{\times n}$,
- and Bob is given a variable number $y$ and replies with an assignment $b \in \Z_2$. The winning condition is 
- \begin{align*}
- 	a(y) &= b && \text{(Consistency)} \\
-	\sum_{y = 1}^n H_{xy} a(y) &\equiv b(x) \pmod 2. &&\text{(Constraint satisfaction)}
- \end{align*}
+ Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
+ where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
+ $c$ is a length-$n$ vector with entries in $\Z_2$ too. 
+ The associated linear system game involves two
+ players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
+ and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
+ that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
+ Formally, the winning condition is 
+ \begin{align*}
+ 	a(j) &= b && \text{(Consistency)} \\
+	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
+ \end{align*}
+ for all $(i,j) \in \calX \times \calY$.
 \end{definition}
@@
 $V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
+We focus on quantum strategies for the linear system game presented in terms of binary observables.
+\begin{definition}[Quantum strategy of a linear system game]
+\label{def:q_strat}
+A quantum strategy for the linear system game $(Hx = c)$ consists of 
+\begin{enumerate}
+	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
+	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
+	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
+	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
+	on $\calH_A$ such that 
+	\begin{enumerate}
+		\item $A_{ij}^2 = \1$ for every $i,j$,
+		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
+		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
+	\end{enumerate} 
+	and
+	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
+\end{enumerate}
+\end{definition}
+Note that any quantum strategy presented in terms of binary observables can be 
+converted to a quantum strategy presented in terms of projective measurement, and
+vice versa.
+
+It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
+satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
+operator solution in the following sense.
+\begin{definition}[Operator solution of a linear system]
+\label{def:op_sol}
+	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
+	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that 
+	\begin{enumerate}
+		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
+		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
+		\item for all $1 \leq i \leq m$,
+		\begin{align*}
+			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
+		\end{align*}
+	\end{enumerate}
+	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
+	solution in which the Hilbert space is finite-dimensional.
+\end{definition}
+Perfect quantum strategies can be extracted from operator solutions and vice versa.
+
+Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
+over $\Z_2$, which is called the solution group.
+\begin{definition}[Solution group of a linear system game]
+	\label{def:presentation}
+	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
+	is the group
+	\begin{align*}
+		\Gamma(H,c) := \ip{
+		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
+				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
+				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
+				} .
+	\end{align*}
+\end{definition}
+For concepts about group presentation, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
+Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
+a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.
 
@@
 where $d$ is prime and has primitive root $2$. 
-If $d$ has primitive root $2$,
-then $2$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$.
-When $d$ is prime, $\Z_d^\times = \{1,2\dots d-1\}$.
 The correlation we constructed is the optimal correlation for a game $\G$, which is the combination of two tests.
@@
 
-Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$, which
-is included in the group $K$, which has presentation
-\begin{align*}
-	K = \langle a,b,c,x,y: a^2=b^2=c^2 = e, c=ab, yay^{-1} = a, yby^{-1}= c, xyx^{-1} = y^2\rangle.
-\end{align*}
+Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
 The main component of $\G$ is a linear system game $\LS$, whose solution group is the embedding of the 
@@
 \end{align}
-
+In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
+relation $uxu^{-1} = x^2$.
 \begin{proposition}
 	\label{prop:embed}
-	The group $\Pg$ can be embedded into a linear system game, $\LS$, over $\Z_2$,
+	The group $\Pg$ can be embedded into a linear system game $\LS$ over $\Z_2$,
 	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
 \end{proposition}
-The process of embedding $\Pg$
-into the solution group of $\LS$ follows the recipe given in the proofs of
+The process of embedding $\Pg$ into the solution group of $\LS$ follows the recipe given in the proofs of
 Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
-The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}..
-\begin{proof}
-The first step is to embed $\Pg$ into a linear-plus-conjugacy group $\Pg''$ where
-all the generators are of order $2$, following the instructions given in the proof of  
-Proposition~$4.8$ of the Ref.~\cite{slofstra2017}.
-We first introduce $x_1,x_2$ such that $x_1^2=x_2^2=e$, $x=x_1x_2$ and $u x_2 u^{-1}=x_2$.
-We also introduce $x' = ux_1u^{-1}$, 
-then we embed $\Pg$ in $\Pg'$ as
-\begin{align}
-	\Pg' = \langle x_1,x_2,x',u: x_1^2=x_2^2=x'^2=e,
-	x_1x_2x_1=x', ux_1u^{-1}=x', ux_2u^{-1} =x_2 \rangle.
-\end{align}
-Next, we introduce $u_1,u_2$ such that $u_1^2=u_2^2=e$ and $u=u_1u_2$, 
-and also $u_3.u_4$ of order $2$ such that the conjugacy relations involving them are 
-\begin{align*}
-u_2x_2u_2 = u_3, && u_1u_3u_1 = x_2\\
-u_2x_1u_2 = u_4, && u_1u_4u_1 = x',
-\end{align*}
-then
-$\Pg'$ is further embedded in $\Pg''$ as
-\begin{equation}
-\begin{aligned}
-	\Pg'' =  \langle &x_1,x_2,x',u_1,u_2,u_3,u_4: \text{all elements are of order $2$},\notag\\
-	 &u_2x_2u_2 = u_3, u_1u_3u_1 = x_2,
-u_2x_1u_2 = u_4, u_1u_4u_1 = x',x_1x_2x_1=x' \rangle.
-\end{aligned}
-\end{equation}	
-To represent the conjugacy relations by a tuple, we relabel the some of the generators as
-\begin{align*}
-	u_1 = x_3, && u_2 = x_4, && x' = x_5, && u_3 = x_6, && u_4 = x_7,
-\end{align*}
-so that a simpler form of the group $\Pg''$ is 
-\begin{equation}
-\begin{aligned}
-	\Pg'' = \langle \{x_i\}_{i=1}^7 : x_i^2 = e \; \forall i, 
-	x_1x_2x_1=x_5, x_4x_2x_4 = x_6,
-	 x_4x_1x_4=x_7, x_3x_2x_3 = x_6, x_3x_5x_3=x_7\rangle
-\end{aligned}
-\end{equation}
-We collect the subscript of $x_i$'s in the conjugacy relations and define
-\begin{align}
-	C= \{ (1,2,5), (3,5,7), (4,1,7), (4,2,6), (3,2,6)\},
-\end{align}
-so that $(i,j,k) \in C$ if and only if $x_ix_jx_i = x_k$ in $\Pg''$.
-
-Next we embed $\Pg''$ into $\Pg_{NLC}$ to make $x_j$ and $x_k$ commute if $(i,j,k) \in C$,
-where $\Pg_{NLS}$ is a nice linear-plus-conjugacy group.
-This steps are given in the proof of Lemma~$4.4$ of the Ref.~\cite{slofstra2017}.
-The group $\Pg_{NLS}$ is defined as 
-\begin{equation}
-\begin{split}
-\Pg_{NLS} = \langle \{x_i, w_i, y_i, j_i\}_{i=1}^{7},f : &f^2 = x_i^2 =w_i^2=y_i^2=j_i^2= e, \\
-	&x_i = y_iz_i = fw_i,\; fy_if =z_i \quad\text{where } 1 \leq i \leq 7 \\
-	&y_j z_k = z_ky_j,\; w_iy_jw_i = z_k \quad\text{for all } (i,j,k)\in C \rangle.
-\end{split}
-\end{equation}
-To summarize the linear relations, we first introduce generator $g_{jk} = y_j z_k$ for all $(i,j,k) \in C$
-such that $g_{jk}^2 = e$. Now the group has $34$ generator.
-The $19$ linear relations are
-\begin{align*}
-	&x_i y_i z_i = e \quad \text{for} \quad i =1\dots 7 \\
-	&x_i f w_i = e  \quad \text{for} \quad i =1\dots 7\\
-	&g_{jk}y_jz_k =e \quad \text{for all}\quad (i,j,k) \in C.
-\end{align*}
-The $12$ conjugacy relations are 
-\begin{align*}
-	&fy_if = z_i\quad \text{for} \quad i =1\dots 7\\
-	&w_iy_j w_i = z_k \quad\text{for all } (i,j,k)\in C.
-\end{align*}
-We can standardise the generators by relabeling the generators all as $x_i$.
-There are $29$ generators in $\Pg_{NLS}$.
-
-The last step is given in the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}, which
-embeds all the conjugacy relations in linear relations.
-This is done by introduce $7$ new variables and $6$ linear relations for each
-conjugacy relations. For example, If $I = (i,j,k)$ is a conjugacy relation, then we introduce
-generators $y_{Ii}$ for $i=1 \dots 6$. Note that $y_{Ii}$ shall not be confused with the $y_i$'s
-in the previous step. The new linear relations are
-\begin{align*}
-	x_i y_{I1} y_{I2} = e && x_j y_{I2} y_{I3} = e && y_{I3}y_{I4}y_{I5} = e\\
-	x_i y_{I5} y_{I6} = e && x_k y_{I6} y_{I7} = e && y_{I1}y_{I4}y_{I7} = e.
-\end{align*}
-In the end, the solution group of $\LS$, $\Pg_{\LS}$,  
-has $118$ variables and $91$ equations.
-\end{proof}
+The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
+We give details of this embedding process in \cref{sec:power2}.
+
 In the later parts of the paper, we use $n = 118$ and $m = 91$ to refer to the size of $\LS$.
@@
 even if the generators $u$ and $x$ can have arbitrary order. 
-
 We denote the special operators in the operator solution of $\LS$ that correpsond to generators 
-$u = x_3x_4$ and $x = x_1x_2$ by $U$ and $S$.
-The special property of $U$ and $S$ is summarized in the following lemma. 
+$u = x_3x_4$ and $x = x_1x_2$ by $U$ and $X$.
+The key relation that we will use in the later section is that 
+\begin{align}
+	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^2\ket{\psi}, 
+\end{align}
+where $\ket{\psi}$ is the state shared between Alice and Bob and $A_i$ is 
+Alice's observable for $1 \leq i \leq n$.
+
+The special property of $U$ and $X$ is summarized in the following lemma. 
 \begin{lemma}
@@
 %======================================
-\section{The extended weighted CHSH game}
+\section{The extended weighted CHSH test}
 \label{sec:chsh}
 %======================================
-The extended weighted CHSH game is added to make sure that the operator $X$ extracted from 
+Before introducing the extended weighted CHSH test, we fill in some background about the weighted CHSH inequality,
+namely, that its maximal violation can self-test $2$-dimensional EPR pair and rotated Pauli operators.
+The robust self-testing result is summarized in the following theorem.
+\begin{theorem}
+\label{thm:selftest}
+	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the violation
+	at least $2\sqrt{1+\alpha^2} - \epsilon$
+	for some $\epsilon$, then
+	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
+	\begin{align}
+		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{aux} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O(\sqrt{\epsilon})
+	\end{align}
+	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and $A_x, B_y$ are 
+	defined in \cref{def:ideal}. \hl{Error term depend on $\alpha$.}
+\end{theorem}
+Our approach is very similar to the one used in Ref.~\cite{bamps2015} so we 
+defer the proof of \cref{thm:selftest} till \cref{sec:selftest}.
+After proving the robust self-testing result, we take one step further and observe an interesting property of the 
+product of Bob's observables.
+\begin{proposition}
+\label{prop:2d-subspace}
+	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
+	violation of  $\I_{\cot(-\pi/2d)}$, then $\supp(\Tr_A(\ketbra{\psi}{\psi}))$ is spanned by $\omega_d$-eigenvectors 
+	and $\omega_d^{-1}$ -eigenvectors of $\tilde{B}_0\tilde{B}_1$.
+\end{proposition}
+\begin{proof}[Proof of \cref{prop:2d-subspace}]
+	By \cref{thm:selftest}, the condition that the strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
+	maximal value of $\I_{\cot(-\pi/2d)} $ implies that 
+	\begin{align}
+		\ket{\tpsi} = \sum_{i=1}^m \frac{c_i}{\sqrt{2}} (\ket{u_{i,0}}\ket{u_{i,0}}+\ket{u_{i,1}}\ket{u_{i,1}}),
+	\end{align}
+	where $c_i$'s are coefficients such that $\sum_{i=1}^m \norm{c_i}^2 = 1$.
+	The special property of the subspace $V_i = \spn( \ket{u_{i,0}}, \ket{u_{i,1}})$ is that 
+	\begin{align*}
+	(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,0}} = 2\cos(-\pi/2d) \ket{u_{i,0}} 
+	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,1}} = -2\cos(-\pi/2d) \ket{u_{i,1}}\\
+	(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,0}} = 2\sin(-\pi/2d) \ket{u_{i,1}} 
+	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,1}} = 2\sin(-\pi/2d) \ket{u_{i,0}}.
+	\end{align*}
+	It is straightforward to calculate that 
+	\begin{align*}
+		\tilde{B}_0\tilde{B}_1 \ket{u_{i,0}} = \cos(\pi/d) \ket{u_{i,0}} -\sin(\pi/d) \ket{u_{i,1}},&&
+		\tilde{B}_0\tilde{B}_1\ket{u_{i,1}} = \sin(\pi/d)\ket{u_{i,0}} + \cos(\pi/d) \ket{u_{i,1}},
+	\end{align*}
+	so we can conclude that 
+	\begin{align*}
+		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} + i\ket{u_{i,1}}) = e^{i \frac{\pi}{d}} (\ket{u_{i,0}} + i\ket{u_{i,1}}), &&
+		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} - i\ket{u_{i,1}}) = e^{-i \frac{\pi}{d}} (\ket{u_{i,0}} - i\ket{u_{i,1}}).
+	\end{align*}
+	Hence each $V_i$ is spanned by $\omega_d$-eigenvector and $\omega_d^{-1}$-eigenvector of $\tB_0\tB_1$.
+\end{proof}
+Suppose the subspace $V = \spn(\ket{u_0}, \ket{u_1})$, then
+the actual eigenbasis of $X = B_0B_1$ that we use is 
+\begin{align}
+	\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{u_0} + i\ket{u_1}), &&
+	\ket{x_{d-1}} = \frac{-e^{i\pi/2d}}{\sqrt{2}}(\ket{u_0} - i\ket{u_1}),
+\end{align}
+such that 
+\begin{align}
+	&B_0 = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
+	&B_1 =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1}.
+\end{align}
+The form of $B_1$ is important for the whole embedding argument to work in \cref{sec:main}.
+
+The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
 Alice and Bob's operator solution have eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
@@
 $U$ and $X$ has the eigen-structure required by \cref{lm:ux_independ}.
-We denote this game that enforces the eigenvalues of the observable $U$ by
-$\CHSH_U$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
-
-In this game, Alice and Bob each gets a question $x$,$y \in \{ 0, 1, \ast\}$ and 
+We denote this game that enforces the eigenvalues of the observable $X$ by
+$\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
+
+In this test, Alice and Bob each gets a question $x$,$y \in \{ 0, 1, \ast\}$ and 
 they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
-Our self-test result follows the optimal behaviour in this game,
+Our self-test result follows the optimal correlation of this test.
 Before presenting the optimal correlation, we give intuitions about how the players should behave.
@@
 %=====================================
-In this section, we introduce the combined game $\G{d-1}$ and then
+In this section, we introduce the combined game $\G$ and then
 prove that it can self-test the state $\ket{\EPR{d-1}}$.

### 2019-01-31 Draft/draft.tex
Honghao: new proof of Prop.12, constructed isometries for Thm. 15, and other editorial changes

@@
 \newcommand{\lB}{\overline{B}}
+\newcommand{\dr}[1]{d^{(#1)}}
 
@@
 In this report, we give an affirmative answer to this question by proving the following theorem.
-\begin{theorem}
+\begin{theorem}[Informal]
 \label{thm:inf}
@@
 given in the following theorem.
-\begin{theorem}
+\begin{theorem}[Informal]
 \label{thm:pr_2}
@@
 \end{theorem}
-Note that although the sizes of the question and answer
-sets do not depend on $d$, the optimal correlation does.
-This correlation can be easily converted to work for dimensions with primitive $3$ or $5$.
+The correlation that we use to prove \cref{thm:pr_2} is denoted by $C(\dr{2})$.
+We use the superscript $(2)$ to denote the primitive root of $d$.
+Note that although the size of $C(\dr{2})$ does not depend on $d$, the optimal correlation does.
+This correlation can be easily modified to self-test the maximally entangled state whose local dimension has 
+primitive $3$ or $5$.
 
@@
 The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
-In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 0,1$ 
+In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
 on Hilbert space $\calH_A$ and $\calH_B$ respectively.
@@
 	\label{eq:chsh_op}
-	\I_\alpha = \alpha\ip{A_0B_0}+\alpha\ip{A_0B_1} + \ip{A_1B_0} - \ip{A_1B_1}\leq 2\alpha,
+	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
 \end{align}
@@
 	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
-	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz$, $A_1 = \paulix$,
-	$B_0 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_1 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
+	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
+	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
 \end{definition}
@@
 present a correlation that can self-test $\ket{\EPR{d-1}}$, 
-where $d$ is prime and has primitive root $2$. 
-The correlation we constructed is the optimal correlation for a game $\G$, which is the combination of two tests.
+where $d$ is prime and has primitive root $2$,
+and this correlation is denoted by $C(\dr{2})$.
+The correlation we constructed is the optimal correlation for a game $\G(\dr{2})$, which is the combination of two tests.
 In this section, we introduce the linear system game which tests a relation that should be satisfied by 
@@
 Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
-The main component of $\G$ is a linear system game $\LS$, whose solution group is the embedding of the 
+The main component of $\G(\dr{2})$ is a linear system game $\LS$, whose solution group is the embedding of the 
 following group
@@
 even if the generators $u$ and $x$ can have arbitrary order. 
-We denote the special operators in the operator solution of $\LS$ that correpsond to generators 
-$u = x_3x_4$ and $x = x_1x_2$ by $U$ and $X$.
-The key relation that we will use in the later section is that 
+The product of the generators $x_1$ and $x_2$ from the solution group of $\LS$ plays the role 
+of the generator $x$ in $\Pg$ and the product of the generators $x_3$ and $x_4$ plays the role
+of the generator $u$ in $\Pg$. As shown in \cref{sec:power2}, $x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
+\begin{align}
+	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^2.
+\end{align}
+Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
+the key relation that 
 \begin{align}
@@
 \end{align}
-where $\ket{\psi}$ is the state shared between Alice and Bob and $A_i$ is 
-Alice's observable for $1 \leq i \leq n$.
-
+and similarly on Bob's side.
+If we denote the unitary corresponding to the generator $u$ of $\Pg$ by $U$ and the unitary
+corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
+$UXU\ct \ket{\psi} = X^2 \ket{\psi}$.
 The special property of $U$ and $X$ is summarized in the following lemma.
+
 \begin{lemma}
@@
 \label{thm:selftest}
-	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the violation
+	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the violation
 	at least $2\sqrt{1+\alpha^2} - \epsilon$
@@
 	\begin{align}
-		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{aux} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O(\sqrt{\epsilon})
-	\end{align}
-	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and $A_x, B_y$ are 
-	defined in \cref{def:ideal}. \hl{Error term depend on $\alpha$.}
+		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha+\frac{1}{\alpha}) \sqrt{\epsilon})
+	\end{align}
+	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $A_x, B_y$ are 
+	defined in \cref{def:ideal}.
 \end{theorem}
@@
 \label{prop:2d-subspace}
-	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
-	violation of  $\I_{\cot(-\pi/2d)}$, then $\supp(\Tr_A(\ketbra{\psi}{\psi}))$ is spanned by $\omega_d$-eigenvectors 
-	and $\omega_d^{-1}$ -eigenvectors of $\tilde{B}_0\tilde{B}_1$.
+	Let $\mu = \arctan(1/\alpha)$ for some $\alpha$.
+	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
+	violation of  $\I_{\alpha}$, then $\tilde{B}_0\tilde{B}_1$ has eigenvalues $e^{i2\mu}$ and $e^{-i2\mu}$.
 \end{proposition}
 \begin{proof}[Proof of \cref{prop:2d-subspace}]
-	By \cref{thm:selftest}, the condition that the strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
-	maximal value of $\I_{\cot(-\pi/2d)} $ implies that 
-	\begin{align}
-		\ket{\tpsi} = \sum_{i=1}^m \frac{c_i}{\sqrt{2}} (\ket{u_{i,0}}\ket{u_{i,0}}+\ket{u_{i,1}}\ket{u_{i,1}}),
-	\end{align}
-	where $c_i$'s are coefficients such that $\sum_{i=1}^m \norm{c_i}^2 = 1$.
-	The special property of the subspace $V_i = \spn( \ket{u_{i,0}}, \ket{u_{i,1}})$ is that 
-	\begin{align*}
-	(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,0}} = 2\cos(-\pi/2d) \ket{u_{i,0}} 
-	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,1}} = -2\cos(-\pi/2d) \ket{u_{i,1}}\\
-	(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,0}} = 2\sin(-\pi/2d) \ket{u_{i,1}} 
-	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,1}} = 2\sin(-\pi/2d) \ket{u_{i,0}}.
-	\end{align*}
-	It is straightforward to calculate that 
-	\begin{align*}
-		\tilde{B}_0\tilde{B}_1 \ket{u_{i,0}} = \cos(\pi/d) \ket{u_{i,0}} -\sin(\pi/d) \ket{u_{i,1}},&&
-		\tilde{B}_0\tilde{B}_1\ket{u_{i,1}} = \sin(\pi/d)\ket{u_{i,0}} + \cos(\pi/d) \ket{u_{i,1}},
-	\end{align*}
-	so we can conclude that 
-	\begin{align*}
-		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} + i\ket{u_{i,1}}) = e^{i \frac{\pi}{d}} (\ket{u_{i,0}} + i\ket{u_{i,1}}), &&
-		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} - i\ket{u_{i,1}}) = e^{-i \frac{\pi}{d}} (\ket{u_{i,0}} - i\ket{u_{i,1}}).
-	\end{align*}
-	Hence each $V_i$ is spanned by $\omega_d$-eigenvector and $\omega_d^{-1}$-eigenvector of $\tB_0\tB_1$.
+	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we know
+	$\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu)$ is a binary observable. \textcolor{red}{HF: Do we need to justify it?}
+	Expanding $\tilde{Z}_B^2$ we get
+	\begin{align*}
+		\1 = \tilde{Z}_B^2 = \frac{\tB_1^2 + \tB_1\tB_2 + \tB_2\tB_1 + \tB_2^2}{4\cos(\mu)^2}
+		=\frac{2\1 + \tB_1\tB_2 + \tB_2\tB_1}{4\cos^2(\mu)},
+	\end{align*}
+	so we can derive that 
+	\begin{align}
+	\label{eq:eig_v}
+		\tB_1\tB_2 + \tB_2\tB_1 = 2(2\cos^2(\mu)-1)\1 = 2 \cos(2\mu) \1.
+	\end{align}
+	Observe that $(\tB_1\tB_2)^\dagger = \tB_2\tB_1$ and 
+	$(\tB_2\tB_1)(\tB_1\tB_2) = \tB_2\1\tB_2 = \1$, then we can conclude that $\tB_1\tB_2$ is unitary.
+	Suppose the eigen-decomposition of $\tB_1\tB_2$ is
+	\begin{align}
+		\tB_1\tB_2 = \sum_{i=1}^m \lambda_i \ketbra{i}{i}
+	\end{align}
+	for some orthonormal set of eigenvectors $\{ \ket{i} \}_{i=1}^m$
+	and $\norm{\lambda_i} =1$ for $1 \leq i \leq m$.
+	Eq.~\ref{eq:eig_v} tells us that for each $1 \leq i \leq m$
+	\begin{align*}
+		\lambda_i + \lambda_i^{-1} = 2\Re(\lambda_i) = 2 \cos(2\mu),
+	\end{align*}
+	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.
+
+%	\begin{align}
+%		\ket{\tpsi} = \sum_{i=1}^m \frac{c_i}{\sqrt{2}} (\ket{u_{i,0}}\ket{u_{i,0}}+\ket{u_{i,1}}\ket{u_{i,1}}),
+%	\end{align}
+%	where $c_i$'s are coefficients such that $\sum_{i=1}^m \norm{c_i}^2 = 1$.
+%	The special property of the subspace $V_i = \spn( \ket{u_{i,0}}, \ket{u_{i,1}})$ is that 
+%	\begin{align*}
+%	(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,0}} = 2\cos(-\pi/2d) \ket{u_{i,0}} 
+%	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,1}} = -2\cos(-\pi/2d) \ket{u_{i,1}}\\
+%	(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,0}} = 2\sin(-\pi/2d) \ket{u_{i,1}} 
+%	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,1}} = 2\sin(-\pi/2d) \ket{u_{i,0}}.
+%	\end{align*}
+%	It is straightforward to calculate that 
+%	\begin{align*}
+%		\tilde{B}_0\tilde{B}_1 \ket{u_{i,0}} = \cos(\pi/d) \ket{u_{i,0}} -\sin(\pi/d) \ket{u_{i,1}},&&
+%		\tilde{B}_0\tilde{B}_1\ket{u_{i,1}} = \sin(\pi/d)\ket{u_{i,0}} + \cos(\pi/d) \ket{u_{i,1}},
+%	\end{align*}
+%	so we can conclude that 
+%	\begin{align*}
+%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} + i\ket{u_{i,1}}) = e^{i \frac{\pi}{d}} (\ket{u_{i,0}} + i\ket{u_{i,1}}), &&
+%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} - i\ket{u_{i,1}}) = e^{-i \frac{\pi}{d}} (\ket{u_{i,0}} - i\ket{u_{i,1}}).
+%	\end{align*}
+%	Hence each $V_i$ is spanned by $\omega_d$-eigenvector and $\omega_d^{-1}$-eigenvector of $\tB_0\tB_1$.
 \end{proof}
-Suppose the subspace $V = \spn(\ket{u_0}, \ket{u_1})$, then
-the actual eigenbasis of $X = B_0B_1$ that we use is 
-\begin{align}
-	\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{u_0} + i\ket{u_1}), &&
-	\ket{x_{d-1}} = \frac{-e^{i\pi/2d}}{\sqrt{2}}(\ket{u_0} - i\ket{u_1}),
-\end{align}
-such that 
-\begin{align}
-	&B_0 = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
-	&B_1 =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1}.
-\end{align}
-The form of $B_1$ is important for the whole embedding argument to work in \cref{sec:main}.
 
 The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
-Alice and Bob's operator solution have eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
+Alice and Bob's operator solution of $\LS$ has eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
 In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
@@
 
-In this test, Alice and Bob each gets a question $x$,$y \in \{ 0, 1, \ast\}$ and 
+In this test, Alice and Bob each gets a question $x$,$y \in \{ 1, 2, \ast\}$ and 
 they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
-Our self-test result follows the optimal correlation of this test.
+The correlation $C(\dr{2})$ is the optimal correlation of this test.
 Before presenting the optimal correlation, we give intuitions about how the players should behave.
@@
 	their answer should agree;
-	\item \textbf{Case 2a:} when $x,y \in \{0,1\}$ and if they answer with $a,b \in \{0,1\}$, then
-	their answers are scored according to $I_{\cot(-\pi/2d)}$;
-	\item \textbf{Case 2b:} when $x,y \in \{0,1\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
-	\item \textbf{Case 3:} when $x \in {0,1}, y = \ast$, if Bob answers $\diamond$, 
+	\item \textbf{Case 2a:} when $x,y \in \{1,2\}$ and if they answer with $a,b \in \{0,1\}$, then
+	their answers are scored according to $I_{\cot(-\pi/d)}$;
+	\item \textbf{Case 2b:} when $x,y \in \{1,2\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
+	\item \textbf{Case 3:} when $x \in {1,2}, y = \ast$, if Bob answers $\diamond$, 
 	Alice should answer with $\{0.1\}$ but not $\perp$,
@@
 define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
-maximize $\langle I_{\cot(-\pi/2d)} \rangle$.
+maximize $\langle I_{\cot(-\pi/d)} \rangle$.
 
@@
 \multicolumn{2}{|c|}{} &
-\multicolumn{3}{|c|}{$x=0$}&
-\multicolumn{3}{|c|}{$x=1$} \\
+\multicolumn{3}{|c|}{$x=1$}&
+\multicolumn{3}{|c|}{$x=2$} \\
 \cline{3-8}
@@
 \hline
-\multirow{2}{*}{$y = 0$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d-1}$ & $\frac{\sin^2(\pi/4d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
-& $\frac{1+\sin(\pi/2d)}{2(d-1)}$ & $\frac{1-\sin(\pi/2d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
+\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
+& $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/4d)}{d-1}$ & $\frac{\cos^2(\pi/4d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
-&  $\frac{1-\sin(\pi/2d)}{2(d-1)}$ & $\frac{1+\sin(\pi/2d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
+&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
+&  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
 \hline
-\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d-1}$ & $\frac{\sin^2(\pi/4d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
-$ \frac{1-\sin(\pi/2d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/2d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
+\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
+$ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/4d)}{d-1}$ & $\frac{\cos^2(\pi/4d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
-$ \frac{1+\sin(\pi/2d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/2d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
+&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
+$ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
 \hline
@@
 	&A_\ast^\diamond = \Pi_V, A_\ast^\perp = \Pi_V^\perp \\
-	&A_0^0 = \ketbra{u_1}{u_1}, A_0^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_0^\perp = \Pi_V^\perp\\
-	&A_1^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
-	A_0^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_0^\perp = \Pi_V^\perp.
+	&A_1^0 = \ketbra{u_1}{u_1}, A_1^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_1^\perp = \Pi_V^\perp\\
+	&A_2^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
+	A_2^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_2^\perp = \Pi_V^\perp.
 \end{align*}
@@
 	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
-	&B_0^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} + \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
-	\left( \cos(\frac{\pi}{4d})\bra{u_1} + \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
-	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} - \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
-	\left( \sin(\frac{\pi}{4d})\bra{u_1} - \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
-	&B_1^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} - \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
-	\left( \cos(\frac{\pi}{4d})\bra{u_1} - \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
-	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} + \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
-	\left( \sin(\frac{\pi}{4d})\bra{u_1} + \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right).
-\end{align*}
-About Bob's projectors for input $y \in [2]$, we are only interested in their actions when restricted 
+	&B_1^0|_V = \left( \cos(\frac{\pi}{2d})\ket{u_1} + \sin(\frac{\pi}{2d})\ket{u_{d-1}}\right)
+	\left( \cos(\frac{\pi}{2d})\bra{u_1} + \sin(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
+	&B_1^1|_V = \left( \sin(\frac{\pi}{2d})\ket{u_1} - \cos(\frac{\pi}{2d})\ket{u_{d-1}}\right)
+	\left( \sin(\frac{\pi}{2d})\bra{u_1} - \cos(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
+	&B_2^0|_V = \left( \cos(\frac{\pi}{2d})\ket{u_1} - \sin(\frac{\pi}{2d})\ket{u_{d-1}}\right)
+	\left( \cos(\frac{\pi}{2d})\bra{u_1} - \sin(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
+	&B_2^1|_V = \left( \sin(\frac{\pi}{2d})\ket{u_1} + \cos(\frac{\pi}{2d})\ket{u_{d-1}}\right)
+	\left( \sin(\frac{\pi}{2d})\bra{u_1} + \cos(\frac{\pi}{2d})\bra{u_{d-1}}\right).
+\end{align*}
+About Bob's projectors for input $y \in [2]+1$, we are only interested in their actions when restricted 
 to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.
@@
 	Suppose a quantum strategy $\left(\{\{\tA_x^a\}_a\}_x, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}\right)$
-	achieves the optimal correlation of $\CHSH$, 
+	achieves the optimal correlation of the weighted $\CHSH$ test, 
 	and let $\ket{\tpsi'} = \tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}/\norm{\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}}^2$,
-	then there exists unitaries $U_A$ and $U_B$ 
+	then there exists isometries $\Phi_A$ and $\Phi_B$ 
 	and a quantum state $\ket{junk}$
@@
 	\begin{align*}
-		&U_A\x U_B \left( \ket{\tpsi'}\right) = \ket{\EPR{2}}\x \ket{junk} \\
-		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 + \tB_1}{2\cos(\pi/2d)}\right)\ket{\tpsi'}\right]
+		&\Phi_A\x \Phi_B \left( \ket{\tpsi'}\right) = \ket{\EPR{2}}\x \ket{junk} \\
+		&\Phi_A\x \Phi_B \left[\left(\1 \x  \frac{\tB_1 + \tB_2}{2\cos(\pi/d)}\right)\ket{\tpsi'}\right]
 		=[(\1 \x \pauliz) \ket{\EPR{2}}] \x \ket{junk} \\
-		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 - \tB_1}{-2\sin(\pi/2d)}\right)\ket{\tpsi'} \right]
+		&\Phi_A\x \Phi_B \left[\left(\1 \x  \frac{\tB_1 - \tB_2}{-2\sin(\pi/d)}\right)\ket{\tpsi'} \right]
 		=[(\1 \x \paulix) \ket{\EPR{2}}] \x \ket{junk} 
 	\end{align*}
-	where $\tB_0 = \tB_0^0 - \tB_0^1$ and $\tB_1 = \tB_1^0 - \tB_1^1$.
+	where $\tB_1 = \tB_1^0 - \tB_1^1$ and $\tB_2 = \tB_2^0 - \tB_2^1$.
 \end{lemma}
@@
 
-From the marginal distribution $\pb{\diamond}{\ast} = \pa{0}{0}+\pa{1}{0} = 2/d-1$,
-we know $\| \tB_\ast^\diamond \ket{\tpsi} \| = \| (\tA_0^0+\tA_0^1) \ket{\tpsi}\| = \sqrt{2/d-1}$.
-Since $\pr{0\diamond}{0\ast} + \pr{1\diamond}{0\ast} = 2/d-1$, we find that 
-\begin{align*}
-	\frac{\bra{\tpsi}\tB_\ast^\diamond (\tA_0^0+\tA_0^1) \tB_\ast^\diamond\ket{\tpsi}}{ \| \tB_\ast^\diamond \ket{\tpsi} \|^2} = 1,
+From the marginal distribution $\pb{\diamond}{\ast} = \pa{0}{1}+\pa{1}{1} = 2/(d-1)$,
+we know $\| \tB_\ast^\diamond \ket{\tpsi} \| = \| (\tA_1^0+\tA_1^1) \ket{\tpsi}\| = \sqrt{2/d-1}$.
+Since $\pr{0\diamond}{1\ast} + \pr{1\diamond}{1\ast} = 2/(d-1)$, we find that 
+\begin{align*}
+	\frac{\bra{\tpsi}\tB_\ast^\diamond (\tA_1^0+\tA_1^1) \tB_\ast^\diamond\ket{\tpsi}}{ \| \tB_\ast^\diamond \ket{\tpsi} \|^2} = 1,
 \end{align*}
@@
 \begin{align}
-	(\tA_0^0+\tA_0^1)\tB_\ast^\diamond \ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
-\end{align}
-Using the commutation relation between $(\tA_0^0+\tA_0^1)$ and $\tB_\ast^\diamond$, we get
-\begin{align*}
-	\frac{\bra{\tpsi} (\tA_0^0+\tA_0^1) \tB_\ast^\diamond(\tA_0^0+\tA_0^1)\ket{\tpsi}}{ \| (\tA_0^0+\tA_0^1) \ket{\tpsi} \|^2} = 1,
+	(\tA_1^0+\tA_1^1)\tB_\ast^\diamond \ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
+\end{align}
+Using the commutation relation between $(\tA_1^0+\tA_1^1)$ and $\tB_\ast^\diamond$, we get
+\begin{align*}
+	\frac{\bra{\tpsi} (\tA_1^0+\tA_1^1) \tB_\ast^\diamond(\tA_1^0+\tA_1^1)\ket{\tpsi}}{ \| (\tA_1^0+\tA_1^1) \ket{\tpsi} \|^2} = 1,
 \end{align*}
@@
 \begin{align}
-	\tB_\ast^\diamond (\tA_0^0+\tA_0^1) \ket{\tpsi} = (\tA_0^0+\tA_0^1)\ket{\tpsi}.
+	\tB_\ast^\diamond (\tA_1^0+\tA_1^1) \ket{\tpsi} = (\tA_1^0+\tA_1^1)\ket{\tpsi}.
 \end{align}
@@
 \begin{align}
-	(\tA_0^0+\tA_0^1)\ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
+	(\tA_1^0+\tA_1^1)\ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
 \end{align}
@@
 \begin{align}
-	\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi} = (\tA_0^0+\tA_0^1)\ket{\tpsi} = (\tA_1^0+\tA_1^1)\ket{\tpsi}.
+	\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi} = (\tA_1^0+\tA_1^1)\ket{\tpsi} = (\tA_2^0+\tA_2^1)\ket{\tpsi}.
 \end{align}
@@
 \begin{align}
-	\tB_\ast^\perp \ket{\tpsi} = \tA_\ast^\perp \ket{\tpsi} = \tA_0^\perp \ket{\tpsi} = \tA_1^\perp \ket{\tpsi},
+	\tB_\ast^\perp \ket{\tpsi} = \tA_\ast^\perp \ket{\tpsi} = \tA_1^\perp \ket{\tpsi} = \tA_2^\perp \ket{\tpsi},
 \end{align}
@@
 
-Next we examine the CHSH-type correlation when $x,y \in [2]$,
-\begin{align*}
-	   \bra{\tpsi} \tA_0^0\tB_0^0 \ket{\tpsi} 
-	= &\bra{\tpsi}(\tA_\ast^\diamond + \tA_\ast^\perp) \tA_0^0\tB_0^0 (\tA_\ast^\diamond + \tA_\ast^\perp)\ket{\tpsi} \\
-	= & \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_\ast^\perp\ket{\tpsi} \\
-	&+\bra{\tpsi}\tA_\ast^\perp \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\perp \tA_0^0\tB_0^0 \tA_\ast^\perp\ket{\tpsi}\\
-	= & \bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_0^\perp\ket{\tpsi} \\
-	&+\bra{\tpsi}\tA_0^\perp \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_0^\perp \tA_0^0\tB_0^0 \tA_0^\perp\ket{\tpsi}\\
-	=&\bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi},
-\end{align*}
-where we use the facts that $\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi}$, $\tA_\ast^\perp \ket{\tpsi} = \tA_0^\perp \ket{\tpsi}$ and that 
-$\spn(\tA_0^0) \cap \spn(\tA_0^\perp) = \emptyset$. 
+Next we examine the CHSH-type correlation when $x,y \in [2]+1$,
+\begin{align*}
+	   \bra{\tpsi} \tA_1^0\tB_1^0 \ket{\tpsi} 
+	= &\bra{\tpsi}(\tA_\ast^\diamond + \tA_\ast^\perp) \tA_1^0\tB_1^0 (\tA_\ast^\diamond + \tA_\ast^\perp)\ket{\tpsi} \\
+	= & \bra{\tpsi}\tA_\ast^\diamond \tA_1^0\tB_1^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_1^0\tB_1^0 \tA_\ast^\perp\ket{\tpsi} \\
+	&+\bra{\tpsi}\tA_\ast^\perp \tA_1^0\tB_1^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\perp \tA_1^0\tB_1^0 \tA_\ast^\perp\ket{\tpsi}\\
+	= & \bra{\tpsi}\tB_\ast^\diamond \tA_1^0\tB_1^0 \tB_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_1^0\tB_1^0 \tA_0^\perp\ket{\tpsi} \\
+	&+\bra{\tpsi}\tA_0^\perp \tA_1^0\tB_1^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_0^\perp \tA_1^0\tB_1^0 \tA_0^\perp\ket{\tpsi}\\
+	=&\bra{\tpsi}\tB_\ast^\diamond \tA_1^0\tB_1^0 \tB_\ast^\diamond\ket{\tpsi},
+\end{align*}
+where we use the facts that $\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi}$, $\tA_\ast^\perp \ket{\tpsi} = \tA_1^\perp \ket{\tpsi}$ and that 
+$\spn(\tA_1^0) \cap \spn(\tA_0^\perp) = \emptyset$. 
 This means that if Alice and Bob share the state $\tB_\ast^\diamond \ket{\tpsi}/\|\tB_\ast^\diamond \ket{\tpsi}\|$ and apply 
-$\tA_0^0\tB_0^0$, the conditional probability is
-\begin{align}
-	\frac{\bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi}}{\bra{\tpsi} \tB_\ast^\diamond \tB_\ast^\diamond \ket{\tpsi}} = \frac{\cos^2(\pi/4d)}{2}.
-\end{align} 
-We can re-normalize the other correlations of $a,b \in [2]$ when $x,y \in [2]$ similarly, and get a new set of correlations 
+$\tA_1^0\tB_1^0$, the conditional probability is
+\begin{align}
+	\frac{\bra{\tpsi}\tB_\ast^\diamond \tA_1^0\tB_1^0 \tB_\ast^\diamond\ket{\tpsi}}{\bra{\tpsi} \tB_\ast^\diamond \tB_\ast^\diamond \ket{\tpsi}} = \frac{\cos^2(\pi/2d)}{2}.
+\end{align} 
+We can re-normalize the other correlations of $a,b \in [2]$ when $x,y \in [2+1]$ similarly, and get a new set of correlations 
 which achieves the maximal value of $\langle \1_{-\cot(\pi/2d)}\rangle$. 
@@
 Note that the combination of \cref{lm:chsh_comp} with \cref{prop:2d-subspace} gives us that 
-$\tB_0\tB_1$ has eigenvalues $\omega_d$ and $\omega_d^{-1}$.
+$\tB_1\tB_2$ has eigenvalues $\omega_d$ and $\omega_d^{-1}$.
 
@@
 %=====================================
-In this section, we introduce the combined game $\G$ and then
+In this section, we introduce the correlation $C(\dr{2})$, which is the
+ideal correlation of $\G(\dr{2})$, and then
 prove that it can self-test the state $\ket{\EPR{d-1}}$.
@@
 %-----------------------------------------------------------------
-\subsection{The correlation for the game $\G$}
+\subsection{The correlation $C(\dr{2})$}
 %-----------------------------------------------------------------
 Assume the linear system game has $n=118$ variables and $m=91$ equations.
+In game $\G(\dr{2})$, 
 Alice receives $x \in \{1,\dots m+3 \}$ and Bob receives
@@
 	(The intuition behind is that $B_1B_2 = X$.);
-	\item otherwise, their behaviour is irrelavant.
+	\item otherwise, their behaviour is irrelevant.
 \end{itemize}
-Note that the dimension $d$ is defined in the rules of $\CHSH_X$.
+Note that the dimension $\dr{2}$ is defined in the rules of $\CHSH_X$.
 
 \begin{proposition}
-	The game $\G{d-1}$ can be won perfectly by a quantum strategy.
+	The game $\G(\dr{2})$ can be won perfectly by a quantum strategy.
 \end{proposition}
-We prove this proposition by giving the optimal strategy.
+We prove this proposition by giving the ideal strategy.
 \begin{proof}
-We determine the operator solution first and then we determine the shared state.
+The construction start with the ideal strategy for the weighted $\CHSH_X$ test.
+We choose $\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1} \ket{ii}$ and $V = \spn(\ket{1} ,\ket{d-1})$.
+Alice's projectors and observables for the weighted $\CHSH_X$ test are
+\begin{align*}
+	&A_\ast^\diamond = \ketbra{1}{1} + \ketbra{d-1}{d-1}, &&A_\ast^\perp = \1 - A_\ast^\diamond, \\
+	&A_1 = A_1^0-A_1^1 = \ketbra{1}{1} - \ketbra{d-1}{d-1}, &&A_1^\perp = A_\ast^\perp,\\
+	&A_2 = A_2^0-A_2^1 = \ketbra{1}{d-1} + \ketbra{d-1}{1} ,&&A_2^\perp = A_\ast^\perp.
+\end{align*}
+Bob's observables restricted to the subspace $V$ is
+\begin{align*}
+	B_1|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) - \sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}),\\
+	B_2|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) +\sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}).
+\end{align*}
+To make sure operator $B_2$ commutes with the operator $U$ that we will construct later, we pick a 
+special basis of $X =B_1B_2$, which is
+\begin{align}
+	\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{1} + i\ket{d-1}), &&
+	\ket{x_{d-1}} = \frac{-e^{i\pi/d}}{\sqrt{2}}(\ket{1} - i\ket{d-1}).
+\end{align}
+It can be checked that $X\ket{x_1} = \omega_d \ket{x_1}$ and $X\ket{x_{d-1}} = \omega_d^{d-1} \ket{x_{d-1}}$.
+In this basis, $B_1$ and $B_2$ are expressed as 
+\begin{align}
+	&B_1|_V = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
+	&B_2|_V =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1}.
+\end{align}
 Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
-the observables $B_1$ and $B_2$ are extended from the formulation given in the proof
-of \cref{prop:2d-subspace},
+the observables $B_1$ and $B_2$ are extended from $B_1|_V$ and $B_2|_V$ as follows
 %\begin{align}
@@
 \begin{align}
-	B_1 &= \ketbra{x_0}{x_0} + 
-	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/d}\ketbra{x_{d-k}}{x_k}\right)\\
-	B_2 &= \ketbra{x_0}{x_0} + 
-	\sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
-\end{align}
-It can be checked that $B_1B_2 = \sum_{i=0}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ and the operator $U$ is
-\begin{align}
-	U = \sum_{i=0}^{d-1} \ketbra{x_{i/2 \pmod{d}}}{x_i}.
+	B_1 &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
+	B_2 &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
+\end{align}
+It can be checked that $B_1B_2 = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ and the operator $U$ is
+\begin{align}
+	U = \sum_{i=1}^{d-1} \ketbra{x_{i/2 \pmod{d}}}{x_i}.
 \end{align}
@@
 \begin{align}
-	UB_2U\ct = U\ketbra{x_0}{x_0}U\ct + \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct 
-	= \ketbra{x_0}{x_0} + \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct.
+	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct.
 \end{align}
@@
 \end{proof}
-Next we are going to prove that the strategy winning this game optimally can self-test $d-1$-dimensional EPR pair.
+Next we are going to prove that the correlation $C(\dr{2})$ that is produced by the 
+strategy winning this game optimally, can self-test $d-1$-dimensional EPR pair.
 
 %-----------------------------------------------------------------
-\subsection{Proof of \cref{thm:pr_2}}
+\subsection{Self-test}
 %-----------------------------------------------------------------
 \hl{This subsection needs to be formalized.}
-
+We give a formal version of \cref{thm:pr_2} first and then prove it.
+\begin{theorem}
+	If a quantum strategy using the shared state $\ket{\psi}$ achieves the ideal 2-party correlation $C(d,2)$ where $d$ is an odd
+	prime number with primitive root $2$, then there exist local isometries $\Phi_A$ and $\Phi_B$, and a state $\ket{junk}$ such 
+	that $\Phi_A\x\Phi_B \ket{\psi} = \ket{\EPR{d-1}} \x \ket{junk}$.
+\end{theorem}
+\begin{proof}
 Suppose Alice and Bob achieve the optimal correlation with the quantum strategy $(\ket{\psi}, \{A_x\}, \{B_y\})$
@@
 Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.
-Hence, by \cref{eq:ux_relation} we can calculate the eigen-decomposition of $X_A$ in $\supp(\rho_A)$.
-as follows
+By \cref{eq:ux_relation} we can calculate that
 \begin{align}
@@
 so $U_A^\dagger \ket{x_{1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^2$.
-By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{2^i} (U_A^\dagger)^i\ket{x_{A,1}}$. 
+By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{2^i} (U_A^\dagger)^i\ket{x_{1}}$. 
 From the set $\{(U_A^\dagger)^i \Pi_{V_1} (U_A)^i \}_{i=0}^{d-2}$, we can identify $\Pi_{V_i}$ for $i = 1 \dots  d-1$
@@
 \end{align}
-Since unitary transformation does not change the rank of a matrix, we know $\rank(\Pi_{V_1}) = \rank(\Pi_{V_{i}}) =m$
-for $ i =1 \dots d-1$,
-and we assume 
-\begin{align}
- \Pi_{V_i} = \sum_{j=1}^m \ketbra{x_{i,j}}{x_{i,j}}.
-\end{align}
+Since unitary transformation does not change the rank of a matrix, we know $\rank(\Pi_{V_1}) = \rank(\Pi_{V_{i}}) =N$
+for $ i =1 \dots d-1$.
+We pick a basis for $V_1$ such that 
+\begin{align}
+	\Pi_{V_1} =  \sum_{j=1}^N \ketbra{x_{1,j}}{x_{1,j}},
+\end{align}
+then we can construct 
+\begin{align}
+ \Pi_{V_i} = \sum_{j=1}^N \ketbra{x_{i,j}}{x_{i,j}},
+\end{align}
+where $\ket{x_{i,j}} = (U\ct)^{k_i} \ket{x_{1,j}}$ for $2^{k_i} \equiv i \pmod{d}$ and $1 \leq j \leq N$.
 By \cref{eq:ux_relation} we also know that $U_A \ket{x_{i,j}} = \ket{x_{i/2,j}}$ for $i = 1,2 \dots d-1$.
@@
 	\label{eq:d-1}
-	\Pi_{W_j} \tau \Pi_{W_j}  = c_j \1_{S_A} \text{ for } j = 1\dots m.
+	\Pi_{W_j} \tau \Pi_{W_j}  = c_j \1_{W_j} \text{ for } j = 1\dots N.
 \end{align}
@@
 \begin{align}
-	\sum_{j =1}^m \Pi_{W_j} \ket{\psi} =\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}. 
+	\sum_{j =1}^N \Pi_{W_j} \ket{\psi} =\sum_{i=1}^{d-1} \sum_{j=1}^N c_j \ket{x_{i,j}}\ket{x_{i,j}}. 
 \end{align}
@@
  \begin{align}
- 	2 \sum_{j=1}^m \norm{c_j}^2 = \frac{2}{d-1}.
- \end{align}
- Then we can calculate the norm of $\sum_{j =1}^m \Pi_{W_j} \ket{\psi}$, which is
- \begin{align}
- \norm{\sum_{j =1}^m \Pi_{W_j} \ket{\psi}}^2 = \sum_{i=1}^{d-1} \sum_{j=1}^m \norm{c_j}^2 = 1 = \norm{\ket{\psi}}^2.
- \end{align}
- In the end, we can conclude that $\supp{\rho_A} = \cup_{i=1}^{d-1} V_i$ and there exist local isometries $\Phi_A$ and $\Phi_B$
- such that 
- \begin{align}
- 	\Phi_A\x\Phi_B  \ket{\psi} =  (\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{ii}) \x \ket{junk}.
- \end{align}
-
+ 	2 \sum_{j=1}^N \norm{c_j}^2 = \frac{2}{d-1}.
+ \end{align}
+ Then we can calculate the norm of $\sum_{j =1}^N \Pi_{W_j} \ket{\psi}$, which is
+ \begin{align}
+ \norm{\sum_{j =1}^N \Pi_{W_j} \ket{\psi}}^2 = \sum_{i=1}^{d-1} \sum_{j=1}^N \norm{c_j}^2 = 1 = \norm{\ket{\psi}}^2.
+ \end{align}
+ We can conclude that $\supp{\rho_A} = \cup_{i=1}^{d-1} V_i$ and 
+ \begin{align}
+ 	\ket{\psi} = \sum_{i=1}^{d-1}\sum_{j=1}^N c_j \ket{x_{i,j}}\ket{x_{i,j}}.
+ \end{align}
+
+The last step is to construct the local isometries $\Phi_A$ and $\Phi_B$ that can produce $\ket{\EPR{d-1}}$ from $\ket{\psi}$.
+We give steps about how $\Phi_A$ and $\Phi_B$ works.
+Since the subspaces $W_j$'s are orthogonal, Alice and Bob can map state $\ket{\psi}$ to the state 
+\begin{align}
+	\ket{\psi'} = \sum_{i=1}^{d-1}\sum_{j=1}^N c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{j}_A\ket{j}_B.
+\end{align}
+Note that we added subscript $A$ and $B$ to stress the subsystems holden by Alice and Bob respectively.
+Since $\ket{x_{i,j}}$ is orthogonal to $\ket{x_{i',j'}}$ for $i\neq i'$ or $j \neq j'$, we further assume that there exists 
+a unitary $O$ such that $O\ket{x_{i,j}} = O\ket{x_{i,j+1}}$ for all $i$ and $j$, but when $j = N$, $O\ket{x_{i,N}} = \ket{x_{i,1}}$.
+Then controlled by the appended register, Alice and Bob can apply $(O\ct)^j$ to the original system
+and $\ket{\psi'}$ is mapped to
+\begin{align}
+	 &\sum_{i=1}^{d-1}\sum_{j=1}^N c_j [(O\ct)^j\ket{x_{i,j}}_A] \x [(O\ct)^j\ket{x_{i,j}}_B] \x \ket{j}_A\ket{j}_B\\
+	 = &\sum_{i=1}^{d-1}\sum_{j=1}^N c_j \ket{x_{i,1}}_A\ket{x_{i,1}}_B \ket{j}_A\ket{j}_B\\
+	 =  &\frac{1}{\sqrt{d}} \sum_{i=1}^{d-1} \ket{x_{i,1}}_A\ket{x_{i,1}}_B \x \sum_{j=1}^N \sqrt{d}c_j \ket{j}_A\ket{j}_B
+\end{align}
+After relabelling $\ket{x_{i,1}}$ as $\ket{i}$, we factor $\ket{\EPR{d-1}}$ out of $\Phi_A \x \Phi_B \ket{\psi}$.
+\end{proof}
 %The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
@@
 	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
-	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_0B_0+A_0B_1) -  A_1B_0 + A_1B_1.
+	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_1B_1+A_1B_2) -  A_2B_1 + A_2B_2.
 \end{align} 
@@
 \begin{align*}
-	Z_A = A_0 &\quad X_A = A_1\\
-	Z_B = \frac{B_0+B_1}{2\cos(\mu)} &\quad X_B = \frac{B_0-B_1}{2\sin(\mu)},
+	Z_A = A_1 &\quad X_A = A_2\\
+	Z_B = \frac{B_1+B_2}{2\cos(\mu)} &\quad X_B = \frac{B_1-B_2}{2\sin(\mu)},
 \end{align*}
@@
 With appropriate substitutions, the rest of the proof follows the same derivation as that in Appendix A of Ref.~\cite{bamps2015},
-so we omit it here.
+so we omit it here. The dependence of the error term on $\alpha$ comes from the fact that 
+\begin{align}
+\frac{1}{\cos(\arctan(1/\alpha)) \sin^{1/2}(\arctan(1/\alpha))} = \frac{1}{\alpha}+\frac{3}{4}\alpha - O(\alpha^3).
+\end{align}
+
 \end{proof}

### 2019-01-31 Draft/draft.tex
Honghao: generalized our result to work for prime numbers whose primitive root is 2, 3 or 5

@@
 	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
-	primitive root $2$, can be self-tested by a constant-sized correlation.
+	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
 \end{theorem}
-The correlation that we use to prove \cref{thm:pr_2} is denoted by $C(\dr{2})$.
-We use the superscript $(2)$ to denote the primitive root of $d$.
-Note that although the size of $C(\dr{2})$ does not depend on $d$, the optimal correlation does.
-This correlation can be easily modified to self-test the maximally entangled state whose local dimension has 
-primitive $3$ or $5$.
+The correlation that we use to prove \cref{thm:pr_2} is denoted by $C(\dr{r})$.
+We use the superscript $(r)$ to denote the primitive root of $d$.
+Note that although the size of $C(\dr{r})$ does not depend on $d$, the optimal correlation does.
 
@@
 \begin{align}
-	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/2}{k},
-\end{align}
-where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity.
+	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
+\end{align}
+where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
+and $r$ is the primitive root of $d$.
 Through out this paper, any operation on the label of the eigenvector $\ket{i}$ is taken modulo $d$,
-unless otherwise specified, for example, the $i/2$ above.
+unless otherwise specified, for example, the $i/r$ above.
 
@@
 present a correlation that can self-test $\ket{\EPR{d-1}}$, 
-where $d$ is prime and has primitive root $2$,
-and this correlation is denoted by $C(\dr{2})$.
-The correlation we constructed is the optimal correlation for a game $\G(\dr{2})$, which is the combination of two tests.
+where $d$ is prime and has primitive root $r \in \{2, 3, 5\}$,
+and this correlation is denoted by $C(\dr{r})$.
+The correlation we constructed is the optimal correlation for a game $\G(\dr{r})$, which is the combination of two tests.
 In this section, we introduce the linear system game which tests a relation that should be satisfied by 
@@
 Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
-The main component of $\G(\dr{2})$ is a linear system game $\LS$, whose solution group is the embedding of the 
+The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
 following group
 \begin{align}
-	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
+	\Pg_r= \langle u, x : uxu^{-1} = x^r \rangle, \text{ for } r \in \{2, 3,5\}.
 \end{align}
 In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
-relation $uxu^{-1} = x^2$.
+relation $uxu^{-1} = x^r$.
 \begin{proposition}
 	\label{prop:embed}
-	The group $\Pg$ can be embedded into a linear system game $\LS$ over $\Z_2$,
-	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
+	The group $\Pg_r$ can be embedded into a linear system game $\LS$ over $\Z_2$,
+	with constant numbers of variables and equations, where each equation involves $3$ variables.
 \end{proposition}
-The process of embedding $\Pg$ into the solution group of $\LS$ follows the recipe given in the proofs of
+The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
 Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
 The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
-We give details of this embedding process in \cref{sec:power2}.
-
-In the later parts of the paper, we use $n = 118$ and $m = 91$ to refer to the size of $\LS$.
-The key feature of this embedding is that $\LS$ has constant-sized input-output alphabet
-even if the generators $u$ and $x$ can have arbitrary order. 
-The product of the generators $x_1$ and $x_2$ from the solution group of $\LS$ plays the role 
-of the generator $x$ in $\Pg$ and the product of the generators $x_3$ and $x_4$ plays the role
-of the generator $u$ in $\Pg$. As shown in \cref{sec:power2}, $x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
-\begin{align}
-	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^2.
+We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
+and \cref{sec:power5} for $r = 5$.
+
+In the later parts of the paper, we use $n_r$ and $m_r$ to refer to the size of $\LS_r$.
+The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
+even if the generators $u$ and $x$ have arbitrary order. 
+The product of the generators $x_1$ and $x_2$ from the solution group of $\LS_r$ plays the role 
+of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
+of the generator $u$ in $\Pg_r$. As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
+$x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
+\begin{align}
+	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^r.
 \end{align}
@@
 \begin{align}
-	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^2\ket{\psi}, 
+	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^r\ket{\psi}, 
 \end{align}
 and similarly on Bob's side.
-If we denote the unitary corresponding to the generator $u$ of $\Pg$ by $U$ and the unitary
+If we denote the unitary corresponding to the generator $u$ of $\Pg_r$ by $U$ and the unitary
 corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
-$UXU\ct \ket{\psi} = X^2 \ket{\psi}$.
+$UXU\ct \ket{\psi} = X^r \ket{\psi}$.
 The special property of $U$ and $X$ is summarized in the following lemma.
@@
 	\begin{align}
-		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
-	\end{align}
+		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/r}{i},
+	\end{align}
+	where $d$ is an odd prime number with primitive root $r$,
 	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
@@
 \end{lemma}
-Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
+Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^r$.
 In the self-test proof, this lemma will be a critical step.
@@
 \end{align}
-We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
-The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
+We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
+The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
 Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
@@
 \begin{align}
-	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/2^k}\braket{i}{1}.
-\end{align}
-For the term $\braket{1}{i/2^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $2^k \equiv 1 \pmod{d}$, or equivalently,
+	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/r^k}\braket{i}{1}.
+\end{align}
+For the term $\braket{1}{i/r^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
 $k = k_1$. Hence, we can conclude that 
@@
 	\bra{j}M\ket{j} 
-	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/2^k}\braket{i}{j} 
+	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/r^k}\braket{i}{j} 
 	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
@@
 \end{proof}
+Note that the primitive root $r$ in the lemma is not restricted to the set $\{2,3,5\}$, so this lemma works for any 
+odd prime number $d$.
+
 %\begin{align}
@@
 In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
-$U$ and $X$ has the eigen-structure required by \cref{lm:ux_independ}.
+$X$ has the eigen-structure required by \cref{lm:ux_independ}.
 We denote this game that enforces the eigenvalues of the observable $X$ by
 $\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
+We remark that for the extended weighted CHSH test, the primitive root of $d$ is irrelevant,
+so we drop the superscript $(r)$.
 
@@
 %=====================================
-In this section, we introduce the correlation $C(\dr{2})$, which is the
-ideal correlation of $\G(\dr{2})$, and then
+In this section, we introduce the correlation $C(\dr{r})$, which is the
+ideal correlation of $\G(\dr{r})$, and then
 prove that it can self-test the state $\ket{\EPR{d-1}}$.
@@
 %-----------------------------------------------------------------
-\subsection{The correlation $C(\dr{2})$}
+\subsection{The correlation $C(\dr{r})$}
 %-----------------------------------------------------------------
-Assume the linear system game has $n=118$ variables and $m=91$ equations.
-In game $\G(\dr{2})$, 
-Alice receives $x \in \{1,\dots m+3 \}$ and Bob receives
-$y \in \{1,\dots,n+1\}$. We follow the previous structure by first give intuition about how they should
+Recall that the linear system game $\LS_r$ has $n_r$ variables and $m_r$ equations.
+In game $\G(\dr{r})$, 
+Alice receives $x \in \{1,\dots m_r+3 \}$ and Bob receives
+$y \in \{1,\dots,n_r+1\}$. We follow the previous structure by first give intuition about how they should
 behave in this game. The correlation can be easily extracted from the behaviour list below.
 \begin{itemize}
-	\item When $x \in \{1,\dots m\}$ and $y \in \{1, \dots n\}$, they should win the 
-	linear system game $\LS$ perfectly;
-	\item when $x \in \{m+1, m+2, m+3\}$ and $y \in \{1, 2, n+1\}$, they should follow the
+	\item When $x \in \{1,\dots m_r\}$ and $y \in \{1, \dots n_r\}$, they should win the 
+	linear system game $\LS_r$ perfectly;
+	\item when $x \in \{m_r+1, m_r+2, m_r+3\}$ and $y \in \{1, 2, n_r+1\}$, they should follow the
 	optimal correlation of the test $\CHSH_X$, where 
 	\begin{align}
-		&\ast_A = m+1, \quad 0_A = m+2,\quad 1_A = m+3,\\
-		&\ast_B = n+1,\quad 0_B = 1, \quad 1_A = 2,
+		&\ast_A = m_r+1, \quad 0_A = m_r+2,\quad 1_A = m_r+3,\\
+		&\ast_B = n_r+1,\quad 0_B = 1, \quad 1_A = 2,
 	\end{align}
@@
 \end{itemize}
-Note that the dimension $\dr{2}$ is defined in the rules of $\CHSH_X$.
+Note that the dimension $\dr{r}$ is defined in the rules of $\CHSH_X$.
 
 \begin{proposition}
-	The game $\G(\dr{2})$ can be won perfectly by a quantum strategy.
+	\label{prop:realize}
+	The correlation $C(\dr{r})$ can be realized by a quantum strategy.
 \end{proposition}
@@
 \begin{align}
-	U = \sum_{i=1}^{d-1} \ketbra{x_{i/2 \pmod{d}}}{x_i}.
+	U = \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.
 \end{align}
@@
 \begin{align}
-	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct.
-\end{align}
-There are two cases to consider which are the index is even or odd.
-Note that in the following calculation, the division is not with respect to the modulo $d$.
-When the index $i$ is even, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{i/2}}{x_{d-i/2}}$, and
-when the index $i$ is odd, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{(d+i)/2}}{x_{(d-i)/2}}$,
-so we can calculate that 
-\begin{align}
-	\sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct 
-	=& \sum_{i=1}^{(d-1)/2}U\ketbra{x_{2i}}{x_{d-2i}}U\ct 
-	+ \sum_{i=0}^{(d-1)/2-1} U\ketbra{x_{2i+1}}{x_{d-(2i+1)}}U\ct\\
-	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=0}^{(d-1)/2-1} \ketbra{x_{(d+1)/2+i}}{x_{(d-1)/2-i}}\\
-	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=(d+1)/2}^{d-1} \ketbra{x_i}{x_{d-i}}\\
-	=&\sum_{i=1}^{d-1} \ketbra{x_i}{x_{d-i}}.
-\end{align}
-The decomposition of $U$ into $B_3$ and $B_4$ is similar to the decomposition of $X$ and we leave it to the curious 
-readers.
+	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_{(d-i)/r \pmod{d}}}.
+\end{align}
+Let $i_1 = i/r \pmod{d}$ and $i_2  = (d-i)/r \pmod{d}$, then
+\begin{align*}
+	i_1 + i_2 \equiv& \frac{i}{r} + \frac{d-i}{r} \pmod{d} \\
+	\equiv& \frac{d}{r} \pmod{d}.
+\end{align*}
+Suppose $d/r \pmod{d} \equiv x$ for some integer $x$, then
+\begin{align}
+	rx \equiv d \pmod{d}.
+\end{align}
+Since $d$ is a odd prime number and $r < d$, then $r$ cannot divide $d$, so $x = 0$ or $d$.
+Considering the fact that $1 \leq i_1 \leq d-1$ and $1 \leq i_2 \leq d-1$, we know $x = i_1+i_2 = d$.
+Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
+Now suppose for $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_i'}{x_{d-i'}}U\ct$,
+it means that $i/r \equiv i'/r \pmod{d}$, which further implies that $i = i'$.
+To conclude, conjugation by $U$ only permutes the terms of $B_2$, so
+\begin{align}
+	UB_2U\ct = B_2.
+\end{align}
+%There are two cases to consider which are the index is dividable by $r$ or not.
+%Note that in the following calculation, the division is not with respect to the modulo $d$.
+%When the index $i \equiv 0 \pmod{r}$, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{i/2}}{x_{d-i/r}}$, and
+%when the index $i \not\equiv 0 \pmod{r}$, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{(d+i)/2}}{x_{(d-i)/2}}$,
+%so we can calculate that 
+%\begin{align}
+%	\sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct 
+%	=& \sum_{i=1}^{(d-1)/2}U\ketbra{x_{2i}}{x_{d-2i}}U\ct 
+%	+ \sum_{i=0}^{(d-1)/2-1} U\ketbra{x_{2i+1}}{x_{d-(2i+1)}}U\ct\\
+%	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=0}^{(d-1)/2-1} \ketbra{x_{(d+1)/2+i}}{x_{(d-1)/2-i}}\\
+%	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=(d+1)/2}^{d-1} \ketbra{x_i}{x_{d-i}}\\
+%	=&\sum_{i=1}^{d-1} \ketbra{x_i}{x_{d-i}}.
+%\end{align}
+The decomposition of $U$ into $B_3$ and $B_4$ is similar to the decomposition of $X$.
+Suppose the eigen-decomposition of $U$ is
+\begin{align}
+	U = \sum_{i=0}^{d-1} \omega_{d-1}^i \ketbra{u_i}{u_i},
+\end{align} 
+then the decomposition is the following 
+\begin{align}
+	B_3 =& \ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} + \sum_{k=1}^{(d-3)/2}\left( \omega_d^k\ketbra{u_k}{u_{d-1-k}} + \omega_d^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\
+	B_4 &= \ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} + \sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right).
+\end{align}
 
@@
 \end{proof}
-Next we are going to prove that the correlation $C(\dr{2})$ that is produced by the 
+Next we are going to prove that the correlation $C(\dr{r})$, which is produced by the 
 strategy winning this game optimally, can self-test $d-1$-dimensional EPR pair.
@@
 \begin{theorem}
-	If a quantum strategy using the shared state $\ket{\psi}$ achieves the ideal 2-party correlation $C(d,2)$ where $d$ is an odd
-	prime number with primitive root $2$, then there exist local isometries $\Phi_A$ and $\Phi_B$, and a state $\ket{junk}$ such 
+\label{thm:selftest}
+	If a quantum strategy using the shared state $\ket{\psi}$ achieves the ideal 2-party correlation $C(\dr{r})$ where $d$ is an odd
+	prime number with primitive root $r \in \{2,3,5\}$, then there exist local isometries $\Phi_A$ and $\Phi_B$, and a state $\ket{junk}$ such 
 	that $\Phi_A\x\Phi_B \ket{\psi} = \ket{\EPR{d-1}} \x \ket{junk}$.
@@
 By Lemma~$4.3$ of Ref.~\cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
-of the linear system game $\LS$. 
-For each variable $\{ x_i \}_{i=1}^n$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
+of the linear system game $\LS_r$. 
+For each variable $\{ x_i \}_{i=1}^{n_r}$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
 The condition that they agree with assignment to variables means that 
@@
 	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
-	\text{ for } 1 \leq i \leq n
+	\text{ for } 1 \leq i \leq n_r
 \end{align}
@@
 \begin{align}
-	\Tr(\rho_A \Pi_{j: H_{ij} \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m
+	\Tr(\rho_A \Pi_{j: H(i,j) \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m_r
 \end{align}
@@
 \begin{align}
-\Pi_{j:H_{ij} \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m.
-\end{align}
-Since the relation $uxu^{-1} = x^2$ is embedded in this linear system game, we know
-\begin{align}
-	A_3A_4 A_1A_2 (A_3A_4)^\dagger \ket{v}= (A_1A_2)^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
-\end{align}
-How $u$ and $x$ are splitted into order-$2$ generators can be found in Appendix~\ref{sec:construct}.
+\Pi_{j:H(i,j) \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m_r.
+\end{align}
+Since the relation $uxu^{-1} = x^r$, where $r$ is the primitive root of $d$, is embedded in this linear system game, we know
+\begin{align}
+	A_3A_4 A_1A_2 (A_3A_4)^\dagger \ket{v}= (A_1A_2)^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
+\end{align}
 For simplicity, we define $X_A = A_1A_2$ and $U_A=A_3A_4$ such that
@@
 	\label{eq:ux_relation}
-	U_AX_AU_A^\dagger \ket{v} = X_A^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
+	U_AX_AU_A^\dagger \ket{v} = X_A^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
 \end{align}
@@
 
-Suppose $A_{m+1} = A_\ast^\diamond- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
+Suppose $A_{m_r+1} = A_\ast^\diamond- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
 $2m$-dimensional vector space and $\Pi_{V_A}$ is the projector onto it. The reason why it has dimension $2m$
-will be clear shortly. On Bob's side, we also have $B_{n+1} = B_\ast^\diamond- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
+will be clear shortly. On Bob's side, we also have $B_{n_r+1} = B_\ast^\diamond- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
 Recall that from the extended weighted CHSH test, we know
@@
 \label{eq:ladder}
- X_AU_A^\dagger \ket{x_{1}} = U_A^\dagger X_A^2 \ket{x_{1}} = \omega_d^2 U_A^\dagger \ket{x_{1}},
-\end{align}
-so $U_A^\dagger \ket{x_{1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^2$.
-By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{2^i} (U_A^\dagger)^i\ket{x_{1}}$. 
+ X_AU_A^\dagger \ket{x_{1}} = U_A^\dagger X_A^r \ket{x_{1}} = \omega_d^r U_A^\dagger \ket{x_{1}},
+\end{align}
+so $U_A^\dagger \ket{x_{1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^r$.
+By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{r^i} (U_A^\dagger)^i\ket{x_{1}}$. 
 From the set $\{(U_A^\dagger)^i \Pi_{V_1} (U_A)^i \}_{i=0}^{d-2}$, we can identify $\Pi_{V_i}$ for $i = 1 \dots  d-1$
@@
 \begin{align}
-	\Pi_{V_1} =  \sum_{j=1}^N \ketbra{x_{1,j}}{x_{1,j}},
+	\Pi_{V_1} =  \sum_{j=1}^m \ketbra{x_{1,j}}{x_{1,j}},
 \end{align}
@@
 \begin{align}
- \Pi_{V_i} = \sum_{j=1}^N \ketbra{x_{i,j}}{x_{i,j}},
-\end{align}
-where $\ket{x_{i,j}} = (U\ct)^{k_i} \ket{x_{1,j}}$ for $2^{k_i} \equiv i \pmod{d}$ and $1 \leq j \leq N$.
+ \Pi_{V_i} = \sum_{j=1}^m \ketbra{x_{i,j}}{x_{i,j}},
+\end{align}
+where $\ket{x_{i,j}} = (U\ct)^{k_i} \ket{x_{1,j}}$ for $r^{k_i} \equiv i \pmod{d}$ and $1 \leq j \leq m$.
 By \cref{eq:ux_relation} we also know that $U_A \ket{x_{i,j}} = \ket{x_{i/2,j}}$ for $i = 1,2 \dots d-1$.
@@
 	\label{eq:d-1}
-	\Pi_{W_j} \tau \Pi_{W_j}  = c_j \1_{W_j} \text{ for } j = 1\dots N.
+	\Pi_{W_j} \tau \Pi_{W_j}  = c_j \1_{W_j} \text{ for } j = 1\dots m.
 \end{align}
@@
 \begin{align}
-	\sum_{j =1}^N \Pi_{W_j} \ket{\psi} =\sum_{i=1}^{d-1} \sum_{j=1}^N c_j \ket{x_{i,j}}\ket{x_{i,j}}. 
+	\sum_{j =1}^N \Pi_{W_j} \ket{\psi} =\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}. 
 \end{align}
@@
  \begin{align}
- 	2 \sum_{j=1}^N \norm{c_j}^2 = \frac{2}{d-1}.
- \end{align}
- Then we can calculate the norm of $\sum_{j =1}^N \Pi_{W_j} \ket{\psi}$, which is
- \begin{align}
- \norm{\sum_{j =1}^N \Pi_{W_j} \ket{\psi}}^2 = \sum_{i=1}^{d-1} \sum_{j=1}^N \norm{c_j}^2 = 1 = \norm{\ket{\psi}}^2.
+ 	2 \sum_{j=1}^m \norm{c_j}^2 = \frac{2}{d-1}.
+ \end{align}
+ Then we can calculate the norm of $\sum_{j =1}^m \Pi_{W_j} \ket{\psi}$, which is
+ \begin{align}
+ \norm{\sum_{j =1}^m \Pi_{W_j} \ket{\psi}}^2 = \sum_{i=1}^{d-1} \sum_{j=1}^m \norm{c_j}^2 = 1 = \norm{\ket{\psi}}^2.
  \end{align}
@@
  \begin{align}
- 	\ket{\psi} = \sum_{i=1}^{d-1}\sum_{j=1}^N c_j \ket{x_{i,j}}\ket{x_{i,j}}.
+ 	\ket{\psi} = \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}.
  \end{align}
@@
 \begin{align}
-	\ket{\psi'} = \sum_{i=1}^{d-1}\sum_{j=1}^N c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{j}_A\ket{j}_B.
+	\ket{\psi'} = \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{j}_A\ket{j}_B.
 \end{align}
@@
 \begin{align}
-	 &\sum_{i=1}^{d-1}\sum_{j=1}^N c_j [(O\ct)^j\ket{x_{i,j}}_A] \x [(O\ct)^j\ket{x_{i,j}}_B] \x \ket{j}_A\ket{j}_B\\
-	 = &\sum_{i=1}^{d-1}\sum_{j=1}^N c_j \ket{x_{i,1}}_A\ket{x_{i,1}}_B \ket{j}_A\ket{j}_B\\
-	 =  &\frac{1}{\sqrt{d}} \sum_{i=1}^{d-1} \ket{x_{i,1}}_A\ket{x_{i,1}}_B \x \sum_{j=1}^N \sqrt{d}c_j \ket{j}_A\ket{j}_B
+	 &\sum_{i=1}^{d-1}\sum_{j=1}^m c_j [(O\ct)^j\ket{x_{i,j}}_A] \x [(O\ct)^j\ket{x_{i,j}}_B] \x \ket{j}_A\ket{j}_B\\
+	 = &\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,1}}_A\ket{x_{i,1}}_B \ket{j}_A\ket{j}_B\\
+	 =  &\frac{1}{\sqrt{d}} \sum_{i=1}^{d-1} \ket{x_{i,1}}_A\ket{x_{i,1}}_B \x \sum_{j=1}^m \sqrt{d}c_j \ket{j}_A\ket{j}_B
 \end{align}
@@
 %\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
-%========================================
-\section{Extending $\G$ for general prime numbers }
-\label{sec:extend}
-%========================================
+In summary, for any odd prime number $d$ whose primitive root is $2$,$3$ or $5$, 
+\cref{prop:realize} tells us that the correlation $C(d)$ is achievable by a quantum strategy 
+and \cref{thm:selftest} tells us that the correlation $C(d)$ can self-test the EPR pair of
+local dimension $d-1$. Moreover, there are infinitely many prime numbers
+whose primitive root is in the set $\{2,3,5\}$ \cite{murty1988},
+Hence, our main result is the following theorem.
+\begin{theorem}
+	There exists an infinity-sized set $D$ of prime numbers such that 
+	each $d \in D$ has primitive root $2$, $3$ or $5$ and there exists
+	a constant-sized correlation $C(d)$ that can self-test the EPR pair of 
+	local dimension $d-1$.
+\end{theorem}
+We remark that our proof works for any odd prime number with primitive root $r$.
+However, since there is no upper-bound of $r$ for a general prime number $d$, we 
+cannot claim the corresponding correlation $C(d)$ is constant-sized. On the other
+hand, since $r$ is usually much smaller than $d$, our result implies a more efficient
+way to test EPR pairs of certain size than the one proposed in Ref.~\cite{cgs2017}.
 

### 2019-02-01 Draft/draft.tex
Honghao: minor modifications

@@
 To prove \cref{thm:inf}, we give explicit self-testing proof of 
-the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$ by explicitly giving the 
-correlation that achieves this goal. Then the self-testing property of this correlation is 
-given in the following theorem.
-\begin{theorem}[Informal]
-\label{thm:pr_2}
-	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
-	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
-\end{theorem}
-The correlation that we use to prove \cref{thm:pr_2} is denoted by $C(\dr{r})$.
+the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$,$3$, or $5$, 
+by explicitly giving the correlation that achieves self-testin. 
+%Then the self-testing property of this correlation is 
+%given in the following theorem.
+%\begin{theorem}[Informal]
+%\label{thm:pr_2}
+%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
+%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
+%\end{theorem}
+Our correlation is denoted by $C(\dr{r})$ for prime $d$.
 We use the superscript $(r)$ to denote the primitive root of $d$.
@@
 First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
-some unknown operator which is decomposed into two binary observables, which is not done before.
+some unknown operator which is decomposed into two binary observables.
+The variant of the CHSH inequality that we use is not used in the self-testing literature befor.
 Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintain
@@
 We start with notations and background information in \cref{sec:prelim}.
-Since the game we designed consists of two sub-tests, we introduce one test
-in \cref{sec:lsg} and one in \cref{sec:chsh}. Our main result is based the combination
-of the sub-tests and presented in \cref{sec:main}. In \cref{sec:extend}, we show how to adapt
-our nonlocal game to self-test maximally entangled state of different dimensions.
+Since the correlation we designed satisfies two sub-tests, we introduce one test
+in \cref{sec:lsg} and the other one in \cref{sec:chsh}. Our main result is based on the combination
+of the sub-tests and presented in \cref{sec:main}.
 
@@
 $\Z_d^\times = \{1,2\dots d-1\}$.
-The EPR pair of local dimension $d-1$ for some prime $d$, which has primitive root $2$, 
-is denoted by
+The EPR pair of local dimension $d-1$ for some prime $d$ is denoted by
 \begin{align}
@@
 and $r$ is the primitive root of $d$.
-Through out this paper, any operation on the label of the eigenvector $\ket{i}$ is taken modulo $d$,
-unless otherwise specified, for example, the $i/r$ above.
+Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
+unless otherwise specified, for example, the $k/r$ above.
 
@@
 on Hilbert space $\calH_A$ and $\calH_B$ respectively.
-A binary observable is a Hermitian matrix whose eigenvalues are either $+1$ or $-1$.
+A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
 The weighted CHSH inequality is given by 
@@
 An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
-measurements, which is the phenomenon of self-test. We give formal statement of this self-test result in \cref{sec:chsh}.
+measurements, which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.
 
@@
 pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
-to our new nonlocal game.
-
-The quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side and 
-$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. Then the behaviour of Alice and Bob is described 
-by the conditional probability
+to our new result.
+
+A quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side, 
+$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
+the condition that $P^2 = P = P\ct$.
+Then Alice and Bob's quantum strategy produces the correlation
 \begin{align}
@@
 where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
-Note that we may use the term behaviour and correlation interchangeably.
-The \emph{value} of a strategy is given by
-\begin{align}
-	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
-\end{align}
-
-The main contribution of our work is the construction of a correlation, which is the optimal correlation of a game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
+%Note that we may use the term behaviour and correlation interchangeably.
+%The value of a strategy is given by
+%\begin{align}
+%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
+%\end{align}
+
+The main contribution of our work is the construction of a correlation, which is the optimal correlation of a nonlocal game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
 such that this correlation can self-test $\ket{\EPR{d-1}}$ for arbitrary $d \in D$. 
 The nonlocal game $\G$ is a linear system game with strict enforcements. 
-We introduce the definition of self-testing first, the definition of linear system game, 
+We introduce the definition of self-testing, the definition of linear system game, 
 and its operator solution, 
@@
  where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
- $c$ is a length-$n$ vector with entries in $\Z_2$ too. 
+ $c$ is a length-$n$ vector with entries in $\Z_2$. 
  The associated linear system game involves two
@@
 \end{align}
-In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
+In other words, relations in the presentation of the solution group of $\LS_r$ can be combined to derive the
 relation $uxu^{-1} = x^r$.
@@
 	\label{prop:embed}
-	The group $\Pg_r$ can be embedded into a linear system game $\LS$ over $\Z_2$,
+	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
 	with constant numbers of variables and equations, where each equation involves $3$ variables.
@@
 The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
-Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
+Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
 The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
@@
 For the term $\braket{1}{i/r^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
-$k = k_1$. Hence, we can conclude that 
+$k = k_1$. We can conclude that 
 \begin{align}
@@
 \end{align}
-where $W_{m,n} = \omega_d^{mn}$. Then we define
+where $W(m,n) = \omega_d^{mn}$. Then we define
 \begin{align}
@@
 hand, since $r$ is usually much smaller than $d$, our result implies a more efficient
-way to test EPR pairs of certain size than the one proposed in Ref.~\cite{cgs2017}.
+way to test EPR pairs of prime local dimension than the one proposed in Ref.~\cite{cgs2017}.
+The size of our correlation grows linearly in $r$ whereas the Coladangelo \textit{et. al.}'s
+method uses correlation grows linearly in $d$.
 

### 2019-02-01 Draft/draft.tex
Honghao: minor changes

@@
 Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
-of the generalized Magic Square game and Magic Pentagram game, one can self-test
+of the generalized Magic Square game and Magic Pentagram game, one can robustly self-test
 $N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
 Both the Magic Square game and the Magic Pentagram game have constant question alphabet
-but growing answer alphabet.
-
-In summary, general $d$-dimensional maximally entangled states are self-tested by
+but answer alphabet of size $d$.
+
+At a high level, general $d$-dimensional maximally entangled states are self-tested by
 modifying the correlation and enlarging the size of the correlation.
@@
 An equivalent question to ask is whether it is possible to self-test maximally
-entangled state more efficiently, with constant question and answer set. 
+entangled state of some local dimension more efficiently, with constant correlation size. 
 In this report, we give an affirmative answer to this question by proving the following theorem.
@@
 
-The set $D$ is easily characterizable as it contains all the odd prime numbers with 
+The set $D$ is easily characterizable as it contains all the odd prime numbers with smallest
 primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
-with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
+with smallest primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
 To prove \cref{thm:inf}, we give explicit self-testing proof of 
 the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$,$3$, or $5$, 
-by explicitly giving the correlation that achieves self-testin. 
+by explicitly giving the correlation that achieves self-testing. 
 %Then the self-testing property of this correlation is 
@@
 First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
-some unknown operator which is decomposed into two binary observables.
-The variant of the CHSH inequality that we use is not used in the self-testing literature befor.
-Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintain
+some unknown operator which is the product of two binary observables used in the weighted CHSH test.
+The variant of the CHSH inequality that we use is not used in the self-testing literature before.
+Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintains
 certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
-Intuitively, such decomposition can be seen as the inverse of the decomposition used in the proof of Jordan's lemma.
+Intuitively, such decomposition can be seen as the inverse of the Jordan's lemma decomposition.
 The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
@@
 We start with notations and background information in \cref{sec:prelim}.
-Since the correlation we designed satisfies two sub-tests, we introduce one test
-in \cref{sec:lsg} and the other one in \cref{sec:chsh}. Our main result is based on the combination
-of the sub-tests and presented in \cref{sec:main}.
+Since the correlation we designed can win a special linear system game and satisfy
+an extended weighted CHSH test, we introduce the linear system game
+in \cref{sec:lsg} and the extended weighted CHSH test in \cref{sec:chsh}. 
+Our main result is based on the combination of the two tests and presented in \cref{sec:main}.
 
@@
 
-We use some basic number theory concepts in our work. A primitive root of a prime number
+We use some basic number theory in our work. A primitive root of a prime number
 $d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
 $r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
-$\Z_d^\times = \{1,2\dots d-1\}$.
+$\Z_d^\times = \{1,2\dots d-1\}$. When we say $d$ has primitive root $r$, we always mean
+that $r$ is the smallest primitive root.
+
 The EPR pair of local dimension $d-1$ for some prime $d$ is denoted by
@@
 An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
-measurements, which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.
+measurements up to isometry, 
+which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.
 
@@
 
-The main contribution of our work is the construction of a correlation, which is the optimal correlation of a nonlocal game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
-such that this correlation can self-test $\ket{\EPR{d-1}}$ for arbitrary $d \in D$. 
-The nonlocal game $\G$ is a linear system game with strict enforcements. 
-We introduce the definition of self-testing, the definition of linear system game, 
+The main contribution of our work is the construction of a correlation, which is the combination of 
+the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
+and the optimal correlation to violate the weighted CHSH inequality.
+The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
+primitive root. 
+In the next part, we introduce the definition of self-testing, the definition of linear system game, 
 and its operator solution, 
@@
 Perfect quantum strategies can be extracted from operator solutions and vice versa.
-
 Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
@@
 \end{definition}
-For concepts about group presentation, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
+For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
 Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 

### 2019-02-03 Draft/draft.tex
Made comments (in blue) on the first 6 pages.

@@
 
+\def\carl#1{{\color{blue} #1 -Carl}}
+
 \affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
@@
 some unknown operator which is the product of two binary observables used in the weighted CHSH test.
+\carl{I think this game might have been defined in APM12, and if so we need to cite it.}
 The variant of the CHSH inequality that we use is not used in the self-testing literature before.
@@
 certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
+\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
 Intuitively, such decomposition can be seen as the inverse of the Jordan's lemma decomposition.
@@
 which is the core idea in all the previous self-testing results.
+\carl{Are we sure about that ("all")?}
 Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.
@@
 $\Z_d^\times = \{1,2\dots d-1\}$. When we say $d$ has primitive root $r$, we always mean
-that $r$ is the smallest primitive root.
+that $r$ is the smallest primitive root.  \carl{I'm not clear on what that last sentence means.  You just defined what a primitive root
+is --- are you changing the definition now?}
 
@@
 where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
-and $r$ is the primitive root of $d$.
+and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
+definitions and notation for now.}
 Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
@@
 In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
-on Hilbert space $\calH_A$ and $\calH_B$ respectively.
+on Hilbert space $\calH_A$ and $\calH_B$ respectively.  \carl{It needs to be clearer who Alice and Bob
+are --- perhaps you should put this subsection after the ``Nonlocal games'' subsection.}
 A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
@@
 \end{align}
-where $\ip{A_xB_y}$ is the expectation value of of the observables.
+where $\ip{A_xB_y}$ is the expectation value of of the observables.  \carl{Same here -- it's not clear enough
+what this means until the reader has seen the ``Nonlocal games'' subsection.}
 If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
@@
 \end{definition}
+\carl{Just to be complete, you should say what $\pauliz$ and $\paulix$ denote.}
 An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
@@
 the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
-pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
+pair to $\{0,1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
 to our new result.
@@
 $\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
-the condition that $P^2 = P = P\ct$.
+the condition that $P^2 = P = P\ct$.  \carl{You need to put explicit labels on the quantum systems used by
+Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
+the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
 Then Alice and Bob's quantum strategy produces the correlation
@@
 the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
-and the optimal correlation to violate the weighted CHSH inequality.
+and the optimal correlation to violate the weighted CHSH inequality.  \carl{The reader does not 
+know yet what a linear system game is, so this comment is more confusing than helpful.}
 The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
@@
 following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
+
+\carl{Before the next definition, you should define what a ``correlation'' is.}
 \begin{definition}[Self-testing]
@@
 so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
-$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
+$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.  \carl{Make this clear in the definition itself.}
 We focus on quantum strategies for the linear system game presented in terms of binary observables.
@@
 converted to a quantum strategy presented in terms of projective measurement, and
-vice versa.
+vice versa.  \carl{This is not entirely true.  A ``quantum strategy presented in terms of projective measurement'' allows
+Alice to give answers that violate the ``Constraint satisfaction'' condition, while a ``quantum strategy presented 
+in terms of binary observables'' does not.}
 
@@
 satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
-operator solution in the following sense.
+operator solution in the following sense.  \carl{There's a missing reference here?}
 \begin{definition}[Operator solution of a linear system]
@@
 	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
-	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that 
+	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
+	be best to just state the definition for finite dimensions only.)}
 	\begin{enumerate}
@@
 \end{definition}
+\carl{Don't you also need a commutativity condition for $J$ with $\{ x_i \}$?}
 For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
@@
 a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.
+
+\carl{Section 2 needs to be cleaned up in some places, but overall it is pretty good.}
 
@@
 where $d$ is prime and has primitive root $r \in \{2, 3, 5\}$,
-and this correlation is denoted by $C(\dr{r})$.
+and this correlation is denoted by $C(\dr{r})$.  \carl{Be more precise --- we are constructing
+such a correlation for any $d$ which has $2, 3,$ or $5$ as a primitive root.}
 The correlation we constructed is the optimal correlation for a game $\G(\dr{r})$, which is the combination of two tests.
@@
 
-Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
+Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.  \carl{That sentence
+is too vague -- either make it a rigorous statement or leave it out.}
 The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
@@
 	with constant numbers of variables and equations, where each equation involves $3$ variables.
+	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
+	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
 \end{proposition}
@@
 of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
-of the generator $u$ in $\Pg_r$. As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
+of the generator $u$ in $\Pg_r$.   \carl{It's reasonable to make a couple informal statements
+at the beginning of a section, but you shouldn't be making
+such vague statements at this point.  Everything said at this point in the section should have a precise mathematical
+meaning.}
+As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
 $x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
@@
 We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
+\carl{We shouldn't be making extra assumptions that are not stated in the lemma.  This looks to me more like
+a definition of the variables $\{ k_i \}$, rather than an assumption.}
 The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.

### 2019-02-05 Draft/draft.tex
I read up to the middle of page 10, and added more comments

@@
 $\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
+\carl{Nice proof.  I like the use of the Vandermonde matrix.  We can think a little about possible simplifications.}
 \end{proof}
@@
 	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $A_x, B_y$ are 
-	defined in \cref{def:ideal}.
+	defined in \cref{def:ideal}.  \carl{You're using both ``aux'' and ``junk'' for the auxilliary state.  Also you need
+	to be clearer about what label you are using for Alice's and Bob's systems (see my previous comment on this).}
 \end{theorem}
@@
 	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
-	violation of  $\I_{\alpha}$, then $\tilde{B}_0\tilde{B}_1$ has eigenvalues $e^{i2\mu}$ and $e^{-i2\mu}$.
+	violation of  $\I_{\alpha}$, then $\tilde{B}_0\tilde{B}_1$ has eigenvalues $e^{i2\mu}$ and $e^{-i2\mu}$.  \carl{Make clear
+	that we mean that these are the only eigenvalues.}
 \end{proposition}
@@
 	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we know
-	$\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu)$ is a binary observable. \textcolor{red}{HF: Do we need to justify it?}
+	$\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu)$ is a binary observable. \textcolor{red}{HF: Do we need to justify it?}  \carl{Yes,
+	you should say more specifically where that is proved.}
 	Expanding $\tilde{Z}_B^2$ we get
@@
 	Observe that $(\tB_1\tB_2)^\dagger = \tB_2\tB_1$ and 
-	$(\tB_2\tB_1)(\tB_1\tB_2) = \tB_2\1\tB_2 = \1$, then we can conclude that $\tB_1\tB_2$ is unitary.
+	$(\tB_2\tB_1)(\tB_1\tB_2) = \tB_2\1\tB_2 = \1$, then we can conclude that $\tB_1\tB_2$ is unitary.  \carl{(It's a product
+	of unitaries, so that step is immediate.)}
 	Suppose the eigen-decomposition of $\tB_1\tB_2$ is
@@
 	\end{align*}
-	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.
+	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.  \carl{Good proof (if you fill in the step at
+	the beginning).}
 
@@
 so we drop the superscript $(r)$.
+\carl{You need to be more clear --- after reading this, I am still not sure what mathematical object ``$\CHSH_X$'' refers to.}
 
@@
 \textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$.
-We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and
+We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ \carl{(That's not 
+the way I usually see the $\setminus$ symbol used.)} and
 define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
@@
 to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.
+
+\carl{This good, but I imagine a reader being a little confused about what you are doing
+with these correlations (since the previous subsection wasn't very clear).}
 

### 2019-02-06 Draft/draft.tex
Honghao: start rewriting section 5.1

--- 2019-02-03 Draft/draft.tex
@@
 $r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
-$\Z_d^\times = \{1,2\dots d-1\}$. When we say $d$ has primitive root $r$, we always mean
-that $r$ is the smallest primitive root.  \carl{I'm not clear on what that last sentence means.  You just defined what a primitive root
+$\Z_d^\times = \{1,2\dots d-1\}$. \textcolor{red}{When the prime number $d$ has multiple primitive roots,
+we always work with the smallest one.}
+\carl{I'm not clear on what that last sentence means.  You just defined what a primitive root
 is --- are you changing the definition now?}
@@
 	\begin{align}
-		&\ast_A = m_r+1, \quad 0_A = m_r+2,\quad 1_A = m_r+3,\\
-		&\ast_B = n_r+1,\quad 0_B = 1, \quad 1_A = 2,
+		&\ast_A = m_r+1, \quad 1_A = m_r+2,\quad 2_A = m_r+3,\\
+		&\ast_B = n_r+1,\quad 1_B = 1, \quad 2_A = 2,
 	\end{align}
@@
 \begin{proof}
-The construction start with the ideal strategy for the weighted $\CHSH_X$ test.
-We choose $\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1} \ket{ii}$ and $V = \spn(\ket{1} ,\ket{d-1})$.
+We give the ideal strategy for the extended weighted $\CHSH_X$ test first and then based on it we give a representation of 
+group $\Gamma(\LS)$, $\Psi$, which can be converted to an ideal strategy for $\LS$. 
+The ideal strategy for $C(\dr{r})$ is the combination of the two ideal strategies for the two tests.
+
+\textbf{The ideal strategy for the weighted $\CHSH_X$ test}.
+Alice and Bob share state $\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1} \ket{ii}$ and choose the special subspace to be 
+$V = \spn(\ket{1} ,\ket{d-1})$.
 Alice's projectors and observables for the weighted $\CHSH_X$ test are
 \begin{align*}
-	&A_\ast^\diamond = \ketbra{1}{1} + \ketbra{d-1}{d-1}, &&A_\ast^\perp = \1 - A_\ast^\diamond, \\
-	&A_1 = A_1^0-A_1^1 = \ketbra{1}{1} - \ketbra{d-1}{d-1}, &&A_1^\perp = A_\ast^\perp,\\
-	&A_2 = A_2^0-A_2^1 = \ketbra{1}{d-1} + \ketbra{d-1}{1} ,&&A_2^\perp = A_\ast^\perp.
-\end{align*}
-Bob's observables restricted to the subspace $V$ is
+	&A_0^\diamond = \ketbra{1}{1} + \ketbra{d-1}{d-1}, &&A_0^\perp = \1 - A_\ast^\diamond, \\
+	&A_{m_r+2} = A_{m_r+2}^0-A_{m_r+2}^1 = \ketbra{1}{1} - \ketbra{d-1}{d-1}, &&A_{m_r+2}^\perp = A_\ast^\perp,\\
+	&A_{m_r+3} = A_{m_r+3}^0-A_{m_r+3}^1 = \ketbra{1}{d-1} + \ketbra{d-1}{1} ,&&A_{m_r+3}^\perp = A_\ast^\perp.
+\end{align*}
+Recall that in the extended weighted $\CHSH_X$ test, what matters is the 
+Bob's observables restricted to the subspace $V$, which are given by
 \begin{align*}
@@
 \end{align*}
-To make sure operator $B_2$ commutes with the operator $U$ that we will construct later, we pick a 
-special basis of $X =B_1B_2$, which is
+To make sure operator $B_2$ commutes with the operator $U = \Psi(x_3x_4) = \Psi(u)$ that we will construct later, we pick a 
+special basis of $X|_V =B_1|_VB_2|_V$, which is
 \begin{align}
@@
 It can be checked that $X\ket{x_1} = \omega_d \ket{x_1}$ and $X\ket{x_{d-1}} = \omega_d^{d-1} \ket{x_{d-1}}$.
-In this basis, $B_1$ and $B_2$ are expressed as 
+In this basis, $B_1|_V$ and $B_2|_V$ are expressed as 
 \begin{align}
@@
 \end{align}
+
+\textbf{The ideal strategy for $\LS_r$}.
+We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n_r(x)$.
+In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_{G(x)}$ for the group 
+\begin{align}
+	G(x) = \ip{ \{x_i\}_{i=1}^{n_r(x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
+\end{align}
+where details of $C_r$ can be found in the appendices. 
+Note that the relation $uxu^{-1} = x^2$ is embedded in the conjugation relations in $C_r$.
+Building on $\Psi_{G(x)}$, we can construct
+the representation $\Psi_{\Gamma(\LS_r)}$ for the solution group $\Gamma(\LS_r)$.
+
 Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
-the observables $B_1$ and $B_2$ are extended from $B_1|_V$ and $B_2|_V$ as follows
+the observables $A_1 = B_1 = \Psi_{G(x)}(x_1)$ and $A_2 = B_2 = \Psi_{G(x)}(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows
 %\begin{align}
@@
 \begin{align}
-	B_1 &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
-	B_2 &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
-\end{align}
-It can be checked that $B_1B_2 = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ and the operator $U$ is
-\begin{align}
-	U = \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.
+	A_1 = B_1 = \Psi_{G(x)}(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
+	A_2 = B_2 = \Psi_{G(x)}(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
+\end{align}
+It can be checked that $X = \Psi_{G(x)}(x_1x_2) = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ 
+The relation $uxu^{-1} = x^r$ and $X$ determine that 
+\begin{align}
+	U =\Psi_{G(x)}(u) = \Psi_{G(x)}(x_3x_4) =  \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.
 \end{align}
 The first step of the embedding procedure in the proof of \cref{prop:embed} requires
-the commutativity between $U$ and $B_2$, which can be verified as follows,
+the commutativity between $U$ and $B_2$, so we prove the commutation relation first and
+then give $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$.
+The commutation relation can be checked as follows,
 \begin{align}
@@
 %\end{align}
-The decomposition of $U$ into $B_3$ and $B_4$ is similar to the decomposition of $X$.
-Suppose the eigen-decomposition of $U$ is
-\begin{align}
-	U = \sum_{i=0}^{d-1} \omega_{d-1}^i \ketbra{u_i}{u_i},
-\end{align} 
-then the decomposition is the following 
-\begin{align}
-	B_3 =& \ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} + \sum_{k=1}^{(d-3)/2}\left( \omega_d^k\ketbra{u_k}{u_{d-1-k}} + \omega_d^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\
-	B_4 &= \ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} + \sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right).
-\end{align}
-
+The decomposition of $U$ into $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$ is similar to the decomposition of $X$.
+Since $u$ has order $d-1$, we can find an eigenbasis $\{ \ket{u_i} \}_{i=0}^{d-2}$ such that the eigen-decomposition of $U$ is
+\begin{align}
+	U = \sum_{i=0}^{d-2} \omega_{d-1}^i \ketbra{u_i}{u_i},
+\end{align} 
+then $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$ are  
+\begin{align*}
+	A_3 = B_3 =\Psi_{G(x)}(x_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
+	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
+	A_4 = B_4  =\Psi_{G(x)}(x_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
+	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right).
+\end{align*}
+The conjugation relations in $C_r$ determines the representations of 
+the rest of the $x_i$'s from $x_1,x_2,x_3$ and $x_4$. 
+For example, if $x_5 = x_1x_2x_1 \in C_r$, then
+\begin{align}
+	\Psi_{G(x)}(x_5) = \Psi_{G(x)}(x_1)\Psi_{G(x)}(x_2) \Psi_{G(x)}(x_1).
+\end{align}
+
+Next, we consider the representation $\Psi_{G(x,y,z,w)}$.
 In the next step of embedding, for each $x_i$, we find $y_i$ ,$z_i$, $w_i$ and $f$ such that

### 2019-02-06 Draft/draft.tex
Honghao: finished rewriting sec. 5.1

@@
 
+% Comments
+\def\carl#1{{\color{blue} #1 -Carl}}
+\newcommand{\hf}[1]{\textcolor{red}{#1}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \renewcommand\Affilfont{\itshape\small}
-
-\def\carl#1{{\color{blue} #1 -Carl}}
 
@@
 We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n_r(x)$.
-In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_{G(x)}$ for the group 
-\begin{align}
-	G(x) = \ip{ \{x_i\}_{i=1}^{n_r(x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
+In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_1$ for the group 
+\begin{align}
+	G_r(x) = \ip{ \{x_i\}_{i=1}^{n_r(x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
 \end{align}
 where details of $C_r$ can be found in the appendices. 
-Note that the relation $uxu^{-1} = x^2$ is embedded in the conjugation relations in $C_r$.
-Building on $\Psi_{G(x)}$, we can construct
-the representation $\Psi_{\Gamma(\LS_r)}$ for the solution group $\Gamma(\LS_r)$.
+Note that the relation $uxu^{-1} = x^r$ is embedded in the conjugation relations in $C_r$.
+Building on $\Psi_1$, we can construct 
+the representation $\Psi_{\LS_r}$ for the solution group $\Gamma(\LS_r)$.
 
 Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
-the observables $A_1 = B_1 = \Psi_{G(x)}(x_1)$ and $A_2 = B_2 = \Psi_{G(x)}(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows
+the observables $A_1 = B_1 = \Psi_1(x_1)$ and $A_2 = B_2 = \Psi_1(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows
 %\begin{align}
@@
 \begin{align}
-	A_1 = B_1 = \Psi_{G(x)}(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
-	A_2 = B_2 = \Psi_{G(x)}(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
-\end{align}
-It can be checked that $X = \Psi_{G(x)}(x_1x_2) = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ 
+	A_1 = B_1 = \Psi_1(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
+	A_2 = B_2 = \Psi_1(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
+\end{align}
+It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ 
 The relation $uxu^{-1} = x^r$ and $X$ determine that 
 \begin{align}
-	U =\Psi_{G(x)}(u) = \Psi_{G(x)}(x_3x_4) =  \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.
+	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.
 \end{align}
@@
 the commutativity between $U$ and $B_2$, so we prove the commutation relation first and
-then give $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$.
+then give $\Psi_1(x_3)$ and $\Psi_1(x_4)$.
 The commutation relation can be checked as follows,
@@
 %\end{align}
-The decomposition of $U$ into $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$ is similar to the decomposition of $X$.
+The decomposition of $U$ into $\Psi_1(x_3)$ and $\Psi_1(x_4)$ is similar to the decomposition of $X$.
 Since $u$ has order $d-1$, we can find an eigenbasis $\{ \ket{u_i} \}_{i=0}^{d-2}$ such that the eigen-decomposition of $U$ is
@@
 \end{align} 
-then $\Psi_{G(x)}(x_3)$ and $\Psi_{G(x)}(x_4)$ are  
-\begin{align*}
-	A_3 = B_3 =\Psi_{G(x)}(x_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
+then $\Psi_1(x_3)$ and $\Psi_1(x_4)$ are  
+\begin{align*}
+	A_3 = B_3 =\Psi_1(x_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
 	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
-	A_4 = B_4  =\Psi_{G(x)}(x_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
+	A_4 = B_4  =\Psi_1(x_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
 	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right).
@@
 \begin{align}
-	\Psi_{G(x)}(x_5) = \Psi_{G(x)}(x_1)\Psi_{G(x)}(x_2) \Psi_{G(x)}(x_1).
-\end{align}
-
-Next, we consider the representation $\Psi_{G(x,y,z,w)}$.
-In the next step of embedding, for each $x_i$, we find $y_i$ ,$z_i$, $w_i$ and $f$ such that
-$x_i = y_iz_i = fw_i$. We demonstrate how this splitting is done by pick $x_1$ as an example, 
-which is mapped to $B_1$ in the previous step. Now we map $x_1$ to $B_1'$ which is
-\begin{align}
-	B_1' = \begin{pmatrix}
-	B_1 & 0 \\
-	0 & B_1
-	\end{pmatrix},
-\end{align}
-then $y_1$, $z_1$, $w_1$ and $f$ are mapped to
-\begin{align}
-y_1 \to 
-\begin{pmatrix}
-B_1 & 0\\
+	\Psi_1(x_5) = \Psi_1(x_1)\Psi_1(x_2) \Psi_1(x_1).
+\end{align}
+
+Next, we consider the representation $\Psi_2$ for the group 
+\begin{align*}
+	G(x,y,z,w) = \ip{ \{x_i, w_i, y_i, z_i\}_{i=1}^{n_r(x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r} :&\text{all elements are of order $2$},\\
+	&x_i = y_iz_i = fw_i,\; fy_if =z_i \text{ for } i= 1 \dots n_r(x) \\
+	&g_{jk}y_j z_k = e,\; w_iy_jw_i = z_k \text{ for all } (i,j,k)\in C_r}.
+\end{align*}
+The representation $\Psi_2$ of $G(x,y,z,w)$ should satisfy the condition that for each $x_i$, 
+$\Psi_2(x_i) = \Psi_2(y_i)\Psi_2(z_i) = \Psi_2(f)\Psi_2(w_i)$. We demonstrate how this representation is constructed 
+for $x_i$, $y_i$, $z_i$, $w_i$ and $f$ where $i = 1 \dots n_r(x)$.
+Building on $\Psi_1$, we have $\Psi_2(x_i) = \Psi_1(x_i) \oplus \Psi_1(x_i)$, then
+$y_i$, $z_i$, $w_i$ and $f$ are mapped to
+\begin{align*}
+\Psi_2(y_i) = 
+\begin{pmatrix}
+\Psi_1(x_i) & 0\\
 0 & \1
@@
 &&
-z_1 \to
+\Psi_2(z_i) \to
 \begin{pmatrix}
 \1 & 0\\
-0 & B_1
+0 & \Psi_1(x_i)
 \end{pmatrix},
 \\
-w_1 \to 
-\begin{pmatrix}
-0 & B_1\\
-B_1 & 0
+\Psi_2(w_i) = 
+\begin{pmatrix}
+0 & \Psi_1(x_i)\\
+\Psi_1(x_i) & 0
 \end{pmatrix},
 &&
-f \to
+\Psi_2(f) \to
 \begin{pmatrix}
@@
 \end{pmatrix}.
-\end{align}
-
-The last step of embedding follows the same manner as we double the dimension of the operators again.
-For example, $y_1$ is mapped to $B_1 \oplus \1 \oplus B_1 \oplus \1$ and $z_1$ is mapped to 
-$\1 \oplus B_1 \oplus \1 \oplus B_1$, so effectively, $x_1$ is mapped to $B_1^{\oplus 4}$.
-\footnote{Details of this step of embedding can be found in proof of Proposition~$4.2$ in Ref.~\cite{slofstra2017}.}
-
-In the end, we determine the shared state.
-The optimal correlation for $\CHSH_X$ uses state 
-$\ket{\psi} = \frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$, 
-so the shared state for $\G$ is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$.
+\end{align*}
+It can be easily checked that the order-$2$ generators are mapped to order-$2$ operators and
+the relations satisfied by the generators are preserved.
+For each $g_{jk}$ where $(i,j,k) \in C_r$, $\Psi_2(g_{jk}) = \Psi_2(y_j)\Psi_2(z_k)$ following
+their defining relations.
+
+The group $G_r(x,y,z,w)$ is embedded in $\Gamma(\LS_r)$ by replacing the conjugacy relations 
+by linear relations. The new generators are $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{n_r(x)}
+\cup \{\{y_{K,k}\}_{k=1}^7\}_{K \in C_r}$. How the new linear relations can embed the conjugacy relations 
+in $G_r(x,y,z,w)$ can be found in the appendices. Now we define the representation $\Psi_{\LS_r}$ of
+$\Gamma(\LS_r)$. For any generator $a \in \{x_i, w_i, y_i, z_i\}_{i=1}^{n_r(x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r}$,
+\begin{align}
+	\Psi_{\LS_r}(a) = \Psi_2(a) \oplus \Psi_2(a) = \Psi_1(a)^{\oplus 4}.
+\end{align}
+For generators $\{y_{F_j,k}\}_{k=1}^7\}_{j=1}^{n_r(x)}$,
+\begin{align*}
+	\Psi_{\LS_r}(y_{F_j,1}) = 
+	\begin{pmatrix}
+		0 & \Psi_2(f) \\
+		\Psi_2(f) & 0
+	\end{pmatrix},
+	&&
+	\Psi_{\LS_r}(y_{F_j,2}) = 
+	\begin{pmatrix}
+		0 & \1\\
+		\1 & 0
+	\end{pmatrix},\\
+	\Psi_{\LS_r}(y_{F_j,3}) = 
+	\begin{pmatrix}
+		0 & \Psi_2(y_j) \\
+		\Psi_2(y_j) & 0
+	\end{pmatrix},
+	&&
+	\Psi_{\LS_r}(y_{F_j,4}) = 
+	\begin{pmatrix}
+		0 & \Psi_2(y_jf) \\
+		\Psi_2(fy_j) & 0
+	\end{pmatrix},\\
+	\Psi_{\LS_r}(y_{F_j,5}) = 
+	\begin{pmatrix}
+		 \Psi_2(fy_jf) & 0\\
+		  0 & \Psi_2(f)
+	\end{pmatrix},
+	&&
+	\Psi_{\LS_r}(y_{F_j,6}) = 
+	\begin{pmatrix}
+		 \Psi_2(y_jz_j) & 0\\
+		 0 & \1
+	\end{pmatrix},\\
+	\Psi_{\LS_r}(y_{F_j,7}) = 
+	\begin{pmatrix}
+		 \Psi_2(y_j) & 0\\
+		 0 & \Psi_2(z_j)
+	\end{pmatrix}.
+\end{align*}
+For generators $\{\{y_{K,k}\}_{k=1}^7\}_{K=(k_1,k_2,k_3) \in C_r}$,
+\begin{align*}
+	\Psi_{\LS_r}(y_{K,1}) = 
+	\begin{pmatrix}
+		0 & \Psi_2(w_{k_1}) \\
+		\Psi_2(w_{k_1}) & 0
+	\end{pmatrix},
+	&&
+	\Psi_{\LS_r}(y_{F_j,2}) = 
+	\begin{pmatrix}
+		0 & \1\\
+		\1 & 0
+	\end{pmatrix},\\
+	\Psi_{\LS_r}(y_{F_j,3}) = 
+	\begin{pmatrix}
+		0 & \Psi_2(y_{k_2}) \\
+		\Psi_2(y_{k_2}) & 0
+	\end{pmatrix},
+	&&
+	\Psi_{\LS_r}(y_{F_j,4}) = 
+	\begin{pmatrix}
+		0 & \Psi_2(y_{k_2}w_{k_1}) \\
+		\Psi_2(w_{k_1}y_{k_2}) & 0
+	\end{pmatrix},\\
+	\Psi_{\LS_r}(y_{F_j,5}) = 
+	\begin{pmatrix}
+		 \Psi_2(w_{k_1}y_{k_2}w_{k_1}) & 0\\
+		  0 & \Psi_2(w_{k_1})
+	\end{pmatrix},
+	&&
+	\Psi_{\LS_r}(y_{F_j,6}) = 
+	\begin{pmatrix}
+		 \Psi_2(y_{k_2}z_{k_3}) & 0\\
+		 0 & \1
+	\end{pmatrix},\\
+	\Psi_{\LS_r}(y_{F_j,7}) = 
+	\begin{pmatrix}
+		 \Psi_2(y_{k_2}) & 0\\
+		 0 & \Psi_2(z_{k_3})
+	\end{pmatrix}.
+\end{align*}
+
+In the end, to compensate the enlarged Hilbert space, the shared state is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$,
+where $\ket{\psi} = \frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{i}\ket{i}$.
+At the same time, the observables for the extended weighted CHSH test are mapped to four copies of themselves. 
 \end{proof}

### 2019-02-07 Draft/draft.tex
Honghao: modified the proofs of Prop.11 and Prop.13

@@
 
+% Group
+\newcommand{\Zd}{\Z_d^{\times}}
+
 % Identity operator
@@
 \newcommand{\tB}{\tilde{B}}
+\newcommand{\tZ}{\tilde{Z}}
 \newcommand{\tW}{\tilde{W}}
@@
 $d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
-$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
-$\Z_d^\times = \{1,2\dots d-1\}$. \textcolor{red}{When the prime number $d$ has multiple primitive roots,
+$r$ is the generator of the multiplicative group of integers modulo $d$, $\Zd$ where
+$\Zd = \{1,2\dots d-1\}$. \textcolor{red}{When the prime number $d$ has multiple primitive roots,
 we always work with the smallest one.}
@@
 	Let $\mu = \arctan(1/\alpha)$ for some $\alpha$.
-	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
-	violation of  $\I_{\alpha}$, then $\tilde{B}_0\tilde{B}_1$ has eigenvalues $e^{i2\mu}$ and $e^{-i2\mu}$.  \carl{Make clear
+	If a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
+	violation of  $\I_{\alpha}$, then \hf{the only eigenvalues of $\tilde{B}_0\tilde{B}_1$ on the support of 
+	$\tilde{\rho}_B = \Tr_A(\ketbra{\tpsi}{\tpsi})$
+	are $e^{i2\mu}$ and $e^{-i2\mu}$.}  \carl{Make clear
 	that we mean that these are the only eigenvalues.}
@@
 \begin{proof}[Proof of \cref{prop:2d-subspace}]
-	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we know
-	$\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu)$ is a binary observable. \textcolor{red}{HF: Do we need to justify it?}  \carl{Yes,
-	you should say more specifically where that is proved.}
+	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we define
+	\begin{align*}	
+	\tilde{Z}_A = \tA_1, &&
+	\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu).
+	\end{align*}
+	Substituting $\epsilon = 0$ into \cref{eq:zazb} we know that 
+	\begin{align}
+		\tZ_B \ket{\tpsi} = \tZ_A \ket{\psi}.
+	\end{align}
+	Using this relation, we get
+	\begin{align}
+		\tZ_B^2\ket{\tpsi} = \tZ_B \tZ_A\ket{\tpsi} = \tZ_A \tZ_B \ket{\tpsi} = \tZ_A^2 \ket{\tpsi} = \ket{\tpsi},
+	\end{align}
+	where we also use the facts that $\tZ_A$ and $\tZ_B$ commute and $\tZ_A^2 = A_1^2 = \1$.
+	Hence we can conclude that $\tZ_B^2 =\1$ on $\supp(\tilde{\rho}_B)$.
 	Expanding $\tilde{Z}_B^2$ we get
@@
 	\end{align}
-	Observe that $(\tB_1\tB_2)^\dagger = \tB_2\tB_1$ and 
-	$(\tB_2\tB_1)(\tB_1\tB_2) = \tB_2\1\tB_2 = \1$, then we can conclude that $\tB_1\tB_2$ is unitary.  \carl{(It's a product
-	of unitaries, so that step is immediate.)}
-	Suppose the eigen-decomposition of $\tB_1\tB_2$ is
+	\hf{Since $\tB_1\tB_2$ is the product of two unitaries,}
+	we can assume the eigen-decomposition of $\tB_1\tB_2$ is
 	\begin{align}
@@
 	\end{align*}
-	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.  \carl{Good proof (if you fill in the step at
-	the beginning).}
-
+	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.	
 %	\begin{align}
@@
 \end{align}
-It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ 
+It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 
 The relation $uxu^{-1} = x^r$ and $X$ determine that 
 \begin{align}
-	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.
-\end{align}
+	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i \in \Zd} \ketbra{x_{r^{-1}i}}{x_i},
+\end{align}
+\hf{where $r^{-1}$ is the multiplicative inverse of $r$ in $\Zd$.
+All the multiplications done on the label $i$ of the state $\ket{x_i}$ are within the group $\Zd$.}
 The first step of the embedding procedure in the proof of \cref{prop:embed} requires
@@
 \begin{align}
-	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_{(d-i)/r \pmod{d}}}.
-\end{align}
-Let $i_1 = i/r \pmod{d}$ and $i_2  = (d-i)/r \pmod{d}$, then
-\begin{align*}
-	i_1 + i_2 \equiv& \frac{i}{r} + \frac{d-i}{r} \pmod{d} \\
-	\equiv& \frac{d}{r} \pmod{d}.
-\end{align*}
-Suppose $d/r \pmod{d} \equiv x$ for some integer $x$, then
-\begin{align}
-	rx \equiv d \pmod{d}.
-\end{align}
-Since $d$ is a odd prime number and $r < d$, then $r$ cannot divide $d$, so $x = 0$ or $d$.
-Considering the fact that $1 \leq i_1 \leq d-1$ and $1 \leq i_2 \leq d-1$, we know $x = i_1+i_2 = d$.
+	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}}.
+\end{align}
+Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then
+\begin{align*}
+	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .
+\end{align*}
+Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then
+\begin{align}
+	rx \equiv d \pmod{d}
+\end{align}
+Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.
 Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
-Now suppose for $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_i'}{x_{d-i'}}U\ct$,
-it means that $i/r \equiv i'/r \pmod{d}$, which further implies that $i = i'$.
-To conclude, conjugation by $U$ only permutes the terms of $B_2$, so
+Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
+it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
+What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so
 \begin{align}
@@
 \begin{align}
-	&\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
+	\label{eq:zazb} &\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
 	&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\

### 2019-02-08 Draft/draft.tex
Honghao: expanded Appendix A to add more precise error bound

@@
 
+% TikZ
+\usepackage{tikz}	
+\usetikzlibrary{backgrounds,fit,decorations.pathreplacing}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\tB}{\tilde{B}}
+\newcommand{\tX}{\tilde{X}}
 \newcommand{\tZ}{\tilde{Z}}
@@
 	\begin{align}
-		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha+\frac{1}{\alpha}) \sqrt{\epsilon})
+		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha^2+\frac{1}{\alpha}) \sqrt{\epsilon})
 	\end{align}
@@
 %========================================
+This proof follows the same line of argument in Appendix A of Ref.~\cite{bamps2015}.
+We first find two sum-of-square decompositions of $2\sqrt{\alpha^2+1} \1 - \I_\alpha$.
+The decompositions allow us to determine some key relations between Alice and Bob's observables
+and their shared state, which will be used to draw the closeness conclusion.
+
 \begin{proof}
-Following the techniques developed in Ref.~\cite{bamps2015}, the first step is to find a sum-of-square decomposition of 
+The first step is to find a sum-of-square decomposition of 
+the following Bell expression
 \begin{align}
@@
 
-Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_{y \in [2]}\}$ achieves that 
-$\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$.
+Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x=1,2}, \{\tilde{B}_{y }\}_{y=1,2}$ achieves that 
+$\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$ where
+$\bar{\I}_\alpha$ is expressed with $\tA_x$ and $\tB_y$.
 The second step is to establish bounds of the following form
@@
 	\label{eq:zazb} &\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
-	&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\
-	&\|(\tilde{X}_A-\tilde{X}_B)\ket{\psi}\| \leq c_3 \sqrt{\epsilon}\\
-	&\|(\tilde{Z}_A\tilde{X}_A+\tilde{X}_A\tilde{Z}_A)\ket{\psi}\| \leq c_4 \sqrt{\epsilon}.
-\end{align}
-Now we write $s = \sin(\mu)$, $c = \cos(\mu)$ and define
-\begin{align*}
-	S_1 &= \frac{\sqrt{s}}{2} \bar{\I}_\alpha, \quad
+	\label{eq:xzxz}&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\
+	\label{eq:xaxb}&\|(\tilde{X}_A-\tilde{X}_B)\ket{\psi}\| \leq c_3 \sqrt{\epsilon}\\
+	\label{eq:anticom} &\|(\tilde{Z}_A\tilde{X}_A+\tilde{X}_A\tilde{Z}_A)\ket{\psi}\| \leq c_4 \sqrt{\epsilon}.
+\end{align}
+Going back to the sum-of-square decomposition, we write $s = \sin(\mu)$, $c = \cos(\mu)$ and define
+\begin{align*}
+	S_1 = \frac{\sqrt{s}}{2} \bar{\I}_\alpha, &&
 	S_2 = \sqrt{s}c(\tilde{Z}_A\tilde{X}_B+\tilde{X}_A\tilde{Z}_B),\\
-	S_3 &= \frac{c}{\sqrt{s}}(\tilde{Z}_A-\tilde{Z}_B),\quad
+	S_3 = \frac{c}{\sqrt{s}}(\tilde{Z}_A-\tilde{Z}_B), &&
 	S_4 = \sqrt{s}(\tilde{X}_A-\tilde{X}_B)
 \end{align*}
-then $\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2$ and $\bra{\psi}\bar{\I}_\alpha \ket{\psi} \leq \epsilon$ implies that 
+then 
+\begin{align}
+\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2
+\end{align}
+ and $\bra{\psi}\bar{\I}_\alpha \ket{\psi} \leq \epsilon$ implies that 
 $\bra{\psi}S^2_i \ket{\psi} \leq \epsilon$ and $\|S_i \ket{\psi} \| \leq \sqrt{\epsilon}$ for $i = 1,2,3,4$.
-We can easily check that 
+The coefficients $c_1$, $c_2$ and $c_3$ in \cref{eq:zazb,eq:xzxz,eq:xaxb} can be determined from $S_1$,$S_2$ and $S_3$ as
 \begin{align*}
@@
 
-With appropriate substitutions, the rest of the proof follows the same derivation as that in Appendix A of Ref.~\cite{bamps2015},
-so we omit it here. The dependence of the error term on $\alpha$ comes from the fact that 
-\begin{align}
-\frac{1}{\cos(\arctan(1/\alpha)) \sin^{1/2}(\arctan(1/\alpha))} = \frac{1}{\alpha}+\frac{3}{4}\alpha - O(\alpha^3).
-\end{align}
-
+Now we introduce the isometries $\Phi_A$ and $\Phi_B$ mentioned in the statement of the theorem.
+They are the same as the ones used in Ref.~\cite{bamps2015}.
+To construct $\Phi_A$ and $\Phi_B$ we need to regularize $\tZ_B$ and $\tX_B$ to make sure the corresponding operations 
+are unitaries in the isometries. We define $\tZ_B^\ast$ to be the operator obtained from $\tZ_B$ by changing all the $0$-eigenvalues
+to $1$ and 
+\begin{align*}
+\tZ_B' = \tZ_B^\ast |\tZ_B|^{-1}.
+\end{align*}
+In a similar way, we define $\tX_B^\ast$ and $\tX_B'$.
+On Alice's side, since $\tZ_A$ and $\tX_A$ are unitaries already,
+we define
+\begin{align}
+	\tZ_A' = \tZ_A, && \tX_A' = \tX_A.
+\end{align}
+The isometries are illustrated in the figure below.
+\begin{figure}[H]
+\center
+        \begin{tikzpicture}[thick]
+        %
+        % `operator' will only be used by Hadamard (H) gates here.
+        % `phase' is used for controlled phase gates (dots).
+        % `surround' is used for the background box.
+        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
+        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
+        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
+        %
+        % Bracket
+        \draw[decorate,decoration={brace,mirror},thick] (0,-1) to
+    	node[midway,left] (bracket1) {$\ket{\tpsi}$}
+    	(0,-2);
+        % Qubits
+        \node at (0,0) (q1) {$\ket{0}$};
+        \node at (0,-1) (q2) {};
+        \node at (0,-2) (q3) {};
+        \node at (0,-3) (q4) {$\ket{0}$};
+        %
+        % Column 1
+        \node[operator] (op11) at (1,0) {H} edge [-] (q1);
+        \node[operator] (op14) at (1,-3) {H} edge [-] (q4);
+        %
+        % Column 3
+        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
+	\node[operator] (op22) at (2,-1) {$\tZ_A'$} edge [-] (q2);
+	\node[operator] (op23) at (2, -2) {$\tZ_B'$} edge[-] (q3);
+        \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
+        \draw[-] (phase11) -- (op22);
+        \draw[-] (phase14) -- (op23);
+        %
+        % Column 4
+        \node[operator] (op31) at (3,0) {H} edge [-] (phase11);
+        \node[operator] (op34) at (3,-3) {H} edge [-] (phase14);
+        %
+        % Column 5
+        \node[phase] (phase21) at (4,0) {} edge [-] (op31);
+	\node[operator] (op42) at (4,-1) {$\tX_A'$} edge [-] (op22);
+	\node[operator] (op43) at (4, -2) {$\tX_B'$} edge[-] (op23);
+        \node[phase] (phase24) at (4,-3) {} edge [-] (op34);
+        \draw[-] (phase21) -- (op42);
+        \draw[-] (phase24) -- (op43);
+        %
+        % Column 6
+        \node (end2) at (5,-1) {} edge [-] (op42);
+        \node (end3) at (5,-2) {} edge [-] (op43);
+        %
+        % Bracket
+        \draw[decorate,decoration={brace},thick] (5,-1) to
+    	node[midway,right] (bracket) {$\ket{junk}$}
+    	(5,-2);
+        %
+        % Column 7
+        \node (end1) at (6.5,-0.5) {} edge [-] (phase21);
+        \node (end4) at (6.5,-2.5) {} edge [-] (phase24);
+        % Dashed line
+        \draw[loosely dotted] (0,-1.5) -- (5,-1.5);
+        % Bracket
+        \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
+    	node[midway,right] (bracket2) {$\frac{\ket{00}+\ket{11}}{\sqrt{2}}$}
+    	(6.5,-2.5);
+        %
+        % Background Box
+        \begin{pgfonlayer}{background} 
+        \node[surround] (background) [fit = (q1) (op14) (bracket1)(bracket2)] {};
+        \end{pgfonlayer}
+        %
+        \end{tikzpicture}
+	\caption{The isometries $\Phi_A$ and $\Phi_B$.}
+\end{figure}
+To bound $e_{xy} := \norm{ (\Phi_A\x\Phi_B) (\tA_x \x \tB_y) \ket{\tpsi} - \ket{junk} \x (A_x\x B_y) \ket{\EPR{2}}}$,
+there are some intermediate steps. Since the derivations are the same as in Ref.~\cite{bamps2015}, 
+we only record the key relations here.
+\begin{align}
+	&\norm{(\tZ_B' - \tZ_B) \ket{\tpsi}} \leq c_1 \sqrt{\epsilon},\\
+	&\norm{(\tZ_B' - \tZ_A') \ket{\tpsi}} \leq 2c_1 \sqrt{\epsilon}, \\
+	&\norm{(\tX_B' - \tX_B) \ket{\tpsi}} \leq \frac{c+1}{s^{3/2}} \sqrt{\epsilon} := c_5\sqrt{\epsilon},\\
+	&\norm{(\tX_B'\tZ_B'+ \tZ_B'\tX_B')\ket{\tpsi}} \leq [2c_1 + 2c_3 + 2c_5 + (\sqrt{2}+1/c)(2c_1+c_4)]\sqrt{\epsilon}
+	:= c_6 \sqrt{\epsilon}.
+\end{align}
+Then we can calculate that 
+\begin{align}
+	&e_{00} = e_{10} = 2c_6 \sqrt{\epsilon}\\
+	&e_{20} = 2(c_4 + c_6) \sqrt{\epsilon}\\
+	&e_{01} = e_{02} = e_{11} = e_{12} = [c(c_1)+s(2c_4 + c_5) + 2c_6]\sqrt{\epsilon}\\
+	&e_{21} = e_{22} = [2c_4 + c(c_1)+s(2c_4 + c_5) + 2c_6]\sqrt{\epsilon},
+\end{align}
+so an upper bound of the error is that
+\begin{align}
+	\forall x,y \in \{0,1,2\}, e_{xy} \in O((\frac{1}{cs^{1/2}} + \frac{1}{s^{3/2}})\sqrt{\epsilon}).
+\end{align}
+The dependence of the error term on $\alpha$ comes from the fact that 
+\begin{align}
+&\frac{1}{\cos(\arctan(1/\alpha)) \sin^{1/2}(\arctan(1/\alpha))} = \frac{1}{\alpha}+\frac{3}{4}\alpha - O(\alpha^3),\\
+&\frac{1}{\sin^{3/2}(\arctan(1/\alpha))} = 1 + \frac{3}{4}\alpha^2 - O(\alpha^4).
+\end{align}
 \end{proof}

### 2019-02-22 Draft/draft.tex
Honghao: more on robustness
Honghao: a more promising way to apply the isometry; a more complete self-testing proof

@@
 \hline
-\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
+\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{\sin^2(\pi/d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
 & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
+&$b=1$ & $\frac{\sin^2(\pi/d)}{d-1}$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
 &  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
 \hline
-\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
+\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{\sin^2(\pi/d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
 $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
+&$b=1$ & $\frac{\sin^2(\pi/d)}{d-1}$ & $\frac{\cos^2(\pi/d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
 $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
@@
 	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
-	&B_1^0|_V = \left( \cos(\frac{\pi}{2d})\ket{u_1} + \sin(\frac{\pi}{2d})\ket{u_{d-1}}\right)
-	\left( \cos(\frac{\pi}{2d})\bra{u_1} + \sin(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
-	&B_1^1|_V = \left( \sin(\frac{\pi}{2d})\ket{u_1} - \cos(\frac{\pi}{2d})\ket{u_{d-1}}\right)
-	\left( \sin(\frac{\pi}{2d})\bra{u_1} - \cos(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
-	&B_2^0|_V = \left( \cos(\frac{\pi}{2d})\ket{u_1} - \sin(\frac{\pi}{2d})\ket{u_{d-1}}\right)
-	\left( \cos(\frac{\pi}{2d})\bra{u_1} - \sin(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
-	&B_2^1|_V = \left( \sin(\frac{\pi}{2d})\ket{u_1} + \cos(\frac{\pi}{2d})\ket{u_{d-1}}\right)
-	\left( \sin(\frac{\pi}{2d})\bra{u_1} + \cos(\frac{\pi}{2d})\bra{u_{d-1}}\right).
+	&B_1^0|_V = \left( \cos(\frac{\pi}{d})\ket{u_1} + \sin(\frac{\pi}{d})\ket{u_{d-1}}\right)
+	\left( \cos(\frac{\pi}{d})\bra{u_1} + \sin(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
+	&B_1^1|_V = \left( \sin(\frac{\pi}{d})\ket{u_1} - \cos(\frac{\pi}{d})\ket{u_{d-1}}\right)
+	\left( \sin(\frac{\pi}{d})\bra{u_1} - \cos(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
+	&B_2^0|_V = \left( \cos(\frac{\pi}{d})\ket{u_1} - \sin(\frac{\pi}{d})\ket{u_{d-1}}\right)
+	\left( \cos(\frac{\pi}{d})\bra{u_1} - \sin(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
+	&B_2^1|_V = \left( \sin(\frac{\pi}{d})\ket{u_1} + \cos(\frac{\pi}{d})\ket{u_{d-1}}\right)
+	\left( \sin(\frac{\pi}{d})\bra{u_1} + \cos(\frac{\pi}{d})\bra{u_{d-1}}\right).
 \end{align*}
@@
 The last step is to construct the local isometries $\Phi_A$ and $\Phi_B$ that can produce $\ket{\EPR{d-1}}$ from $\ket{\psi}$.
-We give steps about how $\Phi_A$ and $\Phi_B$ works.
-Since the subspaces $W_j$'s are orthogonal, Alice and Bob can map state $\ket{\psi}$ to the state 
-\begin{align}
-	\ket{\psi'} = \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{j}_A\ket{j}_B.
-\end{align}
-Note that we added subscript $A$ and $B$ to stress the subsystems holden by Alice and Bob respectively.
-Since $\ket{x_{i,j}}$ is orthogonal to $\ket{x_{i',j'}}$ for $i\neq i'$ or $j \neq j'$, we further assume that there exists 
-a unitary $O$ such that $O\ket{x_{i,j}} = O\ket{x_{i,j+1}}$ for all $i$ and $j$, but when $j = N$, $O\ket{x_{i,N}} = \ket{x_{i,1}}$.
-Then controlled by the appended register, Alice and Bob can apply $(O\ct)^j$ to the original system
-and $\ket{\psi'}$ is mapped to
-\begin{align}
-	 &\sum_{i=1}^{d-1}\sum_{j=1}^m c_j [(O\ct)^j\ket{x_{i,j}}_A] \x [(O\ct)^j\ket{x_{i,j}}_B] \x \ket{j}_A\ket{j}_B\\
-	 = &\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,1}}_A\ket{x_{i,1}}_B \ket{j}_A\ket{j}_B\\
-	 =  &\frac{1}{\sqrt{d}} \sum_{i=1}^{d-1} \ket{x_{i,1}}_A\ket{x_{i,1}}_B \x \sum_{j=1}^m \sqrt{d}c_j \ket{j}_A\ket{j}_B
-\end{align}
-After relabelling $\ket{x_{i,1}}$ as $\ket{i}$, we factor $\ket{\EPR{d-1}}$ out of $\Phi_A \x \Phi_B \ket{\psi}$.
+To help understanding, we draw a diagram to demonstrate the isometry first and then show
+how this isometry works.
+\begin{figure}[H]
+\center
+        \begin{tikzpicture}[thick]
+        %
+        % `operator' will only be used by Hadamard (H) gates here.
+        % `phase' is used for controlled phase gates (dots).
+        % `surround' is used for the background box.
+        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
+        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
+        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
+        %
+        % Bracket
+        \draw[decorate,decoration={brace,mirror},thick] (0,-1) to
+    	node[midway,left] (bracket1) {$\ket{\psi}$}
+    	(0,-2);
+        % Qubits
+        \node at (0,0) (q1) {$\ket{0}$};
+        \node at (0,-1) (q2) {};
+        \node at (0,-2) (q3) {};
+        \node at (0,-3) (q4) {$\ket{0}$};
+        %
+        % Column 1
+        \node[operator] (op11) at (1,0) {$QFT_d$} edge [-] (q1);
+        \node[operator] (op14) at (1,-3) {$QFT_d$} edge [-] (q4);
+        %
+        % Column 3
+        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
+	\node[operator] (op22) at (2,-1) {$X_A$} edge [-] (q2);
+	\node[operator] (op23) at (2, -2) {$X_B$} edge[-] (q3);
+        \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
+        \draw[-] (phase11) -- (op22);
+        \draw[-] (phase14) -- (op23);
+        %
+        % Column 4
+        \node[operator] (op31) at (3,0) {$QFT_d^{-1}$} edge [-] (phase11);
+        \node[operator] (op34) at (3,-3) {$QFT_d^{-1}$} edge [-] (phase14);
+        %
+        % Column 5
+        \node[phase] (phase21) at (4,0) {} edge [-] (op31);
+	\node[operator] (op42) at (4,-1) {$U_A$} edge [-] (op22);
+	\node[operator] (op43) at (4, -2) {$U_B$} edge[-] (op23);
+        \node[phase] (phase24) at (4,-3) {} edge [-] (op34);
+        \draw[-] (phase21) -- (op42);
+        \draw[-] (phase24) -- (op43);
+        %
+        % Column 6
+        \node (end2) at (5,-1) {} edge [-] (op42);
+        \node (end3) at (5,-2) {} edge [-] (op43);
+        %
+        % Bracket
+        \draw[decorate,decoration={brace},thick] (5,-1) to
+    	node[midway,right] (bracket) {$\ket{junk}$}
+    	(5,-2);
+        %
+        % Column 7
+        \node (end1) at (6.5,-0.5) {} edge [-] (phase21);
+        \node (end4) at (6.5,-2.5) {} edge [-] (phase24);
+        % Dashed line
+        \draw[loosely dotted] (0,-1.5) -- (5,-1.5);
+        % Bracket
+        \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
+    	node[midway,right] (bracket2) {$\ket{\EPR{d-1}}$}
+    	(6.5,-2.5);
+        %
+        % Background Box
+        \begin{pgfonlayer}{background} 
+        \node[surround] (background) [fit = (q1) (op14) (bracket1)(bracket2)] {};
+        \end{pgfonlayer}
+        %
+        \end{tikzpicture}
+	\caption{The isometries $\Phi_A$ and $\Phi_B$.}
+\end{figure}
+The isometry maps the state $\ket{\psi}$ in the following steps:
+\begin{enumerate}
+	\item Append $\ket{0}_A$ on Alice's side and $\ket{0}_B$ on Bob's side as control registers, and
+	the state becomes $\ket{\psi} \ket{0}_A \ket{0}_B$;
+	\item Apply $QFT_d$ to the control registers, and the state becomes
+	\begin{align}
+		\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \ket{\psi} \ket{k_1}_A \ket{k_2}_B;
+	\end{align}
+	\item Apply $X_A^{k_1}$ to Alice's share of $\ket{\psi}$ and $X_B^{k_2}$ to Bob's share controlled
+	by the control registers, and the state becomes
+	\begin{align}
+		&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1}X_A^{k_1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B\\
+		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1}\ket{x_{i,j}}_A X_B^{k_2}\ket{x_{i,j}}_B
+		\ket{k_1}_A \ket{k_2}_B\\
+		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1i+k_2i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
+		\ket{k_1}_A \ket{k_2}_B;
+	\end{align}
+	\item Apply $QFT_d^{-1}$ to the control registers, and the state becomes
+	\begin{align}
+		&\frac{1}{d^2} \sum_{l_1,l_2 =0}^{d-1}\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i-l_1)+k_2(i-l_2)} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
+		\ket{l_1}_A \ket{l_2}_B\\
+		=& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B;
+	\end{align}
+	\item Let $n_i$ satisfy the condition $r^{n_i} \equiv i \pmod{d}$, apply $U_A^{(i)} = U_A^{n_i}$ to Alice's share of $\ket{\psi}$ and $U_B^{(i)} = U_B^{n_i}$ to Bob's share controlled
+	by the control registers, and the state becomes
+	\begin{align}
+		&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B \\
+		=&\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i r^{-n_i} ,j}}_A \ket{x_{i r^{-n_i},j}}_B \ket{i}_A\ket{i}_B\\
+		=& \sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i i^{-1},j}}_A \ket{x_{i i^{-1},j}}_B \ket{i}_A\ket{i}_B\\
+		= &\left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \sum_{i=1}^{d-1} \ket{i}_A\ket{i}_B\\
+		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
+		\frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1}\ket{i}_A\ket{i}_B\\
+		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \ket{\EPR{d-1}},
+	\end{align}
+	where in the last line we used the fact that $\norm{\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B} = 1/\sqrt{d-1}$.
+\end{enumerate}
+
+If the initial state is $X_A\ket{\psi}$, the isometry maps the state as following
+\begin{align}
+	X_A\ket{\psi} \to &X_A\ket{\psi}\ket{0}_A\ket{0}_B\\
+	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
+	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A^{k_1+1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
+	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1+k_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
+		\ket{k_1}_A \ket{k_2}_B\\
+	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1-l_1)i+(k_2-l_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
+		\ket{l_1}_A \ket{l_2}_B\\
+	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B\\
+	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
+	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{i}_A\ket{i}_B\\
+	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
+		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\omega_d^i \ket{i}_A\ket{i}_B\\
+	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tX_A \ket{\EPR{d-1}},
+\end{align}
+where $\tX_A$ is the ideal $X$ operator.
+The case of $X_B\ket{\psi}$ is similar, so we omit it here.
+
+If the initial state is $U_A\ket{\psi}$, the isometry maps the state as following
+\begin{align}
+	U_A\ket{\psi} \to &U_A\ket{\psi}\ket{0}_A\ket{0}_B\\
+	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} U_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
+	= &\frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A\ket{x_{i,j}}_A\ket{x_{i,j}}_B
+		\ket{k_1}_A \ket{k_2}_B\\
+	= & \frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i r^{-1} ,j}}_A\ket{x_{i,j}}_B
+		\ket{k_1}_A \ket{k_2}_B\\
+	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1} \ket{x_{i r^{-1} ,j}}_A
+	X_B^{k_2}\ket{x_{i,j}}_B  \ket{k_1}_A \ket{k_2}_B \\
+	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1 i/r}\omega_d^{k_2i} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
+		\ket{k_1}_A \ket{k_2}_B\\
+	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i/r-l_1)}\omega_d^{(k_2(i-l_2)} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
+		\ket{l_1}_A \ket{l_2}_B\\
+	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j  \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B \ket{ir^{-1}}_A \ket{i}_B\\
+	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(ir^{-1})}\ket{x_{ir^{-1},j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
+	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{ir^{-1}}_A\ket{i}_B\\
+	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
+		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\ket{ir^{-1}}_A\ket{i}_B\\
+	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tU_A \ket{\EPR{d-1}},
+\end{align}
+where $\tU_A$ is the ideal $U$ operator on Alice's side.
+The derivation is similar when $U_B$ is applied, so we omit it here.
 \end{proof}

### 2019-02-27 Draft/draft.tex
Honghao: small fixes in the draft
Honghao: found an error in the self-testing, not sure how to fix it

@@
 \newcommand{\tZ}{\tilde{Z}}
+\newcommand{\tU}{\tilde{U}}
 \newcommand{\tW}{\tilde{W}}
@@
 \end{align}
+\textcolor{red}{If we express $\ket{j}$'s as $\ket{x_j}$'s, then we can find that 
+shared state is $\ket{\psi} = 1/2\sum_{j=0}^{d-2} e^{-ir^j\pi/d} (\ketbra{x_{r^j}}{x_{d-r^j}} + \ketbra{x_{d-r^j}}{x_{r^j}}$.}
 
@@
 onto the $\omega_d^{-1}$-eigenspace of $X_A$.
+\textcolor{red}{Here I assume that $\Pi_{V_1} \ket{\psi} = \ket{\psi}$ and $\Pi_{V_{d-1}} \ket{\psi} = \ket{\psi}$,
+but it is not true.}
 Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.

### 2019-02-27 Draft/draft.tex
Honghao: small fix

--- 2019-02-22 Draft/draft.tex
@@
 \end{align}
+\hl{If we express $\ket{j}$'s as $\ket{x_j}$'s, then we can find that 
+shared state is $\sum_{j=1}^{d-1} \ket{j}\ket{j} = \sum_{j=0}^{(d-1)/2} e^{-ij\pi/d} (\ketbra{x_{j}}{x_{d-j}} + \ketbra{x_{d-j}}{x_{j}}$.}
 
@@
 onto the $\omega_d^{-1}$-eigenspace of $X_A$.
+\hl{Here I assume that $\Pi_{V_1} \ket{\psi} = \ket{\psi}$ and $\Pi_{V_{d-1}} \ket{\psi} = \ket{\psi}$,
+but it is not true.}
 Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.

### 2019-03-14 Draft/draft.tex
Honghao: fix a typo
Honghao: find another problem of the self-test proof

--- 2019-02-22 Draft/draft.tex
@@
 \end{align}
+\hl{If we express $\ket{j}$'s as $\ket{x_j}$'s, then we can find that 
+shared state is}\\
+\hl{ $\sum_{j=1}^{d-1} \ket{j}\ket{j} = \sum_{j=0}^{(d-1)/2} e^{-ij\pi/d} (\ket{x_{j}}\ket{x_{d-j}} + \ket{x_{d-j}}\ket{x_{j}}$.}
 
@@
 onto the $\omega_d^{-1}$-eigenspace of $X_A$.
+\hl{Here what we need is that $\Pi_{V_1,A} \ket{\psi} = \Pi_{V_{d-1},B} \ket{\psi} = \Pi_{V_1,A}\Pi_{V_{d-1},B}\ket{\psi}$
+and $\Pi_{V_1,B} \ket{\psi} = \Pi_{V_{d-1},A} \ket{\psi} = \Pi_{V_1,B}\Pi_{V_{d-1},A}\ket{\psi}$.
+This is not proved because $\Pi_{V_1}$ and $\Pi_{V_{d-1}}$ are not in the strategy.}
 Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.
@@
 such that $\Pi_{V_i}$ is the projector onto the $\omega_d^i$-eigenspace of $X_A$,
+\hl{Actually, we are not sure about the containment between $\supp((U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)})$ and 
+$\supp(\Pi_{V_{d-1}})$, so we cannot say that $\Pi_{V_{d-1}} = (U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)}$.}
 and 
@@
 \begin{align*}
-	Z_A = A_1 &\quad X_A = A_2\\
-	Z_B = \frac{B_1+B_2}{2\cos(\mu)} &\quad X_B = \frac{B_1-B_2}{2\sin(\mu)},
+	&Z_A = A_1 && X_A = A_2\\
+	&Z_B = \frac{B_1+B_2}{2\cos(\mu)} && X_B = \frac{B_1-B_2}{2\sin(\mu)},
 \end{align*}

### 2019-03-31 Draft/draft.tex
Honghao: reorganized the Prelim section: put linear system game and nonlocal game part together and remove definitions of solution group and operator solution

@@
 \newcommand{\SVT}{SVT}
-\newcommand{\EPR}[1]{EPR^{(#1)}}
+\newcommand{\EPR}[1]{\Sigma^{(#1)}}
 \newcommand{\paulix}{\sigma_x}
@@
 \newcommand{\I}{\mathcal{I}}
+
+% Square root of epsilon
+\newcommand{\ep}{\epsilon}
+\newcommand{\se}{\sqrt{\epsilon}}
+\newcommand{\qe}{\epsilon^{1/4}}
+\newcommand{\sd}{\sqrt{d}}
+\newcommand{\sr}{\sqrt{r}}
+\newcommand{\qd}{d^{1/4}}
+
+% Approximately equatli
+\newcommand{\appd}[1]{\simeq_{#1}}
 
@@
 In order to accomplish our goal, we introduce new techniques for self-testing.
-First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
+First of all, we use a different variant of the weighted CHSH inequality, \hf{which was first introduced in \cite{acin2012}}, to enforce the eigenvalue of
 some unknown operator which is the product of two binary observables used in the weighted CHSH test.
-\carl{I think this game might have been defined in APM12, and if so we need to cite it.}
 The variant of the CHSH inequality that we use is not used in the self-testing literature before.
@@
 The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
-which is the core idea in all the previous self-testing results.
+which is the core idea in \hf{most of} the previous self-testing results.
 \carl{Are we sure about that ("all")?}
@@
 %========================================
+\textbf{Notations}.
 We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
-%We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.
-
+The maximally entangled state of local dimension $d-1$ for some prime $d$ is denoted by
+\begin{align}
+\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
+\end{align}
+The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
+We denote a Hilbert space by $\calH$. Note that we only work with finite Hilbert spaces in this work.
+When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
+$\calH_B$.
+The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, the Pauli operators
+are defined by
+\begin{align}
+	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
+\end{align}
+
+For quantum states and operators on different Hilbert spaces, we use subscripts to label them.
+For example, $O_A$ is an operator on Alice's side and $\ket{0}_{B}$ is a state on Bob's side. 
+The only exception is for projectors used in a quantum strategy defined below, where the subscript 
+is the input and the superscript is the output. For example, $A_x^a$ is Alice's projector for input $x$ and output $a$.
+Operators defined by the projectors follow the same convention. For example, $A_x := A_x^0 - A_x^1$.
+
+We use the following notation for the closeness between states.
+\begin{align}
+	\ket{u} \appd{\epsilon} \ket{v} \iff \norm{\ket{u} - \ket{v}} \leq \epsilon. 
+\end{align}
+Similarly, for $a,b \in \C$, we have
+$a \appd{\epsilon} b \iff \norm{a-b} \leq \epsilon$.
+
+\textbf{Number theory}.
 We use some basic number theory in our work. A primitive root of a prime number
-$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
-$r$ is the generator of the multiplicative group of integers modulo $d$, $\Zd$ where
-$\Zd = \{1,2\dots d-1\}$. \textcolor{red}{When the prime number $d$ has multiple primitive roots,
-we always work with the smallest one.}
-\carl{I'm not clear on what that last sentence means.  You just defined what a primitive root
-is --- are you changing the definition now?}
-
-The EPR pair of local dimension $d-1$ for some prime $d$ is denoted by
-\begin{align}
-\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{i = 0}^{d-2} \ket{ii}.
-\end{align}
-The superscript $(d-1)$ stresses the local dimension and we follow this convention through this paper.
-
-We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
-\begin{align}
-	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
-\end{align}
-where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
-and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
-definitions and notation for now.}
-Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
-unless otherwise specified, for example, the $k/r$ above.
-
-\textbf{The weighted CHSH inequality \cite{acin2012}.}
-The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
-In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
-on Hilbert space $\calH_A$ and $\calH_B$ respectively.  \carl{It needs to be clearer who Alice and Bob
-are --- perhaps you should put this subsection after the ``Nonlocal games'' subsection.}
-A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
-The weighted CHSH inequality is given by 
-\begin{align}
-	\label{eq:chsh_op}
-	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
-\end{align}
-where $\ip{A_xB_y}$ is the expectation value of of the observables.  \carl{Same here -- it's not clear enough
-what this means until the reader has seen the ``Nonlocal games'' subsection.}
-If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
-the weighted CHSH inequality.
-However, If they share entangled state $\ket{\psi}$, the maximal violation is 
-\begin{align}
-\label{eq:chsh_max}
- \I_\alpha \leq 2\sqrt{1+\alpha^2}.
-\end{align}
-\begin{definition}[Ideal strategy for $\I_\alpha$]
-	\label{def:ideal}
-	Define $\mu = \arctan(1/\alpha)$.
-	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
-	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
-	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
-\end{definition}
-\carl{Just to be complete, you should say what $\pauliz$ and $\paulix$ denote.}
-An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
-measurements up to isometry, 
-which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.
-
-\textbf{Nonlocal games}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
+$d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
+in the multiplicative group of integers modulo $d$, $\Zd$. Equivalently,
+$r$ is the generator of $\Zd$.
+
+%We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
+%\begin{align}
+%	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
+%\end{align}
+%where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
+%and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
+%definitions and notation for now.}
+%Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
+%unless otherwise specified, for example, the $k/r$ above.
+
+\textbf{Nonlocal games}. 
+The two players of a nonlocal game are Alice and Bob. Each of them is requested
 to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
@@
 
-A quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side, 
+A quantum strategy of a nonlocal game consists of projective measurements $\{\{A_x^a\}_a\}_x$ on Alice's side, 
 $\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
@@
 the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
+\hf{Addressed in the notation part. --H.F}
 Then Alice and Bob's quantum strategy produces the correlation
@@
 where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
-%Note that we may use the term behaviour and correlation interchangeably.
-%The value of a strategy is given by
-%\begin{align}
-%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
-%\end{align}
-
-The main contribution of our work is the construction of a correlation, which is the combination of 
-the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
-and the optimal correlation to violate the weighted CHSH inequality.  \carl{The reader does not 
-know yet what a linear system game is, so this comment is more confusing than helpful.}
-The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
-primitive root. 
-In the next part, we introduce the definition of self-testing, the definition of linear system game, 
-and its operator solution, 
-following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
-
-\carl{Before the next definition, you should define what a ``correlation'' is.}
-\begin{definition}[Self-testing]
-	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
-	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
-	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
-	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
-	such that 	
-	\begin{align*}
-		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
-	\end{align*}
-\end{definition}
+A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
+
 \begin{definition}[Linear system game]
@@
 
-It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
-satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
-operator solution in the following sense.  \carl{There's a missing reference here?}
-\begin{definition}[Operator solution of a linear system]
-\label{def:op_sol}
-	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
-	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
-	be best to just state the definition for finite dimensions only.)}
-	\begin{enumerate}
-		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
-		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
-		\item for all $1 \leq i \leq m$,
-		\begin{align*}
-			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
-		\end{align*}
-	\end{enumerate}
-	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
-	solution in which the Hilbert space is finite-dimensional.
+%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
+%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
+%operator solution in the following sense.  \carl{There's a missing reference here?}
+%\begin{definition}[Operator solution of a linear system]
+%\label{def:op_sol}
+%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
+%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
+%	be best to just state the definition for finite dimensions only.)}
+%	\begin{enumerate}
+%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
+%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
+%		\item for all $1 \leq i \leq m$,
+%		\begin{align*}
+%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
+%		\end{align*}
+%	\end{enumerate}
+%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
+%	solution in which the Hilbert space is finite-dimensional.
+%\end{definition}
+%Perfect quantum strategies can be extracted from operator solutions and vice versa.
+%Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
+%over $\Z_2$, which is called the solution group.
+%\begin{definition}[Solution group of a linear system game]
+%	\label{def:presentation}
+%	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
+%	is the group
+%	\begin{align*}
+%		\Gamma(H,c) := \ip{
+%		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
+%				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
+%				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
+%				} .
+%	\end{align*}
+%\end{definition}
+%\carl{Don't you also need a commutativity condition for $J$ with $\{ x_i \}$?}
+%For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
+%Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
+%a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.
+
+\textbf{The weighted CHSH inequality \cite{acin2012}.}
+The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
+In the CHSH scenario, $\calX = \calY = \{1, 2\}$ and $\calA = \calB = \{0,1\}$.
+We define binary observables $A_x := A_x^0 - A_x^1$ and $B_y := B_y^0 - B_y^1$ from Alice and Bob's projectors.
+It is easy to see that the binary observables are Hermitian and their only eigenvalues are either $+1$ or $-1$.
+The weighted CHSH inequality is given by 
+\begin{align}
+	\label{eq:chsh_op}
+	\ip{\I_\alpha} = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
+\end{align}
+where $\ip{A_xB_y} := \bra{\psi} A_x B_y \ket{\psi}$ is the expectation value of of the observables. 
+If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
+the weighted CHSH inequality.
+However, If they share entangled state $\ket{\psi}$, the maximal violation is 
+\begin{align}
+\label{eq:chsh_max}
+ \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
+\end{align}
+\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
+	\label{def:ideal}
+	Define $\mu = \arctan(1/\alpha)$.
+	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
+	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
+	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
 \end{definition}
-Perfect quantum strategies can be extracted from operator solutions and vice versa.
-Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
-over $\Z_2$, which is called the solution group.
-\begin{definition}[Solution group of a linear system game]
-	\label{def:presentation}
-	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
-	is the group
-	\begin{align*}
-		\Gamma(H,c) := \ip{
-		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
-				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
-				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
-				} .
+An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
+measurements up to isometry, 
+which is a phenomenon referred as a self-test.
+We give the definition of a self-test below and the
+formal statement of this self-testing property of $\I_\alpha$. in \cref{sec:chsh}.
+
+%Note that we may use the term behaviour and correlation interchangeably.
+%The value of a strategy is given by
+%\begin{align}
+%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
+%\end{align}
+
+%The main contribution of our work is the construction of a correlation, which is the combination of 
+%the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
+%and the optimal correlation to violate the weighted CHSH inequality.  \carl{The reader does not 
+%know yet what a linear system game is, so this comment is more confusing than helpful.}
+%The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
+%primitive root. 
+%In the next part, we introduce the definition of self-testing, the definition of linear system game, 
+%and its operator solution, 
+%following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
+
+\carl{Before the next definition, you should define what a ``correlation'' is.}
+\hf{Mentioned in the nonlocal game part, but not sure how to make it a definition. --HF}
+\begin{definition}[Self-testing]
+	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
+	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
+	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
+	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
+	such that 	
+	\begin{align*}
+		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
 	\end{align*}
 \end{definition}
-\carl{Don't you also need a commutativity condition for $J$ with $\{ x_i \}$?}
-For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
-Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
-a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.
 

### 2019-04-02 Draft/draft.tex
Honghao: added the statistical distance measure and justifications, also refined the ideal strategy.

@@
 present a correlation that can self-test $\ket{\EPR{d-1}}$, 
-where $d$ is prime and has primitive root $r \in \{2, 3, 5\}$,
+where $d$ is prime with primitive root $r$,
 and this correlation is denoted by $C(\dr{r})$.  \carl{Be more precise --- we are constructing
 such a correlation for any $d$ which has $2, 3,$ or $5$ as a primitive root.}
-The correlation we constructed is the optimal correlation for a game $\G(\dr{r})$, which is the combination of two tests.
-In this section, we introduce the linear system game which tests a relation that should be satisfied by 
+\hf{One part of $C(\dr{r})$ is produced by the optimal quantum strategy of a linear system game, denoted by $\LS$.}
+In this section, we introduce the linear system game which tests a key relation that should be satisfied by 
 Alice and Bob's observables.
@@
 is too vague -- either make it a rigorous statement or leave it out.}
-The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
-following group
-\begin{align}
-	\Pg_r= \langle u, x : uxu^{-1} = x^r \rangle, \text{ for } r \in \{2, 3,5\}.
-\end{align}
-In other words, relations in the presentation of the solution group of $\LS_r$ can be combined to derive the
-relation $uxu^{-1} = x^r$.  
+\hf{We generalize this relation and make he solution group of $\LS$ the embedding of the 
+following group}
+\begin{align}
+	\Pg_r= \langle u, o : uou^{-1} = o^r \rangle, \text{ for } r \in \N.
+\end{align}
+In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
+relation $uou^{-1} = o^r$.  
 \begin{proposition}
@@
 	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
-	with constant numbers of variables and equations, where each equation involves $3$ variables.
+	with the numbers of variables and equations linear in $r$, where each equation involves $3$ variables.
 	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
@@
 \textbf{The ideal strategy for the weighted $\CHSH_X$ test}.
-Alice and Bob share state $\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1} \ket{ii}$ and choose the special subspace to be 
+Alice and Bob share state 
+\begin{align}
+	\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})
+\end{align}	
+and choose the special subspace to be 
 $V = \spn(\ket{1} ,\ket{d-1})$.
@@
 \end{align}
-\hl{If we express $\ket{j}$'s as $\ket{x_j}$'s, then we can find that 
-shared state is}\\
-\hl{ $\sum_{j=1}^{d-1} \ket{j}\ket{j} = \sum_{j=0}^{(d-1)/2} e^{-ij\pi/d} (\ket{x_{j}}\ket{x_{d-j}} + \ket{x_{d-j}}\ket{x_{j}}$.}
+Extending $B_1|_V$ and $B_2|_V$ to the whole space spanned by $\{ \ket{j} \}_{j=1}^{d-1}$ gives us that
+\begin{align}
+	B_1 =\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} &&
+	B_2 = \sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}},
+\end{align}
+where the basis state $\ket{x_j}$ and $\ket{x_{d-j}}$ are defined by
+\begin{align}
+	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
+	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) \text{ for } j = 1 \dots \frac{d-1}{2}.
+\end{align}
+If we use the basis $\{ \ket{x_j} \}_{j=1}^{d-1}$, the shared state is 
+\begin{align}
+	\ket{\psi} =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\\
+	=& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2}  e^{ij\pi/d}e^{-ij\pi/d} (\ket{x_{j}}\ket{x_{d-j}} + \ket{x_{d-j}}\ket{x_{j}} \\
+	=& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j} \ket{x_{d-j}}.
+\end{align}
 

### 2019-04-07 Draft/draft.tex
Honghao: more details about the robustness of the linear system game and the ideal strategy

@@
 \label{def:q_strat}
-A quantum strategy for the linear system game $(Hx = c)$ consists of 
+A quantum strategy presented in terms of observables for the linear system game $(Hx = c)$ consists of 
 \begin{enumerate}
@@
 Note that any quantum strategy presented in terms of binary observables can be 
-converted to a quantum strategy presented in terms of projective measurement, and
-vice versa.  \carl{This is not entirely true.  A ``quantum strategy presented in terms of projective measurement'' allows
-Alice to give answers that violate the ``Constraint satisfaction'' condition, while a ``quantum strategy presented 
-in terms of binary observables'' does not.}
+converted to a quantum strategy presented in terms of projective measurement by looking into
+the spectrum decompositions of the observables.
 
@@
 %Perfect quantum strategies can be extracted from operator solutions and vice versa.
-%Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
-%over $\Z_2$, which is called the solution group.
-%\begin{definition}[Solution group of a linear system game]
-%	\label{def:presentation}
-%	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
-%	is the group
-%	\begin{align*}
-%		\Gamma(H,c) := \ip{
-%		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
-%				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
-%				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
-%				} .
-%	\end{align*}
-%\end{definition}
-%\carl{Don't you also need a commutativity condition for $J$ with $\{ x_i \}$?}
-%For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
-%Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
-%a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.
+Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
+over $\Z_2$, which is called the solution group.
+\begin{definition}[Solution group of a linear system game]
+	\label{def:presentation}
+	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
+	is the group
+	\begin{align*}
+		\Gamma(H,c) := \ip{
+		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
+				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
+				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
+				} .
+	\end{align*}
+\end{definition}
+Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,c)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
+the linear system game ($Hx = c$) is given by 
+\begin{enumerate}
+	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
+	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$,
+	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
+\end{enumerate}
+We follow a similar approach to construct our ideal strategy. However, our strategy uses a different maximally entangled state,
+so we justify our strategy more carefully.
+For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
+For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.
 
@@
 
-Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.  \carl{That sentence
-is too vague -- either make it a rigorous statement or leave it out.}
-\hf{We generalize this relation and make he solution group of $\LS$ the embedding of the 
+In Slofstra's seminal work~\cite{slofstra2017} embeds the group
+\begin{align}
+	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
+\end{align}
+into a linear system game such that the relations in the definition of $K$ can be reproduced from the
+combination of the equations of the linear system game. The special relation $xyx^{-1} = y^2$ inspired 
+our work.
+\hf{We generalize this relation and make he solution group of $\LS_r$ the embedding of the 
 following group}
@@
 	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
-	with the numbers of variables and equations linear in $r$, where each equation involves $3$ variables.
+	with the numbers of variables, $n_r := 17r + 73$, 
+	and the number of equations, $m_r =15r + 61$, where each equation involves $3$ variables.
 	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
@@
 \end{align}
-%There are two cases to consider which are the index is dividable by $r$ or not.
-%Note that in the following calculation, the division is not with respect to the modulo $d$.
-%When the index $i \equiv 0 \pmod{r}$, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{i/2}}{x_{d-i/r}}$, and
-%when the index $i \not\equiv 0 \pmod{r}$, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{(d+i)/2}}{x_{(d-i)/2}}$,
-%so we can calculate that 
-%\begin{align}
-%	\sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct 
-%	=& \sum_{i=1}^{(d-1)/2}U\ketbra{x_{2i}}{x_{d-2i}}U\ct 
-%	+ \sum_{i=0}^{(d-1)/2-1} U\ketbra{x_{2i+1}}{x_{d-(2i+1)}}U\ct\\
-%	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=0}^{(d-1)/2-1} \ketbra{x_{(d+1)/2+i}}{x_{(d-1)/2-i}}\\
-%	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=(d+1)/2}^{d-1} \ketbra{x_i}{x_{d-i}}\\
-%	=&\sum_{i=1}^{d-1} \ketbra{x_i}{x_{d-i}}.
-%\end{align}
+
 The decomposition of $U$ into $\Psi_1(x_3)$ and $\Psi_1(x_4)$ is similar to the decomposition of $X$.
@@
 \end{align*}
+Next we will show that 
+\begin{align}
+	A_3\x B_3 \ket{\psi} = \ket{\psi} && A_4 \x B_4 \ket{\psi} = \ket{\psi}.
+\end{align}
+For this purpose, we use a different expression of $\ket{\psi}$, which is
+\begin{align}
+	\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{j=0}^{d-2} \ket{r^j} \ket{r^{d-1-j}}.
+\end{align}
+Then the eigenvectors of $U$ are 
+\begin{align}
+	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{r^j}.
+\end{align}
+Hence we can express $\ket{r^j}$ in terms of $\ket{u_k}$ as 
+\begin{align}
+	\ket{r^j} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
+\end{align}
+Then $B_4$ acts on $\ket{r^j}$ as 
+\begin{align}
+	B_4 \ket{r^j} =& \frac{1}{\sqrt{d-1}} B_4\left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
+	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
+	=&\frac{1}{\sqrt{d-1}} \left(\ket{u_0} + (-1)^j\ket{u_{(d-1)/2}}  + 
+	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_{d-1-k}} + \omega_{d-1}^{jk} \ket{u_{k}})\right) \\
+	=& \ket{r^{d-1-j}}.
+\end{align}
+We first verify that $U \x U \ket{\psi} = \ket{\psi}$
+\begin{align}
+	U \x U \ket{\psi} &= \frac{1}{\sqrt{d-1}}\sum_{j = 0}^{d-2} \ketbra{ r^{j}r^{-1}}{r^j} \ket{r^j} \x \ketbra{r^{d-1-j} r^{-1}}{r^{d-1-j}} \ket{r^{d-1-j}} \\
+	&=\frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{r^{j-1}}\ket{r^{d-1-j}} = \ket{\psi},
+\end{align}
+where we use the fact that $\ket{r^{-1}} = \ket{r^{d-2}}$.
+Then we show that $A_4 \x B_4 \ket{\psi} = \ket{\psi}$ as 
+\begin{align}
+	A_4 \x B_4 \ket{\psi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} A_4 \x B_4 \ket{r^j} \ket{r^{d-1-j}} 
+	= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{r^{d-1-j}} \ket{r^{j}} =\ket{\psi},
+\end{align}
+which combined with the previous fact implies that $A_3 \x B_3 \ket{\psi} = \ket{\psi}$.
+
 The conjugation relations in $C_r$ determines the representations of 

### 2019-04-15 Draft/draft.tex
Honghao: trying to self-test the 2 EPR pairs

@@
 \newcommand{\dr}[1]{d^{(#1)}}
+\newcommand{\nr}{n(r)}
+\newcommand{\mr}{m(r)}
 
@@
 	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
-	with the numbers of variables, $n_r := 17r + 73$, 
-	and the number of equations, $m_r =15r + 61$, where each equation involves $3$ variables.
+	with the numbers of variables, $\nr := 17r + 73$, 
+	and the number of equations, $\mr =15r + 61$, where each equation involves $3$ variables.
 	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
@@
 
-In the later parts of the paper, we use $n_r$ and $m_r$ to refer to the size of $\LS_r$.
+In the later parts of the paper, we use $\nr$ and $\mr$ to refer to the size of $\LS_r$.
 The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
@@
 %-----------------------------------------------------------------
-Recall that the linear system game $\LS_r$ has $n_r$ variables and $m_r$ equations.
+Recall that the linear system game $\LS_r$ has $\nr$ variables and $\mr$ equations.
 In game $\G(\dr{r})$, 
-Alice receives $x \in \{1,\dots m_r+3 \}$ and Bob receives
-$y \in \{1,\dots,n_r+1\}$. We follow the previous structure by first give intuition about how they should
+Alice receives $x \in \{1,\dots \mr+3 \}$ and Bob receives
+$y \in \{1,\dots,\nr+1\}$. We follow the previous structure by first give intuition about how they should
 behave in this game. The correlation can be easily extracted from the behaviour list below.
 \begin{itemize}
-	\item When $x \in \{1,\dots m_r\}$ and $y \in \{1, \dots n_r\}$, they should win the 
+	\item When $x \in \{1,\dots \mr\}$ and $y \in \{1, \dots \nr\}$, they should win the 
 	linear system game $\LS_r$ perfectly;
-	\item when $x \in \{m_r+1, m_r+2, m_r+3\}$ and $y \in \{1, 2, n_r+1\}$, they should follow the
+	\item when $x \in \{\mr+1, \mr+2, \mr+3\}$ and $y \in \{1, 2, \nr+1\}$, they should follow the
 	optimal correlation of the test $\CHSH_X$, where 
@@
 		&\ast_A = m_r+1, \quad 1_A = m_r+2,\quad 2_A = m_r+3,\\
-		&\ast_B = n_r+1,\quad 1_B = 1, \quad 2_A = 2,
+		&\ast_B = \nr+1,\quad 1_B = 1, \quad 2_A = 2,
 	\end{align}
@@
 \textbf{The ideal strategy for $\LS_r$}.
-We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n_r(x)$.
+We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n(r,x)$.
 In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_1$ for the group 
 \begin{align}
-	G_r(x) = \ip{ \{x_i\}_{i=1}^{n_r(x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
-\end{align}
+	G_r(x) = \ip{ \{x_i\}_{i=1}^{n(r,x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
+\end{align}
+on the vector space $W_{d-1} = \spn(\{ \ket{x_j} \}_{j=1}^{d-1})$,
 where details of $C_r$ can be found in the appendices. 
-Note that the relation $uxu^{-1} = x^r$ is embedded in the conjugation relations in $C_r$.
+Note that the relation $uou^{-1} = x^r$ is embedded in the conjugation relations in $C_r$.
 Building on $\Psi_1$, we can construct 
@@
 \end{align}
-It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 
-The relation $uxu^{-1} = x^r$ and $X$ determine that 
+It can be checked that $O = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 
+The relation $uou^{-1} = x^r$ and the form of $O$ determine that 
 \begin{align}
@@
 \begin{align}
-	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}}.
-\end{align}
-Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then
-\begin{align*}
-	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .
-\end{align*}
-Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then
-\begin{align}
-	rx \equiv d \pmod{d}
-\end{align}
-Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.
-Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
-Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
-it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
-What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so
-\begin{align}
-	UB_2U\ct = B_2.
-\end{align}
+	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}} =B_2.
+\end{align}
+%Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then
+%\begin{align*}
+%	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .
+%\end{align*}
+%Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then
+%\begin{align}
+%	rx \equiv d \pmod{d}
+%\end{align}
+%Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.
+%Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
+%Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
+%it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
+%What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so
+%\begin{align}
+%	UB_2U\ct = B_2.
+%\end{align}
 
@@
 \begin{align*}
-	G(x,y,z,w) = \ip{ \{x_i, w_i, y_i, z_i\}_{i=1}^{n_r(x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r} :&\text{all elements are of order $2$},\\
-	&x_i = y_iz_i = fw_i,\; fy_if =z_i \text{ for } i= 1 \dots n_r(x) \\
-	&g_{jk}y_j z_k = e,\; w_iy_jw_i = z_k \text{ for all } (i,j,k)\in C_r}.
-\end{align*}
+	G(x,y,z,w) = \ip{ \{x_i, w_i, y_i, z_i\}_{i=1}^{n(r,x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r} :&\text{all elements are of order $2$},\\
+	&x_i = y_iz_i = fw_i,\; fy_if =z_i \text{ for } i= 1 \dots \nr(x) \\
+	&g_{jk}y_j z_k = e,\; w_iy_jw_i = z_k \text{ for all } (i,j,k)\in C_r},
+\end{align*}
+on the vector space $W_2 \x W_{d-1}$,
+where $W_2 = \spn\{ \ket{x_1}, \ket{x_2}\}$.
+Note that the choice of the basis states of $W_2$ is arbitrary.
+On $W_2$, we define 
+\begin{align}
+	\1_{W_2} = \ketbra{x_1}{x_1} + \ketbra{x_2}{x_2}, && X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1}.
+\end{align}
+Another property that we should note is that from the presentation, we can deduce that for all $i = 1 \dots n(r,x)$, 
+\begin{align}
+	fx_i fx_i = f (fw_i) f (fw_i) = w_i w_i = e,
+\end{align}
+so $f$ commutes with $x_i$ for all $i$.
 The representation $\Psi_2$ of $G(x,y,z,w)$ should satisfy the condition that for each $x_i$, 
 $\Psi_2(x_i) = \Psi_2(y_i)\Psi_2(z_i) = \Psi_2(f)\Psi_2(w_i)$. We demonstrate how this representation is constructed 
-for $x_i$, $y_i$, $z_i$, $w_i$ and $f$ where $i = 1 \dots n_r(x)$.
-Building on $\Psi_1$, we have $\Psi_2(x_i) = \Psi_1(x_i) \oplus \Psi_1(x_i)$, then
+for $x_i$, $y_i$, $z_i$, $w_i$ and $f$ where $i = 1 \dots n(r,x)$.
+Building on $\Psi_1$, we have $\Psi_2(x_i) = \1_{W_2} \x \Psi_1(x_i)$, then
 $y_i$, $z_i$, $w_i$ and $f$ are mapped to
 \begin{align*}
-\Psi_2(y_i) = 
-\begin{pmatrix}
-\Psi_1(x_i) & 0\\
-0 & \1
-\end{pmatrix},
-&&
-\Psi_2(z_i) \to
-\begin{pmatrix}
-\1 & 0\\
-0 & \Psi_1(x_i)
-\end{pmatrix},
-\\
-\Psi_2(w_i) = 
-\begin{pmatrix}
-0 & \Psi_1(x_i)\\
-\Psi_1(x_i) & 0
-\end{pmatrix},
-&&
-\Psi_2(f) \to
-\begin{pmatrix}
-0 & \1\\
-\1 & 0
-\end{pmatrix}.
+&\Psi_2(y_i) = \ketbra{x_1}{x_1} \x \Psi_1(x_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
+&\Psi_2(z_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(x_i) \\
+&\Psi_2(w_i) =  X_{W_2} \x \Psi_1(x_i)\\
+&\Psi_2(f) = X_{W_2} \x \1_{W_{d-1}}.
 \end{align*}
@@
 the relations satisfied by the generators are preserved.
-For each $g_{jk}$ where $(i,j,k) \in C_r$, $\Psi_2(g_{jk}) = \Psi_2(y_j)\Psi_2(z_k)$ following
-their defining relations.
+For each $g_{jk}$ where $(i,j,k) \in C_r$, 
+\begin{align}
+\Psi_2(g_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(x_j) + \ketbra{x_2}{x_2} \x \Psi_1(x_k).
+\end{align}
 
 The group $G_r(x,y,z,w)$ is embedded in $\Gamma(\LS_r)$ by replacing the conjugacy relations 
-by linear relations. The new generators are $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{n_r(x)}
+by linear relations. The new generators are $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{n(r,x)}
 \cup \{\{y_{K,k}\}_{k=1}^7\}_{K \in C_r}$. How the new linear relations can embed the conjugacy relations 
-in $G_r(x,y,z,w)$ can be found in the appendices. Now we define the representation $\Psi_{\LS_r}$ of
-$\Gamma(\LS_r)$. For any generator $a \in \{x_i, w_i, y_i, z_i\}_{i=1}^{n_r(x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r}$,
-\begin{align}
-	\Psi_{\LS_r}(a) = \Psi_2(a) \oplus \Psi_2(a) = \Psi_1(a)^{\oplus 4}.
-\end{align}
-For generators $\{y_{F_j,k}\}_{k=1}^7\}_{j=1}^{n_r(x)}$,
-\begin{align*}
-	\Psi_{\LS_r}(y_{F_j,1}) = 
-	\begin{pmatrix}
-		0 & \Psi_2(f) \\
-		\Psi_2(f) & 0
-	\end{pmatrix},
-	&&
-	\Psi_{\LS_r}(y_{F_j,2}) = 
-	\begin{pmatrix}
-		0 & \1\\
-		\1 & 0
-	\end{pmatrix},\\
-	\Psi_{\LS_r}(y_{F_j,3}) = 
-	\begin{pmatrix}
-		0 & \Psi_2(y_j) \\
-		\Psi_2(y_j) & 0
-	\end{pmatrix},
-	&&
-	\Psi_{\LS_r}(y_{F_j,4}) = 
-	\begin{pmatrix}
-		0 & \Psi_2(y_jf) \\
-		\Psi_2(fy_j) & 0
-	\end{pmatrix},\\
-	\Psi_{\LS_r}(y_{F_j,5}) = 
-	\begin{pmatrix}
-		 \Psi_2(fy_jf) & 0\\
-		  0 & \Psi_2(f)
-	\end{pmatrix},
-	&&
-	\Psi_{\LS_r}(y_{F_j,6}) = 
-	\begin{pmatrix}
-		 \Psi_2(y_jz_j) & 0\\
-		 0 & \1
-	\end{pmatrix},\\
-	\Psi_{\LS_r}(y_{F_j,7}) = 
-	\begin{pmatrix}
-		 \Psi_2(y_j) & 0\\
-		 0 & \Psi_2(z_j)
-	\end{pmatrix}.
+in $G_r(x,y,z,w)$ can be found in the appendices. 
+The relations that we should pay attention to are
+\begin{align}
+	fy_{F_j,1}y_{F_j,2} =  e, && y_j y_{F_j,2}y_{F_j,3} = e \text{ for } j = 1 \dots n(r,x),
+\end{align}
+which imply that $y_{F_j, 2}$ commutes with $f$ and $y_j$.
+Since $z_j = fy_jf$, $y_{F_j, 2}$ commutes with $z_j$ too.
+We also know that $x_j = y_jz_j$, so we can conclude that $y_{F_j, 2}$ commutes with $x_j$.
+
+Now we define the representation $\Psi_{\LS_r}$ of
+$\Gamma(\LS_r)$ on $W_2 \x W_2 \x W_{d-1}$. For any generator $a \in \{x_i, w_i, y_i, z_i\}_{i=1}^{n(r,x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r}$,
+\begin{align}
+	\Psi_{\LS_r}(a) = \1_{W_2} \x \Psi_2(a) 
+\end{align}
+For generators $\{y_{F_j,k}\}_{k=1}^7\}_{j=1}^{n(r,x)}$,
+\begin{align*}
+	\Psi_{\LS_r}(y_{F_j,1}) &=X_{W_2} \x \Psi_2(f) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}}\\
+	\Psi_{\LS_r}(y_{F_j,2}) &= X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
+	\Psi_{\LS_r}(y_{F_j,3}) &= X_{W_2} \x \Psi_2(y_j) = X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_1(x_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
+	\Psi_{\LS_r}(y_{F_j,4}) &= \ketbra{x_1}{x_2} \x \Psi_2(y_jf) + \ketbra{x_2}{x_1} \x \Psi_2(fy_j)\\
+	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_1(x_j) + \ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_2}{x_1x_1} \x \Psi_1(x_j)\\ 
+	\Psi_{\LS_r}(y_{F_j,5}) &= \ketbra{x_1}{x_1} \x \Psi_2(fy_jf) + \ketbra{x_2}{x_2} \x \Psi_2(f) \\
+	&= \ketbra{x_1x_}{x_1x_1} \x \1_{W_{d-1}} + \ketbra{x_1x_2}{x_1x_2} \x \Psi_1(x_j) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
+	\Psi_{\LS_r}(y_{F_j,6}) &=  \ketbra{x_1}{x_1} \x \Psi_2(fy_jf) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	&=(\ketbra{x_1x_1}{x_1x_1}+  \ketbra{x_1x_2}{x_1x_2}) \x \Psi_1(x_j) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi_{\LS_r}(y_{F_j,7}) &= \ketbra{x_1}{x_1} \x \Psi_2(y_j) + \ketbra{x_2}{x_2} \x \Psi_2(z_j) \\
+	&=\ketbra{x_1x_1}{x_1x_1} \x \Psi_1(x_j) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1}) + \ketbra{x_2x_2}{x_2x_2} \x \Psi_1(x_j)
 \end{align*}
@@
 \begin{align*}
-	\Psi_{\LS_r}(y_{K,1}) = 
-	\begin{pmatrix}
-		0 & \Psi_2(w_{k_1}) \\
-		\Psi_2(w_{k_1}) & 0
-	\end{pmatrix},
-	&&
-	\Psi_{\LS_r}(y_{F_j,2}) = 
-	\begin{pmatrix}
-		0 & \1\\
-		\1 & 0
-	\end{pmatrix},\\
-	\Psi_{\LS_r}(y_{F_j,3}) = 
-	\begin{pmatrix}
-		0 & \Psi_2(y_{k_2}) \\
-		\Psi_2(y_{k_2}) & 0
-	\end{pmatrix},
-	&&
-	\Psi_{\LS_r}(y_{F_j,4}) = 
-	\begin{pmatrix}
-		0 & \Psi_2(y_{k_2}w_{k_1}) \\
-		\Psi_2(w_{k_1}y_{k_2}) & 0
-	\end{pmatrix},\\
-	\Psi_{\LS_r}(y_{F_j,5}) = 
-	\begin{pmatrix}
-		 \Psi_2(w_{k_1}y_{k_2}w_{k_1}) & 0\\
-		  0 & \Psi_2(w_{k_1})
-	\end{pmatrix},
-	&&
-	\Psi_{\LS_r}(y_{F_j,6}) = 
-	\begin{pmatrix}
-		 \Psi_2(y_{k_2}z_{k_3}) & 0\\
-		 0 & \1
-	\end{pmatrix},\\
-	\Psi_{\LS_r}(y_{F_j,7}) = 
-	\begin{pmatrix}
-		 \Psi_2(y_{k_2}) & 0\\
-		 0 & \Psi_2(z_{k_3})
-	\end{pmatrix}.
+	\Psi_{\LS_r}(y_{K,1}) &= X_{W_2} \x \Psi_2(w_{k_1}) = X_{W_2} \x X_{W_2} \x \Psi_1(x_{k_1}) \\
+	\Psi_{\LS_r}(y_{F_j,2}) &= X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi_{\LS_r}(y_{F_j,3}) &= X_{W_2} \x \Psi_2(y_{k_2}) = X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_1(x_{k_2}) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
+	\Psi_{\LS_r}(y_{F_j,4}) &= \ketbra{x_1}{x_2} \x  \Psi_2(y_{k_2}w_{k_1}) + \ketbra{x_2}{x_1} \x \Psi_2(w_{k_1}y_{k_2})\\
+	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_1(x_{k_2}x_{k_1}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_1(x_{k_1})
+	+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_1(x_{k_1}x_{k_2}) \\
+	\Psi_{\LS_r}(y_{F_j,5}) &= \ketbra{x_1}{x_1} \x \Psi_2(w_{k_1}y_{k_2}w_{k_1}) + \ketbra{x_2}{x_2} \x  \Psi_2(w_{k_1})\\
+	&= \ketbra{x_1x_1}{x_1x_1} \x \1_{W_{d-1}} + \ketbra{x_1x_2}{x_1x_2} \x \Psi_1(x_{k_1}x_{k_2}x_{k_1}) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_1(x_{k_1})\\
+	\Psi_{\LS_r}(y_{F_j,6}) &=  \ketbra{x_1}{x_1} \x \Psi_2(y_{k_2}z_{k_3}) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_1(x_{k_2}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_1(x_{k_3}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi_{\LS_r}(y_{F_j,7}) &= \ketbra{x_1}{x_1} \x \Psi_2(y_{k_2}) + \ketbra{x_2}{x_2} \x \Psi_2(z_{k_3})\\
+	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_1(x_{k_2}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}} + 
+	\ketbra{x_2x_2}{x_2x_2} \x \Psi_1(x_{k_3})
 \end{align*}

### 2019-04-22 Draft/draft.tex
Honghao: rewrote section 2

@@
 \newcommand{\mr}{m(r)}
+\newcommand{\ux}{\underline{x}}
+\newcommand{\uc}{\underline{c}}
+\newcommand{\ua}{\underline{a}}
 
@@
 
-\title{Self-test prime dimensional EPR pairs with constant alphabet}
+\title{Robust self-testing of large entanglement with constant alphabet}
 
@@
 %========================================
-\textbf{Notations}.
-We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
-The maximally entangled state of local dimension $d-1$ for some prime $d$ is denoted by
+%-----------------------------------
+\subsection{Notations}
+%-----------------------------------
+The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we are interested in is denoted by
 \begin{align}
@@
 $\calH_B$.
-The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, the Pauli operators
-are defined by
+The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
+the maximally entangled state is denoted by 
+\begin{align}
+	\ket{\EPR{2}} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
+\end{align}
+and the Pauli operators are given by
 \begin{align}
@@
 The only exception is for projectors used in a quantum strategy defined below, where the subscript 
-is the input and the superscript is the output. For example, $A_x^a$ is Alice's projector for input $x$ and output $a$.
-Operators defined by the projectors follow the same convention. For example, $A_x := A_x^0 - A_x^1$.
-
-We use the following notation for the closeness between states.
+is the input and the superscript is the output. For example, $M_x^a$ is Alice's projector for input $x$ and output $a$.
+Operators defined by the projectors follow the same convention, for example, $M_x := M_x^0 - M_x^1$.
+
+We use the following notation for the closeness between quantum states.
 \begin{align}
@@
 \end{align}
-Similarly, for $a,b \in \C$, we have
+Similarly, for numbers $a,b \in \C$, the closeness is denoted by
 $a \appd{\epsilon} b \iff \norm{a-b} \leq \epsilon$.
 
-\textbf{Number theory}.
-We use some basic number theory in our work. A primitive root of a prime number
+We use some basic number theory in our work. 
+\begin{definition}
+A primitive root of a prime number
 $d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
-in the multiplicative group of integers modulo $d$, $\Zd$. Equivalently,
+in the multiplicative group of integers modulo $d$, $\Zd$.
+\end{definition}
+In other words,
 $r$ is the generator of $\Zd$.
@@
 %unless otherwise specified, for example, the $k/r$ above.
-
-\textbf{Nonlocal games}. 
-The two players of a nonlocal game are Alice and Bob. Each of them is requested
-to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
+%-----------------------------------------
+\subsection{Nonlocal games}
+%-----------------------------------------
+In a nonlocal game, there are two players, Alice and Bob and each of them is requested
+to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and her answer set by $\calA$. Similarly,
 Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
 comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
-and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
-because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
-the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
-pair to $\{0,1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
-to our new result.
-
-A quantum strategy of a nonlocal game consists of projective measurements $\{\{A_x^a\}_a\}_x$ on Alice's side, 
-$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
-the condition that $P^2 = P = P\ct$.  \carl{You need to put explicit labels on the quantum systems used by
+and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. 
+Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
+pair to $\{0,1\}$ which corresponds to losing and winning. 
+Such games are nonlocal
+because Alice and Bob cannot communicate after getting their questions but they may share some strategy beforehand.
+
+A quantum strategy of a nonlocal game presented in terms of projective measurements
+consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
+$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
+$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
+\carl{You need to put explicit labels on the quantum systems used by
 Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
@@
 \hf{Addressed in the notation part. --H.F}
-Then Alice and Bob's quantum strategy produces the correlation
+Then Alice and Bob's quantum strategy produces the conditional probability distribution
 \begin{align}
@@
 \end{align}
-where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
+\begin{definition}
+	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
+	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
+\end{definition}
 A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
-
 \begin{definition}[Linear system game]
- Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
- where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
- $c$ is a length-$n$ vector with entries in $\Z_2$. 
+ Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
+ where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
+ $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
  The associated linear system game involves two
- players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
- and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
- that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
- Formally, the winning condition is 
- \begin{align*}
- 	a(j) &= b && \text{(Consistency)} \\
-	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
- \end{align*}
- for all $(i,j) \in \calX \times \calY$. 
+ players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
+ and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
+ scoring function is defined by
+ \begin{align}
+ 	V(\ua, b, i, j) =
+	\begin{cases}
+		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
+		0,  \quad \text{otherwise.}
+	\end{cases}
+\end{align}
 \end{definition}
-The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
-so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
-$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.  \carl{Make this clear in the definition itself.}
-We focus on quantum strategies for the linear system game presented in terms of binary observables.
+\carl{Make this clear in the definition itself.}
+\hf{I made the definition of the scoring function part of the big definition now.}
+In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
 \begin{definition}[Quantum strategy of a linear system game]
 \label{def:q_strat}
-A quantum strategy presented in terms of observables for the linear system game $(Hx = c)$ consists of 
+A quantum strategy presented in terms of observables for the linear system game $(H\ux = \uc)$ consists of 
 \begin{enumerate}
@@
 		\item $A_{ij}^2 = \1$ for every $i,j$,
-		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
+		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
 		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
@@
 converted to a quantum strategy presented in terms of projective measurement by looking into
-the spectrum decompositions of the observables.
+the spectral decompositions of the observables.
 
@@
 %Perfect quantum strategies can be extracted from operator solutions and vice versa.
-Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
+A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
+the finite-dimensional representation of a finitely presented group
 over $\Z_2$, which is called the solution group.
@@
 	\label{def:presentation}
-	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
+	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
 	is the group
 	\begin{align*}
-		\Gamma(H,c) := \ip{
+		\Gamma(H,\uc) := \ip{
 		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
-				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
+				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
 				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
@@
 \end{definition}
-Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,c)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
-the linear system game ($Hx = c$) is given by 
+Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
+the linear system game ($H\ux = \uc$) has
 \begin{enumerate}
@@
 
-\textbf{The weighted CHSH inequality \cite{acin2012}.}
-The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
-In the CHSH scenario, $\calX = \calY = \{1, 2\}$ and $\calA = \calB = \{0,1\}$.
-We define binary observables $A_x := A_x^0 - A_x^1$ and $B_y := B_y^0 - B_y^1$ from Alice and Bob's projectors.
-It is easy to see that the binary observables are Hermitian and their only eigenvalues are either $+1$ or $-1$.
-The weighted CHSH inequality is given by 
+%-------------------------------------------------------------------------------
+\subsection{The weighted CHSH inequality \cite{acin2012}.}
+%-------------------------------------------------------------------------------
+The weighted CHSH inequality is extracted from the CHSH test, which is another nonlocal game. 
+The input sets and output sets of Alice and Bob are
+$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
+The scoring function for the $\alpha$-weighted CHSH test is defined by
+\begin{align}
+	V(a,b,x,y)_{\alpha-CHSH} = 
+	\begin{cases}
+		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
+		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
+		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
+	\end{cases}
+\end{align}
+Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
+We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
+The weighted CHSH inequality states that 
 \begin{align}
 	\label{eq:chsh_op}
-	\ip{\I_\alpha} = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
-\end{align}
-where $\ip{A_xB_y} := \bra{\psi} A_x B_y \ket{\psi}$ is the expectation value of of the observables. 
-If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
-the weighted CHSH inequality.
-However, If they share entangled state $\ket{\psi}$, the maximal violation is 
+	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2\alpha,
+\end{align}
+where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of of the observables. 
+The weighted CHSH inequality is true 
+If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
+However, If they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
 \begin{align}
@@
 	Define $\mu = \arctan(1/\alpha)$.
-	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
-	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
-	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
+	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
+	consists of the joint state $\ket{\EPR{2}}$ and observables $M_1 = \pauliz$, $M_2 = \paulix$,
+	$N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
 \end{definition}
-An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
-measurements up to isometry, 
-which is a phenomenon referred as a self-test.
-We give the definition of a self-test below and the
-formal statement of this self-testing property of $\I_\alpha$. in \cref{sec:chsh}.
+An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
+value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
+strategy up to some local isometry, 
+which is a phenomenon referred as a robust self-test.
+We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.
 
@@
 \carl{Before the next definition, you should define what a ``correlation'' is.}
-\hf{Mentioned in the nonlocal game part, but not sure how to make it a definition. --HF}
-\begin{definition}[Self-testing]
-	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
-	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
-	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
-	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
-	such that 	
-	\begin{align*}
-		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
-	\end{align*}
-\end{definition}
+\hf{Done. I decided to remove the definition of self-testing here because I think it is hard
+to give a general robust self-testing definition and it suffices to just give our robust self-testing result.}
+%\begin{definition}[Self-testing]
+%	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
+%	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
+%	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
+%	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
+%	such that 	
+%	\begin{align*}
+%		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
+%	\end{align*}
+%\end{definition}
 

### 2019-04-23 Draft/draft.tex
Honghao: finished section 3

@@
 \end{definition}
+We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
 Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
@@
 %=======================================
-\section{The linear system game}
-\label{sec:lsg}
+\section{The linear constraint test}
+\label{sec:lct}
 %=======================================
-The goal of this section and the following two sections is to 
-present a correlation that can self-test $\ket{\EPR{d-1}}$, 
-where $d$ is prime with primitive root $r$,
-and this correlation is denoted by $C(\dr{r})$.  \carl{Be more precise --- we are constructing
-such a correlation for any $d$ which has $2, 3,$ or $5$ as a primitive root.}
-\hf{One part of $C(\dr{r})$ is produced by the optimal quantum strategy of a linear system game, denoted by $\LS$.}
-In this section, we introduce the linear system game which tests a key relation that should be satisfied by 
-Alice and Bob's observables.
-
-In Slofstra's seminal work~\cite{slofstra2017} embeds the group
+In this section, we introduce a linear constraint test that is satisfied by our correlation.
+The linear constraint test is designed to enforce relations that should be satisfied by 
+Alice and Bob's observables and it is inspired by 
+Slofstra's seminal work~\cite{slofstra2017}, in which he
+embeds the group
 \begin{align}
@@
 \end{align}
-into a linear system game such that the relations in the definition of $K$ can be reproduced from the
-combination of the equations of the linear system game. The special relation $xyx^{-1} = y^2$ inspired 
-our work.
-\hf{We generalize this relation and make he solution group of $\LS_r$ the embedding of the 
+into a linear system game such that the relations in the definition of $K$ can be derived from the
+combination of the equations of the linear system game. Then he showed the difference between exact representations
+and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
+\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
 following group}
 \begin{align}
-	\Pg_r= \langle u, o : uou^{-1} = o^r \rangle, \text{ for } r \in \N.
-\end{align}
-In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
-relation $uou^{-1} = o^r$.  
+	G = \langle u, o : uou^{-1} = o^r \rangle, 
+\end{align}
+for some $r \in \N$ into a linear constraint test.
+
+%------------------------------------------------------------------------
+\subsection{The embedding of $G$}
+%------------------------------------------------------------------------
+The main result of this subsection is summarized in the following theorem.
+\begin{theorem}
+	The relation $uou^{-1} = o^r$ can be embedded in a linear constraint test which has
+	$n(r) := 18r+86$ variables and $m(r) := 16r + 72$ equations, where each equation has $3$ variables.
+\end{theorem}
+We prove this by constructing the solution group $\Gamma$ of the linear constraint test. 
+We also prove some properties of the generators of $\Gamma$ along the way.
+
+We embed $G$ into $\Gamma$ in three steps and introduce two intermediate groups $G_0$ and $G_1$, which are defined below.
+\begin{definition}
+	The presentation of $G_0$ has order-$2$ generators:
+	\begin{align}
+		\{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5
+	\end{align}
+	and relations:
+	\begin{align}
+	&u_3 = u_2o_1u_2 && u_4 = u_2o_2u_2 \\
+	&u_5 = u_1u_3u_1 && o_2 = u_1u_4u_1\\
+	&u_5 = o_1 o_r o_1,
+	\end{align}
+	and when $r$ is even
+	\begin{align}
+	&o_{1+2j} = o_1o_{2j}o_1 && o_{2+2j} = o_2o_{1+2j}o_2&& \text{ for } j = 1 \dots r/2 - 1;
+	\end{align}
+	when $r$ is odd
+	\begin{align}
+	&o_3 = o_2o_1o_2 &&
+	 o_{2+2j} =o_1o_{1+2j}o_1 && o_{3+2j} = o_2o_{2j+2}o_2 &&\text{ for } j = 1 \dots (r-3)/2.
+	\end{align}
+\end{definition}
 \begin{proposition}
-	\label{prop:embed}
-	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
-	with the numbers of variables, $\nr := 17r + 73$, 
-	and the number of equations, $\mr =15r + 61$, where each equation involves $3$ variables.
-	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
-	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
+	The group $G_1$ embeds the relation 
+	\begin{align}
+		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
+	\end{align}
+	for any $ j \in \N$.
 \end{proposition}
-The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
-Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
-The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
-We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
-and \cref{sec:power5} for $r = 5$.
-
-In the later parts of the paper, we use $\nr$ and $\mr$ to refer to the size of $\LS_r$.
-The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
-even if the generators $u$ and $x$ have arbitrary order. 
-The product of the generators $x_1$ and $x_2$ from the solution group of $\LS_r$ plays the role 
-of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
-of the generator $u$ in $\Pg_r$.   \carl{It's reasonable to make a couple informal statements
-at the beginning of a section, but you shouldn't be making
-such vague statements at this point.  Everything said at this point in the section should have a precise mathematical
-meaning.}
-As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
-$x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
-\begin{align}
-	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^r.
-\end{align}
-Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
-the key relation that 
-\begin{align}
-	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^r\ket{\psi}, 
-\end{align}
-and similarly on Bob's side.
-If we denote the unitary corresponding to the generator $u$ of $\Pg_r$ by $U$ and the unitary
-corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
-$UXU\ct \ket{\psi} = X^r \ket{\psi}$.
-The special property of $U$ and $X$ is summarized in the following lemma.
-
-\begin{lemma}
-	\label{lm:ux_independ}
-	Suppose there exist unitaries $U$ and $X$ which have the following forms
-	\begin{align}
-		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/r}{i},
-	\end{align}
-	where $d$ is an odd prime number with primitive root $r$,
-	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
-	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
-\end{lemma}
-Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^r$.
-In the self-test proof, this lemma will be a critical step.
+The proof follows the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017}
 \begin{proof}
-We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
-Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
-such that 
-\begin{align}
-	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
-\end{align}
-We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
-\carl{We shouldn't be making extra assumptions that are not stated in the lemma.  This looks to me more like
-a definition of the variables $\{ k_i \}$, rather than an assumption.}
-The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
-Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
-where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
-Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.
-
-We start with proving that $\ket{x_{k_1}} = 0$.
-Proving $\ket{x_{k_i}} = 0$ for other $i$ follows a similar argument, so we briefly
-discuss about it in the end.
-The entry $\bra{1}M\ket{1}$ can be expressed as  
-\begin{align}
-	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/r^k}\braket{i}{1}.
-\end{align}
-For the term $\braket{1}{i/r^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
-$k = k_1$. We can conclude that 
-\begin{align}
-	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
-\end{align}
-Similarly we can determine that for all $j = 1,2\dots d-1$,
-\begin{align}
-	\bra{j}M\ket{j} 
-	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/r^k}\braket{i}{j} 
-	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
-\end{align}
-Hence we get $d-1$ equations with $d-1$ variables, and the linear system is
-\begin{align}
-	W \ket{x_{k_1}} = 0,
-\end{align}
-where $W(m,n) = \omega_d^{mn}$. Then we define
-\begin{align}
-	\tW = 
-	\begin{pmatrix}
-	1 & 1 \\
-	1 & W
-	\end{pmatrix}.
-\end{align}
-First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
-Next, we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
-and prove that it satisfies the condition
-that 
-\begin{align}
-	\tW \ket{\tx_{k_1}} = 0,
-\end{align}
-which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
-We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which is required by the first row of $\tW$.
-It can be proved by summing the known $d-1$ equations as follows
-\begin{align}
-	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
-	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
-	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
-	= \sum_{l = 1}^{d-1}- x_{k_1,l}
-\end{align}
-where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
-Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.
-
-For $\ket{x_{k_a}}$, we look at entries $\{\bra{j}M\ket{aj}\}_{j=1}^{d-1}$ for $a = 2 \dots d-1$ and get equations
-of the form
-\begin{align}
-	0 = \bra{j}M\ket{aj} = \sum_{l=1}^{d-1} x_{k_a, l} \omega_d^{ajl} 
-\end{align}
-The corresponding coefficient matrix has value $\omega_d^{amn}$ at coordinate $(m,n)$,
-so it is also a submatrix of a Vandermonde matrix. Similar argument gives us that $\ket{x_{k_a}} = 0$.
-
-To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
-$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
-\carl{Nice proof.  I like the use of the Vandermonde matrix.  We can think a little about possible simplifications.}
+	We prove it by induction.
+	Direct calculation gives us that
+	\begin{align} 
+		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
+	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
+	=& u_5 o_2\\
+	=& o_1o_ro_1 o_2.
+	\end{align}
+	Then substituting the definitions of $o_k$ for $k = r \dots 3$ gives us the case for $j=1$.
+
+	Now assume the statement is true for $j = n$, then when $j = n+1$
+	\begin{align}
+		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
+		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
+		 =& (o_1o_2)^{r^{n+1}},
+	\end{align}
+	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$ and $o_1o_2$.
+	Hence, the statement is true.
 \end{proof}
-Note that the primitive root $r$ in the lemma is not restricted to the set $\{2,3,5\}$, so this lemma works for any 
-odd prime number $d$.
-
-%\begin{align}
-%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
-%\end{align}
-%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
-%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
-%by the following relations
-%\begin{align}
-%\label{eq:sim}
-%	u_x x u_x = x^2, \quad
-%	u_z z u_z = z^2.
-%\end{align}
-%Consequently, the $d$ dependency of $\G$ comes from constraints imposed by other components of the game,
-%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
-%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
-%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
-%relation $xzx^{-1}z^{-1} = \J$.
-%
-%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
-%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
-%\begin{align}
-%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
-%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
-%\end{align}
-%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
-%we can verify that 
-%\begin{align}
-%	U_xU_z = \1 = U_zU_x,
-%\end{align}
-%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
-%In the end, we define $\Pg_{\LS}$ by
-%\begin{equation}
-%\begin{aligned}
-%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
-%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
-%\end{aligned}
-%\end{equation}
-%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
-%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
+To better characterize all the conjugation relations above and simplify the form of $G_1$
+and make the introduction of $G_2$ easier, we relabel $u_i$ and $o_i$'s
+as $a_i$'s such that
+\begin{align}
+	a_j := 
+	\begin{cases}
+	 o_j \text{ for } j = 1,2 \\
+	 u_{j-2} \text{ for } j = 3\dots 7 \\
+	o_{j- 5} \text{ for } j = 8 \dots r+5.
+	\end{cases}
+\end{align}
+Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
+\begin{align}
+	(i,j,k) \in C(r) \iff a_ia_ja_i = a_k.
+\end{align}
+The size of $C(r)$ is $r+3$. 
+%We can also employ some ordering of $C(r)$ such that $C(r,j)$ is a unique tuple for 
+%$j = 1 \dots r+3$.
+In this way, the group $G_0$ can be presented by
+\begin{align}
+	G_0  = \ip{ \{a_i\}_{i=1}^{r+5} : C(r) }.
+\end{align}
+
+Then we define the group $G_1$.
+\begin{definition}
+The presentation of $G_1$ has order-$2$ generators:
+\begin{align*}
+	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f, g, \{h_{jk}\}_{(i,j,k) \in C(r)};
+\end{align*}
+and relations:
+\begin{align*}
+	&a_i = b_ic_i = fd_i = gv_i,&& fb_if =c_i &&\text{ for } i= 1 \dots r+5 \\
+	&h_{jk}b_j c_k = e,&& d_ib_jd_i = c_k &&\text{ for all } (i,j,k) \in C(r).
+\end{align*}
+\end{definition}
+Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
+We introduce the generator $g$ so that later we can associate $f$ with $g$ in linear relations of the Magic Square game.
+Such relations are important for the self-testing proof.
+Two important properties of $G_1$ are given in propositions below.
+The first property of $G_1$ was first proved in Lemma~$4.4$ of \cite{slofstra2017}.
+\begin{proposition}
+	The group $G_1$ embeds relation $x_ix_jx_i = x_k$ for all $(i,j,k) \in C(r)$.
+\end{proposition}
+\begin{proof}
+	We first show that $d_i c_j d_i = b_k$, which is because
+	\begin{align}
+		d_i c_j d_i = d_i (f b_j f) d_i = f (d_i b_j d_i) f = f c_k f = b_k.
+	\end{align}
+	Then, we can prove that 
+	\begin{align}
+		a_i a_j a_i = f d_i b_j c_j f d_i = (f d_i b_j d_i f)(f d_i c_j d_i f) = (f c_k f)(f b_k f) = b_k c_k = a_k. 
+	\end{align}
+\end{proof}
+\begin{proposition}
+	In the group $G_1$, the generators $f$ and $g$ commute with $a_i$ for all $i = 1 \dots r+5$.
+\end{proposition}
+\begin{proof}
+	We can check that
+	\begin{align}
+		fa_i f a_i = d_i d_i = e && g a_i g a_i = v_i v_i  = e,
+	\end{align}
+	for all $i = 1 \dots r+5$.
+\end{proof}
+Note that there are two types of conjugacy relations in $G_1$. One is of the form
+$f b_i f = c_i$ for all $i = 1 \dots r+5$. The other one is of the form 
+$d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
+we are going to embed it into a different set of linear relations in $\Gamma$.
+
+\begin{definition}
+The presentation of $\Gamma$ has order-$2$ generators:
+\begin{align*}
+	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
+	\{\{ k_{c,j} \}_{j=1}^6\}_{c \in C(r)},
+\end{align*}
+and relations:
+\begin{itemize}
+\item for all $i = 1 \dots r+5$:
+\begin{align}
+	&a_i = b_ic_i = f_0d_i = g_0v_i \\
+	&g_2 a_i w_i = e \\
+	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
+	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
+\end{align}
+which embed $f_0 b_i f_0 = c_i$;
+\item for all $ c = (i,j,k) \in C(r)$:
+\begin{align}
+	&h_{jk}b_j c_k = e\\
+	&d_i k_{c,1} f_2 = e && b_j f_2 k_{c,2} = e && k_{c,2} k_{c,3} k_{c,4} = e\\
+	&d_i k_{c,4} k_{c,5} = e && c_k k_{c,5} k_{c,6} =e && k_{c,1} k_{c,3} k_{c,6} = e,
+\end{align}
+which embed $d_i b_j d_i = c_k$;
+\item relations of a Magic Square test:
+\begin{align}
+	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
+	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
+\end{align}
+which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
+\item $J$ commutes with all the other generators.
+\end{itemize}
+\end{definition}
+The special properties of the generators of $\Gamma$ are summarized in the two propositions below.
+\begin{proposition}
+	The group $\Gamma$ embeds all the conjugacy relations of $G_1$.
+	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
+\end{proposition}
+The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
+\begin{proposition}
+	In the group $\Gamma$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
+	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
+\end{proposition}
+\begin{proof}
+	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
+	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
+	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
+	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
+\end{proof}
+
+%------------------------------------------------------------------------
+\subsection{The representation of $\Gamma$}
+%------------------------------------------------------------------------
+In this section we give the presentation of $\Gamma$ which is built upon the representation 
+$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma$ to construct the
+ideal strategy that realizes our correlation.
+
+Before giving the representation, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
+of the representations,
+\begin{align}
+	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
+\end{align}
+Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
+modulo $d$ implicitly. We use the second form of the basis when it is convenient.
+We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
+On the Hilbert space $W_2$, we define
+\begin{align}
+	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
+	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
+	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
+\end{align}
+\begin{definition}
+The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
+\begin{align}
+	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
+	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
+	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
+	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
+	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
+	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
+\end{align}
+where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
+\begin{align}
+	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
+\end{align}
+The representation of the rest of the generators
+can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
+conjugation relations.
+\end{definition}
+We can check that
+\begin{align}
+	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
+	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
+\end{align}
+which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
+$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.
+
+Following the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}, we construct a representation of $G_1$.
+\begin{definition}
+The representation $\Psi_1$ of $G_1$ on $W_2 \x W_{d-1}$ is defined by
+\begin{itemize}
+\item for $f_0$ and $g_0$
+\begin{align}
+	&\Psi_1(f_0) = X_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi_1(g_0) = Z_{W_2} \x \1_{W_{d-1}},
+\end{align}
+\item
+for $i = 1 \dots r+5$,
+\begin{align}
+	&\Psi_1(a_i) = \1_{W_2} \x \Psi_0(a_i) \\
+	&\Psi_1(b_i) = \ketbra{x_1}{x_1} \x \Psi_1(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
+	&\Psi_1(c_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(a_i) \\
+	&\Psi_1(d_i) =  X_{W_2} \x \Psi_0(a_i)\\
+	&\Psi_1(v_i) = Z_{W_2} \x \Psi_0(a_i).
+\end{align}
+\item for $(i,j,k) \in C(r)$,
+\begin{align}
+	\Psi_1(h_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(a_j) + \ketbra{x_2}{x_2} \x \Psi_1(a_k).
+\end{align}
+\end{itemize}
+\end{definition}
+
+Finally, we follow the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017} to construct the 
+representation of $\Gamma$.
+\begin{definition}
+The representation $\Psi$ of $\Gamma$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
+\begin{itemize}
+\item for any $x$ which is also a generator of $G_1$,
+\begin{align}
+	\Psi(x) = \1_{W_2} \x \Psi_1(x);
+\end{align}
+\item for the generators involved in the Magic square test
+\begin{align}
+	&\Psi(f_1) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi(g_1) = Z_{W_2} \x Z_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi(f_2) = X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi(g_2) = Z_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
+	& \Psi(m_0) = Z_{W_2} \x X_{W_2} \x \1_{W_{d-1}}\\
+	& \Psi(m_1) = X_{W_2} \x Z_{W_2} \x \1_{W_{d-1}}\\
+	& \Psi(m_2) = Y_{W_2} \x Y_{W_2} \x \1_{W_{d-1}}\\
+	& \Psi(J) = - \1_{W_2} \x \1_{W_2} \x \1_{W_{d-1}};
+\end{align}
+\item for the generators $\{ w_i \}_{i=1}^{r+5}$:
+\begin{align}
+	\Psi(w_i) = Z_{W_2} \x \1_{W_{d-1}} \x \Psi_0(a_i);
+\end{align}
+\item for the generators to embed the relation $f b_i f = c_i$:
+\begin{align}
+	\Psi(k_{i,1}) &= X_{W_2} \x \Psi_1(b_i) = X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_0(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
+	\Psi(k_{i,2}) &= \ketbra{x_1}{x_2} \x \Psi_1(b_if_0) + \ketbra{x_2}{x_1} \x \Psi_1(f_0b_i)\\
+	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_2x_1}+\ketbra{x_2x_1}{x_1x_2})\x\1_{W_{d-1}}\\
+	&+ \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_i)\\ 
+	\Psi(k_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(f_0b_if_0) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
+	&= \ketbra{x_1x_1}{x_1x_1} \x \1_{W_{d-1}} + \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
+	\Psi(k_{i,4}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_ic_i) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	&=(\ketbra{x_1x_1}{x_1x_1}+  \ketbra{x_1x_2}{x_1x_2}) \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi(k_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i) \\
+	&=\ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1}) \x \1_{W_{d-1}}\\
+	&+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_0(a_i);
+\end{align}
+\item for the generators to embed the relation $d_i b_j d_i = c_k$:
+\begin{align*}
+	\Psi(k_{c,1}) &= X_{W_2} \x \Psi_1(d_i) = X_{W_2} \x X_{W_2} \x \Psi_0(a_{i}) \\
+	\Psi(k_{c,2}) &= X_{W_2} \x \Psi_1(b_j) = X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
+	\Psi(k_{c,3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
+	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_{j}x_{i}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_0(a_i)\\
+	&+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_{i}a_{j}) \\
+	\Psi(k_{c,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(d_ib_jd_i) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
+	&= \ketbra{x_1x_1}{x_1x_1} \x \1_{W_{d-1}} + \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_ia_ja_i) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_0(a_i)\\
+	\Psi(k_{c,5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_{k}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi(k_{c,6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k})\\
+	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}}\\
+	 &+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_1(a_{k}).
+\end{align*}
+\end{itemize}
+\end{definition}
 
@@
 %%=====================================
-\section{Equations to embed $uxu^{-1} = x^2$}
-\label{sec:power2}
+\section{ The special property of $U$ and $O$}
+\label{sec:u_and_o}
 %%=====================================
-\input{power2_equations}
-
-%%=====================================
-\section{Equations to embed $uxu^{-1} = x^3$}
-\label{sec:power3}
-%%=====================================
-\input{power3_equations}
-
-%%=====================================
-\section{Equations to embed $uxu^{-1} = x^5$}
-\label{sec:power5}
-%%=====================================
-\input{power5_equations}
+\begin{lemma}
+	\label{lm:ux_independ}
+	Suppose there exist unitaries $U$ and $X$ which have the following forms
+	\begin{align}
+		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/r}{i},
+	\end{align}
+	where $d$ is an odd prime number with primitive root $r$,
+	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
+	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
+\end{lemma}
+Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^r$.
+In the self-test proof, this lemma will be a critical step.
+\begin{proof}
+We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
+Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
+such that 
+\begin{align}
+	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
+\end{align}
+We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
+\carl{We shouldn't be making extra assumptions that are not stated in the lemma.  This looks to me more like
+a definition of the variables $\{ k_i \}$, rather than an assumption.}
+The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
+Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
+where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
+Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.
+
+We start with proving that $\ket{x_{k_1}} = 0$.
+Proving $\ket{x_{k_i}} = 0$ for other $i$ follows a similar argument, so we briefly
+discuss about it in the end.
+The entry $\bra{1}M\ket{1}$ can be expressed as  
+\begin{align}
+	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/r^k}\braket{i}{1}.
+\end{align}
+For the term $\braket{1}{i/r^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
+$k = k_1$. We can conclude that 
+\begin{align}
+	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
+\end{align}
+Similarly we can determine that for all $j = 1,2\dots d-1$,
+\begin{align}
+	\bra{j}M\ket{j} 
+	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/r^k}\braket{i}{j} 
+	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
+\end{align}
+Hence we get $d-1$ equations with $d-1$ variables, and the linear system is
+\begin{align}
+	W \ket{x_{k_1}} = 0,
+\end{align}
+where $W(m,n) = \omega_d^{mn}$. Then we define
+\begin{align}
+	\tW = 
+	\begin{pmatrix}
+	1 & 1 \\
+	1 & W
+	\end{pmatrix}.
+\end{align}
+First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
+Next, we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
+and prove that it satisfies the condition
+that 
+\begin{align}
+	\tW \ket{\tx_{k_1}} = 0,
+\end{align}
+which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
+We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which is required by the first row of $\tW$.
+It can be proved by summing the known $d-1$ equations as follows
+\begin{align}
+	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
+	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
+	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
+	= \sum_{l = 1}^{d-1}- x_{k_1,l}
+\end{align}
+where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
+Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.
+
+For $\ket{x_{k_a}}$, we look at entries $\{\bra{j}M\ket{aj}\}_{j=1}^{d-1}$ for $a = 2 \dots d-1$ and get equations
+of the form
+\begin{align}
+	0 = \bra{j}M\ket{aj} = \sum_{l=1}^{d-1} x_{k_a, l} \omega_d^{ajl} 
+\end{align}
+The corresponding coefficient matrix has value $\omega_d^{amn}$ at coordinate $(m,n)$,
+so it is also a submatrix of a Vandermonde matrix. Similar argument gives us that $\ket{x_{k_a}} = 0$.
+
+To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
+$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
+\carl{Nice proof.  I like the use of the Vandermonde matrix.  We can think a little about possible simplifications.}
+\end{proof}
+Note that the primitive root $r$ in the lemma is not restricted to the set $\{2,3,5\}$, so this lemma works for any 
+odd prime number $d$.
 

### 2019-04-26 Draft/draft.tex
Honghao: small modification
Honghao: writing section 6.1

@@
 \newcommand{\LS}{LS}
+\newcommand{\tM}{\tilde{M}}
+\newcommand{\tN}{\tilde{N}}
 \newcommand{\tA}{\tilde{A}}
@@
 \newcommand{\pb}[2]{P_B(#1|#2)}
+\newcommand{\tpr}[2]{\tilde{P}(#1|#2)}
 
@@
 \label{def:q_strat}
-A quantum strategy presented in terms of observables for the linear system game $(H\ux = \uc)$ consists of 
+A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
 \begin{enumerate}
@@
 	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
-	consists of the joint state $\ket{\EPR{2}}$ and observables $M_1 = \pauliz$, $M_2 = \paulix$,
-	$N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
+	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
+	$\tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $\tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
 \end{definition}
@@
 
-%Note that we may use the term behaviour and correlation interchangeably.
-%The value of a strategy is given by
-%\begin{align}
-%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
-%\end{align}
-
-%The main contribution of our work is the construction of a correlation, which is the combination of 
-%the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
-%and the optimal correlation to violate the weighted CHSH inequality.  \carl{The reader does not 
-%know yet what a linear system game is, so this comment is more confusing than helpful.}
-%The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
-%primitive root. 
-%In the next part, we introduce the definition of self-testing, the definition of linear system game, 
-%and its operator solution, 
-%following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
-
 \carl{Before the next definition, you should define what a ``correlation'' is.}
@@
 to give a general robust self-testing definition and it suffices to just give our robust self-testing result.}
-%\begin{definition}[Self-testing]
-%	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
-%	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
-%	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
-%	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
-%	such that 	
-%	\begin{align*}
-%		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
-%	\end{align*}
-%\end{definition}
 
 \carl{Section 2 needs to be cleaned up in some places, but overall it is pretty good.}
-
-%The main tool to understand linear system game is through its solution group over $\Z_d$.
-%\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
-%	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
-%	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
-%	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
-%	\begin{align}
-%		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
-%	\end{align}
-%	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
-%	\begin{align}
-%		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
-%	\end{align}
-%	Then the solution group has presentation 
-%	\begin{align}
-%	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
-%	\end{align}
-%\end{definition}
-%Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
-%Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
-%\begin{definition}[Operator solution]
-%	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
-%	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
-%	representation mapping $\J$ to $\overline{\omega_d}\1$.
-%\end{definition}
-%What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
-%linear system game from its operator solution and vice versa.
 
@@
 \begin{definition}
+\label{def:gamma}
 The presentation of $\Gamma$ has order-$2$ generators:
@@
 \begin{align}
+	\label{eq:w_subspace}
 	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
@@
 \begin{definition}
+\label{def:rep_gamma}
 The representation $\Psi$ of $\Gamma$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
@@
 \end{definition}
-
-%======================================
-\section{The extended weighted CHSH test}
+The validation of $\Psi_1$ and $\Psi$ are done in Slofstra's work \cite{slofstra2017}.
+
+%====================================================
+\section{Robust self-testing of $\ket{\EPR{2}}$ \textit{via} $\I_\alpha$}
 \label{sec:chsh}
-%======================================
-Before introducing the extended weighted CHSH test, we fill in some background about the weighted CHSH inequality,
-namely, that its maximal violation can self-test $2$-dimensional EPR pair and rotated Pauli operators.
-The robust self-testing result is summarized in the following theorem.
+%====================================================
+In this section, we show how the weighted CHSH inequality can be used to self-test $\ket{\EPR{2}}$ robustly.
+Intuitively, it means that if some quantum strategy achieves a value $\ip{\I_\alpha}$ that is close to $\ip{\I_\alpha}_{\max}$,
+then the shared state must be close to $\ket{\EPR{2}}$ and their observables are close to rotated Pauli operators up to
+some local isometry.
+The formal statement is given in the theorem below. Since the proof uses the same technique as the one used in Ref.~\cite{bamps2015},
+we defer the proof till \cref{sec:selftest}. Instead, we only list the key relations used in the proof because they will be reused in the later parts of 
+the paper.
 \begin{theorem}
 \label{thm:selftest}
-	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the violation
-	at least $2\sqrt{1+\alpha^2} - \epsilon$
-	for some $\epsilon$, then
+	Suppose the quantum strategy $(\ket{\psi}, \{M_x:=M_x^0-M_x^1\}_{x=1,2}, \{N_y :=N_y^0-N_y^1\}_{y = 1,2} )$ achieves that
+	$\ip{\I_\alpha} \geq 2\sqrt{1+\alpha^2} - \epsilon$
+	for some $\epsilon > 0$, then we define $\mu := \arctan(1/\alpha)$ and
 	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
-	\begin{align}
-		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha^2+\frac{1}{\alpha}) \sqrt{\epsilon})
-	\end{align}
-	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $A_x, B_y$ are 
+	\begin{align*}
+		\| \Phi( M_x \x N_y \ket{\psi}) -\ket{aux} \x (\tM_x \x \tN_y) \ket{\EPR{2}}  \| = O(\frac{1}{\cos^2(\mu)\sin^{1/2}(\mu)}+
+		\frac{1}{\sin(\mu)^{3/2}})) \sqrt{\epsilon}
+	\end{align*}
+	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $\tM_x, \tN_y$ are 
 	defined in \cref{def:ideal}.  \carl{You're using both ``aux'' and ``junk'' for the auxilliary state.  Also you need
@@
 \end{theorem}
-Our approach is very similar to the one used in Ref.~\cite{bamps2015} so we 
-defer the proof of \cref{thm:selftest} till \cref{sec:selftest}.
-After proving the robust self-testing result, we take one step further and observe an interesting property of the 
-product of Bob's observables.
+We follow the convention and define $c := \cos(\mu)$, $s := \sin(\mu)$, and
+\begin{align}
+	&Z_A := M_1 && X_A := M_2\\
+	&Z_B := \frac{N_1+N_2}{2c} && X_B := \frac{N_1-N_2}{2s}.
+\end{align}
+The key relations that we will reuse are
+\begin{align}
+	\label{eq:za-zb}& Z_A\ket{\psi} \appd{\frac{\sqrt{s\epsilon}}{c}} Z_B\ket{\psi},\\
+	\label{eq:xa-xb}&X_A\ket{\psi} \appd{\frac{\sqrt{\epsilon}}{\sqrt{s}}} X_B \ket{\psi}, \\
+	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{\frac{c+1}{c\sqrt{s}} \se} X_B(\1-Z_A) \ket{\psi},\\
+	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{ \frac{s+1}{c\sqrt{s}} \se} Z_B(\1-X_A) \ket{\psi},\\
+	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{\frac{1+c+s}{c\sqrt{s}} \se} -X_AZ_A \ket{\psi},\\
+	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{\frac{2s^2+cs+c+s}{cs\sqrt{s}} \sqrt{\epsilon}} -X_BZ_B \ket{\psi},
+\end{align}
+where \cref{eq:zaxaxbzb} can be derived from \cref{eq:za-zb}, \cref{eq:xa-xb} and \cref{eq:zaxa}.
+%==========================
+\section{The full test}
+\label{sec:full_test}
+%==========================
+The full test consists of three subtest: the linear constraint test,
+the extended weighted CHSH test and a commutation test. We explain how the three tests are conducted and
+combined below.
+
+\textbf{The linear constraint test}.
+Recall that the the linear constraint test with solution group $\Gamma$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
+equations labelled by $i \in \{1, 2 \dots \mr\}$.
+We denote the linear system associated with the linear constraint test by $H\underline{x} = \uc$ and
+define $X_i := \{ \ux : \sum_{k} H(i,k)\ux(k) = \uc(i) \}$ and $I_i = \{ k : H(i,k) = 1\}$.
+From the construction of $\Gamma$, we know that $| I_i| \leq 3$.
+The correspondence between $\ux$ and the generators of $\Gamma$ is that
+\begin{align*}
+	&\ux(j) := a_j &&&&\text{ for } j = 1 \dots r+5 \\
+	&\ux(r+6+j) := f_j&& \ux(r+9+j) := g_j &&\text{ for } j = 0,1,2 
+\end{align*} 
+The correspondence can be arbitrary for $j > r+11$.
+We conduct the linear constraint test in a way such that Bob is always get a variable label
+but Alice gets either an equation label, in which case she needs to give the full assignment to this equation,
+or a pair of equation label and variable label, in which case she only needs to give the assignment to the particular 
+variable in the given equation. In this way, we force Alice and Bob to use an binary observable strategy for the linear constraint 
+test.
+
+\textbf{The extended weighted CHSH test}.
+In this test, 
+the input alphabets are $\calX = \calY = \{\ast, 1, 2, \nr+1,\nr+2\}$.
+For each question, there is an associated answer set:
+\begin{itemize}
+	\item when the question is $\ast$, the answer set is $\{\diamond, \perp\}$;
+	\item when the question is $1$ or $2$, the answer set is $\{0,1\}$;
+	\item when the question is $\nr+1$ or $\nr+2$, the answer set is $\{0, 1, \perp\}$.
+\end{itemize}
+Note that when the referee wants to ask Alice $x = 1,2$, the referee gives Alice a pair $(i_x. x)$ where 
+$i_x$ labels an equation containing the variable labelled by $x$. 
+For simplicity we omit the $i_x$ part in the alphabet $\calX$.
+Later we will show that the $i_x$ part can be made implicit.
+The test is conducted in the following way:
+\begin{enumerate}
+	\item if $x = y = \ast$, Alice and Bob should answer with $a = b \in \{\diamond, \perp\}$;
+	\item if $x = y \in \{1,2\}$, Alice and Bob should answer with $a = b \in \{0, 1\}$, as in the linear constraint test;
+	\item if $x = y \in \{n+1, n+2\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
+	\item if $x \in \{1,2\}$ and $y \in \{n+1, n+2\}$, 
+		\begin{enumerate}
+		\item if they answer with $a,b \in \{0,1\}$, then
+	they should maximize $\ip{\I_{\cot(-\pi/d)}}$ with Alice and Bob's roles flipped, 
+		\item if Bob answers with $\perp$, then Alice's answer doesn't matter;
+		\end{enumerate}
+	\item if $x \in \{n+1, n+2\}$ and $y \in \{1,2\}$,
+	\begin{enumerate} 
+		\item if they answer with $a,b \in \{0,1\}$, then
+		they should maximize $\ip{\I_{\cot(-\pi/d)}}$, 
+		\item if Alice answers with $\perp$, then Bob's answer doesn't matter;
+	\end{enumerate}
+	\item $x \in \{n+1,n+2\}, y = \ast$ 
+		\begin{enumerate}
+		\item if Bob answers with $\diamond$, Alice should answer with $\{0.1\}$ but not $\perp$, 
+		\item if Bob answers with $\perp$ Alice should answer with $\perp$ too;
+		\end{enumerate}
+	\item $x = \ast, y \in \{n+1, n+2\}$
+	\begin{enumerate}
+		\item if Alice answers with $\diamond$, Bob should answer with $\{0.1\}$ but not $\perp$, 
+		\item if Alice answers $\perp$, Bob should answer $\perp$ too.
+	\end{enumerate}
+\end{enumerate}
+
+\textbf{The commutation test.}
+In this test, we reuse questions from the two other tests so the answer
+set for each question is the same across the tests.
+There are $8$ test cases.
+In each test case, Alice is given one of two questions.
+One of the possible question is to assign a value to some variable of the linear constraint test.
+Again, the equation label is implicit when this variable is given.
+The other possibility is to answer $\nr+1$ or $\nr+2$.
+Bob is given both of the question so he needs to give answers to both questions.
+Their answers should agree on the question that is given to both.
+The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
+Alice's input is determined by the pair so she receives one of the two questions with equal probability.
+
+The full correlation is generated by a strategy that can pass all the three tests. We give the ideal strategy first.
+%--------------------------------------------
+\subsection{The ideal strategy}
+%--------------------------------------------
+Recall the two subspaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}. 
+In the ideal strategy Alice and Bob share the state 
+\begin{align*}
+\ket{\psi} = &(\frac{1}{\sqrt{2}} \ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
+=&(\frac{1}{\sqrt{2}} \ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
+\end{align*}
+Here we introduce the second basis $\{ \ket{j} \}_{j=1}^{d-1}$ of $W_{d-1}$ so that
+the observables used in the extended weighted CHSH test have a simpler form.
+The two basis are related by
+\begin{align*}
+	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
+	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) && \text{for } j = 1 \dots \frac{d-1}{2}.
+\end{align*}
+We define two subspaces $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$ on
+$W_{d-1}$ and
+define $\Pi_V$ and $\Pi_{V^\perp}$ to be the corresponding projectors. Note that $V$ is the subspace on which they should maximize $\ip{\I_{\cot(-\pi/d)}}$.
+We define the states for the measurements used in the extended weighted CHSH test as follows
+\begin{align*}
+	&\ket{1_1} = \cos(-\pi/2d)\ket{1} + \sin(-\pi/2d)\ket{d-1}
+	&&\ket{(d-1)_1} = \sin(-\pi/2d)\ket{1} - \cos(-\pi/2d)\ket{d-1}\\
+	&\ket{1_2} = \cos(-\pi/2d)\ket{1} - \sin(-\pi/2d)\ket{d-1}
+	&&\ket{(d-1)_2} = \sin(-\pi/2d)\ket{1} + \cos(-\pi/2d)\ket{d-1}\\
+	&\ket{+} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
+	&&\ket{-} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
+\end{align*}
+Then the measurements are
+\begin{align*}
+	&M_\ast^\diamond =(\1_{W_2})^{\x 2} \x \Pi_V && M_\ast^\perp = M_{n+1}^\perp = M_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
+	&N_\ast^\diamond = (\1_{W_2})^{\x 2} \x \Pi_V && N_\ast^\perp = N_{n+1}^\perp = N_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
+	&M_{n+1}^0 =N_{n+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && M_{n+1}^1=N_{n+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
+	&M_{n+2}^0 =N_{n+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{+}{+} && M_{n+2}^1= N_{n+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{-}{-}\\
+	&M_1^0 = N_1^0 =(\1_{W_2})^{\x 2} \x  \ketbra{1_1}{1_1} && M_1^1 = N_1^1 =(\1_{W_2})^{\x 2} \x  \ketbra{(d-1)_1}{(d-1)_1}\\
+	&M_2^0 = N_2^0 = (\1_{W_2})^{\x 2} \x \ketbra{1_2}{1_2} && M_1^1 = N_1^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_2}{(d-1)_2}.
+\end{align*}
+To present the observables used in the linear constraints test, we relabel the generators of $\Gamma$ as $x_i$ for $i = 1 \dots \nr$. Then the 
+observables are
+\begin{align}
+	M_i = N_i = \Psi(x_i),
+\end{align}
+where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
+To make sure the strategy is correct, there are some facts to check.
 \begin{proposition}
-\label{prop:2d-subspace}
-	Let $\mu = \arctan(1/\alpha)$ for some $\alpha$.
-	If a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
-	violation of  $\I_{\alpha}$, then \hf{the only eigenvalues of $\tilde{B}_0\tilde{B}_1$ on the support of 
-	$\tilde{\rho}_B = \Tr_A(\ketbra{\tpsi}{\tpsi})$
-	are $e^{i2\mu}$ and $e^{-i2\mu}$.}  \carl{Make clear
-	that we mean that these are the only eigenvalues.}
+Let $M_1 = N_1 :=\Psi(a_1)$, $M_2 = N_2 := \Psi(a_2)$, $M_3 = N_3 := \Psi(a_3)$
+and $M_4 = N_4 := \Psi(a_4)$, then
+\begin{align}
+	\label{eq:mn_preserve} &M_i N_i \ket{\psi} = \ket{\psi} && \text{for } i = 1 \dots 4,\\
+	\label{eq:o2_comm} &(M_3M_4)M_2(M_4M_3) = M_2,
+\end{align}
+and similar commutation relation holds on Bob's side too.
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:2d-subspace}]
-	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we define
+\begin{proof}
+	Since all the operators involved in this proposition act trivially on $W_2^{\x 2}$, we focus on
+	their actions on $W_{d-1}$. In the later proof, by $\ket{\psi}$ we mean the part of $\ket{\psi}$ on $W_{d-1}$.
+
+	We prove \cref{eq:o2_comm} first. It is simple to check that
+	\begin{align}
+		&M_1M_2= \sum_{j=1}^{d-1} \omega_d^{j} \ketbra{x_j}{x_j},\\
+		&M_3M_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
+	\end{align}
+	and that 
+	\begin{align}
+		M_3M_4 M_2 M_4 M_3 = &\sum_{j=0}^{(d-3)/2} M_3M_4 (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) M_4M_3\\
+		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}} = M_2.
+	\end{align}
+
+	Next we prove \cref{eq:mn_preserve}. It is straightforward to see that $M_iN_i \ket{\psi} = \ket{\psi}$ for $i = 1,2$.
+	Before checking $i=3$ and $i=4$, we first observe that
+	\begin{align}
+		M_3M_4 N_3 N_4 \ket{\psi} = \ket{\psi}.
+	\end{align}
+	The eigenvectors of $M_3M_4$ and $N_3N_4$ are 
+        \begin{align}
+        		\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
+        \end{align}
+        Hence we can express $\ket{x_{r^j}}$ in terms of $\ket{u_k}$ as 
+        \begin{align}
+        		\ket{x_{r^j}} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
+        \end{align}
+        Then $M_4$ acts on $\ket{x_{r^j}}$ by
         \begin{align*}
-	\tilde{Z}_A = \tA_1, &&
-	\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu).
+        		M_4 \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} M_4\left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
+        	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
+        	=&\frac{1}{\sqrt{d-1}} \left(\ket{u_0} + (-1)^j\ket{u_{(d-1)/2}}  + 
+        	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_{d-1-k}} + \omega_{d-1}^{jk} \ket{u_{k}})\right) \\
+        	=& \ket{x_{r^{d-1-j}}}.
         \end{align*}
-	Substituting $\epsilon = 0$ into \cref{eq:zazb} we know that 
-	\begin{align}
-		\tZ_B \ket{\tpsi} = \tZ_A \ket{\psi}.
-	\end{align}
-	Using this relation, we get
-	\begin{align}
-		\tZ_B^2\ket{\tpsi} = \tZ_B \tZ_A\ket{\tpsi} = \tZ_A \tZ_B \ket{\tpsi} = \tZ_A^2 \ket{\tpsi} = \ket{\tpsi},
-	\end{align}
-	where we also use the facts that $\tZ_A$ and $\tZ_B$ commute and $\tZ_A^2 = A_1^2 = \1$.
-	Hence we can conclude that $\tZ_B^2 =\1$ on $\supp(\tilde{\rho}_B)$.
-	Expanding $\tilde{Z}_B^2$ we get
-	\begin{align*}
-		\1 = \tilde{Z}_B^2 = \frac{\tB_1^2 + \tB_1\tB_2 + \tB_2\tB_1 + \tB_2^2}{4\cos(\mu)^2}
-		=\frac{2\1 + \tB_1\tB_2 + \tB_2\tB_1}{4\cos^2(\mu)},
-	\end{align*}
-	so we can derive that 
-	\begin{align}
-	\label{eq:eig_v}
-		\tB_1\tB_2 + \tB_2\tB_1 = 2(2\cos^2(\mu)-1)\1 = 2 \cos(2\mu) \1.
-	\end{align}
-	\hf{Since $\tB_1\tB_2$ is the product of two unitaries,}
-	we can assume the eigen-decomposition of $\tB_1\tB_2$ is
-	\begin{align}
-		\tB_1\tB_2 = \sum_{i=1}^m \lambda_i \ketbra{i}{i}
-	\end{align}
-	for some orthonormal set of eigenvectors $\{ \ket{i} \}_{i=1}^m$
-	and $\norm{\lambda_i} =1$ for $1 \leq i \leq m$.
-	Eq.~\ref{eq:eig_v} tells us that for each $1 \leq i \leq m$
-	\begin{align*}
-		\lambda_i + \lambda_i^{-1} = 2\Re(\lambda_i) = 2 \cos(2\mu),
-	\end{align*}
-	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.	
-%	\begin{align}
-%		\ket{\tpsi} = \sum_{i=1}^m \frac{c_i}{\sqrt{2}} (\ket{u_{i,0}}\ket{u_{i,0}}+\ket{u_{i,1}}\ket{u_{i,1}}),
-%	\end{align}
-%	where $c_i$'s are coefficients such that $\sum_{i=1}^m \norm{c_i}^2 = 1$.
-%	The special property of the subspace $V_i = \spn( \ket{u_{i,0}}, \ket{u_{i,1}})$ is that 
-%	\begin{align*}
-%	(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,0}} = 2\cos(-\pi/2d) \ket{u_{i,0}} 
-%	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,1}} = -2\cos(-\pi/2d) \ket{u_{i,1}}\\
-%	(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,0}} = 2\sin(-\pi/2d) \ket{u_{i,1}} 
-%	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,1}} = 2\sin(-\pi/2d) \ket{u_{i,0}}.
-%	\end{align*}
-%	It is straightforward to calculate that 
-%	\begin{align*}
-%		\tilde{B}_0\tilde{B}_1 \ket{u_{i,0}} = \cos(\pi/d) \ket{u_{i,0}} -\sin(\pi/d) \ket{u_{i,1}},&&
-%		\tilde{B}_0\tilde{B}_1\ket{u_{i,1}} = \sin(\pi/d)\ket{u_{i,0}} + \cos(\pi/d) \ket{u_{i,1}},
-%	\end{align*}
-%	so we can conclude that 
-%	\begin{align*}
-%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} + i\ket{u_{i,1}}) = e^{i \frac{\pi}{d}} (\ket{u_{i,0}} + i\ket{u_{i,1}}), &&
-%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} - i\ket{u_{i,1}}) = e^{-i \frac{\pi}{d}} (\ket{u_{i,0}} - i\ket{u_{i,1}}).
-%	\end{align*}
-%	Hence each $V_i$ is spanned by $\omega_d$-eigenvector and $\omega_d^{-1}$-eigenvector of $\tB_0\tB_1$.
+        Then we show that $M_4  N_4 \ket{\psi} = \ket{\psi}$ as 
+        \begin{align}
+        	M_4 N_4 \ket{\psi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} M_4  N_4 \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
+        	= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\psi},
+        \end{align}
+	Combining it with the fact that $M_3M_4 N_3N_4 \ket{\psi} = \ket{\psi}$, we can conclude that
+	$M_3N_3 \ket{\psi} = \ket{\psi}$.
 \end{proof}
-
-The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
-Alice and Bob's operator solution of $\LS$ has eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
-In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
-$X$ has the eigen-structure required by \cref{lm:ux_independ}.
-We denote this game that enforces the eigenvalues of the observable $X$ by
-$\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
-We remark that for the extended weighted CHSH test, the primitive root of $d$ is irrelevant,
-so we drop the superscript $(r)$.
-\carl{You need to be more clear --- after reading this, I am still not sure what mathematical object ``$\CHSH_X$'' refers to.}
-
-In this test, Alice and Bob each gets a question $x$,$y \in \{ 1, 2, \ast\}$ and 
-they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
-The correlation $C(\dr{2})$ is the optimal correlation of this test.
-Before presenting the optimal correlation, we give intuitions about how the players should behave.
-\begin{itemize}
-	\item \textbf{Case 1:} when $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
-	their answer should agree;
-	\item \textbf{Case 2a:} when $x,y \in \{1,2\}$ and if they answer with $a,b \in \{0,1\}$, then
-	their answers are scored according to $I_{\cot(-\pi/d)}$;
-	\item \textbf{Case 2b:} when $x,y \in \{1,2\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
-	\item \textbf{Case 3:} when $x \in {1,2}, y = \ast$, if Bob answers $\diamond$, 
-	Alice should answer with $\{0.1\}$ but not $\perp$,
-	if Bob answers $\perp$, Alice should answer $\perp$ too.
-\end{itemize}
-\textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$.
-We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ \carl{(That's not 
-the way I usually see the $\setminus$ symbol used.)} and
-define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
-maximize $\langle I_{\cot(-\pi/d)} \rangle$.
-
-For completeness, we show the ideal correlation in the following three charts and then give the projectors. 
-Note that we don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ for all possible $x$,$y$ 
-because they are irrelevant.
+The similar result, i.e., $M_jN_j \ket{\psi} = \ket{\psi}$ for $j = 1 \dots \nr$, are easy to check because all the observables are defined by $M_j, N_j$ for $j=1,2,3,4$.
+An interesting property of $U := M_3M_4$ and $O := M_1M_2$ is summarized in the proposition below. 
+\begin{lemma}
+	\label{lm:uo_independ}
+	The unitaries $O$ and $U$ of the form
+	\begin{align}
+		O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j} && U = \sum_{j=1}^{d-1}\ketbra{x_{j r^{-1}}}{x_j},
+	\end{align}
+	where $d$ is an odd prime number with primitive root $r$, generates
+	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
+\end{lemma}
+The proof of this lemma is provided in \cref{sec:u_and_o}.
+Our self-test argument certifies that Alice and Bob has such $O$ and $U$ in their hands, so
+it provides another angle to justify our self-testing argument.
+
+%---------------------------------------------------
+\subsection{The full correlation}
+%---------------------------------------------------
+The full correlation is generated by the ideal strategy presented in the previous subsection.
+To help readers understanding later parts of this paper better, 
+parts of the full correlation is given in the tables below.
 \begin{table}[H]
@@
 \end{tabular}
-\caption{Alice and Bob's behaviour when $x=y=\ast$.}
+\caption{The correlation for $x=y=\ast$.}
 \end{center}
@@
 \multicolumn{2}{|c|}{} &
-\multicolumn{3}{|c|}{$x=1$}&
-\multicolumn{3}{|c|}{$x=2$} \\
+\multicolumn{3}{|c|}{$x=\nr+1$}&
+\multicolumn{3}{|c|}{$x=\nr+2$} \\
 \cline{3-8}
@@
 \hline
-\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{\sin^2(\pi/d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
+\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
 & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/d)}{d-1}$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
+&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
 &  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
 \hline
-\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{\sin^2(\pi/d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
+\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
 $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/d)}{d-1}$ & $\frac{\cos^2(\pi/d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
+&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
 $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
@@
 \end{center}
-\caption{Alice and Bob's behaviour when $x,y \in [2]$.}
+\caption{The correlation for $x \in \{n+1, n+2\}$ and $y \in \{1,2\}$.}
+\label{tb:chsh}
+\end{table}
+We don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ for all possible $x$,$y$ 
+because they are irrelevant.
+Note that when $x \in \{1,2\}$ and $y \in \{\nr+1, \nr+2\}$, the correlation table is 
+the transpose of Table~\ref{tb:chsh}, so we omit it here.
+
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{|c|c||c|c|c|c|c|c|c|c|}
+\hline
+\multicolumn{2}{|c|}{} &
+\multicolumn{3}{|c|}{$x=\nr+1$}&
+\multicolumn{3}{|c|}{$x=\nr+2$}&
+\multicolumn{2}{|c|}{$x=\ast$}\\
+\cline{3-10}
+\multicolumn{2}{|c|}{} &
+$a = 0$ & $a=1$ & $a=\perp$ &
+$a = 0$ & $a=1$ & $a=\perp$ &
+$a = \diamond$ & $a = \perp$\\
+\hline
+\hline
+\multirow{3}{*}{$y = \nr+1$} & $b=0$ & $\frac{1}{d-1}$ & $0$ & 0 
+& $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ & 0 & $\frac{1}{d-1}$ & 0 \\
+\cline{2-10}
+&$b=1$ & 0 & $\frac{1}{d-1}$ & $0$ 
+&  $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ & 0 &$\frac{1}{d-1}$ & 0 \\
+\cline{2-10}
+&$b=\perp$ & 0 & 0 & $\frac{d-3}{d-1}$ 
+&  0 & 0 &  $\frac{d-3}{d-1} $ &0 & $\frac{d-3}{d-1}$ \\
+\hline
+\multirow{3}{*}{$y = \nr+2$} & $b=0$ & $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ & 0 
+& $\frac{1}{d-1}$ & $0$ & 0 & $\frac{1}{d-1}$ & 0 \\
+\cline{2-10}
+&$b=1$ & $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ & $0$ 
+&  0 & $\frac{1}{d-1}$ & $0$ &$\frac{1}{d-1}$ & 0 \\
+\cline{2-10}
+&$b=\perp$ & 0 & 0 & \small $\frac{d-3}{d-1}$ 
+&  0 & 0 & \small $\frac{d-3}{d-1} $ &0 &\small $\frac{d-3}{d-1}$ \\
+\hline
+\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $\frac{1}{d-1}$ & $\frac{1}{d-1}$ & 0 
+& $\frac{1}{d-1}$ & $\frac{1}{d-1}$ & 0 & $\frac{2}{d-1}$ & 0 \\
+\cline{2-10}
+&$b=\perp$ & 0 & 0 & $\frac{d-3}{d-1}$ 
+&  0 & 0 & \small $\frac{d-3}{d-1} $ &0 & \small $\frac{d-3}{d-1}$ \\
+\hline
+\end{tabular}
+\end{center}
+\caption{The correlation for $x ,y\in\{\nr+1,\nr+2, \ast\} $.}
 \end{table}
@@
 \multicolumn{2}{|c|}{} &
-\multicolumn{3}{|c|}{$x=1$}&
-\multicolumn{3}{|c|}{$x=2$} \\
+\multicolumn{6}{|c|}{$y=(\nr+1, r+6)$}\\
 \cline{3-8}
 \multicolumn{2}{|c|}{} &
-$a = 0$ & $a=1$ & $a=\perp$ &
-$a = 0$ & $a=1$ & $a=\perp$\\
+$b = 00$ & $b=01$ & 
+$b = 10$ & $b=11$ &
+$b = \perp0$ & $b= \perp1$   \\
 \hline
 \hline
-\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/(d-1)$ & $1/(d-1)$ & 0 
-& $1/(d-1)$ & $1/(d-1)$ & 0 \\
+\multirow{3}{*}{$x = \nr+1$} & $a=0$ & $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ &  $0$
+& $0$ & $0$ & $0$  \\
 \cline{2-8}
-&$b=\perp$ & 0 & 0 & $\frac{d-3}{d-1}$ 
-&  0 & 0 & \small $\frac{d-3}{d-1} $  \\
+&$a=1$ & $0$ & $0 $ & $\frac{1}{2d-2}$ 
+&  $\frac{1}{2d-2}$ & $0$ & $0$  \\
+\cline{2-8}
+&$b=\perp$ & 0 & 0 & $0$ 
+&  0 & $\frac{d-3}{2d-2}$ & $\frac{d-3}{2d-2} $  \\
+\hline
+\multirow{2}{*}{$x = r+6$} & $a=0$ & $\frac{1}{2d-2}$ & $0$ & $\frac{1}{2d-2}$ 
+& $0$ & $\frac{d-3}{2d-2}$ & 0  \\
+\cline{2-8}
+&$a=1$ & $0$ & $\frac{1}{2d-2}$ & $0$ 
+&  $\frac{1}{2d-2}$ & $0$ & $\frac{d-3}{2d-2}$  \\
 \hline
@@
 \end{center}
-\caption{Alice and Bob's behaviour when $x\in [2]$ and $y = \ast$.}
+\caption{The correlation for the commutation test between $M_{r+6}$ and $M_{\nr+1}$.}
 \end{table}
-Alice's projectors are 
-\begin{align*}
-	&A_\ast^\diamond = \Pi_V, A_\ast^\perp = \Pi_V^\perp \\
-	&A_1^0 = \ketbra{u_1}{u_1}, A_1^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_1^\perp = \Pi_V^\perp\\
-	&A_2^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
-	A_2^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_2^\perp = \Pi_V^\perp.
-\end{align*}
-Bob's projectors are 
-\begin{align*}
-	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
-	&B_1^0|_V = \left( \cos(\frac{\pi}{d})\ket{u_1} + \sin(\frac{\pi}{d})\ket{u_{d-1}}\right)
-	\left( \cos(\frac{\pi}{d})\bra{u_1} + \sin(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
-	&B_1^1|_V = \left( \sin(\frac{\pi}{d})\ket{u_1} - \cos(\frac{\pi}{d})\ket{u_{d-1}}\right)
-	\left( \sin(\frac{\pi}{d})\bra{u_1} - \cos(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
-	&B_2^0|_V = \left( \cos(\frac{\pi}{d})\ket{u_1} - \sin(\frac{\pi}{d})\ket{u_{d-1}}\right)
-	\left( \cos(\frac{\pi}{d})\bra{u_1} - \sin(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
-	&B_2^1|_V = \left( \sin(\frac{\pi}{d})\ket{u_1} + \cos(\frac{\pi}{d})\ket{u_{d-1}}\right)
-	\left( \sin(\frac{\pi}{d})\bra{u_1} + \cos(\frac{\pi}{d})\bra{u_{d-1}}\right).
-\end{align*}
-About Bob's projectors for input $y \in [2]+1$, we are only interested in their actions when restricted 
-to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.
-
-\carl{This good, but I imagine a reader being a little confused about what you are doing
-with these correlations (since the previous subsection wasn't very clear).}
-
-The self-testing property of this correlation is summarized in the following lemma.
-\begin{lemma}
-	\label{lm:chsh_comp}
-	Suppose a quantum strategy $\left(\{\{\tA_x^a\}_a\}_x, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}\right)$
-	achieves the optimal correlation of the weighted $\CHSH$ test, 
-	and let $\ket{\tpsi'} = \tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}/\norm{\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}}^2$,
-	then there exists isometries $\Phi_A$ and $\Phi_B$ 
-	and a quantum state $\ket{junk}$
-	such that 
-	\begin{align*}
-		&\Phi_A\x \Phi_B \left( \ket{\tpsi'}\right) = \ket{\EPR{2}}\x \ket{junk} \\
-		&\Phi_A\x \Phi_B \left[\left(\1 \x  \frac{\tB_1 + \tB_2}{2\cos(\pi/d)}\right)\ket{\tpsi'}\right]
-		=[(\1 \x \pauliz) \ket{\EPR{2}}] \x \ket{junk} \\
-		&\Phi_A\x \Phi_B \left[\left(\1 \x  \frac{\tB_1 - \tB_2}{-2\sin(\pi/d)}\right)\ket{\tpsi'} \right]
-		=[(\1 \x \paulix) \ket{\EPR{2}}] \x \ket{junk} 
-	\end{align*}
-	where $\tB_1 = \tB_1^0 - \tB_1^1$ and $\tB_2 = \tB_2^0 - \tB_2^1$.
-\end{lemma}
-\begin{proof}
-Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \x\tB_y^b$ in the following proof.
-
-From the marginal distribution $\pb{\diamond}{\ast} = \pa{0}{1}+\pa{1}{1} = 2/(d-1)$,
-we know $\| \tB_\ast^\diamond \ket{\tpsi} \| = \| (\tA_1^0+\tA_1^1) \ket{\tpsi}\| = \sqrt{2/d-1}$.
-Since $\pr{0\diamond}{1\ast} + \pr{1\diamond}{1\ast} = 2/(d-1)$, we find that 
-\begin{align*}
-	\frac{\bra{\tpsi}\tB_\ast^\diamond (\tA_1^0+\tA_1^1) \tB_\ast^\diamond\ket{\tpsi}}{ \| \tB_\ast^\diamond \ket{\tpsi} \|^2} = 1,
-\end{align*}
-which means that 
-\begin{align}
-	(\tA_1^0+\tA_1^1)\tB_\ast^\diamond \ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
-\end{align}
-Using the commutation relation between $(\tA_1^0+\tA_1^1)$ and $\tB_\ast^\diamond$, we get
-\begin{align*}
-	\frac{\bra{\tpsi} (\tA_1^0+\tA_1^1) \tB_\ast^\diamond(\tA_1^0+\tA_1^1)\ket{\tpsi}}{ \| (\tA_1^0+\tA_1^1) \ket{\tpsi} \|^2} = 1,
-\end{align*}
-Similar argument gives us that 
-\begin{align}
-	\tB_\ast^\diamond (\tA_1^0+\tA_1^1) \ket{\tpsi} = (\tA_1^0+\tA_1^1)\ket{\tpsi}.
-\end{align}
-The two equations above can be chained by commutativity to reach the conclusion that 
-\begin{align}
-	(\tA_1^0+\tA_1^1)\ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
-\end{align}
-Following the same line of argument, we can conclude that
-\begin{align}
-	\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi} = (\tA_1^0+\tA_1^1)\ket{\tpsi} = (\tA_2^0+\tA_2^1)\ket{\tpsi}.
-\end{align}
-Looking at the marginal distribution when Alice and Bob output $\perp$, we conclude that 
-\begin{align}
-	\tB_\ast^\perp \ket{\tpsi} = \tA_\ast^\perp \ket{\tpsi} = \tA_1^\perp \ket{\tpsi} = \tA_2^\perp \ket{\tpsi},
-\end{align}
-with similar arguments.
-
-Next we examine the CHSH-type correlation when $x,y \in [2]+1$,
-\begin{align*}
-	   \bra{\tpsi} \tA_1^0\tB_1^0 \ket{\tpsi} 
-	= &\bra{\tpsi}(\tA_\ast^\diamond + \tA_\ast^\perp) \tA_1^0\tB_1^0 (\tA_\ast^\diamond + \tA_\ast^\perp)\ket{\tpsi} \\
-	= & \bra{\tpsi}\tA_\ast^\diamond \tA_1^0\tB_1^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_1^0\tB_1^0 \tA_\ast^\perp\ket{\tpsi} \\
-	&+\bra{\tpsi}\tA_\ast^\perp \tA_1^0\tB_1^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\perp \tA_1^0\tB_1^0 \tA_\ast^\perp\ket{\tpsi}\\
-	= & \bra{\tpsi}\tB_\ast^\diamond \tA_1^0\tB_1^0 \tB_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_1^0\tB_1^0 \tA_0^\perp\ket{\tpsi} \\
-	&+\bra{\tpsi}\tA_0^\perp \tA_1^0\tB_1^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_0^\perp \tA_1^0\tB_1^0 \tA_0^\perp\ket{\tpsi}\\
-	=&\bra{\tpsi}\tB_\ast^\diamond \tA_1^0\tB_1^0 \tB_\ast^\diamond\ket{\tpsi},
-\end{align*}
-where we use the facts that $\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi}$, $\tA_\ast^\perp \ket{\tpsi} = \tA_1^\perp \ket{\tpsi}$ and that 
-$\spn(\tA_1^0) \cap \spn(\tA_0^\perp) = \emptyset$. 
-This means that if Alice and Bob share the state $\tB_\ast^\diamond \ket{\tpsi}/\|\tB_\ast^\diamond \ket{\tpsi}\|$ and apply 
-$\tA_1^0\tB_1^0$, the conditional probability is
-\begin{align}
-	\frac{\bra{\tpsi}\tB_\ast^\diamond \tA_1^0\tB_1^0 \tB_\ast^\diamond\ket{\tpsi}}{\bra{\tpsi} \tB_\ast^\diamond \tB_\ast^\diamond \ket{\tpsi}} = \frac{\cos^2(\pi/2d)}{2}.
-\end{align} 
-We can re-normalize the other correlations of $a,b \in [2]$ when $x,y \in [2+1]$ similarly, and get a new set of correlations 
-which achieves the maximal value of $\langle \1_{-\cot(\pi/2d)}\rangle$. 
-The conclusion of \cref{lm:chsh_comp} follows the application of \cref{thm:selftest} on the state $\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi}/\|\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi}\|$ as $\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}$.
-\end{proof}
-Note that the combination of \cref{lm:chsh_comp} with \cref{prop:2d-subspace} gives us that 
-$\tB_1\tB_2$ has eigenvalues $\omega_d$ and $\omega_d^{-1}$.
+The correlation table for the other $7$ commutation tests are similar.
 
@@
 %=====================================
-In this section, we introduce the correlation $C(\dr{r})$, which is the
-ideal correlation of $\G(\dr{r})$, and then
-prove that it can self-test the state $\ket{\EPR{d-1}}$.
-
-%-----------------------------------------------------------------
-\subsection{The correlation $C(\dr{r})$}
-%-----------------------------------------------------------------
-Recall that the linear system game $\LS_r$ has $\nr$ variables and $\mr$ equations.
-In game $\G(\dr{r})$, 
-Alice receives $x \in \{1,\dots \mr+3 \}$ and Bob receives
-$y \in \{1,\dots,\nr+1\}$. We follow the previous structure by first give intuition about how they should
-behave in this game. The correlation can be easily extracted from the behaviour list below.
-\begin{itemize}
-	\item When $x \in \{1,\dots \mr\}$ and $y \in \{1, \dots \nr\}$, they should win the 
-	linear system game $\LS_r$ perfectly;
-	\item when $x \in \{\mr+1, \mr+2, \mr+3\}$ and $y \in \{1, 2, \nr+1\}$, they should follow the
-	optimal correlation of the test $\CHSH_X$, where 
-	\begin{align}
-		&\ast_A = m_r+1, \quad 1_A = m_r+2,\quad 2_A = m_r+3,\\
-		&\ast_B = \nr+1,\quad 1_B = 1, \quad 2_A = 2,
-	\end{align}
-	are the inputs for the game $\CHSH_X$
-	(The intuition behind is that $B_1B_2 = X$.);
-	\item otherwise, their behaviour is irrelevant.
-\end{itemize}
-Note that the dimension $\dr{r}$ is defined in the rules of $\CHSH_X$.
-
+In this section, we examine the properties of a strategy $S$ that can reproduce the
+full correlation approximately and 
+prove that the strategy $S$ must contain the state $\ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}$
+up to some local isometry.
+
+Let us denote the full correlation by $( \tpr{ab}{xy} )$, then the formal statement of an approximate strategy is given below.
+\begin{definition}
+	We say a quantum strategy $S = (\ket{\psi}, \{M_x^a\}, \{N_y^b\})$, which produces the correlation
+	$( \pr{ab}{xy} = \bra{\psi} M_x^a N_y^b \ket{\psi} )$ such that
+	\begin{align}
+	E_{xy} \sum_{ab} |\pr{ab}{xy} - \tpr{ab}{xy}| \leq \ep,
+	\end{align}
+	is an $\ep$-approximate quantum strategy.
+\end{definition}
+In the our full test, the probability distribution over all the questions $(x,y)$ is uniform.
+Since the number of all the possible questions is $O(r^2)$ and 
+the number of possible output pairs is $(a,b)$ is constant for each question pair $(x,y)$, 
+the approximate condition directly imply that 
+$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$, for all $(a,b,x,y)$.
+
+In the next three subsections, we analyze the implication of an approximate strategy to pass the 
+three subtests given in \cref{sec:full_test}.
+
+%------------------------------------------------------------------------------------------
+\subsection{Implication of passing the linear constraint test}
+\label{sec:imp_lct}
+%------------------------------------------------------------------------------------------
+We slightly change the notation so that instead of the notation $(x,y)$, Alice gets equation number $i$, sometimes with a variable label $j$,
+ and Bob gets a variable label $j$.
+The way we conducted the linear constraint test forces Alice to have binary observables $\{M_{ij}\}$ that satisfies 
+\cref{def:q_strat}.
 \begin{proposition}
-	\label{prop:realize}
-	The correlation $C(\dr{r})$ can be realized by a quantum strategy.
+	\label{prop:lct_base}
+	Let $S$ be an $\ep$-approximate strategy,
+	then there exist binary observables $\{ M_j \}_{j \in [\nr]}$, such that
+	\begin{align}
+		&M_j N_j \ket{\psi} \appd{O(r\se)} \ket{\psi} \\
+		&\Pi_{j \in I_i} M_j \ket{\psi} \appd{O(r\se)}(-1)^{\uc(i)} \ket{\psi}.
+	\end{align}
 \end{proposition}
-We prove this proposition by giving the ideal strategy.
 \begin{proof}
-We give the ideal strategy for the extended weighted $\CHSH_X$ test first and then based on it we give a representation of 
-group $\Gamma(\LS)$, $\Psi$, which can be converted to an ideal strategy for $\LS$. 
-The ideal strategy for $C(\dr{r})$ is the combination of the two ideal strategies for the two tests.
-
-\textbf{The ideal strategy for the weighted $\CHSH_X$ test}.
-Alice and Bob share state 
-\begin{align}
-	\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})
-\end{align}	
-and choose the special subspace to be 
-$V = \spn(\ket{1} ,\ket{d-1})$.
-Alice's projectors and observables for the weighted $\CHSH_X$ test are
+Since $\tpr{\ux b}{ij}$ win's the linear system game optimally, we know that 
+$
+\sum_{\ux,b: \ux \in X_i, \ux(j) = b} \tpr{\ux b}{ij} = 1
+$
+for all $i = 1 \dots \mr$.
+It has been shown \cite{slofstra2017} that 
+\begin{align}
+	\bra{\psi} M_{ij} N_j \ket{\psi} = 2 \sum_{\ux,b: \ux \in X_i, \ux(j) = b} \pr{\ux b}{ij} -1 \appd{O(r^2 \ep)} 1.
+\end{align}
+Since $M_{ij}$ and $N_j$ are unitaries, we know that
+\begin{align}
+	M_{ij} \ket{\psi} \appd{O(r\se)} N_j \ket{\psi} \text{ for all } i \leq \mr \text{ and } j \leq \nr.
+\end{align}
+We define $M_j := M_{ij}$ for the smallest $i$ such that $ j \in I_i$ then 
+\begin{align}
+	M_j N_j \ket{\psi} \appd{O(r\se)} M_{ij}N_j\ket{\psi} \appd{O(r\se)} \ket{\psi} \quad \text{ for all } j \leq \nr.
+\end{align}
+
+The definition of $M_{ij}$ tells us that 
+$
+\bra{\psi} \Pi_{j \in I_i} M_{ij} \ket{\psi} = (-1)^{\uc(i)}
+$
+or equivalently,
+\begin{align}
+	\Pi_{j \in I_i} M_{ij} \ket{\psi} = (-1)^{b_i} \ket{\psi}\quad\text{ for all } i \leq \mr.
+\end{align}	
+If we replace each $M_{ij}$ with $M_j$ in the equation above, we demonstrate the effect on a
+general case that $I_i = \{j_1, j_2, j_3\}$,
 \begin{align*}
-	&A_0^\diamond = \ketbra{1}{1} + \ketbra{d-1}{d-1}, &&A_0^\perp = \1 - A_\ast^\diamond, \\
-	&A_{m_r+2} = A_{m_r+2}^0-A_{m_r+2}^1 = \ketbra{1}{1} - \ketbra{d-1}{d-1}, &&A_{m_r+2}^\perp = A_\ast^\perp,\\
-	&A_{m_r+3} = A_{m_r+3}^0-A_{m_r+3}^1 = \ketbra{1}{d-1} + \ketbra{d-1}{1} ,&&A_{m_r+3}^\perp = A_\ast^\perp.
+	&\norm{ M_{ij_1}M_{ij_2}M_{ij_3} \ket{\psi} - M_{j_1}M_{j_2}M_{j_3} \ket{\psi}}\\
+	\leq & \norm{M_{ij_1}M_{ij_2}M_{ij_3} \ket{\psi} - M_{j_1}M_{ij_2}M_{ij_3} \ket{\psi}}+
+	\norm{M_{j_1}M_{ij_2}M_{ij_3} \ket{\psi} - M_{j_1}M_{j_2}M_{ij_3} \ket{\psi}} +\\
+	&\norm{M_{j_1}M_{j_2}M_{ij_3} \ket{\psi} - M_{j_1}M_{j_2}M_{j_3} \ket{\psi}}\\
+	\leq &3O(r\se) = O(r\se).
 \end{align*}
-Recall that in the extended weighted $\CHSH_X$ test, what matters is the 
-Bob's observables restricted to the subspace $V$, which are given by
+Hence we can conclude that 
+\begin{align}
+	\Pi_{j \in I_i} M_j \ket{\psi} \appd{O(r\se)} (-1)^{\uc(i)}\ket{\psi} \quad \text{ for all } i \leq \mr.
+\end{align}
+\end{proof}
+Note that with the same technique, we can prove that 
+\begin{align}
+	\Pi_{j \in I_i} N_j \ket{\psi} \appd{O(r\se)} (-1)^{\uc(i)}\ket{\psi} \quad \text{ for all } i \leq \mr.
+\end{align}
+
+Following the steps of the embedding of $(a_3a_4)^l a_1a_2(a_4a_3)^l = (a_1a_2)^{r^l}$ into $\Gamma$,
+we can get the following corollary.
+\begin{proposition}
+\label{prop:lct_adv}
+Let $S$ be an $\ep$-approximate strategy defined earlier and $\{M_j, N_j\}_{j \in \nr}$ be the observables defined in 
+\cref{prop:lct_base}, 
+then
+\begin{align}
+	M_1M_2 (M_4M_3)^l \ket{\psi}\appd{O(r^{l+1} \se)} (M_4M_3)^l (M_1M_2)^{r^l} \ket{\psi} \text{ for all } l \geq 1.
+\end{align}
+\end{proposition}
+\begin{proof}
+The $l = 1$ case follows from the fact that the linear system game embeds $O(r)$ conjugacy relations and 
+all the $O(r)$ conjugacy relations are used in the derivation of $(a_3a_4)a_1a_2(a_4a_3) = (a_1a_2)^r$, so we 
+have
+\begin{align}
+	\label{eq:ls_comm_rel}
+	M_1M_2 (M_4M_3) \ket{\psi} \appd{O(r\se)} (M_4M_3)(M_1M_2)^r \ket{\psi}.
+\end{align}
+Assume the statement is true for $l = n$, then consider the case that $l = n+1$,
 \begin{align*}
-	B_1|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) - \sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}),\\
-	B_2|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) +\sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}).
+	M_1M_2 (M_4M_3)^{n+1} \ket{\psi}  &\appd{O(r\se)} (N_3N_4) M_1M_2(M_4M_3)^n \ket{\psi} \\
+	&\appd{O(r^{n+1}\se)} (N_3N_4) (M_4M_3)^k (M_1M_2)^{r^n} \ket{\psi}\\
+	&\appd{O(r\se)} (M_4M_3)^n (M_1M_2)^{r^n} (M_4M_3) \ket{\psi} \\
+	& \appd{O(r^{n+1} \se)} (M_4M_3)^{n+1} (M_1M_2)^{r^{n+1}} \ket{\psi},
 \end{align*}
-To make sure operator $B_2$ commutes with the operator $U = \Psi(x_3x_4) = \Psi(u)$ that we will construct later, we pick a 
-special basis of $X|_V =B_1|_VB_2|_V$, which is
-\begin{align}
-	\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{1} + i\ket{d-1}), &&
-	\ket{x_{d-1}} = \frac{-e^{i\pi/d}}{\sqrt{2}}(\ket{1} - i\ket{d-1}).
-\end{align}
-It can be checked that $X\ket{x_1} = \omega_d \ket{x_1}$ and $X\ket{x_{d-1}} = \omega_d^{d-1} \ket{x_{d-1}}$.
-In this basis, $B_1|_V$ and $B_2|_V$ are expressed as 
-\begin{align}
-	&B_1|_V = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
-	&B_2|_V =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1}.
-\end{align}
-Extending $B_1|_V$ and $B_2|_V$ to the whole space spanned by $\{ \ket{j} \}_{j=1}^{d-1}$ gives us that
-\begin{align}
-	B_1 =\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} &&
-	B_2 = \sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}},
-\end{align}
-where the basis state $\ket{x_j}$ and $\ket{x_{d-j}}$ are defined by
-\begin{align}
-	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
-	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) \text{ for } j = 1 \dots \frac{d-1}{2}.
-\end{align}
-If we use the basis $\{ \ket{x_j} \}_{j=1}^{d-1}$, the shared state is 
-\begin{align}
-	\ket{\psi} =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\\
-	=& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2}  e^{ij\pi/d}e^{-ij\pi/d} (\ket{x_{j}}\ket{x_{d-j}} + \ket{x_{d-j}}\ket{x_{j}} \\
-	=& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j} \ket{x_{d-j}}.
-\end{align}
-
-\textbf{The ideal strategy for $\LS_r$}.
-We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n(r,x)$.
-In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_1$ for the group 
-\begin{align}
-	G_r(x) = \ip{ \{x_i\}_{i=1}^{n(r,x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
-\end{align}
-on the vector space $W_{d-1} = \spn(\{ \ket{x_j} \}_{j=1}^{d-1})$,
-where details of $C_r$ can be found in the appendices. 
-Note that the relation $uou^{-1} = x^r$ is embedded in the conjugation relations in $C_r$.
-Building on $\Psi_1$, we can construct 
-the representation $\Psi_{\LS_r}$ for the solution group $\Gamma(\LS_r)$.
-
-Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
-the observables $A_1 = B_1 = \Psi_1(x_1)$ and $A_2 = B_2 = \Psi_1(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows
+where from the second to the last line we repeat the process of applying \cref{eq:ls_comm_rel} 
+and the relation $M_1M_2 \ket{\psi} \appd{O(r\se)} N_1N_2 \ket{\psi}$, $r^n$ times.
+In summary, we have 
+\begin{align}
+	M_1M_2(M_4M_3)^{n+1} \ket{\psi} \appd{O(r^{n+2} \se)} (M_4M_3)^{n+1} (M_1M_2)^{r^{n+1}}\ket{\psi},
+\end{align}
+because $O(r^{n+1} \se)+O(r^{n+1}\se) = O(r^{n+2} \se)$.
+By the principal of proof by induction, the proof is complete.
+\end{proof}
+%An informal justification of the corollary is the following calculation
 %\begin{align}
-%	B_1 = \ketbra{x_0}{x_0} + 
-%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/2d}\ketbra{x_{d-k}}{x_k}\right)\\
-%	B_2 = \ketbra{x_0}{x_0} + 
-%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_{d-k}}{x_k} + e^{-ik\pi/2d}\ketbra{x_{k}}{x_{d-k}}\right)
+%	M_1M_2(M_4M_3)^k \ket{\psi} &\appd{O((k-1)r\se)} (N_3N_4)^{k-1} M_1M_2(M_4M_3) \ket{\psi} \\
+%	&\appd{O(r\se)} (N_3N_4)^{k-1}(M_4M_3) (M_1M_2)^r \ket{\psi} \\
+%	&\appd{O(r\se)} (N_4N_4)^{k-2} (M_4M_3) (M_1M_2)^{r} (M_4M_3) \ket{\psi}\\
+%	&\appd{O(r^2 \se)} (N_4N_3)^{k-2} (M_4M_3)^2 (M_1M_2)^{r^2} \ket{\psi} \\
+%	& \ldots (k-2  \text{ more such swaps} ) \ldots \\
+%	&\appd{O(r^{k-1}\se)} (M_4M_3)^{k} (M_1M_2)^{r^{k}}\ket{\psi}.
 %\end{align}
-\begin{align}
-	A_1 = B_1 = \Psi_1(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
-	A_2 = B_2 = \Psi_1(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
-\end{align}
-It can be checked that $O = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 
-The relation $uou^{-1} = x^r$ and the form of $O$ determine that 
-\begin{align}
-	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i \in \Zd} \ketbra{x_{r^{-1}i}}{x_i},
-\end{align}
-\hf{where $r^{-1}$ is the multiplicative inverse of $r$ in $\Zd$.
-All the multiplications done on the label $i$ of the state $\ket{x_i}$ are within the group $\Zd$.}
-The first step of the embedding procedure in the proof of \cref{prop:embed} requires
-the commutativity between $U$ and $B_2$, so we prove the commutation relation first and
-then give $\Psi_1(x_3)$ and $\Psi_1(x_4)$.
-The commutation relation can be checked as follows,
-\begin{align}
-	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}} =B_2.
-\end{align}
-%Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then
-%\begin{align*}
-%	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .
-%\end{align*}
-%Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then
+%The total distance introduced by the whole procedure above is
 %\begin{align}
-%	rx \equiv d \pmod{d}
+%	\sum_{j=0}^{k-1} O(r^j \se) = O(r^k \se).
 %\end{align}
-%Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.
-%Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
-%Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
-%it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
-%What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so
-%\begin{align}
-%	UB_2U\ct = B_2.
-%\end{align}
-
-The decomposition of $U$ into $\Psi_1(x_3)$ and $\Psi_1(x_4)$ is similar to the decomposition of $X$.
-Since $u$ has order $d-1$, we can find an eigenbasis $\{ \ket{u_i} \}_{i=0}^{d-2}$ such that the eigen-decomposition of $U$ is
-\begin{align}
-	U = \sum_{i=0}^{d-2} \omega_{d-1}^i \ketbra{u_i}{u_i},
-\end{align} 
-then $\Psi_1(x_3)$ and $\Psi_1(x_4)$ are  
-\begin{align*}
-	A_3 = B_3 =\Psi_1(x_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
-	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
-	A_4 = B_4  =\Psi_1(x_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
-	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right).
-\end{align*}
-Next we will show that 
-\begin{align}
-	A_3\x B_3 \ket{\psi} = \ket{\psi} && A_4 \x B_4 \ket{\psi} = \ket{\psi}.
-\end{align}
-For this purpose, we use a different expression of $\ket{\psi}$, which is
-\begin{align}
-	\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{j=0}^{d-2} \ket{r^j} \ket{r^{d-1-j}}.
-\end{align}
-Then the eigenvectors of $U$ are 
-\begin{align}
-	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{r^j}.
-\end{align}
-Hence we can express $\ket{r^j}$ in terms of $\ket{u_k}$ as 
-\begin{align}
-	\ket{r^j} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
-\end{align}
-Then $B_4$ acts on $\ket{r^j}$ as 
-\begin{align}
-	B_4 \ket{r^j} =& \frac{1}{\sqrt{d-1}} B_4\left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
-	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
-	=&\frac{1}{\sqrt{d-1}} \left(\ket{u_0} + (-1)^j\ket{u_{(d-1)/2}}  + 
-	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_{d-1-k}} + \omega_{d-1}^{jk} \ket{u_{k}})\right) \\
-	=& \ket{r^{d-1-j}}.
-\end{align}
-We first verify that $U \x U \ket{\psi} = \ket{\psi}$
-\begin{align}
-	U \x U \ket{\psi} &= \frac{1}{\sqrt{d-1}}\sum_{j = 0}^{d-2} \ketbra{ r^{j}r^{-1}}{r^j} \ket{r^j} \x \ketbra{r^{d-1-j} r^{-1}}{r^{d-1-j}} \ket{r^{d-1-j}} \\
-	&=\frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{r^{j-1}}\ket{r^{d-1-j}} = \ket{\psi},
-\end{align}
-where we use the fact that $\ket{r^{-1}} = \ket{r^{d-2}}$.
-Then we show that $A_4 \x B_4 \ket{\psi} = \ket{\psi}$ as 
-\begin{align}
-	A_4 \x B_4 \ket{\psi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} A_4 \x B_4 \ket{r^j} \ket{r^{d-1-j}} 
-	= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{r^{d-1-j}} \ket{r^{j}} =\ket{\psi},
-\end{align}
-which combined with the previous fact implies that $A_3 \x B_3 \ket{\psi} = \ket{\psi}$.
-
-The conjugation relations in $C_r$ determines the representations of 
-the rest of the $x_i$'s from $x_1,x_2,x_3$ and $x_4$. 
-For example, if $x_5 = x_1x_2x_1 \in C_r$, then
-\begin{align}
-	\Psi_1(x_5) = \Psi_1(x_1)\Psi_1(x_2) \Psi_1(x_1).
-\end{align}
-
-Next, we consider the representation $\Psi_2$ for the group 
-\begin{align*}
-	G(x,y,z,w) = \ip{ \{x_i, w_i, y_i, z_i\}_{i=1}^{n(r,x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r} :&\text{all elements are of order $2$},\\
-	&x_i = y_iz_i = fw_i,\; fy_if =z_i \text{ for } i= 1 \dots \nr(x) \\
-	&g_{jk}y_j z_k = e,\; w_iy_jw_i = z_k \text{ for all } (i,j,k)\in C_r},
-\end{align*}
-on the vector space $W_2 \x W_{d-1}$,
-where $W_2 = \spn\{ \ket{x_1}, \ket{x_2}\}$.
-Note that the choice of the basis states of $W_2$ is arbitrary.
-On $W_2$, we define 
-\begin{align}
-	\1_{W_2} = \ketbra{x_1}{x_1} + \ketbra{x_2}{x_2}, && X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1}.
-\end{align}
-Another property that we should note is that from the presentation, we can deduce that for all $i = 1 \dots n(r,x)$, 
-\begin{align}
-	fx_i fx_i = f (fw_i) f (fw_i) = w_i w_i = e,
-\end{align}
-so $f$ commutes with $x_i$ for all $i$.
-The representation $\Psi_2$ of $G(x,y,z,w)$ should satisfy the condition that for each $x_i$, 
-$\Psi_2(x_i) = \Psi_2(y_i)\Psi_2(z_i) = \Psi_2(f)\Psi_2(w_i)$. We demonstrate how this representation is constructed 
-for $x_i$, $y_i$, $z_i$, $w_i$ and $f$ where $i = 1 \dots n(r,x)$.
-Building on $\Psi_1$, we have $\Psi_2(x_i) = \1_{W_2} \x \Psi_1(x_i)$, then
-$y_i$, $z_i$, $w_i$ and $f$ are mapped to
-\begin{align*}
-&\Psi_2(y_i) = \ketbra{x_1}{x_1} \x \Psi_1(x_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
-&\Psi_2(z_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(x_i) \\
-&\Psi_2(w_i) =  X_{W_2} \x \Psi_1(x_i)\\
-&\Psi_2(f) = X_{W_2} \x \1_{W_{d-1}}.
-\end{align*}
-It can be easily checked that the order-$2$ generators are mapped to order-$2$ operators and
-the relations satisfied by the generators are preserved.
-For each $g_{jk}$ where $(i,j,k) \in C_r$, 
-\begin{align}
-\Psi_2(g_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(x_j) + \ketbra{x_2}{x_2} \x \Psi_1(x_k).
-\end{align}
-
-The group $G_r(x,y,z,w)$ is embedded in $\Gamma(\LS_r)$ by replacing the conjugacy relations 
-by linear relations. The new generators are $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{n(r,x)}
-\cup \{\{y_{K,k}\}_{k=1}^7\}_{K \in C_r}$. How the new linear relations can embed the conjugacy relations 
-in $G_r(x,y,z,w)$ can be found in the appendices. 
-The relations that we should pay attention to are
-\begin{align}
-	fy_{F_j,1}y_{F_j,2} =  e, && y_j y_{F_j,2}y_{F_j,3} = e \text{ for } j = 1 \dots n(r,x),
-\end{align}
-which imply that $y_{F_j, 2}$ commutes with $f$ and $y_j$.
-Since $z_j = fy_jf$, $y_{F_j, 2}$ commutes with $z_j$ too.
-We also know that $x_j = y_jz_j$, so we can conclude that $y_{F_j, 2}$ commutes with $x_j$.
-
-Now we define the representation $\Psi_{\LS_r}$ of
-$\Gamma(\LS_r)$ on $W_2 \x W_2 \x W_{d-1}$. For any generator $a \in \{x_i, w_i, y_i, z_i\}_{i=1}^{n(r,x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r}$,
-\begin{align}
-	\Psi_{\LS_r}(a) = \1_{W_2} \x \Psi_2(a) 
-\end{align}
-For generators $\{y_{F_j,k}\}_{k=1}^7\}_{j=1}^{n(r,x)}$,
-\begin{align*}
-	\Psi_{\LS_r}(y_{F_j,1}) &=X_{W_2} \x \Psi_2(f) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}}\\
-	\Psi_{\LS_r}(y_{F_j,2}) &= X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
-	\Psi_{\LS_r}(y_{F_j,3}) &= X_{W_2} \x \Psi_2(y_j) = X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_1(x_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
-	\Psi_{\LS_r}(y_{F_j,4}) &= \ketbra{x_1}{x_2} \x \Psi_2(y_jf) + \ketbra{x_2}{x_1} \x \Psi_2(fy_j)\\
-	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_1(x_j) + \ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_2}{x_1x_1} \x \Psi_1(x_j)\\ 
-	\Psi_{\LS_r}(y_{F_j,5}) &= \ketbra{x_1}{x_1} \x \Psi_2(fy_jf) + \ketbra{x_2}{x_2} \x \Psi_2(f) \\
-	&= \ketbra{x_1x_}{x_1x_1} \x \1_{W_{d-1}} + \ketbra{x_1x_2}{x_1x_2} \x \Psi_1(x_j) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
-	\Psi_{\LS_r}(y_{F_j,6}) &=  \ketbra{x_1}{x_1} \x \Psi_2(fy_jf) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	&=(\ketbra{x_1x_1}{x_1x_1}+  \ketbra{x_1x_2}{x_1x_2}) \x \Psi_1(x_j) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi_{\LS_r}(y_{F_j,7}) &= \ketbra{x_1}{x_1} \x \Psi_2(y_j) + \ketbra{x_2}{x_2} \x \Psi_2(z_j) \\
-	&=\ketbra{x_1x_1}{x_1x_1} \x \Psi_1(x_j) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1}) + \ketbra{x_2x_2}{x_2x_2} \x \Psi_1(x_j)
-\end{align*}
-For generators $\{\{y_{K,k}\}_{k=1}^7\}_{K=(k_1,k_2,k_3) \in C_r}$,
-\begin{align*}
-	\Psi_{\LS_r}(y_{K,1}) &= X_{W_2} \x \Psi_2(w_{k_1}) = X_{W_2} \x X_{W_2} \x \Psi_1(x_{k_1}) \\
-	\Psi_{\LS_r}(y_{F_j,2}) &= X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi_{\LS_r}(y_{F_j,3}) &= X_{W_2} \x \Psi_2(y_{k_2}) = X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_1(x_{k_2}) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
-	\Psi_{\LS_r}(y_{F_j,4}) &= \ketbra{x_1}{x_2} \x  \Psi_2(y_{k_2}w_{k_1}) + \ketbra{x_2}{x_1} \x \Psi_2(w_{k_1}y_{k_2})\\
-	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_1(x_{k_2}x_{k_1}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_1(x_{k_1})
-	+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_1(x_{k_1}x_{k_2}) \\
-	\Psi_{\LS_r}(y_{F_j,5}) &= \ketbra{x_1}{x_1} \x \Psi_2(w_{k_1}y_{k_2}w_{k_1}) + \ketbra{x_2}{x_2} \x  \Psi_2(w_{k_1})\\
-	&= \ketbra{x_1x_1}{x_1x_1} \x \1_{W_{d-1}} + \ketbra{x_1x_2}{x_1x_2} \x \Psi_1(x_{k_1}x_{k_2}x_{k_1}) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_1(x_{k_1})\\
-	\Psi_{\LS_r}(y_{F_j,6}) &=  \ketbra{x_1}{x_1} \x \Psi_2(y_{k_2}z_{k_3}) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_1(x_{k_2}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_1(x_{k_3}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi_{\LS_r}(y_{F_j,7}) &= \ketbra{x_1}{x_1} \x \Psi_2(y_{k_2}) + \ketbra{x_2}{x_2} \x \Psi_2(z_{k_3})\\
-	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_1(x_{k_2}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}} + 
-	\ketbra{x_2x_2}{x_2x_2} \x \Psi_1(x_{k_3})
-\end{align*}
-
-In the end, to compensate the enlarged Hilbert space, the shared state is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$,
-where $\ket{\psi} = \frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{i}\ket{i}$.
-At the same time, the observables for the extended weighted CHSH test are mapped to four copies of themselves. 
-\end{proof}
-Next we are going to prove that the correlation $C(\dr{r})$, which is produced by the 
-strategy winning this game optimally, can self-test $d-1$-dimensional EPR pair.
+
+For simplicity, we define $O_A = M_1M_2$ and $U_A=M_3M_4$ such that
+the conclusion of \cref{prop:lct_adv} can be rewritten as 
+\begin{align}
+	U_A^k O_A (U_A\ct)^k \ket{\psi} \appd{O(r^{k+1} \se)} O_A^{r^k} \ket{\psi}.
+\end{align}
+Similar relation holds on Bob's side too.
+
+The other relations that are embedded in $\Gamma$ are 
+\begin{align}
+	\label{eq:comm}&[f_0, a_i] = [f_2, a_i] = [g_0, a_i] = [g_2, a_i] = e \text{ for all } i = 1 \dots r+5 \\
+	\label{eq:mg1}&f_0g_0 = Jg_0f_0 \\
+	\label{eq:mg2}&f_2g_2 = J g_2 f_2.
+\end{align}
+We summarize the implications in the following corollary.
+\begin{proposition}
+	\label{prop:lct_comm}
+	Let $S$, $\{M_j, N_j\}_{j=1}^{\nr}$ be the strategy and observables defined in \cref{prop:lct_base},
+	then
+	\begin{align}
+		&M_{r+6} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+6} \ket{\psi} && 
+		M_{r+8}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+8} \ket{\psi} \\
+		&M_{r+9} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+9} \ket{\psi} && 
+		M_{r+11}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+11} \ket{\psi} 
+	\end{align}
+	for all $j = 1 \dots r+5$, and
+	\begin{align}
+		&M_{r+6}M_{r+9} \ket{\psi} \appd{O(r\se)} - M_{r+9}M_{r+6} \ket{\psi} \\
+		&M_{r+8}M_{r+11} \ket{\psi} \appd{O(r\se)} -M_{r+11}M_{r+8} \ket{\psi}.
+	\end{align}
+\end{proposition}
+Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma$,
+so this proposition can be proved using the same technique as that used in the proof of \cref{prop:lct_base}.
 
@@
 %========================================
-\section{Proof of \cref{thm:selftest} }
+\section{The proof of \cref{thm:selftest} }
 \label{sec:selftest}
@@
 This proof follows the same line of argument in Appendix A of Ref.~\cite{bamps2015}.
-We first find two sum-of-square decompositions of $2\sqrt{\alpha^2+1} \1 - \I_\alpha$.
+We first find two sum-of-square decompositions of $2\sqrt{\alpha^2+1} \1 - \I_\alpha$,
+where $\I_\alpha$ is expressed in terms of $\{M_x\}$ and $\{N_y\}$.
 The decompositions allow us to determine some key relations between Alice and Bob's observables
-and their shared state, which will be used to draw the closeness conclusion.
+and their shared state, which will be used to draw the conclusion.
 
@@
 	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
-	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_1B_1+A_1B_2) -  A_2B_1 + A_2B_2.
-\end{align} 
-With the following notation
+	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(M_1N_1+M_1N_2) -  M_2N_1 + M_2N_2.
+\end{align} 
+With the notation $c:= \cos(\mu)$, $s := \sin(\mu)$ and 
 \begin{align*}
-	&Z_A = A_1 && X_A = A_2\\
-	&Z_B = \frac{B_1+B_2}{2\cos(\mu)} && X_B = \frac{B_1-B_2}{2\sin(\mu)},
+	&Z_A = M_1 && X_A = M_2\\
+	&Z_B = \frac{N_1+N_2}{2c} && X_B = \frac{N_1-N_2}{2s},
 \end{align*}
@@
 \begin{align}
-	\label{eq:sos1}&\bar{\I}_\alpha = \frac{\sin(\mu)\bar{\I}_\alpha^2 + 4\sin(\mu)\cos(\mu)^2(Z_AX_B+X_AZ_B)^2}{4},\\
-	\label{eq:sos2}&\bar{\I}_\alpha = \frac{\cos^2(\mu)}{\sin(\mu)}(Z_A-Z_B)^2 + \sin(\mu) (X_A-X_B)^2.
-\end{align}
-The verification is omitted here.
-
-Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x=1,2}, \{\tilde{B}_{y }\}_{y=1,2}$ achieves that 
-$\bra{\psi} \bar{\I}_\alpha \ket{\psi} \leq \epsilon$ where
-$\bar{\I}_\alpha$ is expressed with $\tA_x$ and $\tB_y$.
-The second step is to establish bounds of the following form
-\begin{align}
-	\label{eq:zazb} &\|(\tilde{Z}_A-\tilde{Z}_B)\ket{\psi}\| \leq c_1 \sqrt{\epsilon}\\
-	\label{eq:xzxz}&\|(\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A))\ket{\psi}\| \leq c_2 \sqrt{\epsilon}\\
-	\label{eq:xaxb}&\|(\tilde{X}_A-\tilde{X}_B)\ket{\psi}\| \leq c_3 \sqrt{\epsilon}\\
-	\label{eq:anticom} &\|(\tilde{Z}_A\tilde{X}_A+\tilde{X}_A\tilde{Z}_A)\ket{\psi}\| \leq c_4 \sqrt{\epsilon}.
-\end{align}
-Going back to the sum-of-square decomposition, we write $s = \sin(\mu)$, $c = \cos(\mu)$ and define
+	\label{eq:sos1}&\bar{\I}_\alpha = \frac{s \bar{\I}_\alpha^2 + 4sc^2(Z_AX_B+X_AZ_B)^2}{4},\\
+	\label{eq:sos2}&\bar{\I}_\alpha = \frac{c^2}{s}(Z_A-Z_B)^2 + s(X_A-X_B)^2.
+\end{align}
+The verification is omitted here. From the SOS decomposition, we establish \cref{eq:za-zb,eq:xa-xb,eq:xazb,eq:zaxb,eq:zaxa,eq:zaxaxbzb}.
+We define
 \begin{align*}
-	S_1 = \frac{\sqrt{s}}{2} \bar{\I}_\alpha, &&
-	S_2 = \sqrt{s}c(\tilde{Z}_A\tilde{X}_B+\tilde{X}_A\tilde{Z}_B),\\
-	S_3 = \frac{c}{\sqrt{s}}(\tilde{Z}_A-\tilde{Z}_B), &&
-	S_4 = \sqrt{s}(\tilde{X}_A-\tilde{X}_B)
+	&S_1 = \frac{\sqrt{s}}{2} \bar{\I}_\alpha, &&
+	S_2 = \sqrt{s}c(Z_AX_B+ X_AZ_B),\\
+	&S_3 = \frac{c}{\sqrt{s}}(Z_A-Z_B), &&
+	S_4 = \sqrt{s}(X_A-X_B)
 \end{align*}
@@
 \end{align}
- and $\bra{\psi}\bar{\I}_\alpha \ket{\psi} \leq \epsilon$ implies that 
-$\bra{\psi}S^2_i \ket{\psi} \leq \epsilon$ and $\|S_i \ket{\psi} \| \leq \sqrt{\epsilon}$ for $i = 1,2,3,4$.
-The coefficients $c_1$, $c_2$ and $c_3$ in \cref{eq:zazb,eq:xzxz,eq:xaxb} can be determined from $S_1$,$S_2$ and $S_3$ as
-\begin{align*}
-	c_1 = \frac{\sqrt{s}}{c}, \quad
-	c_2 = \frac{1}{\sqrt{s}} + \frac{1}{c\sqrt{s}}, \quad
-	c_3 = \frac{1}{\sqrt{s}}.
-\end{align*}
-where we use the relation that $\tilde{X}_A(\1+\tilde{Z}_B)-\tilde{X}_B(\1-\tilde{Z}_A) = S_4/s^{1/2} + S_2/(cs^{1/2})$.
-To calculate $c_4$, we use the relation
-\begin{align}
-	\tilde{Z}_A\tilde{X}_A + \tilde{X}_A\tilde{Z}_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}
-\end{align}
-and reach the conclusion that  
-\begin{align}
-	c_4 = \frac{1+c+s}{c\sqrt{s}}
-\end{align}
-where we use that fact that $\tilde{Z}_A, \tilde{X}_A$ are unitaries.
+The fact that the quantum strategy $(\ket{\psi}, \{M_x\}_{x=1,2}, \{N_{y }\}_{y=1,2}$ achieves that 
+$\ip{\bar{\I}_\alpha} \leq \epsilon$ implies that
+$\bra{\psi} S_i^2 \ket{\psi} \leq \ep$, and equivalently, $\norm{S_i \ket{\psi}} \leq \se$ for $i = 1,2,3,4$.
+From the definitions of $S_i$'s, we can get that 
+\begin{align}
+	&\norm{(X_AZ_B+X_BZ_A)\ket{\psi}} \leq \frac{1}{c\sqrt{s}} \se\\
+	&\norm{(Z_A-Z_B)\ket{\psi}} \leq \frac{\sqrt{s}}{c} \se\\
+	&\norm{(X_A-X_B)\ket{\psi}} \leq \frac{1}{\sqrt{s}} \se.
+\end{align}
+The first and the second inequality give us that 
+\begin{align}
+	\norm{ [Z_A(\1+X_B) - (\1-X_A)Z_B] \ket{\psi} } 
+	\leq \norm{(X_AZ_B+X_BZ_A)\ket{\psi}} + \norm{(Z_A-Z_B)\ket{\psi}}
+	\leq \frac{s+1}{c\sqrt{s}} \se.
+\end{align}
+Similarly, the first and the third inequality give us that 
+\begin{align}
+	\norm{[X_A(\1+Z_B) - X_B(\1-Z_A)] \ket{\psi}} \leq \frac{c+1}{c\sqrt{s}} \se.
+\end{align}
+Since $Z_AX_A +X_A Z_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}$, we can deduce that
+\begin{align}
+	\norm{ (Z_A X_A+X_AZ_A)\ket{\psi}} \leq \frac{1+c+s}{c\sqrt{s}} \se.
+\end{align}
+To prove \cref{eq:zaxaxbzb}, we switch to the approximate relation form and derive that 
+\begin{align}
+	X_AZ_A \ket{\psi} &\appd{\frac{1+c+s}{c\sqrt{s}} \se}  -Z_AX_A \ket{\psi} \\
+	&\appd{\frac{\sqrt{s}}{c} \se} -Z_AX_B \ket{\psi} \\
+	&\appd{\frac{1}{s^{3/2} }\se} -X_BZ_B\ket{\psi},
+\end{align}
+where in the last line we use the fact $\norm{X_B} \leq 1/s$.
 
@@
 They are the same as the ones used in Ref.~\cite{bamps2015}.
-To construct $\Phi_A$ and $\Phi_B$ we need to regularize $\tZ_B$ and $\tX_B$ to make sure the corresponding operations 
-are unitaries in the isometries. We define $\tZ_B^\ast$ to be the operator obtained from $\tZ_B$ by changing all the $0$-eigenvalues
+To construct $\Phi_A$ and $\Phi_B$ we need to regularize $Z_B$ and $X_B$ to make sure the corresponding operations 
+are unitary in the isometries. We define $Z_B^\ast$ to be the operator obtained from $Z_B$ by changing all the $0$-eigenvalues
 to $1$ and 
 \begin{align*}
-\tZ_B' = \tZ_B^\ast |\tZ_B|^{-1}.
+Z_B' := Z_B^\ast |Z_B^\ast|^{-1},
 \end{align*}
-In a similar way, we define $\tX_B^\ast$ and $\tX_B'$.
-On Alice's side, since $\tZ_A$ and $\tX_A$ are unitaries already,
+where $|Z_B^\ast|$ is obtained from $Z_B^\ast$ by replacing all negative eigenvalues by its absolute value.
+In a similar way, we define $X_B^\ast$ and $X_B'$.
+On Alice's side, since $Z_A$ and $X_A$ are unitaries already,
 we define
-\begin{align}
-	\tZ_A' = \tZ_A, && \tX_A' = \tX_A.
-\end{align}
+$Z_A' := Z_A$ and $X_A' = X_A$.
 The isometries are illustrated in the figure below.
@@
         \node[phase] (phase11) at (2,0) {} edge [-] (op11);
-	\node[operator] (op22) at (2,-1) {$\tZ_A'$} edge [-] (q2);
-	\node[operator] (op23) at (2, -2) {$\tZ_B'$} edge[-] (q3);
+	\node[operator] (op22) at (2,-1) {$Z_A'$} edge [-] (q2);
+	\node[operator] (op23) at (2, -2) {$Z_B'$} edge[-] (q3);
         \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
@@
         \node[phase] (phase21) at (4,0) {} edge [-] (op31);
-	\node[operator] (op42) at (4,-1) {$\tX_A'$} edge [-] (op22);
-	\node[operator] (op43) at (4, -2) {$\tX_B'$} edge[-] (op23);
+	\node[operator] (op42) at (4,-1) {$X_A'$} edge [-] (op22);
+	\node[operator] (op43) at (4, -2) {$X_B'$} edge[-] (op23);
         \node[phase] (phase24) at (4,-3) {} edge [-] (op34);
@@
         \draw[decorate,decoration={brace},thick] (5,-1) to
-    	node[midway,right] (bracket) {$\ket{junk}$}
+    	node[midway,right] (bracket) {$\ket{aux}$}
     	(5,-2);
@@
 we only record the key relations here.
-\begin{align}
-	&\norm{(\tZ_B' - \tZ_B) \ket{\tpsi}} \leq c_1 \sqrt{\epsilon},\\
-	&\norm{(\tZ_B' - \tZ_A') \ket{\tpsi}} \leq 2c_1 \sqrt{\epsilon}, \\
-	&\norm{(\tX_B' - \tX_B) \ket{\tpsi}} \leq \frac{c+1}{s^{3/2}} \sqrt{\epsilon} := c_5\sqrt{\epsilon},\\
-	&\norm{(\tX_B'\tZ_B'+ \tZ_B'\tX_B')\ket{\tpsi}} \leq [2c_1 + 2c_3 + 2c_5 + (\sqrt{2}+1/c)(2c_1+c_4)]\sqrt{\epsilon}
-	:= c_6 \sqrt{\epsilon}.
-\end{align}
+\begin{align*}
+	&\norm{(Z_B' - Z_B) \ket{\tpsi}} \leq \frac{\sqrt{s}}{c} \sqrt{\epsilon},\\
+	&\norm{(Z_B' - Z_A') \ket{\tpsi}} \leq 2 \frac{\sqrt{s}}{c}\sqrt{\epsilon}, \\
+	&\norm{(X_B' - X_B) \ket{\tpsi}} \leq \frac{c+1}{s^{3/2}} \sqrt{\epsilon} := \delta_1 \sqrt{\epsilon},\\
+	&\norm{(X_B'Z_B'+ Z_B'X_B')\ket{\tpsi}} \leq [\frac{2\sqrt{s}}{c} + \frac{2}{\sqrt{s}} + 2\delta_1 + 
+	(\sqrt{2}+\frac{1}{c})(2\frac{\sqrt{s}}{c}+\frac{1+c+s}{c\sqrt{s}})]\sqrt{\epsilon}
+	:= \delta_2 \sqrt{\epsilon}.
+\end{align*}
 Then we can calculate that 
-\begin{align}
-	&e_{00} = e_{10} = 2c_6 \sqrt{\epsilon}\\
-	&e_{20} = 2(c_4 + c_6) \sqrt{\epsilon}\\
-	&e_{01} = e_{02} = e_{11} = e_{12} = [c(c_1)+s(2c_4 + c_5) + 2c_6]\sqrt{\epsilon}\\
-	&e_{21} = e_{22} = [2c_4 + c(c_1)+s(2c_4 + c_5) + 2c_6]\sqrt{\epsilon},
-\end{align}
+\begin{align*}
+	&e_{00} = e_{10} = 2\delta_2 \sqrt{\epsilon}\\
+	&e_{20} = 2(\frac{1+c+s}{c\sqrt{s}} + \delta_2) \sqrt{\epsilon}\\
+	&e_{01} = e_{02} = e_{11} = e_{12} = [\sqrt{s}+s(2\frac{1+c+s}{c\sqrt{s}} + \delta_1) + 2\delta_2]\sqrt{\epsilon}\\
+	&e_{21} = e_{22} = [2\frac{1+c+s}{c\sqrt{s}} + \sqrt{s}+s(2\frac{1+c+s}{c\sqrt{s}} + \delta_1) + 2\delta_2]\sqrt{\epsilon},
+\end{align*}
 so an upper bound of the error is that
 \begin{align}
-	\forall x,y \in \{0,1,2\}, e_{xy} \in O((\frac{1}{cs^{1/2}} + \frac{1}{s^{3/2}})\sqrt{\epsilon}).
-\end{align}
-The dependence of the error term on $\alpha$ comes from the fact that 
-\begin{align}
-&\frac{1}{\cos(\arctan(1/\alpha)) \sin^{1/2}(\arctan(1/\alpha))} = \frac{1}{\alpha}+\frac{3}{4}\alpha - O(\alpha^3),\\
-&\frac{1}{\sin^{3/2}(\arctan(1/\alpha))} = 1 + \frac{3}{4}\alpha^2 - O(\alpha^4).
+	\forall x,y \in \{0,1,2\}, e_{xy} \in O((\frac{1}{c^2s^{1/2}} + \frac{1}{s^{3/2}})\sqrt{\epsilon}).
 \end{align}
@@
 %%=====================================
-\section{ The special property of $U$ and $O$}
+\section{The proof of \cref{lm:uo_independ}}
 \label{sec:u_and_o}
 %%=====================================
-\begin{lemma}
-	\label{lm:ux_independ}
-	Suppose there exist unitaries $U$ and $X$ which have the following forms
-	\begin{align}
-		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/r}{i},
-	\end{align}
-	where $d$ is an odd prime number with primitive root $r$,
-	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
-	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
-\end{lemma}
-Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^r$.
-In the self-test proof, this lemma will be a critical step.
+
+We are going to prove 
+the set $\{U^k O^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of the ring of $(d-1)\times (d-1)$ matrices over $\C$
+Note that the unitaries $U$ and $O$ defined in the lemma above satisfy the condition $UOU^\dagger = O^r$.
+In this proof, we denote the set $\{0,1,2\dots d-2\}$ by $[d-1]$ and the set $\{1,2 \dots d-1\}$ by $[d-1]+1$.
 \begin{proof}
-We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
+We are going to show the $(d-1)^2$ matrices from the set $\{U^k O^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
 Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
@@
 \begin{align}
-	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
-\end{align}
-We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
+	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k O^l = 0. 
+\end{align}
+We \hf{define} a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
 \carl{We shouldn't be making extra assumptions that are not stated in the lemma.  This looks to me more like
@@
 \begin{align}
-	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/r^k}\braket{i}{1}.
-\end{align}
-For the term $\braket{1}{i/r^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
+	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i (r^{-1})^k}\braket{i}{1}.
+\end{align}
+For the term $\braket{1}{i (r^{-1})^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
 $k = k_1$. We can conclude that 
@@
 	\bra{j}M\ket{j} 
-	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/r^k}\braket{i}{j} 
+	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i (r^{-1})^k}\braket{i}{j} 
 	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
@@
 \end{proof}
-Note that the primitive root $r$ in the lemma is not restricted to the set $\{2,3,5\}$, so this lemma works for any 
-odd prime number $d$.
 

### 2019-04-29 Draft/draft.tex
Honghao: finished section 6

@@
 % Clever references
+
 \usepackage{cleveref}%[nameinlink]
+
 \crefname{lemma}{Lemma}{Lemmas}
@@
 \crefname{table}{Table}{Tables}
+
 % \crefname{algorithm}{Algorithm}{Algorithms}
@@
 \newcommand{\ua}{\underline{a}}
+\newcommand{\ub}{\underline{b}}
 
@@
 
-\newtheorem{theorem}{Theorem}
+\newtheorem{theorem}{Theorem}[section]
 \newtheorem{lemma}[theorem]{Lemma}
@@
 
-\title{Robust self-testing of large entanglement with constant alphabet}
+\title{Robust self-testing of large entanglement with constant-sized correlations}
 
@@
 \carl{Section 2 needs to be cleaned up in some places, but overall it is pretty good.}
+
+%-----------------------------------------------------------
+\subsection{Approximation tools}
+%-----------------------------------------------------------
+In the rest of the paper, we use the following approximation results implicitly and explicitly.
+\begin{proposition}
+	\label{prop:inner_pd}
+	Let $\ket{v}$ and $\ket{v'}$ be vectors with length less than equal to $1$ satisfying the relation that $\ket{v} \appd{\epsilon} \ket{v'}$
+	then for any unit vector $\ket{u}$,
+	\begin{align}
+		 \braket{v}{u} \appd{\ep} \braket{v'}{u} .
+	\end{align}	
+\end{proposition}
+\begin{proof}
+	We can write $\ket{v'} = \ket{v} + \ket{v''}$, where $\norm{\ket{v''}} \leq \epsilon$,
+	then
+	\begin{align}
+	\norm{ \braket{v}{u} - \braket{v'}{u} } = \norm{\braket{v''}{u}} \leq \norm{\ket{u}}\norm{\ket{v''}} \leq \epsilon.
+	\end{align}
+\end{proof}
+\begin{proposition}
+	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with length less than equal to $1$
+	such that 
+	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$
+	then 
+	\begin{align}
+		\braket{u_1}{u_2} \appd{\ep_1+ \ep_2} \braket{v_1}{v_2}.
+	\end{align}
+\end{proposition}
+\begin{proof}
+	By direct calculation we have
+	\begin{align}
+		\norm{ \braket{u_1}{u_2} - \braket{v_1}{v_2}} \leq &\norm{\braket{u_1}{u_2} - \braket{v_1}{u_2}}
+		+ \norm{\braket{v_1}{u_2} - \braket{v_1}{v_2}} \\
+		\leq & \ep_1 + \ep_2,
+	\end{align}
+	where we used \cref{prop:inner_pd}.
+\end{proof}
+\begin{proposition}
+\label{prop:orthog}
+	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with length less or equal to $1$,
+	which satisfy the condition that 
+	\begin{align}
+		H\ket{u} \appd{\ep_1} a \ket{u}, \\
+		H\ket{v} \appd{\ep_2} b \ket{v}, 
+	\end{align}
+	for some $a > b \in \R$, then
+	\begin{align}
+		\norm{\braket{u}{v}} \leq \frac{\ep_1+\ep_2}{a-b}.
+	\end{align}
+\end{proposition}
+\begin{proof}
+	We write $H\ket{u} = a\ket{u} + \ket{u'}$ such that $\norm{\ket{u'}} \leq \ep_1$.
+	Similarly, we write $H\ket{v} = b\ket{v} + \ket{v'}$ such that $\norm{\ket{v'}} \leq \ep_2$.
+	Then, we know
+	\begin{align}
+		\bra{v}H\ket{u} = a\braket{v}{u} + \braket{v}{u'},\\
+		\bra{v}H\ket{u}  =b\braket{v}{u} + \braket{v'}{u},
+	\end{align}
+	Subtracting the second equation from the first equation gives us that 
+	\begin{align}
+		\norm{\braket{v}{u}} = \frac{\norm{\braket{v'}{u} -  \braket{v}{u'}}}{a-b} \leq \frac{\norm{\ket{v}}\norm{\ket{u'}}+
+		\norm{\ket{u}}\norm{\ket{v'}}}{a-b} 
+		\leq \frac{\ep_1+\ep_2}{a-b}.
+	\end{align}
+\end{proof}
+\begin{proposition}
+\label{prop:close_vec}
+	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$ and
+	$\norm{\ket{v}} \appd{\ep_2} 1$ , if $\braket{u}{v} \geq 1 - \ep_3$,
+	then
+	\begin{align}
+		\ket{u} \appd{O(\sqrt{\ep_1+\ep_2+\ep_3})} \ket{v}.
+	\end{align}
+\end{proposition}
+\begin{proof}
+	Direct calculation gives us that
+	\begin{align}
+		\norm{\ket{u} - \ket{v}}^2 &= \norm{\ket{u}}^2 + \norm{\ket{v}}^2 - 2\braket{u}{v} \\
+		&\leq (1+\ep_1)^2 + (1+\ep_2)^2 - 2(1 - \ep_3)\\
+		&= 2(\ep_1+\ep_2+\ep_3)+ \ep_1^2 + \ep_2^2\\
+		& = O(\ep_1+\ep_2+\ep_3).
+	\end{align}
+\end{proof}
+\begin{proposition}
+	Let $\ket{u}$ be a vector with length less or equal to $1$ such that for a unitary $U$,
+	\begin{align}
+		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C,
+	\end{align}
+	then
+	\begin{align}
+		U^n \ket{u} \appd{n\ep} a^n \ket{u} \text{ for all } n \geq 1.
+	\end{align}
+\end{proposition}
+\begin{proof}
+	We can prove it by induction. 
+	For $n=1$, the statement is satisfied.
+	Assume it holds for $n = k-1$ and consider $n = k$, then we have
+	\begin{align}
+		&\norm{U^k \ket{u} - a^k\ket{u}} \\
+		\leq &\norm{U} \norm{U^{k-1} \ket{\psi} - a^{k-1}\ket{\psi}} + \norm{a^{k-1}}
+		\norm{U\ket{\psi} - a \ket{\psi}}\\
+		\leq &(k-1)\ep + \ep = k \ep,
+	\end{align}
+	where we used the fact that $\norm{U} = 1$ and $\norm{a} \leq 1$.
+\end{proof}
 
@@
 \caption{The correlation for the commutation test between $M_{r+6}$ and $M_{\nr+1}$.}
+\label{tbl:comm}
 \end{table}
@@
 \end{align}
-Similar relation holds on Bob's side too.
+On Bob's side, we also define $O_B = N_1N_2$ and $U_B = N_3N_4$ 
+and similar relations hold.
 
@@
 so this proposition can be proved using the same technique as that used in the proof of \cref{prop:lct_base}.
-
-%-----------------------------------------------------------------
-\subsection{Self-test}
-%-----------------------------------------------------------------
-\hl{This subsection needs to be formalized.}
-We give a formal version of \cref{thm:pr_2} first and then prove it.
+%------------------------------------------------------------------------------------------
+\subsection{Implication of passing the extended weighted CHSH test}
+\label{sec:imp_chsh}
+%------------------------------------------------------------------------------------------
+\begin{proposition}
+\label{prop:chsh_base}
+Let $S$ be an $\ep$-approximate quantum strategy,
+then the strategy $S$ satisfy the following relations
+\begin{align}
+	  M_\ast^\diamond N_\ast^\diamond \ket{\psi}
+	  \appd{O( r\se)}&M_\ast^\diamond \ket{\psi} \appd{O( r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
+	  \appd{O( r\se)}&N_\ast^\diamond \ket{\psi} \appd{O( r\se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
+	M_\ast^\perp N_\ast^\perp\ket{\psi}\appd{O( r\se)} &M_\ast^\perp\ket{\psi} \appd{O( r\se)} M_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} M_{\nr+2}^\perp \ket{\psi}\\
+	\appd{O( r\se)}&N_\ast^\perp\ket{\psi} \appd{O( r\se)} N_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} N_{\nr+2}^\perp \ket{\psi}.
+\end{align}
+and
+\begin{align}
+&M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+1}^0 \ket{\psi} && M_{\nr+1}^1\ket{\psi} \appd{O( r\se)} N_{\nr+1}^1 \ket{\psi}\\
+&M_{\nr+2}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+2}^0 \ket{\psi} && M_{\nr+2}^1\ket{\psi} \appd{O( r\se)} N_{\nr+2}^1 \ket{\psi}.
+\end{align}
+\end{proposition}
+
+\begin{proof} 
+Recall that the implication of $S$ being an $\ep$-approximate strategy is that 
+$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$. 
+We prove $(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\se)} N_\ast^\diamond \ket{\psi}$ as an example.
+The rest of the relations follow the same line of arguments.
+From the correlation, we can observe that
+\begin{align*}
+ \bra{\psi} (M_{\nr+1}^0+M_{\nr+1}^1)N_\ast^\diamond \ket{\psi} = \frac{2}{d-1} - O(r^2 \epsilon).
+\end{align*}
+On the other hand, the correlation also tells us that 
+\begin{align*}
+	\bra{\psi} N_\ast^\diamond \ket{\psi} \appd{O(r^2\epsilon)} 
+ \bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r^2\epsilon)} \frac{2}{d-1},
+\end{align*}
+which implies that 
+\begin{align*}
+	&\norm{(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - N_\ast^\diamond\ket{\psi}}^2 \\
+	= &\bra{\psi} N_\ast^\diamond \ket{\psi}+\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} - 2\bra{\psi}N_\ast^\diamond(M_{\nr+1}^0 + M_{\nr+1}^1)N_\ast^\diamond \ket{\psi}\\
+	= &O(r^2 \epsilon),
+\end{align*}
+where we used the fact that $(M_{\nr+1}^0 + M_{\nr+1}^1)^2 = M_{\nr+1}^0 + M_{\nr+1}^1$.
+Hence we can conclude that $(M_{\nr+1}^0 + M_{\nr+1}^1)N_\ast^\diamond \ket{\psi} \appd{O(r\se)} N_\ast^\diamond\ket{\psi}$.
+%From the correlation, we know that 
+%\begin{align}
+%	\bra{\psi} M_\ast^\perp N_\ast^\perp \ket{\psi} = \frac{d-3}{d-1} - O(r^2 \ep).
+%\end{align}
+%In the mean time, we also have 
+%$\norm{M_\ast^\perp \ket{\psi}}^2 \appd{O(r^2\ep)} \norm{N_\ast^\perp\ket{\psi}}^2 \appd{O(r^2\ep)} (d-3)/(d-1)$.
+%The two facts above imply that 
+%\begin{align}
+%	\norm{M_\ast^\perp \ket{\psi} - N_\ast^\perp \ket{\psi}}^2 = \norm{M_\ast^\perp \ket{\psi}}^2 + \norm{N_\ast^\perp \ket{\psi}}^2
+%	- 2 \bra{\psi} M_\ast^\perp N_\ast^\perp \ket{\psi}  = O(r^2 \ep),
+%\end{align}
+%or equivalently,
+%\begin{align}
+%	M_\ast^\perp \ket{\psi} \appd{O(r\se)} N_\ast^\perp \ket{\psi}.
+%\end{align}
+\end{proof}
+
+%Another conclusion we can draw is that $B_\ast^\diamond = A_\ast^\diamond$ and $B_\ast^\perp = A_\ast^\perp$.
+%We can assume the Schmidt decomposition of $\ket{\psi}$ is
+%\begin{align}
+%	\ket{\psi} = \sum_{i=1}^d \lambda_i \ket{i}\ket{i}.
+%\end{align}
+%If $\supp{A_\ast^\diamond} \neq \supp{B_\ast^\diamond}$, then $B_\ast^\diamond\ket{\psi} \neq A_\ast^\diamond\ket{\psi}$. Since $B_\ast^\diamond$ and $A_\ast^\diamond$ are projectors,
+%By the orthogonality relations, we can also conclude that $A_\ast^\perp = B_\ast^\perp$.
+
+%Maybe we can first conclude that $\spn(A_0^0+A_0^1) = \spn(A_1^0+A_1^1) = \spn(A_\ast^\diamond)$.
+\begin{proposition}
+	\label{prop:s1s2}
+	Let $S$ be an $\ep$-approximate strategy. We define
+	\begin{align}
+		&M_{\nr+1} = M_{\nr+1}^0 - M_{\nr+1}^1 && M_{\nr+2} = M_{\nr+2}^0 - M_{\nr+2}^1,\\
+		&N_{\nr+1} = N_{\nr+1}^0 - N_{\nr+1}^1 && N_{\nr+2} = N_{\nr+2}^0 - N_{\nr+2}^1.
+	\end{align}
+	Then $S$ induces two strategies that achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, which are
+	\begin{align}
+		S_1 = \left(M_{\nr+1}, M_{\nr+2}, N_1, N_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right),\\
+		S_2 = \left(N_{\nr+1}, N_{\nr+2}, M_1, M_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right).
+	\end{align}
+\end{proposition}
+\begin{proof}
+We will prove that $\bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi} \appd{O(\sd r\se)} \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi}$ as an example,
+\begin{align*}
+	   \bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi} 
+	= &\bra{\psi}(M_\ast^\diamond + M_\ast^\perp) M_{\nr+1}^0N_1^0 (M_\ast^\diamond + M_\ast^\perp)\ket{\psi} \\
+	= & \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\perp\ket{\psi}\\
+	&+\bra{\psi}M_\ast^\perp M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\perp M_{\nr+1}^0N_1^0 M_\ast^\perp\ket{\psi}\\
+	\appd{O(r\se)}&  \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_{\nr+1}^\perp\ket{\psi} \\
+	&+\bra{\psi}M_{\nr+1}^\perp M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_{\nr+1}^\perp M_{\nr+1}^0N_1^0 M_{\nr+1}^\perp\ket{\psi}\\
+	=&\bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi},
+\end{align*}
+where we use the facts that $M_\ast^\perp \ket{\psi} \appd{O(r\se)} M_{\nr+1}^\perp \ket{\psi}$ and that 
+$\supp(M_{\nr+1}^0) \cap \supp(M_{\nr+1}^\perp) = \emptyset$. This means that if Alice and Bob share state $M_\ast^\diamond \ket{\psi}/\norm{M_\ast^\diamond \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
+we get conditional probability
+\begin{align*}
+	\frac{\bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi}}{\bra{\psi} M_\ast^\diamond \ket{\psi}}  
+	\appd{O(d r\se)} \frac{\bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi}}{\bra{\psi} M_\ast^\diamond \ket{\psi}}
+	\appd{O(d r^2 \ep)}
+	\frac{\cos^2(-\pi/2d)}{2}.
+\end{align*} 
+because
+\begin{align*}
+	\frac{ \norm{\bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} -  \bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi}}}
+	{\bra{\psi} M_\ast^\diamond \ket{\psi}} \leq \frac{O(r\se)}{\frac{2}{d-1} - O(r^2 \ep)} = O(d r  \se).
+\end{align*}
+Using the fact that $O(d r \se)$ dominates $O(dr^2 \ep)$,
+we can prove that the correlation generated by $S_1$ 
+is $O(dr\se)$-close to the ideal correlation that achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$.
+Hence, the strategy $S_1$ achieves the value $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r \se)$.
+The proof for $S_2$ is very similar so we omit it here.
+\end{proof}
+Based on \cref{prop:chsh_base,prop:s1s2}, we identify a special component of $\ket{\psi}$, whose special properties are summarized
+in the proposition below. In the next lemma, we establish that this special component can be used to approximate $\ket{\psi}$. 
+\begin{proposition}
+	Let $S$ be an $\ep$-approximate strategy and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.
+	We also define
+	\begin{align}
+		&\ket{\psi_1} =1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi} \\
+		&\ket{\psi_2} = 1/2(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)  \ket{\psi} \\
+		&\ket{\psi_3} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}\\
+		&\ket{\psi_4} =1/2(N_{\nr+1}^1 + iN_{\nr+2}N_{\nr+1}^1 -iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}
+	\end{align}
+	then
+	\begin{align}
+	 \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \sr\qe)} \ket{\psi_3} \text{ and } \ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_4}, \\
+	 \label{eq:psi1_sum} &M_\ast^\diamond \ket{\psi} \appd{O( r\se)} \ket{\psi_1}+\ket{\psi_2}, \\
+	 \label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
+	 \label{eq:psi1_norm} &\norm{\ket{\psi_i}}^2 \appd{O(r\se)} 1/(d-1) \quad \text{ for } i = 1, 2, 3, 4,\\
+	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d\ket{\psi_1},\\
+	 \label{eq:psi1_eig2} &M_1M_2 \ket{\psi_1} \appd{O(\sd\sr \qe)} \omega_d^{-1} \ket{\psi_1}.
+	\end{align}
+\end{proposition}
+In this proof, we use the notation $c := \cos(\pi/d)$ and $s := \sin(\pi/d)$.
+\begin{proof}
+	We prove \cref{eq:psi1_eq} to \cref{eq:psi1_eig2} one by one.
+
+	\textbf{To prove \cref{eq:psi1_eq}}, 
+	recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^0 \ket{\psi}$ 
+	and $M_{\nr+1}^1 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^1 \ket{\psi}$ proved in \cref{prop:chsh_base},
+	so it suffices to show
+	$(M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}$ is close to $(- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}$,
+	or equivalently,
+	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
+
+	At this point, we use the anticommutation relation induced by $S_1$ (\cref{eq:zaxa}) and conclude that 
+	\begin{align}
+		M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^\diamond\ket{\psi}}}}{c\sqrt{s}}O(\sd\sr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}.
+	\end{align}
+	If we use the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \sr \qe)$.
+	Then we can show that 
+	\begin{align*}
+		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \\
+			&\appd{O(r\se)} M_{\nr+2}M_{\nr+1} M_\ast^\diamond \ket{\psi} \\
+			&\appd{O(\sd \sr \qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}\\
+			&\appd{O(r\se)} -M_{\nr+1}M_{\nr+2} \ket{\psi} \\
+			&\appd{O(r\se)} -M_{\nr+1} N_{\nr+2} \ket{\psi} \\
+			&\appd{O(r\se)} -N_{\nr+2} N_{\nr+1} \ket{\psi}.
+	\end{align*}
+	The proof of $\ket{\psi_2} \appd{O(\sd \sr \qe)} \ket{\psi_4}$ is similar.
+
+	\textbf{To prove \cref{eq:psi1_sum}}, we use the definition of $\ket{\psi_1}$ and $\ket{\psi_2}$
+	\begin{align}
+		\ket{\psi_2} + \ket{\psi_1} = 1/2( 2M_{\nr+1}^0 + 2M_{\nr+1}^1) \ket{\psi} \appd{O(r\se)} M_\ast^\diamond \ket{\psi}.
+	\end{align}
+
+	\textbf{To prove \cref{eq:psi1_orth}}, we expand the inner product
+	\begin{align*}
+		&\braket{\psi_1}{\psi_2}\\
+	 = &1/4\bra{\psi}(M_{\nr+1}^0 - iM_{\nr+1}^1M_{\nr+2} + iM_{\nr+1}^0M_{\nr+2} +M_{\nr+1}^1)\\
+	 &(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)\ket{\psi}\\
+	 =& 1/2i \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0-M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
+	\end{align*}
+	Then we will show that $\bra{\psi} M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} 0$ as follows
+	\begin{align*}
+	 \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0\ket{\psi} &\appd{O(r\se)}  \bra{\psi}(N_{\nr+1}^0M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
+	  &=\bra{\psi}M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
+	&\appd{O(r^2\ep)} 0,
+	\end{align*}
+	where the last approximation comes from the correlation.
+	Similarly, we have 
+	\begin{align*}
+	\bra{\psi}(M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{O(r\se)} \bra{\psi} M_{\nr+2}N_{\nr+1}^1 \ket{\psi} \appd{O(r^2\ep)} 0.
+	\end{align*}
+	Hence, $\braket{\psi_2}{\psi_1} \appd{O(r\se)} 0$.
+
+	\textbf{To prove \cref{eq:psi1_norm}}, we use $\norm{\ket{\psi_1}}^2$ as an example. 
+	The norms of the other $3$ vectors can be derived with previous results.
+	We start by expanding the inner product
+	\begin{align*}
+		&\braket{\psi_1}{\psi_1} \\
+		=&1/4\bra{\psi}(M_{n+1}^0 - iM_{n+1}^1M_{n+2} + iM_{n+1}^0M_{n+2} +M_{n+1}^1)\\
+		&(M_{n+1}^0 + iM_{n+2}M_{n+1}^1 -iM_{n+2}M_{n+1}^0 + M_{n+1}^1)\ket{\psi}\\
+		=&1/2\bra{\psi}(M_{n+1}^0+M_{n+1}^1-iM_{n+1}^1M_{n+2}M_{n+1}^0+iM_{n+1}^0M_{n+2}M_{n+1}^1\ket{\psi}
+	\end{align*}
+	Here we apply the same trick to flip $M_{n+1}^1$ to Bob's side and get 
+	\begin{align*}
+		\bra{\psi}M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^0\ket{\psi} 
+		&\appd{O(r\se)} \bra{\psi}N_{\nr+1}^1M_{\nr+2}N_{\nr+1}^0\ket{\psi} \\
+		&= \bra{\psi}N_{\nr+1}^1N_{\nr+1}^0M_{\nr+2}\ket{\psi} = 0.
+	\end{align*}
+	Similarly, we have $\bra{\psi}M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{ O(r\se)} 0$.
+	Hence, we get 
+	\begin{align}
+		\braket{\psi_1}{\psi_1} \appd{O(r\se)} 1/2\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1\ket{\psi} \appd{O(r^2\ep)} 
+		 \frac{1}{d-1}.
+	\end{align}
+%	Using the fact that for $0 < x < 1$, $\sqrt{1+x} = 1 + 1/2 x - O(x^2)$ and $\sqrt{1-x} = 1- 1/2x - O(x^2)$,
+%	we have
+%	\begin{align}
+%		1-\frac{(d-1)r^2 \ep}{2} \leq \sqrt{d-1} \norm{\ket{\psi_1}} \leq 1 + \frac{(d-1)r^2 \ep}{2},
+%	\end{align}
+%	and we conclude that 
+%	\begin{align}
+%		\norm{\ket{\psi_1}} \appd{O(\sd r^2 \ep)} \frac{1}{\sqrt{d-1}}.
+%	\end{align}
+
+	\textbf{To prove \cref{eq:psi1_eig1}},
+	we need to dive deeper into the implication of the fact that $S_1$ almost achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$.
+	We define
+	\begin{align}
+		&Z_A  := M_{\nr+1} && X_A := M_{\nr+2} \\
+		&Z_B := \frac{N_1+N_2}{2c} && X_B := \frac{N_1-N_2}{-2s}.
+	\end{align}
+	Note that $Z_A$ should be defined by $M_{\nr+1}^0 - M_{\nr+1}^1 + M_{\nr+1}^\perp$,
+	but $M_{\nr+1}^\perp$ is almost orthogonal to $M_\ast^\diamond$, so we omit the $M_{\nr+1}^\perp$ term here.
+	In the definition of $X_A$, we omit $M_{\nr+2}^\perp$ too.
+
+	Recalling \cref{eq:za-zb}, which states that
+	\begin{align*}
+		\norm{Z_B M_\ast^\diamond \ket{\psi} - M_{\nr+1}M_\ast^\diamond \ket{\psi}} \leq 
+		\sqrt{s}\norm{M_\ast^\diamond \ket{\psi}} O(\sd \sr \qe)
+		= O(\sr \qe/ \sd ).
+	\end{align*}
+	Since $M_\ast^\diamond \ket{\psi} \appd{O(r\se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$,
+	the equation above can be rewritten as 
+	\begin{align*}
+		Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \appd{O(\sr \qe / \sd )} (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}.
+	\end{align*}
+	On the other hand, using the fact $M_{\nr+1}^0 M_{\nr+1}^1 = 0$, we can get that
+	\begin{align*}
+		O(r\se/d) \geq &\norm{Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}}^2\\
+		=&\norm{ Z_BM_{\nr+1}^0 \ket{\psi} - M_{\nr+1}^0\ket{\psi}}^2 + \norm{ Z_BM_{\nr+1}^1 \ket{\psi} + M_{\nr+1}^1\ket{\psi}}^2,
+	\end{align*}
+	which immediately gives us that 
+	\begin{align}
+		&\frac{N_1+N_2}{2c} M_{\nr+1}^0\ket{\psi} \appd{O( \sr \qe /\sd)} M_{\nr+1}^0 \ket{\psi},\\
+		&\frac{N_1+N_2}{2c} M_{\nr+1}^1\ket{\psi} \appd{O( \sr \qe /\sd)} -M_{\nr+1}^1 \ket{\psi}.
+	\end{align}
+		Substituting the appropriate operators and states into \cref{eq:zaxb,eq:xazb}, we get
+	\begin{align*}
+		\frac{N_1-N_2}{-2s} M_{\nr+1}^0M_\ast^\diamond \ket{\psi} 
+		\appd{\norm{M_\ast^\diamond\ket{\psi}}/\sqrt{s} O(\sd \sr \qe)}M_{\nr+2} M_{\nr+1}^1M_\ast^\diamond\ket{\psi}\\
+		\frac{N_1 -N_2}{-2s} M_{\nr+1}^1M_\ast^\diamond \ket{\psi}  
+		\appd{\norm{M_\ast^\diamond \ket{\psi}}/\sqrt{s}O(\sd \sr \qe)}M_{\nr+2} M_{\nr+1}^0 M_\ast^\diamond \ket{\psi}.
+	\end{align*}
+	Using the facts that $M_\ast^\diamond \ket{\psi} \appd{O(r\se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$
+	and $O(\sd \sr \qe)$ dominates $O(r \se)$, we know
+	\begin{align}
+		(N_1-N_2) M_{\nr+1}^0 \ket{\psi} \appd{O(\sr\qe/\sd )} -2sM_{\nr+2} M_{n+1}^1 \ket{\psi},\\
+		(N_1-N_2) M_{\nr+1}^1 \ket{\psi}\appd{O(\sr\qe/\sd )} -2sM_{\nr+2} M_{n+1}^0 \ket{\psi}.
+	\end{align}
+	In summary, we have shown that 
+        \begin{align}
+        		&N_1M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \qe/ \sd)} cM_{\nr+1}^0\ket{\psi} - sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
+        		&N_1M_{\nr+1}^1 \ket{\psi} \appd{O(\sr \qe/ \sd)} -cM_{\nr+1}^1\ket{\psi} - sM_{\nr+2}M_{\nr+1}^0\ket{\psi},\\
+        		&N_2M_{\nr+1}^0 \ket{\psi} \appd{O( \sr \qe /\sd)} cM_{\nr+1}^0\ket{\psi} + sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
+        		&N_2M_{\nr+1}^1 \ket{\psi} \appd{O(\sr \qe/ \sd )} -cM_{\nr+1}^1\ket{\psi} + sM_{\nr+2}M_{\nr+1}^0\ket{\psi}.
+        \end{align}
+        Then we can calculate that 
+        \begin{align*}
+        		&\quad N_1N_2 M_{\nr+1}^0 \ket{\psi} \\
+		&\appd{O(\sr \qe/\sd)} (c N_1M_{\nr+1}^0 +sM_{\nr+2}N_1M_{\nr+1}^1)\ket{\psi}\\
+        		&\appd{O( \sr \qe/\sd)}(c^2M_{\nr+1}^0- csM_{\nr+2}M_{\nr+1}^1 -csM_{\nr+2}M_{\nr+1}^1 -s^2 M_{\nr+2}^2 M_{\nr+1}^0)\ket{\psi}\\
+        		&= (\cos(2\pi/d) M_{\nr+1}^0 - \sin(2\pi/d) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.
+        \end{align*}
+        and 
+        \begin{align*}
+        		&\quad N_1N_2 M_{\nr+1}^1 \ket{\psi} \\
+		&\appd{O( \sr \qe/\sd)} (-c N_1M_{\nr+1}^1 +sM_{\nr+2}N_1M_{\nr+1}^0)\ket{\psi}\\
+        		&\appd{O(\sr \qe/\sd)}(c^2M_{\nr+1}^1+ csM_{\nr+2}M_{\nr+1}^0 +csM_{\nr+2}M_{\nr+1}^0 -s^2 M_{\nr+2}^2 M_{\nr+1}^1)\ket{\psi}\\
+        		&= (\cos(2\pi/d) M_{\nr+1}^1 + \sin(2\pi/d) M_{\nr+2}M_{\nr+1}^0)\ket{\psi},
+        \end{align*}
+        or equivalently,
+        \begin{align*}
+        		N_1N_2 M_{\nr+2}M_{\nr+1}^1 \ket{\psi}\appd{O(\sr \qe/\sd)} 
+		\sin(\frac{2\pi}{d}) M_{\nr+1}^0\ket{\psi} + \cos(\frac{2\pi}{d})M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
+        \end{align*}
+        Combining the two results above we know
+	\begin{align}
+		\label{eq:omegad}
+		&N_1N_2 (M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi} 
+		\appd{O(\sr \qe/\sd)}\omega_d(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
+	\end{align}
+	Multiplying both sides by $1/2(\1 - iM_{\nr+2})$, we get
+	\begin{align}
+		N_1N_2 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d\ket{\psi_1}.
+	\end{align}
+	Note that here we use another form of $\ket{\psi_1}$ which is 
+	$\ket{\psi_1} = 1/2(\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi}$.
+
+	\textbf{To prove \cref{eq:psi1_eig2}},
+	we first show that $M_1M_2 \ket{\psi_3}\appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_3}$, then we 
+	use the fact that $\ket{\psi_3} \appd{O(\sd \sr\qe)} \ket{\psi_1}$ to draw the conclusion.
+
+	From the strategy $S_2$, we can summarize that 
+	\begin{align}
+		&(M_1+M_2) N_{\nr+1}^0 \ket{\psi} \appd{O(\sr \qe/\sd)} 2c N_{\nr+1}^0 \ket{\psi}.\\
+		&(M_1+M_2) N_{\nr+1}^1 \ket{\psi}  \appd{O(\sr \qe/\sd)} -2cN_{\nr+1}^1 \ket{\psi},\\
+		&(M_1-M_2) N_{\nr+1}^0\ket{\psi} \appd{O(\sr\qe/\sd)}-2sN_{\nr+2} N_{\nr+1}^1\ket{\psi}\\
+		&(M_1 -M_2)N_{\nr+1}^1 \ket{\psi} \appd{O(\sr\qe/\sd)} -2sN_{\nr+2} N_{\nr+1}^0 \ket{\psi}.
+	\end{align}
+	With similar calculation as in the previous case, we can get 
+	\begin{align}
+		M_1M_2 (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi} \appd{O(\sr \qe/\sd)} 
+		\omega_d^{-1} (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1)\ket{\psi} .
+	\end{align}
+	Multiplying both sides of the equation above by $1/2(\1+iN_{\nr+2})$ we get
+	\begin{align}
+		M_1M_2 \ket{\psi_3} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_3},
+	\end{align}
+	where we use the fact that $\ket{\psi_3} = 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$
+	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \sr\qe)} \ket{\psi_3}$ gives us that 
+	\begin{align}
+		M_1M_2 \ket{\psi_1} \appd{O(\sd \sr \qe)} \omega_d^{-1}\ket{\psi_1}.
+	\end{align}
+\end{proof}
+%Note that it can be shown that 
+%\begin{align}
+%	&\ket{\psi_1} =  (\1 - iA_{n+2})(\1 + i \frac{B_1 - B_2}{-2\sin(\pi/d)})A_{n+1}^0 \ket{\psi}\\
+%	&\ket{\psi_2} =  (\1 - iA_{n+2})(\1 + i \frac{B_1 - B_2}{-2\sin(\pi/d)})A_{n+1}^1 \ket{\psi}.
+%\end{align}
+Next lemma is the major result of this subsection, which gives us a decomposition of $\ket{\psi}$.
+Before proving the next lemma, we make one important observation.
+Recall that \cref{prop:lct_base} establishes that there exist observables $\{M_i, N_i\}$ such that 
+$M_iN_i \ket{\psi} \appd{O(r\se)} \ket{\psi}$ for $i = 1 \dots \nr$.
+Then we can deduce that 
+\begin{align}
+	M_3M_4 \x N_3N_4 \ket{\psi} \appd{O(r\se)} M_3 \x N_3 \ket{\psi} \appd{O(r\se)} \ket{\psi},
+\end{align}
+or equivalently,
+\begin{align}
+	U_A \x U_B \ket{\psi} \appd{O(r\se)} \ket{\psi}.
+\end{align}
+Intuitively, it means that $U_A U_B $ only permutes the Schmidt basis of $\ket{\psi}$.
+Similarly, we also have $U_A\ct U_B\ct \ket{\psi} \appd{O(r\se)} \ket{\psi}$.
+We use this observation in the proof of the following proposition.
+\begin{lemma}
+\label{lm:decomp_psi}
+Let $S$ be an $\ep$-approximate strategy and 
+define 
+$\ket{\psi'} := \sum_{j=1}^{(d-1)} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}$,
+then
+\begin{align}
+	&\ket{\psi} \appd{O(d^{7/4} r^{1/4} \ep^{1/8})} \ket{\psi'},
+\end{align}
+where $\log_r j$ is the discrete log.
+\end{lemma}
+\begin{proof}
+	We first prove that $\norm{\ket{\psi'}}^2 \appd{O(d^4 \sr \ep^{1/8})} 1$.
+	Observe that 
+	\begin{align*}
+		\bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j}  \ket{\psi_1} =
+		\braket{\psi_1}{\psi_1} \appd{O(r\se)} \frac{1}{d-1}.
+	\end{align*}
+	Using the relation $O_A(U_A\ct)^j \ket{\psi} \appd{O(r^j \se)} (U_A\ct)^j O_A^{r^j}\ket{\psi}$ and $\ket{\psi_1} \appd{O(\sd \sr \qe)} \ket{\psi_3}$,
+        we can see that 
+        \begin{align*}
+            	O_A (U_A\ct)^j \ket{\psi_1} &\appd{O(\sd \sr \qe)} O_A(U_A\ct)^j \ket{\psi_3} \\
+            	& = 1/2 (\1 + i N_{\nr+2})(N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1) O_A (U_A\ct)^j \ket{\psi} \\
+            	& \appd{O(r^j \se)} 1/2  (\1 + i N_{\nr+2})(N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1)  (U_A\ct)^j O_A^{r^j} \ket{\psi} \\
+            	& = (U_A\ct)^j O_A^{r^j} \ket{\psi_3} \\
+            	& \appd{O(r^j \sr \qe/\sd)} \omega_d^{-r^j}(U_A\ct)^j \ket{\psi_3} \\
+            	& \appd{O(\sd \sr\qe)} \omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
+        \end{align*}
+        In short, we have shown that 
+        \begin{align}
+        		O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j+1/2} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
+        \end{align}
+	Hence for $j \neq j'$, \cref{prop:orthog} tells us that  
+	\begin{align}
+		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O(d^{3/2} (r^j + r^{j'})\sr \qe)} 0.
+	\end{align}
+	We can calculate the norm of $\ket{\psi'}$ as 
+	\begin{align*}
+		\braket{\psi'}{\psi'} &=\sum_{j,j'=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j'} \ket{\psi_1}\\
+		&\appd{O(d^{5/2} r^{d+1/2} \qe)} \sum_{j=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}\\
+		&\appd{O(dr\se)} (d-1) \frac{1}{d-1} = 1.
+	\end{align*}
+
+	Next we calculate $\braket{\psi}{\psi'}$ which is
+	\begin{align*}
+		\braket{\psi}{\psi'} = \sum_{j=1}^{d-1} \bra{\psi} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}
+		 \appd{O(dr\se)} (d-1) \braket{\psi}{\psi_1}.
+	\end{align*}
+	The problem is reduced to calculate $\braket{\psi}{\psi_1}$, which is
+	\begin{align*}
+		\braket{\psi}{\psi_1} &= \frac{1}{2} \bra{\psi} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi}\\
+		& = \frac{1}{2} \left(\bra{\psi}(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - i \bra{\psi}M_{\nr+2}M_{\nr+1} \ket{\psi} \right)\\
+		& \appd{O(r\se)} \frac{1}{2} \left(\bra{\psi}(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}  - i \bra{\psi}N_{\nr+2}M_{\nr+1} \ket{\psi} \right)\\
+		& \appd{O(r^2 \ep)} \frac{1}{2} \frac{2}{d-1} = \frac{1}{d-1},
+	\end{align*}
+	where the last approximation comes from the correlation.
+	Hence, we know $\braket{\psi}{\psi'} \appd{O(d r \se)} 1$.
+	In the end, we apply \cref{prop:close_vec} to get
+	\begin{align}
+		\ket{\psi} \appd{O(d^{5/4} r^{d/2+1/4} \ep^{1/8})} \ket{\psi'}.
+	\end{align}
+\end{proof}
+
+%------------------------------------------------------------------------------------------
+\subsection{Implications of passing the commutation test}
+\label{sec:imp_comm}
+%-------------------------------------------------------------------------------------------
+The commutation test is introduced to certify the operators used for the Magic Square test and 
+the operators for the extended weighted CHSH test commute. For details of the general commutation test, 
+we refer to Appendix~A.$2$ of \cite{coladan2017verifier}. 
+We use the similar technique in our proof but our proof also bases on the correlation given in \cref{tbl:comm}.
+
+The implication of passing the commutation test is summarized in the following proposition.
+\begin{proposition}
+	\label{prop:rel_comm}
+	Let $S$ be an $\ep$-approximate strategy ,
+	then 
+	\begin{align}
+		&M_{\nr+1}^0 M_j \ket{\psi} \appd{O(r\se)} M_{j} M_{\nr+1}^0 \ket{\psi}, &&
+		M_{\nr+1}^1 M_j \ket{\psi} \appd{O(r\se)} M_{j} M_{\nr+1}^1 \ket{\psi}, \\
+		&M_{\nr+2} M_j \ket{\psi} \appd{O(r\se)} M_j M_{\nr+2} \ket{\psi},
+	\end{align}
+	for $j = r+6, r+8,r+9,r+11$.
+\end{proposition}
+Note that $M_j$'s tested in the commutation test are also used in the Magic Square test,
+which will be used to construct the isometry later.
+\begin{proof}
+	The case of $M_j M_{\nr+2}$ is an application of Lemma~$28$ of \cite{coladan2017verifier} with $\se$ replaced by $O(r\se)$.
+
+	For the other relations, we prove $M_{\nr+1}^0M_{r+6} \ket{\psi} \appd{O(r\se)} M_{r+6}M_{\nr+1} \ket{\psi}$ to demonstrate 
+	the techniques involved. We denote Bob's projectors by $\{ N_{(\nr+1, r+6)}^{b_1 b_2} \}$ where $b_1 \in \{0, 1, \perp\}$ and
+	$b_2 \in \{0,1\}$. From the correlation, we can get that 
+	\begin{align*}
+		&M_{\nr+1}^0 \ket{\psi} \appd{O(r\se)} (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01}) \ket{\psi} \\
+		&M_{r+6} \ket{\psi} \appd{O(r\se)} (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, r+6)}^{b_1b_2})\ket{\psi}.
+	\end{align*}
+	Then we can show that
+	\begin{align*}
+		M_{\nr+1}^0 M_{r+6} \ket{\psi} &\appd{O(r\se)} M_{\nr+1}^0 (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, r+6)}^{b_1b_2})\ket{\psi}\\
+		&\appd{O(r\se)}(\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, r+6)}^{b_1b_2}) (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01})
+		\ket{\psi} \\
+		&= (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01}) (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, r+6)}^{b_1b_2})  \ket{\psi} \\
+		& \appd{O(r\se)} (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01}) M_{r+6} \ket{\psi} \\
+		&= M_{r+6}  (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01}) \ket{\psi} \\
+		& \appd{O(r\se)} M_{r+6}M_{\nr+1}^0 \ket{\psi}.
+	\end{align*}
+\end{proof}
+%-----------------------------------------------
+\subsection{An isometry}
+\label{sec:isometry}
+%-----------------------------------------------
+With the previous propositions and lemmas, we can prove the self-testing theorem.
 \begin{theorem}
-\label{thm:selftest}
-	If a quantum strategy using the shared state $\ket{\psi}$ achieves the ideal 2-party correlation $C(\dr{r})$ where $d$ is an odd
-	prime number with primitive root $r \in \{2,3,5\}$, then there exist local isometries $\Phi_A$ and $\Phi_B$, and a state $\ket{junk}$ such 
-	that $\Phi_A\x\Phi_B \ket{\psi} = \ket{\EPR{d-1}} \x \ket{junk}$.
+	\label{thm:self-test}
+	Let $S$ be an $\ep$-approximate strategy.
+	There exists an isometry   
+	$\Phi_A \x \Phi_B = (\Phi_{A,2} \x \Phi_{B,2})(\Phi_{A,1}\x\Phi_{B,2})$ and a state $\ket{junk}$
+	such that $\norm{\ket{junk}}^2 \appd{O(dr\se)} 1$ and 
+	\begin{align}
+		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d^{5/4} r^{2d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
+		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d^{5/4} r^{2d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
+		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d^{5/4}r^{2d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
+		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d^{5/4} r^{2d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'} \\
+		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d^{5/4} r^{2d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_{j r^{-1}}}_{B'}.
+	\end{align}
 \end{theorem}
-\begin{proof}
-Suppose Alice and Bob achieve the optimal correlation with the quantum strategy $(\ket{\psi}, \{A_x\}, \{B_y\})$
-for all $x,y \in \calX \times \calY$ .
-The observables $A_x$ and $B_y$ and the shared state $\ket{\psi}$ shall not be confused with the ones used in the optimal strategy.
-By Lemma~$4.3$ of Ref.~\cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
-of the linear system game $\LS_r$. 
-For each variable $\{ x_i \}_{i=1}^{n_r}$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
-The condition that they agree with assignment to variables means that 
-\begin{align}
-	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
-	\text{ for } 1 \leq i \leq n_r
-\end{align}
-and the condition that Alice's assignments satisfy the constraint means that 
-\begin{align}
-	\Tr(\rho_A \Pi_{j: H(i,j) \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m_r
-\end{align}
-where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$. 
-Similarly we define $\rho_B = \Tr_A(\ketbra{\psi}{\psi})$.
-For any $\ket{v} \in \supp(\rho_A)$,
-we have 
-\begin{align}
-\Pi_{j:H(i,j) \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m_r.
-\end{align}
-Since the relation $uxu^{-1} = x^r$, where $r$ is the primitive root of $d$, is embedded in this linear system game, we know
-\begin{align}
-	A_3A_4 A_1A_2 (A_3A_4)^\dagger \ket{v}= (A_1A_2)^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
-\end{align}
-For simplicity, we define $X_A = A_1A_2$ and $U_A=A_3A_4$ such that
-the condition is equivalent to
-\begin{align}
-	\label{eq:ux_relation}
-	U_AX_AU_A^\dagger \ket{v} = X_A^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
-\end{align}
-We will come back to the implication of this condition later.
-
-Suppose $A_{m_r+1} = A_\ast^\diamond- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
-$2m$-dimensional vector space and $\Pi_{V_A}$ is the projector onto it. The reason why it has dimension $2m$
-will be clear shortly. On Bob's side, we also have $B_{n_r+1} = B_\ast^\diamond- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
-Recall that from the extended weighted CHSH test, we know
-\begin{align}
-	A_\ast^\diamond \ket{\psi} = B_\ast^\diamond \ket{\psi} = A_\ast^\diamond \x B_\ast^\diamond \ket{\psi},
-\end{align}
-which implies that with an appropriate change of basis, we can get $V_A = V_B$, so in the rest of the proof
-we drop the subscript of $V$.
-By \cref{lm:chsh_comp} and \cref{prop:2d-subspace}, we know $V$ consists of $\omega_d$-eigenvectors and $\omega_d^{-1}$ eigenvectors of 
-$X_A$, so we can write 
-\begin{align}
-	\Pi_{V} = \Pi_{V_1} + \Pi_{V_{d-1}},
-\end{align}
-where $\Pi_{V_{1}}$ is the projector onto the $\omega_d$-eigenspace of $X_A$ and $\Pi_{V_{d-1}}$ is the projector 
-onto the $\omega_d^{-1}$-eigenspace of $X_A$.
-\hl{Here what we need is that $\Pi_{V_1,A} \ket{\psi} = \Pi_{V_{d-1},B} \ket{\psi} = \Pi_{V_1,A}\Pi_{V_{d-1},B}\ket{\psi}$
-and $\Pi_{V_1,B} \ket{\psi} = \Pi_{V_{d-1},A} \ket{\psi} = \Pi_{V_1,B}\Pi_{V_{d-1},A}\ket{\psi}$.
-This is not proved because $\Pi_{V_1}$ and $\Pi_{V_{d-1}}$ are not in the strategy.}
-Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.
-By \cref{eq:ux_relation} we can calculate that
-\begin{align}
-\label{eq:ladder}
- X_AU_A^\dagger \ket{x_{1}} = U_A^\dagger X_A^r \ket{x_{1}} = \omega_d^r U_A^\dagger \ket{x_{1}},
-\end{align}
-so $U_A^\dagger \ket{x_{1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^r$.
-By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{r^i} (U_A^\dagger)^i\ket{x_{1}}$. 
-From the set $\{(U_A^\dagger)^i \Pi_{V_1} (U_A)^i \}_{i=0}^{d-2}$, we can identify $\Pi_{V_i}$ for $i = 1 \dots  d-1$
-such that $\Pi_{V_i}$ is the projector onto the $\omega_d^i$-eigenspace of $X_A$,
-\hl{Actually, we are not sure about the containment between $\supp((U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)})$ and 
-$\supp(\Pi_{V_{d-1}})$, so we cannot say that $\Pi_{V_{d-1}} = (U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)}$.}
-and 
-\begin{align}
- \cup_{i \in [d-1]+1} V_i \subset \supp(\rho_A).
-\end{align}
-Since unitary transformation does not change the rank of a matrix, we know $\rank(\Pi_{V_1}) = \rank(\Pi_{V_{i}}) =N$
-for $ i =1 \dots d-1$.
-We pick a basis for $V_1$ such that 
-\begin{align}
-	\Pi_{V_1} =  \sum_{j=1}^m \ketbra{x_{1,j}}{x_{1,j}},
-\end{align}
-then we can construct 
-\begin{align}
- \Pi_{V_i} = \sum_{j=1}^m \ketbra{x_{i,j}}{x_{i,j}},
-\end{align}
-where $\ket{x_{i,j}} = (U\ct)^{k_i} \ket{x_{1,j}}$ for $r^{k_i} \equiv i \pmod{d}$ and $1 \leq j \leq m$.
-By \cref{eq:ux_relation} we also know that $U_A \ket{x_{i,j}} = \ket{x_{i/2,j}}$ for $i = 1,2 \dots d-1$.
-In order to apply \cref{lm:ux_independ}, we construct $m$ subspaces $\{W_j\}_{j=1}^m$ where 
-\begin{align}
-	W_j = \spn( \{ \ket{x_{i,j}} \}_{i=1}^{d-1} )
-\end{align}
-The subspace $W_j$ is orthogonal to $W_{j'}$ for $j \neq j'$, and
-$U_A$ and $X_A$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
-restricted to each $W_j$.
-Similar argument also applies to operator $X_B$ and $U_B$ on Bob's side.
-
-%Similar argument applies to Bob's operators. We can identify $X_B = B_1B_2$, 
-%$U_B=B_3B_4$ and a vector space $S_B =\spn\{ \ket{x_{B,1}}, \ket{x_{B,2}} \dots  \ket{x_{B,d-1}} \} \subset \supp(\rho_B)$,
-%such that 
-%\begin{align}
-%	X_B = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_{B,i}}{x_{B,i}} && U_B = \sum_{i=1}^{d-1} \ketbra{x_{B,i/2}}{x_{B,i}},
-%\end{align}
-%when their actions are restricted to $S_B$. Moreover, we can define a unitary $V: \supp{\rho_B} \to \supp(\rho_A)$,
-%which maps $\ket{x_{B,i}}$ to $\ket{x_{A,i}}$ for $i=1\dots d-1$.
-
-%and projectors $\Pi_{S_A}$ and $\Pi_{S_B}$ to be the projectors onto $S_A$ and $S_B$ respectively.
-%From now on, we focus on the state $\ket{\psi_S}$ which is defined as
-%\begin{align}
-%	\ket{\psi_S} = (\Pi_{S_A} \x (V\Pi_{S_B}))\ket{\psi} = \vc(\tau) 
-%\end{align}
-%for some $\tau \in L(S_A)$.
-With an appropriate change of basis, we 
-assume that $\ket{\psi} = \vc(\tau)$ for some $\tau \in L(\supp(\rho_A))$
-The consistency condition is equivalent to
-\begin{align}
-\label{eq:con_tau}
-	A_i \tau B_i^\dagger = \tau.
-\end{align}
-Substituting $i=1,2$ into \cref{eq:con_tau}, we get 
-\begin{align}
-	X_A \tau X_A^\dagger = A_1A_2\tau B_2^\dagger B_1^\dagger = A_1\tau B_1^\dagger = \tau.
-\end{align}
-Similar argument gives us that 
-\begin{align}
-	U_A \tau U_A^\dagger = \tau.
-\end{align}
-Then we can conclude that for any $k \in \{0,1 \dots d-2\}$ and $l \in \{1,2\dots d-1\}$
-\begin{align}
-	U_A^kX_A^l \tau (U_A^kX_A^l)^\dagger = \tau.
-\end{align}
-Let $\Pi_{W_j}$ be the projector onto $W_j$. 
-By \cref{lm:ux_independ}, $\Pi_{W_j} \tau \Pi_{W_j}$ commutes with all the $(d-1) \times (d-1)$ matrices, which means that 
-\begin{align}
-	\label{eq:d-1}
-	\Pi_{W_j} \tau \Pi_{W_j}  = c_j \1_{W_j} \text{ for } j = 1\dots m.
-\end{align}
-In the vector form, we know
-\begin{align}
-	\sum_{j =1}^N \Pi_{W_j} \ket{\psi} =\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}. 
-\end{align}
-Recalling the fact that 
-\begin{align}
-\norm{ \Pi_{V_1} + \Pi_{V_{d-1}} \ket{\psi}}^2 = \norm{\Pi_{V_1} \ket{\psi}}^2 + \norm{\Pi_{V_{d-1}} \ket{\psi}}^2 = \frac{2}{d-1},
- \end{align}
- it means that 
- \begin{align}
- 	2 \sum_{j=1}^m \norm{c_j}^2 = \frac{2}{d-1}.
- \end{align}
- Then we can calculate the norm of $\sum_{j =1}^m \Pi_{W_j} \ket{\psi}$, which is
- \begin{align}
- \norm{\sum_{j =1}^m \Pi_{W_j} \ket{\psi}}^2 = \sum_{i=1}^{d-1} \sum_{j=1}^m \norm{c_j}^2 = 1 = \norm{\ket{\psi}}^2.
- \end{align}
- We can conclude that $\supp{\rho_A} = \cup_{i=1}^{d-1} V_i$ and 
- \begin{align}
- 	\ket{\psi} = \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}.
- \end{align}
-
-The last step is to construct the local isometries $\Phi_A$ and $\Phi_B$ that can produce $\ket{\EPR{d-1}}$ from $\ket{\psi}$.
-To help understanding, we draw a diagram to demonstrate the isometry first and then show
-how this isometry works.
+Before proving \cref{thm:self-test}, we state the consequence of it.
+It implies that,
+for any odd prime number $d$ with primitive root $r$, 
+there exists a correlation of size $\Theta(r^2)$ that can self-test the maximally
+entangled state of local dimension $4(d-1)$.
+Moreover, there are infinitely many prime numbers
+whose primitive roots are in the set $\{2,3,5\}$ \cite{murty1988},
+Hence, our main result is the following theorem.
+\begin{theorem}
+	There exists an infinity-sized set $D$ of prime numbers such that 
+	for each $d \in D$, there exists
+	a constant-sized correlation that can self-test the maximally entangled state
+	of local dimension $4(d-1)$.
+\end{theorem}
+
+The isometry used in the proof of \cref{thm:self-test} has two steps. 
+We denote the isometry used in the first step and the second step by $\Phi_{A,1} \x \Phi_{B,1}$ and 
+$\Phi_{A,2} \x \Phi_{B,2}$ respectively, which are illustrated 
+in the two figures below.
+In the first step, 
+we use $U_A, O_A$ and $U_B$, $O_B$ to distill a copy of $\ket{\EPR{d-1}}$.
+In the second step. we use the observables $M_{r+6},M_{r+8}, M_{r+9}, M_{r+11}$ and 
+$N_{r+6}, N_{r+8}, N_{r+9}, N_{r+11}$ to distill two copies of $\ket{\EPR{2}}$.
+Intuitively, $M_{r+6}$ acts as $\1 \x X$; $M_{r+8}$ acts as $X \x \1 $;
+$M_{r+9}$ acts as $\1 \x Z$ and $M_{r+11}$ acts as $Z \x \1$; and similarly on Bob's side.
+
 \begin{figure}[H]
@@
         \node[phase] (phase11) at (2,0) {} edge [-] (op11);
-	\node[operator] (op22) at (2,-1) {$X_A$} edge [-] (q2);
-	\node[operator] (op23) at (2, -2) {$X_B$} edge[-] (q3);
+	\node[operator] (op22) at (2,-1) {$O_A$} edge [-] (q2);
+	\node[operator] (op23) at (2, -2) {$O_B$} edge[-] (q3);
         \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
@@
         \draw[decorate,decoration={brace},thick] (5,-1) to
-    	node[midway,right] (bracket) {$\ket{junk}$}
+    	node[midway,right] (bracket) {$\ket{reuse}$}
     	(5,-2);
@@
         \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
-    	node[midway,right] (bracket2) {$\ket{\EPR{d-1}}$}
+    	node[midway,right] (bracket2) {$\sum_{j=1}^{d-1}\ket{j}\ket{d-j}$}
     	(6.5,-2.5);
@@
         \end{tikzpicture}
-	\caption{The isometries $\Phi_A$ and $\Phi_B$.}
+	\caption{The isometries $\Phi_{A,1} \x \Phi_{B,1}$.}
 \end{figure}
-The isometry maps the state $\ket{\psi}$ in the following steps:
+
+The first isometry has the following steps:
 \begin{enumerate}
-	\item Append $\ket{0}_A$ on Alice's side and $\ket{0}_B$ on Bob's side as control registers, and
-	the state becomes $\ket{\psi} \ket{0}_A \ket{0}_B$;
-	\item Apply $QFT_d$ to the control registers, and the state becomes
-	\begin{align}
-		\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \ket{\psi} \ket{k_1}_A \ket{k_2}_B;
-	\end{align}
-	\item Apply $X_A^{k_1}$ to Alice's share of $\ket{\psi}$ and $X_B^{k_2}$ to Bob's share controlled
-	by the control registers, and the state becomes
-	\begin{align}
-		&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1}X_A^{k_1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B\\
-		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1}\ket{x_{i,j}}_A X_B^{k_2}\ket{x_{i,j}}_B
-		\ket{k_1}_A \ket{k_2}_B\\
-		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1i+k_2i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
-		\ket{k_1}_A \ket{k_2}_B;
-	\end{align}
-	\item Apply $QFT_d^{-1}$ to the control registers, and the state becomes
-	\begin{align}
-		&\frac{1}{d^2} \sum_{l_1,l_2 =0}^{d-1}\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i-l_1)+k_2(i-l_2)} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
-		\ket{l_1}_A \ket{l_2}_B\\
-		=& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B;
-	\end{align}
-	\item Let $n_i$ satisfy the condition $r^{n_i} \equiv i \pmod{d}$, apply $U_A^{(i)} = U_A^{n_i}$ to Alice's share of $\ket{\psi}$ and $U_B^{(i)} = U_B^{n_i}$ to Bob's share controlled
-	by the control registers, and the state becomes
-	\begin{align}
-		&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B \\
-		=&\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i r^{-n_i} ,j}}_A \ket{x_{i r^{-n_i},j}}_B \ket{i}_A\ket{i}_B\\
-		=& \sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i i^{-1},j}}_A \ket{x_{i i^{-1},j}}_B \ket{i}_A\ket{i}_B\\
-		= &\left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \sum_{i=1}^{d-1} \ket{i}_A\ket{i}_B\\
-		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
-		\frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1}\ket{i}_A\ket{i}_B\\
-		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \ket{\EPR{d-1}},
-	\end{align}
-	where in the last line we used the fact that $\norm{\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B} = 1/\sqrt{d-1}$.
+	\item Append control register $\ket{0}_{A'}$ on Alice's side and $\ket{0}_{B'}$ on Bob's side;
+	\item Apply Quantum Fourier Transform ($QFT_d$) to Alice and Bob's control registers;
+	\item Apply Controlled-$O_{A/B}$ operations (i.e. if the control register is in state $\ket{k}_{A'/ B'}$, apply
+	$O_{A/B}^k$.);
+	\item Apply inverse Quantum Fourier Transform ($QFT_d^{-1}$) to the control registers;
+	\item Apply Controlled-$U_{A/B}$ operations (i.e. If Alice's control register is in state $\ket{j}$, she applies
+	$U_A^{\log_r (d-j)}$. If Bob's control register is in state $\ket{j}$, he applies $(U_B\ct)^{\log_r j}$).
 \end{enumerate}
 
-If the initial state is $X_A\ket{\psi}$, the isometry maps the state as following
-\begin{align}
-	X_A\ket{\psi} \to &X_A\ket{\psi}\ket{0}_A\ket{0}_B\\
-	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
-	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A^{k_1+1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
-	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1+k_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
-		\ket{k_1}_A \ket{k_2}_B\\
-	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1-l_1)i+(k_2-l_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
-		\ket{l_1}_A \ket{l_2}_B\\
-	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B\\
-	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
-	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{i}_A\ket{i}_B\\
-	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
-		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\omega_d^i \ket{i}_A\ket{i}_B\\
-	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tX_A \ket{\EPR{d-1}},
-\end{align}
-where $\tX_A$ is the ideal $X$ operator.
-The case of $X_B\ket{\psi}$ is similar, so we omit it here.
-
-If the initial state is $U_A\ket{\psi}$, the isometry maps the state as following
-\begin{align}
-	U_A\ket{\psi} \to &U_A\ket{\psi}\ket{0}_A\ket{0}_B\\
-	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} U_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
-	= &\frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A\ket{x_{i,j}}_A\ket{x_{i,j}}_B
-		\ket{k_1}_A \ket{k_2}_B\\
-	= & \frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i r^{-1} ,j}}_A\ket{x_{i,j}}_B
-		\ket{k_1}_A \ket{k_2}_B\\
-	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1} \ket{x_{i r^{-1} ,j}}_A
-	X_B^{k_2}\ket{x_{i,j}}_B  \ket{k_1}_A \ket{k_2}_B \\
-	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1 i/r}\omega_d^{k_2i} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
-		\ket{k_1}_A \ket{k_2}_B\\
-	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i/r-l_1)}\omega_d^{(k_2(i-l_2)} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
-		\ket{l_1}_A \ket{l_2}_B\\
-	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j  \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B \ket{ir^{-1}}_A \ket{i}_B\\
-	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(ir^{-1})}\ket{x_{ir^{-1},j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
-	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{ir^{-1}}_A\ket{i}_B\\
-	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
-		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\ket{ir^{-1}}_A\ket{i}_B\\
-	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tU_A \ket{\EPR{d-1}},
-\end{align}
-where $\tU_A$ is the ideal $U$ operator on Alice's side.
-The derivation is similar when $U_B$ is applied, so we omit it here.
+\begin{figure}[H]
+\center
+        \begin{tikzpicture}[thick]
+        %
+        % `operator' will only be used by Hadamard (H) gates here.
+        % `phase' is used for controlled phase gates (dots).
+        % `surround' is used for the background box.
+        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
+        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
+        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
+        %
+        % Bracket
+        \draw[decorate,decoration={brace,mirror},thick] (0,-2) to
+    	node[midway,left] (bracket1) {$\ket{reuse}$}
+    	(0,-3);
+        % Qubits
+        \node at (0,0) (q1) {$\ket{0}$};
+        \node at (0,-1) (q2) {$\ket{0}$};
+        \node at (0,-2) (q3) {};
+        \node at (0,-3) (q4) {};
+        \node at (0,-4) (q5) {$\ket{0}$};
+        \node at (0,-5) (q6) {$\ket{0}$};
+        %
+        % Column 1
+        \node[operator] (op11) at (1,0) {$H$} edge [-] (q1);
+        \node[operator] (op12) at (1,-1) {$H$} edge [-] (q2);
+         \node[operator] (op15) at (1,-4) {$H$} edge [-] (q5);
+        \node[operator] (op16) at (1,-5) {$H$} edge [-] (q6);
+        %
+        % Column 3
+        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
+	\node[operator] (op23) at (2,-2) {$M_{r+11}$} edge [-] (q3);
+	\node[operator] (op24) at (2, -3) {$N_{r+11}$} edge[-] (q4);
+        \node[phase] (phase16) at (2,-5) {} edge [-] (op16);
+        \draw[-] (phase11) -- (op23);
+        \draw[-] (phase16) -- (op24);
+        %
+        % Column 4
+        \node[phase] (phase12) at (3.5,-1) {} edge [-] (op12);
+	\node[operator] (op33) at (3.5,-2) {$M_{r+9}$} edge [-] (op23);
+	\node[operator] (op34) at (3.5, -3) {$N_{r+9}$} edge[-] (op24);
+        \node[phase] (phase15) at (3.5,-4) {} edge [-] (op15);
+        \draw[-] (phase12) -- (op33);
+        \draw[-] (phase15) -- (op34);
+        %
+         % Column 5
+        \node[operator] (op41) at (4.5,0) {$H$} edge [-] (phase11);
+        \node[operator] (op42) at (4.5,-1) {$H$} edge [-] (phase12);
+         \node[operator] (op45) at (4.5,-4) {$H$} edge [-] (phase15);
+        \node[operator] (op46) at (4.5,-5) {$H$} edge [-] (phase16);
+        %
+        % Column 6
+        \node[phase] (phase51) at (5.5,0) {} edge [-] (op41);
+	\node[operator] (op53) at (5.5,-2) {$M_{r+8}$} edge [-] (op33);
+	\node[operator] (op54) at (5.5, -3) {$N_{r+8}$} edge[-] (op34);
+        \node[phase] (phase56) at (5.5,-5) {} edge [-] (op46);
+        \draw[-] (phase51) -- (op53);
+        \draw[-] (phase56) -- (op54);
+        %
+        % Column 7
+        \node[phase] (phase62) at (7,-1) {} edge [-] (op42);
+	\node[operator] (op63) at (7,-2) {$M_{r+6}$} edge [-] (op53);
+	\node[operator] (op64) at (7, -3) {$N_{r+6}$} edge[-] (op54);
+        \node[phase] (phase65) at (7,-4) {} edge [-] (op45);
+        \draw[-] (phase62) -- (op63);
+        \draw[-] (phase65) -- (op64);
+        %
+        % Bracket
+        \node(end3) at (8, -2) {} edge [-] (op63);
+        \node(end4) at (8, -3) {} edge [-] (op64);
+        \draw[decorate,decoration={brace},thick] (8.2,-2) to
+    	node[midway,right] (bracket) {$\ket{junk}$}
+    	(8.2,-3);
+        %
+        % Column 7
+        \node (end1) at (9.5,-1) {} edge [-] (phase51);
+        \node(end2) at (9.5, -1.5) {} edge [-] (phase62);
+       \node(end5) at (9.5, -3.5) {} edge [-] (phase65);
+        \node (end6) at (9.5,-4) {} edge [-] (phase56);
+        % Dashed line
+        \draw[loosely dotted] (0,-2.5) -- (7.8,-2.5);
+        \draw[solid] (end1) -- (9.3, -1);
+        % Bracket
+        \draw[decorate,decoration={brace},thick,] (9.5,-1.1) to
+    	node[midway,right] (bracket2) {$\ket{\EPR{2}}^{\x 2}$}
+    	(9.5,-3.9);
+        %
+        % Background Box
+        \begin{pgfonlayer}{background} 
+        \node[surround] (background) [fit = (q1) (op16) (bracket1)(bracket2)] {};
+        \end{pgfonlayer}
+        %
+        \end{tikzpicture}
+	\caption{The isometries $\Phi_{A,2} \x \Phi_{B,2}$.}
+\end{figure}
+
+The second isometry is the standard isometry used in the self-testing result of the Magic Square game \cite{wu2016}.
+The only thing to note is that the state $\ket{reuse}$, which is on the same Hilbert space as $\ket{\psi}$ and produced by $\Phi_{A,1} \x \Phi_{B,1}$, is the input state to $\Phi_{A,2} \x \Phi_{B,2}$.
+In this sense, our isometry is a $2$-step sequential procedure.
+
+%We first list the key relations needed for $\Phi_{A,1} \x \Phi_{B,1}$ to work.
+%\begin{align}
+%	&\ket{\psi} \appd{O(d^{5/4} r^{d/2} r^{1/4} \ep^{1/8})}\ket{\psi'} = \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1},\\
+%	&O_A(U_A\ct)^{\log_r j} \ket{\psi_1} \appd{O(\sd r^j \sr \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}\\
+%	&O_B(U_A\ct)^{\log_r j} \ket{\psi_1} \appd{O(\sd r^j \sr \qe)}\omega_d^{r^j}  (U_A\ct)^j \ket{\psi_1}.
+%\end{align}
+%The second isometry just requires properties of the Magic Square game, especially, the commutation relations in \cref{prop:lct_comm}.
+
+\begin{proof}[Proof of \cref{thm:self-test}]
+The proof takes two steps. 
+We first show that 
+\begin{align}
+	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/4} r^{2d+1/2} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
+\end{align}
+Then we show that there exists a state $\ket{junk}$ such that  
+\begin{align}
+\label{eq:phi2_result}
+\Phi_{A,2} \x \Phi_{B,2} (\sqrt{d-1}\ket{\psi_1}) \appd{O(r\se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2}.
+\end{align}
+Combining the two equations above we get that 
+\begin{align*}
+	&\Phi_{A,2} \x \Phi_{B,2}( \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi})) \\
+	&\appd{O(d^{5/2} \sr \ep^{1/8})} \Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \x\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
+	&\appd{O(r\se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
+\end{align*}
+where we use the fact that $\Phi_{A,2}\x \Phi_{B,2}$ only acts on the state $\ket{\psi_1}$.
+
+\cref{lm:decomp_psi} implies that $ \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi}) \appd{O(d^{5/4} r^{d/2} r^{1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi'})$,  
+so we focus on how the isometry evolves $\ket{\psi'}$.
+The evolution is summarized below.
+	\begin{align}
+		& \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_1}_{A'}\ket{x_1}_{B'}\\
+		\xrightarrow[]{QFT_d}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}  \ket{\psi_1}\ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\xrightarrow[]{\text{Controlled-}O_{A/B}}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} O_A^{k_1}(U_A\ct)^{\log_r j} O_B^{k_2}(U_B\ct)^{\log_r j}
+		\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\appd{O(\sd r^{2d} \sr \qe)}&\frac{1}{d} \sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}\omega_d^{(k_2-k_1)j}\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\xrightarrow[]{QFT_d^{-1}} &\frac{1}{d^2}\sum_{l_1,l_2 = 0}^{d-1}\sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} 
+		\omega_d^{k_1(d-j-l_1)}\omega_d^{k_2(j-l_2)}\ket{\psi_1} \ket{x_{l_1}}_{A'}\ket{x_{l_2}}_{B'}\\
+		= &\sum_{j=1}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
+		\xrightarrow[]{\text{Controlled-}U_{A/B}}& \sum_{j=1}^{d-1} U_A^{\log_r j} (U_A\ct)^{\log_r j} U_B^{\log_r j} (U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
+		=&\ket{\psi_1} \x \sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
+	\end{align}
+In summary, we have shown that
+\begin{align}
+	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/4} r^{2d+1/2} \ep^{1/8})} \sqrt{d-1} \ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
+\end{align}
+where we use the fact that $O(d^{5/4} r^{2d+1/2} \ep^{1/8})$ dominates both $O(d^{5/4} r^{d/2+1/4} \ep^{1/8})$ and 
+$O(\sd r^{2d} \sr \qe)$.
+Since $\norm{\ket{\psi_1}}^2 \appd{O(r \se)} 1/(d-1)$, we know $ \sqrt{d-1} \norm{\ket{\psi_1}} \appd{O(\sd \sr\qe)} 1$.
+
+To prove \cref{eq:phi2_result}, we first
+recall that 
+$\ket{\psi_1} 
+	=\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}.
+$
+The other observation that we need is that 
+\begin{align}
+	&\Phi_{A,2} \x \Phi_{B,2} (\ket{\psi_1})  \\
+	= &\frac{1}{16} \sum_{\ua \ub \in\{0,1\}^4}
+	M_{r+6}^{\ua(4)}N_{r+6}^{\ub(4)}M_{r+8}^{\ua(3)}N_{r+8}^{\ub(3)}M_{r+9}^{\ua(2)}N_{r+9}^{\ub(2)}M_{r+11}^{\ua(1)}N_{r+11}^{\ub(1)}
+	\ket{\psi_1} \ket{\ua}_{A''} \ket{\ub}_{B''}
+\end{align}
+For simplicity we define $M^{\ua} := M_{r+6}^{\ua(4)}M_{r+8}^{\ua(3)}M_{r+9}^{\ua(2)}M_{r+11}^{\ua(1)}$ and
+$N^{\ub} := N_{r+6}^{\ub(4)}N_{r+8}^{\ub(3)}N_{r+9}^{\ub(2)}N_{r+11}^{\ub(1)} $.
+We would like to show that 
+\begin{align}
+\label{eq:mua_comm}
+M^{\ua} \ket{\psi_1} \appd{O(r\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)
+M^{\ua} \ket{\psi},
+\end{align}
+for all $\ua \in \{0,1\}^4$,
+%which implies that 
+%\begin{align*}
+%	\Phi_{A,2} \x &\Phi_{B,2} (\ket{\psi_1}) \appd{O(r\se)} \\
+%	&\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)(\Phi_{A,2} \x \Phi_{B,2}(\ket{\psi}))
+%\end{align*}
+%because $N^{\ub}$ commutes with $\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$
+%for all $\ub \in \{0,1\}^4$.
+which can be justified by \cref{prop:rel_comm}.
+We show how to apply \cref{prop:rel_comm} to commute $M_{r+11}^{\ua(1)}$ through 
+$\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$ and then similar process can be repeated for $M_{r+9}, M_{r+8}$ and $M_{r+6}$,
+\begin{align*}
+	&\quad M_{r+11}^{\ua(1)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \\
+	&\appd{O(r\se)} \frac{1}{2}[ (M_{\nr+1}^0+M_{\nr+1}^1) M_{r+11}^{\ua(1)} -i M_{r+11}^{\ua(1)} M_{\nr+2}N_{\nr+1}] \ket{\psi} \\
+	&\appd{O(r\se)} \frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M_{r+11}^{\ua(1)} - iM_{\nr+2}M_{r+11}^{\ua(1)} N_{\nr+1}] \ket{\psi} \\
+	&\appd{O(r\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M_{r+11}^{\ua(1)} - iM_{\nr+2}M_{r+11}^{\ua(1)} M_{\nr+1}] \ket{\psi} \\
+	&\appd{O(r\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M_{r+11}^{\ua(1)} - iM_{\nr+2}M_{\nr+1}M_{r+11}^{\ua(1)} ] \ket{\psi}.
+\end{align*}
+In summary, we have 
+\begin{align}
+	M^{\ua} N^{\ub} \ket{\psi_1} \appd{O(r\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)M^{\ua}N^{\ub} \ket{\psi}
+\end{align}
+for all $\ua, \ub \in \{0,1\}^4$, which implies that 
+\begin{align}
+	\Phi_{A,2} \x& \Phi_{B,2}(\ket{\psi_1}) \appd{O(r\se)}\\
+	 &\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)(\Phi_{A,2}\x\Phi_{B,2} (\ket{\psi}).
+\end{align}
+At this point we can apply Lemma C.$1$ of \cite{wu2016} to $\Phi_{A,2}\x\Phi_{B,2} (\ket{\psi})$ and conclude that 
+\begin{align}
+	\Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \appd{O(\sd r \se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2},
+\end{align} 
+for some state $\ket{junk}$ whose norm can be deduced from the norm of $\ket{\psi_1}$.
+
+In the rest of the proof, we only show how $\Phi_{A,1} \x \Phi_{B,1}$ acts on $O_A\ket{\psi}$ and $U_A\ket{\psi}$.
+
+If the initial state is $O_A\ket{\psi}$, we first use the fact that 
+$ \Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi}) \appd{O(d^{5/4} r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi'})$, 
+and then we calculate $\Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi'})$ as
+\begin{align}
+	O_A \ket{\psi'} \ket{0}_{A'}\ket{0}_{B'} =&  
+		\sum_{j=1}^{d-1} O_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1}\ket{x_1}_{A'}\ket{x_1}_{B'}\\
+		\appd{O(\sd r^{d+1/2} \ep^{1/4})}&\sum_{j=1}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} \ket{\psi_1} \ket{x_1}_{A'}\ket{x_1}_{B'}\\
+		\xrightarrow[]{QFT_d} &\frac{1}{d}\sum_{j=1}^{d-1} \sum_{k_1,k_2 = 0}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} 
+		\ket{\psi_1}\ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\xrightarrow[]{\text{Controlled-}O_{A/B}}&\frac{1}{d}\sum_{j=1}^{d-1}\sum_{k_1,k_2 = 0}^{d-1} 
+		 O_A^{k_1}(U_A\ct)^{\log_r j} O_B^{k_2}(U_B\ct)^{\log_r j} \omega_d^{-j} \ket{\psi_1} 
+		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\appd{O(\sd r^{2d+1/2}  \ep^{1/4})}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}
+		\omega_d^{-j}\omega_d^{(k_2-k_1)j}\ket{\psi_1}
+		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\xrightarrow[]{QFT_d^{-1}}& \sum_{j=1}^{d-1}  (U_A\ct U_B\ct)^{\log_r j}  
+		\omega_d^{d-j}\ket{\psi_1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
+		\xrightarrow[]{\text{Controlled-}U_{A/B}}&   \sqrt{d-1} \ket{\psi_1} \x  
+		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
+\end{align}
+The analysis for $\Phi_{A,1} \x\Phi_{B,1} (O_B \ket{\psi})$ is very similar.
+
+If the initial state is $U_A\ket{\psi}$, we first use the fact that 
+$ \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi}) \appd{O(d^{5/4}r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi'})$, 
+and then we calculate $\Phi_{A,1} \x \Phi_{B,1} U_A\ket{\psi'})$.
+\begin{align}
+	U_A \ket{\psi'} \ket{0}_{A'}\ket{0}_{B'} =&  
+		\sum_{j=1}^{d-1} U_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1} \ket{x_1}_{A'}\ket{x_1}_{B'}\\
+		=&\sum_{j=1}^{d-1}(U_A\ct)^{\log_r j-1}  (U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_1}_{A'}\ket{x_1}_{B'}\\
+		\xrightarrow[]{QFT_d} &\frac{1}{d}\sum_{j=1}^{d-1} \sum_{k_1,k_2 = 0}^{d-1}(U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j} \ket{\psi_1}  \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\xrightarrow[]{\text{Controlled-}O_{A/B}}&\frac{1}{d}\sum_{j=1}^{d-1}\sum_{k_1,k_2 = 0}^{d-1} 
+		 O_A^{k_1}(U_A\ct)^{\log_r j-1} O_B^{k_2}(U_B\ct)^{\log_r j} \ket{\psi_1} 
+		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\appd{O(\sd r^{2d+1/2} \qe)}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}
+		\omega_d^{k_2j-k_1jr^{-1}}\ket{\psi_1}
+		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\xrightarrow[]{QFT_d^{-1}}& \sum_{j=1}^{d-1}  (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}  
+		\ket{\psi_1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'}\\
+		\xrightarrow[]{\text{Controlled-}U_{A/B}}& \sqrt{d-1} \ket{\psi_1} \x  
+		\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'},
+\end{align}
+where we use the fact that $(d-j)r^{-1} \equiv d -jr^{-1} \pmod{d}$.
+The analysis for $\Phi_{A,1} \x\Phi_{B,1} (U_B \ket{\psi})$ is very similar.
 \end{proof}
+
+%%-----------------------------------------------------------------
+%\subsection{Self-test}
+%%-----------------------------------------------------------------
+%\hl{This subsection needs to be formalized.}
+%We give a formal version of \cref{thm:pr_2} first and then prove it.
+%\begin{theorem}
+%\label{thm:selftest}
+%	If a quantum strategy using the shared state $\ket{\psi}$ achieves the ideal 2-party correlation $C(\dr{r})$ where $d$ is an odd
+%	prime number with primitive root $r \in \{2,3,5\}$, then there exist local isometries $\Phi_A$ and $\Phi_B$, and a state $\ket{junk}$ such 
+%	that $\Phi_A\x\Phi_B \ket{\psi} = \ket{\EPR{d-1}} \x \ket{junk}$.
+%\end{theorem}
+%\begin{proof}
+%Suppose Alice and Bob achieve the optimal correlation with the quantum strategy $(\ket{\psi}, \{A_x\}, \{B_y\})$
+%for all $x,y \in \calX \times \calY$ .
+%The observables $A_x$ and $B_y$ and the shared state $\ket{\psi}$ shall not be confused with the ones used in the optimal strategy.
+%By Lemma~$4.3$ of Ref.~\cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
+%of the linear system game $\LS_r$. 
+%For each variable $\{ x_i \}_{i=1}^{n_r}$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
+%The condition that they agree with assignment to variables means that 
+%\begin{align}
+%	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
+%	\text{ for } 1 \leq i \leq n_r
+%\end{align}
+%and the condition that Alice's assignments satisfy the constraint means that 
+%\begin{align}
+%	\Tr(\rho_A \Pi_{j: H(i,j) \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m_r
+%\end{align}
+%where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$. 
+%Similarly we define $\rho_B = \Tr_A(\ketbra{\psi}{\psi})$.
+%For any $\ket{v} \in \supp(\rho_A)$,
+%we have 
+%\begin{align}
+%\Pi_{j:H(i,j) \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m_r.
+%\end{align}
+%Since the relation $uxu^{-1} = x^r$, where $r$ is the primitive root of $d$, is embedded in this linear system game, we know
+%\begin{align}
+%	A_3A_4 A_1A_2 (A_3A_4)^\dagger \ket{v}= (A_1A_2)^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
+%\end{align}
+%For simplicity, we define $X_A = A_1A_2$ and $U_A=A_3A_4$ such that
+%the condition is equivalent to
+%\begin{align}
+%	\label{eq:ux_relation}
+%	U_AX_AU_A^\dagger \ket{v} = X_A^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
+%\end{align}
+%We will come back to the implication of this condition later.
+%
+%Suppose $A_{m_r+1} = A_\ast^\diamond- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
+%$2m$-dimensional vector space and $\Pi_{V_A}$ is the projector onto it. The reason why it has dimension $2m$
+%will be clear shortly. On Bob's side, we also have $B_{n_r+1} = B_\ast^\diamond- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
+%Recall that from the extended weighted CHSH test, we know
+%\begin{align}
+%	A_\ast^\diamond \ket{\psi} = B_\ast^\diamond \ket{\psi} = A_\ast^\diamond \x B_\ast^\diamond \ket{\psi},
+%\end{align}
+%which implies that with an appropriate change of basis, we can get $V_A = V_B$, so in the rest of the proof
+%we drop the subscript of $V$.
+%By \cref{lm:chsh_comp} and \cref{prop:2d-subspace}, we know $V$ consists of $\omega_d$-eigenvectors and $\omega_d^{-1}$ eigenvectors of 
+%$X_A$, so we can write 
+%\begin{align}
+%	\Pi_{V} = \Pi_{V_1} + \Pi_{V_{d-1}},
+%\end{align}
+%where $\Pi_{V_{1}}$ is the projector onto the $\omega_d$-eigenspace of $X_A$ and $\Pi_{V_{d-1}}$ is the projector 
+%onto the $\omega_d^{-1}$-eigenspace of $X_A$.
+%\hl{Here what we need is that $\Pi_{V_1,A} \ket{\psi} = \Pi_{V_{d-1},B} \ket{\psi} = \Pi_{V_1,A}\Pi_{V_{d-1},B}\ket{\psi}$
+%and $\Pi_{V_1,B} \ket{\psi} = \Pi_{V_{d-1},A} \ket{\psi} = \Pi_{V_1,B}\Pi_{V_{d-1},A}\ket{\psi}$.
+%This is not proved because $\Pi_{V_1}$ and $\Pi_{V_{d-1}}$ are not in the strategy.}
+%Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.
+%By \cref{eq:ux_relation} we can calculate that
+%\begin{align}
+%\label{eq:ladder}
+% X_AU_A^\dagger \ket{x_{1}} = U_A^\dagger X_A^r \ket{x_{1}} = \omega_d^r U_A^\dagger \ket{x_{1}},
+%\end{align}
+%so $U_A^\dagger \ket{x_{1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^r$.
+%By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{r^i} (U_A^\dagger)^i\ket{x_{1}}$. 
+%From the set $\{(U_A^\dagger)^i \Pi_{V_1} (U_A)^i \}_{i=0}^{d-2}$, we can identify $\Pi_{V_i}$ for $i = 1 \dots  d-1$
+%such that $\Pi_{V_i}$ is the projector onto the $\omega_d^i$-eigenspace of $X_A$,
+%\hl{Actually, we are not sure about the containment between $\supp((U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)})$ and 
+%$\supp(\Pi_{V_{d-1}})$, so we cannot say that $\Pi_{V_{d-1}} = (U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)}$.}
+%and 
+%\begin{align}
+% \cup_{i \in [d-1]+1} V_i \subset \supp(\rho_A).
+%\end{align}
+%Since unitary transformation does not change the rank of a matrix, we know $\rank(\Pi_{V_1}) = \rank(\Pi_{V_{i}}) =N$
+%for $ i =1 \dots d-1$.
+%We pick a basis for $V_1$ such that 
+%\begin{align}
+%	\Pi_{V_1} =  \sum_{j=1}^m \ketbra{x_{1,j}}{x_{1,j}},
+%\end{align}
+%then we can construct 
+%\begin{align}
+% \Pi_{V_i} = \sum_{j=1}^m \ketbra{x_{i,j}}{x_{i,j}},
+%\end{align}
+%where $\ket{x_{i,j}} = (U\ct)^{k_i} \ket{x_{1,j}}$ for $r^{k_i} \equiv i \pmod{d}$ and $1 \leq j \leq m$.
+%By \cref{eq:ux_relation} we also know that $U_A \ket{x_{i,j}} = \ket{x_{i/2,j}}$ for $i = 1,2 \dots d-1$.
+%In order to apply \cref{lm:ux_independ}, we construct $m$ subspaces $\{W_j\}_{j=1}^m$ where 
+%\begin{align}
+%	W_j = \spn( \{ \ket{x_{i,j}} \}_{i=1}^{d-1} )
+%\end{align}
+%The subspace $W_j$ is orthogonal to $W_{j'}$ for $j \neq j'$, and
+%$U_A$ and $X_A$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
+%restricted to each $W_j$.
+%Similar argument also applies to operator $X_B$ and $U_B$ on Bob's side.
+
+%With an appropriate change of basis, we 
+%assume that $\ket{\psi} = \vc(\tau)$ for some $\tau \in L(\supp(\rho_A))$
+%The consistency condition is equivalent to
+%\begin{align}
+%\label{eq:con_tau}
+%	A_i \tau B_i^\dagger = \tau.
+%\end{align}
+%Substituting $i=1,2$ into \cref{eq:con_tau}, we get 
+%\begin{align}
+%	X_A \tau X_A^\dagger = A_1A_2\tau B_2^\dagger B_1^\dagger = A_1\tau B_1^\dagger = \tau.
+%\end{align}
+%Similar argument gives us that 
+%\begin{align}
+%	U_A \tau U_A^\dagger = \tau.
+%\end{align}
+%Then we can conclude that for any $k \in \{0,1 \dots d-2\}$ and $l \in \{1,2\dots d-1\}$
+%\begin{align}
+%	U_A^kX_A^l \tau (U_A^kX_A^l)^\dagger = \tau.
+%\end{align}
+%Let $\Pi_{W_j}$ be the projector onto $W_j$. 
+%By \cref{lm:ux_independ}, $\Pi_{W_j} \tau \Pi_{W_j}$ commutes with all the $(d-1) \times (d-1)$ matrices, which means that 
+%\begin{align}
+%	\label{eq:d-1}
+%	\Pi_{W_j} \tau \Pi_{W_j}  = c_j \1_{W_j} \text{ for } j = 1\dots m.
+%\end{align}
+%In the vector form, we know
+%\begin{align}
+%	\sum_{j =1}^N \Pi_{W_j} \ket{\psi} =\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}. 
+%\end{align}
+%Recalling the fact that 
+%\begin{align}
+%\norm{ \Pi_{V_1} + \Pi_{V_{d-1}} \ket{\psi}}^2 = \norm{\Pi_{V_1} \ket{\psi}}^2 + \norm{\Pi_{V_{d-1}} \ket{\psi}}^2 = \frac{2}{d-1},
+% \end{align}
+% it means that 
+% \begin{align}
+% 	2 \sum_{j=1}^m \norm{c_j}^2 = \frac{2}{d-1}.
+% \end{align}
+% Then we can calculate the norm of $\sum_{j =1}^m \Pi_{W_j} \ket{\psi}$, which is
+% \begin{align}
+% \norm{\sum_{j =1}^m \Pi_{W_j} \ket{\psi}}^2 = \sum_{i=1}^{d-1} \sum_{j=1}^m \norm{c_j}^2 = 1 = \norm{\ket{\psi}}^2.
+% \end{align}
+% We can conclude that $\supp{\rho_A} = \cup_{i=1}^{d-1} V_i$ and 
+% \begin{align}
+% 	\ket{\psi} = \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}.
+% \end{align}
+% 
+%The last step is to construct the local isometries $\Phi_A$ and $\Phi_B$ that can produce $\ket{\EPR{d-1}}$ from $\ket{\psi}$.
+%To help understanding, we draw a diagram to demonstrate the isometry first and then show
+%how this isometry works.
+%\begin{figure}[H]
+%\center
+%        \begin{tikzpicture}[thick]
+%        %
+%        % `operator' will only be used by Hadamard (H) gates here.
+%        % `phase' is used for controlled phase gates (dots).
+%        % `surround' is used for the background box.
+%        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
+%        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
+%        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
+%        %
+%        % Bracket
+%        \draw[decorate,decoration={brace,mirror},thick] (0,-1) to
+%    	node[midway,left] (bracket1) {$\ket{\psi}$}
+%    	(0,-2);
+%        % Qubits
+%        \node at (0,0) (q1) {$\ket{0}$};
+%        \node at (0,-1) (q2) {};
+%        \node at (0,-2) (q3) {};
+%        \node at (0,-3) (q4) {$\ket{0}$};
+%        %
+%        % Column 1
+%        \node[operator] (op11) at (1,0) {$QFT_d$} edge [-] (q1);
+%        \node[operator] (op14) at (1,-3) {$QFT_d$} edge [-] (q4);
+%        %
+%        % Column 3
+%        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
+%	\node[operator] (op22) at (2,-1) {$X_A$} edge [-] (q2);
+%	\node[operator] (op23) at (2, -2) {$X_B$} edge[-] (q3);
+%        \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
+%        \draw[-] (phase11) -- (op22);
+%        \draw[-] (phase14) -- (op23);
+%        %
+%        % Column 4
+%        \node[operator] (op31) at (3,0) {$QFT_d^{-1}$} edge [-] (phase11);
+%        \node[operator] (op34) at (3,-3) {$QFT_d^{-1}$} edge [-] (phase14);
+%        %
+%        % Column 5
+%        \node[phase] (phase21) at (4,0) {} edge [-] (op31);
+%	\node[operator] (op42) at (4,-1) {$U_A$} edge [-] (op22);
+%	\node[operator] (op43) at (4, -2) {$U_B$} edge[-] (op23);
+%        \node[phase] (phase24) at (4,-3) {} edge [-] (op34);
+%        \draw[-] (phase21) -- (op42);
+%        \draw[-] (phase24) -- (op43);
+%        %
+%        % Column 6
+%        \node (end2) at (5,-1) {} edge [-] (op42);
+%        \node (end3) at (5,-2) {} edge [-] (op43);
+%        %
+%        % Bracket
+%        \draw[decorate,decoration={brace},thick] (5,-1) to
+%    	node[midway,right] (bracket) {$\ket{junk}$}
+%    	(5,-2);
+%        %
+%        % Column 7
+%        \node (end1) at (6.5,-0.5) {} edge [-] (phase21);
+%        \node (end4) at (6.5,-2.5) {} edge [-] (phase24);
+%        % Dashed line
+%        \draw[loosely dotted] (0,-1.5) -- (5,-1.5);
+%        % Bracket
+%        \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
+%    	node[midway,right] (bracket2) {$\ket{\EPR{d-1}}$}
+%    	(6.5,-2.5);
+%        %
+%        % Background Box
+%        \begin{pgfonlayer}{background} 
+%        \node[surround] (background) [fit = (q1) (op14) (bracket1)(bracket2)] {};
+%        \end{pgfonlayer}
+%        %
+%        \end{tikzpicture}
+%	\caption{The isometries $\Phi_A$ and $\Phi_B$.}
+%\end{figure}
+%The isometry maps the state $\ket{\psi}$ in the following steps:
+%\begin{enumerate}
+%	\item Append $\ket{0}_A$ on Alice's side and $\ket{0}_B$ on Bob's side as control registers, and
+%	the state becomes $\ket{\psi} \ket{0}_A \ket{0}_B$;
+%	\item Apply $QFT_d$ to the control registers, and the state becomes
+%	\begin{align}
+%		\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \ket{\psi} \ket{k_1}_A \ket{k_2}_B;
+%	\end{align}
+%	\item Apply $X_A^{k_1}$ to Alice's share of $\ket{\psi}$ and $X_B^{k_2}$ to Bob's share controlled
+%	by the control registers, and the state becomes
+%	\begin{align}
+%		&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1}X_A^{k_1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B\\
+%		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1}\ket{x_{i,j}}_A X_B^{k_2}\ket{x_{i,j}}_B
+%		\ket{k_1}_A \ket{k_2}_B\\
+%		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1i+k_2i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
+%		\ket{k_1}_A \ket{k_2}_B;
+%	\end{align}
+%	\item Apply $QFT_d^{-1}$ to the control registers, and the state becomes
+%	\begin{align}
+%		&\frac{1}{d^2} \sum_{l_1,l_2 =0}^{d-1}\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i-l_1)+k_2(i-l_2)} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
+%		\ket{l_1}_A \ket{l_2}_B\\
+%		=& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B;
+%	\end{align}
+%	\item Let $n_i$ satisfy the condition $r^{n_i} \equiv i \pmod{d}$, apply $U_A^{(i)} = U_A^{n_i}$ to Alice's share of $\ket{\psi}$ and $U_B^{(i)} = U_B^{n_i}$ to Bob's share controlled
+%	by the control registers, and the state becomes
+%	\begin{align}
+%		&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B \\
+%		=&\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i r^{-n_i} ,j}}_A \ket{x_{i r^{-n_i},j}}_B \ket{i}_A\ket{i}_B\\
+%		=& \sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i i^{-1},j}}_A \ket{x_{i i^{-1},j}}_B \ket{i}_A\ket{i}_B\\
+%		= &\left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \sum_{i=1}^{d-1} \ket{i}_A\ket{i}_B\\
+%		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
+%		\frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1}\ket{i}_A\ket{i}_B\\
+%		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \ket{\EPR{d-1}},
+%	\end{align}
+%	where in the last line we used the fact that $\norm{\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B} = 1/\sqrt{d-1}$.
+%\end{enumerate}
+%
+%If the initial state is $X_A\ket{\psi}$, the isometry maps the state as following
+%\begin{align}
+%	X_A\ket{\psi} \to &X_A\ket{\psi}\ket{0}_A\ket{0}_B\\
+%	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
+%	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A^{k_1+1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
+%	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1+k_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
+%		\ket{k_1}_A \ket{k_2}_B\\
+%	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1-l_1)i+(k_2-l_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
+%		\ket{l_1}_A \ket{l_2}_B\\
+%	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B\\
+%	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
+%	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{i}_A\ket{i}_B\\
+%	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
+%		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\omega_d^i \ket{i}_A\ket{i}_B\\
+%	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tX_A \ket{\EPR{d-1}},
+%\end{align}
+%where $\tX_A$ is the ideal $X$ operator.
+%The case of $X_B\ket{\psi}$ is similar, so we omit it here. 
+%
+%If the initial state is $U_A\ket{\psi}$, the isometry maps the state as following
+%\begin{align}
+%	U_A\ket{\psi} \to &U_A\ket{\psi}\ket{0}_A\ket{0}_B\\
+%	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} U_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
+%	= &\frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A\ket{x_{i,j}}_A\ket{x_{i,j}}_B
+%		\ket{k_1}_A \ket{k_2}_B\\
+%	= & \frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i r^{-1} ,j}}_A\ket{x_{i,j}}_B
+%		\ket{k_1}_A \ket{k_2}_B\\
+%	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1} \ket{x_{i r^{-1} ,j}}_A
+%	X_B^{k_2}\ket{x_{i,j}}_B  \ket{k_1}_A \ket{k_2}_B \\
+%	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1 i/r}\omega_d^{k_2i} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
+%		\ket{k_1}_A \ket{k_2}_B\\
+%	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i/r-l_1)}\omega_d^{(k_2(i-l_2)} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
+%		\ket{l_1}_A \ket{l_2}_B\\
+%	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j  \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B \ket{ir^{-1}}_A \ket{i}_B\\
+%	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(ir^{-1})}\ket{x_{ir^{-1},j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
+%	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{ir^{-1}}_A\ket{i}_B\\
+%	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
+%		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\ket{ir^{-1}}_A\ket{i}_B\\
+%	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tU_A \ket{\EPR{d-1}},
+%\end{align}
+%where $\tU_A$ is the ideal $U$ operator on Alice's side.
+%The derivation is similar when $U_B$ is applied, so we omit it here.
+%\end{proof}
 %The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
@@
 %\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
-In summary, for any odd prime number $d$ whose primitive root is $2$,$3$ or $5$, 
-\cref{prop:realize} tells us that the correlation $C(d)$ is achievable by a quantum strategy 
-and \cref{thm:selftest} tells us that the correlation $C(d)$ can self-test the EPR pair of
-local dimension $d-1$. Moreover, there are infinitely many prime numbers
-whose primitive root is in the set $\{2,3,5\}$ \cite{murty1988},
-Hence, our main result is the following theorem.
-\begin{theorem}
-	There exists an infinity-sized set $D$ of prime numbers such that 
-	each $d \in D$ has primitive root $2$, $3$ or $5$ and there exists
-	a constant-sized correlation $C(d)$ that can self-test the EPR pair of 
-	local dimension $d-1$.
-\end{theorem}
-We remark that our proof works for any odd prime number with primitive root $r$.
-However, since there is no upper-bound of $r$ for a general prime number $d$, we 
-cannot claim the corresponding correlation $C(d)$ is constant-sized. On the other
-hand, since $r$ is usually much smaller than $d$, our result implies a more efficient
-way to test EPR pairs of prime local dimension than the one proposed in Ref.~\cite{cgs2017}.
-The size of our correlation grows linearly in $r$ whereas the Coladangelo \textit{et. al.}'s
-method uses correlation grows linearly in $d$.
+
+%We remark that our proof works for any odd prime number with primitive root $r$.
+%However, since there is no upper-bound of $r$ for a general prime number $d$, we 
+%cannot claim the corresponding correlation $C(d)$ is constant-sized. On the other
+%hand, since $r$ is usually much smaller than $d$, our result implies a more efficient
+%way to test EPR pairs of prime local dimension than the one proposed in Ref.~\cite{cgs2017}.
+%The size of our correlation grows linearly in $r$ whereas the Coladangelo \textit{et. al.}'s
+%method uses correlation grows linearly in $d$.
 

### 2019-04-29 Draft/draft.tex
Added comments to section 2 of the draft

@@
 The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
-We denote a Hilbert space by $\calH$. Note that we only work with finite Hilbert spaces in this work.
+We denote a Hilbert space by $\calH$.  \carl{That last sentence is too vague.  Does $\calH$ refer to a specific Hilbert space?}
+Note that we only work with finite Hilbert spaces in this work.
 When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
@@
 in the multiplicative group of integers modulo $d$, $\Zd$.
+\carl{I'm skeptical about whether that's the standard definition.
+(For example, the definition on wikipedia doesn't include that ``smallest integer'' part.)}
 \end{definition}
@@
 $(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
-\carl{You need to put explicit labels on the quantum systems used by
-Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
-the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
-\hf{Addressed in the notation part. --H.F}
 Then Alice and Bob's quantum strategy produces the conditional probability distribution
@@
 \end{align}
+\carl{Check the use of notation above (``$A$'', ``$B$'').}
 \begin{definition}
@@
 \end{definition}
-\carl{Make this clear in the definition itself.}
-\hf{I made the definition of the scoring function part of the big definition now.}
 In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
@@
 \begin{enumerate}
-	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
+	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;  \carl{``finite-dimensional''?}
 	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
-	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
+	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;  \carl{You're using ``$A$,$B$'' here still.}
 	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
@@
 converted to a quantum strategy presented in terms of projective measurement by looking into
-the spectral decompositions of the observables.
+the spectral decompositions of the observables.  \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}
 
@@
 the finite-dimensional representation of a finitely presented group
-over $\Z_2$, which is called the solution group.
+over $\Z_2$, which is called the solution group.  \carl{The phrase ``the finite-dimensional
+representation'' is confusing -- it sound like you are implying that there is only one representation.}
 \begin{definition}[Solution group of a linear system game]
@@
 We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
-Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
-the linear system game ($H\ux = \uc$) has
+Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a perfect strategy for 
+the linear system game ($H\ux = \uc$) has \carl{Replace ``has'' with ``is given by''.}
 \begin{enumerate}
 	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
-	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$,
+	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
 	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
 \end{enumerate}
-We follow a similar approach to construct our ideal strategy. However, our strategy uses a different maximally entangled state,
+We follow a similar approach to construct our ideal strategy.
+\carl{I don't think the reader will know what ``ideal strategy'' refers to at this point.}.
+However, our strategy uses a different maximally entangled state,
 so we justify our strategy more carefully.
 For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
-For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.
+For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.  \carl{These last two sentences seem out of place -- consider rephrasing and relocating.}
 
@@
 \end{align}
+\carl{What is the input distribution?}
 Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
@@
 \end{align}
-where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of of the observables. 
+where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of the observables. 
 The weighted CHSH inequality is true 
-If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
-However, If they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
+if Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
+However, if they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
 \begin{align}
@@
 \end{align}
+\carl{You need to cite the results that you're summarizing here (or refer to an appendix).}
 \begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
@@
 
-\carl{Before the next definition, you should define what a ``correlation'' is.}
-\hf{Done. I decided to remove the definition of self-testing here because I think it is hard
-to give a general robust self-testing definition and it suffices to just give our robust self-testing result.}
-
-\carl{Section 2 needs to be cleaned up in some places, but overall it is pretty good.}
-
 %-----------------------------------------------------------
@@
 	\end{align}	
+	\carl{Check the grammar in this proposition.}
 \end{proposition}
@@
 \end{proof}
+\carl{Question: Do we actually need the assumption that $v,v'$ have length less than $1$?}
 \begin{proposition}
@@
 \end{proposition}
+\carl{Fix the grammar in the proposition above.}
 \begin{proof}
@@
 \begin{proposition}
-	Let $\ket{u}$ be a vector with length less or equal to $1$ such that for a unitary $U$,
+	Let $\ket{u}$ be a vector with length less than or equal to $1$ such that for a unitary $U$,
 	\begin{align}

### 2019-05-01 Draft/draft.tex
Honghao: updated section 2

@@
 
+\newcommand{\fC}{\mathfrak{C}}
+
 % Probabilities
@@
 \newcommand{\hf}[1]{\textcolor{red}{#1}}
+\newcommand{\hfc}[1]{\textcolor{red}{#1 -H.F.}}
 
@@
 
-\title{Robust self-testing of large entanglement with constant-sized correlations}
+\title{Constant-sized correlations are sufficient for 
+robust self-testing of maximally entangled states with unbounded dimension}
 
@@
 Self-testing general $d$-dimensional EPR pairs is a harder task.
-Recently, a remarkable result by Coladangelo \textit{et al}.\cite{cgs2017} 
-has shown that the maximally entangled state with arbitrary local dimension 
-can be self-tested with constant question alphabet but answer alphabet growing with
-the local dimension. 
-Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
-of the generalized Magic Square game and Magic Pentagram game, one can robustly self-test
-$N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
-Both the Magic Square game and the Magic Pentagram game have constant question alphabet
-but answer alphabet of size $d$.
+Proving robustness is harder.
 
@@
 The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
-We denote a Hilbert space by $\calH$.  \carl{That last sentence is too vague.  Does $\calH$ refer to a specific Hilbert space?}
+Usually, we denote a \hf{general} Hilbert space by $\calH$.  
+\carl{That last sentence is too vague.  Does $\calH$ refer to a specific Hilbert space?}
+\hfc{How about now?}
 Note that we only work with finite Hilbert spaces in this work.
@@
 A primitive root of a prime number
-$d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
+$d$ is \hf{an integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
 in the multiplicative group of integers modulo $d$, $\Zd$.
@@
 (For example, the definition on wikipedia doesn't include that ``smallest integer'' part.)}
+\hfc{How about now?}
 \end{definition}
@@
 $r$ is the generator of $\Zd$.
+\hf{In our work, we always pick $r$ to be the smallest primitive root of $d$.}
 
@@
 comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
-and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. 
-Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
-pair to $\{0,1\}$ which corresponds to losing and winning. 
+and $V: \calA \times \calB \times \calX \times \calY \rightarrow \{0,1\}$, which is the scoring function. 
+The score $0$ and $1$ correspond to losing and winning. 
 Such games are nonlocal
 because Alice and Bob cannot communicate after getting their questions but they may share some strategy beforehand.
+
+\hf{In our work, we consider a special case of nonlocal games, which we call a nonlocal test.
+There are three differences between a nonlocal game and a nonlocal test:
+\begin{itemize}
+	\item only a subset of all the question pairs are given to Alice and Bob;
+	\item the answer sets for different questions are different;
+	\item the scoring function maps input-output pairs to real numbers $(\R)$.
+\end{itemize}
+}
 
@@
 \begin{align}
-	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
-\end{align}
-\carl{Check the use of notation above (``$A$'', ``$B$'').}
+	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
+\end{align}
+\hf{For simplicity we omit the tensor product between operators acting on different Hilbert spaces in the rest of the work.}
+
 \begin{definition}
@@
 \end{definition}
-In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
+In the rest of the paper, we will work with quantum strategies for the linear system game presented in terms of binary observables.
 \begin{definition}[Quantum strategy of a linear system game]
@@
 \begin{enumerate}
-	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;  \carl{``finite-dimensional''?}
-	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
-	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;  \carl{You're using ``$A$,$B$'' here still.}
-	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
+	\item a pair of finite-dimensional Hilbert spaces $\calH_A$ and $\calH_B$; 
+	\item a collection of binary observables $N_j$, $1 \leq j \leq n$, on $\calH_B$
+	such that $N_j^2 = \1$ for every $1 \leq j \leq n$; 
+	\item a collection of binary observables $M_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
 	on $\calH_A$ such that 
 	\begin{enumerate}
-		\item $A_{ij}^2 = \1$ for every $i,j$,
-		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
-		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
+		\item $M_{ij}^2 = \1$ for every $i,j$,
+		\item $\Pi_j M_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
+		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
 	\end{enumerate} 
@@
 converted to a quantum strategy presented in terms of projective measurement by looking into
-the spectral decompositions of the observables.  \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}
+the spectral decompositions of the observables. 
+\hf{More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
+implies that they share a common eigenspace. The collection of eigenvalues associated with one eigenstate is the assignment
+to the whole equation when this eigenstate is measured in a projective measurement strategy.}
+ \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}
 
@@
 A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
-the finite-dimensional representation of a finitely presented group
-over $\Z_2$, which is called the solution group.  \carl{The phrase ``the finite-dimensional
+\hf{a} finite-dimensional representation of a finitely presented group
+over $\Z_2$, which is called the solution group.  
+\hf{Here we skip the background about group representations and presentations.
+For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
+For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}. }
+\carl{The phrase ``the finite-dimensional
 representation'' is confusing -- it sound like you are implying that there is only one representation.}
@@
 We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
-Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a perfect strategy for 
-the linear system game ($H\ux = \uc$) has \carl{Replace ``has'' with ``is given by''.}
+\hf{In later parts of this work, we give the solution group instead of the set of linear equations when we defines
+a linear system game.}
+
+Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$, then a perfect strategy for 
+the linear system game ($H\ux = \uc$) is given by 
 \begin{enumerate}
-	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
-	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
+	\item $M_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
+	\item $N_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
+	\hf{I don't think we need to take transpose because these are binary observables. -HF}
 	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
 \end{enumerate}
-We follow a similar approach to construct our ideal strategy.
-\carl{I don't think the reader will know what ``ideal strategy'' refers to at this point.}.
+\hf{Later we will use this approach to construct a strategy for a linear system game.}
+\carl{I don't think the reader will know what ``ideal strategy'' refers to at this point.}
+\hfc{How about now?}
 However, our strategy uses a different maximally entangled state,
 so we justify our strategy more carefully.
-For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
-For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.  \carl{These last two sentences seem out of place -- consider rephrasing and relocating.}
 
@@
 %-------------------------------------------------------------------------------
-The weighted CHSH inequality is extracted from the CHSH test, which is another nonlocal game. 
+\hf{The weighted CHSH inequality a variation of the CHSH inequality \cite{chsh}. 
+We formulate it as a nonlocal test.}
 The input sets and output sets of Alice and Bob are
 $\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
-The scoring function for the $\alpha$-weighted CHSH test is defined by
+The scoring function for the $\alpha$-weighted CHSH test, for $|\alpha|\geq 1$,  is defined by
 \begin{align}
@@
 \end{align}
-\carl{What is the input distribution?}
+The input distribution is $\pi(x,y) = 1/4$ for all $(x,y) \in \calX \times \calY$.
 Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
@@
 	\label{eq:chsh_op}
-	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2\alpha,
+	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
 \end{align}
@@
 However, if they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
-\begin{align}
-\label{eq:chsh_max}
- \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
-\end{align}
+$ \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}$ \cite{acin2012}.
 \carl{You need to cite the results that you're summarizing here (or refer to an appendix).}
-\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
+\hfc{I cited the paper in the title of this subsection. Maybe I add a sentence saying that this subsection
+summarizes results in \cite{acin2012}?}
+\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$ \cite{acin2012}]
 	\label{def:ideal}
@@
 We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.
+\hf{In \cref{sec:full_test} we design
+a nonlocal test call the extended weighted CHSH test based on the weighted CHSH inequality.}
 
@@
 	\label{prop:inner_pd}
-	Let $\ket{v}$ and $\ket{v'}$ be vectors with length less than equal to $1$ satisfying the relation that $\ket{v} \appd{\epsilon} \ket{v'}$
+	Let $\ket{v}$ and $\ket{v'}$ be vectors such that the relation $\ket{v} \appd{\epsilon} \ket{v'}$ holds,
 	then for any unit vector $\ket{u}$,
-	\begin{align}
+	\begin{align*}
 		 \braket{v}{u} \appd{\ep} \braket{v'}{u} .
-	\end{align}	
+	\end{align*}	
 	\carl{Check the grammar in this proposition.}
@@
 	then
-	\begin{align}
+	\begin{align*}
 	\norm{ \braket{v}{u} - \braket{v'}{u} } = \norm{\braket{v''}{u}} \leq \norm{\ket{u}}\norm{\ket{v''}} \leq \epsilon.
-	\end{align}
+	\end{align*}
 \end{proof}
 \carl{Question: Do we actually need the assumption that $v,v'$ have length less than $1$?}
+\hfc{You are right. We don't.}
 \begin{proposition}
-	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with length less than equal to $1$
+	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with norm less than equal to $1$
 	such that 
-	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$
+	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$,
 	then 
-	\begin{align}
+	\begin{align*}
 		\braket{u_1}{u_2} \appd{\ep_1+ \ep_2} \braket{v_1}{v_2}.
-	\end{align}
+	\end{align*}
 \end{proposition}
@@
 	By direct calculation we have
-	\begin{align}
+	\begin{align*}
 		\norm{ \braket{u_1}{u_2} - \braket{v_1}{v_2}} \leq &\norm{\braket{u_1}{u_2} - \braket{v_1}{u_2}}
@@
 		\leq & \ep_1 + \ep_2,
-	\end{align}
+	\end{align*}
 	where we used \cref{prop:inner_pd}.
@@
 \label{prop:orthog}
-	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with length less or equal to $1$,
-	which satisfy the condition that 
-	\begin{align}
-		H\ket{u} \appd{\ep_1} a \ket{u}, \\
+	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with norm less or equal to $1$
+	such that
+	\begin{align*}
+		H\ket{u} \appd{\ep_1} a \ket{u} &&
 		H\ket{v} \appd{\ep_2} b \ket{v}, 
-	\end{align}
+	\end{align*}
 	for some $a > b \in \R$, then
-	\begin{align}
+	\begin{align*}
 		\norm{\braket{u}{v}} \leq \frac{\ep_1+\ep_2}{a-b}.
-	\end{align}
+	\end{align*}
 \end{proposition}
@@
 	Then, we know
-	\begin{align}
+	\begin{align*}
 		\bra{v}H\ket{u} = a\braket{v}{u} + \braket{v}{u'},\\
 		\bra{v}H\ket{u}  =b\braket{v}{u} + \braket{v'}{u},
-	\end{align}
+	\end{align*}
 	Subtracting the second equation from the first equation gives us that 
-	\begin{align}
+	\begin{align*}
 		\norm{\braket{v}{u}} = \frac{\norm{\braket{v'}{u} -  \braket{v}{u'}}}{a-b} \leq \frac{\norm{\ket{v}}\norm{\ket{u'}}+
@@
 		\leq \frac{\ep_1+\ep_2}{a-b}.
-	\end{align}
+	\end{align*}
 \end{proof}
@@
 \label{prop:close_vec}
-	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$ and
-	$\norm{\ket{v}} \appd{\ep_2} 1$ , if $\braket{u}{v} \geq 1 - \ep_3$,
+	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$,
+	$\norm{\ket{v}} \appd{\ep_2} 1$, and $\braket{u}{v} \geq 1 - \ep_3$,
 	then
-	\begin{align}
+	\begin{align*}
 		\ket{u} \appd{O(\sqrt{\ep_1+\ep_2+\ep_3})} \ket{v}.
-	\end{align}
+	\end{align*}
 \end{proposition}
@@
 	Direct calculation gives us that
-	\begin{align}
+	\begin{align*}
 		\norm{\ket{u} - \ket{v}}^2 &= \norm{\ket{u}}^2 + \norm{\ket{v}}^2 - 2\braket{u}{v} \\
@@
 		& = O(\ep_1+\ep_2+\ep_3).
-	\end{align}
+	\end{align*}
 \end{proof}
 \begin{proposition}
-	Let $\ket{u}$ be a vector with length less than or equal to $1$ such that for a unitary $U$,
-	\begin{align}
+	Let $\ket{u}$ be a vector with norm less than or equal to $1$ such that for a unitary $U$,
+	\begin{align*}
 		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C,
-	\end{align}
+	\end{align*}
 	then
-	\begin{align}
+	\begin{align*}
 		U^n \ket{u} \appd{n\ep} a^n \ket{u} \text{ for all } n \geq 1.
-	\end{align}
+	\end{align*}
 \end{proposition}
@@
 	We can prove it by induction. 
-	For $n=1$, the statement is satisfied.
-	Assume it holds for $n = k-1$ and consider $n = k$, then we have
-	\begin{align}
-		&\norm{U^k \ket{u} - a^k\ket{u}} \\
-		\leq &\norm{U} \norm{U^{k-1} \ket{\psi} - a^{k-1}\ket{\psi}} + \norm{a^{k-1}}
+	For $k=1$, the statement is satisfied.
+	Assume it holds for $k = n-1$ and consider $k = n$, then we have
+	\begin{align*}
+		&\norm{U^n \ket{u} - a^n\ket{u}} \\
+		\leq &\norm{U} \norm{U^{n-1} \ket{\psi} - a^{n-1}\ket{\psi}} + \norm{a^{n-1}}
 		\norm{U\ket{\psi} - a \ket{\psi}}\\
-		\leq &(k-1)\ep + \ep = k \ep,
-	\end{align}
+		\leq &(n-1)\ep + \ep = n \ep,
+	\end{align*}
 	where we used the fact that $\norm{U} = 1$ and $\norm{a} \leq 1$.
@@
 %=======================================
-\section{The linear constraint test}
-\label{sec:lct}
+\section{The linear system game}
+\label{sec:lsg}
 %=======================================
@@
 The formal statement is given in the theorem below. Since the proof uses the same technique as the one used in Ref.~\cite{bamps2015},
-we defer the proof till \cref{sec:selftest}. Instead, we only list the key relations used in the proof because they will be reused in the later parts of 
-the paper.
+we defer the proof till \cref{sec:selftest}. Instead, we only list the key relations used in the proof because they will be reused in 
+\cref{sec:main} where we prove our robust self-testing result.
 \begin{theorem}
@@
 The full correlation is generated by the ideal strategy presented in the previous subsection.
-To help readers understanding later parts of this paper better, 
+To help readers understanding the proofs in \cref{sec:main} of this paper better, 
 parts of the full correlation is given in the tables below.

### 2019-05-01 Draft/draft.tex
Honghao: edits of section 3

@@
 \end{definition}
+\hf{A widely-used example of linear system games is the Magic Square game introduced in Ref.~\cite{magic_square}.
+For the formulation of the Magic Square game as a linear system game
+and the general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.}
+
 In the rest of the paper, we will work with quantum strategies for the linear system game presented in terms of binary observables.
@@
 %=======================================
-In this section, we introduce a linear constraint test that is satisfied by our correlation.
-The linear constraint test is designed to enforce relations that should be satisfied by 
-Alice and Bob's observables and it is inspired by 
+In this section, we introduce a linear system game which is a component of the full test.
+This game is designed to enforce relations that should be satisfied by 
+Alice and Bob's observables. The inspiration comes from 
 Slofstra's seminal work~\cite{slofstra2017}, in which he
@@
 into a linear system game such that the relations in the definition of $K$ can be derived from the
-combination of the equations of the linear system game. Then he showed the difference between exact representations
+combination of the linear equations. Then he showed the difference between exact representations
 and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
 \hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
-following group}
-\begin{align}
-	G = \langle u, o : uou^{-1} = o^r \rangle, 
-\end{align}
-for some $r \in \N$ into a linear constraint test.
+following relation
+$
+uou^{-1} = o^r 
+$
+for some $r \in \N$ into a linear system game.}
 
@@
 \begin{theorem}
-	The relation $uou^{-1} = o^r$ can be embedded in a linear constraint test which has
-	$n(r) := 18r+86$ variables and $m(r) := 16r + 72$ equations, where each equation has $3$ variables.
+	The relation $uou^{-1} = o^r$ can be embedded in a linear system game which has
+	$n(r) := 18r+85$ variables and $m(r) := 17r + 77$ equations, where each equation has $3$ variables.
 \end{theorem}
-We prove this by constructing the solution group $\Gamma$ of the linear constraint test. 
+We prove this by constructing the solution group $\Gamma$ of the linear system game. 
 We also prove some properties of the generators of $\Gamma$ along the way.
 
-We embed $G$ into $\Gamma$ in three steps and introduce two intermediate groups $G_0$ and $G_1$, which are defined below.
+We embed $uou^{-1}= o^r$ into $\Gamma$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
 \begin{definition}	
+\label{def:g0}
 	The presentation of $G_0$ has order-$2$ generators:
-	\begin{align}
+	\begin{align*}
 		\{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5
-	\end{align}
+	\end{align*}
 	and relations:
-	\begin{align}
+	\begin{align*}
 	&u_3 = u_2o_1u_2 && u_4 = u_2o_2u_2 \\
@@
 	&u_5 = o_1 o_r o_1,
-	\end{align}
+	\end{align*}
 	and when $r$ is even
-	\begin{align}
+	\begin{align*}
 	&o_{1+2j} = o_1o_{2j}o_1 && o_{2+2j} = o_2o_{1+2j}o_2&& \text{ for } j = 1 \dots r/2 - 1;
-	\end{align}
+	\end{align*}
 	when $r$ is odd
-	\begin{align}
+	\begin{align*}
 	&o_3 = o_2o_1o_2 &&
 	 o_{2+2j} =o_1o_{1+2j}o_1 && o_{3+2j} = o_2o_{2j+2}o_2 &&\text{ for } j = 1 \dots (r-3)/2.
-	\end{align}
+	\end{align*}
 \end{definition}
 \begin{proposition}
-	The group $G_1$ embeds the relation 
+	The group $G_0$ embeds the relation 
 	\begin{align}
@@
 	Direct calculation gives us that
-	\begin{align} 
+	\begin{align*} 
 		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
@@
 	=& o_1o_ro_1 o_2.
-	\end{align}
-	Then substituting the definitions of $o_k$ for $k = r \dots 3$ gives us the case for $j=1$.
-
-	Now assume the statement is true for $j = n$, then when $j = n+1$
-	\begin{align}
+	\end{align*}
+	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above and
+	proves the $j=1$ case.
+
+	Now assume the statement is true for $j = n$, then for $j = n+1$
+	\begin{align*}
 		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
@@
 		 =& (o_1o_2)^{r^{n+1}},
-	\end{align}
-	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$ and $o_1o_2$.
+	\end{align*}
+	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$.
 	Hence, the statement is true.
 \end{proof}
-To better characterize all the conjugation relations above and simplify the form of $G_1$
-and make the introduction of $G_2$ easier, we relabel $u_i$ and $o_i$'s
+To better characterize all the conjugation relations above and simplify the form of $G_1$ defined below, 
+we relabel $u_i$ and $o_i$'s
 as $a_i$'s such that
@@
 Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
-\begin{align}
+\begin{align*}
 	(i,j,k) \in C(r) \iff a_ia_ja_i = a_k.
-\end{align}
+\end{align*}
 The size of $C(r)$ is $r+3$. 
@@
 In this way, the group $G_0$ can be presented by
-\begin{align}
+$
 G_0  = \ip{ \{a_i\}_{i=1}^{r+5} : C(r) }.
-\end{align}
-
+$
 Then we define the group $G_1$.
@@
 	We first show that $d_i c_j d_i = b_k$, which is because
-	\begin{align}
+	\begin{align*}
 		d_i c_j d_i = d_i (f b_j f) d_i = f (d_i b_j d_i) f = f c_k f = b_k.
-	\end{align}
+	\end{align*}
 	Then, we can prove that 
-	\begin{align}
+	\begin{align*}
 		a_i a_j a_i = f d_i b_j c_j f d_i = (f d_i b_j d_i f)(f d_i c_j d_i f) = (f c_k f)(f b_k f) = b_k c_k = a_k. 
-	\end{align}
+	\end{align*}
 \end{proof}
@@
 	We can check that
-	\begin{align}
+	\begin{align*}
 		fa_i f a_i = d_i d_i = e && g a_i g a_i = v_i v_i  = e,
-	\end{align}
+	\end{align*}
 	for all $i = 1 \dots r+5$.
@@
 	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
-	\{\{ k_{c,j} \}_{j=1}^6\}_{c \in C(r)},
+	\{\{ k_{l,j} \}_{j=1}^6\}_{l \in C(r)},
 \end{align*}
@@
 \item for all $i = 1 \dots r+5$:
-\begin{align}
+\begin{align*}
 	&a_i = b_ic_i = f_0d_i = g_0v_i \\
@@
 	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
-\end{align}
+\end{align*}
 which embed $f_0 b_i f_0 = c_i$;
-\item for all $ c = (i,j,k) \in C(r)$:
-\begin{align}
+\item for all $ l = (i,j,k) \in C(r)$:
+\begin{align*}
 	&h_{jk}b_j c_k = e\\
-	&d_i k_{c,1} f_2 = e && b_j f_2 k_{c,2} = e && k_{c,2} k_{c,3} k_{c,4} = e\\
-	&d_i k_{c,4} k_{c,5} = e && c_k k_{c,5} k_{c,6} =e && k_{c,1} k_{c,3} k_{c,6} = e,
-\end{align}
+	&d_i k_{l,1} f_2 = e && b_j f_2 k_{l,2} = e && k_{l,2} k_{l,3} k_{l,4} = e\\
+	&d_i k_{l,4} k_{l,5} = e && c_k k_{l,5} k_{l,6} =e && k_{l,1} k_{l,3} k_{l,6} = e,
+\end{align*}
 which embed $d_i b_j d_i = c_k$;
-\item relations of a Magic Square test:
-\begin{align}
+\item relations of a Magic Square game:
+\begin{align*}
 	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
 	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
-\end{align}
+\end{align*}
 which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
@@
 %------------------------------------------------------------------------
-In this section we give the presentation of $\Gamma$ which is built upon the representation 
+In this section we give a representation of $\Gamma$ which is built upon the representation 
 $\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma$ to construct the
@@
 
-Before giving the representation, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
+Before giving the representations, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
 of the representations,
@@
 \item for $f_0$ and $g_0$
-\begin{align}
+\begin{align*}
 	&\Psi_1(f_0) = X_{W_2} \x \1_{W_{d-1}} \\
 	&\Psi_1(g_0) = Z_{W_2} \x \1_{W_{d-1}},
-\end{align}
+\end{align*}
 \item
 for $i = 1 \dots r+5$,
-\begin{align}
+\begin{align*}
 	&\Psi_1(a_i) = \1_{W_2} \x \Psi_0(a_i) \\
@@
 	&\Psi_1(v_i) = Z_{W_2} \x \Psi_0(a_i).
-\end{align}
+\end{align*}
 \item for $(i,j,k) \in C(r)$,
-\begin{align}
+\begin{align*}
 	\Psi_1(h_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(a_j) + \ketbra{x_2}{x_2} \x \Psi_1(a_k).
-\end{align}
+\end{align*}
 \end{itemize}
@@
 \item for any $x$ which is also a generator of $G_1$,
-\begin{align}
+\begin{align*}
 	\Psi(x) = \1_{W_2} \x \Psi_1(x);
-\end{align}
+\end{align*}
 \item for the generators involved in the Magic square test
-\begin{align}
+\begin{align*}
 	&\Psi(f_1) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}} \\
@@
 	& \Psi(J) = - \1_{W_2} \x \1_{W_2} \x \1_{W_{d-1}};
-\end{align}
+\end{align*}
 \item for the generators $\{ w_i \}_{i=1}^{r+5}$:
-\begin{align}
+\begin{align*}
 	\Psi(w_i) = Z_{W_2} \x \1_{W_{d-1}} \x \Psi_0(a_i);
-\end{align}
+\end{align*}
 \item for the generators to embed the relation $f b_i f = c_i$:
-\begin{align}
+\begin{align*}
 	\Psi(k_{i,1}) &= X_{W_2} \x \Psi_1(b_i) = X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_0(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
@@
 	&+ \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_i)\\ 
-	\Psi(k_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(f_0b_if_0) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
-	&= \ketbra{x_1x_1}{x_1x_1} \x \1_{W_{d-1}} + \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
+	\Psi(k_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_if_0b_i) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
+	&= \ketbra{x_1}{x_1} \x X_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
 	\Psi(k_{i,4}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_ic_i) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	&=(\ketbra{x_1x_1}{x_1x_1}+  \ketbra{x_1x_2}{x_1x_2}) \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	&=\ketbra{x_1}{x_1} \x \1_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
 	\Psi(k_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i) \\
@@
 	&+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_0(a_i);
-\end{align}
-\item for the generators to embed the relation $d_i b_j d_i = c_k$:
-\begin{align*}
-	\Psi(k_{c,1}) &= X_{W_2} \x \Psi_1(d_i) = X_{W_2} \x X_{W_2} \x \Psi_0(a_{i}) \\
-	\Psi(k_{c,2}) &= X_{W_2} \x \Psi_1(b_j) = X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
-	\Psi(k_{c,3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
-	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_{j}x_{i}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_0(a_i)\\
+\end{align*}
+\item for the generators to embed the relation $d_i b_j d_i = c_k$ with $l = (i,j,k)$:
+\begin{align*}
+	\Psi(k_{l,1}) &= X_{W_2} \x \Psi_1(d_i) = X_{W_2} \x X_{W_2} \x \Psi_0(a_{i}) \\
+	\Psi(k_{l,2}) &= X_{W_2} \x \Psi_1(b_j) = X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
+	\Psi(k_{l,3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
+	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_{j}a_{i}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_0(a_i)\\
 	&+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_{i}a_{j}) \\
-	\Psi(k_{c,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(d_ib_jd_i) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
-	&= \ketbra{x_1x_1}{x_1x_1} \x \1_{W_{d-1}} + \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_ia_ja_i) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_0(a_i)\\
-	\Psi(k_{c,5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi(k_{l,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_jd_ib_j) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
+	&= \ketbra{x_1}{x_1} \x (\ketbra{x_2}{x_1} \x \Psi_0(a_ia_j)+ \ketbra{x_1}{x_2} \x \Psi_0(a_ja_i)) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_0(a_i)\\
+	\Psi(k_{l,5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
 	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_{k}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi(k_{c,6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k})\\
+	\Psi(k_{l,6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k})\\
 	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}}\\

### 2019-05-02 Draft/draft.tex
Honghao: edits of section 3 and 4:

@@
 %=======================================
-\section{The linear system game}
+\section{The linear system game $\LS(\Gamma_r)$}
 \label{sec:lsg}
@@
 %------------------------------------------------------------------------
-\subsection{The embedding of $G$}
+\subsection{The embedding of $uou^{-1} = o^r$}
 %------------------------------------------------------------------------
@@
 \end{theorem}
-We prove this by constructing the solution group $\Gamma$ of the linear system game. 
-We also prove some properties of the generators of $\Gamma$ along the way.
-
-We embed $uou^{-1}= o^r$ into $\Gamma$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
+We prove this by constructing the solution group $\Gamma_r$ of the linear system game,
+so we denote the linear system game by $\LS(\Gamma_r)$.
+\hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$? Or you have any suggestion about a symbol for this group?}
+We also prove some properties of the generators of $\Gamma_r$ along the way.
+
+We embed $uou^{-1}= o^r$ into $\Gamma_r$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
 \begin{definition}	
@@
 $d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
-we are going to embed it into a different set of linear relations in $\Gamma$.
+we are going to embed it into a different set of linear relations in $\Gamma_r$.
 
@@
 \label{def:gamma}
-The presentation of $\Gamma$ has order-$2$ generators:
+The presentation of $\Gamma_r$ has order-$2$ generators:
 \begin{align*}
@@
 \end{definition}
-The special properties of the generators of $\Gamma$ are summarized in the two propositions below.
+The special properties of the generators of $\Gamma_r$ are summarized in the two propositions below.
 \begin{proposition}
-	The group $\Gamma$ embeds all the conjugacy relations of $G_1$.
+	The group $\Gamma_r$ embeds all the conjugacy relations of $G_1$.
 	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
@@
 \begin{proposition}
-	In the group $\Gamma$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
+	In the group $\Gamma_r$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
 	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
@@
 %------------------------------------------------------------------------
-\subsection{The representation of $\Gamma$}
+\subsection{A representation of $\Gamma_r$}
 %------------------------------------------------------------------------
-In this section we give a representation of $\Gamma$ which is built upon the representation 
-$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma$ to construct the
-ideal strategy that realizes our correlation.
+In this section we give a representation of $\Gamma_r$ which is built upon the representation 
+$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma_r$ to construct the
+ideal strategy of $\LS(\Gamma_r)$.
 
@@
 Finally, we follow the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017} to construct the 
-representation of $\Gamma$.
+representation of $\Gamma_r$.
 \begin{definition}
 \label{def:rep_gamma}
-The representation $\Psi$ of $\Gamma$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
+The representation $\Psi$ of $\Gamma_r$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
 \begin{itemize}
@@
 Intuitively, it means that if some quantum strategy achieves a value $\ip{\I_\alpha}$ that is close to $\ip{\I_\alpha}_{\max}$,
-then the shared state must be close to $\ket{\EPR{2}}$ and their observables are close to rotated Pauli operators up to
-some local isometry.
-The formal statement is given in the theorem below. Since the proof uses the same technique as the one used in Ref.~\cite{bamps2015},
+then the shared state must be close to $\ket{\EPR{2}}$ and their observables are close to the rotated Pauli operators 
+defined in \cref{def:ideal},
+up to some local isometry.
+The formal statement is given in the theorem below. Since the proof uses the same techniques as introduced in Ref.~\cite{bamps2015},
 we defer the proof till \cref{sec:selftest}. Instead, we only list the key relations used in the proof because they will be reused in 
@@
 We follow the convention and define $c := \cos(\mu)$, $s := \sin(\mu)$, and
-\begin{align}
+\begin{align*}
 	&Z_A := M_1 && X_A := M_2\\
 	&Z_B := \frac{N_1+N_2}{2c} && X_B := \frac{N_1-N_2}{2s}.
-\end{align}
+\end{align*}
 The key relations that we will reuse are
@@
 %==========================
-The full test consists of three subtest: the linear constraint test,
+The full test consists of three subtest: the linear system game $\LS(\Gamma_r)$,
 the extended weighted CHSH test and a commutation test. We explain how the three tests are conducted and
@@
 
-\textbf{The linear constraint test}.
-Recall that the the linear constraint test with solution group $\Gamma$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
+\textbf{The linear system game}.
+Recall that the the linear system game with solution group $\Gamma_r$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
 equations labelled by $i \in \{1, 2 \dots \mr\}$.
-We denote the linear system associated with the linear constraint test by $H\underline{x} = \uc$ and
+We denote the associated linear system by $H\underline{x} = \uc$ and
 define $X_i := \{ \ux : \sum_{k} H(i,k)\ux(k) = \uc(i) \}$ and $I_i = \{ k : H(i,k) = 1\}$.
-From the construction of $\Gamma$, we know that $| I_i| \leq 3$.
+From the construction of $\Gamma_r$, we know that $| I_i| \leq 3$.
 The correspondence between $\ux$ and the generators of $\Gamma$ is that

### 2019-05-02 Draft/draft.tex
Honghao: edits up to section 6.2

@@
 
+\begin{abstract}
+	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
+	$\Theta(r^2)$ that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
+	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
+	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
+	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
+	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
+	with unbounded local dimension.
+\end{abstract}
 %========================================
@@
 On the Hilbert space $W_2$, we define
-\begin{align}
+\begin{align*}
 	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
@@
 	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
-\end{align}
+\end{align*}
 \begin{definition}
 The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
-\begin{align}
+\begin{align*}
 	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
@@
 	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
-\end{align}
+\end{align*}
 where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
-\begin{align}
+\begin{align*}
 	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
-\end{align}
+\end{align*}
 The representation of the rest of the generators
@@
 We can check that
-\begin{align}
+\begin{align*}
 	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
 	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
-\end{align}
+\end{align*}
 which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
@@
 
-\textbf{The linear system game}.
 Recall that the the linear system game with solution group $\Gamma_r$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
@@
 
-\textbf{The extended weighted CHSH test}.
-In this test, 
-the input alphabets are $\calX = \calY = \{\ast, 1, 2, \nr+1,\nr+2\}$.
+In the extended weighted CHSH test,
+all the question pairs are $\{ (\ast, \ast) \} \cup \{(\ast, y), (x, \ast)\}_{x,y = \nr+1, \nr+2} \cup 
+\{(x,y)\}_{x=y \in \{\nr+1, \nr+2\}} \cup
+\{(x,y)\}_{x = y \in \{1, 2\}} \cup \{(x,y)\}_{x = 1,2, y =\nr+1, \nr+2} \cup  \{(x,y)\}_{x = \nr+1,\nr+2, y =1, 2}$.
+%the input alphabets are $\calX = \calY = \{\ast, 1, 2, \nr+1,\nr+2\}$.
 For each question, there is an associated answer set:
@@
 \end{itemize}
-Note that when the referee wants to ask Alice $x = 1,2$, the referee gives Alice a pair $(i_x. x)$ where 
+Note that when the referee wants to ask Alice $x = 1,2$, which also labels a variable of $\LS(\Gamma_r)$, 
+the referee gives Alice a pair $(i_x. x)$ where 
 $i_x$ labels an equation containing the variable labelled by $x$. 
-For simplicity we omit the $i_x$ part in the alphabet $\calX$.
+For simplicity we omit the $i_x$ part in the alphabet $\calX$, since $\LS(\Gamma_r)$
+forces Alice to use a binary observable strategy.
 Later we will show that the $i_x$ part can be made implicit.
@@
 
-\textbf{The commutation test.}
-In this test, we reuse questions from the two other tests so the answer
+In the commutation test, 
+we reuse questions from the two other tests so the answer
 set for each question is the same across the tests.
@@
 In each test case, Alice is given one of two questions.
-One of the possible question is to assign a value to some variable of the linear constraint test.
+One of the possible question is to assign a value to some variable of $\LS(\Gamma_r)$.
 Again, the equation label is implicit when this variable is given.
-The other possibility is to answer $\nr+1$ or $\nr+2$.
+The other possibility is to answer $\nr+1$ or $\nr+2$ from the extended weighted CHSH test.
 Bob is given both of the question so he needs to give answers to both questions.
@@
 The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
-Alice's input is determined by the pair so she receives one of the two questions with equal probability.
-
-The full correlation is generated by a strategy that can pass all the three tests. We give the ideal strategy first.
+Alice's input is determined by the pair so she receives one of the two questions of a given pair with equal probability.
+
+The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first.
 %--------------------------------------------
@@
 \begin{align*}
-\ket{\psi} = &(\frac{1}{\sqrt{2}} \ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
-=&(\frac{1}{\sqrt{2}} \ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
+\ket{\psi} = &\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
+=&\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
 \end{align*}
@@
 \begin{align*}
-	&\ket{1_1} = \cos(-\pi/2d)\ket{1} + \sin(-\pi/2d)\ket{d-1}
-	&&\ket{(d-1)_1} = \sin(-\pi/2d)\ket{1} - \cos(-\pi/2d)\ket{d-1}\\
-	&\ket{1_2} = \cos(-\pi/2d)\ket{1} - \sin(-\pi/2d)\ket{d-1}
-	&&\ket{(d-1)_2} = \sin(-\pi/2d)\ket{1} + \cos(-\pi/2d)\ket{d-1}\\
-	&\ket{+} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
-	&&\ket{-} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
+	&\ket{1_+} = \cos(-\frac{\pi}{2d})\ket{1} + \sin(-\frac{\pi}{2d})\ket{d-1}
+	&&\ket{(d-1)_+} = \sin(-\frac{\pi}{2d})\ket{1} - \cos(-\frac{\pi}{2d})\ket{d-1}\\
+	&\ket{1_-} = \cos(-\frac{\pi}{2d})\ket{1} - \sin(-\frac{\pi}{2d})\ket{d-1}
+	&&\ket{(d-1)_-} = \sin(-\frac{\pi}{2d})\ket{1} + \cos(-\frac{\pi}{2d})\ket{d-1}\\
+	&\ket{1_{\times}} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
+	&&\ket{(d-1)_{\times}} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
 \end{align*}
@@
 	&M_{n+1}^0 =N_{n+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && M_{n+1}^1=N_{n+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
-	&M_{n+2}^0 =N_{n+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{+}{+} && M_{n+2}^1= N_{n+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{-}{-}\\
-	&M_1^0 = N_1^0 =(\1_{W_2})^{\x 2} \x  \ketbra{1_1}{1_1} && M_1^1 = N_1^1 =(\1_{W_2})^{\x 2} \x  \ketbra{(d-1)_1}{(d-1)_1}\\
-	&M_2^0 = N_2^0 = (\1_{W_2})^{\x 2} \x \ketbra{1_2}{1_2} && M_1^1 = N_1^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_2}{(d-1)_2}.
-\end{align*}
-To present the observables used in the linear constraints test, we relabel the generators of $\Gamma$ as $x_i$ for $i = 1 \dots \nr$. Then the 
-observables are
+	&M_{n+2}^0 =N_{n+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1_{\times}}{1_{\times}} && M_{n+2}^1= N_{n+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_{\times}}{(d-1)_{\times}}\\
+	&M_1^0 = N_1^0 =(\1_{W_2})^{\x 2} \x  \ketbra{1_+}{1_+} && M_1^1 = N_1^1 =(\1_{W_2})^{\x 2} \x  \ketbra{(d-1)_+}{(d-1)_+}\\
+	&M_2^0 = N_2^0 = (\1_{W_2})^{\x 2} \x \ketbra{1_-}{1_-} && M_1^1 = N_1^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_-}{(d-1)_-}.
+\end{align*}
+The observables for $\LS(\Gamma_r)$ are
 \begin{align}
@@
 where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
-To make sure the strategy is correct, there are some facts to check.
+Note that Alice uses the same observable for the same variable appearing in different equations.
+
+To make sure the strategy is correct, we need to check a few properties of it.
 \begin{proposition}
@@
 	We prove \cref{eq:o2_comm} first. It is simple to check that
-	\begin{align}
-		&M_1M_2= \sum_{j=1}^{d-1} \omega_d^{j} \ketbra{x_j}{x_j},\\
-		&M_3M_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
-	\end{align}
+	\begin{align*}
+		&M_1M_2= \sum_{j=1}^{d-1} \omega_d^{j} \ketbra{x_j}{x_j},
+		&&M_3M_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
+	\end{align*}
 	and that 
-	\begin{align}
+	\begin{align*}
 		M_3M_4 M_2 M_4 M_3 = &\sum_{j=0}^{(d-3)/2} M_3M_4 (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) M_4M_3\\
 		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}} = M_2.
-	\end{align}
+	\end{align*}
 
@@
 	Before checking $i=3$ and $i=4$, we first observe that
-	\begin{align}
+	\begin{align*}
 		M_3M_4 N_3 N_4 \ket{\psi} = \ket{\psi}.
-	\end{align}
+	\end{align*}
 	The eigenvectors of $M_3M_4$ and $N_3N_4$ are 
-        \begin{align}
+        \begin{align*}
         		\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
-        \end{align}
+        \end{align*}
         Hence we can express $\ket{x_{r^j}}$ in terms of $\ket{u_k}$ as 
-        \begin{align}
+        \begin{align*}
         		\ket{x_{r^j}} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
-        \end{align}
+        \end{align*}
         Then $M_4$ acts on $\ket{x_{r^j}}$ by
@@
         Then we show that $M_4  N_4 \ket{\psi} = \ket{\psi}$ as 
-        \begin{align}
+        \begin{align*}
         	M_4 N_4 \ket{\psi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} M_4  N_4 \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
         	= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\psi},
-        \end{align}
+        \end{align*}
 	Combining it with the fact that $M_3M_4 N_3N_4 \ket{\psi} = \ket{\psi}$, we can conclude that
@@
 \end{proof}
-The similar result, i.e., $M_jN_j \ket{\psi} = \ket{\psi}$ for $j = 1 \dots \nr$, are easy to check because all the observables are defined by $M_j, N_j$ for $j=1,2,3,4$.
-An interesting property of $U := M_3M_4$ and $O := M_1M_2$ is summarized in the proposition below. 
+The similar result, i.e., $M_jN_j \ket{\psi} = \ket{\psi}$ for $j = 1 \dots \nr$, are easy to check because all the other observables are defined by $M_j, N_j$ for $j=1,2,3,4$.
+An interesting property of $U_A := M_3M_4$ and $O_A := M_1M_2$ is summarized in the proposition below. 
 \begin{lemma}
@@
 %---------------------------------------------------
-\subsection{The full correlation}
+\subsection{The correlation $\fC(d,r)$}
 %---------------------------------------------------
@@
 %=====================================
-\section{Main result}
+\section{Robust self-testing with $\fC(d,r)$}
 \label{sec:main}
@@
 In this section, we examine the properties of a strategy $S$ that can reproduce the
-full correlation approximately and 
+correlation $\fC(d,r)$ approximately and 
 prove that the strategy $S$ must contain the state $\ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}$
@@
 
-Let us denote the full correlation by $( \tpr{ab}{xy} )$, then the formal statement of an approximate strategy is given below.
+Let us denote the full correlation by $\fC(d,r) = ( \tpr{ab}{xy} )$, then the formal statement of an approximate strategy is given below.
 \begin{definition}
-	We say a quantum strategy $S = (\ket{\psi}, \{M_x^a\}, \{N_y^b\})$, which produces the correlation
+	For a correlation $\tilde{C} = (\tpr{ab}{xy})$,
+	we say a quantum strategy $S = (\ket{\psi}, \{M_x^a\}, \{N_y^b\})$
+	is an $\ep$-approximate quantum strategy of $\tilde{C}$, 
+	if it produces the correlation
 	$( \pr{ab}{xy} = \bra{\psi} M_x^a N_y^b \ket{\psi} )$ such that
 	\begin{align}
-	E_{xy} \sum_{ab} |\pr{ab}{xy} - \tpr{ab}{xy}| \leq \ep,
-	\end{align}
-	is an $\ep$-approximate quantum strategy.
+	E_{(x,y)} \sum_{ab} |\pr{ab}{xy} - \tpr{ab}{xy}| \leq \ep.
+	\end{align}
 \end{definition}
-In the our full test, the probability distribution over all the questions $(x,y)$ is uniform.
-Since the number of all the possible questions is $O(r^2)$ and 
-the number of possible output pairs is $(a,b)$ is constant for each question pair $(x,y)$, 
-the approximate condition directly imply that 
+In our full test, the probability distribution over all the question pairs $(x,y)$ is uniform.
+Since the number of all the possible question pairs is $\Theta(r^2)$ and 
+the number of possible output pairs is constant for each question pair $(x,y)$, 
+the approximate condition directly implies that, if $S$ is an $\ep$-approximate strategy
+of $\fC(d,r)$, then
 $\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$, for all $(a,b,x,y)$.
@@
 %------------------------------------------------------------------------------------------
-\subsection{Implication of passing the linear constraint test}
+\subsection{Implication of passing $\LS(\Gamma_r)$}
 \label{sec:imp_lct}
 %------------------------------------------------------------------------------------------
-We slightly change the notation so that instead of the notation $(x,y)$, Alice gets equation number $i$, sometimes with a variable label $j$,
+In this subsection, we use $(i,j)$ to denote the question pair so that Alice gets equation number $i$, sometimes with a variable label $j$,
  and Bob gets a variable label $j$.
-The way we conducted the linear constraint test forces Alice to have binary observables $\{M_{ij}\}$ that satisfies 
+The way we conduct the linear constraint test forces Alice to have binary observables $\{M_{ij}\}$ that satisfy 
 \cref{def:q_strat}.
@@
 	\label{prop:lct_base}
-	Let $S$ be an $\ep$-approximate strategy,
-	then there exist binary observables $\{ M_j \}_{j \in [\nr]}$, such that
+	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$,
+	then there exist binary observables $\{ M_j \}_{j=1}^{\nr} $, such that
 	\begin{align}
@@
 \begin{proof}
-Since $\tpr{\ux b}{ij}$ win's the linear system game optimally, we know that 
-$
+The condition that $\tpr{\ux b}{ij}$ from $\fC(d,r)$ wins the linear system game optimally is equivalent to
+\begin{align*}
 \sum_{\ux,b: \ux \in X_i, \ux(j) = b} \tpr{\ux b}{ij} = 1
-$
+\end{align*}
 for all $i = 1 \dots \mr$.
-It has been shown \cite{slofstra2017} that 
-\begin{align}
+It has been shown in Ref.~\cite{slofstra2017} that 
+\begin{align*}
 	\bra{\psi} M_{ij} N_j \ket{\psi} = 2 \sum_{\ux,b: \ux \in X_i, \ux(j) = b} \pr{\ux b}{ij} -1 \appd{O(r^2 \ep)} 1.
-\end{align}
+\end{align*}
 Since $M_{ij}$ and $N_j$ are unitaries, we know that
-\begin{align}
-	M_{ij} \ket{\psi} \appd{O(r\se)} N_j \ket{\psi} \text{ for all } i \leq \mr \text{ and } j \leq \nr.
-\end{align}
+\begin{align*}
+	M_{ij} \ket{\psi} \appd{O(r\se)} N_j \ket{\psi} \quad \text{ for all } i \leq \mr \text{ and } j \leq \nr.
+\end{align*}
 We define $M_j := M_{ij}$ for the smallest $i$ such that $ j \in I_i$ then 
-\begin{align}
+\begin{align*}
 	M_j N_j \ket{\psi} \appd{O(r\se)} M_{ij}N_j\ket{\psi} \appd{O(r\se)} \ket{\psi} \quad \text{ for all } j \leq \nr.
-\end{align}
+\end{align*}
 
@@
 or equivalently,
-\begin{align}
+\begin{align*}
 	\Pi_{j \in I_i} M_{ij} \ket{\psi} = (-1)^{b_i} \ket{\psi}\quad\text{ for all } i \leq \mr.
-\end{align}	
+\end{align*}	
 If we replace each $M_{ij}$ with $M_j$ in the equation above, we demonstrate the effect on a
@@
 Hence we can conclude that 
-\begin{align}
+\begin{align*}
 	\Pi_{j \in I_i} M_j \ket{\psi} \appd{O(r\se)} (-1)^{\uc(i)}\ket{\psi} \quad \text{ for all } i \leq \mr.
-\end{align}
+\end{align*}
 \end{proof}
 Note that with the same technique, we can prove that 
-\begin{align}
+\begin{align*}
 	\Pi_{j \in I_i} N_j \ket{\psi} \appd{O(r\se)} (-1)^{\uc(i)}\ket{\psi} \quad \text{ for all } i \leq \mr.
-\end{align}
-
-Following the steps of the embedding of $(a_3a_4)^l a_1a_2(a_4a_3)^l = (a_1a_2)^{r^l}$ into $\Gamma$,
-we can get the following corollary.
+\end{align*}
+
+Following the steps of the embedding of $(a_3a_4)^l a_1a_2(a_4a_3)^l = (a_1a_2)^{r^l}$ into $\Gamma_r$,
+we can get the following proposition.
 \begin{proposition}
 \label{prop:lct_adv}
-Let $S$ be an $\ep$-approximate strategy defined earlier and $\{M_j, N_j\}_{j \in \nr}$ be the observables defined in 
+Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $\{M_j, N_j\}_{j \in \nr}$ be the observables defined in 
 \cref{prop:lct_base}, 
@@
 \begin{align}
-	M_1M_2 (M_4M_3)^l \ket{\psi}\appd{O(r^{l+1} \se)} (M_4M_3)^l (M_1M_2)^{r^l} \ket{\psi} \text{ for all } l \geq 1.
-\end{align}
+	&M_1M_2 (M_4M_3)^l \ket{\psi}\appd{O(r^{l+1} \se)} (M_4M_3)^l (M_1M_2)^{r^l} \ket{\psi}, \\
+	&N_1N_2 (N_4N_3)^l \ket{\psi}\appd{O(r^{l+1} \se)} (N_4N_3)^l (N_1N_2)^{r^l} \ket{\psi}, 
+\end{align}
+for all $l \geq 1$.
 \end{proposition}
@@
 	\label{eq:ls_comm_rel}
-	M_1M_2 (M_4M_3) \ket{\psi} \appd{O(r\se)} (M_4M_3)(M_1M_2)^r \ket{\psi}.
-\end{align}
-Assume the statement is true for $l = n$, then consider the case that $l = n+1$,
+	M_1M_2 (M_4M_3) \ket{\psi} \appd{O(r^2\se)} (M_4M_3)(M_1M_2)^r \ket{\psi}.
+\end{align}
+Assume the statement is true for $l = n$ and consider the case that $l = n+1$,
 \begin{align*}
 	M_1M_2 (M_4M_3)^{n+1} \ket{\psi}  &\appd{O(r\se)} (N_3N_4) M_1M_2(M_4M_3)^n \ket{\psi} \\
-	&\appd{O(r^{n+1}\se)} (N_3N_4) (M_4M_3)^k (M_1M_2)^{r^n} \ket{\psi}\\
+	&\appd{O(r^{n+1}\se)} (N_3N_4) (M_4M_3)^n (M_1M_2)^{r^n} \ket{\psi}\\
 	&\appd{O(r\se)} (M_4M_3)^n (M_1M_2)^{r^n} (M_4M_3) \ket{\psi} \\
@@
 By the principal of proof by induction, the proof is complete.
+The proof for Bob's observables $\{ N_j \}_{j=1}^{\nr}$ is similar.
 \end{proof}
@@
 
-For simplicity, we define $O_A = M_1M_2$ and $U_A=M_3M_4$ such that
+Recall $O_A = M_1M_2$ and $U_A=M_3M_4$, then
 the conclusion of \cref{prop:lct_adv} can be rewritten as 
-\begin{align}
-	U_A^k O_A (U_A\ct)^k \ket{\psi} \appd{O(r^{k+1} \se)} O_A^{r^k} \ket{\psi}.
-\end{align}
+\begin{align*}
+	U_A^n O_A (U_A\ct)^n \ket{\psi} \appd{O(r^{n+1} \se)} O_A^{r^n} \ket{\psi}.
+\end{align*}
 On Bob's side, we also define $O_B = N_1N_2$ and $U_B = N_3N_4$ 
@@
 
-The other relations that are embedded in $\Gamma$ are 
+The other relations that are embedded in $\Gamma_r$ are 
 \begin{align}
@@
 \end{align}
-We summarize the implications in the following corollary.
+We summarize the implications in the following proposition.
 \begin{proposition}
@@
 \end{proposition}
-Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma$,
-so this proposition can be proved using the same technique as that used in the proof of \cref{prop:lct_base}.
+Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma_r$,
+so this proposition can be proved using the same technique used in the proof of \cref{prop:lct_base}.
 %------------------------------------------------------------------------------------------

### 2019-05-03 Draft/draft.tex
Honghao: edits of section 6

@@
 
+In the full test, the question pairs from the three subtests are given to Alice and Bob with equal probability.
 The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first.
@@
 %------------------------------------------------------------------------------------------
+In this subsection, we prove a series of propositions and lemmas which lead to a key result that will be
+used in the self-testing proof.
 \begin{proposition}
 \label{prop:chsh_base}
-Let $S$ be an $\ep$-approximate quantum strategy,
+Let $S$ be an $\ep$-approximate quantum strategy of $\fC(d,r)$,
 then the strategy $S$ satisfy the following relations
@@
 	\label{prop:s1s2}
-	Let $S$ be an $\ep$-approximate strategy. We define
-	\begin{align}
-		&M_{\nr+1} = M_{\nr+1}^0 - M_{\nr+1}^1 && M_{\nr+2} = M_{\nr+2}^0 - M_{\nr+2}^1,\\
-		&N_{\nr+1} = N_{\nr+1}^0 - N_{\nr+1}^1 && N_{\nr+2} = N_{\nr+2}^0 - N_{\nr+2}^1.
+	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$. We define
+	\begin{align}
+		&M_{\nr+1} = M_{\nr+1}^0 - M_{\nr+1}^1  && 
+		M_{\nr+2} = M_{\nr+2}^0 - M_{\nr+2}^1,\\
+		&N_{\nr+1} = N_{\nr+1}^0 - N_{\nr+1}^1  && 
+		N_{\nr+2} = N_{\nr+2}^0 - N_{\nr+2}^1.
 	\end{align}
@@
 \end{proposition}
+
 \begin{proof}
-We will prove that $\bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi} \appd{O(\sd r\se)} \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi}$ as an example,
-\begin{align*}
-	   \bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi} 
-	= &\bra{\psi}(M_\ast^\diamond + M_\ast^\perp) M_{\nr+1}^0N_1^0 (M_\ast^\diamond + M_\ast^\perp)\ket{\psi} \\
-	= & \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\perp\ket{\psi}\\
-	&+\bra{\psi}M_\ast^\perp M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\perp M_{\nr+1}^0N_1^0 M_\ast^\perp\ket{\psi}\\
-	\appd{O(r\se)}&  \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_{\nr+1}^\perp\ket{\psi} \\
-	&+\bra{\psi}M_{\nr+1}^\perp M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_{\nr+1}^\perp M_{\nr+1}^0N_1^0 M_{\nr+1}^\perp\ket{\psi}\\
-	=&\bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi},
-\end{align*}
-where we use the facts that $M_\ast^\perp \ket{\psi} \appd{O(r\se)} M_{\nr+1}^\perp \ket{\psi}$ and that 
-$\supp(M_{\nr+1}^0) \cap \supp(M_{\nr+1}^\perp) = \emptyset$. This means that if Alice and Bob share state $M_\ast^\diamond \ket{\psi}/\norm{M_\ast^\diamond \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
-we get conditional probability
+To prove that $S_1$ achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, we need to examine terms of the form
+$\bra{\psi} M_\ast^\diamond M_{x}^aN_y^b M_\ast^\diamond\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0.1$,
+which relate to $\bra{\psi} M_x^a N_y^b \ket{\psi}$ as follows,
+\begin{align*}
+	   \bra{\psi} M_{x}^aN_y^b \ket{\psi} 
+	= &\bra{\psi}(M_\ast^\diamond + M_\ast^\perp) M_x^a N_y^b (M_\ast^\diamond + M_\ast^\perp)\ket{\psi} \\
+	= & \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\perp\ket{\psi}\\
+	&+\bra{\psi}M_\ast^\perp M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\perp M_x^aN_y^b M_\ast^\perp\ket{\psi}\\
+	\appd{O(r\se)}&  \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_x^\perp\ket{\psi} \\
+	&+\bra{\psi}M_x^\perp M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_x^\perp M_x^aN_y^b M_x^\perp\ket{\psi}\\
+	=&\bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi},
+\end{align*}
+where we use the facts that $M_\ast^\perp \ket{\psi} \appd{O(r\se)} M_x^\perp \ket{\psi}$ and that 
+$\supp(M_x^0) \cap \supp(M_x^\perp) = \emptyset$ for the relevant values of $(x,y,a,b)$.
+This means that if Alice and Bob share state $M_\ast^\diamond \ket{\psi}/\norm{M_\ast^\diamond \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
+they get conditional probability
 \begin{align*}
@@
 \end{align*}
+The rest of the conditional probabilities produced by $S_1$ can be derived in the same way.
 Using the fact that $O(d r \se)$ dominates $O(dr^2 \ep)$,
@@
 \begin{proposition}
-	Let $S$ be an $\ep$-approximate strategy and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.
+	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.
 	We also define
@@
 	$(M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}$ is close to $(- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}$,
-	or equivalently,
-	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
-
-	At this point, we use the anticommutation relation induced by $S_1$ (\cref{eq:zaxa}) and conclude that 
-	\begin{align}
+%	or equivalently,
+%	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
+	At this point, we can use the anti-commutation relation induced by $S_1$ (\cref{eq:zaxa}) and conclude that 
+	\begin{align*}
 		M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^\diamond\ket{\psi}}}}{c\sqrt{s}}O(\sd\sr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}.
-	\end{align}
-	If we use the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \sr \qe)$.
+	\end{align*}
+	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \sr \qe)$.
 	Then we can show that 
@@
 
-	\textbf{To prove \cref{eq:psi1_sum}}, we use the definition of $\ket{\psi_1}$ and $\ket{\psi_2}$
-	\begin{align}
+	\textbf{To prove \cref{eq:psi1_sum}}, we use the definition of $\ket{\psi_1}$ and $\ket{\psi_2}$ and get 
+	\begin{align*}
 		\ket{\psi_2} + \ket{\psi_1} = 1/2( 2M_{\nr+1}^0 + 2M_{\nr+1}^1) \ket{\psi} \appd{O(r\se)} M_\ast^\diamond \ket{\psi}.
-	\end{align}
-
-	\textbf{To prove \cref{eq:psi1_orth}}, we expand the inner product
+	\end{align*}
+
+	\textbf{To prove \cref{eq:psi1_orth}}, we expand the inner product and get 
 	\begin{align*}
@@
 	\end{align}
-	Note that $Z_A$ should be defined by $M_{\nr+1}^0 - M_{\nr+1}^1 + M_{\nr+1}^\perp$,
-	but $M_{\nr+1}^\perp$ is almost orthogonal to $M_\ast^\diamond$, so we omit the $M_{\nr+1}^\perp$ term here.
-	In the definition of $X_A$, we omit $M_{\nr+2}^\perp$ too.
-
+%	Note that $Z_A$ should be defined by $M_{\nr+1}^0 - M_{\nr+1}^1 + M_{\nr+1}^\perp$,
+%	but $M_{\nr+1}^\perp$ is almost orthogonal to $M_\ast^\diamond$, so we omit the $M_{\nr+1}^\perp$ term here.
+%	In the definition of $X_A$, we omit $M_{\nr+2}^\perp$ too.
 	Recalling \cref{eq:za-zb}, which states that
@@
 	In summary, we have shown that 
-        \begin{align}
+        \begin{align*}
         		&N_1M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \qe/ \sd)} cM_{\nr+1}^0\ket{\psi} - sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
@@
         		&N_2M_{\nr+1}^1 \ket{\psi} \appd{O(\sr \qe/ \sd )} -cM_{\nr+1}^1\ket{\psi} + sM_{\nr+2}M_{\nr+1}^0\ket{\psi}.
-        \end{align}
+        \end{align*}
         Then we can calculate that 
@@
         		&\appd{O( \sr \qe/\sd)}(c^2M_{\nr+1}^0- csM_{\nr+2}M_{\nr+1}^1 -csM_{\nr+2}M_{\nr+1}^1 -s^2 M_{\nr+2}^2 M_{\nr+1}^0)\ket{\psi}\\
-        		&= (\cos(2\pi/d) M_{\nr+1}^0 - \sin(2\pi/d) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.
+        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^0 - \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.
         \end{align*}
@@
         		&\appd{O(\sr \qe/\sd)}(c^2M_{\nr+1}^1+ csM_{\nr+2}M_{\nr+1}^0 +csM_{\nr+2}M_{\nr+1}^0 -s^2 M_{\nr+2}^2 M_{\nr+1}^1)\ket{\psi}\\
-        		&= (\cos(2\pi/d) M_{\nr+1}^1 + \sin(2\pi/d) M_{\nr+2}M_{\nr+1}^0)\ket{\psi},
+        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^1 + \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^0)\ket{\psi},
         \end{align*}
@@
 	Note that here we use another form of $\ket{\psi_1}$ which is 
-	$\ket{\psi_1} = 1/2(\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi}$.
+	\begin{align*}
+	\ket{\psi_1} = 1/2(\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
+	\end{align*}
 
@@
 	With similar calculation as in the previous case, we can get 
-	\begin{align}
+	\begin{align*}
 		M_1M_2 (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi} \appd{O(\sr \qe/\sd)} 
 		\omega_d^{-1} (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1)\ket{\psi} .
-	\end{align}
+	\end{align*}
 	Multiplying both sides of the equation above by $1/2(\1+iN_{\nr+2})$ we get
@@
 Then we can deduce that 
-\begin{align}
+\begin{align*}
 	M_3M_4 \x N_3N_4 \ket{\psi} \appd{O(r\se)} M_3 \x N_3 \ket{\psi} \appd{O(r\se)} \ket{\psi},
-\end{align}
+\end{align*}
 or equivalently,
-\begin{align}
+\begin{align*}
 	U_A \x U_B \ket{\psi} \appd{O(r\se)} \ket{\psi}.
-\end{align}
+\end{align*}
 Intuitively, it means that $U_A U_B $ only permutes the Schmidt basis of $\ket{\psi}$.
 Similarly, we also have $U_A\ct U_B\ct \ket{\psi} \appd{O(r\se)} \ket{\psi}$.
-We use this observation in the proof of the following proposition.
+We use this observation in the proof of the following lemma.
 \begin{lemma}
 \label{lm:decomp_psi}
-Let $S$ be an $\ep$-approximate strategy and 
+Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and 
 define 
-$\ket{\psi'} := \sum_{j=1}^{(d-1)} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}$,
+$\ket{\psi'} := \sum_{j=1}^{(d-1)} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}$
+with $\log_r j$ being the discrete log,
 then
 \begin{align}
-	&\ket{\psi} \appd{O(d^{7/4} r^{1/4} \ep^{1/8})} \ket{\psi'},
-\end{align}
-where $\log_r j$ is the discrete log.
+	&\ket{\psi} \appd{O(d^{5/4} r^{d/2} \ep^{1/8})} \ket{\psi'}.
+\end{align}
 \end{lemma}
 \begin{proof}
-	We first prove that $\norm{\ket{\psi'}}^2 \appd{O(d^4 \sr \ep^{1/8})} 1$.
+	We first prove that $\norm{\ket{\psi'}}^2 \appd{O(d^{5/2} r^d \qe)} 1$.
 	Observe that 
@@
         \begin{align}
+        \label{eq:omega}
         		O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j+1/2} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
@@
 	Hence for $j \neq j'$, \cref{prop:orthog} tells us that  
-	\begin{align}
+	\begin{align*}
 		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O(d^{3/2} (r^j + r^{j'})\sr \qe)} 0.
-	\end{align}
+	\end{align*}
 	We can calculate the norm of $\ket{\psi'}$ as 
@@
 		\braket{\psi}{\psi'} = \sum_{j=1}^{d-1} \bra{\psi} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}
-		 \appd{O(dr\se)} (d-1) \braket{\psi}{\psi_1}.
+		 \appd{O(d^2r\se)} (d-1) \braket{\psi}{\psi_1}.
 	\end{align*}
@@
 	where the last approximation comes from the correlation.
-	Hence, we know $\braket{\psi}{\psi'} \appd{O(d r \se)} 1$.
+	Hence, we know $\braket{\psi}{\psi'} \appd{O(d^2 r \se)} 1$.
 	In the end, we apply \cref{prop:close_vec} to get
-	\begin{align}
-		\ket{\psi} \appd{O(d^{5/4} r^{d/2+1/4} \ep^{1/8})} \ket{\psi'}.
-	\end{align}
+	\begin{align*}
+		\ket{\psi} \appd{O(d^{5/4} r^{d/2} \ep^{1/8})} \ket{\psi'}.
+	\end{align*}
 \end{proof}
@@
 %-------------------------------------------------------------------------------------------
-The commutation test is introduced to certify the operators used for the Magic Square test and 
-the operators for the extended weighted CHSH test commute. For details of the general commutation test, 
+The commutation test is introduced to certify the operators used for the Magic Square test (part of $\LS(\Gamma_r)$ and 
+the operators for the extended weighted CHSH test commute. For the details of the general commutation test, 
 we refer to Appendix~A.$2$ of \cite{coladan2017verifier}. 
-We use the similar technique in our proof but our proof also bases on the correlation given in \cref{tbl:comm}.
+We use similar techniques in our proof but our proof also bases on the correlation given in \cref{tbl:comm}.
 
@@
 	\label{prop:rel_comm}
-	Let $S$ be an $\ep$-approximate strategy ,
+	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$,
 	then 
@@
 \end{proposition}
-Note that $M_j$'s tested in the commutation test are also used in the Magic Square test,
-which will be used to construct the isometry later.
+Note that $M_j$'s for $j = r+6, r+8,r+9,r+11$ tested in the commutation test are used in the Magic Square test,
+which will be used to construct the isometry in the next subsection.
 \begin{proof}
@@
 
-	For the other relations, we prove $M_{\nr+1}^0M_{r+6} \ket{\psi} \appd{O(r\se)} M_{r+6}M_{\nr+1} \ket{\psi}$ to demonstrate 
+	For the other relations, we prove $M_{\nr+1}^0M_{r+6} \ket{\psi} \appd{O(r\se)} M_{r+6}M_{\nr+1}^0 \ket{\psi}$ to demonstrate 
 	the techniques involved. We denote Bob's projectors by $\{ N_{(\nr+1, r+6)}^{b_1 b_2} \}$ where $b_1 \in \{0, 1, \perp\}$ and
@@
 %-----------------------------------------------
-\subsection{An isometry}
-\label{sec:isometry}
+\subsection{Robust self-testing}
+\label{sec:self-test}
 %-----------------------------------------------
@@
 	\label{thm:self-test}
-	Let $S$ be an $\ep$-approximate strategy.
+	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$.
 	There exists an isometry   
@@
 	\begin{align}
-		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d^{5/4} r^{2d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
-		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d^{5/4} r^{2d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
+		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d^{5/4}r^{2d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d^{5/2}r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
-		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d^{5/4} r^{2d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d^{5/2} r^{d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d^{5/4} r^{2d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_{j r^{-1}}}_{B'}.
@@
 for any odd prime number $d$ with primitive root $r$, 
-there exists a correlation of size $\Theta(r^2)$ that can self-test the maximally
+there exists a correlation of size $\Theta(r^2)$ that can robustly self-test the maximally
 entangled state of local dimension $4(d-1)$.
@@
 $N_{r+6}, N_{r+8}, N_{r+9}, N_{r+11}$ to distill two copies of $\ket{\EPR{2}}$.
-Intuitively, $M_{r+6}$ acts as $\1 \x X$; $M_{r+8}$ acts as $X \x \1 $;
-$M_{r+9}$ acts as $\1 \x Z$ and $M_{r+11}$ acts as $Z \x \1$; and similarly on Bob's side.
+Intuitively, $M_{r+6}$ acts as $\1 \x \paulix$; $M_{r+8}$ acts as $\paulix \x \1 $;
+$M_{r+9}$ acts as $\1 \x \pauliz$ and $M_{r+11}$ acts as $\pauliz \x \1$; and similarly on Bob's side.
 
@@
         % Qubits
-        \node at (0,0) (q1) {$\ket{0}$};
+        \node at (0,0) (q1) {$\ket{x_0}$};
         \node at (0,-1) (q2) {};
         \node at (0,-2) (q3) {};
-        \node at (0,-3) (q4) {$\ket{0}$};
+        \node at (0,-3) (q4) {$\ket{x_0}$};
         %
@@
 \begin{enumerate}
-	\item Append control register $\ket{0}_{A'}$ on Alice's side and $\ket{0}_{B'}$ on Bob's side;
+	\item Append control register $\ket{x_0}_{A'}$ on Alice's side and $\ket{x_0}_{B'}$ on Bob's side;
 	\item Apply Quantum Fourier Transform ($QFT_d$) to Alice and Bob's control registers;
-	\item Apply Controlled-$O_{A/B}$ operations (i.e. if the control register is in state $\ket{k}_{A'/ B'}$, apply
+	\item Apply Controlled-$O_{A/B}$ operations (i.e. if the control register is in state $\ket{x_k}_{A'/ B'}$, apply
 	$O_{A/B}^k$.);
 	\item Apply inverse Quantum Fourier Transform ($QFT_d^{-1}$) to the control registers;
-	\item Apply Controlled-$U_{A/B}$ operations (i.e. If Alice's control register is in state $\ket{j}$, she applies
-	$U_A^{\log_r (d-j)}$. If Bob's control register is in state $\ket{j}$, he applies $(U_B\ct)^{\log_r j}$).
+	\item Apply Controlled-$U_{A/B}$ operations (i.e. If Alice's control register is in state $\ket{x_j}$, she applies
+	$U_A^{\log_r (d-j)}$. If Bob's control register is in state $\ket{x_j}$, he applies $(U_B\ct)^{\log_r j}$).
 \end{enumerate}
@@
 \begin{align}
-	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/4} r^{2d+1/2} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
+	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/2} r^{d+1/2} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
 \end{align}
@@
 \begin{align*}
-	&\Phi_{A,2} \x \Phi_{B,2}( \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi})) \\
+	&\quad\Phi_{A,2} \x \Phi_{B,2}( \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi})) \\
 	&\appd{O(d^{5/2} \sr \ep^{1/8})} \Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \x\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
@@
 
-\cref{lm:decomp_psi} implies that $ \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi}) \appd{O(d^{5/4} r^{d/2} r^{1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi'})$,  
+\Cref{lm:decomp_psi} implies that $ \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi}) \appd{O(d^{5/4} r^{d/2 +1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi'})$,  
 so we focus on how the isometry evolves $\ket{\psi'}$.
 The evolution is summarized below.
-	\begin{align}
-		& \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_1}_{A'}\ket{x_1}_{B'}\\
+	\begin{align*}
+		& \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
 		\xrightarrow[]{QFT_d}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}  \ket{\psi_1}\ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
@@
 		\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(\sd r^{2d} \sr \qe)}&\frac{1}{d} \sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}\omega_d^{(k_2-k_1)j}\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\xrightarrow[]{QFT_d^{-1}} &\frac{1}{d^2}\sum_{l_1,l_2 = 0}^{d-1}\sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} 
+		\appd{O(d^{5/2} r^{d} \sr \qe)}&\frac{1}{d} \sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}\omega_d^{(k_2-k_1)j}\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\xrightarrow[]{QFT_d^{-1}} &\frac{1}{d^2}\sum_{l_1,l_2 = 0}^{d-1}\sum_{k_1,k_2 = 0}^{d-1}\sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} 
 		\omega_d^{k_1(d-j-l_1)}\omega_d^{k_2(j-l_2)}\ket{\psi_1} \ket{x_{l_1}}_{A'}\ket{x_{l_2}}_{B'}\\
@@
 		\xrightarrow[]{\text{Controlled-}U_{A/B}}& \sum_{j=1}^{d-1} U_A^{\log_r j} (U_A\ct)^{\log_r j} U_B^{\log_r j} (U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
-		=&\ket{\psi_1} \x \sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
-	\end{align}
+		=&\ket{\psi_1} \x \sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
+	\end{align*}
+When we analyze the effect of the controlled-$O_{A/B}$, we applied \cref{eq:omega} repeatedly.
 In summary, we have shown that
 \begin{align}
-	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/4} r^{2d+1/2} \ep^{1/8})} \sqrt{d-1} \ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
-\end{align}
-where we use the fact that $O(d^{5/4} r^{2d+1/2} \ep^{1/8})$ dominates both $O(d^{5/4} r^{d/2+1/4} \ep^{1/8})$ and 
-$O(\sd r^{2d} \sr \qe)$.
+	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/2} r^{d+1/2} \ep^{1/8})} \sqrt{d-1} \ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
+\end{align}
+where we use the fact that $O(d^{5/2} r^{d+1/2} \ep^{1/8})$ dominates both $O(d^{5/4} r^{d/2+1/4} \ep^{1/8})$ and 
+$O(d^{5/2} r^{d+1/2} \qe)$.
 Since $\norm{\ket{\psi_1}}^2 \appd{O(r \se)} 1/(d-1)$, we know $ \sqrt{d-1} \norm{\ket{\psi_1}} \appd{O(\sd \sr\qe)} 1$.
@@
 The other observation that we need is that 
-\begin{align}
+\begin{align*}
 	&\Phi_{A,2} \x \Phi_{B,2} (\ket{\psi_1})  \\
@@
 	\ket{\psi_1} \ket{\ua}_{A''} \ket{\ub}_{B''}
-\end{align}
+\end{align*}
 For simplicity we define $M^{\ua} := M_{r+6}^{\ua(4)}M_{r+8}^{\ua(3)}M_{r+9}^{\ua(2)}M_{r+11}^{\ua(1)}$ and
@@
 for all $\ua, \ub \in \{0,1\}^4$, which implies that 
-\begin{align}
+\begin{align*}
 	\Phi_{A,2} \x& \Phi_{B,2}(\ket{\psi_1}) \appd{O(r\se)}\\
 	 &\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)(\Phi_{A,2}\x\Phi_{B,2} (\ket{\psi}).
-\end{align}
+\end{align*}
 At this point we can apply Lemma C.$1$ of \cite{wu2016} to $\Phi_{A,2}\x\Phi_{B,2} (\ket{\psi})$ and conclude that 
@@
 and then we calculate $\Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi'})$ as
-\begin{align}
-	O_A \ket{\psi'} \ket{0}_{A'}\ket{0}_{B'} =&  
-		\sum_{j=1}^{d-1} O_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1}\ket{x_1}_{A'}\ket{x_1}_{B'}\\
-		\appd{O(\sd r^{d+1/2} \ep^{1/4})}&\sum_{j=1}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} \ket{\psi_1} \ket{x_1}_{A'}\ket{x_1}_{B'}\\
+\begin{align*}
+	O_A \ket{\psi'} \ket{x_0}_{A'}\ket{x_0}_{B'} =&  
+		\sum_{j=1}^{d-1} O_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1}\ket{x_0}_{A'}\ket{x_0}_{B'}\\
+		\appd{O(\sd r^{d+1/2} \ep^{1/4})}&\sum_{j=1}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} \ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
 		\xrightarrow[]{QFT_d} &\frac{1}{d}\sum_{j=1}^{d-1} \sum_{k_1,k_2 = 0}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} 
@@
 		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(\sd r^{2d+1/2}  \ep^{1/4})}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}
+		\appd{O(d^{5/2} r^{d+1/2}  \ep^{1/4})}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}
 		\omega_d^{-j}\omega_d^{(k_2-k_1)j}\ket{\psi_1}
@@
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
-\end{align}
+\end{align*}
 The analysis for $\Phi_{A,1} \x\Phi_{B,1} (O_B \ket{\psi})$ is very similar.
@@
 $ \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi}) \appd{O(d^{5/4}r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi'})$, 
-and then we calculate $\Phi_{A,1} \x \Phi_{B,1} U_A\ket{\psi'})$.
-\begin{align}
-	U_A \ket{\psi'} \ket{0}_{A'}\ket{0}_{B'} =&  
-		\sum_{j=1}^{d-1} U_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1} \ket{x_1}_{A'}\ket{x_1}_{B'}\\
-		=&\sum_{j=1}^{d-1}(U_A\ct)^{\log_r j-1}  (U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_1}_{A'}\ket{x_1}_{B'}\\
+and then we calculate $\Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi'})$.
+\begin{align*}
+	U_A \ket{\psi'} \ket{x_0}_{A'}\ket{x_0}_{B'} =&  
+		\sum_{j=1}^{d-1} U_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
+		=&\sum_{j=1}^{d-1}(U_A\ct)^{\log_r j-1}  (U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
 		\xrightarrow[]{QFT_d} &\frac{1}{d}\sum_{j=1}^{d-1} \sum_{k_1,k_2 = 0}^{d-1}(U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j} \ket{\psi_1}  \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
@@
 		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(\sd r^{2d+1/2} \qe)}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}
+		\appd{O(d^{5/2} r^{d+1/2} \qe)}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}
 		\omega_d^{k_2j-k_1jr^{-1}}\ket{\psi_1}
@@
 		\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'},
-\end{align}
+\end{align*}
 where we use the fact that $(d-j)r^{-1} \equiv d -jr^{-1} \pmod{d}$.

### 2019-05-03 Draft/draft.tex
Added a few comments

--- 2019-05-02 Draft/draft.tex
@@
 	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
-	$\Theta(r^2)$ that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
+	$\Theta(r^2)$ 
+	that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
 	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
@@
 	\item $N_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
-	\hf{I don't think we need to take transpose because these are binary observables. -HF}
+	\hf{I don't think we need to take transpose because these are binary observables. -HF}  \carl{A binary observable can still be different from its transpose.}
 	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
 \end{enumerate}
-\hf{Later we will use this approach to construct a strategy for a linear system game.}
-\carl{I don't think the reader will know what ``ideal strategy'' refers to at this point.}
-\hfc{How about now?}
 However, our strategy uses a different maximally entangled state,
@@
 so we denote the linear system game by $\LS(\Gamma_r)$.
-\hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$? Or you have any suggestion about a symbol for this group?}
+\hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$?
+Or you have any suggestion about a symbol for this group?} \carl{The notation that you're using seems backwards -- I think we should express the solution group as a function of the linear system, not the other way around.}
 We also prove some properties of the generators of $\Gamma_r$ along the way.

### 2019-05-03 Draft/draft.tex
Honghao: edits of section 1

--- 2019-05-03 Draft/draft.tex
@@
 Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
-delegated computation \cite{ruv2013,cgsv2017} and device independent quantum cryptography
-\cite{qkd2011,qkd2014,miller2016,fu2018,eat2018}.
+delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
+\cite{miller2017,fu2018,eat2018}.
+\hfc{Which DIQKD paper should I cite?}
 
@@
 one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
-pair in parallel \cite{mckague2016, coladan2017parallel}. 
+pair in parallel \cite{mckague2016, coladan2016parallel, lowdegree}. 
 Self-testing general $d$-dimensional EPR pairs is a harder task.
-Proving robustness is harder.
+Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
+by constructing an explicit correlation of size $\Theta(d^2)$ that can be used for self-testing,
+which is the only result about the general $d$-dimensional case so far.
+However, proving the robustness of the correlation remains an open problem. 
+Without robustness, we cannot infer anything about a quantum strategy if
+the produced correlation deviates from the ideal correlation, no matter how small the 
+deviation is.
 

### 2019-05-05 Draft/draft.tex
Honghao: edits to section 1

@@
 
-At a high level, general $d$-dimensional maximally entangled states are self-tested by
-modifying the correlation and enlarging the size of the correlation.
-A natural question to ask is whether maximally entangled state with large local dimension
-can be self-tested with fixed-sized correlation. 
-An equivalent question to ask is whether it is possible to self-test maximally
-entangled state of some local dimension more efficiently, with constant correlation size. 
-In this report, we give an affirmative answer to this question by proving the following theorem.
+A natural question to ask is whether maximally entangled states with large local dimension
+can be self-tested with constant-sized correlations. 
+In this paper, we give an affirmative answer to this question by proving the following theorem.
 \begin{theorem}[Informal]
@@
 	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
-	the maximally entangled state of local dimension $d-1$ can be self-tested 
+	the maximally entangled state of local dimension $4d-4$ can be robustly self-tested 
 	with constant-sized question and answer alphabets.
 \end{theorem}
+The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.
 
 The set $D$ is easily characterizable as it contains all the odd prime numbers with smallest
-primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
-with smallest primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
-To prove \cref{thm:inf}, we give explicit self-testing proof of 
-the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$,$3$, or $5$, 
-by explicitly giving the correlation that achieves self-testing. 
+primitive root $2$, $3$ or $5$. It has been shown that  the set $D$ has infinitely many elements \cite{murty1988}.
+To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r^2)$ for each $d \in D$ whose primitive
+root is $r$. This correlation is denoted by $\fC(d,r)$.
+Note that although the size of $\fC(d,r)$ does not depend on $d$, the entries of $\fC(d,r)$ do.
+Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
+that if some quantum strategy can approximate $\fC(d,r)$, then
+the generalized swap isometry \cite{yang2013}
+can produce the desired maximally entangled states when applied to the unknown state used in the strategy.
 %Then the self-testing property of this correlation is 
@@
 %\end{theorem}
-Our correlation is denoted by $C(\dr{r})$ for prime $d$.
-We use the superscript $(r)$ to denote the primitive root of $d$.
-Note that although the size of $C(\dr{r})$ does not depend on $d$, the optimal correlation does.
-
-In order to accomplish our goal, we introduce new techniques for self-testing.
-First of all, we use a different variant of the weighted CHSH inequality, \hf{which was first introduced in \cite{acin2012}}, to enforce the eigenvalue of
-some unknown operator which is the product of two binary observables used in the weighted CHSH test.
-The variant of the CHSH inequality that we use is not used in the self-testing literature before.
-Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintains
-certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
-\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
-Intuitively, such decomposition can be seen as the inverse of the Jordan's lemma decomposition.
-The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
+
+In order to accomplish our goal, we introduce new techniques for robust self-testing.
+We use a different variant of the weighted CHSH inequality, \hf{which was first introduced in Ref.~\cite{acin2012}
+for studying randomness and entanglement and not used in the self-testing literature before}, 
+to enforce the eigenvalue of the product of two binary observables used in the weighted CHSH test.
+The idea of decompose the unitaries of arbitrary order into binary observables was first introduced by Slofstra \cite{slofstra2017}.
+We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, and
+apply it to self-testing proofs.
+Comparing to the previous approaches, which aim to enforcing eigenvalues of individual operators, our approach
+gives us more flexibility in designing the correlation and easier generalization of our proof techniques. 
+The other contribution is that we prove self-testing without using the anti-commutation relation between Pauli operators,
+or the generalized version of it, 
 which is the core idea in \hf{most of} the previous self-testing results.
 \carl{Are we sure about that ("all")?}
-Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.
+Instead, we find a new relation that should be enforced.
+
+pair of operators that can generate the ring of matrices over complex numbers.
+\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
+\hfc{How about now?}
 
@@
 an extended weighted CHSH test, we introduce the linear system game
-in \cref{sec:lsg} and the extended weighted CHSH test in \cref{sec:chsh}. 
-Our main result is based on the combination of the two tests and presented in \cref{sec:main}.
+in \cref{sec:lsg} and the self-testing properties of the extended weighted CHSH inequality in \cref{sec:chsh}. 
+Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
+In the end, we give the robust self-testing proof in \cref{sec:main}.
 
@@
 \begin{theorem}
+	\label{thm:infty}
 	There exists an infinity-sized set $D$ of prime numbers such that 

### 2019-05-06 Draft/draft.tex
Some changes to section 1 and 6 -- Honghao

@@
 
-In order to accomplish our goal, we introduce new techniques for robust self-testing.
-We use a different variant of the weighted CHSH inequality, \hf{which was first introduced in Ref.~\cite{acin2012}
-for studying randomness and entanglement and not used in the self-testing literature before}, 
-to enforce the eigenvalue of the product of two binary observables used in the weighted CHSH test.
-The idea of decompose the unitaries of arbitrary order into binary observables was first introduced by Slofstra \cite{slofstra2017}.
-We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, and
-apply it to self-testing proofs.
-Comparing to the previous approaches, which aim to enforcing eigenvalues of individual operators, our approach
-gives us more flexibility in designing the correlation and easier generalization of our proof techniques. 
-The other contribution is that we prove self-testing without using the anti-commutation relation between Pauli operators,
-or the generalized version of it, 
-which is the core idea in \hf{most of} the previous self-testing results.
-\carl{Are we sure about that ("all")?}
-Instead, we find a new relation that should be enforced.
-
-pair of operators that can generate the ring of matrices over complex numbers.
+In order to accomplish our goal, we first design a linear system game to enforce the 
+relation $UOU\ct = O^r$, with the inspiration comes from Slofstra \cite{slofstra2017}.
+Unlike previous self-testing proofs, which tries to enforce the anti-commutation relation
+between Pauli operators of dimension $2$, $XZ=-ZX$, or the generalized anti-commutation relation 
+between Pauli operators of higher dimension, $XZ = \omega_d ZX$, the dimension $d$ is implicit in our
+relation. 
+The implication is that the eigenvalues of $O$ are powers of $\omega_d$, for
+some $d$ whose primitive root is $r$, and $U$ only permutes the eigenvectors of $O$. 
+Since winning the linear system game requires that Alice
+and Bob share a state $\ket{\psi}$, which satisfies the condition that 
+$O_A \x O_B \ket{\psi} = \ket{\psi}$, intuitively, we know that 
+$\ket{\psi}$ is spanned by eigenvectors of $O$. 
+The other specialty of the linear system game is that it forces Alice and Bob to have binary observables
+whose products are the speical unitaries $U$ and $O$, because the answers to the questions of the 
+linear system games are binary. 
+The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
+We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
+The fact that Alice and Bob only have binary observables make it easier for us 
+to compose the linear system game with another test, which we call the extended weighted CHSH test.
+The core idea of the extended weighted CHSH test is to certify that Alice and Bob's observables and state 
+for the linear system game can also be used to violate the weighted CHSH inequality \cite{acin2012} maximally.
+We find that the maximal violation of the weighted CHSH inequality can certify the eigenvalues of the product
+of Bob's observables. 
+At this point, we can use the extended weighted CHSH test to certify that
+$O$ has eigenvalue $\omega_d$ and $d$ is prime, then we know $O$ also has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$.
+In the end, we can use the generalized swap isometry \cite{yang2013} to prove our robust self-testing.
+Note that our robust self-testing proof follows a different line of arguments from what was originally
+proposed in Ref.~\cite{yang2013}.
 \carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
@@
 		&\ket{\psi_1} =1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi} \\
-		&\ket{\psi_2} = 1/2(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)  \ket{\psi} \\
-		&\ket{\psi_3} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}\\
-		&\ket{\psi_4} =1/2(N_{\nr+1}^1 + iN_{\nr+2}N_{\nr+1}^1 -iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}
+		%&\ket{\psi_2} = 1/2(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)  \ket{\psi} \\
+		&\ket{\psi_2} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}\\
+		%&\ket{\psi_4} =1/2(N_{\nr+1}^1 + iN_{\nr+2}N_{\nr+1}^1 -iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}
 	\end{align}
@@
 	\begin{align}
-	 \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \sr\qe)} \ket{\psi_3} \text{ and } \ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_4}, \\
-	 \label{eq:psi1_sum} &M_\ast^\diamond \ket{\psi} \appd{O( r\se)} \ket{\psi_1}+\ket{\psi_2}, \\
-	 \label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
-	 \label{eq:psi1_norm} &\norm{\ket{\psi_i}}^2 \appd{O(r\se)} 1/(d-1) \quad \text{ for } i = 1, 2, 3, 4,\\
+	 \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \sr\qe)} \ket{\psi_2},\\ 
+	 %\text{ and } \ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_4}, \\
+	 %\label{eq:psi1_sum} &M_\ast^\diamond \ket{\psi} \appd{O( r\se)} \ket{\psi_1}+\ket{\psi_2}, \\
+	 %\label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
+	 \label{eq:psi1_norm} &\norm{\ket{\psi_i}}^2 \appd{O(r\se)} 1/(d-1) \quad \text{ for } i = 1, 2\\
 	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d\ket{\psi_1},\\
@@
 	The proof of $\ket{\psi_2} \appd{O(\sd \sr \qe)} \ket{\psi_4}$ is similar.
-
-	\textbf{To prove \cref{eq:psi1_sum}}, we use the definition of $\ket{\psi_1}$ and $\ket{\psi_2}$ and get 
-	\begin{align*}
-		\ket{\psi_2} + \ket{\psi_1} = 1/2( 2M_{\nr+1}^0 + 2M_{\nr+1}^1) \ket{\psi} \appd{O(r\se)} M_\ast^\diamond \ket{\psi}.
-	\end{align*}
-
-	\textbf{To prove \cref{eq:psi1_orth}}, we expand the inner product and get 
-	\begin{align*}
-		&\braket{\psi_1}{\psi_2}\\
-	 = &1/4\bra{\psi}(M_{\nr+1}^0 - iM_{\nr+1}^1M_{\nr+2} + iM_{\nr+1}^0M_{\nr+2} +M_{\nr+1}^1)\\
-	 &(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)\ket{\psi}\\
-	 =& 1/2i \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0-M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
-	\end{align*}
-	Then we will show that $\bra{\psi} M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} 0$ as follows
-	\begin{align*}
-	 \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0\ket{\psi} &\appd{O(r\se)}  \bra{\psi}(N_{\nr+1}^0M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
-	  &=\bra{\psi}M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
-	&\appd{O(r^2\ep)} 0,
-	\end{align*}
-	where the last approximation comes from the correlation.
-	Similarly, we have 
-	\begin{align*}
-	\bra{\psi}(M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{O(r\se)} \bra{\psi} M_{\nr+2}N_{\nr+1}^1 \ket{\psi} \appd{O(r^2\ep)} 0.
-	\end{align*}
-	Hence, $\braket{\psi_2}{\psi_1} \appd{O(r\se)} 0$.
 
@@
 	\textbf{To prove \cref{eq:psi1_eig2}},
-	we first show that $M_1M_2 \ket{\psi_3}\appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_3}$, then we 
-	use the fact that $\ket{\psi_3} \appd{O(\sd \sr\qe)} \ket{\psi_1}$ to draw the conclusion.
+	we first show that $M_1M_2 \ket{\psi_2}\appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_2}$, then we 
+	use the fact that $\ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_1}$ to draw the conclusion.
 
@@
 	\begin{align}
-		M_1M_2 \ket{\psi_3} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_3},
-	\end{align}
-	where we use the fact that $\ket{\psi_3} = 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$
-	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \sr\qe)} \ket{\psi_3}$ gives us that 
+		M_1M_2 \ket{\psi_2} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_2},
+	\end{align}
+	where we use the fact that $\ket{\psi_2} = 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$
+	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \sr\qe)} \ket{\psi_2}$ gives us that 
 	\begin{align}

### 2019-05-06 Draft/draft.tex
Honghao: fix grammar and the notation of the linear system game

@@
 
-\title{Constant-sized correlations are sufficient for 
-robust self-testing of maximally entangled states with unbounded dimension}
+\title{Constant-sized correlations are sufficient to 
+robustly self-test maximally entangled states with unbounded dimension}
 
@@
 	\label{prop:inner_pd}
-	Let $\ket{v}$ and $\ket{v'}$ be vectors such that the relation $\ket{v} \appd{\epsilon} \ket{v'}$ holds,
-	then for any unit vector $\ket{u}$,
+	Let $\ket{v}$ and $\ket{v'}$ be vectors such that the relation $\ket{v} \appd{\epsilon} \ket{v'}$ holds.
+	Then for any unit vector $\ket{u}$,
 	\begin{align*}
@@
 	such that 
-	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$,
-	then 
+	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$.
+	Then, 
 	\begin{align*}
@@
 	\end{align*}
-	for some $a > b \in \R$, then
+	for some $a > b \in \R$. Then,
 	\begin{align*}
@@
 	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$,
-	$\norm{\ket{v}} \appd{\ep_2} 1$, and $\braket{u}{v} \geq 1 - \ep_3$,
-	then
+	$\norm{\ket{v}} \appd{\ep_2} 1$, and $\braket{u}{v} \geq 1 - \ep_3$.
+	Then
 	\begin{align*}
@@
 	\begin{align*}
-		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C,
-	\end{align*}
-	then
+		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C.
+	\end{align*}
+	Then,
 	\begin{align*}
@@
 %=======================================
-\section{The linear system game $\LS(\Gamma_r)$}
+\section{The linear system game $\LS(r)$}
 \label{sec:lsg}
@@
 \end{theorem}
-We prove this by constructing the solution group $\Gamma_r$ of the linear system game,
-so we denote the linear system game by $\LS(\Gamma_r)$.
+We prove this by constructing the solution group $\Gamma(\LS_r)$ of the linear system game,
+and we denote the linear system game by $\LS(r)$.
 \hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$?
 Or you have any suggestion about a symbol for this group?} \carl{The notation that you're using seems backwards -- I think we should express the solution group as a function of the linear system, not the other way around.}
-We also prove some properties of the generators of $\Gamma_r$ along the way.
-
-We embed $uou^{-1}= o^r$ into $\Gamma_r$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
+We also prove some properties of the generators of $\Gamma(\LS(r))$ along the way.
+
+We embed $uou^{-1}= o^r$ into $\Gamma(\LS(r))$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
 \begin{definition}	
@@
 $d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
-we are going to embed it into a different set of linear relations in $\Gamma_r$.
+we are going to embed it into a different set of linear relations in $\Gamma(\LS(r))$.
 
@@
 \label{def:gamma}
-The presentation of $\Gamma_r$ has order-$2$ generators:
+The presentation of $\Gamma(\LS(r))$ has order-$2$ generators:
 \begin{align*}
@@
 \end{definition}
-The special properties of the generators of $\Gamma_r$ are summarized in the two propositions below.
+The special properties of the generators of $\Gamma(\LS(r))$ are summarized in the two propositions below.
 \begin{proposition}
-	The group $\Gamma_r$ embeds all the conjugacy relations of $G_1$.
+	The group $\Gamma(\LS(r))$ embeds all the conjugacy relations of $G_1$.
 	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
@@
 \begin{proposition}
-	In the group $\Gamma_r$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
+	In the group $\Gamma(\LS(r))$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
 	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
@@
 %------------------------------------------------------------------------
-\subsection{A representation of $\Gamma_r$}
+\subsection{A representation of $\Gamma(\LS(r))$}
 %------------------------------------------------------------------------
-In this section we give a representation of $\Gamma_r$ which is built upon the representation 
-$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma_r$ to construct the
-ideal strategy of $\LS(\Gamma_r)$.
+In this section we give a representation of $\Gamma(\LS(r))$ which is built upon the representation 
+$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma(\LS(r))$ to construct the
+ideal strategy of $\LS(r)$.
 
@@
 Finally, we follow the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017} to construct the 
-representation of $\Gamma_r$.
+representation of $\Gamma(\LS(r))$.
 \begin{definition}
 \label{def:rep_gamma}
-The representation $\Psi$ of $\Gamma_r$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
+The representation $\Psi$ of $\Gamma(\LS(r))$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
 \begin{itemize}
@@
 \begin{align*}
-	\Psi(k_{i,1}) &= X_{W_2} \x \Psi_1(b_i) = X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_0(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
+	\Psi(k_{i,1}) &= X_{W_2} \x \Psi_1(b_i) \\
+	%= X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_0(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
 	\Psi(k_{i,2}) &= \ketbra{x_1}{x_2} \x \Psi_1(b_if_0) + \ketbra{x_2}{x_1} \x \Psi_1(f_0b_i)\\
-	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_2x_1}+\ketbra{x_2x_1}{x_1x_2})\x\1_{W_{d-1}}\\
-	&+ \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_i)\\ 
+%	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_2x_1}+\ketbra{x_2x_1}{x_1x_2})\x\1_{W_{d-1}}\\
+%	&+ \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_i)\\ 
 	\Psi(k_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_if_0b_i) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
-	&= \ketbra{x_1}{x_1} \x X_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
+	%&= \ketbra{x_1}{x_1} \x X_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
 	\Psi(k_{i,4}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_ic_i) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	&=\ketbra{x_1}{x_1} \x \1_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi(k_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i) \\
-	&=\ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1}) \x \1_{W_{d-1}}\\
-	&+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_0(a_i);
+	%&=\ketbra{x_1}{x_1} \x \1_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi(k_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i) 
+%	&=\ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1}) \x \1_{W_{d-1}}\\
+%	&+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_0(a_i);
 \end{align*}
@@
 \begin{align*}
-	\Psi(k_{l,1}) &= X_{W_2} \x \Psi_1(d_i) = X_{W_2} \x X_{W_2} \x \Psi_0(a_{i}) \\
-	\Psi(k_{l,2}) &= X_{W_2} \x \Psi_1(b_j) = X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
+	\Psi(k_{l,1}) &= X_{W_2} \x \Psi_1(d_i) \\
+	%= X_{W_2} \x X_{W_2} \x \Psi_0(a_{i}) \\
+	\Psi(k_{l,2}) &= X_{W_2} \x \Psi_1(b_j) \\
+	%= X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
 	\Psi(k_{l,3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
-	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_{j}a_{i}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_0(a_i)\\
-	&+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_{i}a_{j}) \\
+%	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_{j}a_{i}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_0(a_i)\\
+%	&+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_{i}a_{j}) \\
 	\Psi(k_{l,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_jd_ib_j) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
-	&= \ketbra{x_1}{x_1} \x (\ketbra{x_2}{x_1} \x \Psi_0(a_ia_j)+ \ketbra{x_1}{x_2} \x \Psi_0(a_ja_i)) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_0(a_i)\\
+	%&= \ketbra{x_1}{x_1} \x (\ketbra{x_2}{x_1} \x \Psi_0(a_ia_j)+ \ketbra{x_1}{x_2} \x \Psi_0(a_ja_i)) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_0(a_i)\\
 	\Psi(k_{l,5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_{k}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi(k_{l,6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k})\\
-	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}}\\
-	 &+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_1(a_{k}).
+	%&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_{k}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi(k_{l,6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k})
+%	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}}\\
+%	 &+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_1(a_{k}).
 \end{align*}
@@
 %==========================
-The full test consists of three subtest: the linear system game $\LS(\Gamma_r)$,
+The full test consists of three subtest: the linear system game $\LS(r)$,
 the extended weighted CHSH test and a commutation test. We explain how the three tests are conducted and
@@
 
-Recall that the the linear system game with solution group $\Gamma_r$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
+Recall that the the linear system game with solution group $\Gamma(\LS(r))$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
 equations labelled by $i \in \{1, 2 \dots \mr\}$.
@@
 define $X_i := \{ \ux : \sum_{k} H(i,k)\ux(k) = \uc(i) \}$ and $I_i = \{ k : H(i,k) = 1\}$.
-From the construction of $\Gamma_r$, we know that $| I_i| \leq 3$.
+From the construction of $\Gamma(\LS(r))$, we know that $| I_i| \leq 3$.
 The correspondence between $\ux$ and the generators of $\Gamma$ is that
@@
 \end{itemize}
-Note that when the referee wants to ask Alice $x = 1,2$, which also labels a variable of $\LS(\Gamma_r)$, 
+Note that when the referee wants to ask Alice $x = 1,2$, which also labels a variable of $\LS(r)$, 
 the referee gives Alice a pair $(i_x. x)$ where 
 $i_x$ labels an equation containing the variable labelled by $x$. 
-For simplicity we omit the $i_x$ part in the alphabet $\calX$, since $\LS(\Gamma_r)$
+For simplicity we omit the $i_x$ part in the alphabet $\calX$, since $\LS(r)$
 forces Alice to use a binary observable strategy.
@@
 In each test case, Alice is given one of two questions.
-One of the possible question is to assign a value to some variable of $\LS(\Gamma_r)$.
+One of the possible question is to assign a value to some variable of $\LS(r)$.
 Again, the equation label is implicit when this variable is given.
@@
 \end{align*}
-The observables for $\LS(\Gamma_r)$ are
+The observables for $\LS(r)$ are
 \begin{align}
@@
 %------------------------------------------------------------------------------------------
-\subsection{Implication of passing $\LS(\Gamma_r)$}
+\subsection{Implication of passing $\LS(r)$}
 \label{sec:imp_lct}
@@
 %-------------------------------------------------------------------------------------------
-The commutation test is introduced to certify the operators used for the Magic Square test (part of $\LS(\Gamma_r)$ and 
+The commutation test is introduced to certify the operators used for the Magic Square test (part of $\LS(r)$ and 
 the operators for the extended weighted CHSH test commute. For the details of the general commutation test, 

### 2019-05-10 Draft/draft.tex
Honghao: going over the draft again with edits and tightened error bounds

@@
 In order to accomplish our goal, we first design a linear system game to enforce the 
-relation $UOU\ct = O^r$, with the inspiration comes from Slofstra \cite{slofstra2017}.
-Unlike previous self-testing proofs, which tries to enforce the anti-commutation relation
-between Pauli operators of dimension $2$, $XZ=-ZX$, or the generalized anti-commutation relation 
-between Pauli operators of higher dimension, $XZ = \omega_d ZX$, the dimension $d$ is implicit in our
-relation. 
-The implication is that the eigenvalues of $O$ are powers of $\omega_d$, for
-some $d$ whose primitive root is $r$, and $U$ only permutes the eigenvectors of $O$. 
-Since winning the linear system game requires that Alice
-and Bob share a state $\ket{\psi}$, which satisfies the condition that 
-$O_A \x O_B \ket{\psi} = \ket{\psi}$, intuitively, we know that 
-$\ket{\psi}$ is spanned by eigenvectors of $O$. 
-The other specialty of the linear system game is that it forces Alice and Bob to have binary observables
-whose products are the speical unitaries $U$ and $O$, because the answers to the questions of the 
+relation $UOU\ct = O^r$, which is a generalization of a relation in Ref.~\cite{slofstra2017}.
+The number of variables and the number of equations of the linear system game depend linearly on $r$,
+which makes our correlation of size $\Theta(r^2)$.
+Unlike previous self-testing proofs, which try to enforce the anti-commutation relation
+$XZ = \omega_d^{-1} ZX$ between Pauli operators of dimension $d \geq 2$, 
+our approach is more succinct in terms of the size of the correlation but at a cost that
+it only works for odd prime $d$.
+The reason why we focus on this relation is that if we can certify that $O$ has one eigenvalue $\omega_d$
+for some $d$ with primitive $r$,
+then it guarantees that $O$ has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$ and $U$ only
+permutes the eigenvectors of $O$ in certain way.
+After knowing the eigenvalues of $O$, we can use infer the structure of the shared state $\ket{\psi}$
+based on the two relation of $\ket{\psi}$ imposed by the linear system game --
+$U_A \x U_B \ket{\psi} = \ket{\psi}$ and $O_A \x O_B \ket{\psi} = \ket{\psi}$.
+The two relations imply that $\ket{\psi}$ is spanned by eigenvectors of $O$ and its
+Schmidt coefficient follows some pattern that is invariant under the permutation by $U$.
+At this point, we can use the generalized swap isometry \cite{yang2013} to extract a copy of the 
+$(d-1)$-dimensional maximally entangled state. Note that our robust self-testing proof 
+follows a different line of arguments from what was originally
+proposed in Ref.~\cite{yang2013}.
+Our self-testing proof actually certifies $\ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}$. 
+The self-testing of $\ket{\EPR{2}}^{\x 2}$ follows a known result \cite{wu2016}.
+
+The remaining question is how to certify a particular eigenvalue of $O$. Before going to the answer,
+we remark that 
+the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
+whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
 linear system games are binary. 
@@
 The fact that Alice and Bob only have binary observables make it easier for us 
-to compose the linear system game with another test, which we call the extended weighted CHSH test.
+to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
+The difference between a nonlocal game and a nonlocal test will be discussed later.
 The core idea of the extended weighted CHSH test is to certify that Alice and Bob's observables and state 
@@
 of Bob's observables. 
-At this point, we can use the extended weighted CHSH test to certify that
-$O$ has eigenvalue $\omega_d$ and $d$ is prime, then we know $O$ also has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$.
-In the end, we can use the generalized swap isometry \cite{yang2013} to prove our robust self-testing.
-Note that our robust self-testing proof follows a different line of arguments from what was originally
-proposed in Ref.~\cite{yang2013}.
+At this point, we fix a prime $d$ by picking the weight in the weighted CHSH inequality and 
+use the extended weighted CHSH test to certify that
+$O$ has eigenvalue $\omega_d$.
 \carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
@@
 Operators defined by the projectors follow the same convention, for example, $M_x := M_x^0 - M_x^1$.
+If we add tilde to an operator, then this operator is fully characterized and belongs to some ideal strategy.
+Otherwise, the operator is general and the only assumption is that it is finite-dimensional.
 
@@
 \label{prop:orthog}
-	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with norm less or equal to $1$
+	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors
 	such that
@@
 	\begin{align*}
-		\norm{\braket{u}{v}} \leq \frac{\ep_1+\ep_2}{a-b}.
+		\norm{\braket{u}{v}} \leq \max(\norm{\ket{u}}, \norm{\ket{v}})\frac{\ep_1+\ep_2}{a-b}.
 	\end{align*}
@@
 		\norm{\ket{u}}\norm{\ket{v'}}}{a-b} 
-		\leq \frac{\ep_1+\ep_2}{a-b}.
+		\leq \max(\norm{\ket{u}}, \norm{\ket{v}})\frac{\ep_1+\ep_2}{a-b}.
 	\end{align*}
@@
 into a linear system game such that the relations in the definition of $K$ can be derived from the
-combination of the linear equations. Then he showed the difference between exact representations
+combination of the linear equations. Then he shows the difference between exact representations
 and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
@@
 $
-for some $r \in \N$ into a linear system game.}
+for some $r \in \N$ into a linear system game, denoted by $\LS(r)$.}
 
@@
 \begin{theorem}
-	The relation $uou^{-1} = o^r$ can be embedded in a linear system game which has
+	The relation $uou^{-1} = o^r$ can be embedded in a binary linear system game which has
 	$n(r) := 18r+85$ variables and $m(r) := 17r + 77$ equations, where each equation has $3$ variables.
 \end{theorem}
-We prove this by constructing the solution group $\Gamma(\LS_r)$ of the linear system game,
-and we denote the linear system game by $\LS(r)$.
+We prove this by constructing the solution group $\Gamma(\LS(r))$ of the linear system game.
 \hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$?
@@
 	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above and
-	proves the $j=1$ case.
+	prove the $j=1$ case.
 
@@
 \begin{align*}
-	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f, g, \{h_{jk}\}_{(i,j,k) \in C(r)};
+	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f_0, g_0, \{h_{jk}\}_{(i,j,k) \in C(r)};
 \end{align*}
@@
 \begin{align*}
-	&a_i = b_ic_i = fd_i = gv_i,&& fb_if =c_i &&\text{ for } i= 1 \dots r+5 \\
+	&a_i = b_ic_i = f_0d_i = g_0v_i,&& f_0b_if_0 =c_i &&\text{ for } i= 1 \dots r+5 \\
 	&h_{jk}b_j c_k = e,&& d_ib_jd_i = c_k &&\text{ for all } (i,j,k) \in C(r).
@@
 Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
-We introduce the generator $g$ so that later we can associate $f$ with $g$ in linear relations of the Magic Square game.
+We introduce the generator $g_0$ so that later we can associate $f_0$ with $g_0$ in linear relations of the Magic Square game.
 Such relations are important for the self-testing proof.
@@
 	\begin{align*}
-		d_i c_j d_i = d_i (f b_j f) d_i = f (d_i b_j d_i) f = f c_k f = b_k.
+		d_i c_j d_i = d_i (f_0 b_j f_0) d_i = f_0 (d_i b_j d_i) f_0 = f_0 c_k f_0 = b_k.
 	\end{align*}
@@
 	\begin{align*}
-		a_i a_j a_i = f d_i b_j c_j f d_i = (f d_i b_j d_i f)(f d_i c_j d_i f) = (f c_k f)(f b_k f) = b_k c_k = a_k. 
+		a_i a_j a_i = f_0 d_i b_j c_j f_0 d_i = (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) = (f_0 c_k f_0)(f_0 b_k f_0) = b_k c_k = a_k. 
 	\end{align*}
@@
 \begin{proposition}
-	In the group $G_1$, the generators $f$ and $g$ commute with $a_i$ for all $i = 1 \dots r+5$.
+	In the group $G_1$, the generators $f_0$ and $g_0$ commute with $a_i$ for all $i = 1 \dots r+5$.
 \end{proposition}
@@
 	\begin{align*}
-		fa_i f a_i = d_i d_i = e && g a_i g a_i = v_i v_i  = e,
+		f_0a_i f_0 a_i = d_i d_i = e && g_0 a_i g_0 a_i = v_i v_i  = e,
 	\end{align*}
@@
 \end{definition}
-The special properties of the generators of $\Gamma(\LS(r))$ are summarized in the two propositions below.
+Note that $\Gamma(\LS(r))$ has all the generators of $G_1$ but all the conjugacy relations 
+from $G_1$ are broken into linear relations.
+Formal statements of the properties of $\Gamma(\LS(r))$ are summarized in the two propositions below.
 \begin{proposition}
@@
 \end{align}
+The basis of $W_{d-1}$ is the eigenbasis of an operator $O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}$.
 Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
-modulo $d$ implicitly. We use the second form of the basis when it is convenient.
+modulo $d$ implicitly,
+because another form of $O$ is $\sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}$.
+We use the second form of the basis when it is convenient.
 We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
@@
 can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
-conjugation relations.
+conjugacy relations.
 \end{definition}
@@
 \end{align*}
-\item for the generators involved in the Magic square test
+\item for the generators involved in the Magic square game
 \begin{align*}
@@
 \end{definition}
-The validation of $\Psi_1$ and $\Psi$ are done in Slofstra's work \cite{slofstra2017}.
+The validation of $\Psi_1$ and $\Psi$ are done in the proofs of Lemma $4.4$ and Proposition $4.2$ in Ref.~\cite{slofstra2017}.
 
@@
 \label{thm:selftest}
-	Suppose the quantum strategy $(\ket{\psi}, \{M_x:=M_x^0-M_x^1\}_{x=1,2}, \{N_y :=N_y^0-N_y^1\}_{y = 1,2} )$ achieves that
-	$\ip{\I_\alpha} \geq 2\sqrt{1+\alpha^2} - \epsilon$
-	for some $\epsilon > 0$, then we define $\mu := \arctan(1/\alpha)$ and
+    Define $\mu := \arctan(1/\alpha)$.
+	If a quantum strategy $(\ket{\psi}, \{M_x:=M_x^0-M_x^1\}_{x=1,2}, \{N_y :=N_y^0-N_y^1\}_{y = 1,2} )$ achieves that
+	$\ip{\I_\alpha} \geq \ip{\I_\alpha}_{\max} - \epsilon$
+	for some $\epsilon > 0$, then
 	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
@@
 	to be clearer about what label you are using for Alice's and Bob's systems (see my previous comment on this).}
+	\hfc{This problem should be fixed now.}
 \end{theorem}
@@
 %==========================
-The full test consists of three subtest: the linear system game $\LS(r)$,
+The full test consists of three tests: the linear system game $\LS(r)$,
 the extended weighted CHSH test and a commutation test. We explain how the three tests are conducted and
@@
 equations labelled by $i \in \{1, 2 \dots \mr\}$.
-We denote the associated linear system by $H\underline{x} = \uc$ and
-define $X_i := \{ \ux : \sum_{k} H(i,k)\ux(k) = \uc(i) \}$ and $I_i = \{ k : H(i,k) = 1\}$.
-From the construction of $\Gamma(\LS(r))$, we know that $| I_i| \leq 3$.
-The correspondence between $\ux$ and the generators of $\Gamma$ is that
+We denote the associated linear system by $H\ux = \uc$ and
+define $X_i := \{ \ux : \sum_{k} H(i,k)\ux(k) = \uc(i) \}$, which is the answer set of equation $i$,
+and $I_i = \{ k : H(i,k) = 1\}$, which is the set of all the nonzero coefficient of equation $i$.
+From the construction of $\Gamma(\LS(r))$, we know that $| I_i| = 3$ for all $i$.
+The correspondence between $\ux$ and the generators of $\Gamma(\LS(r))$ is that
 \begin{align*}
@@
 We conduct the linear constraint test in a way such that Bob is always get a variable label
-but Alice gets either an equation label, in which case she needs to give the full assignment to this equation,
+but Alice gets either an equation label, in which case she needs to give the full assignment to the given equation,
 or a pair of equation label and variable label, in which case she only needs to give the assignment to the particular 
-variable in the given equation. In this way, we force Alice and Bob to use an binary observable strategy for the linear constraint 
-test.
+variable in the given equation. In this way, we force Alice and Bob to use an binary observable strategy 
+for the linear system game.
 
@@
 \{(x,y)\}_{x=y \in \{\nr+1, \nr+2\}} \cup
-\{(x,y)\}_{x = y \in \{1, 2\}} \cup \{(x,y)\}_{x = 1,2, y =\nr+1, \nr+2} \cup  \{(x,y)\}_{x = \nr+1,\nr+2, y =1, 2}$.
+\{(x,y)\}_{x = 1,2, y =\nr+1, \nr+2} \cup  \{(x,y)\}_{x = \nr+1,\nr+2, y =1, 2}$.
 %the input alphabets are $\calX = \calY = \{\ast, 1, 2, \nr+1,\nr+2\}$.
@@
 $i_x$ labels an equation containing the variable labelled by $x$. 
-For simplicity we omit the $i_x$ part in the alphabet $\calX$, since $\LS(r)$
-forces Alice to use a binary observable strategy.
+For simplicity we omit the $i_x$ part in the alphabet $\calX$.
 Later we will show that the $i_x$ part can be made implicit.
@@
 	\item if $x = y = \ast$, Alice and Bob should answer with $a = b \in \{\diamond, \perp\}$;
-	\item if $x = y \in \{1,2\}$, Alice and Bob should answer with $a = b \in \{0, 1\}$, as in the linear constraint test;
 	\item if $x = y \in \{n+1, n+2\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
@@
 
-In the commutation test, 
+Our commutation test is slightly different from the one used in Ref.~\cite{coladan2017verifier}.
+The commutation relations that we test are
+\begin{align*}
+    [M_{\nr+1}, M_j] = [M_{\nr+2}, M_j] = \1,
+\end{align*}
+where $j = r+6, r+8, r+9, r+11$.
+The difference is that we will examine the probability distribution 
+generated by this test and conclude that $M_{\nr+1}^0$ and $M_{\nr+1}^1$ commute with
+$M_j$ for $j = r+6, r+8, r+9, r+11$.
 we reuse questions from the two other tests so the answer
 set for each question is the same across the tests.
-There are $8$ test cases.
-In each test case, Alice is given one of two questions.
-One of the possible question is to assign a value to some variable of $\LS(r)$.
-Again, the equation label is implicit when this variable is given.
-The other possibility is to answer $\nr+1$ or $\nr+2$ from the extended weighted CHSH test.
+There are $8$ test cases, one for each commutation relation.
+In each test case, Alice is given one of the two questions involved.
+If her question is to assign a value to some variable of $\LS(r)$,
+the equation label is implicit.
 Bob is given both of the question so he needs to give answers to both questions.
 Their answers should agree on the question that is given to both.
-The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
-Alice's input is determined by the pair so she receives one of the two questions of a given pair with equal probability.
-
-In the full test, the question pairs from the three subtests are given to Alice and Bob with equal probability.
-The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first.
+%The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
+%Alice's input is determined by the pair so she receives one of the two questions of a given pair with equal probability.
+
+In the full test, the question pairs from the three sub-tests are given to Alice and Bob with equal probability.
+The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three sub-tests. We give the ideal strategy first and then $\fC(d,r)$.
 %--------------------------------------------
@@
 \begin{align*}
-\ket{\psi} = &\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
+\ket{\tpsi} = &\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
 =&\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
@@
 \begin{align*}
-	&M_\ast^\diamond =(\1_{W_2})^{\x 2} \x \Pi_V && M_\ast^\perp = M_{n+1}^\perp = M_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
-	&N_\ast^\diamond = (\1_{W_2})^{\x 2} \x \Pi_V && N_\ast^\perp = N_{n+1}^\perp = N_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
-	&M_{n+1}^0 =N_{n+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && M_{n+1}^1=N_{n+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
-	&M_{n+2}^0 =N_{n+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1_{\times}}{1_{\times}} && M_{n+2}^1= N_{n+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_{\times}}{(d-1)_{\times}}\\
-	&M_1^0 = N_1^0 =(\1_{W_2})^{\x 2} \x  \ketbra{1_+}{1_+} && M_1^1 = N_1^1 =(\1_{W_2})^{\x 2} \x  \ketbra{(d-1)_+}{(d-1)_+}\\
-	&M_2^0 = N_2^0 = (\1_{W_2})^{\x 2} \x \ketbra{1_-}{1_-} && M_1^1 = N_1^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_-}{(d-1)_-}.
+	&\tM_\ast^\diamond =(\1_{W_2})^{\x 2} \x \Pi_V && \tM_\ast^\perp = \tM_{\nr+1}^\perp = \tM_{\nr+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
+	&\tN_\ast^\diamond = (\1_{W_2})^{\x 2} \x \Pi_V && \tN_\ast^\perp = \tN_{\nr+1}^\perp = \tN_{\nr+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
+	&\tM_{\nr+1}^0 =\tN_{\nr+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && \tM_{\nr+1}^1=\tN_{\nr+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
+	&\tM_{\nr+2}^0 =\tN_{\nr+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1_{\times}}{1_{\times}} && \tM_{\nr+2}^1= \tN_{\nr+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_{\times}}{(d-1)_{\times}}.
 \end{align*}
@@
 \begin{align}
-	M_i = N_i = \Psi(x_i),
+	\tM_i = \tN_i = \Psi(x_i),
 \end{align}
@@
 Note that Alice uses the same observable for the same variable appearing in different equations.
+In particular, the action of $\tM_1, \tN_1$ and $\tM_2, \tN_2$ on the subspace $V$ can be expressed as
+\begin{align*}
+	&\tM_1^0 = \tN_1^0 =  \ketbra{1_+}{1_+} && \tM_1^1 = \tN_1^1 =  \ketbra{(d-1)_+}{(d-1)_+}\\
+	&\tM_2^0 = \tN_2^0 =  \ketbra{1_-}{1_-} && \tM_1^1 = \tN_1^1 =  \ketbra{(d-1)_-}{(d-1)_-}.
+\end{align*}
 
@@
 \begin{proposition}
-Let $M_1 = N_1 :=\Psi(a_1)$, $M_2 = N_2 := \Psi(a_2)$, $M_3 = N_3 := \Psi(a_3)$
-and $M_4 = N_4 := \Psi(a_4)$, then
-\begin{align}
-	\label{eq:mn_preserve} &M_i N_i \ket{\psi} = \ket{\psi} && \text{for } i = 1 \dots 4,\\
-	\label{eq:o2_comm} &(M_3M_4)M_2(M_4M_3) = M_2,
-\end{align}
-and similar commutation relation holds on Bob's side too.
+The observables $\tM_1 = \tN_1 :=\Psi(a_1)$, $\tM_2 = \tN_2 := \Psi(a_2)$, $\tM_3 = \tN_3 := \Psi(a_3)$
+and $\tM_4 = \tN_4 := \Psi(a_4)$ satisfy the relations
+\begin{align}
+	\label{eq:mn_preserve} &\tM_i \tN_i \ket{\psi} = \ket{\psi} && \text{for } i = 1 \dots 4,\\
+	\label{eq:o2_comm} &(\tM_3\tM_4)\tM_2(\tM_4\tM_3) = \tM_2,
+\end{align}
+and similar commutation relations on Bob's side.
 \end{proposition}
@@
 	Since all the operators involved in this proposition act trivially on $W_2^{\x 2}$, we focus on
-	their actions on $W_{d-1}$. In the later proof, by $\ket{\psi}$ we mean the part of $\ket{\psi}$ on $W_{d-1}$.
+	their actions on $W_{d-1}$. In the later proof, by $\ket{\tpsi}$ we mean the part of $\ket{\tpsi}$ on $W_{d-1}$.
 
@@
 	\begin{align*}
-		&M_1M_2= \sum_{j=1}^{d-1} \omega_d^{j} \ketbra{x_j}{x_j},
-		&&M_3M_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
+		&\tM_1\tM_2= \sum_{j=1}^{d-1} \omega_d^{j} \ketbra{x_j}{x_j},
+		&&\tM_3\tM_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
 	\end{align*}
@@
 	\begin{align*}
-		M_3M_4 M_2 M_4 M_3 = &\sum_{j=0}^{(d-3)/2} M_3M_4 (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) M_4M_3\\
-		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}} = M_2.
-	\end{align*}
-
-	Next we prove \cref{eq:mn_preserve}. It is straightforward to see that $M_iN_i \ket{\psi} = \ket{\psi}$ for $i = 1,2$.
-	Before checking $i=3$ and $i=4$, we first observe that
-	\begin{align*}
-		M_3M_4 N_3 N_4 \ket{\psi} = \ket{\psi}.
-	\end{align*}
-	The eigenvectors of $M_3M_4$ and $N_3N_4$ are 
+		\tM_3\tM_4 \tM_2 \tM_4 \tM_3 = &\sum_{j=0}^{(d-3)/2} M_3M_4 (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) M_4M_3\\
+		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}} = \tM_2.
+	\end{align*}
+
+	Next we prove \cref{eq:mn_preserve}. It is straightforward to see that $\tM_i\tN_i \ket{\tpsi} = \ket{\tpsi}$ for $i = 1,2$.
+	Before checking the two cases $i=3$ and $i=4$, we first observe that
+	\begin{align*}
+		\tM_3\tM_4 \tN_3 \tN_4 \ket{\tpsi} = \ket{\tpsi}.
+	\end{align*}
+	The eigenvectors of $\tM_3\tM_4$ and $\tN_3\tN_4$ are 
         \begin{align*}
@@
         \end{align*}
-        Then $M_4$ acts on $\ket{x_{r^j}}$ by
-        \begin{align*}
-        		M_4 \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} M_4\left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
+        Then $\tM_4$ acts on $\ket{x_{r^j}}$ by
+        \begin{align*}
+        		\tM_4 \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} M_4\left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
         	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
@@
         \end{align*}
-        Then we show that $M_4  N_4 \ket{\psi} = \ket{\psi}$ as 
-        \begin{align*}
-        	M_4 N_4 \ket{\psi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} M_4  N_4 \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
+        Then we can show that $\tM_4  \tN_4 \ket{\tpsi} = \ket{\tpsi}$ because 
+        \begin{align*}
+        	\tM_4 \tN_4 \ket{\tpsi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \tM_4  \tN_4 \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
         	= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\psi},
         \end{align*}
-	Combining it with the fact that $M_3M_4 N_3N_4 \ket{\psi} = \ket{\psi}$, we can conclude that
-	$M_3N_3 \ket{\psi} = \ket{\psi}$.
+	Combining it with the fact that $\tM_3\tM_4 \tN_3\tN_4 \ket{\tpsi} = \ket{\tpsi}$, we can conclude that
+	$\tM_3\tN_3 \ket{\tpsi} = \ket{\tpsi}$.
 \end{proof}
-The similar result, i.e., $M_jN_j \ket{\psi} = \ket{\psi}$ for $j = 1 \dots \nr$, are easy to check because all the other observables are defined by $M_j, N_j$ for $j=1,2,3,4$.
-An interesting property of $U_A := M_3M_4$ and $O_A := M_1M_2$ is summarized in the proposition below. 
+The similar result, i.e., $\tM_j\tN_j \ket{\tpsi} = \ket{\tpsi}$ for $j = 1 \dots \nr$, are easy to check because all the other observables are defined by $\tM_j, \tN_j$ for $j=1,2,3,4$.
+An interesting property of $U_A := \tM_3\tM_4$ and $O_A := \tM_1\tM_2$ is summarized in the proposition below. 
 \begin{lemma}
@@
 Our self-test argument certifies that Alice and Bob has such $O$ and $U$ in their hands, so
-it provides another angle to justify our self-testing argument.
+this proposition provides another angle to justify our self-testing argument.
 
@@
 of $\fC(d,r)$, then
-$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$, for all $(a,b,x,y)$.
+\begin{align*}
+    \pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy},
+\end{align*}
+for all $(a,b,x,y)$.
 
@@
 %------------------------------------------------------------------------------------------
-\subsection{Implication of passing $\LS(r)$}
+\subsection{Implication of winning $\LS(r)$}
 \label{sec:imp_lct}
 %------------------------------------------------------------------------------------------
-In this subsection, we use $(i,j)$ to denote the question pair so that Alice gets equation number $i$, sometimes with a variable label $j$,
- and Bob gets a variable label $j$.
+In this subsection, we use $(i,j)$ to denote the question pair so that Alice gets equation number $i$, 
+sometimes with a variable label $j$, and Bob gets a variable label $j$.
 The way we conduct the linear constraint test forces Alice to have binary observables $\{M_{ij}\}$ that satisfy 
@@
 	\label{prop:lct_base}
-	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$,
-	then there exist binary observables $\{ M_j \}_{j=1}^{\nr} $, such that
+	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$.
+	Then there exist binary observables $\{ M_j \}_{j=1}^{\nr} $, such that
 	\begin{align}
@@
 \begin{proof}
-The condition that $\tpr{\ux b}{ij}$ from $\fC(d,r)$ wins the linear system game optimally is equivalent to
+The condition that $(\tpr{\ux b}{ij})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
 \begin{align*}
@@
 
-Following the steps of the embedding of $(a_3a_4)^l a_1a_2(a_4a_3)^l = (a_1a_2)^{r^l}$ into $\Gamma_r$,
-we can get the following proposition.
+Following the steps of the embedding of $(a_3a_4)^l a_1a_2(a_4a_3)^l = (a_1a_2)^{r^l}$ into $\Gamma(\LS(r))$,
+we can prove the following proposition.
 \begin{proposition}
@@
 Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $\{M_j, N_j\}_{j \in \nr}$ be the observables defined in 
-\cref{prop:lct_base}, 
-then
+\cref{prop:lct_base}. 
+Then,
 \begin{align}
@@
 \begin{proof}
-The $l = 1$ case follows from the fact that the linear system game embeds $O(r)$ conjugacy relations and 
+The $l = 1$ case follows from the fact that $\Gamma(\LS(r))$ embeds $O(r)$ conjugacy relations and 
 all the $O(r)$ conjugacy relations are used in the derivation of $(a_3a_4)a_1a_2(a_4a_3) = (a_1a_2)^r$, so we 
@@
 	&\appd{O(r\se)} (M_4M_3)^n (M_1M_2)^{r^n} (M_4M_3) \ket{\psi} \\
-	& \appd{O(r^{n+1} \se)} (M_4M_3)^{n+1} (M_1M_2)^{r^{n+1}} \ket{\psi},
+	& \appd{O(r^{n+2} \se)} (M_4M_3)^{n+1} (M_1M_2)^{r^{n+1}} \ket{\psi},
 \end{align*}
 where from the second to the last line we repeat the process of applying \cref{eq:ls_comm_rel} 
-and the relation $M_1M_2 \ket{\psi} \appd{O(r\se)} N_1N_2 \ket{\psi}$, $r^n$ times.
+and the relation $(M_1M_2)^r \ket{\psi} \appd{O(r^2\se)} (N_1N_2)^r \ket{\psi}$, $r^n$ times.
 In summary, we have 
 \begin{align}
-	M_1M_2(M_4M_3)^{n+1} \ket{\psi} \appd{O(r^{n+2} \se)} (M_4M_3)^{n+1} (M_1M_2)^{r^{n+1}}\ket{\psi},
-\end{align}
-because $O(r^{n+1} \se)+O(r^{n+1}\se) = O(r^{n+2} \se)$.
+	M_1M_2(M_4M_3)^{n+1} \ket{\psi} \appd{O(r^{n+2} \se)} (M_4M_3)^{n+1} (M_1M_2)^{r^{n+1}}\ket{\psi}.
+\end{align}
 By the principal of proof by induction, the proof is complete.
@@
 
-Recall $O_A = M_1M_2$ and $U_A=M_3M_4$, then
+Recall that we define $O_A = M_1M_2$ and $U_A=M_3M_4$, then
 the conclusion of \cref{prop:lct_adv} can be rewritten as 
 \begin{align*}
-	U_A^n O_A (U_A\ct)^n \ket{\psi} \appd{O(r^{n+1} \se)} O_A^{r^n} \ket{\psi}.
+	 O_A (U_A\ct)^n \ket{\psi} \appd{O(r^{n+1} \se)} (U_A\ct)^n O_A^{r^n} \ket{\psi}.
 \end{align*}
 On Bob's side, we also define $O_B = N_1N_2$ and $U_B = N_3N_4$ 
-and similar relations hold.
+and the similar relation holds.
 
@@
 	\label{prop:lct_comm}
-	Let $S$, $\{M_j, N_j\}_{j=1}^{\nr}$ be the strategy and observables defined in \cref{prop:lct_base},
-	then
+	Let $S$, $\{M_j, N_j\}_{j=1}^{\nr}$ be the strategy and observables defined in \cref{prop:lct_base}.
+	Then,
 	\begin{align}
@@
 	\begin{align}
-		&M_{r+6}M_{r+9} \ket{\psi} \appd{O(r\se)} - M_{r+9}M_{r+6} \ket{\psi} \\
+		&M_{r+6}M_{r+9} \ket{\psi} \appd{O(r\se)} -M_{r+9}M_{r+6} \ket{\psi} \\
 		&M_{r+8}M_{r+11} \ket{\psi} \appd{O(r\se)} -M_{r+11}M_{r+8} \ket{\psi}.
@@
 \end{proposition}
-Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma_r$,
-so this proposition can be proved using the same technique used in the proof of \cref{prop:lct_base}.
+Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma(\LS(r))$,
+so this proposition can be proved with the same techniques used in the proof of \cref{prop:lct_base}.
 %------------------------------------------------------------------------------------------
@@
 \label{prop:chsh_base}
-Let $S$ be an $\ep$-approximate quantum strategy of $\fC(d,r)$,
-then the strategy $S$ satisfy the following relations
-\begin{align}
+Let $S$ be an $\ep$-approximate quantum strategy of $\fC(d,r)$.
+Then the strategy $S$ satisfies the following relations
+\begin{align*}
 	  M_\ast^\diamond N_\ast^\diamond \ket{\psi}
-	  \appd{O( r\se)}&M_\ast^\diamond \ket{\psi} \appd{O( r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
-	  \appd{O( r\se)}&N_\ast^\diamond \ket{\psi} \appd{O( r\se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
-	M_\ast^\perp N_\ast^\perp\ket{\psi}\appd{O( r\se)} &M_\ast^\perp\ket{\psi} \appd{O( r\se)} M_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} M_{\nr+2}^\perp \ket{\psi}\\
-	\appd{O( r\se)}&N_\ast^\perp\ket{\psi} \appd{O( r\se)} N_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} N_{\nr+2}^\perp \ket{\psi}.
-\end{align}
+	  &\appd{O( r\se)}M_\ast^\diamond \ket{\psi}\\
+	  &\appd{O( r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi}\\
+	  &\appd{O( r\se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
+	  &\appd{O( r\se)} N_\ast^\diamond \ket{\psi}\\
+	  &\appd{O( r\se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi}\\
+	  &\appd{O( r\se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
+	M_\ast^\perp N_\ast^\perp\ket{\psi}&\appd{O( r\se)} M_\ast^\perp\ket{\psi}\\
+	&\appd{O( r\se)} M_{\nr+1}^\perp \ket{\psi}\\
+	&\appd{O( r\se)} M_{\nr+2}^\perp \ket{\psi}\\
+	&\appd{O( r\se)} N_\ast^\perp\ket{\psi}\\
+	&\appd{O( r\se)} N_{\nr+1}^\perp \ket{\psi}\\
+	&\appd{O( r\se)} N_{\nr+2}^\perp \ket{\psi},
+\end{align*}
 and
-\begin{align}
+\begin{align*}
 &M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+1}^0 \ket{\psi} && M_{\nr+1}^1\ket{\psi} \appd{O( r\se)} N_{\nr+1}^1 \ket{\psi}\\
 &M_{\nr+2}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+2}^0 \ket{\psi} && M_{\nr+2}^1\ket{\psi} \appd{O( r\se)} N_{\nr+2}^1 \ket{\psi}.
-\end{align}
+\end{align*}
 \end{proposition}
@@
 \begin{proof} 
+We prove $(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\se)} N_\ast^\diamond \ket{\psi}$ as an example.
+The rest of the relations follow the same line of argument.
+
 Recall that the implication of $S$ being an $\ep$-approximate strategy is that 
-$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$. 
-We prove $(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\se)} N_\ast^\diamond \ket{\psi}$ as an example.
-The rest of the relations follow the same line of arguments.
+$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$ for all question and answer pairs $(x,y)$ and $(a,b)$.
 From the correlation, we can observe that
@@
 	\end{align}
-	Then $S$ induces two strategies that achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, which are
+	Then $S$ induces two $O(d r\se)$-approximate strategies of the ideal correlation that achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$, which are
 	\begin{align}
@@
 where we use the facts that $M_\ast^\perp \ket{\psi} \appd{O(r\se)} M_x^\perp \ket{\psi}$ and that 
-$\supp(M_x^0) \cap \supp(M_x^\perp) = \emptyset$ for the relevant values of $(x,y,a,b)$.
+$M_x^0 M_x^\perp = 0$ for the relevant values of $(x,y,a,b)$.
 This means that if Alice and Bob share state $M_\ast^\diamond \ket{\psi}/\norm{M_\ast^\diamond \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
@@
 Using the fact that $O(d r \se)$ dominates $O(dr^2 \ep)$,
-we can prove that the correlation generated by $S_1$ 
-is $O(dr\se)$-close to the ideal correlation that achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$.
-Hence, the strategy $S_1$ achieves the value $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r \se)$.
+we can prove that $S_1$ is an $O(dr\se)$-approximate strategy of the ideal correlation that achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$.
 The proof for $S_2$ is very similar so we omit it here.
@@
 Based on \cref{prop:chsh_base,prop:s1s2}, we identify a special component of $\ket{\psi}$, whose special properties are summarized
-in the proposition below. In the next lemma, we establish that this special component can be used to approximate $\ket{\psi}$. 
+in the proposition below. In the next lemma, we prove that this special component can be used to approximate $\ket{\psi}$. 
 \begin{proposition}
+    \label{prop:psi1}
 	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.
-	We also define
-	\begin{align}
-		&\ket{\psi_1} =1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi} \\
+	Then, the state
+	\begin{align}
+		&\ket{\psi_1} =1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi}.
 		%&\ket{\psi_2} = 1/2(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)  \ket{\psi} \\
-		&\ket{\psi_2} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}\\
 		%&\ket{\psi_4} =1/2(N_{\nr+1}^1 + iN_{\nr+2}N_{\nr+1}^1 -iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}
 	\end{align}
-	then
-	\begin{align}
-	 \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \sr\qe)} \ket{\psi_2},\\ 
+	satisfies the following properties
+	\begin{align}
 	 %\text{ and } \ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_4}, \\
@@
 	 %\label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
-	 \label{eq:psi1_norm} &\norm{\ket{\psi_i}}^2 \appd{O(r\se)} 1/(d-1) \quad \text{ for } i = 1, 2\\
+	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(r\se)} 1/(d-1),\\
 	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d\ket{\psi_1},\\
@@
 \begin{proof}
-	We prove \cref{eq:psi1_eq} to \cref{eq:psi1_eig2} one by one.
-
-	\textbf{To prove \cref{eq:psi1_eq}}, 
-	recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^0 \ket{\psi}$ 
-	and $M_{\nr+1}^1 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^1 \ket{\psi}$ proved in \cref{prop:chsh_base},
-	so it suffices to show
-	$(M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}$ is close to $(- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}$,
-%	or equivalently,
-%	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
-	At this point, we can use the anti-commutation relation induced by $S_1$ (\cref{eq:zaxa}) and conclude that 
-	\begin{align*}
-		M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^\diamond\ket{\psi}}}}{c\sqrt{s}}O(\sd\sr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}.
-	\end{align*}
-	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \sr \qe)$.
-	Then we can show that 
-	\begin{align*}
-		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \\
-			&\appd{O(r\se)} M_{\nr+2}M_{\nr+1} M_\ast^\diamond \ket{\psi} \\
-			&\appd{O(\sd \sr \qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}\\
-			&\appd{O(r\se)} -M_{\nr+1}M_{\nr+2} \ket{\psi} \\
-			&\appd{O(r\se)} -M_{\nr+1} N_{\nr+2} \ket{\psi} \\
-			&\appd{O(r\se)} -N_{\nr+2} N_{\nr+1} \ket{\psi}.
-	\end{align*}
-	The proof of $\ket{\psi_2} \appd{O(\sd \sr \qe)} \ket{\psi_4}$ is similar.
-
-	\textbf{To prove \cref{eq:psi1_norm}}, we use $\norm{\ket{\psi_1}}^2$ as an example. 
-	The norms of the other $3$ vectors can be derived with previous results.
-	We start by expanding the inner product
+    \textbf{To prove \cref{eq:psi1_norm}}, 
+	we start by expanding the inner product
 	\begin{align*}
 		&\braket{\psi_1}{\psi_1} \\
-		=&1/4\bra{\psi}(M_{n+1}^0 - iM_{n+1}^1M_{n+2} + iM_{n+1}^0M_{n+2} +M_{n+1}^1)\\
-		&(M_{n+1}^0 + iM_{n+2}M_{n+1}^1 -iM_{n+2}M_{n+1}^0 + M_{n+1}^1)\ket{\psi}\\
-		=&1/2\bra{\psi}(M_{n+1}^0+M_{n+1}^1-iM_{n+1}^1M_{n+2}M_{n+1}^0+iM_{n+1}^0M_{n+2}M_{n+1}^1\ket{\psi}
-	\end{align*}
-	Here we apply the same trick to flip $M_{n+1}^1$ to Bob's side and get 
+		=&1/4\bra{\psi}(M_{\nr+1}^0 - iM_{\nr+1}^1M_{\nr+2} + iM_{\nr+1}^0M_{\nr+2} +M_{\nr+1}^1)\\
+		&(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 -iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi}\\
+		=&1/2\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1-iM_{\nr+1}^1M_{\nr+2}M_{\nr+1}^0+iM_{\nr+1}^0M_{\nr+2}M_{\nr+1}^1\ket{\psi}
+	\end{align*}
+	Here we apply the trick to flip $M_{\nr+1}^1$ and $M_{\nr+1}^0$ to Bob's side and get 
 	\begin{align*}
@@
 	\textbf{To prove \cref{eq:psi1_eig1}},
-	we need to dive deeper into the implication of the fact that $S_1$ almost achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$.
-	We define
+	we need to dive deeper into the implication of the fact that $S_1$ achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$ approximately.
+	Define
 	\begin{align}
@@
 %	In the definition of $X_A$, we omit $M_{\nr+2}^\perp$ too.
-	Recalling \cref{eq:za-zb}, which states that
+	Recall \cref{eq:za-zb}, which states that
 	\begin{align*}
@@
 
-	\textbf{To prove \cref{eq:psi1_eig2}},
-	we first show that $M_1M_2 \ket{\psi_2}\appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_2}$, then we 
-	use the fact that $\ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_1}$ to draw the conclusion.
-
-	From the strategy $S_2$, we can summarize that 
+	\textbf{To prove \cref{eq:psi1_eig2}}, we introduce an approximation of $\ket{\psi_1}$, which is 
+	\begin{align}
+	    &\ket{\psi_2} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi},
+	\end{align}
+	and we will first show that 
+	\begin{align}
+	    \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \sr\qe)} \ket{\psi_2}.
+	\end{align}
+
+	To prove \cref{eq:psi1_eq}, 
+	we first recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^0 \ket{\psi}$ 
+	and $M_{\nr+1}^1 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^1 \ket{\psi}$ from \cref{prop:chsh_base},
+	so it suffices to show
+	$(M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}$ is close to $(- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}$,
+%	or equivalently,
+%	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
+	At this point, we can use the anti-commutation relation (\cref{eq:zaxa}) induced by $S_1$  and conclude that 
+	\begin{align*}
+		M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^\diamond\ket{\psi}}}}{c\sqrt{s}}O(\sd\sr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}.
+	\end{align*}
+	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \sr \qe)$.
+	Then we can show that 
+	\begin{align*}
+		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \\
+			&\appd{O(r\se)} M_{\nr+2}M_{\nr+1} M_\ast^\diamond \ket{\psi} \\
+			&\appd{O(\sd \sr \qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}\\
+			&\appd{O(r\se)} -M_{\nr+1}M_{\nr+2} \ket{\psi} \\
+			&\appd{O(r\se)} -M_{\nr+1} N_{\nr+2} \ket{\psi} \\
+			&\appd{O(r\se)} -N_{\nr+2} N_{\nr+1} \ket{\psi},
+	\end{align*}
+	where we use the fact that $M_\ast^\diamond \ket{\psi} \appd{O(r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\se)}
+	(M_{\nr+2}^0+M_{\nr+2}^1) \ket{\psi}$.
+
+	Next, we show that $M_1M_2 \ket{\psi_2}\appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_2}$, which gives
+	us \cref{eq:psi1_eig2} after substituting in\cref{eq:psi1_eq}.
+	From the strategy $S_2$, we can deduce that 
 	\begin{align}
@@
 		&(M_1-M_2) N_{\nr+1}^0\ket{\psi} \appd{O(\sr\qe/\sd)}-2sN_{\nr+2} N_{\nr+1}^1\ket{\psi}\\
-		&(M_1 -M_2)N_{\nr+1}^1 \ket{\psi} \appd{O(\sr\qe/\sd)} -2sN_{\nr+2} N_{\nr+1}^0 \ket{\psi}.
+		&(M_1-M_2)N_{\nr+1}^1 \ket{\psi} \appd{O(\sr\qe/\sd)} -2sN_{\nr+2} N_{\nr+1}^0 \ket{\psi}.
 	\end{align}
@@
 \begin{align*}
-	M_3M_4 \x N_3N_4 \ket{\psi} \appd{O(r\se)} M_3 \x N_3 \ket{\psi} \appd{O(r\se)} \ket{\psi},
+	M_4M_3 \x N_4N_3 \ket{\psi} \appd{O(r\se)} M_4 \x N_4 \ket{\psi} \appd{O(r\se)} \ket{\psi},
 \end{align*}
@@
 \begin{align*}
-	U_A \x U_B \ket{\psi} \appd{O(r\se)} \ket{\psi}.
-\end{align*}
-Intuitively, it means that $U_A U_B $ only permutes the Schmidt basis of $\ket{\psi}$.
-Similarly, we also have $U_A\ct U_B\ct \ket{\psi} \appd{O(r\se)} \ket{\psi}$.
+	U_A\ct \x U_B\ct \ket{\psi} \appd{O(r\se)} \ket{\psi}.
+\end{align*}
+Intuitively, it means that $\ket{\psi}$ is invariant under the permutation induced by $U_A\ct U_B\ct$.
 We use this observation in the proof of the following lemma.
@@
 $\ket{\psi'} := \sum_{j=1}^{(d-1)} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}$
-with $\log_r j$ being the discrete log,
-then
-\begin{align}
-	&\ket{\psi} \appd{O(d^{5/4} r^{d/2} \ep^{1/8})} \ket{\psi'}.
+with $\log_r j$ being the discrete log.
+Then,
+\begin{align}
+	&\ket{\psi} \appd{O(d r^{d/2} \ep^{1/8})} \ket{\psi'}.
 \end{align}
@@
 \begin{proof}
-	We first prove that $\norm{\ket{\psi'}}^2 \appd{O(d^{5/2} r^d \qe)} 1$.
+	We first prove that $\norm{\ket{\psi'}}^2 \appd{O(d r^d \qe)} 1$.
 	Observe that 
@@
 	\end{align*}
-	Using the relation $O_A(U_A\ct)^j \ket{\psi} \appd{O(r^j \se)} (U_A\ct)^j O_A^{r^j}\ket{\psi}$ and $\ket{\psi_1} \appd{O(\sd \sr \qe)} \ket{\psi_3}$,
-        we can see that 
-        \begin{align*}
-            	O_A (U_A\ct)^j \ket{\psi_1} &\appd{O(\sd \sr \qe)} O_A(U_A\ct)^j \ket{\psi_3} \\
-            	& = 1/2 (\1 + i N_{\nr+2})(N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1) O_A (U_A\ct)^j \ket{\psi} \\
-            	& \appd{O(r^j \se)} 1/2  (\1 + i N_{\nr+2})(N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1)  (U_A\ct)^j O_A^{r^j} \ket{\psi} \\
-            	& = (U_A\ct)^j O_A^{r^j} \ket{\psi_3} \\
-            	& \appd{O(r^j \sr \qe/\sd)} \omega_d^{-r^j}(U_A\ct)^j \ket{\psi_3} \\
-            	& \appd{O(\sd \sr\qe)} \omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
+	Using the relation $O_B(U_B\ct)^j \ket{\psi} \appd{O(r^j \se)} (U_B\ct)^j O_B^{r^j}\ket{\psi}$ and \cref{eq:psi1_eig1}, we can deduce that 
+	\begin{align*}
+	    O_B (U_B\ct)^j \ket{\psi_1} &= \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1)  O_B (U_B\ct)^j \ket{\psi}\\
+	                                & \appd{O(r^j \se)} \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) (U_B\ct)^j O_B^{r^j} \ket{\psi} \\
+	                                & = (U_B\ct)^j O_B^{r^j} \ket{\psi_1} \\
+	                                & \appd{O(r^j \sr \qe/ \sd)} \omega_d^{r^j} (U_B\ct)^j\ket{\psi_1}.
 	\end{align*}
@@
     \begin{align}
-        \label{eq:omega}
+    \label{eq:B_omega}
+        	O_B (U_B\ct)^j \ket{\psi_1} \appd{O(r^{j+1/2} \qe/ \sd )}\omega_d^{r^j}  (U_B\ct)^j \ket{\psi_1}.
+    \end{align}
+	%Using the relation $O_A(U_A\ct)^j \ket{\psi} \appd{O(r^j \se)} (U_A\ct)^j O_A^{r^j}\ket{\psi}$ and $\ket{\psi_1} \appd{O(\sd \sr \qe)} \ket{\psi_2}$ defined in the proof of \cref{prop:psi1},
+    %we can see that 
+    %\begin{align*}
+            % 	O_A (U_A\ct)^j \ket{\psi_1} &\appd{O(\sd \sr \qe)} O_A(U_A\ct)^j \ket{\psi_2} \\
+            % 	& = 1/2 (\1 + i N_{\nr+2})(N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1) O_A (U_A\ct)^j \ket{\psi} \\
+            % 	& \appd{O(r^j \se)} 1/2  (\1 + i N_{\nr+2})(N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1)  (U_A\ct)^j O_A^{r^j} \ket{\psi} \\
+            % 	& = (U_A\ct)^j O_A^{r^j} \ket{\psi_2} \\
+            % 	& \appd{O(r^j \sr \qe/\sd)} \omega_d^{-r^j}(U_A\ct)^j \ket{\psi_2} \\
+            % 	& \appd{O(\sd \sr\qe)} \omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
+    %\end{align*}
+    %In short, we have shown that 
+    With similar reasoning, we can also get
+    \begin{align}
+    \label{eq:A_omega}
         O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j+1/2} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
     \end{align}
-	Hence for $j \neq j'$, \cref{prop:orthog} tells us that  
-	\begin{align*}
-		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O(d^{3/2} (r^j + r^{j'})\sr \qe)} 0.
+	Hence for $j \neq j'$, Applying \cref{prop:orthog} to \cref{eq:B_omega} gives us that  
+	\begin{align*}
+		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O( (r^j + r^{j'})\sr \qe)} 0.
 	\end{align*}
@@
 		\braket{\psi'}{\psi'} &=\sum_{j,j'=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j'} \ket{\psi_1}\\
-		&\appd{O(d^{5/2} r^{d+1/2} \qe)} \sum_{j=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}\\
+		&\appd{O(dr^{d+1/2} \qe)} \sum_{j=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}\\
 		&\appd{O(dr\se)} (d-1) \frac{1}{d-1} = 1.
@@
 	\begin{align*}
-		\ket{\psi} \appd{O(d^{5/4} r^{d/2} \ep^{1/8})} \ket{\psi'}.
+		\ket{\psi} \appd{O(d r^{d/2} \ep^{1/8})} \ket{\psi'}.
 	\end{align*}
@@
 	\label{prop:rel_comm}
-	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$,
-	then 
+	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$.
+	Then, 
 	\begin{align}
@@
 \begin{proof}
-	The case of $M_j M_{\nr+2}$ is an application of Lemma~$28$ of \cite{coladan2017verifier} with $\se$ replaced by $O(r\se)$.
+	The case of $[M_j, M_{\nr+2}]$ is an application of Lemma~$28$ of \cite{coladan2017verifier} with $\se$ replaced by $O(r\se)$.
 
@@
 	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	There exists an isometry   
+	Then there exists an isometry   
 	$\Phi_A \x \Phi_B = (\Phi_{A,2} \x \Phi_{B,2})(\Phi_{A,1}\x\Phi_{B,2})$ and a state $\ket{junk}$
@@
         \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
-    	node[midway,right] (bracket2) {$\sum_{j=1}^{d-1}\ket{j}\ket{d-j}$}
+    	node[midway,right] (bracket2) {$\sum_{j=1}^{d-1}\ket{x_j}\ket{x_{d-j}}$}
     	(6.5,-2.5);
@@
 	\item Apply Controlled-$U_{A/B}$ operations (i.e. If Alice's control register is in state $\ket{x_j}$, she applies
-	$U_A^{\log_r (d-j)}$. If Bob's control register is in state $\ket{x_j}$, he applies $(U_B\ct)^{\log_r j}$).
+	$U_A^{\log_r (d-j)}$. If Bob's control register is in state $\ket{x_j}$, he applies $(U_B)^{\log_r j}$).
 \end{enumerate}
@@
 
-\Cref{lm:decomp_psi} implies that $ \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi}) \appd{O(d^{5/4} r^{d/2 +1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi'})$,  
+\Cref{lm:decomp_psi} implies that $ \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi}) \appd{O(d r^{d/2 +1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi'})$,  
 so we focus on how the isometry evolves $\ket{\psi'}$.
@@
 	\end{align*}
-When we analyze the effect of the controlled-$O_{A/B}$, we applied \cref{eq:omega} repeatedly.
+When we analyze the effect of the controlled-$O_{A/B}$, we applied \cref{eq:A_omega,eq:B_omega} repeatedly.
 In summary, we have shown that
@@
 \end{align}
-where we use the fact that $O(d^{5/2} r^{d+1/2} \ep^{1/8})$ dominates both $O(d^{5/4} r^{d/2+1/4} \ep^{1/8})$ and 
+where we use the fact that $O(d^{5/2} r^{d+1/2} \ep^{1/8})$ dominates both $O(d r^{d/2+1/4} \ep^{1/8})$ and 
 $O(d^{5/2} r^{d+1/2} \qe)$.

### 2019-05-15 Draft/draft.tex
Honghao: work on section 2

@@
 \DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
+\DeclarePairedDelimiter{\cnorm}{\lvert}{\rvert}
 \DeclarePairedDelimiter{\of}{\lparen}{\rparen}
@@
 \newcommand{\ub}{\underline{b}}
-
 \newcommand{\fC}{\mathfrak{C}}
+\newcommand{\ba}{\pmb{a}}
 
@@
 relation $UOU\ct = O^r$, which is a generalization of a relation in Ref.~\cite{slofstra2017}.
+\carl{A reader may get lost at the last sentence -- you're jumping into the material too quickly without enough explanation.}
 The number of variables and the number of equations of the linear system game depend linearly on $r$,
@@
 $O$ has eigenvalue $\omega_d$.
-\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
-\hfc{How about now?}
 
@@
 %-----------------------------------
-\subsection{Notations}
+\subsection{Notations and mathematical background}
 %-----------------------------------
@@
 The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
-Usually, we denote a \hf{general} Hilbert space by $\calH$.  
-\carl{That last sentence is too vague.  Does $\calH$ refer to a specific Hilbert space?}
-\hfc{How about now?}
-Note that we only work with finite Hilbert spaces in this work.
-When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
-$\calH_B$.
+\hfc{I removed the sentence about $\calH$.}
 The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
@@
 Similarly, for numbers $a,b \in \C$, the closeness is denoted by
-$a \appd{\epsilon} b \iff \norm{a-b} \leq \epsilon$.
+$a \appd{\epsilon} b \iff \cnorm{a-b} \leq \epsilon$.
 
@@
 A primitive root of a prime number
-$d$ is \hf{an integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
-in the multiplicative group of integers modulo $d$, $\Zd$.
-\carl{I'm skeptical about whether that's the standard definition.
-(For example, the definition on wikipedia doesn't include that ``smallest integer'' part.)}
-\hfc{How about now?}
+$d$ is \hf{an integer} $r$ such that $r$ has multiplicative order $d-1$
+in the group of integers modulo $d$, $\Zd$.
 \end{definition}
@@
 $r$ is the generator of $\Zd$.
-\hf{In our work, we always pick $r$ to be the smallest primitive root of $d$.}
-
-%We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
-%\begin{align}
-%	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
-%\end{align}
-%where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
-%and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
-%definitions and notation for now.}
-%Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
-%unless otherwise specified, for example, the $k/r$ above.
+
+We also need some basic notions of group presentation and group
+representation, so 
+We give the definitions of group presentation and group representations below.
+\begin{definition}
+    Let $S$ be a set of letters.
+We denote by $\mathcal{F}(S)$ the free group generated by $S$.
+As a set, $\mathcal{F}(S)$ consists of all finite words made from $\set{s, s^{−1}| s \in S}$ such that no $ss^{−1}$ or $s^{−1}s$ appears as a substring for any $s$.
+The group law is given by concatenation and cancellation.
+\end{definition}
+\begin{definition}[Group Presentation]
+    Given a set $S$, let $\mathcal{F}(S)$ be the free group generated by $S$ and $R$ be a subset of $\mathcal{F}(S)$.
+    Then $\ip{S:R}$ denotes the quotient of $\mathcal{F}(S)$
+    by the normal subgroup generated by $R$.
+    If the group $G$ is isomorphic to $ip{S:R}$,
+    then we say $G$ 
+    has a presentation $\ip{S:R}$. 
+\end{definition}
+The elements of $S$ are the \emph{generators} and the elements
+of $R$ are the \emph{relations}.
+If both sets $S$ and $R$ are finite, then we say the group $G = \ip{S:R}$ is \emph{finitely-presentable}.
+For more properties of group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
+\begin{definition}
+    A representation of $G$ on the Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
+\end{definition}
+In this work, we only consider representations on a finite-dimensional Hilbert space.
+For other concepts and properties related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}. 
+The other concept that we need is about the embedding of a group.
+\begin{definition}
+    We say a group $K$ is an embedding of $G$ if there exists an injective group homomorphism: $\phi: G \rightarrow K$.
+\end{definition}
 %-----------------------------------------
@@
 and $V: \calA \times \calB \times \calX \times \calY \rightarrow \{0,1\}$, which is the scoring function. 
-The score $0$ and $1$ correspond to losing and winning. 
+The scores $0$ and $1$ correspond to losing and winning. 
 Such games are nonlocal
@@
 \hf{In our work, we consider a special case of nonlocal games, which we call a nonlocal test.
-There are three differences between a nonlocal game and a nonlocal test:
-\begin{itemize}
-	\item only a subset of all the question pairs are given to Alice and Bob;
-	\item the answer sets for different questions are different;
-	\item the scoring function maps input-output pairs to real numbers $(\R)$.
-\end{itemize}
+A nonlocal test is a nonlocal game without the scoring function.
 }
@@
 consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
-$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
+$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. 
+By projective measurements, we mean that  
 $(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
@@
 \end{align}
-\hf{For simplicity we omit the tensor product between operators acting on different Hilbert spaces in the rest of the work.}
+\hf{For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
+\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.}
 
 \begin{definition}
-	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
+	Given sets $\calX, \calY, \calA, \calB$, a correlation is a conditional probability distribution
 	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.  
@@
 \begin{definition}[Linear system game]
- Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
+ Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
  where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
- $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
+ $c$ is a length-$n$ vector with entries in $\Z_2$. 
  The associated linear system game involves two
- players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
+ players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ba \in \calA = \Z_2^{\times n}$,
  and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
@@
 	\begin{cases}
-		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
+		1, \quad \text{if } \sum_{k=1}^n H(i,k) a(k) \equiv c(i) \pmod 2 \text{ and } a(j) = b \\
 		0,  \quad \text{otherwise.}
@@
 \end{definition}
-\hf{A widely-used example of linear system games is the Magic Square game introduced in Ref.~\cite{magic_square}.
+\hf{A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
+have equations
+\begin{align*}
+    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
+    x_7 + x_8 + x_9 = 0 \\
+    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
+    x_3 + x_6 + x_9 = 0.
+\end{align*}
 For the formulation of the Magic Square game as a linear system game
@@
 \label{def:q_strat}
-A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
+A quantum strategy presented in terms of binary observables for the linear system game $(Hx = c)$ consists of 
 \begin{enumerate}
@@
 		\item $M_{ij}^2 = \1$ for every $i,j$,
-		\item $\Pi_j M_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
+		\item $\Pi_j M_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
 		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
@@
 the spectral decompositions of the observables. 
-\hf{More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
+More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
 implies that they share a common eigenspace. The collection of eigenvalues associated with one eigenstate is the assignment
-to the whole equation when this eigenstate is measured in a projective measurement strategy.}
- \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}
+to the whole equation when this eigenstate is measured in a projective measurement strategy \cite{cleve2014}.
 
@@
 %Perfect quantum strategies can be extracted from operator solutions and vice versa.
-A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
-\hf{a} finite-dimensional representation of a finitely presented group
-over $\Z_2$, which is called the solution group.  
-\hf{Here we skip the background about group representations and presentations.
-For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
-For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}. }
-\carl{The phrase ``the finite-dimensional
-representation'' is confusing -- it sound like you are implying that there is only one representation.}
+A quantum strategy using binary observables for the linear system game associated with $Hx = c$ can be constructed from
+a finite-dimensional representation of a finitely presentable group
+over $\Z_2$, called the solution group. 
 \begin{definition}[Solution group of a linear system game]
 	\label{def:presentation}
-	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
+	Let $Hx = c$ be an $m \times n$ linear system. The solution group of this system
 	is the group
 	\begin{align*}
-		\Gamma(H,\uc) := \ip{
+		\Gamma(H,c) := \ip{
 		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
-				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
+				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
 				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
-				} .
+				}.
 	\end{align*}
 \end{definition}
-We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
-\hf{In later parts of this work, we give the solution group instead of the set of linear equations when we defines
-a linear system game.}
-
-Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$, then a perfect strategy for 
-the linear system game ($H\ux = \uc$) is given by 
+The element $e$ is the identity element, so the relation $J^2 = x_i^2 = e$ means that all the generators are 
+of order $2$.
+
+Let $\Psi$ be a finite-dimensional representation of $\Gamma(H, c)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$. Then a perfect strategy for 
+the linear system game ($Hx = c$) is given by 
 \begin{enumerate}
 	\item $M_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
-	\item $N_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
-	\hf{I don't think we need to take transpose because these are binary observables. -HF}  \carl{A binary observable can still be different from its transpose.}
+	\item $N_j = \Psi(x_j)\tp$ for all $1 \leq j \leq n$, 
 	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
 \end{enumerate}
-However, our strategy uses a different maximally entangled state,
+Later, the quantum strategy of our linear system game is based on a representation of its solution group,
+but our strategy uses a different maximally entangled state,
 so we justify our strategy more carefully.
@@
 \hf{The weighted CHSH inequality a variation of the CHSH inequality \cite{chsh}. 
-We formulate it as a nonlocal test.}
+We formulate it as a nonlocal game.}
 The input sets and output sets of Alice and Bob are
@@
 		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
-		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
-		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
+		(-1)^{a + b}, \quad \text{if } x = 2,\; y = 1 \\
+		(-1)^{1 + a + b}, \quad \text{if } x = y = 2.
 	\end{cases}
@@
 	\label{eq:chsh_op}
-	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
-\end{align}
-where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of the observables. 
+	\I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
+\end{align}
+where $\ip{M_x N_y} := \bra{\psi} M_x N_y \ket{\psi}$ is the expectation value of the observables. 
 The weighted CHSH inequality is true 
 if Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
-However, if they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
-$ \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}$ \cite{acin2012}.
-\carl{You need to cite the results that you're summarizing here (or refer to an appendix).}
-\hfc{I cited the paper in the title of this subsection. Maybe I add a sentence saying that this subsection
-summarizes results in \cite{acin2012}?}
-\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$ \cite{acin2012}]
+However, if they share an entangled state $\ket{\psi}$, the value of $\I_\alpha$ can be as large as
+$ \I_\alpha^{\max} = 2\sqrt{1+\alpha^2}$ \cite{acin2012}.
+\begin{definition}[Ideal strategy to achieve $\I_\alpha^{\max}$ \cite{acin2012}]
 	\label{def:ideal}
 	Define $\mu = \arctan(1/\alpha)$.
-	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
+	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\I_\alpha^{\max}$, 
 	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
@@
 An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
-value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
+value $\I_\alpha$ close to $\I_\alpha^{\max}$, then the strategy is close to the ideal 
 strategy up to some local isometry, 
 which is a phenomenon referred as a robust self-test.
-We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.
+We give the formal statement of this self-testing property of $\I_\alpha$ in \cref{sec:chsh}.
 \hf{In \cref{sec:full_test} we design
-a nonlocal test call the extended weighted CHSH test based on the weighted CHSH inequality.}
+a nonlocal test called the extended weighted CHSH test based on the weighted CHSH inequality.}
 
@@
 	\begin{align*}
-		 \braket{v}{u} \appd{\ep} \braket{v'}{u} .
-	\end{align*}	
-	\carl{Check the grammar in this proposition.}
+		 \braket{v}{u} \appd{\ep} \braket{v'}{u}.
+	\end{align*}	
 \end{proposition}
@@
 \end{proof}
-\carl{Question: Do we actually need the assumption that $v,v'$ have length less than $1$?}
-\hfc{You are right. We don't.}
 \begin{proposition}
@@
 \label{prop:orthog}
-	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors
+	Let $U$ be a unitary matrix and $\ket{u}$ and $\ket{v}$ be two vectors
 	such that
 	\begin{align*}
-		H\ket{u} \appd{\ep_1} a \ket{u} &&
-		H\ket{v} \appd{\ep_2} b \ket{v}, 
-	\end{align*}
-	for some $a > b \in \R$. Then,
-	\begin{align*}
-		\norm{\braket{u}{v}} \leq \max(\norm{\ket{u}}, \norm{\ket{v}})\frac{\ep_1+\ep_2}{a-b}.
+		U\ket{u} \appd{\ep_1} a \ket{u} &&
+		V\ket{v} \appd{\ep_2} b \ket{v}, 
+	\end{align*}
+	for some $a \neq b \in \C$ such that $\norm{a} = \norm{b} = 1$. Then,
+	\begin{align*}
+		\norm{\braket{u}{v}} \leq \max(\norm{\ket{u}}, \norm{\ket{v}})\frac{\ep_1+\ep_2}{\norm{1-a^{-1}b}} + \frac{\ep_1\ep_2}{\norm{1-a^{-1}b}}.
 	\end{align*}
@@
 \begin{proof}
-	We write $H\ket{u} = a\ket{u} + \ket{u'}$ such that $\norm{\ket{u'}} \leq \ep_1$.
-	Similarly, we write $H\ket{v} = b\ket{v} + \ket{v'}$ such that $\norm{\ket{v'}} \leq \ep_2$.
-	Then, we know
-	\begin{align*}
-		\bra{v}H\ket{u} = a\braket{v}{u} + \braket{v}{u'},\\
-		\bra{v}H\ket{u}  =b\braket{v}{u} + \braket{v'}{u},
-	\end{align*}
-	Subtracting the second equation from the first equation gives us that 
-	\begin{align*}
-		\norm{\braket{v}{u}} = \frac{\norm{\braket{v'}{u} -  \braket{v}{u'}}}{a-b} \leq \frac{\norm{\ket{v}}\norm{\ket{u'}}+
-		\norm{\ket{u}}\norm{\ket{v'}}}{a-b} 
-		\leq \max(\norm{\ket{u}}, \norm{\ket{v}})\frac{\ep_1+\ep_2}{a-b}.
+	We write $U\ket{u} = a\ket{u} + \ket{u'}$ such that $\norm{\ket{u'}} \leq \ep_1$.
+	Similarly, we write $U\ket{v} = b\ket{v} + \ket{v'}$ such that $\norm{\ket{v'}} \leq \ep_2$.
+	Then,
+	\begin{align*}
+		\braket{u}{v} =& \braket{Uu}{Uv} \\
+		=& (a^{-1}\bra{u}+\bra{u'})(b\ket{v}+\ket{v'})\\
+		=& a^{-1}b \braket{u}{v} + a^{-1}\braket{u}{v'}
+		+ b \braket{u'}{v} + \braket{u'}{v'},
+	\end{align*}
+	which implies that 
+	\begin{align*}
+		\norm{\braket{v}{u}} &= \frac{\norm{a^{-1}\braket{u}{v'} +  b\braket{u'}{v}+ \braket{u'}{v'}}}{\norm{1 - a^{-1}b}} \\
+		&\leq \frac{\norm{a}\norm{\ket{v}}\norm{\ket{u'}}+
+		\norm{b}\norm{\ket{u}}\norm{\ket{v'}} + 
+		\norm{\ket{u'}}\norm{\ket{v'}}}{\norm{1 - a^{-1}b}} \\
+		&\leq \max(\norm{\ket{u}}, \norm{\ket{v}})\frac{\ep_1+\ep_2}{\norm{1-a^{-1}b}}
+		+ \frac{\ep_1\ep_2}{\norm{1-a^{-1}b}}.
 	\end{align*}
@@
 \end{proposition}
-\carl{Fix the grammar in the proposition above.}
 \begin{proof}
@@
 \begin{align}
-	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
-\end{align}
-into a linear system game such that the relations in the definition of $K$ can be derived from the
-combination of the linear equations. Then he shows the difference between exact representations
+	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2},
+\end{align}
+into a linear system game such that 
+\hf{there exists an injective homomorphism $\phi: K \rightarrow \Gamma$, where $\Gamma$ is
+the solution group of the linear system game.}
+\hf{In other words, the relations in the definition of $K$ can be derived from the
+combination of the linear equations of $\Gamma$.} Then he shows the difference between exact representations
 and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
@@
 \end{definition}
+\carl{At this point I think we are overloading the reader
+with technical material.  This stuff needs to be broken up into
+smaller pieces, and perhaps explained intuitively.}
 Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
@@
 	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(r\se)} 1/(d-1),\\
-	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d\ket{\psi_1},\\
-	 \label{eq:psi1_eig2} &M_1M_2 \ket{\psi_1} \appd{O(\sd\sr \qe)} \omega_d^{-1} \ket{\psi_1}.
+	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d\ket{\psi_1} 
+	 && N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_1} \\
+	 \label{eq:psi1_eig2} &M_1M_2 \ket{\psi_1} \appd{O(\sd\sr \qe)} \omega_d^{-1} \ket{\psi_1}
+	 && M_2M_1 \ket{\psi_1} \appd{O(\sd\sr \qe)} \omega_d \ket{\psi_1}.
 	\end{align}
@@
 	\end{align*}
+	With similar calculations, we can get that 
+	\begin{align}
+	    N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_1}.
+	\end{align}
 
@@
 		M_1M_2 \ket{\psi_1} \appd{O(\sd \sr \qe)} \omega_d^{-1}\ket{\psi_1}.
+	\end{align}
+	With similar derivation we can get that 
+	\begin{align}
+	    M_2M_1 \ket{\psi_1} \appd{O(\sd \sr \qe)} \omega_d\ket{\psi_1}.
 	\end{align}
@@
 	    O_B (U_B\ct)^j \ket{\psi_1} &= \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1)  O_B (U_B\ct)^j \ket{\psi}\\
-	                                & \appd{O(r^j \se)} \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) (U_B\ct)^j O_B^{r^j} \ket{\psi} \\
+	                                & \appd{O(r^j \se)} \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) (U_B\ct)^j 
+	                                O_B^{r^j} \ket{\psi} \\
 	                                & = (U_B\ct)^j O_B^{r^j} \ket{\psi_1} \\
-	                                & \appd{O(r^j \sr \qe/ \sd)} \omega_d^{r^j} (U_B\ct)^j\ket{\psi_1}.
+	                                & \appd{O(r^j \sr \qe/ \sd)} \omega_d^{r^j} (U_B\ct)^j\ket{\psi_1}
 	\end{align*}
@@
         \label{eq:B_omega}
-        	O_B (U_B\ct)^j \ket{\psi_1} \appd{O(r^{j+1/2} \qe/ \sd )}\omega_d^{r^j}  (U_B\ct)^j \ket{\psi_1}.
+        O_B (U_B\ct)^j \ket{\psi_1} \appd{O(r^{j+1/2} \qe/ \sd )} \omega_d^{r^j}  (U_B\ct)^j \ket{\psi_1}.
     \end{align}
@@
     %In short, we have shown that 
-    With similar reasoning, we can also get
+    With similar derivation, we can also get
     \begin{align}
     \label{eq:A_omega}
-        O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j+1/2} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
-    \end{align}
-	Hence for $j \neq j'$, Applying \cref{prop:orthog} to \cref{eq:B_omega} gives us that  
-	\begin{align*}
-		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O( (r^j + r^{j'})\sr \qe)} 0.
-	\end{align*}
+        O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j+1/2} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1},
+    \end{align}
+    which will be used later as well.
+	Hence for $j \neq j'$, $(U_A\ct U_B\ct)^{j} \ket{\psi_1}$ and $(U_A\ct U_B\ct)^{ j'} \ket{\psi_1}$ are close to eigenvectors
+	of the unitary $O_B$ with different eigenvalues.
+	Applying \cref{prop:orthog} to \cref{eq:B_omega} gives us that  
+	\begin{align*}
+		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O( (r^j + r^{j'})\sr \qe)} 0,
+	\end{align*}
+	where we use the fact that $\norm{1 - \omega_d^{r^{j'}-r^j}} = O(1/d)$.
 	We can calculate the norm of $\ket{\psi'}$ as 

### 2019-06-24 Draft/draft.tex
Changes to section 2 - 5.

@@
 \newcommand{\ba}{\pmb{a}}
+\newcommand{\bc}{\pmb{c}}
+\newcommand{\bS}{\pmb{S}}
 
@@
 % Comments
-\def\carl#1{{\color{blue} #1 -Carl}}
+\def\carl#1{{\color{blue} #1}}
 \newcommand{\hf}[1]{\textcolor{red}{#1}}
@@
 \hfc{Which DIQKD paper should I cite?}
+\carl{Two possible papers that you could cite are Mayer Yao 1998 (which originated the idea of self-testing as far as I know, and mentions QKD) and my paper (miller2017, which you've already cited --- indeed it uses the concept of self-testing).
+Also you should check Vazirani-Vidick's 2014 PRL paper to see if it mentions self-testing at all.
+(It was the first to fully prove DI-QKD.)}
 
@@
 pair in parallel \cite{mckague2016, coladan2016parallel, lowdegree}. 
+\carl{I believe the first to prove robust self-testing of a single EPR pair was McKague-Yang-Scarani 2012.}
 Self-testing general $d$-dimensional EPR pairs is a harder task.
@@
 
-The set $D$ is easily characterizable as it contains all the odd prime numbers with smallest
-primitive root $2$, $3$ or $5$. It has been shown that  the set $D$ has infinitely many elements \cite{murty1988}.
+The set $D$ is, \carl{
+specifically, the set of all 
+odd prime numbers whose smallest primitive root is either $2$, $3$,
+or $5$}.  It has been shown that \carl{this set} has infinitely many elements \cite{murty1988}.
 To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r^2)$ for each $d \in D$ whose primitive
@@
 %\end{theorem}
+\carl{The paper \cite{bamps2015} says that the earlier paper \cite{yang2013} has ``flaws.'' Check what those flaws are, and make sure that they won't put a shadow on anything that you're discussing when you cite \cite{yang2013}.}
 
@@
 $O$ has eigenvalue $\omega_d$.
+\carl{This paragraph (also) will need more context.}
 
@@
 %-----------------------------------
-The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we are interested in is denoted by
+The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we \hf{self-test} is denoted by
 \begin{align}
@@
 The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
-\hfc{I removed the sentence about $\calH$.}
+\hf{The special form of this maximally entangled state is the effect of our linear system game.} \carl{I don't know what that sentence means.  Refer to something specific.}
 The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
-the maximally entangled state is denoted by 
-\begin{align}
-	\ket{\EPR{2}} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
+\hf{the EPR pair is denoted by} 
+\begin{align}
+	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
 \end{align}
@@
 \end{align}
+\hf{Note that we only work with finite Hilbert spaces in our work.}
 
@@
 A primitive root of a prime number
-$d$ is \hf{an integer} $r$ such that $r$ has multiplicative order $d-1$
-in the group of integers modulo $d$, $\Zd$.
+$d$ is an integer $r$ such that $r$ has multiplicative order $d-1$
+in the ring of integers modulo $d$, $\mathbb{Z}_d$.
 \end{definition}
 In other words,
-$r$ is the generator of $\Zd$.
+$r$ is a generator of $\Zd$.
 
@@
 representation, so 
-We give the definitions of group presentation and group representations below.
-\begin{definition}
-    Let $S$ be a set of letters.
-We denote by $\mathcal{F}(S)$ the free group generated by $S$.
-As a set, $\mathcal{F}(S)$ consists of all finite words made from $\set{s, s^{−1}| s \in S}$ such that no $ss^{−1}$ or $s^{−1}s$ appears as a substring for any $s$.
+We \hf{introduce them} below.
+For more contexts, please refer to Ref.~\cite{dummit2004}.
+
+\hf{
+Let $S$ be a set of letters. We denote by $\mathcal{F}(S)$ the \emph{free group generated by $S$}, 
+which consists of all finite words made from $\set{s, s^{−1}| s \in S}$ such that no $ss^{−1}$ or $s^{−1}s$ appears as a substring for any $s$,
+where $s^{-1}$ denotes the inverse of $s$. 
 The group law is given by concatenation and cancellation.
-\end{definition}
-\begin{definition}[Group Presentation]
+For a more formal treatment, we refer to Section $6.3$ of Ref.~\cite{dummit2004}.}
+\carl{This definition is (still) confusing.  It would be ok to simply cite the concept of a free group, provided that you refer to a precise \& complete definition.}
+
+\begin{definition}[Group presentation]
     Given a set $S$, let $\mathcal{F}(S)$ be the free group generated by $S$ and $R$ be a subset of $\mathcal{F}(S)$.
@@
     by the normal subgroup generated by $R$.
-    If the group $G$ is isomorphic to $ip{S:R}$,
+    If the group $G$ is isomorphic to $\ip{S:R}$,
     then we say $G$ 
@@
 \end{definition}
+If both sets $S$ and $R$ are finite, then we say the group $G = \ip{S:R}$ is \emph{finitely-presentable}.
 The elements of $S$ are the \emph{generators} and the elements
 of $R$ are the \emph{relations}.
-If both sets $S$ and $R$ are finite, then we say the group $G = \ip{S:R}$ is \emph{finitely-presentable}.
-For more properties of group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
+When we refer to an equation
+of the form $a = b$ with $a, b \in \mathcal{F} ( S )$ as a ``relation,'' 
+it is understood 
+that we mean the element $ab^{-1} 
+\in R$.
+\hf{ There are two types of relations that we will be working with.
+} 
+Considering \hf{a subset of generators} $\{ s_j \}_{j=1}^n \subset S$ \hf{such that $s_{j_1} \neq s_{j_2}$ if $j_1 \neq j_2$},
+the relations of the form $\Pi_{j=1}^n s_j  = e$, where $e$ is the identity element, are called 
+\emph{linear relations};
+and the relations of the form
+$s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.   \carl{This last sentence
+needs to be made more precise (e.g., are
+repetitions allows in the linear relations)?}
+\hfc{I thought the fact that $\{s_j\}$ is a subset of $S$ guarantees that there will be no repetitions in a linear relation.}
 \begin{definition}
-    A representation of $G$ on the Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
+    A representation of $G$ on the finite Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
 \end{definition}
-In this work, we only consider representations on a finite-dimensional Hilbert space.
-For other concepts and properties related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}. 
-The other concept that we need is about the embedding of a group.
-\begin{definition}
-    We say a group $K$ is an embedding of $G$ if there exists an injective group homomorphism: $\phi: G \rightarrow K$.
+The last concept of group theory that we need is group embedding.
+\begin{definition}[Group embedding]
+    An embedding of $G$ into $K$ is an injective group homomorphism: $\phi: G \rightarrow K$.
 \end{definition}
@@
 comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
-and $V: \calA \times \calB \times \calX \times \calY \rightarrow \{0,1\}$, which is the scoring function. 
-The scores $0$ and $1$ correspond to losing and winning. 
-Such games are nonlocal
-because Alice and Bob cannot communicate after getting their questions but they may share some strategy beforehand.
-
-\hf{In our work, we consider a special case of nonlocal games, which we call a nonlocal test.
-A nonlocal test is a nonlocal game without the scoring function.
-}
+and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function.
+
+\hf{We also define A nonlocal test 
+to be a tuple $(\calX, \calY, \calA, \calB, \pi)$, where
+$\calX, \calY, \calA, \calB$ and $\pi$ are as defined for a nonlocal game, so a nonlocal test doesn't have a scoring function.}
 
@@
 \end{align}
-\hf{For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
-\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.}
-
+\hf{Note that the tensor product structure indicates that the
+two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.}
+For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
+\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
 \begin{definition}
@@
 \end{definition}
-A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
-\begin{definition}[Linear system game]
- Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
- where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
- $c$ is a length-$n$ vector with entries in $\Z_2$. 
+A particular type of nonlocal games that we are interested in is called linear system games.
+\begin{definition}[Binary linear system game]
+ Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ \carl{(meaning that} $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
+ $c$ is a length-$n$ vector with entries in $\Z_2$\carl{)}. 
  The associated linear system game involves two
- players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ba \in \calA = \Z_2^{\times n}$,
- and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
+ players Alice and Bob. 
+ Alice is given an equation number $i \in \calX = \{1 \dots m\}$,
+ and replies with $\ba \in \calA = \Z_2^{\times n}$.
+ Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
  scoring function is defined by
@@
 \end{definition}
-\hf{A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
+A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
 have equations
@@
 \end{align*}
-For the formulation of the Magic Square game as a linear system game
-and the general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.}
-
-In the rest of the paper, we will work with quantum strategies for the linear system game presented in terms of binary observables.
-\begin{definition}[Quantum strategy of a linear system game]
+\hf{Note that the equations above are taken modulo $2$.
+We follow this convention in the rest of our work.}
+For the formulation of a general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.
+
+% \hf{In our work, a binary linear system game is conducted in a slightly different way.
+% Instead of always getting an equation number, Alice gets an equation number or 
+% a pair of equation number and variable number with equal probability. In the later case,
+% she just needs to give assignment to the particular variable.
+% By conducting a binary linear system game in this way,
+% we force Alice and Bob to share
+% a quantum strategy in terms of binary observables.}
+% \carl{Is this modification necessary?}
+\begin{definition}[Binary observable strategy of a linear system game]
 \label{def:q_strat}
-A quantum strategy presented in terms of binary observables for the linear system game $(Hx = c)$ consists of 
+A quantum strategy presented in terms of binary observables for the binary linear system game $Hx = c$ consists of 
 \begin{enumerate}
@@
 	\begin{enumerate}
-		\item $M_{ij}^2 = \1$ for every $i,j$,
-		\item $\Pi_j M_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
-		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
+		\item $M_{ij}^2 = \1$ for every $i,j$, and
+		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every \carl{$i,l,k$ such that} $H(i,l) = H(i,k) =1$;
 	\end{enumerate} 
@@
 \end{definition}
-Note that any quantum strategy presented in terms of binary observables can be 
-converted to a quantum strategy presented in terms of projective measurement by looking into
-the spectral decompositions of the observables. 
-More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
-implies that they share a common eigenspace. The collection of eigenvalues associated with one eigenstate is the assignment
-to the whole equation when this eigenstate is measured in a projective measurement strategy \cite{cleve2014}.
-
-%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
-%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
-%operator solution in the following sense.  \carl{There's a missing reference here?}
-%\begin{definition}[Operator solution of a linear system]
-%\label{def:op_sol}
-%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
-%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
-%	be best to just state the definition for finite dimensions only.)}
-%	\begin{enumerate}
-%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
-%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
-%		\item for all $1 \leq i \leq m$,
-%		\begin{align*}
-%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
-%		\end{align*}
-%	\end{enumerate}
-%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
-%	solution in which the Hilbert space is finite-dimensional.
-%\end{definition}
-%Perfect quantum strategies can be extracted from operator solutions and vice versa.
-A quantum strategy using binary observables for the linear system game associated with $Hx = c$ can be constructed from
+\hf{Note that a measurement strategy of a binary linear system game can be converted to a binary observable strategy. Let a  measurement strategy be 
+$(\{\{M_i^{\ba}\}_{\ba \in X_i}\}_{i=1}^m, \{\{N_j^b\}_{b=0}^1\}_{j=1}^n,\\ \ket{\psi})$, where $X_i$ is some answer set of equation $i$.
+The corresponding binary observable
+strategy consists of, $\ket{\psi}$, $N_j := N_j^0 - N_j^1$ and
+\begin{align*}
+    M_{ij} = \sum_{\ba: a(j)=0} M_i^{\ba} - \sum_{\ba: a(j) =1}
+    M_i^{\ba}
+\end{align*}
+for $1\leq i \leq m$ and $1 \leq j \leq n$. Hence, in the rest of the work, we focus on binary observable strategies.}
+
+% Note that any quantum strategy presented in terms of binary observables can be 
+% converted to a quantum strategy presented in terms of projective measurement by looking into
+% the spectral decompositions of the observables. 
+% More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
+% implies that they share a common eigenspace. The collection of eigenvalues associated with one eigenstate is the assignment
+% to the whole equation when this eigenstate is measured in a projective measurement strategy \cite{cleve2014}.
+
+A \hf{perfect} binary observable strategy for the linear system game associated with $Hx = c$, which always wins the game, can be constructed from
 a finite-dimensional representation of a finitely presentable group
@@
 \end{definition}
-The element $e$ is the identity element, so the relation $J^2 = x_i^2 = e$ means that all the generators are 
-of order $2$.
-
-Let $\Psi$ be a finite-dimensional representation of $\Gamma(H, c)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$. Then a perfect strategy for 
+The relation $J^2 = x_i^2 = e$ means that all the generators are of order $2$.
+Let $\Psi$ be a finite-dimensional representation of $\Gamma(H, c)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$. 
+Then a perfect strategy for 
 the linear system game ($Hx = c$) is given by 
@@
 \end{enumerate}
-Later, the quantum strategy of our linear system game is based on a representation of its solution group,
-but our strategy uses a different maximally entangled state,
-so we justify our strategy more carefully.
 
@@
 
-%=======================================
-\section{The linear system game $\LS(r)$}
+%===============================================
+\section{The binary linear system game $\LS(r)$}
 \label{sec:lsg}
-%=======================================
-In this section, we introduce a linear system game which is a component of the full test.
+%===============================================
+In this section, we introduce a binary linear system game which is a component of the full test.
 This game is designed to enforce relations that should be satisfied by 
-Alice and Bob's observables. The inspiration comes from 
+Alice and Bob's observables.
+
+The inspiration comes from 
 Slofstra's seminal work~\cite{slofstra2017}, in which he
-embeds the group
-\begin{align}
-	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2},
-\end{align}
-into a linear system game such that 
-\hf{there exists an injective homomorphism $\phi: K \rightarrow \Gamma$, where $\Gamma$ is
-the solution group of the linear system game.}
-\hf{In other words, the relations in the definition of $K$ can be derived from the
-combination of the linear equations of $\Gamma$.} Then he shows the difference between exact representations
-and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
-\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
-following relation
-$
-uou^{-1} = o^r 
-$
-for some $r \in \N$ into a linear system game, denoted by $\LS(r)$.}
-
-%------------------------------------------------------------------------
-\subsection{The embedding of $uou^{-1} = o^r$}
-%------------------------------------------------------------------------
-The main result of this subsection is summarized in the following theorem.
-\begin{theorem}
-	The relation $uou^{-1} = o^r$ can be embedded in a binary linear system game which has
-	$n(r) := 18r+85$ variables and $m(r) := 17r + 77$ equations, where each equation has $3$ variables.
-\end{theorem}
-We prove this by constructing the solution group $\Gamma(\LS(r))$ of the linear system game.
-\hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$?
-Or you have any suggestion about a symbol for this group?} \carl{The notation that you're using seems backwards -- I think we should express the solution group as a function of the linear system, not the other way around.}
-We also prove some properties of the generators of $\Gamma(\LS(r))$ along the way.
-
-We embed $uou^{-1}= o^r$ into $\Gamma(\LS(r))$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
-\begin{definition}	
-\label{def:g0}
-	The presentation of $G_0$ has order-$2$ generators:
-	\begin{align*}
-		\{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5
-	\end{align*}
-	and relations:
-	\begin{align*}
-	&u_3 = u_2o_1u_2 && u_4 = u_2o_2u_2 \\
-	&u_5 = u_1u_3u_1 && o_2 = u_1u_4u_1\\
-	&u_5 = o_1 o_r o_1,
-	\end{align*}
-	and when $r$ is even
-	\begin{align*}
-	&o_{1+2j} = o_1o_{2j}o_1 && o_{2+2j} = o_2o_{1+2j}o_2&& \text{ for } j = 1 \dots r/2 - 1;
-	\end{align*}
-	when $r$ is odd
-	\begin{align*}
-	&o_3 = o_2o_1o_2 &&
-	 o_{2+2j} =o_1o_{1+2j}o_1 && o_{3+2j} = o_2o_{2j+2}o_2 &&\text{ for } j = 1 \dots (r-3)/2.
-	\end{align*}
-\end{definition}
-\begin{proposition}
-	The group $G_0$ embeds the relation 
-	\begin{align}
-		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
-	\end{align}
-	for any $ j \in \N$.
-\end{proposition}
-The proof follows the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017}
-\begin{proof}
-	We prove it by induction.
-	Direct calculation gives us that
-	\begin{align*} 
-		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
-	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
-	=& u_5 o_2\\
-	=& o_1o_ro_1 o_2.
-	\end{align*}
-	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above and
-	prove the $j=1$ case.
-
-	Now assume the statement is true for $j = n$, then for $j = n+1$
-	\begin{align*}
-		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
-		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
-		 =& (o_1o_2)^{r^{n+1}},
-	\end{align*}
-	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$.
-	Hence, the statement is true.
-\end{proof}
-To better characterize all the conjugation relations above and simplify the form of $G_1$ defined below, 
-we relabel $u_i$ and $o_i$'s
-as $a_i$'s such that
-\begin{align}
-	a_j := 
-	\begin{cases}
-	 o_j \text{ for } j = 1,2 \\
-	 u_{j-2} \text{ for } j = 3\dots 7 \\
-	o_{j- 5} \text{ for } j = 8 \dots r+5.
-	\end{cases}
-\end{align}
-Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
-\begin{align*}
-	(i,j,k) \in C(r) \iff a_ia_ja_i = a_k.
-\end{align*}
-The size of $C(r)$ is $r+3$. 
-%We can also employ some ordering of $C(r)$ such that $C(r,j)$ is a unique tuple for 
-%$j = 1 \dots r+3$.
-In this way, the group $G_0$ can be presented by
-$
-G_0  = \ip{ \{a_i\}_{i=1}^{r+5} : C(r) }.
-$
-Then we define the group $G_1$.
-\begin{definition}
-The presentation of $G_1$ has order-$2$ generators:
-\begin{align*}
-	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f_0, g_0, \{h_{jk}\}_{(i,j,k) \in C(r)};
-\end{align*}
-and relations:
-\begin{align*}
-	&a_i = b_ic_i = f_0d_i = g_0v_i,&& f_0b_if_0 =c_i &&\text{ for } i= 1 \dots r+5 \\
-	&h_{jk}b_j c_k = e,&& d_ib_jd_i = c_k &&\text{ for all } (i,j,k) \in C(r).
-\end{align*}
-\end{definition}
-\carl{At this point I think we are overloading the reader
-with technical material.  This stuff needs to be broken up into
-smaller pieces, and perhaps explained intuitively.}
-Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
-We introduce the generator $g_0$ so that later we can associate $f_0$ with $g_0$ in linear relations of the Magic Square game.
-Such relations are important for the self-testing proof.
-Two important properties of $G_1$ are given in propositions below.
-The first property of $G_1$ was first proved in Lemma~$4.4$ of \cite{slofstra2017}.
-\begin{proposition}
-	The group $G_1$ embeds relation $x_ix_jx_i = x_k$ for all $(i,j,k) \in C(r)$.
-\end{proposition}
-\begin{proof}
-	We first show that $d_i c_j d_i = b_k$, which is because
-	\begin{align*}
-		d_i c_j d_i = d_i (f_0 b_j f_0) d_i = f_0 (d_i b_j d_i) f_0 = f_0 c_k f_0 = b_k.
-	\end{align*}
-	Then, we can prove that 
-	\begin{align*}
-		a_i a_j a_i = f_0 d_i b_j c_j f_0 d_i = (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) = (f_0 c_k f_0)(f_0 b_k f_0) = b_k c_k = a_k. 
-	\end{align*}
-\end{proof}
-\begin{proposition}
-	In the group $G_1$, the generators $f_0$ and $g_0$ commute with $a_i$ for all $i = 1 \dots r+5$.
-\end{proposition}
-\begin{proof}
-	We can check that
-	\begin{align*}
-		f_0a_i f_0 a_i = d_i d_i = e && g_0 a_i g_0 a_i = v_i v_i  = e,
-	\end{align*}
-	for all $i = 1 \dots r+5$.
-\end{proof}
-Note that there are two types of conjugacy relations in $G_1$. One is of the form
-$f b_i f = c_i$ for all $i = 1 \dots r+5$. The other one is of the form 
-$d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
-we are going to embed it into a different set of linear relations in $\Gamma(\LS(r))$.
-
+embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
+into the solution group of a binary linear system game.  
+We generalize the relation $xyx^{-1} = y^2$ and embed the 
+following group
+\begin{align}
+    \Pg = \ip{u,o:uou^{-1} = o^r},
+\label{pgroup}
+\end{align}
+for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
+Since the steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed in the proofs of Proposition~$33$, Lemma~$29$ and
+Proposition $27$ of Ref.~\cite{slofstra2017}, 
+we defer the formal statements of the embedding procedure till \cref{sec:embedding},
+but give the idea behind this procedure in \cref{sec:embed_idea}. 
+In \cref{sec:lsg_def}, we define $\Gamma$ and introduce how to
+construct $\LS(r)$ from $\Gamma$.
+We also highlight a few operators from a finite-dimensional representation of $\Gamma$.
+The representation will be used later to build the ideal strategy.
+
+%----------------------------------------
+\subsection{A sketch of the procedure
+for constructing $\LS ( r )$}
+\label{sec:embed_idea}
+%----------------------------------------
+The group $\Pg$ (see equation (\ref{pgroup} above) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}), which is the
+solution group of $\LS ( r )$.  
+Thus we obtain a chain of embeddings:
+\begin{align}
+\Pg \hookrightarrow \Pg_0 \hookrightarrow \Pg_1 \hookrightarrow
+\Gamma.
+\end{align}
+The purposes of introducing each intermediate
+group are explained below.
+
+First observe that the generators $u$ and $o$ have arbitrary order in $\Pg$. However, all the generator of a solution
+group are of order-$2$, so it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$
+to a single generator. 
+\hf{This is the reason why we first embed $\Pg$ into $\Pg_0 := \ip{S_0:R_0}$, where all the generators in $S_0$ are of 
+order-$2$ and all the relations in $R_0$ are conjugacy relations.
+The generators in $S_0$ are $a_i$ for $i=1 \dots r+5$.
+The special generators are $a_1, a_2, a_3$ and $a_4$ because the product $a_1a_2$ behaves similarly as $o$
+and the product $a_3a_4$ behaves similarly as $u$.}
+\carl{[You should probably
+say somewhere that $\mathcal{P}_0$ is defined
+by conjugacy relations (since it seems like you're assuming that the reader knows that).]}
+\hfc{Fixed.}
+Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$ (see \cref{prop:g0}), so
+a homomorphism: $\Pg \rightarrow\Pg_0$  that maps $o$ to $a_1a_2$ and $u$ to $a_3a_4$ is an embedding of $\Pg$ into $\Pg_0$
+by Proposition $33$ of Ref.~\cite{slofstra2017}.
+To better characterize the conjugacy relations in $R_0$, we introduce $C(r)$ defined in \cref{eq:cr}
+of tuples $(i,j,k)$ such that $(i,j,k) \in C(r)$ if and only if $a_ia_ja_i = a_k$ is in $R_0$.
+
+\hf{Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$
+and $R_1$ consists of both linear relations and conjugacy relations.
+The special properties of $S_1$ and $R_1$ are
+\begin{enumerate}
+    \item $s_is_js_i = s_k \in R_1$ implies that there exists a generator
+$s' \in S_1$ such that $s' s_j s_k = e \in R_1$;
+    \item every relation in $R_0$ can be derived from $R_1$.
+\end{enumerate}
+Note that $s'$ can be seen as an auxiliary generator such that
+its existence implies that $s_j$ and $s_k$ commute, because
+\begin{align*}
+    [s_j, s_k] = s_j s_k s_j s_k = (s')^2 = e.
+\end{align*}
+Ensuring the conjugacy relations are associating one generator to another one which 
+commutes with it is the purpose of introducing $\Pg_1$. 
+It makes the construction of a finite-dimension representation of $\Gamma$ from
+a finite-dimension representation of $\Pg_1$ easier.}
+\carl{[that's vague -- either explain it or don't say it]}
+\hfc{How about now?} 
+Specifically, in this step, we introduce generators $a_i, b_i, c_i, d_i \in S_1$
+for each generator $a_i \in S_0$.
+There is also a special generator $f_0 \in S_1$ such that
+\begin{align*}
+    a_i = b_ic_i = f_0d_i. 
+\end{align*}
+The relation $a_i = b_ic_i$ guarantees that $b_i$ commutes
+with $c_i$.
+The generators $b_i$ and $c_i$ are also related by a conjugacy relation
+\begin{align*}
+    c_i = f_0 b_i f_0. 
+\end{align*}
+For each $(i,j,k) \in C(r)$, 
+$S_1$ contains an auxiliary generator $h_{jk}$, and
+$R_1$ 
+contains a conjugacy relation 
+\begin{align*}
+    d_ib_jd_i = c_k,
+\end{align*}
+and a linear relation
+\begin{align*}
+    h_{jk}b_jc_k = e.
+\end{align*}
+The introduction of $h_{jk}$ helps us to deduce that 
+$b_j$ commutes with $c_k$.
+Hence, every conjugacy relation in $R_1$ is either of the form
+$f_0b_if_0 = c_i$ for $1 \leq i \leq r+5$, or
+$d_ib_jd_i = c_k$ for $(i,j,k) \in C(r)$.
+\hf{From the conjugacy relations in $R_1$, it can be proven that
+\begin{align*}
+    d_ic_jd_i = b_k \text{ for each } (i,j,k) \in C(r).
+\end{align*}
+Then we can expand $a_ia_ja_i$ by first substituting in $a_i = f_0 d_i$ and $a_j = b_jc_j$ and then repeatedly substituting in the conjugacy relations in $R_1$ and 
+the conjugacy relations deduced above. For details, we refer to the 
+proof of \cref{prop:g0g1}.}
+\carl{It would be good to explain (or at least reiterate) that these relations allow us to recover the conjugacy relations in $\mathcal{R}_0$.}
+\hfc{How about now?}
+
+A representation of $\Pg_1$ can also be built upon a representation of $\Pg_0$.
+Suppose $\Psi_0$ is a representation of $\Pg_0$ on some Hilbert space $\calH$, then 
+ a representation of $\Pg_1$, $\Psi_1$, on the Hilbert space $\C^2 \x \calH$ can
+ be constructed such that
+\begin{align*}
+    &\Psi_1(a_i) = \1_{\C^2} \x \Psi_0(a_i).
+\end{align*}
+For more details of $\Psi_1$, we refer to \cref{sec:rep_gamma}.
+Hence, a homomorphism $\phi: \Pg_0 \rightarrow \Pg_1$ that 
+maps $a_i$ to $a_i$ is an embedding of $\Pg_0$ into $\Pg_1$
+by Lemma $15$ of Ref.~\cite{slofstra2017}.
+
+In the last step, we can construct $\Gamma:= \ip{S:R}$ with $S_1 \subset S$, in a way such that
+$\Gamma$ only has linear relations, and the linear relations can be combined
+to recover the conjugacy relations in $R_1$.
+We demonstrate how relation $f_0 b_1 f_0 = c_1$ is embedded in
+$6$ linear relations of $R$ as an example. 
+The other conjugacy relations of $\Pg_1$ are embedded in linear relations in a similar way.
+We introduce auxiliary generators $f_1, f_2$ and $\{p_{1,j}\}_{j=1}^5$ and they satisfy the linear relations:
+\begin{align*}
+    &f_0 f_1 f_2 = e && b_1 f_2 p_{1,1} = e && p_{1,1} p_{1,2} p_{1,3} = e\\
+	&f_0 p_{1,3} p_{1,4} = e && c_1 p_{1,4} p_{1,5} = e \quad f_1 p_{1,2} p_{1,5} = e.
+\end{align*}
+For details about how the linear relations above
+can be combined to recover $f_0b_1f_0 = c_1$, we refer to \cref{sec:embedding}.
+A representation of $\Gamma$ can also be built upon
+the representation $\Psi_1$ of $\Pg_1$.
+We denote the representation of $\Gamma$ by $\Psi$ and
+it is defined on $\C^2 \x \C^2 \x \calH$ such that
+\begin{align*}
+    \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
+    s \in S_1.
+\end{align*}
+In particular, it means that for each $a_i \in S_0$
+\begin{align*}
+    \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
+\end{align*}
+Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
+maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
+by Lemma $15$ of Ref.~\cite{slofstra2017}.
+
+%----------------------------------------
+\subsection{Formal definitions}
+\label{sec:lsg_def}
+%----------------------------------------
+We define the solution group of the linear system game $\LS(r)$ first, which is constructed following the steps
+described in the previous subsection.
 \begin{definition}
 \label{def:gamma}
-The presentation of $\Gamma(\LS(r))$ has order-$2$ generators:
-\begin{align*}
-	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
-	\{\{ k_{l,j} \}_{j=1}^6\}_{l \in C(r)},
-\end{align*}
-and relations:
+Define the set $S$ to be 
+\begin{align*}
+	S = \{J\} \cup \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
+	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
+\end{align*}
+and the set $R$ to be the union of the following
+set of linear relations:
 \begin{itemize}
-\item for all $i = 1 \dots r+5$:
-\begin{align*}
-	&a_i = b_ic_i = f_0d_i = g_0v_i \\
-	&g_2 a_i w_i = e \\
-	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
-	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
-\end{align*}
-which embed $f_0 b_i f_0 = c_i$;
-\item for all $ l = (i,j,k) \in C(r)$:
-\begin{align*}
-	&h_{jk}b_j c_k = e\\
-	&d_i k_{l,1} f_2 = e && b_j f_2 k_{l,2} = e && k_{l,2} k_{l,3} k_{l,4} = e\\
-	&d_i k_{l,4} k_{l,5} = e && c_k k_{l,5} k_{l,6} =e && k_{l,1} k_{l,3} k_{l,6} = e,
-\end{align*}
-which embed $d_i b_j d_i = c_k$;
-\item relations of a Magic Square game:
-\begin{align*}
-	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
-	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
-\end{align*}
-which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
-\item $J$ commutes with all the other generators.
+\item for each $i = 1 \dots r+5$:
+\begin{align*}
+	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
+	%&g_2 a_i w_i = e \\
+	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
+	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
+\end{align*}
+\item for each $ \bc = (i,j,k) \in C(r)$:
+\begin{align*}
+	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
+	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
+	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
+\end{align*}
+\item 
+$
+	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
+	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
+$
+\item $R_J = \{ JsJs = e \vert s \in S\}$,
+\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
 \end{itemize}
+The group $\Gamma$ is a group with the presentation
+$\ip{S:R}$.
+\carl{[If you're really going to claim
+that this is a complete definition, maybe you should write out the set $C$ somewhere as well?]}
 \end{definition}
-Note that $\Gamma(\LS(r))$ has all the generators of $G_1$ but all the conjugacy relations 
-from $G_1$ are broken into linear relations.
-Formal statements of the properties of $\Gamma(\LS(r))$ are summarized in the two propositions below.
-\begin{proposition}
-	The group $\Gamma(\LS(r))$ embeds all the conjugacy relations of $G_1$.
-	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
-\end{proposition}
-The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
-\begin{proposition}
-	In the group $\Gamma(\LS(r))$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
-	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
-\end{proposition}
-\begin{proof}
-	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
-	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
-	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
-	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
-\end{proof}
-
-%------------------------------------------------------------------------
-\subsection{A representation of $\Gamma(\LS(r))$}
-%------------------------------------------------------------------------
-In this section we give a representation of $\Gamma(\LS(r))$ which is built upon the representation 
-$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma(\LS(r))$ to construct the
-ideal strategy of $\LS(r)$.
-
-Before giving the representations, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
-of the representations,
-\begin{align}
-	\label{eq:w_subspace}
-	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
-\end{align}
-The basis of $W_{d-1}$ is the eigenbasis of an operator $O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}$.
+\hfc{I pointed out in the previous subsection that the definition of $C(r)$ is in the Appendix along with the definition of $\Pg_0$. 
+Since $C(r)$ is defined by $\Pg_0$, a stand-alone definition of $C(r)$
+will only confuse the reader. Are you suggesting that we don't make this a definition?}
+
+\hf{From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$ (defined in \cref{def:lsg}). Basically,
+we associate a variable $x(s)$ to each generator $s \in S$.
+Then each linear relation in $R$ can be translated to a linear equation.
+For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$.
+The construction of $\LS(r)$ proves the following theorem.}
+\begin{theorem}
+	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
+	$n(r) := 16r+75$ variables and $m(r) := 14r + 62$ equations, where each equation has $3$ variables.
+\end{theorem}
+\hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
+number of equation and variable pairs is $N(r) := 157r + 685$.}
+
+\hf{If Alice and Bob has a strategy that can win the game $\LS(r)$
+almost perfectly, then Alice and Bob has operators satisfy the 
+relation in the presentation of $\Pg$ approximately on their shared state. 
+We give the formal statement of this observation in \cref{sec:imp_lct}. }
+\carl{[This comment seems out of place.]}
+\hfc{We just delete the comment?}
+
+\hf{Since the construction of a representation of $\Gamma$ also follows the procedures detailed in Slofstra's work, 
+we defer the full definitions 
+of our representation $\Psi$ of $\Gamma$, i.e. \cref{def:rep_gamma}, till \cref{sec:rep_gamma}. 
+Instead, we present what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$.
+}  \carl{[The reader may be a little lost when you refer to ``the representation of $\Gamma$.''  A reminder of what that means would be in order.]}
+\hfc{How about now?}
+
+The representation $\Psi$ is defined on the Hilbert space
+$W_2 \x W_2 \x W_{d-1}$,
+where $W_k$ denotes a Hilbert space of
+dimension $k$.  We denote the
+standard basis of $W_k$
+by $\{\ket{x_j}\}_{j=1}^{k}$.
+The standard basis of $W_{d-1}$ is the eigenbasis of an operator $O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}$.
 Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
@@
 We use the second form of the basis when it is convenient.
-We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
-On the Hilbert space $W_2$, we define
-\begin{align*}
-	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
-	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
-	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
-\end{align*}
-\begin{definition}
-The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
-\begin{align*}
-	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
-	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
-	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
-	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
-	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
-	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
-\end{align*}
-where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
+The other basis of $W_{d-1}$ that we use is $\{ \ket{u_j} \}_{j=0}^{d-2}$ given by
 \begin{align*}
@@
 \end{align*}
-The representation of the rest of the generators
-can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
-conjugacy relations.
-\end{definition}
-We can check that
-\begin{align*}
-	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
-	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
-\end{align*}
-which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
-$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.
-
-Following the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}, we construct a representation of $G_1$.
-\begin{definition}
-The representation $\Psi_1$ of $G_1$ on $W_2 \x W_{d-1}$ is defined by
-\begin{itemize}
-\item for $f_0$ and $g_0$
-\begin{align*}
-	&\Psi_1(f_0) = X_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi_1(g_0) = Z_{W_2} \x \1_{W_{d-1}},
-\end{align*}
-\item
-for $i = 1 \dots r+5$,
-\begin{align*}
-	&\Psi_1(a_i) = \1_{W_2} \x \Psi_0(a_i) \\
-	&\Psi_1(b_i) = \ketbra{x_1}{x_1} \x \Psi_1(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
-	&\Psi_1(c_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(a_i) \\
-	&\Psi_1(d_i) =  X_{W_2} \x \Psi_0(a_i)\\
-	&\Psi_1(v_i) = Z_{W_2} \x \Psi_0(a_i).
-\end{align*}
-\item for $(i,j,k) \in C(r)$,
-\begin{align*}
-	\Psi_1(h_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(a_j) + \ketbra{x_2}{x_2} \x \Psi_1(a_k).
-\end{align*}
-\end{itemize}
-\end{definition}
-
-Finally, we follow the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017} to construct the 
-representation of $\Gamma(\LS(r))$.
-\begin{definition}
-\label{def:rep_gamma}
-The representation $\Psi$ of $\Gamma(\LS(r))$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
-\begin{itemize}
-\item for any $x$ which is also a generator of $G_1$,
-\begin{align*}
-	\Psi(x) = \1_{W_2} \x \Psi_1(x);
-\end{align*}
-\item for the generators involved in the Magic square game
-\begin{align*}
-	&\Psi(f_1) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi(g_1) = Z_{W_2} \x Z_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi(f_2) = X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi(g_2) = Z_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
-	& \Psi(m_0) = Z_{W_2} \x X_{W_2} \x \1_{W_{d-1}}\\
-	& \Psi(m_1) = X_{W_2} \x Z_{W_2} \x \1_{W_{d-1}}\\
-	& \Psi(m_2) = Y_{W_2} \x Y_{W_2} \x \1_{W_{d-1}}\\
-	& \Psi(J) = - \1_{W_2} \x \1_{W_2} \x \1_{W_{d-1}};
-\end{align*}
-\item for the generators $\{ w_i \}_{i=1}^{r+5}$:
-\begin{align*}
-	\Psi(w_i) = Z_{W_2} \x \1_{W_{d-1}} \x \Psi_0(a_i);
-\end{align*}
-\item for the generators to embed the relation $f b_i f = c_i$:
-\begin{align*}
-	\Psi(k_{i,1}) &= X_{W_2} \x \Psi_1(b_i) \\
-	%= X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_0(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
-	\Psi(k_{i,2}) &= \ketbra{x_1}{x_2} \x \Psi_1(b_if_0) + \ketbra{x_2}{x_1} \x \Psi_1(f_0b_i)\\
-%	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_2x_1}+\ketbra{x_2x_1}{x_1x_2})\x\1_{W_{d-1}}\\
-%	&+ \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_i)\\ 
-	\Psi(k_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_if_0b_i) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
-	%&= \ketbra{x_1}{x_1} \x X_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
-	\Psi(k_{i,4}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_ic_i) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	%&=\ketbra{x_1}{x_1} \x \1_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi(k_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i) 
-%	&=\ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1}) \x \1_{W_{d-1}}\\
-%	&+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_0(a_i);
-\end{align*}
-\item for the generators to embed the relation $d_i b_j d_i = c_k$ with $l = (i,j,k)$:
-\begin{align*}
-	\Psi(k_{l,1}) &= X_{W_2} \x \Psi_1(d_i) \\
-	%= X_{W_2} \x X_{W_2} \x \Psi_0(a_{i}) \\
-	\Psi(k_{l,2}) &= X_{W_2} \x \Psi_1(b_j) \\
-	%= X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
-	\Psi(k_{l,3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
-%	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_{j}a_{i}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_0(a_i)\\
-%	&+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_{i}a_{j}) \\
-	\Psi(k_{l,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_jd_ib_j) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
-	%&= \ketbra{x_1}{x_1} \x (\ketbra{x_2}{x_1} \x \Psi_0(a_ia_j)+ \ketbra{x_1}{x_2} \x \Psi_0(a_ja_i)) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_0(a_i)\\
-	\Psi(k_{l,5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	%&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_{k}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi(k_{l,6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k})
-%	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}}\\
-%	 &+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_1(a_{k}).
-\end{align*}
-\end{itemize}
-\end{definition}
-The validation of $\Psi_1$ and $\Psi$ are done in the proofs of Lemma $4.4$ and Proposition $4.2$ in Ref.~\cite{slofstra2017}.
+We denote the identity operator for the subspace $W_k$ by $\1_{W_k}$.
+Consequently, the representations of $a_1, a_2, a_3$ and $a_4$ are 
+\begin{align*}
+    \Psi(a_1) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}}\right) \\
+    \Psi(a_2) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}} \right)\\
+    \Psi(a_3) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ 
+    &+ \sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right) \Big]\\
+	\Psi(a_4) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\
+	& + \sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right)\Big].
+\end{align*}
+The tensor structure of the representations come from the construction of $\Psi$.
+These operators are important because they give representations of generators 
+$u$ and $o$ of $\Pg$ as $\Psi(a_1a_2) = \1_{W_2} \x \1_{W_2} \x O$
+and $\Psi(a_3a_4) = \1_{W_2} \x \1_{W_2} \x U$ where
+\begin{align}
+    &O = \sum_{j=1}^{d-1} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}, \\
+    &U = \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}}.
+\end{align}
+The operators $U$ and $O$ satisfy the relation $UOU\ct = O^r$.
+
+% \begin{proposition}
+% 	In the group $\Gamma(\LS(r))$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
+% 	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
+% \end{proposition}
+% \begin{proof}
+% 	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
+% 	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
+% 	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
+% 	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
+% \end{proof}
 
 %====================================================
-\section{Robust self-testing of $\ket{\EPR{2}}$ \textit{via} $\I_\alpha$}
+\section{Robust self-testing of $\ket{EPR}$ \textit{via} $\I_\alpha$}
 \label{sec:chsh}
 %====================================================
-In this section, we show how the weighted CHSH inequality can be used to self-test $\ket{\EPR{2}}$ robustly.
-Intuitively, it means that if some quantum strategy achieves a value $\ip{\I_\alpha}$ that is close to $\ip{\I_\alpha}_{\max}$,
-then the shared state must be close to $\ket{\EPR{2}}$ and their observables are close to the rotated Pauli operators 
+In this section, we show how the weighted CHSH inequality can be used to self-test $\ket{EPR}$ and Pauli operators robustly.
+Intuitively, robust self-testing means that if some quantum strategy achieves a value $\I_\alpha$ that is close to $\I_\alpha^{\max}$,
+then the shared state must be close to $\ket{EPR}$ and their observables are close to the rotated Pauli operators 
 defined in \cref{def:ideal},
 up to some local isometry.
-The formal statement is given in the theorem below. Since the proof uses the same techniques as introduced in Ref.~\cite{bamps2015},
-we defer the proof till \cref{sec:selftest}. Instead, we only list the key relations used in the proof because they will be reused in 
-\cref{sec:main} where we prove our robust self-testing result.
+The formal statement is given in the theorem below. Since the proof uses the same techniques as in Ref.~\cite{bamps2015},
+we defer the proof till \cref{sec:selftest}, and we only list the key relations used in the proof because they will be reused in 
+\cref{sec:main}.
 \begin{theorem}
@@
 	If a quantum strategy $(\ket{\psi}, \{M_x:=M_x^0-M_x^1\}_{x=1,2}, \{N_y :=N_y^0-N_y^1\}_{y = 1,2} )$ achieves that
-	$\ip{\I_\alpha} \geq \ip{\I_\alpha}_{\max} - \epsilon$
+	$\I_\alpha \geq \I_\alpha^{\max} - \epsilon$
 	for some $\epsilon > 0$, then
-	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
-	\begin{align*}
-		\| \Phi( M_x \x N_y \ket{\psi}) -\ket{aux} \x (\tM_x \x \tN_y) \ket{\EPR{2}}  \| = O(\frac{1}{\cos^2(\mu)\sin^{1/2}(\mu)}+
+	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{junk}$  such that
+	\begin{align*}
+		\| \Phi( M_x \x N_y \ket{\psi}) -\ket{junk} \x (\tM_x \x \tN_y) \ket{EPR}  \| = O(\frac{1}{\cos^2(\mu)\sin^{1/2}(\mu)}+
 		\frac{1}{\sin(\mu)^{3/2}})) \sqrt{\epsilon}
@@
 	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $\tM_x, \tN_y$ are 
-	defined in \cref{def:ideal}.  \carl{You're using both ``aux'' and ``junk'' for the auxilliary state.  Also you need
-	to be clearer about what label you are using for Alice's and Bob's systems (see my previous comment on this).}
-	\hfc{This problem should be fixed now.}
+	defined in \cref{def:ideal}.  
 \end{theorem}
-We follow the convention and define $c := \cos(\mu)$, $s := \sin(\mu)$, and
+We follow the convention \carl{[What convention?  Be a little more specific about what papers this convention is used in.]} and define $c := \cos(\mu)$, $s := \sin(\mu)$, and
 \begin{align*}
@@
 where \cref{eq:zaxaxbzb} can be derived from \cref{eq:za-zb}, \cref{eq:xa-xb} and \cref{eq:zaxa}.
+\carl{[I don't see a good reason to have such complicated error terms.  You might as well just express all error terms in terms of $\epsilon$ and $\mu$.]}  
 %==========================
@@
 the extended weighted CHSH test and a commutation test. We explain how the three tests are conducted and
-combined below.
-
-Recall that the the linear system game with solution group $\Gamma(\LS(r))$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
-equations labelled by $i \in \{1, 2 \dots \mr\}$.
-We denote the associated linear system by $H\ux = \uc$ and
-define $X_i := \{ \ux : \sum_{k} H(i,k)\ux(k) = \uc(i) \}$, which is the answer set of equation $i$,
-and $I_i = \{ k : H(i,k) = 1\}$, which is the set of all the nonzero coefficient of equation $i$.
-From the construction of $\Gamma(\LS(r))$, we know that $| I_i| = 3$ for all $i$.
-The correspondence between $\ux$ and the generators of $\Gamma(\LS(r))$ is that
-\begin{align*}
-	&\ux(j) := a_j &&&&\text{ for } j = 1 \dots r+5 \\
-	&\ux(r+6+j) := f_j&& \ux(r+9+j) := g_j &&\text{ for } j = 0,1,2 
-\end{align*} 
-The correspondence can be arbitrary for $j > r+11$.
-We conduct the linear constraint test in a way such that Bob is always get a variable label
-but Alice gets either an equation label, in which case she needs to give the full assignment to the given equation,
-or a pair of equation label and variable label, in which case she only needs to give the assignment to the particular 
-variable in the given equation. In this way, we force Alice and Bob to use an binary observable strategy 
-for the linear system game.
+combined in \cref{sec:tests}. Then the ideal strategy that can pass
+the three tests is presented in \cref{sec:ideal_strat}. The full correlation, denoted by $\fC(r,d)$, is generated by the ideal strategy and presented in \cref{sec:cor}.
+
+%----------------------------
+\subsection{The three tests}
+\label{sec:tests}
+%----------------------------
+Recall that the linear system game, $\LS(r)$ defined in \cref{def:gamma}, has $|S| = \nr$ variables and $\mr$ equations.
+The variables are labelled by $x(s)$ for each $s \in S$ and
+the equations are labelled by $i \in \{1, 2 \dots \mr\}$.
+We denote the associated linear system by $Hx = c$ and
+define $X_i := \{ \ba : \sum_{s} H(i,s)a(s) = c(i) \}$, \carl{[This definition isn't clear --- what kind of object is $\ba$?]}
+\hfc{It is a bit string.} 
+which is the answer set of equation $i$,
+and $I_i = \{ s : H(i,s) = 1\}$, which is the set of all the nonzero coefficient of equation $i$.
+From the construction of $\LS(r)$, we know that $|I_i| = 3$ for all $i$.
+The way to conduct $\LS(r)$ is as introduced in \cref{sec:intro}.
 
 In the extended weighted CHSH test,
-all the question pairs are $\{ (\ast, \ast) \} \cup \{(\ast, y), (x, \ast)\}_{x,y = \nr+1, \nr+2} \cup 
-\{(x,y)\}_{x=y \in \{\nr+1, \nr+2\}} \cup
-\{(x,y)\}_{x = 1,2, y =\nr+1, \nr+2} \cup  \{(x,y)\}_{x = \nr+1,\nr+2, y =1, 2}$.
+the question sets are $\calX = \calY = \{\ast, x(a_1), x(a_2), x_{\nr+1}, x_{\nr+2}\}$
+% all the question pairs are $\{ (\ast, \ast) \} \cup \{(\ast, y), (x, \ast)\}_{x,y = \nr+1, \nr+2} \cup 
+% \{(x,y)\}_{x=y \in \{\nr+1, \nr+2\}} \cup
+% \{(x,y)\}_{x = 1,2, y =\nr+1, \nr+2} \cup  \{(x,y)\}_{x = \nr+1,\nr+2, y =1, 2}$.
 %the input alphabets are $\calX = \calY = \{\ast, 1, 2, \nr+1,\nr+2\}$.
+\carl{[I am pretty sure your notation here is more complicated than it needs to be -- why are you using both subscripts and functions to denote variables?]}
 For each question, there is an associated answer set:
@@
 	\item when the question is $\ast$, the answer set is $\{\diamond, \perp\}$;
-	\item when the question is $1$ or $2$, the answer set is $\{0,1\}$;
-	\item when the question is $\nr+1$ or $\nr+2$, the answer set is $\{0, 1, \perp\}$.
+	\item when the question is $x(a_1)$ or $x(a_2)$, the answer set is $\{0,1\}$;
+	\item when the question is $x_{\nr+1}$ or $x_{\nr+2}$, the answer set is $\{0, 1, \perp\}$.
 \end{itemize}
-Note that when the referee wants to ask Alice $x = 1,2$, which also labels a variable of $\LS(r)$, 
-the referee gives Alice a pair $(i_x. x)$ where 
-$i_x$ labels an equation containing the variable labelled by $x$. 
-For simplicity we omit the $i_x$ part in the alphabet $\calX$.
-Later we will show that the $i_x$ part can be made implicit.
-The test is conducted in the following way:
+\carl{[This is not formal enough.
+If you're going to define a test, then you need to do it in a way that matches your earlier definition of a test.
+You should rewrite this section in a way that formally specifies each test: what its input and output alphabets are, and what its input probability distribution is.]}
+Note that when the referee wants to ask Alice $x(a_1)$ or $x(a_2)$, which also labels a variable of $\LS(r)$, 
+the referee gives Alice an equation label $i$ such that  
+the equation $i$ contains the variable $x(a_1)$ or $x(a_2)$. 
+For simplicity we omit the equation label in the alphabet $\calX$, and
+later we will show that the equation label can be made implicit.
+Only some of the question pairs of $\calX \times \calY$ are given to Alice and Bob.
+Alice and Bob's ideal behaviour to pass this test is summarized 
+below:
+\carl{[Does the phrase ``ideal behavior'' have a formal definition?
+This seems to be another case where are you are writing in a way that is sort of formal, and sort of just a sketch -- that's not a good way to write.
+Do one or the other.]}
 \begin{enumerate}
 	\item if $x = y = \ast$, Alice and Bob should answer with $a = b \in \{\diamond, \perp\}$;
-	\item if $x = y \in \{n+1, n+2\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
-	\item if $x \in \{1,2\}$ and $y \in \{n+1, n+2\}$, 
+	\item if $x = y \in \{x_{\nr+1}, x_{\nr+2}\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
+	\item if $x \in \{x(a_1),x(a_2)\}$ and $y \in \{x_{\nr+1}, x_{\nr+2}\}$, 
 		\begin{enumerate}
 		\item if they answer with $a,b \in \{0,1\}$, then
-	they should maximize $\ip{\I_{\cot(-\pi/d)}}$ with Alice and Bob's roles flipped, 
+	they should maximize $\I_{\cot(-\pi/d)}$ with Alice and Bob's roles flipped, 
 		\item if Bob answers with $\perp$, then Alice's answer doesn't matter;
 		\end{enumerate}
-	\item if $x \in \{n+1, n+2\}$ and $y \in \{1,2\}$,
+	\item if $x \in \{x_{\nr+1}, x_{\nr+2}\}$ and $y \in \{x(a_1),x(a_2)\}$,
 	\begin{enumerate} 
 		\item if they answer with $a,b \in \{0,1\}$, then
-		they should maximize $\ip{\I_{\cot(-\pi/d)}}$, 
+		they should maximize $\I_{\cot(-\pi/d)}$, 
 		\item if Alice answers with $\perp$, then Bob's answer doesn't matter;
 	\end{enumerate}
-	\item $x \in \{n+1,n+2\}, y = \ast$ 
+	\item $x \in \{x_{\nr+1},x_{\nr+2}\}, y = \ast$ 
 		\begin{enumerate}
@@
 		\end{enumerate}
-	\item $x = \ast, y \in \{n+1, n+2\}$
+	\item $x = \ast, y \in \{x_{\nr+1}, x_{\nr+2}\}$
 	\begin{enumerate}
@@
 \end{enumerate}
-
-Our commutation test is slightly different from the one used in Ref.~\cite{coladan2017verifier}.
-The commutation relations that we test are
-\begin{align*}
-    [M_{\nr+1}, M_j] = [M_{\nr+2}, M_j] = \1,
-\end{align*}
-where $j = r+6, r+8, r+9, r+11$.
-The difference is that we will examine the probability distribution 
-generated by this test and conclude that $M_{\nr+1}^0$ and $M_{\nr+1}^1$ commute with
-$M_j$ for $j = r+6, r+8, r+9, r+11$.
-we reuse questions from the two other tests so the answer
-set for each question is the same across the tests.
-There are $8$ test cases, one for each commutation relation.
-In each test case, Alice is given one of the two questions involved.
+Only the question pairs mentioned in the list above are given to Alice and Bob.
+
+Our commutation test is the same as the one used in Ref.~\cite{coladan2017verifier}.
+The goal of the commutation test is to make sure that some
+of Alice's binary observables for the other two tests 
+commute with each other when acting on the shared state
+so we reuse questions and answers from the two other tests.
+There are $8$ test cases, where each test case has two questions. 
+In each test case, Alice is given one of the two questions.
 If her question is to assign a value to some variable of $\LS(r)$,
@@
 Their answers should agree on the question that is given to both.
+The $8$ question pairs are $(x_{\nr+1}, x(s))$ and $(x(\nr+2), x(s))$ for
+$s = f_0, f_2, g_0, g_2$.
+What we conclude is slightly different from the original claim
+in Ref.~\cite{coladan2017verifier}.
+Instead of just proving the binary observables commute,
+we prove that the projective measurements
+for question $x_{\nr+1}$ commute with the binary observables for question
+$x(s)$ with $s = f_0, f_2, g_0, g_2$ 
+by examining the probability distribution generated by this test.
+
 %The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
@@
 
-In the full test, the question pairs from the three sub-tests are given to Alice and Bob with equal probability.
-The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three sub-tests. We give the ideal strategy first and then $\fC(d,r)$.
+In the full test, the three tests are conducted with equal probability.
+The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first and then $\fC(d,r)$.
 %--------------------------------------------
 \subsection{The ideal strategy}
+\label{sec:ideal_strat}
 %--------------------------------------------
-Recall the two subspaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}. 
+Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}. 
 In the ideal strategy Alice and Bob share the state 
-\begin{align*}
+\begin{equation}
+    \label{eq:tpsi}
+    \begin{aligned}
         \ket{\tpsi} = &\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
         =&\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
-\end{align*}
-Here we introduce the second basis $\{ \ket{j} \}_{j=1}^{d-1}$ of $W_{d-1}$ so that
+    \end{aligned}
+\end{equation}
+Here we introduce the third basis $\{ \ket{j} \}_{j=1}^{d-1}$ of $W_{d-1}$ so that
 the observables used in the extended weighted CHSH test have a simpler form.
@@
 \end{align*}
-We define two subspaces $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$ on
-$W_{d-1}$ and
-define $\Pi_V$ and $\Pi_{V^\perp}$ to be the corresponding projectors. Note that $V$ is the subspace on which they should maximize $\ip{\I_{\cot(-\pi/d)}}$.
+
+Alice and Bob's observables to win $\LS(r)$ are representing operators of
+the generators of $\Gamma$. The way they pick the representing operators
+is based on the correspondence between the generators of $\Gamma$ and the
+variables of $\LS(r)$. We list some of the key binary observables here:
+\begin{align}
+	\tM_i = \tN_i = 
+	\begin{cases}
+	\Psi(a_i) \quad \text{ for } 1 \leq i \leq r+5\\
+	\Psi(f_{i-r-6}) \quad \text{ for } r+6 \leq i \leq r+8\\
+	\Psi(g_{i-r-9}) \quad \text{ for } r+9 \leq i \leq r+11\\
+	\Psi(m_{i-r-12}) \quad \text{ for } r+12 \leq i \leq r+14,
+	\end{cases}
+\end{align}
+where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
+Note that Alice uses the same observable for the same variable appearing in different equations.
+
+In order to present the ideal strategy to pass the extended weighted CHSH test,
+we define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$,
+and corresponding projective measurements $\Pi_V$ and $\Pi_{V^\perp}$. Note that $V$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$.
 We define the states for the measurements used in the extended weighted CHSH test as follows
@@
 \end{align*}
-Then the measurements are
+The measurements for questions $\ast, \nr+1$ and $\nr+2$ are
 \begin{align*}
@@
 \end{align*}
-The observables for $\LS(r)$ are
-\begin{align}
-	\tM_i = \tN_i = \Psi(x_i),
-\end{align}
-where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
-Note that Alice uses the same observable for the same variable appearing in different equations.
-In particular, the action of $\tM_1, \tN_1$ and $\tM_2, \tN_2$ on the subspace $V$ can be expressed as
+When Alice and Bob gets question $1$ or $2$, what they measure on $V$ are
 \begin{align*}
@@
 \begin{proposition}
-The observables $\tM_1 = \tN_1 :=\Psi(a_1)$, $\tM_2 = \tN_2 := \Psi(a_2)$, $\tM_3 = \tN_3 := \Psi(a_3)$
-and $\tM_4 = \tN_4 := \Psi(a_4)$ satisfy the relations
-\begin{align}
-	\label{eq:mn_preserve} &\tM_i \tN_i \ket{\psi} = \ket{\psi} && \text{for } i = 1 \dots 4,\\
+The observables $\tM_j = \tN_j = \Psi(a_j)$ for $1 \leq j \leq 4$ and the shared state $\ket{\tpsi}$ defined in \cref{eq:tpsi}
+satisfy the relations
+\begin{align}
+	\label{eq:mn_preserve} &\tM_j \tN_j \ket{\tpsi} = \ket{\tpsi} && \text{for } j = 1 \dots 4,\\
 	\label{eq:o2_comm} &(\tM_3\tM_4)\tM_2(\tM_4\tM_3) = \tM_2,
@@
 	\begin{align*}
-		&\tM_1\tM_2= \sum_{j=1}^{d-1} \omega_d^{j} \ketbra{x_j}{x_j},
-		&&\tM_3\tM_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
+		\tM_3\tM_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
 	\end{align*}
@@
 
-	Next we prove \cref{eq:mn_preserve}. It is straightforward to see that $\tM_i\tN_i \ket{\tpsi} = \ket{\tpsi}$ for $i = 1,2$.
-	Before checking the two cases $i=3$ and $i=4$, we first observe that
+	Next we prove \cref{eq:mn_preserve}. It is straightforward to see that $\tM_j\tN_j \ket{\tpsi} = \ket{\tpsi}$ for $j = 1,2$.
+	Before checking the two cases $j=3$ and $j=4$, we first observe that
 	\begin{align*}
@@
     \end{align*}
-        Then we can show that $\tM_4  \tN_4 \ket{\tpsi} = \ket{\tpsi}$ because 
+    Consequently, we can show that $\tM_4  \tN_4 \ket{\tpsi} = \ket{\tpsi}$ because
     \begin{align*}
@@
 The similar result, i.e., $\tM_j\tN_j \ket{\tpsi} = \ket{\tpsi}$ for $j = 1 \dots \nr$, are easy to check because all the other observables are defined by $\tM_j, \tN_j$ for $j=1,2,3,4$.
-An interesting property of $U_A := \tM_3\tM_4$ and $O_A := \tM_1\tM_2$ is summarized in the proposition below. 
-\begin{lemma}
-	\label{lm:uo_independ}
-	The unitaries $O$ and $U$ of the form
-	\begin{align}
-		O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j} && U = \sum_{j=1}^{d-1}\ketbra{x_{j r^{-1}}}{x_j},
-	\end{align}
-	where $d$ is an odd prime number with primitive root $r$, generates
-	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
-\end{lemma}
-The proof of this lemma is provided in \cref{sec:u_and_o}.
-Our self-test argument certifies that Alice and Bob has such $O$ and $U$ in their hands, so
-this proposition provides another angle to justify our self-testing argument.
 
@@
 \subsection{The correlation $\fC(d,r)$}
+\label{sec:cor}
 %---------------------------------------------------
 The full correlation is generated by the ideal strategy presented in the previous subsection.
-To help readers understanding the proofs in \cref{sec:main} of this paper better, 
+We denote the full correlation by $\fC(d,r) = ( \tpr{ab}{xy} )$.
+To help readers understanding the proofs in \cref{sec:main} better, 
 parts of the full correlation is given in the tables below.
@@
 %=====================================
-In this section, we examine the properties of a strategy $S$ that can reproduce the
+In this section, we examine the properties of a strategy $\bS$ that can reproduce the
 correlation $\fC(d,r)$ approximately and 
-prove that the strategy $S$ must contain the state $\ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}$
+prove that the strategy $\bS$ must contain the state $\ket{EPR}^{\x 2} \x \ket{\EPR{d-1}}$
 up to some local isometry.
 
-Let us denote the full correlation by $\fC(d,r) = ( \tpr{ab}{xy} )$, then the formal statement of an approximate strategy is given below.
+We first give the definition of an approximate strategy of a fixed correlation.
 \begin{definition}
 	For a correlation $\tilde{C} = (\tpr{ab}{xy})$,
-	we say a quantum strategy $S = (\ket{\psi}, \{M_x^a\}, \{N_y^b\})$
+	we say a quantum strategy $\bS = (\ket{\psi}, \{M_x^a\}, \{N_y^b\})$
 	is an $\ep$-approximate quantum strategy of $\tilde{C}$, 
@@
 	\begin{align}
+	\label{eq:expect}
 	E_{(x,y)} \sum_{ab} |\pr{ab}{xy} - \tpr{ab}{xy}| \leq \ep.
@@
 In our full test, the probability distribution over all the question pairs $(x,y)$ is uniform.
-Since the number of all the possible question pairs is $\Theta(r^2)$ and 
+The number of all the possible question pairs is determined by
+the number of equation and variable pair of $\LS(r)$, which is
+$N(r) = \Theta(r)$.
+Considering that
 the number of possible output pairs is constant for each question pair $(x,y)$, 
-the approximate condition directly implies that, if $S$ is an $\ep$-approximate strategy
+the approximate condition in \cref{eq:expect} directly implies that, if $\bS$ is an $\ep$-approximate strategy
 of $\fC(d,r)$, then
 \begin{align*}
-    \pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy},
-\end{align*}
-for all $(a,b,x,y)$.
+    \pr{ab}{xy} \appd{O(r\ep)} \tpr{ab}{xy},
+\end{align*}
+for all $(a,b,x,y)$ of the full test.
 
 In the next three subsections, we analyze the implication of an approximate strategy to pass the 
-three subtests given in \cref{sec:full_test}.
+three tests given in \cref{sec:full_test}.
 
@@
 %------------------------------------------------------------------------------------------
-In this subsection, we use $(i,j)$ to denote the question pair so that Alice gets equation number $i$, 
-sometimes with a variable label $j$, and Bob gets a variable label $j$.
-The way we conduct the linear constraint test forces Alice to have binary observables $\{M_{ij}\}$ that satisfy 
-\cref{def:q_strat}.
+In the first half of this subsection, we use $(i,s)$ to denote the question pair so that Alice gets equation number $i$ and Bob gets a variable label $x(s)$ for some $s \in S$.
+For simplicity, we let Bob get the generator $s$ instead.
+
+The first implication of an approximate winning strategy is given in the proposition below.
 \begin{proposition}
 	\label{prop:lct_base}
-	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	Then there exist binary observables $\{ M_j \}_{j=1}^{\nr} $, such that
-	\begin{align}
-		&M_j N_j \ket{\psi} \appd{O(r\se)} \ket{\psi} \\
-		&\Pi_{j \in I_i} M_j \ket{\psi} \appd{O(r\se)}(-1)^{\uc(i)} \ket{\psi}.
+	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
+	Then there exist binary observables $\{ M(s) \}_{s \in S} $, such that
+	\begin{align}
+		&M(s) N(s) \ket{\psi} \appd{O(\sr\se)} \ket{\psi} \\
+		&\Pi_{s \in I_i} M(s) \ket{\psi} \appd{O(\sr\se)}(-1)^{\uc(i)} \ket{\psi}.
 	\end{align}
@@
 \begin{proof}
-The condition that $(\tpr{\ux b}{ij})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
-\begin{align*}
-\sum_{\ux,b: \ux \in X_i, \ux(j) = b} \tpr{\ux b}{ij} = 1
+The condition that $(\tpr{\ba b}{is})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
+\begin{align*}
+\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{is} = 1
 \end{align*}
@@
 \begin{align*}
-	\bra{\psi} M_{ij} N_j \ket{\psi} = 2 \sum_{\ux,b: \ux \in X_i, \ux(j) = b} \pr{\ux b}{ij} -1 \appd{O(r^2 \ep)} 1.
-\end{align*}
-Since $M_{ij}$ and $N_j$ are unitaries, we know that
-\begin{align*}
-	M_{ij} \ket{\psi} \appd{O(r\se)} N_j \ket{\psi} \quad \text{ for all } i \leq \mr \text{ and } j \leq \nr.
-\end{align*}
-We define $M_j := M_{ij}$ for the smallest $i$ such that $ j \in I_i$ then 
-\begin{align*}
-	M_j N_j \ket{\psi} \appd{O(r\se)} M_{ij}N_j\ket{\psi} \appd{O(r\se)} \ket{\psi} \quad \text{ for all } j \leq \nr.
-\end{align*}
-
-The definition of $M_{ij}$ tells us that 
-$
-\bra{\psi} \Pi_{j \in I_i} M_{ij} \ket{\psi} = (-1)^{\uc(i)}
-$
+	\bra{\psi} M_i(s) N(s) \ket{\psi} = 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{ij} -1 \appd{O(r \ep)} 1.
+\end{align*}
+Since $M_i(s)$ and $N(s)$ are unitaries, we know that
+\begin{align*}
+    \norm{M_i(s)\ket{\psi} - N(s)\ket{\psi}}^2 
+    = 2 - 2 \bra{\psi}M_i(s)N(s) \ket{\psi} 
+    \leq 2 - 2(1 - O(r\ep)) = O(r\ep),
+\end{align*}
 or equivalently,
 \begin{align*}
-	\Pi_{j \in I_i} M_{ij} \ket{\psi} = (-1)^{b_i} \ket{\psi}\quad\text{ for all } i \leq \mr.
-\end{align*}	
-If we replace each $M_{ij}$ with $M_j$ in the equation above, we demonstrate the effect on a
-general case that $I_i = \{j_1, j_2, j_3\}$,
-\begin{align*}
-	&\norm{ M_{ij_1}M_{ij_2}M_{ij_3} \ket{\psi} - M_{j_1}M_{j_2}M_{j_3} \ket{\psi}}\\
-	\leq & \norm{M_{ij_1}M_{ij_2}M_{ij_3} \ket{\psi} - M_{j_1}M_{ij_2}M_{ij_3} \ket{\psi}}+
-	\norm{M_{j_1}M_{ij_2}M_{ij_3} \ket{\psi} - M_{j_1}M_{j_2}M_{ij_3} \ket{\psi}} +\\
-	&\norm{M_{j_1}M_{j_2}M_{ij_3} \ket{\psi} - M_{j_1}M_{j_2}M_{j_3} \ket{\psi}}\\
-	\leq &3O(r\se) = O(r\se).
+	M_{i}(s) \ket{\psi} \appd{O(\sr\se)} N(s) \ket{\psi},
+\end{align*}
+for all $1 \leq i \leq \mr$ and $s \in S$.
+We define $M(s) := M_{i}(s)$ for the smallest $i$ such that $ s \in I_i$, then 
+\begin{align*}
+	M(s) N(s) \ket{\psi} \appd{O(\sr\se)} M_{i}(s)N(s)\ket{\psi} \appd{O(\sr\se)} \ket{\psi} \quad \text{ for all } s \leq S.
+\end{align*}
+
+The fact that $\bS$ is an $\ep$-approximate strategy also tells us that
+Alice gives satisfying assignment for each equation with probability $1 - O(r\ep)$,
+or equivalently,
+\begin{align*}
+	\Pi_{s \in I_i} M_{i}(s) \ket{\psi} \appd{O(\sr\se)} (-1)^{c(i)} \ket{\psi}
+\end{align*}
+for $1 \leq i \leq \mr$.
+If we replace each $M_{i}(s)$ with $M(s)$ in the equation above, we demonstrate the effect on a
+general case that $I_i = \{s_1, s_2, s_3\}$,
+\begin{align*}
+	&\norm{ M_{i}(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M(s_3) \ket{\psi}}\\
+	\leq & \norm{M_{i}(s_1)M_{i}(s_2)M_{i}(s_3)\ket{\psi} - M(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi}}+
+	\norm{M(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M_{i}(s_3) \ket{\psi}} +\\
+	&\norm{M(s_1)M(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M(s_3) \ket{\psi}}\\
+	\leq &3O(\sr\se) = O(\sr\se).
 \end{align*}
@@
 \begin{align*}
-	\Pi_{j \in I_i} M_j \ket{\psi} \appd{O(r\se)} (-1)^{\uc(i)}\ket{\psi} \quad \text{ for all } i \leq \mr.
-\end{align*}
+	\Pi_{s \in I_i} M(s) \ket{\psi} \appd{O(\sr\se)} (-1)^{c(i)}\ket{\psi}
+\end{align*}
+for $1 \leq i \leq \mr$.
 \end{proof}
@@
 \begin{align*}
-	\Pi_{j \in I_i} N_j \ket{\psi} \appd{O(r\se)} (-1)^{\uc(i)}\ket{\psi} \quad \text{ for all } i \leq \mr.
-\end{align*}
-
-Following the steps of the embedding of $(a_3a_4)^l a_1a_2(a_4a_3)^l = (a_1a_2)^{r^l}$ into $\Gamma(\LS(r))$,
+	\Pi_{s \in I_i} N(s) \ket{\psi} \appd{O(\sr\se)} (-1)^{c(i)}\ket{\psi} \quad \text{ for all } i \leq \mr.
+\end{align*}
+
+To make the following derivations easier to follow, we define the meaning
+for some operators to approximately satisfy some group relation.
+\begin{definition}
+    Let $S$ be a set of generators, and $\{s_i\}_{i=1}^n$ and $\{s'_j\}_{j=1}^m$
+    be two sequences of $S$.
+    Define a relation $\Pi_{i=1}^n s_i = \Pi_{j=1}^m s'_j$, denoted by $r$.
+    We say operators $\{M(s) : s \in S\}$ $\ep$-approximately satisfy the relation
+    $r$ on the state $\ket{\psi}$ if 
+    \begin{align*}
+        \Pi_{i=1}^n M(s_i)\ket{\psi} \appd{\ep} \Pi_{j=1}^m M(s'_j) \ket{\psi}. 
+    \end{align*}
+\end{definition}
+In other words, \cref{prop:lct_base} is equivalent to the following proposition.
+\begin{proposition}
+    \label{prop:lct_group}
+    Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
+	Then the observables $\{ M(s) \}_{s \in S}$ and
+	$\{N(s)\}_{s \in S}$ $O(\sr \se)$-approximately satisfy
+	each relation $r \in R$ on the shared state $\ket{\psi}$, 
+	where $S$ is the generator set of $\Gamma$
+    and $R$ is the relation set of $\Gamma$.	
+\end{proposition}
+Recall that the group $\Pg_1$ is embedded in $\Gamma$.
+Following the embedding procedure, we can prove the next proposition.
+\begin{proposition}
+    \label{prop:lct_pg1}
+    Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
+	Then the observables $\{ M(s) \}_{s \in S_1}$ and
+	$\{N(s)\}_{s \in S_1}$ $O(\sr\se)$-approximately satisfy
+	each relation $r \in R_1$ on $\ket{\psi}$, 
+	where $S_1$ is the generator set of $\Pg_1$
+    and $R_1$ is the relation set of $\Pg_1$.	
+\end{proposition}
+\begin{proof}
+    First, we prove 
+    \begin{align}
+        \label{eq:f0b1}
+        M(f_0)M(b_1)M(f_0) \ket{\psi} \appd{O(\sr\se)} M(c_1)\ket{\psi}
+    \end{align}
+    to demonstrate the techniques.
+    From the fact that Alice's observables $O(r\se)$-approximately satisfy the linear equations, we can get that
+    \begin{align*}
+        &M(f_0) \ket{\psi} \appd{O(\sr \se)} M(f_1)M(f_2)\ket{\psi} \\
+        &M(b_1) \ket{\psi} \appd{O(\sr \se)} M(f_2)M(p_{1,1}) \ket{\psi}\\
+        &M(f_0) \ket{\psi} \appd{O(\sr \se)} M(p_{1,3})M(p_{1,4}) \ket{\psi}
+    \end{align*}
+    Then we show how to expand $M(f_0)M(b_1)M(f_0)\ket{\psi}$
+    with the three equations above. The trick is to flip some 
+    operators to Bob's side using the relation $M(s) \ket{\psi} \appd{O(\sr \se)} N(s)\ket{\psi}$.
+    \begin{align*}
+        M(f_0)M(b_1)M(f_0) \ket{\psi} 
+        &\appd{O(\sr \se)}M(f_0)M(b_1)M(p_{1,3})M(p_{1,4}) \ket{\psi} \\
+        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})M(f_0)M(f_2)M(p_{1,1}) \ket{\psi} \\
+        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)M(f_0) \ket{\psi} \\
+        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)M(f_1)M(f_2) \ket{\psi} \\
+        & \appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)N(f_2)N(f_1) \ket{\psi} \\
+        &= N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_1) \ket{\psi} \\
+        & \appd{O(\sr \se)} M(f_1)M(p_{1,1})M(p_{1,3})M(p_{1,4}) \ket{\psi}
+    \end{align*}
+    In the rest of the proof, we skip the steps of flipping observables from Alice to Bob's side and then back.
+    \begin{align*}
+        M(f_0)M(b_1)M(f_0) \ket{\psi}
+        &\appd{O(\sr \se)} M(f_1)M(p_{1,1})M(p_{1,3})M(p_{1,4}) \ket{\psi}\\
+        &\appd{O(\sr \se)} M(f_1)M(p_{1,2})M(p_{1,4})\ket{\psi} \\
+        &\appd{O(\sr \se)} M(p_{1,5})M(p_{1,4})\ket{\psi} \\
+        & \appd{O(\sr \se)} M(c_1) \ket{\psi},
+    \end{align*}
+    where from the second line to the third line, we used
+    the relation $M(p_{1,1})M(p_{1,2})M(p_{1,3})\ket{\psi} \appd{O(\sr \se)} \ket{\psi}$, and from the third line to the
+    fourth line, we used the relation 
+    $M(c_1)M(p_{1,4})M(p_{1,5})\ket{\psi} \appd{O(\sr \se)} \ket{\psi}$.
+    The proof for the other relations are similar.
+\end{proof}
+Note that essentially the proof above follows the proof of 
+\cref{prop:g1gamma}. Then we can follow the proof of \cref{prop:g0g1}
+to prove the next proposition.
+\begin{proposition}
+    \label{prop:lct_pg0}
+    Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
+	Then the observables $\{ M(s) \}_{s \in S_0}$ and 
+	$\{N(s)\}_{s \in S_0}$ $O(\sr \se)$-approximately satisfy
+	each relation $r \in R_0$ on the shared state $\ket{\psi}$, 
+	where $S_0$ is the generator set of $\Pg_0$
+    and $R_0$ is the relation set of $\Pg_0$.	
+\end{proposition}
+Following the steps of the embedding of $(a_3a_4)^l a_1a_2(a_4a_3)^l = (a_1a_2)^{r^l}$ into $\Gamma$ presented in
+the proof of \cref{prop:g0},
 we can prove the following proposition.
@@
 \label{prop:lct_adv}
-Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $\{M_j, N_j\}_{j \in \nr}$ be the observables defined in 
-\cref{prop:lct_base}. 
+Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $\{M(s), N(s)\}_{s \in S}$ be the observables defined in 
+\cref{prop:lct_group}. 
 Then,
 \begin{align}
-	&M_1M_2 (M_4M_3)^l \ket{\psi}\appd{O(r^{l+1} \se)} (M_4M_3)^l (M_1M_2)^{r^l} \ket{\psi}, \\
-	&N_1N_2 (N_4N_3)^l \ket{\psi}\appd{O(r^{l+1} \se)} (N_4N_3)^l (N_1N_2)^{r^l} \ket{\psi}, 
+	&M(a_1)M(a_2) (M(a_4)M(a_3))^l \ket{\psi}\appd{O(r^{l+1/2} \se)} (M(a_4)M(a_3))^l (M(a_1)M(a_2))^{r^l} \ket{\psi}, \\
+	&N(a_1)N(a_2) (N(a_4)N(a_3))^l \ket{\psi}\appd{O(r^{l+1/2} \se)} (N(a_4)N(a_3))^l (N(a_1)N(a_2))^{r^l} \ket{\psi}, 
 \end{align}
@@
 \begin{proof}
-The $l = 1$ case follows from the fact that $\Gamma(\LS(r))$ embeds $O(r)$ conjugacy relations and 
-all the $O(r)$ conjugacy relations are used in the derivation of $(a_3a_4)a_1a_2(a_4a_3) = (a_1a_2)^r$, so we 
-have
+Proving the $l=1$ case is essentially proving that observables 
+$\{M(a_i)\}_{i=1}^4$ and $\{N(a_i)\}_{i=1}^4$
+$O(r^{3/2} \se)$-approximately satisfy the relation 
+$(a_3a_4)(a_1a_2)(a_4a_3) = (a_1a_2)^r$ on the shared state $\ket{\psi}$.
+The derivation follows the proof of \cref{prop:g0}.
+The $O(r^{3/2}\se)$ approximation error comes from the fact that 
+the derivation uses $r+3$ conjugacy relations of $R_0$, 
+so we have
 \begin{align}
 	\label{eq:ls_comm_rel}
-	M_1M_2 (M_4M_3) \ket{\psi} \appd{O(r^2\se)} (M_4M_3)(M_1M_2)^r \ket{\psi}.
+	M(a_1)M(a_2) (M(a_4)M(a_3)) \ket{\psi} \appd{O(r^{3/2}\se)} (M(a_4)M(a_3))(M(a_1)M(a_2))^r \ket{\psi}.
 \end{align}
@@
 \begin{align*}
-	M_1M_2 (M_4M_3)^{n+1} \ket{\psi}  &\appd{O(r\se)} (N_3N_4) M_1M_2(M_4M_3)^n \ket{\psi} \\
-	&\appd{O(r^{n+1}\se)} (N_3N_4) (M_4M_3)^n (M_1M_2)^{r^n} \ket{\psi}\\
-	&\appd{O(r\se)} (M_4M_3)^n (M_1M_2)^{r^n} (M_4M_3) \ket{\psi} \\
-	& \appd{O(r^{n+2} \se)} (M_4M_3)^{n+1} (M_1M_2)^{r^{n+1}} \ket{\psi},
+	M(a_1)M(a_2) (M(a_4)M(a_3))^{n+1} \ket{\psi}  &\appd{O(\sr \se)} (N(a_3)N(a_4)) M(a_1)M(a_2)(M(a_4)M(a_3))^n \ket{\psi} \\
+	&\appd{O(r^{n+1/2}\se)} (N(a_3)N(a_4)) (M(a_4)M(a_3))^n (M(a_1)M(a_2))^{r^n} \ket{\psi}\\
+	&\appd{O(\sr \se)} (M(a_4)M(a_3))^n (M(a_1)M(a_2))^{r^n} (M(a_4)M(a_3)) \ket{\psi} \\
+	& \appd{O(r^{n+3/2} \se)} (M(a_4)M(a_3))^{n+1} (M(a_1)M(a_2))^{r^{n+1}} \ket{\psi},
 \end{align*}
 where from the second to the last line we repeat the process of applying \cref{eq:ls_comm_rel} 
-and the relation $(M_1M_2)^r \ket{\psi} \appd{O(r^2\se)} (N_1N_2)^r \ket{\psi}$, $r^n$ times.
+and the relation $(M(a_1)M(a_2))^r \ket{\psi} \appd{O(r^{3/2}\se)} (N(a_1)N(a_2))^r \ket{\psi}$, $r^n$ times.
 In summary, we have 
 \begin{align}
-	M_1M_2(M_4M_3)^{n+1} \ket{\psi} \appd{O(r^{n+2} \se)} (M_4M_3)^{n+1} (M_1M_2)^{r^{n+1}}\ket{\psi}.
-\end{align}
-By the principal of proof by induction, the proof is complete.
-The proof for Bob's observables $\{ N_j \}_{j=1}^{\nr}$ is similar.
+	M(a_1)M(a_2)(M(a_4)M(a_3))^{n+1} \ket{\psi} \appd{O(r^{n+3/2} \se)} (M(a_4)M(a_3)^{n+1} (M(a_1)M(a_2))^{r^{n+1}}\ket{\psi}.
+\end{align}
+By the principal of induction, the proof is complete.
+The proof for Bob's observables $\{ N(s) \}_{s \in S}$ is similar.
 \end{proof}
@@
 
-Recall that we define $O_A = M_1M_2$ and $U_A=M_3M_4$, then
+If we define $O_A := M(a_1)M(a_2)$ and $U_A := M(a_3)M(a_4)$, then
 the conclusion of \cref{prop:lct_adv} can be rewritten as 
 \begin{align*}
-	 O_A (U_A\ct)^n \ket{\psi} \appd{O(r^{n+1} \se)} (U_A\ct)^n O_A^{r^n} \ket{\psi}.
-\end{align*}
-On Bob's side, we also define $O_B = N_1N_2$ and $U_B = N_3N_4$ 
+	 O_A (U_A\ct)^n \ket{\psi} \appd{O(r^{n+1/2} \se)} (U_A\ct)^n O_A^{r^n} \ket{\psi}.
+\end{align*}
+On Bob's side, we also define $O_B = N(a_1)N(a_2)$ and $U_B = N(a_3)N(a_4)$, 
 and the similar relation holds.
 
-The other relations that are embedded in $\Gamma_r$ are 
-\begin{align}
-	\label{eq:comm}&[f_0, a_i] = [f_2, a_i] = [g_0, a_i] = [g_2, a_i] = e \text{ for all } i = 1 \dots r+5 \\
-	\label{eq:mg1}&f_0g_0 = Jg_0f_0 \\
-	\label{eq:mg2}&f_2g_2 = J g_2 f_2.
-\end{align}
+The other relations that are embedded in $\Gamma$ are 
+$f_0g_0 = Jg_0f_0$ and $f_2g_2 = Jg_2 f_2$.
 We summarize the implications in the following proposition.
@@
 	\label{prop:lct_comm}
-	Let $S$, $\{M_j, N_j\}_{j=1}^{\nr}$ be the strategy and observables defined in \cref{prop:lct_base}.
+	Let $\bS$, $\{M(s), N(s)\}_{s \in S}$ be the strategy and observables defined in \cref{prop:lct_group}.
 	Then,
 	\begin{align}
-		&M_{r+6} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+6} \ket{\psi} && 
-		M_{r+8}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+8} \ket{\psi} \\
-		&M_{r+9} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+9} \ket{\psi} && 
-		M_{r+11}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+11} \ket{\psi} 
-	\end{align}
-	for all $j = 1 \dots r+5$, and
-	\begin{align}
-		&M_{r+6}M_{r+9} \ket{\psi} \appd{O(r\se)} -M_{r+9}M_{r+6} \ket{\psi} \\
-		&M_{r+8}M_{r+11} \ket{\psi} \appd{O(r\se)} -M_{r+11}M_{r+8} \ket{\psi}.
+		&M(f_0)M(g_0) \ket{\psi} \appd{O(\sr \se)} -M(g_0)M(f_0) \ket{\psi} \\
+		&M(f_2)M(g_2) \ket{\psi} \appd{O(\sr \se)} -M(g_2)M(f_2) \ket{\psi}.
 	\end{align}
 \end{proposition}
-Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma(\LS(r))$,
-so this proposition can be proved with the same techniques used in the proof of \cref{prop:lct_base}.
+Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma$,
+so this proposition can be proved with the same techniques used in the proof of \cref{prop:lct_group}.
 %------------------------------------------------------------------------------------------
@@
 Recall that the implication of $S$ being an $\ep$-approximate strategy is that 
-$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$ for all question and answer pairs $(x,y)$ and $(a,b)$.
+$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$ for all question 
+pair $(x,y)$ and answer pair $(a,b)$.
 From the correlation, we can observe that
@@
 \appendix
+
+%===========================================
+\section{Embedding $\Pg$ into $\Gamma$}
+\label{sec:embedding}
+%===========================================
+This section supports \cref{sec:embed_idea} by giving the definitions
+of $\Pg_0$ and $\Pg_1$.
+We also prove some properties of the generators of $\Pg_0$, $\Pg_1$ and 
+$\Gamma$ along the way.
+
+Recall that the goal of introducing $\Pg_0$ is to embed
+$\Pg$ in a group with only order-$2$ generators,
+so that it is easier to embed $\Pg$ into a solution group.
+\begin{definition}	
+\label{def:g0}
+	Let the set $S_0$ be 
+	\begin{align*}
+		S_0 = \{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5,
+	\end{align*}
+	and the set $R_0$ be the union of 
+	\begin{align*}
+	&R_{base} = \{s^2 = e | s \in S\},\\
+	&R_{u} = \{ u_3 = u_2o_1u_2 \quad u_4 = u_2o_2u_2 \quad 
+	u_5 = u_1u_3u_1 \quad o_2 = u_1u_4u_1 \quad u_5 = o_1 o_r o_1\},
+	\end{align*}
+	and 
+	\begin{align*}
+	R_o = 
+	\begin{cases} 
+	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1 \quad o_{2+2j} = o_2o_{1+2j}o_2\} \quad \text{ if $r$ is even },\\
+	\{o_3 = o_2o_1o_2\} \cup \bigcup_{j=1}^{(r-3)/2}\{
+	 o_{2+2j} =o_1o_{1+2j}o_1 \quad o_{3+2j} = o_2o_{2j+2}o_2 \}\quad\text{ if $r$ is odd }.
+	\end{cases}
+	\end{align*}
+	The group $\Pg_0$ is a group with presentation $\ip{R_0:S_0}$.
+\end{definition}
+\begin{proposition}
+    \label{prop:g0}
+	The group $\Pg$ is embedded in $\Pg_0$.
+	Furthermore, the generators of $\Pg_0$ satisfy the relation 
+	\begin{align}
+	    \label{eq:uo_rel}
+		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
+	\end{align}
+	for any $ j \in \N$.
+\end{proposition}
+\begin{proof}
+    We prove that $\Pg$ is embedded in $\Pg_0$ by prove the $j = 1$ case of \cref{eq:uo_rel}.
+    After it is proven, a homomorphism $\phi: \Pg \rightarrow \Pg_0$ such that $\phi(u) = u_1u_2$ and $\phi(o) = o_1o_2$ is injective by Proposition $33$
+    and Lemma $15$ of Ref.~\cite{slofstra2017}.
+
+	We prove \cref{eq:uo_rel} by induction.
+	The base case follows the direct calculation given below
+	\begin{align*} 
+		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
+	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
+	=& u_5 o_2\\
+	=& o_1o_ro_1 o_2.
+	\end{align*}
+	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above, which 
+	proves the $j=1$ case.
+
+	Now assume the statement is true for $j = n$, then for $j = n+1$
+	\begin{align*}
+		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
+		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
+		 =& (o_1o_2)^{r^{n+1}},
+	\end{align*}
+	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$, and
+	from the second line to the third line, we applied the $j=1$ case. Hence, the statement is true.
+\end{proof}
+To better characterize all the conjugacy
+relations of $\Pg_0$ and simplify the form of $\Pg_0$, 
+we relabel $u_i$ and $o_i$'s
+as $a_i$'s such that
+\begin{align}
+	a_j := 
+	\begin{cases}
+	 o_j \text{ for } j = 1,2 \\
+	 u_{j-2} \text{ for } j = 3\dots 7 \\
+	 o_{j-5} \text{ for } j = 8 \dots r+5.
+	\end{cases}
+\end{align}
+Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
+\begin{align}
+\label{eq:cr}
+	C(r) = \{ (i,j,k) |  (a_ia_ja_i = a_k) \in R_0 \}.
+\end{align}
+The size of $C(r)$ is $r+3$. 
+A presentation of the group $\Pg_0$ is
+\begin{align*}
+    \Pg_0 = \ip{ \{a_i\}_{i=1}^{r+5} : \{a_i^2 =e \}_{i=1}^{r+5} \cup \{ a_ia_ja_i = a_k \vert (i,j,k) \in C(r)\}}.
+\end{align*}
+
+Next we define the group $\Pg_1$.
+\begin{definition}
+\label{def:g1}
+Define the set $S_1$ to be
+\begin{align*}
+	S_1 = \{a_i, b_i, c_i, d_i\}_{i=1}^{r+5} \cup \{ f_0 \} \cup \{h_{jk}\}_{(i,j,k) \in C(r)},
+\end{align*}
+and the set $R_1$ to be
+\begin{align*}
+	R_1 = &\{ s^2 = e \vert s \in S_1\}\\ 
+	&\cup 
+	\{a_i = b_ic_i = f_0d_i, \quad f_0b_if_0 =c_i\}_{i= 1}^{r+5} \\ 
+	&\cup
+	\{h_{jk}b_j c_k = e, \quad d_ib_jd_i = c_k\}_{(i,j,k) \in C(r)}.
+\end{align*}
+The group $\Pg_1$ is a group with the presentation $\ip{S_1 : R_1}$.
+\end{definition}
+Note that the group $\Pg_1$ is the same as the group $K$ used in the proof of Lemma $29$ of Ref.~\cite{slofstra2017}.
+
+The relation between $\Pg_0$ and $\Pg_1$ is summarized in the propositions below, which was first proved in Lemma $29$ of \cite{slofstra2017}.
+\begin{proposition}
+    \label{prop:g0g1}
+	The group $\Pg_0$ is embedded in $\Pg_1$. 
+\end{proposition}
+\begin{proof}
+    We prove this proposition by showing that generators $a_i$'s in $S_1$
+    satisfy the relation $a_i a_j a_i = a_k$ for all $(i,j,k) \in C(r)$.
+    This means the homomorphism $\phi: \Pg_0 \rightarrow \Pg_1$ that maps $a_i$
+    to $a_i$ is homomorphism from $\Pg_0$ to $\Pg_1$. 
+    The injectivity of $\phi$ follows Lemma $29$ and Lemma $15$ of Ref.~\cite{slofstra2017}.
+
+	We first show that $d_i c_j d_i = b_k$, which is because
+	\begin{align*}
+		d_i c_j d_i = d_i (f_0 b_j f_0) d_i = f_0 (d_i b_j d_i) f_0 = f_0 c_k f_0 = b_k.
+	\end{align*}
+	Then, we can prove that 
+	\begin{align*}
+		a_i a_j a_i = f_0 d_i b_j c_j f_0 d_i 
+		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
+		= (f_0 c_k f_0)(f_0 b_k f_0) 
+		= b_k c_k = a_k,
+	\end{align*}
+	where we use the fact that $f_0$ commutes with $d_i$.
+\end{proof}
+The consequence of this proposition is that $\Pg$ can be embedded in $\Pg_1$.
+
+Recall the definition of $\Gamma$ in \cref{def:gamma}. We prove a property of it.
+\begin{proposition}
+    \label{prop:g1gamma}
+	The group $\Pg_1$ can be embedded in $\Gamma$.
+	The generators of $\Gamma$ also satisfy the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
+\end{proposition}
+\begin{proof}
+    To prove the first claim, we show that the generators
+    $b_i$, $c_i$, $d_i$ satisfy the relations
+    $d_ib_jd_i = c_k$ for each $\bc = (i,j,k) \in C(r)$.
+    \begin{align*}
+        d_ib_jd_i =& (k_{\bc 1} f_2)(f_2 k_{\bc 2})(k_{\bc 4} k_{\bc 5})\\ 
+        =& k_{\bc 1}(k_{\bc 2}k_{\bc 4})k_{\bc 5} \\
+        =& (k_{\bc 1} k_{\bc 3}) k_{\bc 5} \\
+        =& k_{\bc 6} k_{\bc 5} \\
+        =& c_k.
+    \end{align*}
+    The derivation of $f_0 b_i f_0 = c_i$ is similar for $1 \leq i \leq r+5$, so we omit it here.
+    A map $\phi:\Pg_1 \rightarrow \Gamma$ that maps $s$
+    to $s$ for each $s \in S_1$ is a homomorphism between $Pg_1$ and 
+    $Gamma$. It is also injective by Proposition $27$ and Lemma $15$ of 
+    Ref.~\cite{slofstra2017}.
+
+    The second claim follows a similar derivation, so we omit it here too.
+\end{proof}
+Since $\Pg$ is embedded in $\Pg_1$, we can conclude that
+$\Pg$ is embedded in $\Gamma$ as well.
+%========================================
+\section{Definition of $\LS(r)$}
+\label{sec:lsg_def}
+%========================================
+\begin{definition}
+    \label{def:lsg}
+    The linear system game $\LS(r)$ has 
+    variables $x(s)$ for each $s \in S$, and equations:
+    \begin{itemize}
+        \item for each $1 \leq i \leq r+5$:
+        \begin{align*}
+            & x(a_i) + x(b_i) + x(c_i) = 0
+            && x(a_i) + x(f_0) + x(d_i) = 0 \\
+            & x(b_i) + x(f_2) + x(p_{i,1}) = 0 
+            && x(p_{i,2}) + x(p_{i,3}) + x(p_{i,4}) = 0 
+            && x(f_0) + x(p_{i,3}) + x(p_{i,4}) = 0\\
+            & x(c_i) + x(p_{i,4})+x(p_{i,5}) = 0
+            && x(f_1) + x(p_{i,2}) + x(p_{i,3}) = 0; 
+        \end{align*}
+        \item for each $\bc = (i,j,k) \in C(r)$:
+        \begin{align*}
+            & x(h_{jk}) + x(b_j) + x(c_k) = 0 \\
+            & x(d_i) + x(q_{\bc, 1}) + x(f_2) = 0 
+            && x(b_j) + x(f_2) + x(q_{\bc, 2}) = 0 
+            && x(q_{\bc, 2}) + x(q_{\bc, 3}) + x(q_{\bc, 4}) = 0 \\
+            & x(d_i) + x(q_{\bc, 4}) + x(q_{\bc, 5}) = 0 
+            && x(c_k) + x(q_{\bc, 5}) + x(q_{\bc, 6}) = 0 
+            && x(q_{\bc, 1}) + x(q_{\bc, 3}) + x(q_{\bc, 6}) = 0;
+        \end{align*}
+        \item Magic Square equations:
+        \begin{align*}
+            &x(f_0) + x(f_1) + x(f_2) = 0 &&
+            x(g_0) + x(g_1) + x(g_2) = 0 &&
+            x(m_0) + x(m_1) + x(m_2) = 0 \\
+            &x(f_0) + x(g_2) + x(m_0) = 0 &&
+            x(f_2) + x(g_0) + x(m_1) = 0 &&
+            x(f_1) + x(g_1) + x(m_2) = 1.
+        \end{align*} 
+    \end{itemize}
+\end{definition}
+%================================================
+\section{A representation of $\Gamma$}
+\label{sec:rep_gamma}
+%================================================
+In this section we give the full description of a representation of $\Gamma$, 
+which is built upon representations 
+of $\Pg_0$ and $\Pg_1$. We need the representation of $\Gamma$ to construct the
+ideal strategy of $\LS(r)$.
+
+Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}, which are the carrier spaces
+of the representations given below,
+On the Hilbert space $W_2$, we define
+\begin{align*}
+	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
+	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
+	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
+\end{align*}
+\begin{definition}
+\label{def:rep_g0}
+The representation, $\Psi_0$, of $\Pg_0$ on $W_{d-1}$ is defined by
+\begin{align*}
+	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
+	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
+	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
+	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
+	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
+	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
+\end{align*}
+The representation of the rest of the generators
+can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the defining 
+conjugacy relations of $\Pg_0$.
+\end{definition}
+We can check that
+\begin{align*}
+	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
+	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
+\end{align*}
+which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
+$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.
+
+Following the proof of Lemma $29$ of Ref.~\cite{slofstra2017}, we construct a representation of $\Pg_1$.
+\begin{definition}
+\label{def:rep_g1}
+The representation $\Psi_1$ of $\Pg_1$ on $W_2 \x W_{d-1}$ is defined by
+\begin{itemize}
+\item for $f_0$
+\begin{align*}
+	&\Psi_1(f_0) = X_{W_2} \x \1_{W_{d-1}};
+\end{align*}
+\item
+for $i = 1 \dots r+5$,
+\begin{align*}
+	&\Psi_1(a_i) = \1_{W_2} \x \Psi_0(a_i) \\
+	&\Psi_1(b_i) = \ketbra{x_1}{x_1} \x \Psi_1(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
+	&\Psi_1(c_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(a_i) \\
+	&\Psi_1(d_i) =  X_{W_2} \x \Psi_0(a_i);
+\end{align*}
+\item for $(i,j,k) \in C(r)$,
+\begin{align*}
+	\Psi_1(h_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(a_j) + \ketbra{x_2}{x_2} \x \Psi_1(a_k).
+\end{align*}
+\end{itemize}
+\end{definition}
+
+Finally, we follow the proof of Proposition $27$ of Ref.~\cite{slofstra2017} to construct the 
+representation of $\Gamma$.
+\begin{definition}
+\label{def:rep_gamma}
+The representation $\Psi$ of $\Gamma$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
+\begin{itemize}
+\item for $s \in \{a_i, b_i, c_i, d_i\}_{i=1}^{r+5}$,
+\begin{align*}
+	\Psi(s) = \1_{W_2} \x \Psi_1(s);
+\end{align*}
+\item for $f_i$, $g_i$, $m_i$ with $i = 0,1,2$ and $J$
+\begin{align*}
+    &\Psi(f_0) = \1 \x X_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi(f_1) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi(f_2) = X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi(g_0) = \1 \x Z_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi(g_1) = Z_{W_2} \x Z_{W_2} \x \1_{W_{d-1}} \\
+	&\Psi(g_2) = Z_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
+	& \Psi(m_0) = Z_{W_2} \x X_{W_2} \x \1_{W_{d-1}}\\
+	& \Psi(m_1) = X_{W_2} \x Z_{W_2} \x \1_{W_{d-1}}\\
+	& \Psi(m_2) = Y_{W_2} \x Y_{W_2} \x \1_{W_{d-1}}\\
+	& \Psi(J) = - \1_{W_2} \x \1_{W_2} \x \1_{W_{d-1}};
+\end{align*}
+\item for the generators involved in $R_i$
+with $1 \leq i \leq r+5$ :
+\begin{align*}
+	\Psi(p_{i,1}) &= X_{W_2} \x \Psi_1(b_i) \\
+	\Psi(p_{i,2}) &= \ketbra{x_1}{x_2} \x \Psi_1(b_if_0) + \ketbra{x_2}{x_1} \x \Psi_1(f_0b_i)\\
+	\Psi(p_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_if_0b_i) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
+	\Psi(p_{i,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_ic_i) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+    \Psi(p_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i);
+\end{align*}
+\item for the generators involved in $R_{\bc}$ with $\bc = (i,j,k) \in C(r)$:
+\begin{align*}
+	\Psi(q_{\bc, 1}) &= X_{W_2} \x \Psi_1(d_i) \\
+	\Psi(q_{\bc, 2}) &= X_{W_2} \x \Psi_1(b_j) \\
+	\Psi(q_{\bc, 3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
+	\Psi(q_{\bc, 4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_jd_ib_j) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
+	\Psi(q_{\bc, 5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
+	\Psi(q_{\bc, 6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k}).
+\end{align*}
+\end{itemize}
+\end{definition}
+The validation of $\Psi_1$ and $\Psi$ were done in the proofs of 
+Lemma $29$ and Proposition $27$ in Ref.~\cite{slofstra2017}.
 %========================================
@@
 \end{proof}
-%%=====================================
-\section{The proof of \cref{lm:uo_independ}}
-\label{sec:u_and_o}
-%%=====================================
-
-We are going to prove 
-the set $\{U^k O^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of the ring of $(d-1)\times (d-1)$ matrices over $\C$
-Note that the unitaries $U$ and $O$ defined in the lemma above satisfy the condition $UOU^\dagger = O^r$.
-In this proof, we denote the set $\{0,1,2\dots d-2\}$ by $[d-1]$ and the set $\{1,2 \dots d-1\}$ by $[d-1]+1$.
-\begin{proof}
-We are going to show the $(d-1)^2$ matrices from the set $\{U^k O^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
-Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
-such that 
-\begin{align}
-	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k O^l = 0. 
-\end{align}
-We \hf{define} a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
-\carl{We shouldn't be making extra assumptions that are not stated in the lemma.  This looks to me more like
-a definition of the variables $\{ k_i \}$, rather than an assumption.}
-The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
-Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
-where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
-Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.
-
-We start with proving that $\ket{x_{k_1}} = 0$.
-Proving $\ket{x_{k_i}} = 0$ for other $i$ follows a similar argument, so we briefly
-discuss about it in the end.
-The entry $\bra{1}M\ket{1}$ can be expressed as  
-\begin{align}
-	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i (r^{-1})^k}\braket{i}{1}.
-\end{align}
-For the term $\braket{1}{i (r^{-1})^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
-$k = k_1$. We can conclude that 
-\begin{align}
-	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
-\end{align}
-Similarly we can determine that for all $j = 1,2\dots d-1$,
-\begin{align}
-	\bra{j}M\ket{j} 
-	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i (r^{-1})^k}\braket{i}{j} 
-	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
-\end{align}
-Hence we get $d-1$ equations with $d-1$ variables, and the linear system is
-\begin{align}
-	W \ket{x_{k_1}} = 0,
-\end{align}
-where $W(m,n) = \omega_d^{mn}$. Then we define
-\begin{align}
-	\tW = 
-	\begin{pmatrix}
-	1 & 1 \\
-	1 & W
-	\end{pmatrix}.
-\end{align}
-First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
-Next, we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
-and prove that it satisfies the condition
-that 
-\begin{align}
-	\tW \ket{\tx_{k_1}} = 0,
-\end{align}
-which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
-We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which is required by the first row of $\tW$.
-It can be proved by summing the known $d-1$ equations as follows
-\begin{align}
-	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
-	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
-	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
-	= \sum_{l = 1}^{d-1}- x_{k_1,l}
-\end{align}
-where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
-Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.
-
-For $\ket{x_{k_a}}$, we look at entries $\{\bra{j}M\ket{aj}\}_{j=1}^{d-1}$ for $a = 2 \dots d-1$ and get equations
-of the form
-\begin{align}
-	0 = \bra{j}M\ket{aj} = \sum_{l=1}^{d-1} x_{k_a, l} \omega_d^{ajl} 
-\end{align}
-The corresponding coefficient matrix has value $\omega_d^{amn}$ at coordinate $(m,n)$,
-so it is also a submatrix of a Vandermonde matrix. Similar argument gives us that $\ket{x_{k_a}} = 0$.
-
-To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
-$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
-\carl{Nice proof.  I like the use of the Vandermonde matrix.  We can think a little about possible simplifications.}
-\end{proof}
 

### 2019-07-09 Draft/draft.tex
changes to main text and reference list

@@
 \newcommand{\sr}{\sqrt{r}}
+\newcommand{\qr}{r^{1/4}}
 \newcommand{\qd}{d^{1/4}}
@@
 delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
-\cite{miller2017,fu2018,eat2018}.
-\hfc{Which DIQKD paper should I cite?}
+\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
 \carl{Two possible papers that you could cite are Mayer Yao 1998 (which originated the idea of self-testing as far as I know, and mentions QKD) and my paper (miller2017, which you've already cited --- indeed it uses the concept of self-testing).
@@
 (It was the first to fully prove DI-QKD.)}
-
-The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
-one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
-pair in parallel \cite{mckague2016, coladan2016parallel, lowdegree}. 
+\hfc{checked.}
+
+The case of self-testing $2$-dimensional EPR pair is fully understood.
+The techniques for robustly self-testing one EPR pair is 
+first introduced in Ref.~\cite{mckague2012}, then improved in Ref.~\cite{bamps2015}. 
+Ref.~\cite{yang2013} started to think about how to robustly self-testing large dimensional maxially entangled states.
+Its ideas are realized later in Ref.~\cite{coladan2017all}, which proved that all pure bipartite entangled state 
+can be self-tested.
+One can also self-test many copies of the $2$-dimensional EPR
+pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
+The most efficient way uses $O(\log n)$ bits question and
+answers to self-test $n$ copies of $2$-dimensional EPR
+pair \cite{lowdegree}.
 \carl{I believe the first to prove robust self-testing of a single EPR pair was McKague-Yang-Scarani 2012.}
+\hfc{Got it.}
 Self-testing general $d$-dimensional EPR pairs is a harder task.
@@
 \hfc{I thought the fact that $\{s_j\}$ is a subset of $S$ guarantees that there will be no repetitions in a linear relation.}
+There are two special types of groups that we will work with in \cref{sec:lsg}. We give the definitions below.
+\begin{definition}
+    \label{def:spe_conj_grp}
+    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
+    Let
+    \begin{align*}
+        \Gamma = \ip{\{s_i\}_{i \in [n]}  :
+        \{s_i^2=e\}_{i\in [n]} \cup 
+        \{ s_i s_j s_i = s_k\}_{(i,j,k)\in C}}.
+    \end{align*}
+    We say a group is a conjugacy group if it has a presentation of this form. 
+\end{definition}
+A conjugacy group is a special case of what Slofstra defined as 
+a linear-plus-conjugacy group (Definition $26$ of Ref.~\cite{slofstra2017}). The difference is that a conjugacy group does not have linear relations. The next definition follows the 
+definition of a nice linear-plus-conjugacy group (Definition $28$ of \cite{slofstra2017}).
+\begin{definition}
+    \label{def:nice_conj_grp}
+    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
+    Let 
+    \begin{align*}
+        \Gamma = \ip{\{s_i\}_{i \in [n]} \cup \{s_{jk}\}_{(i,j,k)\in C} :
+        \{s_i^2=e\}_{i\in [n]} \cup 
+        \{s_{jk}^2 = e, s_is_js_i = s_k, s_{jk}s_js_k = e\}_{(i,j,k)\in C}}.
+    \end{align*}
+    We say a group is a nice conjugacy group if it has a presentation of this form. 
+\end{definition}
+The relation $s_{jk} s_js_k = e$ implies that $s_j$ commutes with $s_k$
+because
+\begin{align*}
+    [s_j, s_k] = s_js_ks_js_k = s_{jk}^2 = e.
+\end{align*}
+Next we give the definition of a group representation. 
 \begin{definition}
@@
     \Pg = \ip{u,o:uou^{-1} = o^r},
-\label{pgroup}
+\label{eq:pgroup}
 \end{align}
@@
 we defer the formal statements of the embedding procedure till \cref{sec:embedding},
-but give the idea behind this procedure in \cref{sec:embed_idea}. 
+but sketch this procedure in \cref{sec:embed_idea}. 
 In \cref{sec:lsg_def}, we define $\Gamma$ and introduce how to
@@
 %----------------------------------------
-The group $\Pg$ (see equation (\ref{pgroup} above) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}), which is the
+The group $\Pg$ (\cref{eq:pgroup}) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}), which is the
 solution group of $\LS ( r )$.  
@@
 
-First observe that the generators $u$ and $o$ have arbitrary order in $\Pg$. However, all the generator of a solution
-group are of order-$2$, so it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$
-to a single generator. 
-\hf{This is the reason why we first embed $\Pg$ into $\Pg_0 := \ip{S_0:R_0}$, where all the generators in $S_0$ are of 
-order-$2$ and all the relations in $R_0$ are conjugacy relations.
+The group $\Pg_0 := \ip{S_0:R_0}$ is a 
+conjugacy group, which is defined in \cref{def:spe_conj_grp}. 
 The generators in $S_0$ are $a_i$ for $i=1 \dots r+5$.
-The special generators are $a_1, a_2, a_3$ and $a_4$ because the product $a_1a_2$ behaves similarly as $o$
-and the product $a_3a_4$ behaves similarly as $u$.}
-\carl{[You should probably
-say somewhere that $\mathcal{P}_0$ is defined
-by conjugacy relations (since it seems like you're assuming that the reader knows that).]}
-\hfc{Fixed.}
+The purpose of this step is to embed $\Pg$ into a group where all the
+generators are of order-$2$, because
+it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single generator. On the other hand, 
+a homomorphism from $\Pg_0$ to a solution group can be easier to find.
+The special generators of $\Pg_0$ are $a_1, a_2, a_3$ and $a_4$ because the product $a_1a_2$ behaves similarly as $o$
+and the product $a_3a_4$ behaves similarly as $u$.
 Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$ (see \cref{prop:g0}), so
@@
 
-\hf{Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$
-and $R_1$ consists of both linear relations and conjugacy relations.
-The special properties of $S_1$ and $R_1$ are
-\begin{enumerate}
-    \item $s_is_js_i = s_k \in R_1$ implies that there exists a generator
-$s' \in S_1$ such that $s' s_j s_k = e \in R_1$;
-    \item every relation in $R_0$ can be derived from $R_1$.
-\end{enumerate}
-Note that $s'$ can be seen as an auxiliary generator such that
-its existence implies that $s_j$ and $s_k$ commute, because
-\begin{align*}
-    [s_j, s_k] = s_j s_k s_j s_k = (s')^2 = e.
-\end{align*}
-Ensuring the conjugacy relations are associating one generator to another one which 
-commutes with it is the purpose of introducing $\Pg_1$. 
+Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$, which is a nice conjugacy group defined in \cref{def:nice_conj_grp}.
+The special property of $R_1$ is that every relation in $R_0$ can be recovered from $R_1$.
+Ensuring that every conjugacy relation is associating two commuting operators is the purpose of introducing $\Pg_1$. 
 It makes the construction of a finite-dimension representation of $\Gamma$ from
-a finite-dimension representation of $\Pg_1$ easier.}
-\carl{[that's vague -- either explain it or don't say it]}
-\hfc{How about now?} 
+a finite-dimension representation of $\Pg_1$ easier.
 Specifically, in this step, we introduce generators $a_i, b_i, c_i, d_i \in S_1$
@@
 $d_ib_jd_i = c_k$ for $(i,j,k) \in C(r)$.
-\hf{From the conjugacy relations in $R_1$, it can be proven that
+From the conjugacy relations in $R_1$, it can be proven that
 \begin{align*}
@@
 Then we can expand $a_ia_ja_i$ by first substituting in $a_i = f_0 d_i$ and $a_j = b_jc_j$ and then repeatedly substituting in the conjugacy relations in $R_1$ and 
-the conjugacy relations deduced above. For details, we refer to the 
-proof of \cref{prop:g0g1}.}
+the conjugacy relations deduced above, so we can get
+\begin{align*}
+    a_ia_ja_i = f_0 d_i b_jc_j f_0 d_i
+		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
+		= (f_0 c_k f_0)(f_0 b_k f_0) 
+		= b_k c_k = a_k.
+\end{align*}
 \carl{It would be good to explain (or at least reiterate) that these relations allow us to recover the conjugacy relations in $\mathcal{R}_0$.}
-\hfc{How about now?}
+\hfc{I have added some explanation about the derivation. How does it look?}
 
@@
 $6$ linear relations of $R$ as an example. 
-The other conjugacy relations of $\Pg_1$ are embedded in linear relations in a similar way.
-We introduce auxiliary generators $f_1, f_2$ and $\{p_{1,j}\}_{j=1}^5$ and they satisfy the linear relations:
+We introduce auxiliary generators $f_1, f_2$ and $\{p_{1,j}\}_{j=1}^5$ such that they satisfy the linear relations:
 \begin{align*}
@@
 \end{align*}
-For details about how the linear relations above
-can be combined to recover $f_0b_1f_0 = c_1$, we refer to \cref{sec:embedding}.
+Then, we expand $f_0b_1f_0$ by substituting in the equations above and
+get
+\begin{align*}
+    f_0b_1f_0 = (f_1f_2)(f_2p_{1,1})(p_{1,3}p_{1,4}) =
+    f_1 p_{1,2}p_{1,4} = p_{1,5}p_{1,4} = c_1.
+\end{align*}
+The other conjugacy relations of $\Pg_1$ are embedded in linear relations analogously.
+
 A representation of $\Gamma$ can also be built upon
-the representation $\Psi_1$ of $\Pg_1$.
+a representation $\Psi_1$ of $\Pg_1$, which is defined on
+$\C^2 \x \calH$.
 We denote the representation of $\Gamma$ by $\Psi$ and
@@
 \subsection{Formal definitions}
-\label{sec:lsg_def}
+\label{sec:gamma_def}
 %----------------------------------------
@@
 We denote the identity operator for the subspace $W_k$ by $\1_{W_k}$.
-Consequently, the representations of $a_1, a_2, a_3$ and $a_4$ are 
-\begin{align*}
-    \Psi(a_1) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}}\right) \\
-    \Psi(a_2) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}} \right)\\
-    \Psi(a_3) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ 
-    &+ \sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right) \Big]\\
-	\Psi(a_4) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\
+Consequently, the representations of $a_1, a_2, a_3$ and
+$a_4$ are
+\begin{align}
+    \label{eq:o1} \Psi(a_1) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}}\right) \\
+    \label{eq:o2} \Psi(a_2) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}} \right).
+\end{align}
+\begin{equation}
+    \begin{aligned}
+    \label{eq:u1} \Psi(a_3) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ 
+    &+ \sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right) \Big]
+    \end{aligned}
+\end{equation}
+\begin{equation}
+    \begin{aligned}
+    \label{eq:u2}\Psi(a_4) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\
 	& + \sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right)\Big].
-\end{align*}
+    \end{aligned}
+\end{equation}
+
 The tensor structure of the representations come from the construction of $\Psi$.
@@
 The formal statement is given in the theorem below. Since the proof uses the same techniques as in Ref.~\cite{bamps2015},
-we defer the proof till \cref{sec:selftest}, and we only list the key relations used in the proof because they will be reused in 
-\cref{sec:main}.
+we defer the proof till \cref{sec:selftest}, and we only list the key relations used in the proof because they will be reused in \cref{sec:main}.
 \begin{theorem}
@@
 \end{theorem}
-We follow the convention \carl{[What convention?  Be a little more specific about what papers this convention is used in.]} and define $c := \cos(\mu)$, $s := \sin(\mu)$, and
+We follow the convention used in Ref.~\cite{bamps2015},
+\carl{[What convention?  Be a little more specific about what papers this convention is used in.]}, which defines
 \begin{align*}
 	&Z_A := M_1 && X_A := M_2\\
-	&Z_B := \frac{N_1+N_2}{2c} && X_B := \frac{N_1-N_2}{2s}.
-\end{align*}
-The key relations that we will reuse are
-\begin{align}
-	\label{eq:za-zb}& Z_A\ket{\psi} \appd{\frac{\sqrt{s\epsilon}}{c}} Z_B\ket{\psi},\\
-	\label{eq:xa-xb}&X_A\ket{\psi} \appd{\frac{\sqrt{\epsilon}}{\sqrt{s}}} X_B \ket{\psi}, \\
-	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{\frac{c+1}{c\sqrt{s}} \se} X_B(\1-Z_A) \ket{\psi},\\
-	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{ \frac{s+1}{c\sqrt{s}} \se} Z_B(\1-X_A) \ket{\psi},\\
-	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{\frac{1+c+s}{c\sqrt{s}} \se} -X_AZ_A \ket{\psi},\\
-	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{\frac{2s^2+cs+c+s}{cs\sqrt{s}} \sqrt{\epsilon}} -X_BZ_B \ket{\psi},
+	&Z_B := \frac{N_1+N_2}{2\cos{\mu}} && X_B := \frac{N_1-N_2}{2\sin{\mu}}.
+\end{align*}
+Note that in \cref{sec:main}, we take $\mu = \pi/d$, so
+when we derive the error terms below, we only consider $\mu$ 
+that is close to $0$.
+The key relations that will be reuse are
+\begin{align}
+	\label{eq:za-zb}& Z_A\ket{\psi} \appd{O( \sqrt{\mu} \se)} Z_B\ket{\psi},\\
+	\label{eq:xa-xb}&X_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B \ket{\psi}, \\
+	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B(\1-Z_A) \ket{\psi},\\
+	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} Z_B(\1-X_A) \ket{\psi},\\
+	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} -X_AZ_A \ket{\psi},\\
+	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{O(\frac{\se}{\mu^{3/2}})} -X_BZ_B \ket{\psi},
 \end{align}
@@
 %==========================
-The full test consists of three tests: the linear system game $\LS(r)$,
-the extended weighted CHSH test and a commutation test. We explain how the three tests are conducted and
-combined in \cref{sec:tests}. Then the ideal strategy that can pass
-the three tests is presented in \cref{sec:ideal_strat}. The full correlation, denoted by $\fC(r,d)$, is generated by the ideal strategy and presented in \cref{sec:cor}.
+The full test consists of the linear system game $\LS(r)$,
+the extended weighted CHSH test and a commutation game. We explain how the games and test are conducted and
+introduce the ideal strategy for each of them in \cref{sec:tests}. 
+Then we explain how they are combined in the full test and present the ideal strategy for the full test in \cref{sec:ideal_strat}.
+\carl{[I'm a little skeptical that the phrase ``pass the three test'' is meaningful here -- I don't know that these are the kind of tests that can be ``passed.'']}
+\hfc{I have removed that phrase. How is my changes?}
+The full correlation, denoted by $\fC(r,d)$, is generated by the ideal strategy and presented in \cref{sec:cor}.
 
 %----------------------------
-\subsection{The three tests}
+\subsection{The components of the full test}
 \label{sec:tests}
 %----------------------------
-Recall that the linear system game, $\LS(r)$ defined in \cref{def:gamma}, has $|S| = \nr$ variables and $\mr$ equations.
-The variables are labelled by $x(s)$ for each $s \in S$ and
-the equations are labelled by $i \in \{1, 2 \dots \mr\}$.
-We denote the associated linear system by $Hx = c$ and
-define $X_i := \{ \ba : \sum_{s} H(i,s)a(s) = c(i) \}$, \carl{[This definition isn't clear --- what kind of object is $\ba$?]}
-\hfc{It is a bit string.} 
-which is the answer set of equation $i$,
-and $I_i = \{ s : H(i,s) = 1\}$, which is the set of all the nonzero coefficient of equation $i$.
+\textbf{The linear system game $\LS(r)$} (\cref{def:lsg}) consists of
+\begin{align*}
+    & \calX = \{I_i\}_{i=1}^{\mr}, \\
+    & \calY = \{ x(s) : s \in S \},
+\end{align*}
+where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$.
 From the construction of $\LS(r)$, we know that $|I_i| = 3$ for all $i$.
-The way to conduct $\LS(r)$ is as introduced in \cref{sec:intro}.
-
-In the extended weighted CHSH test,
-the question sets are $\calX = \calY = \{\ast, x(a_1), x(a_2), x_{\nr+1}, x_{\nr+2}\}$
-% all the question pairs are $\{ (\ast, \ast) \} \cup \{(\ast, y), (x, \ast)\}_{x,y = \nr+1, \nr+2} \cup 
-% \{(x,y)\}_{x=y \in \{\nr+1, \nr+2\}} \cup
-% \{(x,y)\}_{x = 1,2, y =\nr+1, \nr+2} \cup  \{(x,y)\}_{x = \nr+1,\nr+2, y =1, 2}$.
-%the input alphabets are $\calX = \calY = \{\ast, 1, 2, \nr+1,\nr+2\}$.
-\carl{[I am pretty sure your notation here is more complicated than it needs to be -- why are you using both subscripts and functions to denote variables?]}
-For each question, there is an associated answer set:
-\begin{itemize}
-	\item when the question is $\ast$, the answer set is $\{\diamond, \perp\}$;
-	\item when the question is $x(a_1)$ or $x(a_2)$, the answer set is $\{0,1\}$;
-	\item when the question is $x_{\nr+1}$ or $x_{\nr+2}$, the answer set is $\{0, 1, \perp\}$.
-\end{itemize}
-\carl{[This is not formal enough.
-If you're going to define a test, then you need to do it in a way that matches your earlier definition of a test.
-You should rewrite this section in a way that formally specifies each test: what its input and output alphabets are, and what its input probability distribution is.]}
-Note that when the referee wants to ask Alice $x(a_1)$ or $x(a_2)$, which also labels a variable of $\LS(r)$, 
-the referee gives Alice an equation label $i$ such that  
-the equation $i$ contains the variable $x(a_1)$ or $x(a_2)$. 
-For simplicity we omit the equation label in the alphabet $\calX$, and
-later we will show that the equation label can be made implicit.
-Only some of the question pairs of $\calX \times \calY$ are given to Alice and Bob.
-Alice and Bob's ideal behaviour to pass this test is summarized 
-below:
-\carl{[Does the phrase ``ideal behavior'' have a formal definition?
-This seems to be another case where are you are writing in a way that is sort of formal, and sort of just a sketch -- that's not a good way to write.
-Do one or the other.]}
-\begin{enumerate}
-	\item if $x = y = \ast$, Alice and Bob should answer with $a = b \in \{\diamond, \perp\}$;
-	\item if $x = y \in \{x_{\nr+1}, x_{\nr+2}\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
-	\item if $x \in \{x(a_1),x(a_2)\}$ and $y \in \{x_{\nr+1}, x_{\nr+2}\}$, 
-		\begin{enumerate}
-		\item if they answer with $a,b \in \{0,1\}$, then
-	they should maximize $\I_{\cot(-\pi/d)}$ with Alice and Bob's roles flipped, 
-		\item if Bob answers with $\perp$, then Alice's answer doesn't matter;
-		\end{enumerate}
-	\item if $x \in \{x_{\nr+1}, x_{\nr+2}\}$ and $y \in \{x(a_1),x(a_2)\}$,
-	\begin{enumerate} 
-		\item if they answer with $a,b \in \{0,1\}$, then
-		they should maximize $\I_{\cot(-\pi/d)}$, 
-		\item if Alice answers with $\perp$, then Bob's answer doesn't matter;
-	\end{enumerate}
-	\item $x \in \{x_{\nr+1},x_{\nr+2}\}, y = \ast$ 
-		\begin{enumerate}
-		\item if Bob answers with $\diamond$, Alice should answer with $\{0.1\}$ but not $\perp$, 
-		\item if Bob answers with $\perp$ Alice should answer with $\perp$ too;
-		\end{enumerate}
-	\item $x = \ast, y \in \{x_{\nr+1}, x_{\nr+2}\}$
-	\begin{enumerate}
-		\item if Alice answers with $\diamond$, Bob should answer with $\{0.1\}$ but not $\perp$, 
-		\item if Alice answers $\perp$, Bob should answer $\perp$ too.
-	\end{enumerate}
-\end{enumerate}
-Only the question pairs mentioned in the list above are given to Alice and Bob.
-
-Our commutation test is the same as the one used in Ref.~\cite{coladan2017verifier}.
-The goal of the commutation test is to make sure that some
-of Alice's binary observables for the other two tests 
-commute with each other when acting on the shared state
-so we reuse questions and answers from the two other tests.
-There are $8$ test cases, where each test case has two questions. 
-In each test case, Alice is given one of the two questions.
-If her question is to assign a value to some variable of $\LS(r)$,
-the equation label is implicit.
-Bob is given both of the question so he needs to give answers to both questions.
-Their answers should agree on the question that is given to both.
-The $8$ question pairs are $(x_{\nr+1}, x(s))$ and $(x(\nr+2), x(s))$ for
-$s = f_0, f_2, g_0, g_2$.
-What we conclude is slightly different from the original claim
-in Ref.~\cite{coladan2017verifier}.
-Instead of just proving the binary observables commute,
-we prove that the projective measurements
-for question $x_{\nr+1}$ commute with the binary observables for question
-$x(s)$ with $s = f_0, f_2, g_0, g_2$ 
-by examining the probability distribution generated by this test.
-
-%The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
-%Alice's input is determined by the pair so she receives one of the two questions of a given pair with equal probability.
-
-In the full test, the three tests are conducted with equal probability.
-The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first and then $\fC(d,r)$.
-%--------------------------------------------
-\subsection{The ideal strategy}
-\label{sec:ideal_strat}
-%--------------------------------------------
-Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}. 
+Hence, the answer sets are 
+\begin{align*}
+    \calA = \Z_2^3 && \calB = \Z_2.
+\end{align*}
+The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$.
+We define $X_i := \{ \ba \in \Z_2^3: \sum_{j=1}^3 a(j) = c(i) \}$, which is the set of all the valid answers of equation $i$.
+Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
+the score function is
+\begin{align*}
+    V_{\LS(r)}(\ba, b, I_i, x(s)) = 
+    \begin{cases}
+        1 \text{, if} \ba \in X_i \text{ and } a(s) = b\\
+        0 \text{, otherwise}.
+    \end{cases}
+\end{align*}
+
+The ideal strategy of $\LS(r)$ follows the representation $\Psi$ of $\Gamma$.
+Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}. 
 In the ideal strategy Alice and Bob share the state 
+\begin{align*}
+        \ket{\tpsi} = \frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right).
+\end{align*}
+Alice and Bob's observables for each variable $x(s)$ are
+defined by
+\begin{align*}
+    \tM(s) = \tN(s) = \Psi(s) 
+\end{align*}
+for each $s \in S$.
+
+\textbf{The extended weighted CHSH test} consists of
+\begin{align*}
+    &\calX = \calY = \{0, 1, 2, \nr+1, \nr+2\} \\
+    &\calA = \calB = \{0,1,2\}.
+\end{align*}
+The probability distribution over the question pairs is uniform.
+The reason why this test is called the extended weighted CHSH test will be clear after we introduce
+the ideal strategy.
+
+Recall the Hilbert space $W_{d-1}$ defined in \cref{sec:gamma_def}. 
+The shared state of the ideal strategy is 
 \begin{equation}
@@
     \begin{aligned}
-        \ket{\tpsi} = &\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
-        =&\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
+        \ket{\tpsi} = & \frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\\
+         =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j}).
     \end{aligned}
 \end{equation}
-Here we introduce the third basis $\{ \ket{j} \}_{j=1}^{d-1}$ of $W_{d-1}$ so that
+Here we introduce the third basis of $W_{d-1}$: $\{ \ket{j} \}_{j=1}^{d-1}$, so that
 the observables used in the extended weighted CHSH test have a simpler form.
@@
 	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
-	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) && \text{for } j = 1 \dots \frac{d-1}{2}.
-\end{align*}
-
-Alice and Bob's observables to win $\LS(r)$ are representing operators of
-the generators of $\Gamma$. The way they pick the representing operators
-is based on the correspondence between the generators of $\Gamma$ and the
-variables of $\LS(r)$. We list some of the key binary observables here:
-\begin{align}
-	\tM_i = \tN_i = 
-	\begin{cases}
-	\Psi(a_i) \quad \text{ for } 1 \leq i \leq r+5\\
-	\Psi(f_{i-r-6}) \quad \text{ for } r+6 \leq i \leq r+8\\
-	\Psi(g_{i-r-9}) \quad \text{ for } r+9 \leq i \leq r+11\\
-	\Psi(m_{i-r-12}) \quad \text{ for } r+12 \leq i \leq r+14,
-	\end{cases}
-\end{align}
-where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
-Note that Alice uses the same observable for the same variable appearing in different equations.
-
-In order to present the ideal strategy to pass the extended weighted CHSH test,
-we define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$,
-and corresponding projective measurements $\Pi_V$ and $\Pi_{V^\perp}$. Note that $V$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$.
+	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j})
+\end{align*}
+for $1 \leq j \leq \frac{d-1}{2}$.
+we define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$.
+The corresponding projective measurements are $\Pi_V$ and $\Pi_{V^\perp}$. 
+Note that $V$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$.
 We define the states for the measurements used in the extended weighted CHSH test as follows
@@
 \end{align*}
-The measurements for questions $\ast, \nr+1$ and $\nr+2$ are
-\begin{align*}
-	&\tM_\ast^\diamond =(\1_{W_2})^{\x 2} \x \Pi_V && \tM_\ast^\perp = \tM_{\nr+1}^\perp = \tM_{\nr+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
-	&\tN_\ast^\diamond = (\1_{W_2})^{\x 2} \x \Pi_V && \tN_\ast^\perp = \tN_{\nr+1}^\perp = \tN_{\nr+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
-	&\tM_{\nr+1}^0 =\tN_{\nr+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && \tM_{\nr+1}^1=\tN_{\nr+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
-	&\tM_{\nr+2}^0 =\tN_{\nr+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1_{\times}}{1_{\times}} && \tM_{\nr+2}^1= \tN_{\nr+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_{\times}}{(d-1)_{\times}}.
-\end{align*}
+Alice's measurements for questions $0, \nr+1$ and $\nr+2$ are
+\begin{align*}
+	&\tM_0^0 = \Pi_V && \tM_0^2 = \tM_{\nr+1}^2 = \tM_{\nr+2}^2 = \Pi_{V^\perp}\\
+	&\tM_{\nr+1}^0= \ketbra{1}{1} && \tM_{\nr+1}^1 = \ketbra{d-1}{d-1}\\
+	&\tM_{\nr+2}^0 =  \ketbra{1_{\times}}{1_{\times}} && \tM_{\nr+2}^1 =  \ketbra{(d-1)_{\times}}{(d-1)_{\times}}.
+\end{align*}
+Bob's measurements for questions $0, \nr+1$ and $\nr+2$ are
+\begin{align*}
+    &\tN_0^0 = \Pi_V && \tN_0^2 = \tN_{\nr+1}^2 = \tN_{\nr+2}^2 = \Pi_{V^\perp}\\
+    &\tN_{\nr+1}^0= \ketbra{1}{1} && \tN_{\nr+1}^1 = \ketbra{d-1}{d-1}\\
+	&\tN_{\nr+2}^0=  \ketbra{1_{\times}}{1_{\times}} && \tN_{\nr+2}^1 =  \ketbra{(d-1)_{\times}}{(d-1)_{\times}}.
+\end{align*}
+Observe that the ideal strategy ensures that when 
+Alice and Bob get the same question from the set $\{0,\nr+1,\nr+2\}$, they always give the same answer.
 When Alice and Bob gets question $1$ or $2$, what they measure on $V$ are
@@
 \end{align*}
+What they measure on $V^\perp$ is irrelevant for this test. Later we will see that their measurements on $V^\perp$ are determined by their observables for variables $x(a_1)$ and $x(a_2)$ of $\LS(r)$.
+In other words, they never answer $2$ given question $1$ or $2$.
+
+There are two key observations.
+The first one is that when Alice gets $x \in \{1,2\}$ and Bob gets $y \in \{\nr+1, \nr+2\}$, 
+their answers $a,b \in \{0,1\}$ should maximize $\I_{\cot(-\pi/d)}$ with Alice and Bob's roles flipped.
+The second one is that when Alice gets $x \in \{\nr+1,\nr+2\}$ and Bob gets $y \in \{1, 2\}$,
+their answers $a,b \in \{0,1\}$ should maximize $\I_{\cot(-\pi/d)}$.
+This is the reason behind naming this test the extended weighted CHSH test.
+
+% Note that when the referee wants to ask Alice $x(a_1)$ or $x(a_2)$, which also labels a variable of $\LS(r)$, 
+% the referee gives Alice an equation label $i$ such that  
+% the equation $i$ contains the variable $x(a_1)$ or $x(a_2)$. 
+% For simplicity we omit the equation label in the alphabet $\calX$, and
+% later we will show that the equation label can be made implicit.
+% Only some of the question pairs of $\calX \times \calY$ are given to Alice and Bob.
+% Alice and Bob's ideal behaviour to pass this test is summarized 
+% below:
+% \carl{[Does the phrase ``ideal behavior'' have a formal definition?
+This seems to be another case where are you are writing in a way that is sort of formal, and sort of just a sketch -- that's not a good way to write.
+Do one or the other.]}
+% \begin{enumerate}
+% 	\item if $x = y = \ast$, Alice and Bob should answer with $a = b \in \{0, \perp\}$;
+% 	\item if $x = y \in \{x_{\nr+1}, x_{\nr+2}\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
+% 	\item if $x \in \{x(a_1),x(a_2)\}$ and $y \in \{x_{\nr+1}, x_{\nr+2}\}$, 
+% 		\begin{enumerate}
+% 		\item if they answer with $a,b \in \{0,1\}$, then
+% 	they should maximize $\I_{\cot(-\pi/d)}$ with Alice and Bob's roles flipped, 
+% 		\item if Bob answers with $\perp$, then Alice's answer doesn't matter;
+% 		\end{enumerate}
+% 	\item if $x \in \{x_{\nr+1}, x_{\nr+2}\}$ and $y \in \{x(a_1),x(a_2)\}$,
+% 	\begin{enumerate} 
+% 		\item if they answer with $a,b \in \{0,1\}$, then
+% 		they should maximize $\I_{\cot(-\pi/d)}$, 
+% 		\item if Alice answers with $\perp$, then Bob's answer doesn't matter;
+% 	\end{enumerate}
+% 	\item $x \in \{x_{\nr+1},x_{\nr+2}\}, y = \ast$ 
+% 		\begin{enumerate}
+% 		\item if Bob answers with $0$, Alice should answer with $\{0.1\}$ but not $\perp$, 
+% 		\item if Bob answers with $\perp$ Alice should answer with $\perp$ too;
+% 		\end{enumerate}
+% 	\item $x = \ast, y \in \{x_{\nr+1}, x_{\nr+2}\}$
+% 	\begin{enumerate}
+% 		\item if Alice answers with $0$, Bob should answer with $\{0.1\}$ but not $\perp$, 
+% 		\item if Alice answers $\perp$, Bob should answer $\perp$ too.
+% 	\end{enumerate}
+% \end{enumerate}
+% Only the question pairs mentioned in the list above are given to Alice and Bob.
+
+\textbf{The commutation game}.
+Our commutation game is the based on the commutation test used in Ref.~\cite{coladan2017verifier}.
+The goal of the commutation game is to make sure that some
+of Alice's binary observables for the other two tests 
+commute with each other when acting on the shared state,
+so we reuse questions and answers from the two other tests.
+
+There are $8$ pairs of observables that we test, 
+so Bob's input set consists of all the question pairs
+\begin{align*}
+    \calY = \{(\nr+1, x(s)), (\nr+2, x(s)): s = f_0, f_2, g_0, g_2 \},
+\end{align*}
+and
+Alice's input set is 
+\begin{align*}
+    \calX = \{\nr+1, \nr+2, f_0, f_2, g_0, g_2\}.
+\end{align*}
+The answer sets are 
+\begin{align*}
+    \calA = \Z_3 && \calB = \Z_3 \times \Z_2.
+\end{align*}
+The probability distribution is
+\begin{align*}
+    \pi_{comm}(x,(y_1,y_2)) =
+    \begin{cases}
+        1/16 \text{, if } x = y_1 \text{ or } x = y_2 \\
+        0 \text{, otherwise}.
+    \end{cases}
+\end{align*}
+The scoring function is
+\begin{align*}
+    V_{comm}(a, (b_1,b_2), x, (y_1,y_2)) = 
+    \begin{cases}
+    1 \text{, if } x = y_1 \text{ and } a = b_1 \\
+    1 \text{, if } x = y_2 \text{ and } a = b_2 \\
+    0 \text{, otherwise}.
+    \end{cases}
+\end{align*}
+The probability distribution makes sure that Alice gets one of
+the two questions that Bob gets.
+To win this game, Alice and Bob should agree on the answer to the
+common question.
+We remark that if Alice's question is to assign a value to some variable of $\LS(r)$,
+the label of a equation that contains this variable is given 
+to Alice and the referee checks the bit corresponding to this
+variable in Alice's answer. This is equivalent to asking 
+Alice to measure an observable for the variable.
+
+We defer the ideal strategy for this test till next subsection because the ideal
+strategy to pass the two tests above can pass this test as well.
+
+What we conclude is slightly different from the original claim
+in Ref.~\cite{coladan2017verifier}.
+Instead of just proving the binary observables commute,
+we prove that the projective measurements
+for question $\nr+1$ commute with the binary observables for question
+$x(s)$ with $s = f_0, f_2, g_0, g_2$ 
+by examining the probability distribution generated by the ideal strategy.
+
+%The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
+%Alice's input is determined by the pair so she receives one of the two questions of a given pair with equal probability.
+
+% In the full test, the three tests are conducted with equal probability.
+% The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first and then $\fC(d,r)$.
+%------------------------------------------------
+\subsection{The full test and the ideal strategy}
+\label{sec:ideal_strat}
+%-----------------------------------------------
+The question pairs of the full test is the union of the question pairs of each component.
+The only modification is that we changed question $1$ and $2$ from the extended weighted CHSH test to
+the question $x(a_1)$ and $x(a_2)$ from $\LS(r)$. 
+The three components of the full test are conducted with equal probability.
+
+The ideal strategy for the full test is an extension of the ideal strategy for $\LS(r)$ to make it able to produce the ideal correlation of 
+the extended weighted CHSH test.
+Note that the ideal strategy of the extended weighted CHSH test is defined on $W_{d-1}$ and the ideal strategy of $\LS(r)$ is defined on $W_2^{\x 2} \x W_{d-1}$, 
+so we can modify the ideal strategy of the extended weighted CHSH test by tensoring the shared state with $\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2}$
+and tensoring each projective measurement with $\1_{W_2}^{\x 2}$.
+The effect is the modified strategy for the extended weighted CHSH test 
+becomes compatible with that of $\LS(r)$,
+but the generated correlation remains the same.
+Consequently, the ideal strategy for the full test is defined on $W_2^{\x 2} \x W_{d-1}$.
+The shared state is 
+\begin{align*}
+    \ket{\tpsi} = \frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right).
+\end{align*}
+The observable for each question of $\LS(r)$ is the same as in the ideal
+strategy of $\LS(r)$. For each question from the extended weighted CHSH test, it uses projective measurements from the extended strategy of the test.
 
 To make sure the strategy is correct, we need to check a few properties of it.
+First of all, it is easy to see that this ideal strategy can win the commutation games 
+because the observables for questions $x(f_0), x(f_2),
+x(g_0)$ and $x(g_2)$ act trivially on $W_{d-1}$, which is the subspace the
+measurements for questions $\nr+1$ and $\nr+2$ act on.
+To make sure it wins $\LS(r)$, what we need to check is summarized in the 
+following proposition.
 \begin{proposition}
-The observables $\tM_j = \tN_j = \Psi(a_j)$ for $1 \leq j \leq 4$ and the shared state $\ket{\tpsi}$ defined in \cref{eq:tpsi}
+The observables $\tM(a_j) = \tN(a_j) = \Psi(a_j)$ for $1 \leq j \leq 4$, where $\Psi$ is defined in \cref{def:rep_gamma}, 
+and the shared state $\ket{\tpsi}$ defined in \cref{eq:tpsi}
 satisfy the relations
 \begin{align}
-	\label{eq:mn_preserve} &\tM_j \tN_j \ket{\tpsi} = \ket{\tpsi} && \text{for } j = 1 \dots 4,\\
-	\label{eq:o2_comm} &(\tM_3\tM_4)\tM_2(\tM_4\tM_3) = \tM_2,
-\end{align}
-and similar commutation relations on Bob's side.
+	\label{eq:mn_preserve} &\tM(a_j) \tN(a_j) \ket{\tpsi} = \ket{\tpsi},
+\end{align}
+for $j=1,2,3,4$.
 \end{proposition}
@@
 
-	We prove \cref{eq:o2_comm} first. It is simple to check that
-	\begin{align*}
-		\tM_3\tM_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
-	\end{align*}
-	and that 
-	\begin{align*}
-		\tM_3\tM_4 \tM_2 \tM_4 \tM_3 = &\sum_{j=0}^{(d-3)/2} M_3M_4 (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) M_4M_3\\
-		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}} = \tM_2.
-	\end{align*}
-
-	Next we prove \cref{eq:mn_preserve}. It is straightforward to see that $\tM_j\tN_j \ket{\tpsi} = \ket{\tpsi}$ for $j = 1,2$.
+	Using \cref{eq:o1,eq:o2}, it is straightforward to see that $\tM(a_j)\tN(a_j) \ket{\tpsi} = \ket{\tpsi}$ for $j = 1,2$.
 	Before checking the two cases $j=3$ and $j=4$, we first observe that
 	\begin{align*}
-		\tM_3\tM_4 \tN_3 \tN_4 \ket{\tpsi} = \ket{\tpsi}.
-	\end{align*}
-	The eigenvectors of $\tM_3\tM_4$ and $\tN_3\tN_4$ are 
+		\tM(a_3)\tM(a_4) \tN(a_3) \tN(a_4) \ket{\tpsi} = \ket{\tpsi}.
+	\end{align*}
+	The eigenvectors of $\tM(a_3)\tM(a_4)$ and $\tN(a_3)\tN(a_4)$ are 
     \begin{align*}
@@
     \end{align*}
-    Then $\tM_4$ acts on $\ket{x_{r^j}}$ by
-    \begin{align*}
-        \tM_4 \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} M_4\left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
+    Then using \cref{eq:u2} we can deduce that $\tM(a_4)$ acts on $\ket{x_{r^j}}$ by
+    \begin{align*}
+        \tM(a_4) \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} \tM(a_4) \left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
         \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
@@
     \end{align*}
-    Consequently, we can show that $\tM_4  \tN_4 \ket{\tpsi} = \ket{\tpsi}$ because
-    \begin{align*}
-        \tM_4 \tN_4 \ket{\tpsi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \tM_4  \tN_4 \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
+    Consequently, we can show that $\tM(a_4)  \tN(a_4) \ket{\tpsi} = \ket{\tpsi}$ because
+    \begin{align*}
+        \tM(a_4) \tN(a_4) \ket{\tpsi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \tM(a_4)  \tN(a_4) \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
         = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\psi},
     \end{align*}
-	Combining it with the fact that $\tM_3\tM_4 \tN_3\tN_4 \ket{\tpsi} = \ket{\tpsi}$, we can conclude that
-	$\tM_3\tN_3 \ket{\tpsi} = \ket{\tpsi}$.
+	Combining it with the fact that $\tM(a_3)\tM(a_4) \tN(a_3)\tN(a_4) \ket{\tpsi} = \ket{\tpsi}$, we can conclude that
+	$\tM(a_3)\tN(a_3) \ket{\tpsi} = \ket{\tpsi}$.
 \end{proof}
-The similar result, i.e., $\tM_j\tN_j \ket{\tpsi} = \ket{\tpsi}$ for $j = 1 \dots \nr$, are easy to check because all the other observables are defined by $\tM_j, \tN_j$ for $j=1,2,3,4$.
+The similar result, i.e., $\tM(s)\tN(s) \ket{\tpsi} = \ket{\tpsi}$ for $s \in S$ are easy to check because all the other observables are defined by $\tM(a_j), \tN(a_j)$ for $j=1,2,3,4$ and $\tM(f_0), \tM(f_2), \tM(g_0), \tM(g_2)$ and $\tN(f_0), \tN(f_2), \tN(g_0), \tN(g_2)$, which only act non-trivially on $W_2$.
 
@@
 \multicolumn{2}{|c|}{} &
-\multicolumn{2}{|c|}{$x=\ast$}\\
+\multicolumn{2}{|c|}{$x=0$}\\
 \cline{3-4}
-\multicolumn{2}{|c|}{} &$a = \diamond$ & $a = \perp$ \\
+\multicolumn{2}{|c|}{} &$a = 0$ & $a = 2$ \\
 \hline
 \hline
-\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & 2/(d-1) & 0 \\
+\multirow{2}{*}{$y = 0$} & $b = 0$ & $2/(d-1)$ & $0$ \\
 \cline{2-4}
-&$b=\perp$ & 0 & (d-3)/(d-1) \\
+&$b=2$ & $0$ & $(d-3)/(d-1)$ \\
 \hline
 \end{tabular}
-\caption{The correlation for $x=y=\ast$.}
+\caption{The correlation for $x=y=0$.}
 \end{center}
@@
 \multicolumn{2}{|c|}{} &
-$a = 0$ & $a=1$ & $a=\perp$ &
-$a = 0$ & $a=1$ & $a=\perp$\\
+$a = 0$ & $a=1$ & $a=2$ &
+$a = 0$ & $a=1$ & $a=2$\\
 \hline
@@
 \multicolumn{3}{|c|}{$x=\nr+2$}&
-\multicolumn{2}{|c|}{$x=\ast$}\\
+\multicolumn{2}{|c|}{$x=0$}\\
 \cline{3-10}
 \multicolumn{2}{|c|}{} &
-$a = 0$ & $a=1$ & $a=\perp$ &
-$a = 0$ & $a=1$ & $a=\perp$ &
-$a = \diamond$ & $a = \perp$\\
+$a = 0$ & $a=1$ & $a=2$ &
+$a = 0$ & $a=1$ & $a=2$ &
+$a = 0$ & $a =2 $\\
 \hline
@@
 \cline{2-10}
-&$b=\perp$ & 0 & 0 & $\frac{d-3}{d-1}$ 
+&$b=2$ & 0 & 0 & $\frac{d-3}{d-1}$ 
 &  0 & 0 &  $\frac{d-3}{d-1} $ &0 & $\frac{d-3}{d-1}$ \\
@@
 \cline{2-10}
-&$b=\perp$ & 0 & 0 & \small $\frac{d-3}{d-1}$ 
+&$b=2$ & 0 & 0 & \small $\frac{d-3}{d-1}$ 
 &  0 & 0 & \small $\frac{d-3}{d-1} $ &0 &\small $\frac{d-3}{d-1}$ \\
 \hline
-\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $\frac{1}{d-1}$ & $\frac{1}{d-1}$ & 0 
+\multirow{2}{*}{$y = 0$} & $b=0$ & $\frac{1}{d-1}$ & $\frac{1}{d-1}$ & 0 
 & $\frac{1}{d-1}$ & $\frac{1}{d-1}$ & 0 & $\frac{2}{d-1}$ & 0 \\
 \cline{2-10}
-&$b=\perp$ & 0 & 0 & $\frac{d-3}{d-1}$ 
+&$b=2$ & 0 & 0 & $\frac{d-3}{d-1}$ 
 &  0 & 0 & \small $\frac{d-3}{d-1} $ &0 & \small $\frac{d-3}{d-1}$ \\
@@
 \multicolumn{2}{|c|}{} &
-\multicolumn{6}{|c|}{$y=(\nr+1, r+6)$}\\
+\multicolumn{6}{|c|}{$y=(\nr+1, f_0)$}\\
 \cline{3-8}
 \multicolumn{2}{|c|}{} &
-$b = 00$ & $b=01$ & 
-$b = 10$ & $b=11$ &
-$b = \perp0$ & $b= \perp1$   \\
+$b = (0,0)$ & $b=(0,1)$ & 
+$b = (1,0)$ & $b=(1,1)$ &
+$b = (2,0)$ & $b=(2,1)$   \\
 \hline
@@
 \cline{2-8}
-&$b=\perp$ & 0 & 0 & $0$ 
+&$a=2$ & 0 & 0 & $0$ 
 &  0 & $\frac{d-3}{2d-2}$ & $\frac{d-3}{2d-2} $  \\
 \hline
-\multirow{2}{*}{$x = r+6$} & $a=0$ & $\frac{1}{2d-2}$ & $0$ & $\frac{1}{2d-2}$ 
+\multirow{2}{*}{$x = f_0$} & $a=0$ & $\frac{1}{2d-2}$ & $0$ & $\frac{1}{2d-2}$ 
 & $0$ & $\frac{d-3}{2d-2}$ & 0  \\
@@
 \end{center}
-\caption{The correlation for the commutation test between $M_{r+6}$ and $M_{\nr+1}$.}
+\caption{The correlation for the commutation test between $f_0$ and $\nr+1$.}
 \label{tbl:comm}
 \end{table}
-The correlation table for the other $7$ commutation tests are similar.
+The correlation table for the other seven commutation games are similar.
 
@@
 
-In the next three subsections, we analyze the implication of an approximate strategy to pass the 
-three tests given in \cref{sec:full_test}.
+In the next three subsections, we analyze the implication of an approximate strategy for the 
+three components introduced in \cref{sec:full_test}.
 
@@
 %------------------------------------------------------------------------------------------
-In the first half of this subsection, we use $(i,s)$ to denote the question pair so that Alice gets equation number $i$ and Bob gets a variable label $x(s)$ for some $s \in S$.
+In the first half of this subsection, we use $(i,x(s))$ to denote the question pair so that Alice gets equation number $i$ and Bob gets a variable label $x(s)$ for some $s \in S$.
 For simplicity, we let Bob get the generator $s$ instead.
@@
 \begin{proof}
-The condition that $(\tpr{\ba b}{is})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
+The condition that $(\tpr{\ba b}{i s})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
 \begin{align*}
@@
 for $1 \leq i \leq \mr$.
+Note that with the same technique, we can prove that 
+\begin{align*}
+	\Pi_{s \in I_i} N(s) \ket{\psi} \appd{O(\sr\se)} (-1)^{c(i)}\ket{\psi}  
+\end{align*}
+for $1 \leq i \leq \mr$.
 \end{proof}
-Note that with the same technique, we can prove that 
-\begin{align*}
-	\Pi_{s \in I_i} N(s) \ket{\psi} \appd{O(\sr\se)} (-1)^{c(i)}\ket{\psi} \quad \text{ for all } i \leq \mr.
-\end{align*}
 
@@
     be two sequences of $S$.
-    Define a relation $\Pi_{i=1}^n s_i = \Pi_{j=1}^m s'_j$, denoted by $r$.
+    Define a relation $r$, which is $\Pi_{i=1}^n s_i = \Pi_{j=1}^m s'_j$.
     We say operators $\{M(s) : s \in S\}$ $\ep$-approximately satisfy the relation
@@
     \end{align*}
-    In the rest of the proof, we skip the steps of flipping observables from Alice to Bob's side and then back.
+    In the rest of the proof, we skip the steps of flipping observables from Alice to Bob's side and then flip back.
     \begin{align*}
@@
 \end{proposition}
-Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma$,
+Recall all the relations in \cref{eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma$,
 so this proposition can be proved with the same techniques used in the proof of \cref{prop:lct_group}.
 %------------------------------------------------------------------------------------------
-\subsection{Implication of passing the extended weighted CHSH test}
+\subsection{Implication of the extended weighted CHSH test}
 \label{sec:imp_chsh}
@@
 used in the self-testing proof.
+Note that in the following proofs, the observables $M_1$ and $M_2$ are
+equivalent to $M(a_1)$ and $M(a_2)$ respectively, because questions $1$ 
+and $2$ are equivalent to questions $x(a_1)$ and $x(a_2)$ in the full test.
+Similarly, on Bob's side, we have $N_1 \equiv N(a_1)$ and $N_2 \equiv N(a_2)$.
 \begin{proposition}
 \label{prop:chsh_base}
-Let $S$ be an $\ep$-approximate quantum strategy of $\fC(d,r)$.
-Then the strategy $S$ satisfies the following relations
-\begin{align*}
-	  M_\ast^\diamond N_\ast^\diamond \ket{\psi}
-	  &\appd{O( r\se)}M_\ast^\diamond \ket{\psi}\\
-	  &\appd{O( r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi}\\
-	  &\appd{O( r\se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
-	  &\appd{O( r\se)} N_\ast^\diamond \ket{\psi}\\
-	  &\appd{O( r\se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi}\\
-	  &\appd{O( r\se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
-	M_\ast^\perp N_\ast^\perp\ket{\psi}&\appd{O( r\se)} M_\ast^\perp\ket{\psi}\\
-	&\appd{O( r\se)} M_{\nr+1}^\perp \ket{\psi}\\
-	&\appd{O( r\se)} M_{\nr+2}^\perp \ket{\psi}\\
-	&\appd{O( r\se)} N_\ast^\perp\ket{\psi}\\
-	&\appd{O( r\se)} N_{\nr+1}^\perp \ket{\psi}\\
-	&\appd{O( r\se)} N_{\nr+2}^\perp \ket{\psi},
+Let $\bS$ be an $\ep$-approximate quantum strategy of $\fC(d,r)$.
+Then the strategy $\bS$ satisfies the following relations
+\begin{align*}
+	  M_0^0 N_0^0 \ket{\psi}
+	  &\appd{O( \sr \se)}M_0^0 \ket{\psi}\\
+	  &\appd{O( \sr \se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi}\\
+	  &\appd{O( \sr \se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
+	  &\appd{O( \sr \se)} N_0^0 \ket{\psi}\\
+	  &\appd{O( \sr \se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi}\\
+	  &\appd{O( \sr \se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
+	M_0^2 N_0^2\ket{\psi}&\appd{O( \sr \se)} M_0^2 \ket{\psi}\\
+	&\appd{O( \sr \se)} M_{\nr+1}^2 \ket{\psi}\\
+	&\appd{O( \sr \se)} M_{\nr+2}^2 \ket{\psi}\\
+	&\appd{O( \sr \se)} N_0^2 \ket{\psi}\\
+	&\appd{O( \sr \se)} N_{\nr+1}^2 \ket{\psi}\\
+	&\appd{O( \sr \se)} N_{\nr+2}^2 \ket{\psi},
 \end{align*}
@@
 \begin{align*}
-&M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+1}^0 \ket{\psi} && M_{\nr+1}^1\ket{\psi} \appd{O( r\se)} N_{\nr+1}^1 \ket{\psi}\\
-&M_{\nr+2}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+2}^0 \ket{\psi} && M_{\nr+2}^1\ket{\psi} \appd{O( r\se)} N_{\nr+2}^1 \ket{\psi}.
+&M_{\nr+1}^0 \ket{\psi} \appd{O( \sr \se)} N_{\nr+1}^0 \ket{\psi} && M_{\nr+1}^1\ket{\psi} \appd{O( \sr \se)} N_{\nr+1}^1 \ket{\psi}\\
+&M_{\nr+2}^0 \ket{\psi} \appd{O( \sr \se)} N_{\nr+2}^0 \ket{\psi} && M_{\nr+2}^1\ket{\psi} \appd{O( \sr \se)} N_{\nr+2}^1 \ket{\psi}.
 \end{align*}
@@
 \begin{proof} 
-We prove $(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\se)} N_\ast^\diamond \ket{\psi}$ as an example.
+We prove $(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(\sr \se)} N_0^0 \ket{\psi}$ as an example.
 The rest of the relations follow the same line of argument.
 
-Recall that the implication of $S$ being an $\ep$-approximate strategy is that 
-$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$ for all question 
+Recall that the implication of $\bS$ being an $\ep$-approximate strategy is that 
+$\pr{ab}{xy} \appd{O(r \ep)} \tpr{ab}{xy}$ for all question 
 pair $(x,y)$ and answer pair $(a,b)$.
@@
 \begin{align*}
- \bra{\psi} (M_{\nr+1}^0+M_{\nr+1}^1)N_\ast^\diamond \ket{\psi} = \frac{2}{d-1} - O(r^2 \epsilon).
+ \bra{\psi} (M_{\nr+1}^0+M_{\nr+1}^1)N_0^0 \ket{\psi} = \frac{2}{d-1} - O(r \ep).
 \end{align*}
@@
 \begin{align*}
-	\bra{\psi} N_\ast^\diamond \ket{\psi} \appd{O(r^2\epsilon)} 
- \bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r^2\epsilon)} \frac{2}{d-1},
+	\bra{\psi} N_0^0 \ket{\psi} \appd{O(r\ep)} 
+ \bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\ep)} \frac{2}{d-1},
 \end{align*}
@@
 \begin{align*}
-	&\norm{(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - N_\ast^\diamond\ket{\psi}}^2 \\
-	= &\bra{\psi} N_\ast^\diamond \ket{\psi}+\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} - 2\bra{\psi}N_\ast^\diamond(M_{\nr+1}^0 + M_{\nr+1}^1)N_\ast^\diamond \ket{\psi}\\
-	= &O(r^2 \epsilon),
+	&\norm{(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - N_0^0 \ket{\psi}}^2 \\
+	= &\bra{\psi} N_0^0 \ket{\psi}+\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} - 2\bra{\psi}N_0^0(M_{\nr+1}^0 + M_{\nr+1}^1)N_0^0 \ket{\psi}\\
+	= &O(r \ep),
 \end{align*}
 where we used the fact that $(M_{\nr+1}^0 + M_{\nr+1}^1)^2 = M_{\nr+1}^0 + M_{\nr+1}^1$.
-Hence we can conclude that $(M_{\nr+1}^0 + M_{\nr+1}^1)N_\ast^\diamond \ket{\psi} \appd{O(r\se)} N_\ast^\diamond\ket{\psi}$.
+Hence we can conclude that $(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \appd{O(\sr \se)} N_0^0\ket{\psi}$.
 %From the correlation, we know that 
@@
 
-%Another conclusion we can draw is that $B_\ast^\diamond = A_\ast^\diamond$ and $B_\ast^\perp = A_\ast^\perp$.
+%Another conclusion we can draw is that $B_\ast^0 = A_\ast^0$ and $B_\ast^\perp = A_\ast^\perp$.
 %We can assume the Schmidt decomposition of $\ket{\psi}$ is
@@
 %\end{align}
-%If $\supp{A_\ast^\diamond} \neq \supp{B_\ast^\diamond}$, then $B_\ast^\diamond\ket{\psi} \neq A_\ast^\diamond\ket{\psi}$. Since $B_\ast^\diamond$ and $A_\ast^\diamond$ are projectors,
+%If $\supp{A_\ast^0} \neq \supp{B_\ast^0}$, then $B_\ast^0\ket{\psi} \neq A_\ast^0\ket{\psi}$. Since $B_\ast^0$ and $A_\ast^0$ are projectors,
 %By the orthogonality relations, we can also conclude that $A_\ast^\perp = B_\ast^\perp$.
 
-%Maybe we can first conclude that $\spn(A_0^0+A_0^1) = \spn(A_1^0+A_1^1) = \spn(A_\ast^\diamond)$.
+%Maybe we can first conclude that $\spn(A_0^0+A_0^1) = \spn(A_1^0+A_1^1) = \spn(A_\ast^0)$.
 \begin{proposition}
 	\label{prop:s1s2}
-	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$. We define
+	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$. We define
 	\begin{align}
@@
 	\end{align}
-	Then $S$ induces two $O(d r\se)$-approximate strategies of the ideal correlation that achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$, which are
-	\begin{align}
-		S_1 = \left(M_{\nr+1}, M_{\nr+2}, N_1, N_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right),\\
-		S_2 = \left(N_{\nr+1}, N_{\nr+2}, M_1, M_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right).
+	Then $\bS$ induces two $O(d \sr \se)$-approximate strategies of the ideal correlation that achieves $\I_{\cot(-\pi/d)}^{\max}$, which are
+	\begin{align}
+		\bS_1 = \left(M_{\nr+1}, M_{\nr+2}, N_1, N_2, \frac{M_0^0\ket{\psi}}{\norm{M_0^0\ket{\psi}}}\right),\\
+		\bS_2 = \left(N_{\nr+1}, N_{\nr+2}, M_1, M_2, \frac{M_0^0\ket{\psi}}{\norm{M_0^0\ket{\psi}}}\right).
 	\end{align}
@@
 \begin{proof}
-To prove that $S_1$ achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, we need to examine terms of the form
-$\bra{\psi} M_\ast^\diamond M_{x}^aN_y^b M_\ast^\diamond\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0.1$,
+To prove that $\bS_1$ achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, we need to examine terms of the form
+$\bra{\psi} M_0^0 M_{x}^a N_y^b M_0^0\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0.1$,
 which relate to $\bra{\psi} M_x^a N_y^b \ket{\psi}$ as follows,
@@
 	   \bra{\psi} M_{x}^aN_y^b \ket{\psi} 
-	= &\bra{\psi}(M_\ast^\diamond + M_\ast^\perp) M_x^a N_y^b (M_\ast^\diamond + M_\ast^\perp)\ket{\psi} \\
-	= & \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\perp\ket{\psi}\\
-	&+\bra{\psi}M_\ast^\perp M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\perp M_x^aN_y^b M_\ast^\perp\ket{\psi}\\
-	\appd{O(r\se)}&  \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_x^\perp\ket{\psi} \\
-	&+\bra{\psi}M_x^\perp M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_x^\perp M_x^aN_y^b M_x^\perp\ket{\psi}\\
-	=&\bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi},
-\end{align*}
-where we use the facts that $M_\ast^\perp \ket{\psi} \appd{O(r\se)} M_x^\perp \ket{\psi}$ and that 
-$M_x^0 M_x^\perp = 0$ for the relevant values of $(x,y,a,b)$.
-This means that if Alice and Bob share state $M_\ast^\diamond \ket{\psi}/\norm{M_\ast^\diamond \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
+	= &\bra{\psi}(M_0^0 + M_0^2) M_x^a N_y^b (M_0^0 + M_0^2)\ket{\psi} \\
+	= & \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_0^2\ket{\psi}\\
+	&+\bra{\psi}M_0^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^2 M_x^aN_y^b M_0^2\ket{\psi}\\
+	\appd{O(\sr\se)}&  \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_x^\perp\ket{\psi} \\
+	&+\bra{\psi}M_x^\perp M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_x^\perp M_x^aN_y^b M_x^\perp\ket{\psi}\\
+	=&\bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi},
+\end{align*}
+where we use the facts that $M_0^2 \ket{\psi} \appd{O(\sr \se)} M_x^2 \ket{\psi}$ and that 
+$M_x^0 M_x^2 = 0$ for the relevant values of $(x,y,a,b)$.
+This means that if Alice and Bob share state $M_0^0 \ket{\psi}/\norm{M_0^0 \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
 they get conditional probability
 \begin{align*}
-	\frac{\bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi}}{\bra{\psi} M_\ast^\diamond \ket{\psi}}  
-	\appd{O(d r\se)} \frac{\bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi}}{\bra{\psi} M_\ast^\diamond \ket{\psi}}
-	\appd{O(d r^2 \ep)}
+	\frac{\bra{\psi}M_0^0 M_{\nr+1}^0N_1^0 M_0^0\ket{\psi}}{\bra{\psi} M_0^0 \ket{\psi}}  
+	\appd{O(d \sr \se)} \frac{\bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi}}{\bra{\psi} M_0^0 \ket{\psi}}
+	\appd{O(d r \ep)}
 	\frac{\cos^2(-\pi/2d)}{2}.
@@
 \begin{align*}
-	\frac{ \norm{\bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} -  \bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi}}}
-	{\bra{\psi} M_\ast^\diamond \ket{\psi}} \leq \frac{O(r\se)}{\frac{2}{d-1} - O(r^2 \ep)} = O(d r  \se).
-\end{align*}
-The rest of the conditional probabilities produced by $S_1$ can be derived in the same way.
-Using the fact that $O(d r \se)$ dominates $O(dr^2 \ep)$,
-we can prove that $S_1$ is an $O(dr\se)$-approximate strategy of the ideal correlation that achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$.
-The proof for $S_2$ is very similar so we omit it here.
+	\frac{ \norm{\bra{\psi}M_0^0 M_{\nr+1}^0N_1^0 M_0^0\ket{\psi} -  \bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi}}}
+	{\bra{\psi} M_0^0 \ket{\psi}} \leq \frac{O(\sr\se)}{\frac{2}{d-1} - O(r \ep)} = O(d \sr \se).
+\end{align*}
+The rest of the conditional probabilities produced by $\bS_1$ can be derived in the same way.
+Using the fact that $O(d \sr \se)$ dominates $O(d r \ep)$,
+we can prove that $\bS_1$ is an $O(d \sr\se)$-approximate strategy of the ideal correlation that achieves $\I_{\cot(-\pi/d)}^{\max}$.
+The proof for $\bS_2$ is analogous so we omit it here.
 \end{proof}
@@
     \label{prop:psi1}
-	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.
+	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.
 	Then, the state
@@
 	 %\text{ and } \ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_4}, \\
-	 %\label{eq:psi1_sum} &M_\ast^\diamond \ket{\psi} \appd{O( r\se)} \ket{\psi_1}+\ket{\psi_2}, \\
+	 %\label{eq:psi1_sum} &M_\ast^0 \ket{\psi} \appd{O( r\se)} \ket{\psi_1}+\ket{\psi_2}, \\
 	 %\label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
-	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(r\se)} 1/(d-1),\\
-	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d\ket{\psi_1} 
+	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(\sr\se)} 1/(d-1),\\
+	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\qr \qe/\sd)} \omega_d\ket{\psi_1} 
 	 && N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_1} \\
-	 \label{eq:psi1_eig2} &M_1M_2 \ket{\psi_1} \appd{O(\sd\sr \qe)} \omega_d^{-1} \ket{\psi_1}
-	 && M_2M_1 \ket{\psi_1} \appd{O(\sd\sr \qe)} \omega_d \ket{\psi_1}.
+	 \label{eq:psi1_eig2} &M_1M_2 \ket{\psi_1} \appd{O(\sd\qr \qe)} \omega_d^{-1} \ket{\psi_1}
+	 && M_2M_1 \ket{\psi_1} \appd{O(\sd\qr \qe)} \omega_d \ket{\psi_1}.
 	\end{align}
@@
 		\bra{\psi}M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^0\ket{\psi} 
-		&\appd{O(r\se)} \bra{\psi}N_{\nr+1}^1M_{\nr+2}N_{\nr+1}^0\ket{\psi} \\
+		&\appd{O(\sr\se)} \bra{\psi}N_{\nr+1}^1M_{\nr+2}N_{\nr+1}^0\ket{\psi} \\
 		&= \bra{\psi}N_{\nr+1}^1N_{\nr+1}^0M_{\nr+2}\ket{\psi} = 0.
 	\end{align*}
-	Similarly, we have $\bra{\psi}M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{ O(r\se)} 0$.
+	Similarly, we have $\bra{\psi}M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{ O(\sr \se)} 0$.
 	Hence, we get 
 	\begin{align}
-		\braket{\psi_1}{\psi_1} \appd{O(r\se)} 1/2\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1\ket{\psi} \appd{O(r^2\ep)} 
+		\braket{\psi_1}{\psi_1} \appd{O(\sr\se)} 1/2\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1\ket{\psi} \appd{O(r\ep)} 
 		 \frac{1}{d-1}.
@@
 	\textbf{To prove \cref{eq:psi1_eig1}},
-	we need to dive deeper into the implication of the fact that $S_1$ achieves $\ip{\I_{\cot(-\pi/d)}}_{\max}$ approximately.
+	we need to dive deeper into the implication of the fact that $\bS_1$ achieves $\I_{\cot(-\pi/d)}^{\max}$ approximately.
 	Define
@@
 %	Note that $Z_A$ should be defined by $M_{\nr+1}^0 - M_{\nr+1}^1 + M_{\nr+1}^\perp$,
-%	but $M_{\nr+1}^\perp$ is almost orthogonal to $M_\ast^\diamond$, so we omit the $M_{\nr+1}^\perp$ term here.
+%	but $M_{\nr+1}^\perp$ is almost orthogonal to $M_\ast^0$, so we omit the $M_{\nr+1}^\perp$ term here.
 %	In the definition of $X_A$, we omit $M_{\nr+2}^\perp$ too.
@@
 	\begin{align*}
-		\norm{Z_B M_\ast^\diamond \ket{\psi} - M_{\nr+1}M_\ast^\diamond \ket{\psi}} \leq 
-		\sqrt{s}\norm{M_\ast^\diamond \ket{\psi}} O(\sd \sr \qe)
-		= O(\sr \qe/ \sd ).
-	\end{align*}
-	Since $M_\ast^\diamond \ket{\psi} \appd{O(r\se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$,
+		\norm{Z_B M_0^0 \ket{\psi} - M_{\nr+1}M_\ast^0 \ket{\psi}} \leq 
+		\sqrt{s}\norm{M_0^0 \ket{\psi}} O(\sd \qr \qe)
+		= O(\qr \qe/ \sd ).
+	\end{align*}
+	Since $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$,
 	the equation above can be rewritten as 
 	\begin{align*}
-		Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \appd{O(\sr \qe / \sd )} (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}.
+		Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \appd{O(\qr \qe / \sd )} (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}.
 	\end{align*}
@@
 	\begin{align*}
-		O(r\se/d) \geq &\norm{Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}}^2\\
+		O(\sr \se /d) \geq &\norm{Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}}^2\\
 		=&\norm{ Z_BM_{\nr+1}^0 \ket{\psi} - M_{\nr+1}^0\ket{\psi}}^2 + \norm{ Z_BM_{\nr+1}^1 \ket{\psi} + M_{\nr+1}^1\ket{\psi}}^2,
@@
 	\begin{align}
-		&\frac{N_1+N_2}{2c} M_{\nr+1}^0\ket{\psi} \appd{O( \sr \qe /\sd)} M_{\nr+1}^0 \ket{\psi},\\
-		&\frac{N_1+N_2}{2c} M_{\nr+1}^1\ket{\psi} \appd{O( \sr \qe /\sd)} -M_{\nr+1}^1 \ket{\psi}.
+		&\frac{N_1+N_2}{2c} M_{\nr+1}^0\ket{\psi} \appd{O( \qr \qe /\sd)} M_{\nr+1}^0 \ket{\psi},\\
+		&\frac{N_1+N_2}{2c} M_{\nr+1}^1\ket{\psi} \appd{O( \qr \qe /\sd)} -M_{\nr+1}^1 \ket{\psi}.
 	\end{align}
@@
 	\begin{align*}
-		\frac{N_1-N_2}{-2s} M_{\nr+1}^0M_\ast^\diamond \ket{\psi} 
-		\appd{\norm{M_\ast^\diamond\ket{\psi}}/\sqrt{s} O(\sd \sr \qe)}M_{\nr+2} M_{\nr+1}^1M_\ast^\diamond\ket{\psi}\\
-		\frac{N_1 -N_2}{-2s} M_{\nr+1}^1M_\ast^\diamond \ket{\psi}  
-		\appd{\norm{M_\ast^\diamond \ket{\psi}}/\sqrt{s}O(\sd \sr \qe)}M_{\nr+2} M_{\nr+1}^0 M_\ast^\diamond \ket{\psi}.
-	\end{align*}
-	Using the facts that $M_\ast^\diamond \ket{\psi} \appd{O(r\se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$
-	and $O(\sd \sr \qe)$ dominates $O(r \se)$, we know
-	\begin{align}
-		(N_1-N_2) M_{\nr+1}^0 \ket{\psi} \appd{O(\sr\qe/\sd )} -2sM_{\nr+2} M_{n+1}^1 \ket{\psi},\\
-		(N_1-N_2) M_{\nr+1}^1 \ket{\psi}\appd{O(\sr\qe/\sd )} -2sM_{\nr+2} M_{n+1}^0 \ket{\psi}.
+		\frac{N_1-N_2}{-2s} M_{\nr+1}^0M_0^0 \ket{\psi} 
+		\appd{\norm{M_0^0\ket{\psi}}/\sqrt{s} O(\sd \qr \qe)}M_{\nr+2} M_{\nr+1}^1M_0^0\ket{\psi}\\
+		\frac{N_1 -N_2}{-2s} M_{\nr+1}^1M_\ast^0 \ket{\psi}  
+		\appd{\norm{M_0^0 \ket{\psi}}/\sqrt{s}O(\sd \qr \qe)}M_{\nr+2} M_{\nr+1}^0 M_0^0 \ket{\psi}.
+	\end{align*}
+	Using the facts that $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$
+	and $O(\sd \qr \qe)$ dominates $O(\sr \se)$, we know
+	\begin{align}
+		(N_1-N_2) M_{\nr+1}^0 \ket{\psi} \appd{O(\qr\qe/\sd )} -2sM_{\nr+2} M_{\nr+1}^1 \ket{\psi},\\
+		(N_1-N_2) M_{\nr+1}^1 \ket{\psi}\appd{O(\qr\qe/\sd )} -2sM_{\nr+2} M_{\nr+1}^0 \ket{\psi}.
 	\end{align}
@@
         \begin{align*}
-        		&N_1M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \qe/ \sd)} cM_{\nr+1}^0\ket{\psi} - sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
-        		&N_1M_{\nr+1}^1 \ket{\psi} \appd{O(\sr \qe/ \sd)} -cM_{\nr+1}^1\ket{\psi} - sM_{\nr+2}M_{\nr+1}^0\ket{\psi},\\
-        		&N_2M_{\nr+1}^0 \ket{\psi} \appd{O( \sr \qe /\sd)} cM_{\nr+1}^0\ket{\psi} + sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
-        		&N_2M_{\nr+1}^1 \ket{\psi} \appd{O(\sr \qe/ \sd )} -cM_{\nr+1}^1\ket{\psi} + sM_{\nr+2}M_{\nr+1}^0\ket{\psi}.
+        		&N_1M_{\nr+1}^0 \ket{\psi} \appd{O(\qr \qe/ \sd)} cM_{\nr+1}^0\ket{\psi} - sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
+        		&N_1M_{\nr+1}^1 \ket{\psi} \appd{O(\qr \qe/ \sd)} -cM_{\nr+1}^1\ket{\psi} - sM_{\nr+2}M_{\nr+1}^0\ket{\psi},\\
+        		&N_2M_{\nr+1}^0 \ket{\psi} \appd{O( \qr \qe /\sd)} cM_{\nr+1}^0\ket{\psi} + sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
+        		&N_2M_{\nr+1}^1 \ket{\psi} \appd{O(\qr \qe/ \sd )} -cM_{\nr+1}^1\ket{\psi} + sM_{\nr+2}M_{\nr+1}^0\ket{\psi}.
         \end{align*}
@@
         		&\quad N_1N_2 M_{\nr+1}^0 \ket{\psi} \\
-		&\appd{O(\sr \qe/\sd)} (c N_1M_{\nr+1}^0 +sM_{\nr+2}N_1M_{\nr+1}^1)\ket{\psi}\\
-        		&\appd{O( \sr \qe/\sd)}(c^2M_{\nr+1}^0- csM_{\nr+2}M_{\nr+1}^1 -csM_{\nr+2}M_{\nr+1}^1 -s^2 M_{\nr+2}^2 M_{\nr+1}^0)\ket{\psi}\\
+		        &\appd{O(\qr \qe/\sd)} (c N_1M_{\nr+1}^0 +sM_{\nr+2}N_1M_{\nr+1}^1)\ket{\psi}\\
+        		&\appd{O( \qr \qe/\sd)}(c^2M_{\nr+1}^0- csM_{\nr+2}M_{\nr+1}^1 -csM_{\nr+2}M_{\nr+1}^1 -s^2 M_{\nr+2}^2 M_{\nr+1}^0)\ket{\psi}\\
         		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^0 - \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.
@@
             &\quad N_1N_2 M_{\nr+1}^1 \ket{\psi} \\
-		&\appd{O( \sr \qe/\sd)} (-c N_1M_{\nr+1}^1 +sM_{\nr+2}N_1M_{\nr+1}^0)\ket{\psi}\\
-        		&\appd{O(\sr \qe/\sd)}(c^2M_{\nr+1}^1+ csM_{\nr+2}M_{\nr+1}^0 +csM_{\nr+2}M_{\nr+1}^0 -s^2 M_{\nr+2}^2 M_{\nr+1}^1)\ket{\psi}\\
+		    &\appd{O( \qr \qe/\sd)} (-c N_1M_{\nr+1}^1 +sM_{\nr+2}N_1M_{\nr+1}^0)\ket{\psi}\\
+        		&\appd{O(\qr \qe/\sd)}(c^2M_{\nr+1}^1+ csM_{\nr+2}M_{\nr+1}^0 +csM_{\nr+2}M_{\nr+1}^0 -s^2 M_{\nr+2}^2 M_{\nr+1}^1)\ket{\psi}\\
         		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^1 + \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^0)\ket{\psi},
@@
         \begin{align*}
-        		N_1N_2 M_{\nr+2}M_{\nr+1}^1 \ket{\psi}\appd{O(\sr \qe/\sd)} 
+        		N_1N_2 M_{\nr+2}M_{\nr+1}^1 \ket{\psi}\appd{O(\qr \qe/\sd)} 
 		\sin(\frac{2\pi}{d}) M_{\nr+1}^0\ket{\psi} + \cos(\frac{2\pi}{d})M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
@@
 		&N_1N_2 (M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi} 
-		\appd{O(\sr \qe/\sd)}\omega_d(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
+		\appd{O(\qr \qe/\sd)}\omega_d(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
 	\end{align}
@@
 	\begin{align}
-		N_1N_2 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d\ket{\psi_1}.
+		N_1N_2 \ket{\psi_1} \appd{O(\qr \qe/\sd)} \omega_d\ket{\psi_1}.
 	\end{align}
@@
 	\begin{align}
-	    \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \sr\qe)} \ket{\psi_2}.
+	    \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \qr\qe)} \ket{\psi_2}.
 	\end{align}
@@
 	To prove \cref{eq:psi1_eq}, 
-	we first recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^0 \ket{\psi}$ 
-	and $M_{\nr+1}^1 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^1 \ket{\psi}$ from \cref{prop:chsh_base},
+	we first recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \se)} N_{\nr+1}^0 \ket{\psi}$ 
+	and $M_{\nr+1}^1 \ket{\psi} \appd{O(\sr \se)} N_{\nr+1}^1 \ket{\psi}$ from \cref{prop:chsh_base},
 	so it suffices to show
@@
 %	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
-	At this point, we can use the anti-commutation relation (\cref{eq:zaxa}) induced by $S_1$  and conclude that 
-	\begin{align*}
-		M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^\diamond\ket{\psi}}}}{c\sqrt{s}}O(\sd\sr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}.
-	\end{align*}
-	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \sr \qe)$.
+	At this point, we can use the anti-commutation relation (\cref{eq:zaxa}) induced by $\bS_1$  and conclude that 
+	\begin{align*}
+		M_{\nr+1}M_{\nr+2} M_\ast^0 \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^0\ket{\psi}}}}{c\sqrt{s}}O(\sd\qr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^0 \ket{\psi}.
+	\end{align*}
+	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \qr \qe)$.
 	Then we can show that 
@@
 		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \\
-			&\appd{O(r\se)} M_{\nr+2}M_{\nr+1} M_\ast^\diamond \ket{\psi} \\
-			&\appd{O(\sd \sr \qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}\\
-			&\appd{O(r\se)} -M_{\nr+1}M_{\nr+2} \ket{\psi} \\
-			&\appd{O(r\se)} -M_{\nr+1} N_{\nr+2} \ket{\psi} \\
-			&\appd{O(r\se)} -N_{\nr+2} N_{\nr+1} \ket{\psi},
-	\end{align*}
-	where we use the fact that $M_\ast^\diamond \ket{\psi} \appd{O(r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\se)}
+			&\appd{O(\sr\se)} M_{\nr+2}M_{\nr+1} M_0^0 \ket{\psi} \\
+			&\appd{O(\sd \qr \qe)} -M_{\nr+1}M_{\nr+2} M_0^0 \ket{\psi}\\
+			&\appd{O(\sr \se)} -M_{\nr+1}M_{\nr+2} \ket{\psi} \\
+			&\appd{O(\sr \se)} -M_{\nr+1} N_{\nr+2} \ket{\psi} \\
+			&\appd{O(\sr \se)} -N_{\nr+2} N_{\nr+1} \ket{\psi},
+	\end{align*}
+	where we use the fact that $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(\sr \se)}
 	(M_{\nr+2}^0+M_{\nr+2}^1) \ket{\psi}$.
 
-	Next, we show that $M_1M_2 \ket{\psi_2}\appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_2}$, which gives
+	Next, we show that $M_1M_2 \ket{\psi_2}\appd{O(\qr \qe/\sd)} \omega_d^{-1} \ket{\psi_2}$, which gives
 	us \cref{eq:psi1_eig2} after substituting in\cref{eq:psi1_eq}.
-	From the strategy $S_2$, we can deduce that 
-	\begin{align}
-		&(M_1+M_2) N_{\nr+1}^0 \ket{\psi} \appd{O(\sr \qe/\sd)} 2c N_{\nr+1}^0 \ket{\psi}.\\
-		&(M_1+M_2) N_{\nr+1}^1 \ket{\psi}  \appd{O(\sr \qe/\sd)} -2cN_{\nr+1}^1 \ket{\psi},\\
-		&(M_1-M_2) N_{\nr+1}^0\ket{\psi} \appd{O(\sr\qe/\sd)}-2sN_{\nr+2} N_{\nr+1}^1\ket{\psi}\\
-		&(M_1-M_2)N_{\nr+1}^1 \ket{\psi} \appd{O(\sr\qe/\sd)} -2sN_{\nr+2} N_{\nr+1}^0 \ket{\psi}.
+	From the strategy $\bS_2$, we can deduce that 
+	\begin{align}
+		&(M_1+M_2) N_{\nr+1}^0 \ket{\psi} \appd{O(\qr \qe/\sd)} 2c N_{\nr+1}^0 \ket{\psi}.\\
+		&(M_1+M_2) N_{\nr+1}^1 \ket{\psi}  \appd{O(\qr \qe/\sd)} -2cN_{\nr+1}^1 \ket{\psi},\\
+		&(M_1-M_2) N_{\nr+1}^0\ket{\psi} \appd{O(\qr\qe/\sd)}-2sN_{\nr+2} N_{\nr+1}^1\ket{\psi}\\
+		&(M_1-M_2)N_{\nr+1}^1 \ket{\psi} \appd{O(\qr\qe/\sd)} -2sN_{\nr+2} N_{\nr+1}^0 \ket{\psi}.
 	\end{align}
@@
 	\begin{align*}
-		M_1M_2 (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi} \appd{O(\sr \qe/\sd)} 
+		M_1M_2 (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi} \appd{O(\qr \qe/\sd)} 
 		\omega_d^{-1} (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1)\ket{\psi} .
@@
 	\begin{align}
-		M_1M_2 \ket{\psi_2} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_2},
+		M_1M_2 \ket{\psi_2} \appd{O(\qr \qe/\sd)} \omega_d^{-1}\ket{\psi_2},
 	\end{align}
 	where we use the fact that $\ket{\psi_2} = 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$
-	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \sr\qe)} \ket{\psi_2}$ gives us that 
-	\begin{align}
-		M_1M_2 \ket{\psi_1} \appd{O(\sd \sr \qe)} \omega_d^{-1}\ket{\psi_1}.
+	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \qr\qe)} \ket{\psi_2}$ gives us that 
+	\begin{align}
+		M_1M_2 \ket{\psi_1} \appd{O(\sd \qr \qe)} \omega_d^{-1}\ket{\psi_1}.
 	\end{align}
@@
 	\begin{align}
-	    M_2M_1 \ket{\psi_1} \appd{O(\sd \sr \qe)} \omega_d\ket{\psi_1}.
+	    M_2M_1 \ket{\psi_1} \appd{O(\sd \qr \qe)} \omega_d\ket{\psi_1}.
 	\end{align}
@@
 Before proving the next lemma, we make one important observation.
-Recall that \cref{prop:lct_base} establishes that there exist observables $\{M_i, N_i\}$ such that 
-$M_iN_i \ket{\psi} \appd{O(r\se)} \ket{\psi}$ for $i = 1 \dots \nr$.
+Recall that \cref{prop:lct_base} establishes that there exist observables $\{M(s), N(s)\}$ such that 
+$M(s)N(s) \ket{\psi} \appd{O(\sr\se)} \ket{\psi}$ for $s \in S$.
 Then we can deduce that 
 \begin{align*}
-	M_4M_3 \x N_4N_3 \ket{\psi} \appd{O(r\se)} M_4 \x N_4 \ket{\psi} \appd{O(r\se)} \ket{\psi},
+	M(a_4)M(a_3) \x N(a_4)N(a_3) \ket{\psi} \appd{O(\sr\se)} M(a_4) \x N(a_4) \ket{\psi} \appd{O(\sr\se)} \ket{\psi},
 \end{align*}
@@
 \begin{align*}
-	U_A\ct \x U_B\ct \ket{\psi} \appd{O(r\se)} \ket{\psi}.
+	U_A\ct \x U_B\ct \ket{\psi} \appd{O(\sr\se)} \ket{\psi}.
 \end{align*}
@@
 \label{lm:decomp_psi}
-Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and 
+Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and 
 define 
@@
 		\bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j}  \ket{\psi_1} =
-		\braket{\psi_1}{\psi_1} \appd{O(r\se)} \frac{1}{d-1}.
-	\end{align*}
-	Using the relation $O_B(U_B\ct)^j \ket{\psi} \appd{O(r^j \se)} (U_B\ct)^j O_B^{r^j}\ket{\psi}$ and \cref{eq:psi1_eig1}, we can deduce that 
+		\braket{\psi_1}{\psi_1} \appd{O(\sr\se)} \frac{1}{d-1}.
+	\end{align*}
+	Using the relation $O_B(U_B\ct)^j \ket{\psi} \appd{O(r^{j+1/2} \se)} (U_B\ct)^j O_B^{r^j}\ket{\psi}$ and \cref{eq:psi1_eig1}, we can deduce that 
 	\begin{align*}
 	    O_B (U_B\ct)^j \ket{\psi_1} &= \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1)  O_B (U_B\ct)^j \ket{\psi}\\
-	                                & \appd{O(r^j \se)} \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) (U_B\ct)^j 
+	   & \appd{O(r^{j+1/2} \se)} \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) (U_B\ct)^j 
 	   O_B^{r^j} \ket{\psi} \\
 	   & = (U_B\ct)^j O_B^{r^j} \ket{\psi_1} \\
-	                                & \appd{O(r^j \sr \qe/ \sd)} \omega_d^{r^j} (U_B\ct)^j\ket{\psi_1}
+	   & \appd{O(r^{j+1/4} \qe/ \sd)} \omega_d^{r^j} (U_B\ct)^j\ket{\psi_1}
 	\end{align*}
@@
         \label{eq:B_omega}
-        O_B (U_B\ct)^j \ket{\psi_1} \appd{O(r^{j+1/2} \qe/ \sd )} \omega_d^{r^j}  (U_B\ct)^j \ket{\psi_1}.
-    \end{align}
+        O_B (U_B\ct)^j \ket{\psi_1} \appd{O(r^{j} \qe/ \sd )} \omega_d^{r^j}  (U_B\ct)^j \ket{\psi_1},
+    \end{align}
+    where we drop the insignificant error term $r^{1/4}$.
 	%Using the relation $O_A(U_A\ct)^j \ket{\psi} \appd{O(r^j \se)} (U_A\ct)^j O_A^{r^j}\ket{\psi}$ and $\ket{\psi_1} \appd{O(\sd \sr \qe)} \ket{\psi_2}$ defined in the proof of \cref{prop:psi1},
@@
     \label{eq:A_omega}
-        O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j+1/2} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1},
-    \end{align}
-    which will be used later as well.
+        O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
+    \end{align}
 	Hence for $j \neq j'$, $(U_A\ct U_B\ct)^{j} \ket{\psi_1}$ and $(U_A\ct U_B\ct)^{ j'} \ket{\psi_1}$ are close to eigenvectors
@@
 	\begin{align*}
-		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O( (r^j + r^{j'})\sr \qe)} 0,
+		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O( (r^j + r^{j'}) \qe)} 0,
 	\end{align*}
@@
 		\braket{\psi'}{\psi'} &=\sum_{j,j'=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j'} \ket{\psi_1}\\
-		&\appd{O(dr^{d+1/2} \qe)} \sum_{j=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}\\
+		&\appd{O(dr^{d} \qe)} \sum_{j=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}\\
 		&\appd{O(dr\se)} (d-1) \frac{1}{d-1} = 1.
@@
 		\braket{\psi}{\psi'} = \sum_{j=1}^{d-1} \bra{\psi} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}
-		 \appd{O(d^2r\se)} (d-1) \braket{\psi}{\psi_1}.
+		 \appd{O(d^2\sr\se)} (d-1) \braket{\psi}{\psi_1}.
 	\end{align*}
@@
 		& = \frac{1}{2} \left(\bra{\psi}(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - i \bra{\psi}M_{\nr+2}M_{\nr+1} \ket{\psi} \right)\\
-		& \appd{O(r\se)} \frac{1}{2} \left(\bra{\psi}(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}  - i \bra{\psi}N_{\nr+2}M_{\nr+1} \ket{\psi} \right)\\
+		& \appd{O(\sr\se)} \frac{1}{2} \left(\bra{\psi}(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}  - i \bra{\psi}N_{\nr+2}M_{\nr+1} \ket{\psi} \right)\\
 		& \appd{O(r^2 \ep)} \frac{1}{2} \frac{2}{d-1} = \frac{1}{d-1},
@@
 	where the last approximation comes from the correlation.
-	Hence, we know $\braket{\psi}{\psi'} \appd{O(d^2 r \se)} 1$.
+	Hence, we know $\braket{\psi}{\psi'} \appd{O(d^2 \sr \se)} 1$.
 	In the end, we apply \cref{prop:close_vec} to get
@@
 %------------------------------------------------------------------------------------------
-\subsection{Implications of passing the commutation test}
+\subsection{Implications of passing the commutation games}
 \label{sec:imp_comm}
 %-------------------------------------------------------------------------------------------
-The commutation test is introduced to certify the operators used for the Magic Square test (part of $\LS(r)$ and 
-the operators for the extended weighted CHSH test commute. For the details of the general commutation test, 
+The commutation games are introduced to certify the operators used in $\LS(r)$ commute with 
+the operators for the extended weighted CHSH test. For the details of the general commutation test, 
 we refer to Appendix~A.$2$ of \cite{coladan2017verifier}. 
@@
 
-The implication of passing the commutation test is summarized in the following proposition.
+The implication of winning the commutation games is summarized in the following proposition.
 \begin{proposition}
 	\label{prop:rel_comm}
-	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$.
+	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
 	Then, 
 	\begin{align}
-		&M_{\nr+1}^0 M_j \ket{\psi} \appd{O(r\se)} M_{j} M_{\nr+1}^0 \ket{\psi}, &&
-		M_{\nr+1}^1 M_j \ket{\psi} \appd{O(r\se)} M_{j} M_{\nr+1}^1 \ket{\psi}, \\
-		&M_{\nr+2} M_j \ket{\psi} \appd{O(r\se)} M_j M_{\nr+2} \ket{\psi},
-	\end{align}
-	for $j = r+6, r+8,r+9,r+11$.
+		&M_{\nr+1}^0 M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+1}^0 \ket{\psi}, &&
+		M_{\nr+1}^1 M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+1}^1 \ket{\psi}, \\
+		\label{eq:com_nr2} &M_{\nr+2} M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+2} \ket{\psi},
+	\end{align}
+	for $s = f_0, f_2,g_0,g_2$.
 \end{proposition}
-Note that $M_j$'s for $j = r+6, r+8,r+9,r+11$ tested in the commutation test are used in the Magic Square test,
+Note that the $M(s)$'s for $s = f_0, f_2,g_0,g_2$ tested in the commutation test are used for
+equations of the Magic Square game in $\LS(r)$,
 which will be used to construct the isometry in the next subsection.
 \begin{proof}
-	The case of $[M_j, M_{\nr+2}]$ is an application of Lemma~$28$ of \cite{coladan2017verifier} with $\se$ replaced by $O(r\se)$.
-
-	For the other relations, we prove $M_{\nr+1}^0M_{r+6} \ket{\psi} \appd{O(r\se)} M_{r+6}M_{\nr+1}^0 \ket{\psi}$ to demonstrate 
-	the techniques involved. We denote Bob's projectors by $\{ N_{(\nr+1, r+6)}^{b_1 b_2} \}$ where $b_1 \in \{0, 1, \perp\}$ and
+	Proving \cref{eq:com_nr2} is an application of Lemma~$28$ of \cite{coladan2017verifier} with $\se$ replaced by $O(\sr \se)$.
+
+	For the other relations, we prove $M_{\nr+1}^0M(f_0) \ket{\psi} \appd{O(\sr \se)} M(f_0)M_{\nr+1}^0 \ket{\psi}$ to demonstrate 
+	the techniques involved. We denote Bob's projectors by $\{ N_{(\nr+1, f_0)}^{b_1 b_2} \}$ where $b_1 \in \{0, 1, 2\}$ and
 	$b_2 \in \{0,1\}$. From the correlation, we can get that 
 	\begin{align*}
-		&M_{\nr+1}^0 \ket{\psi} \appd{O(r\se)} (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01}) \ket{\psi} \\
-		&M_{r+6} \ket{\psi} \appd{O(r\se)} (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, r+6)}^{b_1b_2})\ket{\psi}.
+		&M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \se)} 
+		(N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) \ket{\psi} \\
+		&M(f_0) \ket{\psi} \appd{O(\sr \se)} 
+		(\sum_{b_1, b_2} (-1)^{b_2} N_{(\nr+1, f_0)}^{b_1b_2})\ket{\psi}.
 	\end{align*}
@@
 	\begin{align*}
-		M_{\nr+1}^0 M_{r+6} \ket{\psi} &\appd{O(r\se)} M_{\nr+1}^0 (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, r+6)}^{b_1b_2})\ket{\psi}\\
-		&\appd{O(r\se)}(\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, r+6)}^{b_1b_2}) (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01})
-		\ket{\psi} \\
-		&= (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01}) (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, r+6)}^{b_1b_2})  \ket{\psi} \\
-		& \appd{O(r\se)} (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01}) M_{r+6} \ket{\psi} \\
-		&= M_{r+6}  (N_{(\nr+1, r+6)}^{00} + N_{(\nr+1, r+6)}^{01}) \ket{\psi} \\
-		& \appd{O(r\se)} M_{r+6}M_{\nr+1}^0 \ket{\psi}.
+		M_{\nr+1}^0 M(f_0) \ket{\psi} &\appd{O(\sr \se)} M_{\nr+1}^0 (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1,f_0)}^{b_1b_2})\ket{\psi}\\
+		&\appd{O(\sr\se)}(\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, f_0)}^{b_1b_2}) 
+		(N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) \ket{\psi} \\
+		&= (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, f_0)}^{b_1b_2})  \ket{\psi} \\
+		& \appd{O(\sr \se)} (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) M_{r+6} \ket{\psi} \\
+		&= M_{r+6}  (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) \ket{\psi} \\
+		& \appd{O(\sr\se)} M_{r+6}M(f_0)^0 \ket{\psi}.
 	\end{align*}
@@
 %
-%Suppose $A_{m_r+1} = A_\ast^\diamond- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
+%Suppose $A_{m_r+1} = A_\ast^0- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
 %$2m$-dimensional vector space and $\Pi_{V_A}$ is the projector onto it. The reason why it has dimension $2m$
-%will be clear shortly. On Bob's side, we also have $B_{n_r+1} = B_\ast^\diamond- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
+%will be clear shortly. On Bob's side, we also have $B_{n_r+1} = B_\ast^0- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
 %Recall that from the extended weighted CHSH test, we know
 %\begin{align}
-%	A_\ast^\diamond \ket{\psi} = B_\ast^\diamond \ket{\psi} = A_\ast^\diamond \x B_\ast^\diamond \ket{\psi},
+%	A_\ast^0 \ket{\psi} = B_\ast^0 \ket{\psi} = A_\ast^0 \x B_\ast^0 \ket{\psi},
 %\end{align}
@@
 %\begin{align}
-%	\tA_\triangle^\diamond \rho_A \tA_\triangle^\diamond = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^\diamond.
+%	\tA_\triangle^0 \rho_A \tA_\triangle^0 = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^0.
 %\end{align}
@@
 	\begin{align}
+	    \label{eq:uo_comm}
+	    &(u_1u_2) o_2 (u_2u_1) = o_2 \\ 
 	    \label{eq:uo_rel}
-		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
+		&(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
 	\end{align}
@@
 \begin{proof}
-    We prove that $\Pg$ is embedded in $\Pg_0$ by prove the $j = 1$ case of \cref{eq:uo_rel}.
+    We prove \cref{eq:uo_comm} first. It is easy to see that
+    \begin{align}
+        u_1 (u_2o_2u_2) u_1 = u_1u_4u_1 =o_2.
+    \end{align}
+
+    Next, we prove that $\Pg$ is embedded in $\Pg_0$ by prove the $j = 1$ case of \cref{eq:uo_rel}.
     After it is proven, a homomorphism $\phi: \Pg \rightarrow \Pg_0$ such that $\phi(u) = u_1u_2$ and $\phi(o) = o_1o_2$ is injective by Proposition $33$
@@
 	The group $\Pg_1$ can be embedded in $\Gamma$.
-	The generators of $\Gamma$ also satisfy the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
+	The generators of $\Gamma$ also satisfy the relations: 
+	\begin{align}
+	    \label{eq:mg1} &f_0 g_0 f_0 g_0 = J,\\
+	    \label{eq:mg2} &f_2 g_2 f_2 g_2 = J.
+	\end{align}
 \end{proposition}
@@
 $[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$. 
+We can also check that the representation $\Psi_0$ satisfies the relations
+that $\Psi_0(a_3a_4) \Psi_0(a_2) \Psi_0(a_4a_3) = \Psi_0(a_2)$ by observing that
+	\begin{align*}
+		\Psi_0(a_3)\Psi_0(a_4)= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
+	\end{align*}
+	so we can conclude  
+	\begin{align*}
+		&\Psi_0(a_3)\Psi_0(a_4) \Psi_0(a_2) \Psi_0(a_4) \Psi_0(a_3)\\
+		= &\sum_{j=0}^{(d-3)/2} \Psi_0(a_3)\Psi_0(a_4) (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) \Psi_0(a_4)\Psi_0(a_3)\\
+		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}}\\ 
+		=& \Psi_0(a_2).
+	\end{align*}
 

### 2019-07-26 Draft/draft.tex
new definition of the nonlocal game and tests new formulation of the full test

@@
 \usepackage{soul}
-
-% Young Tableaux
-\usepackage{ytableau}
 
@@
 \newcommand{\MS}{MS}
-\newcommand{\SVT}{SVT}
+\newcommand{\EXT}{EXT}
+\newcommand{\LS}{LS}
+\newcommand{\COMM}{COMM}
 \newcommand{\EPR}[1]{\Sigma^{(#1)}}
@@
 \newcommand{\pauliz}{\sigma_z}
-\newcommand{\G}{G}
-\newcommand{\LS}{LS}
+\newcommand{\tP}{\tilde{P}}
+\newcommand{\tQ}{\tilde{Q}}
 \newcommand{\tM}{\tilde{M}}
@@
 \newcommand{\ba}{\pmb{a}}
+\newcommand{\bb}{\pmb{b}}
 \newcommand{\bc}{\pmb{c}}
-\newcommand{\bS}{\pmb{S}}
+\newcommand{\bS}{\mathrm{S}}
 
@@
 The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
-\hf{The special form of this maximally entangled state is the effect of our linear system game.} \carl{I don't know what that sentence means.  Refer to something specific.}
 The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
@@
 \end{align}
-\hf{Note that we only work with finite Hilbert spaces in our work.}
+Note that we only work with finite Hilbert spaces in our work.
 
@@
 representation, so 
-We \hf{introduce them} below.
+We introduce them below.
 For more contexts, please refer to Ref.~\cite{dummit2004}.
@@
 For a more formal treatment, we refer to Section $6.3$ of Ref.~\cite{dummit2004}.}
-\carl{This definition is (still) confusing.  It would be ok to simply cite the concept of a free group, provided that you refer to a precise \& complete definition.}
 
@@
 and the relations of the form
-$s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.   \carl{This last sentence
-needs to be made more precise (e.g., are
-repetitions allows in the linear relations)?}
-\hfc{I thought the fact that $\{s_j\}$ is a subset of $S$ guarantees that there will be no repetitions in a linear relation.}
+$s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.   
 There are two special types of groups that we will work with in \cref{sec:lsg}. We give the definitions below.
@@
 \end{definition}
+\carl{Nice work with the last two definitions -- they are prettty clean.
+I wonder if you could make the last definition even cleaner by simply asserting the relations $s_j s_k = s_k s_j$, and leaving out the generators $s_{jk}$?}
+\hfc{If we treat the commutation relations as conjugacy relations, then the final solution will be more complicated.}
 The relation $s_{jk} s_js_k = e$ implies that $s_j$ commutes with $s_k$
@@
 In a nonlocal game, there are two players, Alice and Bob and each of them is requested
-to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and her answer set by $\calA$. Similarly,
-Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
-comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
-and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function.
+to give an answer for a randomly chosen question. 
+\hf{We denote Alice's question set by $\calX$ and her family of answer sets by $\{\calA_x\}_x$
+for each $x \in \calX$. Similarly,
+Bob's question set is denoted by $\calY$ and his family of answer sets denoted by $\{\calB_y\}_y$ for each $y \in \calY$. 
+Note that when $\calA_x = \calA$ for each $x \in \calX$, we simply say the output alphabet is $\calA$, and we follow this convention on Bob's side too.
+The nonlocal game also
+comes with a functions $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
+and a family of functions $\{ V_{(x,y)} : \calA_x \times \calB_y \rightarrow \R \}_{x,y}$ for each $(x,y) \in \calX \times \calY$, which is 
+the family of scoring functions.
+Note that when $\calA_x = \calA$ for all $x$ and $\calB_y = \calB$ for all $y$, we write the score function as 
+$V: \calA \times \calB \times \calX \times \calY \rightarrow \R$.
+}
 
 \hf{We also define A nonlocal test 
-to be a tuple $(\calX, \calY, \calA, \calB, \pi)$, where
-$\calX, \calY, \calA, \calB$ and $\pi$ are as defined for a nonlocal game, so a nonlocal test doesn't have a scoring function.}
-
-A quantum strategy of a nonlocal game presented in terms of projective measurements
-consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
-$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. 
+to be a tuple $(\calX, \calY, \{\calA_x\}_{x \in \calX}, \{\calB_y\}_{y \in \calY}, \pi)$, where
+$\calX, \calY, \{\calA_x\}_{x}, \{\calB_y\}_{y}$ and $\pi$ are as defined for a nonlocal game.
+Hence, a nonlocal test doesn't have scoring functions.
+}
+
+A quantum strategy of a nonlocal game or a nonlocal test presented in terms of projective measurements
+consists of projective measurements $\{\{M_x^a\}_{a \in \calA_x} \}_{x \in \calX}$ on Alice's side, 
+$\{\{N_y^b\}_{b \in \calB_y} \}_{y \in \calY}$ on Bob's side, and a shared state $\ket{\psi}$. 
 By projective measurements, we mean that  
@@
 \begin{align}
-	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
-\end{align}
-\hf{Note that the tensor product structure indicates that the
-two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.}
+	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
+\end{align}
+for each $(x,y) \in \calX \times \calY$ and $(a,b) \in \calA_x \times \calB_y$.
+Note that the tensor product structure indicates that the
+two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.
 For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
@@
 \begin{definition}
-	Given sets $\calX, \calY, \calA, \calB$, a correlation is a conditional probability distribution
-	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.  
+	Given input alphabets: $\calX$ and $\calY$, and families of output
+	alphabets: $\{\calA_x\}_{x \in \calX}$ and $\{\calB_y\}_{y \in \calY}$, a correlation is a family of conditional probability distributions
+	$\{\pr{ab}{xy}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
 \end{definition}
-A particular type of nonlocal games that we are interested in is called linear system games.
+A particular type of nonlocal games that we are interested in is called binary linear system games.
 \begin{definition}[Binary linear system game]
- Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ \carl{(meaning that} $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
- $c$ is a length-$n$ vector with entries in $\Z_2$\carl{)}. 
+ Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ (meaning that $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
+ $c$ is a length-$n$ vector with entries in $\Z_2$). 
  The associated linear system game involves two
  players Alice and Bob. 
- Alice is given an equation number $i \in \calX = \{1 \dots m\}$,
- and replies with $\ba \in \calA = \Z_2^{\times n}$.
- Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
- scoring function is defined by
- \begin{align}
- 	V(\ua, b, i, j) =
+ The input and output alphabets are 
+ \begin{align*}
+     \calX = \{I_i\}_{i=1}^m && \calY = \{1 \dots n\} \\
+     \calA_{I_i} = \Z_2^{|I_i|} && \calB = \Z_2,
+ \end{align*}
+ where $I_i = \{j : H(i,j) = 1\}$.
+ When Alice and Bob answer with $\ba$ and $b$ for questions $I_i$ and
+ $j$ respectively,
+ the scoring functions are defined by
+ \begin{align}
+ 	V_{(I_i,j)}(\ba, b) =
 	\begin{cases}
-		1, \quad \text{if } \sum_{k=1}^n H(i,k) a(k) \equiv c(i) \pmod 2 \text{ and } a(j) = b \\
+		1, \quad \text{if } \sum_{k \in I_i} H(i,k) a(k) \equiv c(i) \pmod 2 \text{ and } a(j) = b \\
 		0,  \quad \text{otherwise.}
@@
 \end{definition}
+\hfc{I think the order of the variables given to Alice doesn't matter, because
+the linear system is binary.}
 A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
@@
 \end{definition}
-\hf{Note that a measurement strategy of a binary linear system game can be converted to a binary observable strategy. Let a  measurement strategy be 
+Note that a measurement strategy of a binary linear system game can be converted to a binary observable strategy. Let a measurement strategy be 
 $(\{\{M_i^{\ba}\}_{\ba \in X_i}\}_{i=1}^m, \{\{N_j^b\}_{b=0}^1\}_{j=1}^n,\\ \ket{\psi})$, where $X_i$ is some answer set of equation $i$.
@@
 \begin{align*}
-    M_{ij} = \sum_{\ba: a(j)=0} M_i^{\ba} - \sum_{\ba: a(j) =1}
+    M_{ij} := \sum_{\ba: a(j)=0} M_i^{\ba} - \sum_{\ba: a(j) =1}
     M_i^{\ba}
 \end{align*}
-for $1\leq i \leq m$ and $1 \leq j \leq n$. Hence, in the rest of the work, we focus on binary observable strategies.}
+for $1\leq i \leq m$ and $1 \leq j \leq n$. 
+\hf{
+Hence, in the rest of the work, we focus on binary observable strategies,
+when discussing Alice's strategy of some linear system game.
+Specifically, we assume that Alice has a binary observable for each variable
+in each equation ,
+so when she is asked the assignment of a particular variable, she simply
+measures according to the corresponding observable of that variable in some equation.}
 
@@
 but sketch this procedure in \cref{sec:embed_idea}. 
-In \cref{sec:lsg_def}, we define $\Gamma$ and introduce how to
+In \cref{sec:gamma_def}, we define $\Gamma$ and introduce how to
 construct $\LS(r)$ from $\Gamma$.
@@
 The special property of $R_1$ is that every relation in $R_0$ can be recovered from $R_1$.
-Ensuring that every conjugacy relation is associating two commuting operators is the purpose of introducing $\Pg_1$. 
+Ensuring that every conjugacy relation is associating two commuting operators is the purpose of introducing $\Pg_1$. \carl{I think a reader would find that last statement unclear.}
+\hfc{Maybe we just remove it?}
 It makes the construction of a finite-dimension representation of $\Gamma$ from
@@
 \end{align*}
-\carl{It would be good to explain (or at least reiterate) that these relations allow us to recover the conjugacy relations in $\mathcal{R}_0$.}
-\hfc{I have added some explanation about the derivation. How does it look?}
 
@@
 
-A representation of $\Gamma$ can also be built upon
-a representation $\Psi_1$ of $\Pg_1$, which is defined on
-$\C^2 \x \calH$.
+A representation of $\Gamma$ can also be built from
+a representation $\Psi_1$ of $\Pg_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$
+that was constructed above.
+\carl{At this point the reader may be losing track of the precise meaning of what you're saying.
+Perhaps you could simply say, ``A representation of $\Gamma$ can also be built from the
+representation $\Psi_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$ that was constructed above.''}
+\hfc{Fixed, but I worry about the symbol $\circlearrowleft$.}
 We denote the representation of $\Gamma$ by $\Psi$ and
@@
 
-%----------------------------------------
+%---------------------------------------------------
 \subsection{Formal definitions}
 \label{sec:gamma_def}
-%----------------------------------------
-We define the solution group of the linear system game $\LS(r)$ first, which is constructed following the steps
-described in the previous subsection.
+%---------------------------------------------------
+We define the solution group of the linear system game $\LS(r)$ first, following the steps described in the previous subsection.
+Then we define the game $\LS(r)$.
 \begin{definition}
@@
 \begin{align*}
-	S = \{J\} \cup \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
+	S = \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
 	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
@@
 $
-\item $R_J = \{ JsJs = e \vert s \in S\}$,
+\item $R_J = \{ J s J s = e \vert s \in S\}$,
 \item $R_{base} = \{ s^2 = e \vert s \in S\}$.
 \end{itemize}
-The group $\Gamma$ is a group with the presentation
-$\ip{S:R}$.
-\carl{[If you're really going to claim
-that this is a complete definition, maybe you should write out the set $C$ somewhere as well?]}
+\hf{The group $\Gamma$ is a group with the presentation
+$\ip{S \cup \{J\} : R}$.}
 \end{definition}
-\hfc{I pointed out in the previous subsection that the definition of $C(r)$ is in the Appendix along with the definition of $\Pg_0$. 
-Since $C(r)$ is defined by $\Pg_0$, a stand-alone definition of $C(r)$
-will only confuse the reader. Are you suggesting that we don't make this a definition?}
-
-\hf{From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$ (defined in \cref{def:lsg}). Basically,
+
+From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
 we associate a variable $x(s)$ to each generator $s \in S$.
 Then each linear relation in $R$ can be translated to a linear equation.
-For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$.
-The construction of $\LS(r)$ proves the following theorem.}
+For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
+$f_1g_1m_2 = J$ is translated to the equation
+$x(f_1) + x(g_1) + x(m_2) = 1$. 
+The complete list of the equations is given in \cref{def:lsg_eq}.
+\begin{definition}
+\label{def:lsg}
+The linear system game $\LS(r)$ consists of
+\begin{align*}
+    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
+    & \calY^{\LS} = \{ x(s) : s \in S \},
+\end{align*}
+where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
+and $\mr := 14r + 62$ is the number of equations.  
+\carl{Since you are defining Alice's inputs to be subsets of S, why don't you just define Bob's inputs to be elements of S? Also, again you need to account that
+$J$ is an element of $S$.}
+\hfc{I think setting $\calY = S$ will cause confusion.
+You can see the forms of the equations in \cref{def:lsg_eq}.
+If I set the question set to be $S$, the reader will confuse the 
+linear equations with linear relation.
+I have moved $J$ out of $S$.}
+Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
+The answer sets are 
+\begin{align*}
+    \calA^{\LS} = \Z_2^{3} && \calB^{\LS} = \Z_2,
+\end{align*}
+because $|I_i| = 3$ for all $i$.
+The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
+\begin{align*}
+    \pi^{\LS}(I_i, x(s)) = 
+    \begin{cases}
+        1/N(r) & \text{ if } s \in I_i \\
+        0 & \text{otherwise,}
+    \end{cases}
+\end{align*}
+where $N(r) := 157r + 685$ is the total number of valid question pairs.
+We define $X_i := \{ \ba \in \Z_2^3: \sum_{j=1}^3 a(j) = c(i) \}$, which is the set of all the valid answers of equation $i$.
+Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
+the score function is
+\begin{align*}
+    V^{\LS}(\ba, b, I_i, x(s)) = 
+    \begin{cases}
+        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
+        0 \text{, otherwise}.
+    \end{cases}
+\end{align*}
+\end{definition}
+\hfc{Rewritten.}
+The construction of $\LS(r)$ proves the following theorem.
 \begin{theorem}
 	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
-	$n(r) := 16r+75$ variables and $m(r) := 14r + 62$ equations, where each equation has $3$ variables.
+	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
 \end{theorem}
 \hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
-number of equation and variable pairs is $N(r) := 157r + 685$.}
-
-\hf{If Alice and Bob has a strategy that can win the game $\LS(r)$
-almost perfectly, then Alice and Bob has operators satisfy the 
-relation in the presentation of $\Pg$ approximately on their shared state. 
-We give the formal statement of this observation in \cref{sec:imp_lct}. }
-\carl{[This comment seems out of place.]}
-\hfc{We just delete the comment?}
-
-\hf{Since the construction of a representation of $\Gamma$ also follows the procedures detailed in Slofstra's work, 
-we defer the full definitions 
-of our representation $\Psi$ of $\Gamma$, i.e. \cref{def:rep_gamma}, till \cref{sec:rep_gamma}. 
-Instead, we present what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$.
-}  \carl{[The reader may be a little lost when you refer to ``the representation of $\Gamma$.''  A reminder of what that means would be in order.]}
+number of equation and variable pairs is $N(r)$ is of order $\Theta(r)$.}
+
+\hf{The ideal strategy of $\LS(r)$ is based on
+the representation $\Psi$ of $\Gamma$ defined in \cref{def:rep_gamma}
+of \cref{sec:rep_gamma}.
+We discuss the ideal strategy in in \cref{sec:tests}.
+Here we only highlight what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$, along
+with the important properties of the representation of these four generators,
+since they are the key generators of $\Gamma$.
+}
+\carl{This is a meandering paragraph.  Rewrite.}
 \hfc{How about now?}
@@
 dimension $k$.  We denote the
-standard basis of $W_k$
-by $\{\ket{x_j}\}_{j=1}^{k}$.
-The standard basis of $W_{d-1}$ is the eigenbasis of an operator $O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}$.
+standard basis of $W_k$ by $\{\ket{x_j}\}_{j=1}^{k}$.
+We define an operator $O$ on $W_{d-1}$ as
+\begin{align*}
+    O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}.
+\end{align*}
 Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
 modulo $d$ implicitly,
-because another form of $O$ is $\sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}$.
+because another form of $O$ is 
+\begin{align}
+    \label{eq:O}
+    \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}.
+\end{align}
 We use the second form of the basis when it is convenient.
@@
 We denote the identity operator for the subspace $W_k$ by $\1_{W_k}$.
-Consequently, the representations of $a_1, a_2, a_3$ and
+The representations of $a_1, a_2, a_3$ and
 $a_4$ are 
@@
 $u$ and $o$ of $\Pg$ as $\Psi(a_1a_2) = \1_{W_2} \x \1_{W_2} \x O$
-and $\Psi(a_3a_4) = \1_{W_2} \x \1_{W_2} \x U$ where
-\begin{align}
-    &O = \sum_{j=1}^{d-1} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}, \\
-    &U = \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}}.
+and $\Psi(a_3a_4) = \1_{W_2} \x \1_{W_2} \x U$ where $O$ is defined in \cref{eq:O} and
+\begin{align}
+    \label{eq:u1u2}
+    U = \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}}.
 \end{align}
@@
 %====================================================
-\section{Robust self-testing of $\ket{EPR}$ \textit{via} $\I_\alpha$}
+\section{Extending the weighted CHSH inequality $\I_\alpha$ into a nonlocal test}
+\label{sec:ext_chsh}
+%====================================================
+In this section, we introduce the extended weighted CHSH test,
+which is going to be a component of the full test of \cref{sec:full_test}.
+The ideal correlation for this test contains the ideal correlation that 
+achieves $\I_{-\cot(\pi/d)}^{\max}$. 
+To make the study of the implication of a strategy that realize 
+the ideal correlation of the extended weighted CHSH test easier,
+we fill the background of the self-testing property of the
+general weighted CHSH inequality, $\I_\alpha$, first.
+
+%----------------------------------------------------
+\subsection{Robust self-testing of $\ket{EPR}$ \textit{via} $\I_\alpha$}
 \label{sec:chsh}
-%====================================================
+%----------------------------------------------------
 In this section, we show how the weighted CHSH inequality can be used to self-test $\ket{EPR}$ and Pauli operators robustly.
@@
 We follow the convention used in Ref.~\cite{bamps2015},
-\carl{[What convention?  Be a little more specific about what papers this convention is used in.]}, which defines
+which defines
 \begin{align*}
@@
 where \cref{eq:zaxaxbzb} can be derived from \cref{eq:za-zb}, \cref{eq:xa-xb} and \cref{eq:zaxa}.
-\carl{[I don't see a good reason to have such complicated error terms.  You might as well just express all error terms in terms of $\epsilon$ and $\mu$.]}  
+
+%-------------------------------------------
+\subsection{The extended weighted CHSH test}
+\label{sec:ext_w_chsh}
+%-------------------------------------------
+\begin{definition}
+    \label{def:ext_w_chsh}
+    In the extended weighted CHSH test, the input alphabets and output alphabets for Alice and Bob are
+    \begin{align*}
+        &\calX^{\EXT} = \calY^{\EXT} = \{0, 1, 2, \nr+1, \nr+2\}, \\
+        &\calA_x^{\EXT} = \calB_y^{\EXT} =
+        \begin{cases}
+            \{0,2\} &\text{ if } x = y = 0, \\
+            \{0,1\} &\text{ if } x,y \in \{1, 2\} \\
+            \{0,1,2\} &\text{ if } x,y \in \{\nr+1, \nr+2\}. 
+        \end{cases}
+    \end{align*}
+    The probability distribution over the question pairs is uniform.
+\end{definition}
+The reason why this test is called the extended weighted CHSH test will be clear 
+after we introduce the ideal strategy.
+
+Recall the Hilbert space $W_{d-1}$ defined in \cref{sec:gamma_def}. 
+To make the shared state and the observables of the ideal strategy have
+simpler forms, we introduce the third basis of $W_{d-1}$: $\{ \ket{j} \}_{j=1}^{d-1}$, \hf{which is defined by}
+\begin{align*}
+    &\ket{j} = -\frac{1}{\sqrt{2}}(\ket{x_j} + e^{-ij\pi/d}\ket{x_{d-j}}) \\
+    &\ket{d-j} = \frac{i}{\sqrt{2}}(\ket{x_j} - e^{-ij\pi/d}\ket{x_{d-j}})
+	%\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), \\
+	%\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j})
+\end{align*}
+for $1 \leq j \leq \frac{d-1}{2}$.
+The shared state of the ideal strategy is 
+\begin{equation}
+    \label{eq:tpsi}
+    \begin{aligned}
+        \ket{\tpsi}^{\EXT}
+         =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j}),
+    \end{aligned}
+\end{equation}
+where the superscript $\EXT$ stresses the fact this state is for the extended weighted CHSH test.
+Note that in the standard basis of $W_{d-1}$,
+\begin{align*}
+    \ket{\tpsi}^{\EXT} = \frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}.
+\end{align*}
+\carl{The indirect way that you start to use $\left| j \right>$ in your explanation here is confusing.
+If you're going to introduce a new mathematical object, then define it explicitly at the outset.}
+\hfc{Fixed.}
+
+We define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$.
+The corresponding projective measurements are $\Pi_V$ and $\Pi_{V^\perp}$. Note that $V$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$.
+
+First of all, the ideal strategy ensures that when 
+Alice and Bob get the same question from the set $\{0,\nr+1,\nr+2\}$, they always give the same answer.
+Alice's and Bob's measurements for questions $0, \nr+1$ and $\nr+2$ are
+\begin{align*}
+	&\tP_0^0 = \tQ_0^0 = \Pi_V && \tP_0^2 = \tQ_0^2 = \Pi_{V^\perp} \\
+	&\tP_{\nr+1}^0 = \tQ_{\nr+1}^0 = \ketbra{1}{1} &&
+	\tP_{\nr+1}^1 = \tQ_{\nr+1}^1 = \ketbra{d-1}{d-1} \\
+	&\tP_{\nr+2}^0 = \tQ_{\nr+2}^0 = \ketbra{1_{\times}}{1_{\times}} && \tP_{\nr+2}^1 = \tQ_{\nr+2}^1 = \ketbra{(d-1)_{\times}}{(d-1)_{\times}} \\
+	&\tP_{\nr+1}^2 = \tQ_{\nr+1}^2 = \Pi_{V^\perp} &&
+	 \tP_{\nr+2}^2 = \tQ_{\nr+2}^2 = \Pi_{V^\perp},
+\end{align*}
+where
+\begin{align*}
+    \ket{1_{\times}} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
+	&&\ket{(d-1)_{\times}} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
+\end{align*}
+Intuitively, these questions force Alice and Bob to agree on the subspace $V$ and
+on the basis of $V$ that they will measure.
+
+The ideal strategy also ensures that 
+when Alice gets $x \in \{1,2\}$ and Bob gets $y \in \{\nr+1, \nr+2\}$, 
+their answers $a,b \in \{0,1\}$ should maximize $\I_{\cot(-\pi/d)}$ with Alice and Bob's roles flipped;
+and when Alice gets $x \in \{\nr+1,\nr+2\}$ and Bob gets $y \in \{1, 2\}$,
+their answers $a,b \in \{0,1\}$ should maximize $\I_{\cot(-\pi/d)}$.
+This is the reason behind naming this test the extended weighted CHSH test.
+It is also the reason behind having Alice and Bob agreeing on the subspace $V$ 
+by using the other three questions.
+Before introducing the measurements, 
+we define some basis states of $V$
+\begin{align*}
+	&\ket{1_+} = \cos(-\frac{\pi}{2d})\ket{1} + \sin(-\frac{\pi}{2d})\ket{d-1}
+	&&\ket{(d-1)_+} = \sin(-\frac{\pi}{2d})\ket{1} - \cos(-\frac{\pi}{2d})\ket{d-1}\\
+	&\ket{1_-} = \cos(-\frac{\pi}{2d})\ket{1} - \sin(-\frac{\pi}{2d})\ket{d-1}
+	&&\ket{(d-1)_-} = \sin(-\frac{\pi}{2d})\ket{1} + \cos(-\frac{\pi}{2d})\ket{d-1},
+\end{align*}
+so that $\{\ket{1_+}, \ket{(d-1)}_+\}$ and $\{\ket{1_-}, \ket{(d-1)_-}\}$ are two basis
+of $V$.
+When Alice and Bob gets question $1$ or $2$, what they measure on $V$ are
+\begin{align*}
+	&\tP_1^0 = \tQ_1^0 =  \ketbra{1_+}{1_+} && \tP_1^1 = \tQ_1^1 =  \ketbra{(d-1)_+}{(d-1)_+}\\
+	&\tP_2^0 = \tQ_2^0 =  \ketbra{1_-}{1_-} && \tP_1^1 = \tQ_1^1 =  \ketbra{(d-1)_-}{(d-1)_-}.
+\end{align*}
+Notice that their measurements on $V$ follow the measurements to achieve $\I_{\cot(-\pi/d)}^{\max}$.
+What they measure on $V^\perp$ is irrelevant for this test. 
+%Later we will see that their measurements on $V^\perp$ are determined by their observables for variables $x(a_1)$ and $x(a_2)$ of $\LS(r)$.
+
+We will present the ideal correlation of the extended weighted CHSH test
+in \cref{sec:cor} as part of the full correlation.
+
 %==========================
@@
 Then we explain how they are combined in the full test and present the ideal strategy for the full test in \cref{sec:ideal_strat}.
-\carl{[I'm a little skeptical that the phrase ``pass the three test'' is meaningful here -- I don't know that these are the kind of tests that can be ``passed.'']}
-\hfc{I have removed that phrase. How is my changes?}
 The full correlation, denoted by $\fC(r,d)$, is generated by the ideal strategy and presented in \cref{sec:cor}.
@@
 %----------------------------
-\textbf{The linear system game $\LS(r)$} (\cref{def:lsg}) consists of
-\begin{align*}
-    & \calX = \{I_i\}_{i=1}^{\mr}, \\
-    & \calY = \{ x(s) : s \in S \},
-\end{align*}
-where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$.
-From the construction of $\LS(r)$, we know that $|I_i| = 3$ for all $i$.
-Hence, the answer sets are 
-\begin{align*}
-    \calA = \Z_2^3 && \calB = \Z_2.
-\end{align*}
-The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$.
-We define $X_i := \{ \ba \in \Z_2^3: \sum_{j=1}^3 a(j) = c(i) \}$, which is the set of all the valid answers of equation $i$.
-Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
-the score function is
-\begin{align*}
-    V_{\LS(r)}(\ba, b, I_i, x(s)) = 
-    \begin{cases}
-        1 \text{, if} \ba \in X_i \text{ and } a(s) = b\\
-        0 \text{, otherwise}.
-    \end{cases}
-\end{align*}
-
-The ideal strategy of $\LS(r)$ follows the representation $\Psi$ of $\Gamma$.
+
+The first component of the full test is $\LS(r)$ defined in
+\cref{def:lsg}.
+The ideal strategy of $\LS(r)$ follows the representation $\Psi$ of $\Gamma$ (\cref{def:rep_gamma}).
 Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}. 
 In the ideal strategy Alice and Bob share the state 
-\begin{align*}
-        \ket{\tpsi} = \frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right).
-\end{align*}
+\begin{align}
+    \label{eq:ideal_st_ls}
+        \ket{\tpsi}^{\LS} = \frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right).
+\end{align}
 Alice and Bob's observables for each variable $x(s)$ are
@@
 
-\textbf{The extended weighted CHSH test} consists of
-\begin{align*}
-    &\calX = \calY = \{0, 1, 2, \nr+1, \nr+2\} \\
-    &\calA = \calB = \{0,1,2\}.
-\end{align*}
-The probability distribution over the question pairs is uniform.
-The reason why this test is called the extended weighted CHSH test will be clear after we introduce
-the ideal strategy.
-
-Recall the Hilbert space $W_{d-1}$ defined in \cref{sec:gamma_def}. 
-The shared state of the ideal strategy is 
-\begin{equation}
-    \label{eq:tpsi}
-    \begin{aligned}
-        \ket{\tpsi} = & \frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\\
-         =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j}).
-    \end{aligned}
-\end{equation}
-Here we introduce the third basis of $W_{d-1}$: $\{ \ket{j} \}_{j=1}^{d-1}$, so that
-the observables used in the extended weighted CHSH test have a simpler form.
-The two basis are related by
-\begin{align*}
-	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
-	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j})
-\end{align*}
-for $1 \leq j \leq \frac{d-1}{2}$.
-we define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$.
-The corresponding projective measurements are $\Pi_V$ and $\Pi_{V^\perp}$. 
-Note that $V$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$.
-We define the states for the measurements used in the extended weighted CHSH test as follows
-\begin{align*}
-	&\ket{1_+} = \cos(-\frac{\pi}{2d})\ket{1} + \sin(-\frac{\pi}{2d})\ket{d-1}
-	&&\ket{(d-1)_+} = \sin(-\frac{\pi}{2d})\ket{1} - \cos(-\frac{\pi}{2d})\ket{d-1}\\
-	&\ket{1_-} = \cos(-\frac{\pi}{2d})\ket{1} - \sin(-\frac{\pi}{2d})\ket{d-1}
-	&&\ket{(d-1)_-} = \sin(-\frac{\pi}{2d})\ket{1} + \cos(-\frac{\pi}{2d})\ket{d-1}\\
-	&\ket{1_{\times}} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
-	&&\ket{(d-1)_{\times}} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
-\end{align*}
-Alice's measurements for questions $0, \nr+1$ and $\nr+2$ are
-\begin{align*}
-	&\tM_0^0 = \Pi_V && \tM_0^2 = \tM_{\nr+1}^2 = \tM_{\nr+2}^2 = \Pi_{V^\perp}\\
-	&\tM_{\nr+1}^0= \ketbra{1}{1} && \tM_{\nr+1}^1 = \ketbra{d-1}{d-1}\\
-	&\tM_{\nr+2}^0 =  \ketbra{1_{\times}}{1_{\times}} && \tM_{\nr+2}^1 =  \ketbra{(d-1)_{\times}}{(d-1)_{\times}}.
-\end{align*}
-Bob's measurements for questions $0, \nr+1$ and $\nr+2$ are
-\begin{align*}
-    &\tN_0^0 = \Pi_V && \tN_0^2 = \tN_{\nr+1}^2 = \tN_{\nr+2}^2 = \Pi_{V^\perp}\\
-    &\tN_{\nr+1}^0= \ketbra{1}{1} && \tN_{\nr+1}^1 = \ketbra{d-1}{d-1}\\
-	&\tN_{\nr+2}^0=  \ketbra{1_{\times}}{1_{\times}} && \tN_{\nr+2}^1 =  \ketbra{(d-1)_{\times}}{(d-1)_{\times}}.
-\end{align*}
-Observe that the ideal strategy ensures that when 
-Alice and Bob get the same question from the set $\{0,\nr+1,\nr+2\}$, they always give the same answer.
-When Alice and Bob gets question $1$ or $2$, what they measure on $V$ are
-\begin{align*}
-	&\tM_1^0 = \tN_1^0 =  \ketbra{1_+}{1_+} && \tM_1^1 = \tN_1^1 =  \ketbra{(d-1)_+}{(d-1)_+}\\
-	&\tM_2^0 = \tN_2^0 =  \ketbra{1_-}{1_-} && \tM_1^1 = \tN_1^1 =  \ketbra{(d-1)_-}{(d-1)_-}.
-\end{align*}
-What they measure on $V^\perp$ is irrelevant for this test. Later we will see that their measurements on $V^\perp$ are determined by their observables for variables $x(a_1)$ and $x(a_2)$ of $\LS(r)$.
-In other words, they never answer $2$ given question $1$ or $2$.
-
-There are two key observations.
-The first one is that when Alice gets $x \in \{1,2\}$ and Bob gets $y \in \{\nr+1, \nr+2\}$, 
-their answers $a,b \in \{0,1\}$ should maximize $\I_{\cot(-\pi/d)}$ with Alice and Bob's roles flipped.
-The second one is that when Alice gets $x \in \{\nr+1,\nr+2\}$ and Bob gets $y \in \{1, 2\}$,
-their answers $a,b \in \{0,1\}$ should maximize $\I_{\cot(-\pi/d)}$.
-This is the reason behind naming this test the extended weighted CHSH test.
+The second component is the extended weighted CHSH test, introduced in \cref{sec:ext_w_chsh}.
 
@@
 
-\textbf{The commutation game}.
+The third component is a commutation game.
 Our commutation game is the based on the commutation test used in Ref.~\cite{coladan2017verifier}.
@@
 
-There are $8$ pairs of observables that we test, 
-so Bob's input set consists of all the question pairs
-\begin{align*}
-    \calY = \{(\nr+1, x(s)), (\nr+2, x(s)): s = f_0, f_2, g_0, g_2 \},
+Bob's input set consists of eight question pairs
+\begin{align*}
+    \calY^{\COMM} = \{(\nr+1, x(s)), (\nr+2, x(s)): s = f_0, f_2, g_0, g_2 \},
 \end{align*}
@@
 \begin{align*}
-    \calX = \{\nr+1, \nr+2, f_0, f_2, g_0, g_2\}.
+    \calX^{\COMM} = \{\nr+1, \nr+2, f_0, f_2, g_0, g_2\}.
 \end{align*}
@@
 \begin{align*}
-    \calA = \Z_3 && \calB = \Z_3 \times \Z_2.
+    &\calA^{\COMM}_x = 
+    \begin{cases}
+    \Z_3 &\text{ if } x \in \{\nr+1, \nr+2\} \\
+    \Z_2 &\text{otherwise.}
+    \end{cases}
+    \\
+    &\calB^{\COMM} = \Z_3 \times \Z_2.
 \end{align*}
@@
 \begin{align*}
-    \pi_{comm}(x,(y_1,y_2)) =
+    \pi^{\COMM}(x,(y_1,y_2)) =
     \begin{cases}
-        1/16 \text{, if } x = y_1 \text{ or } x = y_2 \\
-        0 \text{, otherwise}.
+        1/16 &\text{ if } x = y_1 \text{ or } x = y_2 \\
+        0   &\text{ otherwise}.
     \end{cases}
@@
 \begin{align*}
-    V_{comm}(a, (b_1,b_2), x, (y_1,y_2)) = 
+    V^{\COMM}(a, (b_1,b_2), x, (y_1,y_2)) = 
     \begin{cases}
-    1 \text{, if } x = y_1 \text{ and } a = b_1 \\
-    1 \text{, if } x = y_2 \text{ and } a = b_2 \\
-    0 \text{, otherwise}.
+    1 &\text{ if } x = y_1 \text{ and } a = b_1 \\
+    1 &\text{ if } x = y_2 \text{ and } a = b_2 \\
+    0 &\text{ otherwise}.
     \end{cases}
@@
 
-What we conclude is slightly different from the original claim
-in Ref.~\cite{coladan2017verifier}.
-Instead of just proving the binary observables commute,
-we prove that the projective measurements
-for question $\nr+1$ commute with the binary observables for question
-$x(s)$ with $s = f_0, f_2, g_0, g_2$ 
-by examining the probability distribution generated by the ideal strategy.
-
-%The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
-%Alice's input is determined by the pair so she receives one of the two questions of a given pair with equal probability.
+% What we conclude is slightly different from the original claim
+% in Ref.~\cite{coladan2017verifier}.
+% Instead of just proving the binary observables commute,
+% we prove that the projective measurements
+% for question $\nr+1$ commute with the binary observables for question
+% $x(s)$ with $s = f_0, f_2, g_0, g_2$ 
+% by examining the probability distribution generated by the ideal strategy.  \carl{I don't think there's enough context for this paragraph.  It may be best to leave it out.}
 
@@
 %-----------------------------------------------
-The question pairs of the full test is the union of the question pairs of each component.
-The only modification is that we changed question $1$ and $2$ from the extended weighted CHSH test to
-the question $x(a_1)$ and $x(a_2)$ from $\LS(r)$. 
-The three components of the full test are conducted with equal probability.
-
-The ideal strategy for the full test is an extension of the ideal strategy for $\LS(r)$ to make it able to produce the ideal correlation of 
+\begin{definition}[The full test]
+The question sets of the full test are
+\begin{align*}
+    \calX = \calX^{\LS} \cup \calX^{\EXT'} \cup \calX^{\COMM} \\
+    \calY = \calY^{\LS} \cup \calY^{\EXT'} \cup \calY^{\COMM},
+\end{align*}
+where $\calX^{\EXT'}$ is obtained from $\calX^{\EXT}$ by replacing 
+$1$ by $x(a_1)$ and $2$ by $x(a_2)$, and similarly for $\calY^{\EXT'}$.
+The answer sets of the full test are
+\begin{align*}
+    \calA_x = 
+    \begin{cases}
+    \Z_2^3 &\text{ if } x \in \calX^{\LS} \\
+    \calA_x^{\EXT'} &\text{ if } x \in \calX^{\EXT'} \\
+    \calA_x^{\COMM} & \text{ if } x \in \calX^{\COMM},
+    \end{cases}
+    &&
+    \calB_y = 
+    \begin{cases}
+    \Z_2 &\text{ if } y \in \calY^{\LS} \\
+    \calB_y^{\EXT'} &\text{ if } y \in \calY^{\EXT'} \\
+    \calB_y^{\COMM} & \text{ if } y \in \calY^{\COMM}.
+    \end{cases}
+\end{align*}
+The answer sets $\calA_x^{\EXT'}$ are obtained from $\calA_x^{\EXT}$
+by setting 
+\begin{align*}
+    \calA_{x(a_1)}^{\EXT'} =\calA_{1}^{\EXT} &&
+    \calA_{x(a_2)}^{\EXT'} =\calA_{2}^{\EXT},
+\end{align*}
+and $\calA_x^{\EXT'} = \calA_x^{\EXT}$ for the other $x \in \calX^{\EXT}$.
+Bob's answer sets $\calB_y^{\EXT'}$ are obtained from $\calB_y^{\EXT}$
+analogously.
+Define $N$ to be the total number of question pairs with nonzero probability 
+of the three components of the full test.
+The question distribution of the full test, $\pi: \calX \times \calY \rightarrow \R$ is defined by
+\begin{align*}
+    \pi(x,y) = \begin{cases}
+    \frac{1}{N} & \text{ if } (x,y) \in \calX^{\LS} \times \calY^{\LS}
+    \text{ and } \pi^{\LS}(x,y) > 0 \\
+    \frac{1}{N} & \text{ if } (x,y) \in \calX^{\EXT'} \times \calY^{\EXT'}\\
+    \frac{1}{N} & \text{ if } (x,y) \in \calX^{\COMM} \times \calY^{\COMM} \text{ and } \pi^{\COMM}(x,y) > 0 \\
+    0 & \text{ otherwise}.
+    \end{cases}
+\end{align*}
+\end{definition}
+
+The ideal strategy for the full test is an extension of the ideal strategy of $\LS(r)$ to make it able to produce the ideal correlation of 
 the extended weighted CHSH test.
-Note that the ideal strategy of the extended weighted CHSH test is defined on $W_{d-1}$ and the ideal strategy of $\LS(r)$ is defined on $W_2^{\x 2} \x W_{d-1}$, 
-so we can modify the ideal strategy of the extended weighted CHSH test by tensoring the shared state with $\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2}$
-and tensoring each projective measurement with $\1_{W_2}^{\x 2}$.
-The effect is the modified strategy for the extended weighted CHSH test 
-becomes compatible with that of $\LS(r)$,
-but the generated correlation remains the same.
-Consequently, the ideal strategy for the full test is defined on $W_2^{\x 2} \x W_{d-1}$.
-The shared state is 
-\begin{align*}
-    \ket{\tpsi} = \frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right).
-\end{align*}
-The observable for each question of $\LS(r)$ is the same as in the ideal
-strategy of $\LS(r)$. For each question from the extended weighted CHSH test, it uses projective measurements from the extended strategy of the test.
-
-To make sure the strategy is correct, we need to check a few properties of it.
-First of all, it is easy to see that this ideal strategy can win the commutation games 
-because the observables for questions $x(f_0), x(f_2),
-x(g_0)$ and $x(g_2)$ act trivially on $W_{d-1}$, which is the subspace the
-measurements for questions $\nr+1$ and $\nr+2$ act on.
-To make sure it wins $\LS(r)$, what we need to check is summarized in the 
+Recall the subspace $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}.
+The shared state of the ideal strategy is
+\begin{align*}
+    \ket{\tpsi} = \ket{\tpsi}^{\LS} = \frac{1}{2}(\ket{x_1}\ket{x_1} + 
+    \ket{x_2}\ket{x_2})^{\x 2} \x \ket{\tpsi}^{\EXT}.
+\end{align*}
+Alice and Bob's observables for each variable in the linear system of 
+$\LS(r)$ are 
+\begin{align*}
+    \tM(s) = \tN(s) = \Psi(s) 
+\end{align*}
+for each $s \in S$ and $\Psi$ is defined in \cref{def:rep_gamma}.
+When Alice get $I_i \in \calX^{\LS}$, she measures her half of the shared
+state according to $\tM(s)$ for each $s \in I_i$.
+
+Alice's and Bob's observables for question $x(a_1)$ and $x(a_2)$ of $\calX^{\EXT'}$ and $\calY^{\EXT'}$ are
+\begin{align*}
+    \tM(a_j) = \tN(a_j) = \Psi(a_j) 
+\end{align*}
+for $j= 1,2$.
+It can be checked that 
+\begin{align*}
+    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_1) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_1^0|_V - \tP_1^1|_V) \\
+    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_2) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_2^0|_V - \tP_2^1|_V),
+\end{align*}
+and similarly on Bob's side.
+Alice's projectors for the other questions of $\calX^{\EXT'}$ are
+\begin{align*}
+    \tM_x^a = \1_{W_2} \x \1_{W_2} \x \tP_x^a
+\end{align*}
+for each $a \in \calA^{\EXT'}_x$.
+Bob's projectors for the other questions of $\calY^{\EXT'}$ are 
+\begin{align*}
+    \tN_y^b = \1_{W_2} \x \1_{W_2} \x \tQ_y^b
+\end{align*}
+for each $b \in \calB^{\EXT'}_y$.
+
+Alice's measurements for $x \in \calX^{\COMM}$ is the same as her
+measurements for the other two tests.
+When Bob gets question $(y_1, y_2) \in \calY^{\COMM}$, he measures 
+according to $\tN_{y_1}^b$ first and then $\tN(y_2)$ because $\tN_{y_1}^b$
+commutes with $\tN(y_2)$ for all $b$ by construction.
+This ensures that the ideal strategy can win the commutation game.
+
+An important property of the ideal strategy for it to win $\LS(r)$ is summarized in the 
 following proposition.
 \begin{proposition}
-The observables $\tM(a_j) = \tN(a_j) = \Psi(a_j)$ for $1 \leq j \leq 4$, where $\Psi$ is defined in \cref{def:rep_gamma}, 
-and the shared state $\ket{\tpsi}$ defined in \cref{eq:tpsi}
+The observables $\tM(s)$, $\tN(s)$
+and the shared state $\ket{\tpsi}$ defined above
 satisfy the relations
 \begin{align}
-	\label{eq:mn_preserve} &\tM(a_j) \tN(a_j) \ket{\tpsi} = \ket{\tpsi},
-\end{align}
-for $j=1,2,3,4$.
+	\label{eq:mn_preserve} &\tM(s) \tN(s) \ket{\tpsi} = \ket{\tpsi},
+\end{align}
+for each $s \in S$.
 \end{proposition}
 \begin{proof}
-	Since all the operators involved in this proposition act trivially on $W_2^{\x 2}$, we focus on
-	their actions on $W_{d-1}$. In the later proof, by $\ket{\tpsi}$ we mean the part of $\ket{\tpsi}$ on $W_{d-1}$.
-
-	Using \cref{eq:o1,eq:o2}, it is straightforward to see that $\tM(a_j)\tN(a_j) \ket{\tpsi} = \ket{\tpsi}$ for $j = 1,2$.
-	Before checking the two cases $j=3$ and $j=4$, we first observe that
-	\begin{align*}
-		\tM(a_3)\tM(a_4) \tN(a_3) \tN(a_4) \ket{\tpsi} = \ket{\tpsi}.
-	\end{align*}
-	The eigenvectors of $\tM(a_3)\tM(a_4)$ and $\tN(a_3)\tN(a_4)$ are 
+    Define $S' = \{f_0, f_1, f_2, g_0, g_1, g_2, m_0, m_1, m_2\} \subset S$. Notice that for each $s \in S'$, both $\tM(s)$ and $\tN(s)$ act
+    trivially on $W_{d-1}$, so we omit the verification that 
+    $\tM(s)\tN(s) \ket{\tpsi} = \ket{\tpsi}$ for each $s \in S'$
+
+	Next, we notice that each $s \in S$ can be expressed as the 
+	product of a sequence of generators in $S'$ and $a_1, a_2, a_3, a_4$, so
+	to prove \cref{eq:mn_preserve}, it suffices to prove that it 
+	holds true for $s = a_1, a_2, a_3, a_4$. 
+	Recall that $\tM(a_j) = \tN(a_j) = \1_{W_2} \x \1_{W_2} \x Psi_0(a_j)$
+	in \cref{def:rep_gamma},
+	where $\Psi_0$ is defined in \cref{def:rep_g0},
+	and $\ket{\tpsi} = \frac{1}{2} (\ket{x_1}\ket{x_1}+\ket{x_2}\ket{x_2})^{\x 2} \x \ket{\tpsi}^{\EXT}$.
+	Hence, the problem is further reduced to proving
+	\begin{align*}
+	    \Psi_0(a_j) \x \Psi_0(a_j) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}.
+	\end{align*}
+	for $1 \leq j \leq 4$.
+
+	Using \cref{eq:o1,eq:o2}, it is straightforward to see that $\Psi_0(a_j)\x \Psi_0(a_j) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ for $j = 1,2$.
+	Before checking the two cases $j=3$ and $j=4$, we can use \cref{eq:u1u2} to derive that
+	\begin{align*}
+		\Psi_0(a_3 a_4) \x\Psi_0(a_3 a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}.
+	\end{align*}
+	The eigenvectors of $\Psi_0(a_3 a_4)$ are $\ket{u_k}$,
+	for $0 \leq k \leq d-2$,
+	and $\ket{u_k}$ are defined by
     \begin{align*}
@@
     \end{align*}
-    Then using \cref{eq:u2} we can deduce that $\tM(a_4)$ acts on $\ket{x_{r^j}}$ by
-    \begin{align*}
-        \tM(a_4) \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} \tM(a_4) \left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
+    Then using \cref{eq:u2} we can deduce that $\Psi_0(a_4)$ acts on $\ket{x_{r^j}}$ by
+    \begin{align*}
+        \Psi_0(a_4) \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} \tM(a_4) \left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
         \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
@@
     \end{align*}
-    Consequently, we can show that $\tM(a_4)  \tN(a_4) \ket{\tpsi} = \ket{\tpsi}$ because
-    \begin{align*}
-        \tM(a_4) \tN(a_4) \ket{\tpsi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \tM(a_4)  \tN(a_4) \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
-        = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\psi},
-    \end{align*}
-	Combining it with the fact that $\tM(a_3)\tM(a_4) \tN(a_3)\tN(a_4) \ket{\tpsi} = \ket{\tpsi}$, we can conclude that
-	$\tM(a_3)\tN(a_3) \ket{\tpsi} = \ket{\tpsi}$.
+    Consequently, we can show that $\Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ 
+    because
+    \begin{align*}
+        \Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \Psi_0(a_4)\x  \Psi_0(a_4) \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
+        = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\tpsi}^{\EXT},
+    \end{align*}
+	Combining it with the fact that $\Psi_0(a_3 a_4) \x \Psi_0(a_3 a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$, we can conclude that
+	$\Psi_0(a_3) \x \Psi_0(a_3) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$.
 \end{proof}
-The similar result, i.e., $\tM(s)\tN(s) \ket{\tpsi} = \ket{\tpsi}$ for $s \in S$ are easy to check because all the other observables are defined by $\tM(a_j), \tN(a_j)$ for $j=1,2,3,4$ and $\tM(f_0), \tM(f_2), \tM(g_0), \tM(g_2)$ and $\tN(f_0), \tN(f_2), \tN(g_0), \tN(g_2)$, which only act non-trivially on $W_2$.
 
@@
 The full correlation is generated by the ideal strategy presented in the previous subsection.
-We denote the full correlation by $\fC(d,r) = ( \tpr{ab}{xy} )$.
-To help readers understanding the proofs in \cref{sec:main} better, 
+We denote the full correlation by $\fC(d,r) = \{( \tpr{ab}{xy} )_{a,b}\}_{x,y}$.
+To help readers to understand the proofs in \cref{sec:main} better, 
 parts of the full correlation is given in the tables below.
@@
 correlation $\fC(d,r)$ approximately and 
-prove that the strategy $\bS$ must contain the state $\ket{EPR}^{\x 2} \x \ket{\EPR{d-1}}$
+prove that the shared state of $\bS$ must be close to the state $\ket{EPR}^{\x 2} \x \ket{\EPR{d-1}}$
 up to some local isometry.
@@
 	\label{eq:expect}
-	E_{(x,y)} \sum_{ab} |\pr{ab}{xy} - \tpr{ab}{xy}| \leq \ep.
+	E_{(x,y)} \sum_{ab} \abs{\pr{ab}{xy} - \tpr{ab}{xy}} \leq \ep.
 	\end{align}
@@
 In our full test, the probability distribution over all the question pairs $(x,y)$ is uniform.
-The number of all the possible question pairs is determined by
-the number of equation and variable pair of $\LS(r)$, which is
-$N(r) = \Theta(r)$.
+The number of all the possible question pairs is 
+$N = \Theta(r)$.
 Considering that
@@
 \end{align*}
-for all $(a,b,x,y)$ of the full test.
+for all valid $(a,b,x,y)$ of the full test.
 
@@
 %------------------------------------------------------------------------------------------
-In the first half of this subsection, we use $(i,x(s))$ to denote the question pair so that Alice gets equation number $i$ and Bob gets a variable label $x(s)$ for some $s \in S$.
-For simplicity, we let Bob get the generator $s$ instead.
+In the first half of this subsection, we use $(I_i,x(s))$ to denote the question pair so that Alice gets equation label $I_i$ and Bob gets a variable label $x(s)$ for some $s \in S$.
+For simplicity, we denote
+Alice's observable for variable $x(s)$ in equation $i$ by $M_i(s)$ and
+Bob's observable for variable $x(s)$ by $N(s)$.
 
@@
 		&M(s) N(s) \ket{\psi} \appd{O(\sr\se)} \ket{\psi} \\
-		&\Pi_{s \in I_i} M(s) \ket{\psi} \appd{O(\sr\se)}(-1)^{\uc(i)} \ket{\psi}.
+		&\Pi_{s \in I_i} M(s) \ket{\psi} \appd{O(\sr\se)}(-1)^{c(i)} \ket{\psi}.
 	\end{align}
@@
 \begin{align*}
-	\bra{\psi} M_i(s) N(s) \ket{\psi} = 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{ij} -1 \appd{O(r \ep)} 1.
-\end{align*}
-Since $M_i(s)$ and $N(s)$ are unitaries, we know that
+	\bra{\psi} M_i(s) N(s) \ket{\psi} &= 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{ij} -1 \\
+	&\appd{O(r \ep)} 2\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{is} - 1 = 1.
+\end{align*}
+Since $M_i(s)$ and $N(s)$ are binary observables, we know that
 \begin{align*}
@@
 \begin{align*}
-	M(s) N(s) \ket{\psi} \appd{O(\sr\se)} M_{i}(s)N(s)\ket{\psi} \appd{O(\sr\se)} \ket{\psi} \quad \text{ for all } s \leq S.
-\end{align*}
+	M(s) N(s) \ket{\psi} & = M_{i}(s)N(s)\ket{\psi} \\
+	    & = N(s) M_{i}(s) \ket{\psi} \\
+	    &\appd{O(\sr\se)} N(s)^2 \ket{\psi} \\
+	    &= \ket{\psi}
+\end{align*}
+for all $s \in S$.
 
@@
 	each relation $r \in R$ on the shared state $\ket{\psi}$, 
-	where $S$ is the generator set of $\Gamma$
-    and $R$ is the relation set of $\Gamma$.	
+	where $S$ and $R$ are defined in the definition of $\Gamma$ 
+	(\cref{def:gamma}).	
 \end{proposition}
@@
 	Then the observables $\{ M(s) \}_{s \in S_1}$ and
-	$\{N(s)\}_{s \in S_1}$ $O(\sr\se)$-approximately satisfy
+	$\{N(s)\}_{s \in S_1}$, defined in 
+\cref{prop:lct_group}, $O(\sr\se)$-approximately satisfy
 	each relation $r \in R_1$ on $\ket{\psi}$, 
@@
 	Then the observables $\{ M(s) \}_{s \in S_0}$ and 
-	$\{N(s)\}_{s \in S_0}$ $O(\sr \se)$-approximately satisfy
+	$\{N(s)\}_{s \in S_0}$, defined in 
+\cref{prop:lct_group}, $O(\sr \se)$-approximately satisfy
 	each relation $r \in R_0$ on the shared state $\ket{\psi}$, 
@@
 The $O(r^{3/2}\se)$ approximation error comes from the fact that 
-the derivation uses $r+3$ conjugacy relations of $R_0$, 
+the derivation has $\Theta(r)$ steps, where each step substitutes in
+a different relation of $R_0$, 
 so we have
@@
 By the principal of induction, the proof is complete.
-The proof for Bob's observables $\{ N(s) \}_{s \in S}$ is similar.
+The proof for Bob's observables $\{ N(s) \}_{s \in S}$ is analogous.
 \end{proof}
@@
 \end{proposition}
-Recall all the relations in \cref{eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma$,
+Recall all the relations in \cref{eq:mg1,eq:mg2} are embedded in the
+six Magic Square relations $R_{MS}$ of $\Gamma$ (\cref{def:gamma}), 
 so this proposition can be proved with the same techniques used in the proof of \cref{prop:lct_group}.
 %------------------------------------------------------------------------------------------
-\subsection{Implication of the extended weighted CHSH test}
+\subsection{Implication of approximating the extended weighted CHSH test}
 \label{sec:imp_chsh}
 %------------------------------------------------------------------------------------------
-In this subsection, we prove a series of propositions and lemmas which lead to a key result that will be
-used in the self-testing proof.
+In this subsection, we prove a series of propositions and lemmas 
+derived from the fact that some strategy can approximate the ideal correlation of the extended weighted CHSH test,
+which lead to a key result that will be
+used in the self-testing proof in \cref{sec:self-test}.
 Note that in the following proofs, the observables $M_1$ and $M_2$ are
@@
 Similarly, on Bob's side, we have $N_1 \equiv N(a_1)$ and $N_2 \equiv N(a_2)$.
+For simplicity, in this subsection, we
+use $M_1, M_2$ and $N_1, N_2$.
 \begin{proposition}
@@
 $\pr{ab}{xy} \appd{O(r \ep)} \tpr{ab}{xy}$ for all question 
-pair $(x,y)$ and answer pair $(a,b)$.
+pair $(x,y)$ and associating answer pair $(a,b)$.
 From the correlation, we can observe that
 \begin{align*}
- \bra{\psi} (M_{\nr+1}^0+M_{\nr+1}^1)N_0^0 \ket{\psi} = \frac{2}{d-1} - O(r \ep).
+ &\bra{\psi} (M_{\nr+1}^0+M_{\nr+1}^1)N_0^0 \ket{\psi} \\
+ = &\pr{0,0}{\nr+1,0} + \pr{1,0}{\nr+1,0}\\
+ \geq &\frac{2}{d-1} - O(r \ep).
 \end{align*}
@@
 \begin{align*}
-	\bra{\psi} N_0^0 \ket{\psi} \appd{O(r\ep)} 
- \bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\ep)} \frac{2}{d-1},
+	&\bra{\psi} N_0^0 \ket{\psi} = \pb{0}{0} \appd{O(r\ep)} \frac{2}{d-1}\\
+ &\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} 
+ = \pa{0}{\nr+1} + \pa{1}{\nr+1}
+ \appd{O(r\ep)} \frac{2}{d-1},
 \end{align*}
@@
 
-%Another conclusion we can draw is that $B_\ast^0 = A_\ast^0$ and $B_\ast^\perp = A_\ast^\perp$.
-%We can assume the Schmidt decomposition of $\ket{\psi}$ is
-%\begin{align}
-%	\ket{\psi} = \sum_{i=1}^d \lambda_i \ket{i}\ket{i}.
-%\end{align}
-%If $\supp{A_\ast^0} \neq \supp{B_\ast^0}$, then $B_\ast^0\ket{\psi} \neq A_\ast^0\ket{\psi}$. Since $B_\ast^0$ and $A_\ast^0$ are projectors,
-%By the orthogonality relations, we can also conclude that $A_\ast^\perp = B_\ast^\perp$.
-
-%Maybe we can first conclude that $\spn(A_0^0+A_0^1) = \spn(A_1^0+A_1^1) = \spn(A_\ast^0)$.
 \begin{proposition}
@@
 To prove that $\bS_1$ achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, we need to examine terms of the form
-$\bra{\psi} M_0^0 M_{x}^a N_y^b M_0^0\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0.1$,
+$\bra{\psi} M_0^0 M_{x}^a N_y^b M_0^0\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0,1$,
 which relate to $\bra{\psi} M_x^a N_y^b \ket{\psi}$ as follows,
@@
 	   \bra{\psi} M_{x}^aN_y^b \ket{\psi} 
-	= &\bra{\psi}(M_0^0 + M_0^2) M_x^a N_y^b (M_0^0 + M_0^2)\ket{\psi} \\
-	= & \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_0^2\ket{\psi}\\
-	&+\bra{\psi}M_0^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^2 M_x^aN_y^b M_0^2\ket{\psi}\\
-	\appd{O(\sr\se)}&  \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_x^\perp\ket{\psi} \\
-	&+\bra{\psi}M_x^\perp M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_x^\perp M_x^aN_y^b M_x^\perp\ket{\psi}\\
-	=&\bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi},
+	&= \bra{\psi}(M_0^0 + M_0^2) M_x^a N_y^b (M_0^0 + M_0^2)\ket{\psi} \\
+	&=  \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_0^2\ket{\psi}\\
+	&\quad\quad+\bra{\psi}M_0^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^2 M_x^aN_y^b M_0^2\ket{\psi}\\
+	&\appd{O(\sr\se)}  \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_x^2\ket{\psi} \\
+	&\quad \quad +\bra{\psi}M_x^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_x^2 M_x^aN_y^b M_x^2\ket{\psi}\\
+	&=\bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi},
 \end{align*}
@@
 $M_x^0 M_x^2 = 0$ for the relevant values of $(x,y,a,b)$.
-This means that if Alice and Bob share state $M_0^0 \ket{\psi}/\norm{M_0^0 \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
+This means that if Alice and Bob share state $M_0^0 \ket{\psi}/\norm{M_0^0 \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$,
 they get conditional probability
@@
 	&\Phi_{A,2} \x \Phi_{B,2} (\ket{\psi_1})  \\
-	= &\frac{1}{16} \sum_{\ua \ub \in\{0,1\}^4}
-	M_{r+6}^{\ua(4)}N_{r+6}^{\ub(4)}M_{r+8}^{\ua(3)}N_{r+8}^{\ub(3)}M_{r+9}^{\ua(2)}N_{r+9}^{\ub(2)}M_{r+11}^{\ua(1)}N_{r+11}^{\ub(1)}
-	\ket{\psi_1} \ket{\ua}_{A''} \ket{\ub}_{B''}
-\end{align*}
-For simplicity we define $M^{\ua} := M_{r+6}^{\ua(4)}M_{r+8}^{\ua(3)}M_{r+9}^{\ua(2)}M_{r+11}^{\ua(1)}$ and
-$N^{\ub} := N_{r+6}^{\ub(4)}N_{r+8}^{\ub(3)}N_{r+9}^{\ub(2)}N_{r+11}^{\ub(1)} $.
+	= &\frac{1}{16} \sum_{\ba, \bb \in\{0,1\}^4}
+	M(f_0)^{a(4)}N(f_0)^{b(4)}M(f_2)^{a(3)}N(f_2)^{b(3)}M(g_0)^{a(2)}N(g_0)^{b(2)}M(g_2)^{a(1)}N(g_2)^{b(1)}
+	\ket{\psi_1} \ket{\ba}_{A''} \ket{\bb}_{B''}
+\end{align*}
+For simplicity we define $M^{\ba} := M(f_0)^{a(4)}M(f_2)^{a(3)}M(g_0)^{a(2)}M(g_2)^{a(1)}$ and
+$N^{\bb} := N(f_0)^{b(4)}N(f_2)^{b(3)}N(g_0)^{b(2)}N(g_2)^{b(1)} $.
 We would like to show that 
@@
 \label{eq:mua_comm}
-M^{\ua} \ket{\psi_1} \appd{O(r\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)
-M^{\ua} \ket{\psi},
-\end{align}
-for all $\ua \in \{0,1\}^4$,
+M^{\ba} \ket{\psi_1} \appd{O(r\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)
+M^{\ba} \ket{\psi},
+\end{align}
+for all $\ba \in \{0,1\}^4$,
 %which implies that 
@@
 which can be justified by \cref{prop:rel_comm}.
-We show how to apply \cref{prop:rel_comm} to commute $M_{r+11}^{\ua(1)}$ through 
-$\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$ and then similar process can be repeated for $M_{r+9}, M_{r+8}$ and $M_{r+6}$,
-\begin{align*}
-	&\quad M_{r+11}^{\ua(1)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \\
-	&\appd{O(r\se)} \frac{1}{2}[ (M_{\nr+1}^0+M_{\nr+1}^1) M_{r+11}^{\ua(1)} -i M_{r+11}^{\ua(1)} M_{\nr+2}N_{\nr+1}] \ket{\psi} \\
-	&\appd{O(r\se)} \frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M_{r+11}^{\ua(1)} - iM_{\nr+2}M_{r+11}^{\ua(1)} N_{\nr+1}] \ket{\psi} \\
-	&\appd{O(r\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M_{r+11}^{\ua(1)} - iM_{\nr+2}M_{r+11}^{\ua(1)} M_{\nr+1}] \ket{\psi} \\
-	&\appd{O(r\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M_{r+11}^{\ua(1)} - iM_{\nr+2}M_{\nr+1}M_{r+11}^{\ua(1)} ] \ket{\psi}.
+We show how to apply \cref{prop:rel_comm} to commute $M(g_2)^{a(1)}$ through 
+$\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$ and then similar process can be repeated for $M(g_0)^{a(2)}, M(f_2)^{a(3)}$ and $M(f_0)^{a(4)}$,
+\begin{align*}
+	&\quad M(g_2)^{a(1)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \\
+	&\appd{O(\sr\se)} \frac{1}{2}[ (M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} -i M(g_2)^{a(1)} M_{\nr+2}N_{\nr+1}] \ket{\psi} \\
+	&\appd{O(\sr\se)} \frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M(g_2)^{a(1)} N_{\nr+1}] \ket{\psi} \\
+	&\appd{O(\sr\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M(g_2)^{a(1)} M_{\nr+1}] \ket{\psi} \\
+	&\appd{O(\sr\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M_{\nr+1}M(g_2)^{a(1)} ] \ket{\psi}.
 \end{align*}
@@
 \begin{align}
-	M^{\ua} N^{\ub} \ket{\psi_1} \appd{O(r\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)M^{\ua}N^{\ub} \ket{\psi}
-\end{align}
-for all $\ua, \ub \in \{0,1\}^4$, which implies that 
-\begin{align*}
-	\Phi_{A,2} \x& \Phi_{B,2}(\ket{\psi_1}) \appd{O(r\se)}\\
+	M^{\ba} N^{\bb} \ket{\psi_1} \appd{O(\sr\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)M^{\ba}N^{\bb} \ket{\psi}
+\end{align}
+for all $\ba, \bb \in \{0,1\}^4$, which implies that 
+\begin{align*}
+	\Phi_{A,2} \x& \Phi_{B,2}(\ket{\psi_1}) \appd{O(\sr\se)}\\
 	 &\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)(\Phi_{A,2}\x\Phi_{B,2} (\ket{\psi}).
@@
 \begin{align}
-	\Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \appd{O(\sd r \se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2},
+	\Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \appd{O(\sd \sr \se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2},
 \end{align} 
@@
 %========================================
-\section{Definition of $\LS(r)$}
-\label{sec:lsg_def}
+\section{The linear system of $\LS(r)$}
+\label{sec:lsg_eq}
 %========================================
 \begin{definition}
-    \label{def:lsg}
-    The linear system game $\LS(r)$ has 
-    variables $x(s)$ for each $s \in S$, and equations:
+    \label{def:lsg_eq}
+    The linear system of $\LS(r)$ has 
+    variables $x(s)$ for each $s \in S \setminus \{J\}$, and equations:
     \begin{itemize}
@@
 
-Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}, which are the carrier spaces
+Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}, which are the carrier spaces
 of the representations given below,

### 2019-08-02 Draft/draft.tex
Changes to section 5 and section 6.1

@@
 %========================================
-Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
+Self-testing is a unique phenomenon of quantum mechanics.
+It is also powerful because only classical interactions are required.
+It has many applications in quantum
 delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
 \cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
-\carl{Two possible papers that you could cite are Mayer Yao 1998 (which originated the idea of self-testing as far as I know, and mentions QKD) and my paper (miller2017, which you've already cited --- indeed it uses the concept of self-testing).
-Also you should check Vazirani-Vidick's 2014 PRL paper to see if it mentions self-testing at all.
-(It was the first to fully prove DI-QKD.)}
-\hfc{checked.}
-
-The case of self-testing $2$-dimensional EPR pair is fully understood.
-The techniques for robustly self-testing one EPR pair is 
+
+The case of self-testing $2$-dimensional EPR pair, which is defined by
+\begin{align*}
+    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
+\end{align*}
+is fully understood.
+The techniques for robustly self-testing $\ket{EPR}$ is 
 first introduced in Ref.~\cite{mckague2012}, then improved in Ref.~\cite{bamps2015}. 
-Ref.~\cite{yang2013} started to think about how to robustly self-testing large dimensional maxially entangled states.
-Its ideas are realized later in Ref.~\cite{coladan2017all}, which proved that all pure bipartite entangled state 
+Ref.~\cite{yang2013} proved an generalized swap-isometry
+that can be used to robustly self-test large dimensional maxially entangled states.
+Its ideas are realized later in Ref.~\cite{coladan2017all}, 
+which proved that all pure bipartite entangled state 
 can be self-tested.
-One can also self-test many copies of the $2$-dimensional EPR
-pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
-The most efficient way uses $O(\log n)$ bits question and
-answers to self-test $n$ copies of $2$-dimensional EPR
-pair \cite{lowdegree}.
-\carl{I believe the first to prove robust self-testing of a single EPR pair was McKague-Yang-Scarani 2012.}
-\hfc{Got it.}
-Self-testing general $d$-dimensional EPR pairs is a harder task.
-Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
-by constructing an explicit correlation of size $\Theta(d^2)$ that can be used for self-testing,
-which is the only result about the general $d$-dimensional case so far.
-However, proving the robustness of the correlation remains an open problem. 
+The authors constructed a family of correlations such
+that each partially or maximally entangled state of any local dimension has
+a self-testing correlation in this family.
+% One can also self-test many copies of the $2$-dimensional EPR
+% pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
+% The most efficient way uses $O(\log n)$ bits question and
+% answers to self-test $n$ copies of $2$-dimensional EPR
+% pair \cite{lowdegree}.
+% Self-testing general $d$-dimensional EPR pairs is a harder task.
+% Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
+To generate a correlation in the family, Alice and Bob
+have constant number of measurement settings but each 
+measurement setting has the same number of outcomes as
+the local dimension of the entangled state to be self-tested. 
+In other words, their correlation is of size $\Theta(d^2)$,
+where $d$ is the local dimension of the entangled state.
+This is the only result about self-testing the general $d$-dimensional entangled state so far.
+However, proving the robustness of the family of correlations remains an open problem. 
 Without robustness, we cannot infer anything about a quantum strategy if
@@
 A natural question to ask is whether maximally entangled states with large local dimension
-can be self-tested with constant-sized correlations. 
+can be robustly self-tested with constant-sized correlations. 
 In this paper, we give an affirmative answer to this question by proving the following theorem.
@@
 	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
-	the maximally entangled state of local dimension $4d-4$ can be robustly self-tested 
+	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
 	with constant-sized question and answer alphabets.
@@
 
-The set $D$ is, \carl{
-specifically, the set of all 
-odd prime numbers whose smallest primitive root is either $2$, $3$,
-or $5$}.  It has been shown that \carl{this set} has infinitely many elements \cite{murty1988}.
-To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r^2)$ for each $d \in D$ whose primitive
-root is $r$. This correlation is denoted by $\fC(d,r)$.
+The set $D$ is, specifically, the set of all 
+odd prime numbers whose smallest primitive root is either $2$, $3$, or $5$.  
+It has been shown that this set has infinitely many elements \cite{murty1988}.
+To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r)$ 
+for each $d \in D$ whose smallest primitive root is $r$.
+This correlation is denoted by $\fC(d,r)$.
 Note that although the size of $\fC(d,r)$ does not depend on $d$, the entries of $\fC(d,r)$ do.
@@
 \carl{The paper \cite{bamps2015} says that the earlier paper \cite{yang2013} has ``flaws.'' Check what those flaws are, and make sure that they won't put a shadow on anything that you're discussing when you cite \cite{yang2013}.}
-
-In order to accomplish our goal, we first design a linear system game to enforce the 
-relation $UOU\ct = O^r$, which is a generalization of a relation in Ref.~\cite{slofstra2017}.
+\hfc{The flaws are in the self-testing proof, not in the 
+proof about the generalized isometry.}
+
+The correlation $\fC(d,r)$ contains the ideal correlation of a specially-designed binary linear system game.
+In a general linear system game, Alice is given a random equation 
+from a linear system and she
+should give an assignment of the equation.
+Bob is asked to assign a value to a random variable of that equation.
+They win the game if Alice's assignment satisfies the equation and Bob's
+assignment to the variable matches Alice's assignment.
+A widely-used and thoroughly-studied example of a linear system game is
+the Magic Square game \cite{magic_square}.
+In this game, the linear system is
+\begin{align*}
+    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
+    x_7 + x_8 + x_9 = 0 \\
+    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
+    x_3 + x_6 + x_9 = 0.
+\end{align*}
+Using two copies of the maximally entangled state
+\begin{align*}
+    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
+\end{align*}
+the Magic square game can be won
+with certainty.
+It has been shown that if a strategy that can win this game almost perfectly, the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
+so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
+The key observation that leads to the self-testing proof is that 
+a winning strategy must contain observables $X$ and $Z$ that 
+satisfy the anti-commutation relation 
+\begin{align*}
+    X Z = - Z X.
+\end{align*}
+Intuitively, we can think of the Magic Square game as a way to enforce the
+anti-commutation relation.
+
+Our linear system game is designed to enforce the relation 
+\begin{align*}
+    U O U\ct = O^r,
+\end{align*}
+for some integer $r$,
+in the sense that the winning strategy contains binary observables
+$M_1, M_2, M_3, M_4$ on Alice's side and 
+$N_1, N_2, N_3, N_4$ on Bob's side such that 
+\begin{align*}
+    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2.
+\end{align*}
+This relation implies the eigenvalue of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root
+is $r$. It also implies that $U$ is a permutation of the eigenbasis of $O$.
+Winning this linear system game implies that Alice and Bob share a state
+$\ket{\psi}$ such that
+\begin{align*}
+    O \x O \ket{\psi} = \ket{\psi}, && 
+    U \x U \ket{\psi} = \ket{\psi}.
+\end{align*}
+These two relations are important for the self-testing argument
+because
+the relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
+is spanned by tensor products of states in the eigenbasis of $O$;
+and $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
+under the permutation induced by $U$. 
+At this point, the eigenvalues of $O$ are unknown, so
+further restricting the eigenvalues of $O$ requires another test, 
+which will be introduced later.
+
+The special feature of our linear system game is that the sizes
+of the question sets for Alice and Bob are of order $\Theta(r)$,
+and the answer sets are of size $\Theta(1)$.
+Restricting $r \leq 5$ in our theorem implies that our linear system 
+game only uses constant-sized question sets and constant-sized answer sets.
 \carl{A reader may get lost at the last sentence -- you're jumping into the material too quickly without enough explanation.}
-The number of variables and the number of equations of the linear system game depend linearly on $r$,
-which makes our correlation of size $\Theta(r^2)$.
-Unlike previous self-testing proofs, which try to enforce the anti-commutation relation
-$XZ = \omega_d^{-1} ZX$ between Pauli operators of dimension $d \geq 2$, 
-our approach is more succinct in terms of the size of the correlation but at a cost that
-it only works for odd prime $d$.
-The reason why we focus on this relation is that if we can certify that $O$ has one eigenvalue $\omega_d$
-for some $d$ with primitive $r$,
-then it guarantees that $O$ has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$ and $U$ only
-permutes the eigenvectors of $O$ in certain way.
-After knowing the eigenvalues of $O$, we can use infer the structure of the shared state $\ket{\psi}$
-based on the two relation of $\ket{\psi}$ imposed by the linear system game --
-$U_A \x U_B \ket{\psi} = \ket{\psi}$ and $O_A \x O_B \ket{\psi} = \ket{\psi}$.
-The two relations imply that $\ket{\psi}$ is spanned by eigenvectors of $O$ and its
-Schmidt coefficient follows some pattern that is invariant under the permutation by $U$.
-At this point, we can use the generalized swap isometry \cite{yang2013} to extract a copy of the 
-$(d-1)$-dimensional maximally entangled state. Note that our robust self-testing proof 
-follows a different line of arguments from what was originally
-proposed in Ref.~\cite{yang2013}.
-Our self-testing proof actually certifies $\ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}$. 
-The self-testing of $\ket{\EPR{2}}^{\x 2}$ follows a known result \cite{wu2016}.
-
-The remaining question is how to certify a particular eigenvalue of $O$. Before going to the answer,
-we remark that 
-the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
-whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
-linear system games are binary. 
-The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
-We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
-The fact that Alice and Bob only have binary observables make it easier for us 
-to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
+\hfc{Rewritten.}
+% The number of variables and the number of equations of the linear system game depend linearly on $r$,
+% which makes our correlation of size $\Theta(r^2)$.
+% Unlike previous self-testing proofs, which try to enforce the anti-commutation relation
+% $XZ = \omega_d^{-1} ZX$ between Pauli operators of dimension $d \geq 2$, 
+% our approach is more succinct in terms of the size of the correlation but at a cost that
+% it only works for odd prime $d$.
+% The reason why we focus on this relation is that if we can certify that $O$ has one eigenvalue $\omega_d$
+% for some $d$ with primitive $r$,
+% then it guarantees that $O$ has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$ and $U$ only
+% permutes the eigenvectors of $O$ in certain way.
+% After knowing the eigenvalues of $O$, we can use infer the structure of the shared state $\ket{\psi}$
+% based on the two relation of $\ket{\psi}$ imposed by the linear system game --
+% $U_A \x U_B \ket{\psi} = \ket{\psi}$ and $O_A \x O_B \ket{\psi} = \ket{\psi}$.
+% The two relations imply that $\ket{\psi}$ is spanned by eigenvectors of $O$ and its
+% Schmidt coefficient follows some pattern that is invariant under the permutation by $U$.
+% At this point, we can use the generalized swap isometry \cite{yang2013} to extract a copy of the 
+% $(d-1)$-dimensional maximally entangled state. Note that our robust self-testing proof 
+% follows a different line of arguments from what was originally
+% proposed in Ref.~\cite{yang2013}.
+
+The remaining question is how to certify a particular eigenvalue of $O$, so we
+design a nonlocal test called the extended weighted CHSH test.
+% Before going to the answer,
+% we remark that 
+% the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
+% whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
+% linear system games are binary. 
+% The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
+% We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
+% The fact that Alice and Bob only have binary observables make it easier for us 
+% to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
 The difference between a nonlocal game and a nonlocal test will be discussed later.
-The core idea of the extended weighted CHSH test is to certify that Alice and Bob's observables and state 
-for the linear system game can also be used to violate the weighted CHSH inequality \cite{acin2012} maximally.
-We find that the maximal violation of the weighted CHSH inequality can certify the eigenvalues of the product
-of Bob's observables. 
-At this point, we fix a prime $d$ by picking the weight in the weighted CHSH inequality and 
-use the extended weighted CHSH test to certify that
-$O$ has eigenvalue $\omega_d$.
+It is designed based on the $\alpha$-weighted CHSH inequality, which is defined by
+\begin{align*}
+    \I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
+\end{align*}
+where $M_x$ and $N_y$ for $x,y \in \{1, 2\}$ are some binary observables.
+Define $\mu = \arctan(1/\alpha)$,
+\begin{align*}
+    \pauliz = \ketbra{0}{0} - \ketbra{1}{1} && \paulix = \ketbra{0}{1} + \ketbra{1}{0},
+\end{align*}
+which are the Pauli-Z and Pauli-X operators.
+This inequality is maximally violated when the shared state is $\ket{EPR}$,
+Alice's binary observables are
+\begin{align*}
+    M_1 = \pauliz && M_2 = \paulix,
+\end{align*}
+and Bob's binary observables are
+\begin{align*}
+    N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
+\end{align*}
+We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
+state $\ket{\psi}$ and the observables $M_1, M_2$ and $N_1, N_2$.
+Then we noticed that 
+\begin{align*}
+    N_1N_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
+\end{align*}
+has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.
+Hence, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
+for some odd prime $d$ whose primitive root is $r$,
+and ask Alice and Bob
+to reuse the observables $M_1, M_2$ and $N_1, N_2$，then we can certify that
+the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
+Combining this observation with the fact that $O$ satisfy the relation $UOU\ct = O^r$,
+we can conclude that all the eigenvalues of $O$ are $\{ e^{ij 2\pi /d} \}_{j=1}^{d-1}$,
+and the eigenspaces of all the eigenvalues have the same cardinality.
+At this point, we has the explicit structure of $O$, so we 
+can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
+to prove the correlation $\fC(r, d)$ can robustly self-test 
+a maximally entangled state of dimension $4(d-1)$.
+
 \carl{This paragraph (also) will need more context.}
+\hfc{Rewritten.}
+
+Our contributions are four-fold.
+\begin{enumerate}
+    \item We identify the constant-sized question and answer sets that can be used to robustly self-test
+    maximally entangled states with unbounded dimensions. Before our work, the most efficient way
+    was to use $O(\log d)$-sized question and answer sets to robustly self-test
+    the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
+    \item Our self-testing proof demonstrate a new way to apply the generalized swap-isometry
+    proposed in Ref.~\cite{yang2013} to robustly self-test a maximally entangled state of large lcoal
+    dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.
+    We believe it can be applied to prove the family of correlations proposed in Ref.~\cite{coladan2017all}
+    are also robust.
+    \item We demonstrate how to enforce relations between operators of large but fixed dimension in a 
+    binary linear system game. Before our work, only the anti-commutation relation between $2$-dimensional
+    Pauli operators can be enforced in a binary linear system game.
+    \item Our result gives us deeper understanding of the set of quantum correlations.
+    In previous works that proved the non-closeness of the set of quantum correlations
+    \cite{slofstra2017}, 
+    lower bounds of the entanglement required to achieve certain correlations are identified.
+    Our work discovers a large family of correlations where we know exactly the amount of entanglement
+    required to achieve each of the correlations in this family. 
+\end{enumerate}
 
@@
  \begin{align*}
-     \calX = \{I_i\}_{i=1}^m && \calY = \{1 \dots n\} \\
-     \calA_{I_i} = \Z_2^{|I_i|} && \calB = \Z_2,
+     \calX = \{I_i\}_{i=1}^m && &\calY = \{1 \dots n\} \\
+     \calA_{I_i} = (\Z_2)^{I_i} && &\calB = \Z_2,
  \end{align*}
@@
 \end{definition}
-\hfc{I think the order of the variables given to Alice doesn't matter, because
-the linear system is binary.}
+
 A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
@@
 \begin{align*}
-    \calA^{\LS} = \Z_2^{3} && \calB^{\LS} = \Z_2,
+    \calA^{\LS} = (\Z_2)^{I_i} && \calB^{\LS} = \Z_2,
 \end{align*}
@@
 where $N(r) := 157r + 685$ is the total number of valid question pairs.
-We define $X_i := \{ \ba \in \Z_2^3: \sum_{j=1}^3 a(j) = c(i) \}$, which is the set of all the valid answers of equation $i$.
+We define $X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \}$, which is the set of all the valid answers of equation $i$.
 Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
@@
 \begin{align*}
-    V^{\LS}(\ba, b, I_i, x(s)) = 
+    V^{\LS}_{I_i, x(s)}(\ba, b) = 
     \begin{cases}
@@
 \end{definition}
-\hfc{Rewritten.}
+\carl{This definition does not seem consistent.  You are using $a$ both as a function on $\{ 1, 2, 3 \}$ and as a function on $S$.}
+\hfc{Fixed.}
 The construction of $\LS(r)$ proves the following theorem.
@@
 }
-\carl{This is a meandering paragraph.  Rewrite.}
-\hfc{How about now?}
 
@@
         &\calX^{\EXT} = \calY^{\EXT} = \{0, 1, 2, \nr+1, \nr+2\}, \\
-        &\calA_x^{\EXT} = \calB_y^{\EXT} =
+        &\calA_z^{\EXT} = \calB_z^{\EXT} =
         \begin{cases}
-            \{0,2\} &\text{ if } x = y = 0, \\
-            \{0,1\} &\text{ if } x,y \in \{1, 2\} \\
-            \{0,1,2\} &\text{ if } x,y \in \{\nr+1, \nr+2\}. 
+            \{0,2\} &\text{ if } z = 0, \\
+            \{0,1\} &\text{ if } z \in \{1, 2\} \\
+            \{0,1,2\} &\text{ if } z \in \{\nr+1, \nr+2\}. 
         \end{cases}
@@
 \end{align*}
-\carl{The indirect way that you start to use $\left| j \right>$ in your explanation here is confusing.
-If you're going to introduce a new mathematical object, then define it explicitly at the outset.}
-\hfc{Fixed.}
 
@@
 \begin{definition}[The full test]
+\label{def:full_test}
+Define 
+\begin{align*}
+    \calX^{\EXT'} = \calY^{\EXT'} = \{0, x(a_1), x(a_2), \nr+1, \nr+2\}.
+\end{align*}
 The question sets of the full test are
@@
 \end{align*}
-where $\calX^{\EXT'}$ is obtained from $\calX^{\EXT}$ by replacing 
-$1$ by $x(a_1)$ and $2$ by $x(a_2)$, and similarly for $\calY^{\EXT'}$.
+Define answer sets $\calA_x^{\EXT'}$ for each $x \in \calX^{\EXT'}$
+by setting 
+\begin{align*}
+    &\calA_{x(a_1)}^{\EXT'} =\calA_{1}^{\EXT} \\
+    &\calA_{x(a_2)}^{\EXT'} =\calA_{2}^{\EXT} \\
+    &\calA_{x}^{\EXT'} = \calA_{x}^{\EXT} 
+    \quad \text{ for } x \neq x(a_1), x(a_2)
+\end{align*}
+The answer sets $\calB_y^{\EXT'}$ are defined analogously.
 The answer sets of the full test are
@@
 \end{align*}
-The answer sets $\calA_x^{\EXT'}$ are obtained from $\calA_x^{\EXT}$
-by setting 
-\begin{align*}
-    \calA_{x(a_1)}^{\EXT'} =\calA_{1}^{\EXT} &&
-    \calA_{x(a_2)}^{\EXT'} =\calA_{2}^{\EXT},
-\end{align*}
-and $\calA_x^{\EXT'} = \calA_x^{\EXT}$ for the other $x \in \calX^{\EXT}$.
-Bob's answer sets $\calB_y^{\EXT'}$ are obtained from $\calB_y^{\EXT}$
-analogously.
 Define $N$ to be the total number of question pairs with nonzero probability 
@@
 \end{definition}
+Note that $\calX^{\EXT'}$ is obtained from $\calX^{\EXT}$ by replacing 
+$1$ by $x(a_1)$ and $2$ by $x(a_2)$, and similarly for $\calY^{\EXT'}$.
+The answer sets $\calA_x^{\EXT'}$ are constructed from $\calA_x^{\EXT}$
+in a similar way.
 
@@
 for $j= 1,2$.
-It can be checked that 
+They can reproduce the ideal correlation because
 \begin{align*}
@@
 and similarly on Bob's side.
+In other words, the observables $\tM(a_j)$ and $\tN(a_j)$ are 
+measuring the same state on the subspace $V$ as $\tP_j$ and $\tQ_j$
+for $j = 1,2$.
+
 Alice's projectors for the other questions of $\calX^{\EXT'}$ are
@@
 \end{definition}
-In our full test, the probability distribution over all the question pairs $(x,y)$ is uniform.
+In our full test, the probability distribution over all the question pairs $(x,y)$ is uniform.  \carl{[You need to address that in the definition itself (otherwise it's not a complete definition).]}
+\hfc{I think I did define the question distribution in \cref{def:full_test}. }
 The number of all the possible question pairs is 
@@
 %------------------------------------------------------------------------------------------
-\subsection{Implication of winning $\LS(r)$}
+\subsection{Implication of approximately winning $\LS(r)$}
 \label{sec:imp_lct}
 %------------------------------------------------------------------------------------------
+\carl{[Regarding the title of this subsection: Technically, you are only assuming that the correlation approximately wins $LS ( r )$.]}
+\hfc{Fixed.}
+
 In the first half of this subsection, we use $(I_i,x(s))$ to denote the question pair so that Alice gets equation label $I_i$ and Bob gets a variable label $x(s)$ for some $s \in S$. 
+\carl{[This last sentence is kind of vague.  If you're recalling notation from a previous subsection, you can just say that.]}
 For simplicity, we denote 
@@
 	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	Then there exist binary observables $\{ M(s) \}_{s \in S} $, such that
+	\hf{Define $M(s) := M_i(s)$ where 
+	$i$ is the smallest among all $i$'s
+	such that $x(s) \in I_i$.}
+	Then, 
 	\begin{align}
@@
 \end{proposition}
+\carl{[This proposition doesn't seem well-phrased --- it doesn't seem useful  to simply claim the existence of binary observables $M ( s )$ without specifying how they are related to the strategy $S$.]}
+\hfc{How about now?}
+
 \begin{proof}
@@
 \end{align*}
+\carl{[The previous sentence \& equation do not make sense to me.]}
 Since $M_i(s)$ and $N(s)$ are binary observables, we know that
@@
 
-To make the following derivations easier to follow, we define the meaning
-for some operators to approximately satisfy some group relation.
+To make the following derivations easier, we introduce the following terminology.
 \begin{definition}
@@
     be two sequences of $S$.
-    Define a relation $r$, which is $\Pi_{i=1}^n s_i = \Pi_{j=1}^m s'_j$.
+    Define a relation $r$, \hf{whose equation form} is $\Pi_{i=1}^n s_i = \Pi_{j=1}^m s'_j$.
     We say operators $\{M(s) : s \in S\}$ $\ep$-approximately satisfy the relation
@@
     \end{align*}
+\carl{[Technically, the word ``relation'' refers to an element of the free group, not to an equation between elements of the free group, so you need to write this in a way that accounts for that.
+It's a minor issue but worth addressing.]}
+\hfc{How about this way?}
 \end{definition}
@@
 \end{proposition}
-Recall that the group $\Pg_1$ is embedded in $\Gamma$.
+Recall that the group $\Pg_1$ (\cref{def:g1}) is embedded in $\Gamma$.
+\carl{[You need to tell the reader where they can find a full definition of $\Pg_1$.
+(Always do so when you reintroduce a mathematical object.)]}
 Following the embedding procedure, we can prove the next proposition.
@@
 \end{proposition}
+
+\carl{[I don't think it's helpful
+to the reader to phrase this result in terms of $\Pg_1$, given that you never wrote out $\Pg_1$ in the main text.
+I think you should write this in such a way that a reader who hasn't read the appendix can follow what you're doing.
+(One possibility is to just prove the relations that you need, step by step, and then just add comments referring to how what you are doing parallels your proofs in the appendix.]}
+\hfc{We need all the relations from $\Pg_1$ (\cref{def:g1}) to recover relations of $\Pg_0$ (\cref{def:g0})
+so it is not possible to write out each one of them. 
+What I am doing is proving one of them and comment that the rest of them require the same argument.
+On the other hand, I don't think it is important for the reader to know the relations of $\Pg_1$
+or $\Pg_0$. The only relation that will feature in the self-test proof is the relation $UOU\ct = O^r$.}
+
 \begin{proof}

### 2019-08-12 Draft/draft.tex
changes to section 3

@@
 for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
-Since the steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed in the proofs of Proposition~$33$, Lemma~$29$ and
-Proposition $27$ of Ref.~\cite{slofstra2017}, 
-we defer the formal statements of the embedding procedure till \cref{sec:embedding},
-but sketch this procedure in \cref{sec:embed_idea}. 
-In \cref{sec:gamma_def}, we define $\Gamma$ and introduce how to
-construct $\LS(r)$ from $\Gamma$.
-We also highlight a few operators from a finite-dimensional representation of $\Gamma$.
+The steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed 
+in the proofs of Proposition~$33$, Lemma~$29$ and Proposition $27$ of Ref.~\cite{slofstra2017}, 
+so the group $\Pg$ (\cref{eq:pgroup}) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}),
+and we obtain a chain of embeddings:
+\begin{align}
+\Pg \hookrightarrow \Pg_0 \hookrightarrow \Pg_1 \hookrightarrow \Gamma.
+\end{align}
+
+This section is structured as follows.
+In \cref{sec:g0}, we define the group $\Pg_0$ and prove that $\Pg$ is embedded in $\Pg_0$.
+In \cref{sec:g1}, we define the group $\Pg_1$ and prove that $\Pg_0$ is embedded in $\Pg_1$.
+\Cref{sec:gamma} contains the definition of the group $\Gamma$ and the proof that $\Pg_1$
+is embedded in $\Gamma$.
+The purposes of introducing each intermediate
+group are explained along the definition.
+Note that, we defer the full definitions of the representations of $\Pg_0$, $\Pg_1$ and $\Gamma$
+until \cref{sec:rep_gamma}. 
+Instead, We only highlight a few operators from a finite-dimensional representation of $\Gamma$.
 The representation will be used later to build the ideal strategy.
+In \cref{sec:gamma_def}, we construct $\LS(r)$ from $\Gamma$ and give the 
+formal definition of $\LS( r )$.
 
 %----------------------------------------
-\subsection{A sketch of the procedure
-for constructing $\LS ( r )$}
-\label{sec:embed_idea}
+\subsection{The group $\Pg_0$}
+\label{sec:g0}
 %----------------------------------------
-The group $\Pg$ (\cref{eq:pgroup}) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}), which is the
-solution group of $\LS ( r )$.  
-Thus we obtain a chain of embeddings:
-\begin{align}
-\Pg \hookrightarrow \Pg_0 \hookrightarrow \Pg_1 \hookrightarrow
-\Gamma.
-\end{align}
-The purposes of introducing each intermediate
-group are explained below.
-
-The group $\Pg_0 := \ip{S_0:R_0}$ is a 
-conjugacy group, which is defined in \cref{def:spe_conj_grp}. 
-The generators in $S_0$ are $a_i$ for $i=1 \dots r+5$.
+
+The group $\Pg_0$ is a conjugacy group (\cref{def:spe_conj_grp}), and is defined below.
 The purpose of this step is to embed $\Pg$ into a group where all the
@@
 a homomorphism from $\Pg_0$ to a solution group can be easier to find.
-The special generators of $\Pg_0$ are $a_1, a_2, a_3$ and $a_4$ because the product $a_1a_2$ behaves similarly as $o$
-and the product $a_3a_4$ behaves similarly as $u$.
-Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$ (see \cref{prop:g0}), so
-a homomorphism: $\Pg \rightarrow\Pg_0$  that maps $o$ to $a_1a_2$ and $u$ to $a_3a_4$ is an embedding of $\Pg$ into $\Pg_0$
-by Proposition $33$ of Ref.~\cite{slofstra2017}.
-To better characterize the conjugacy relations in $R_0$, we introduce $C(r)$ defined in \cref{eq:cr}
-of tuples $(i,j,k)$ such that $(i,j,k) \in C(r)$ if and only if $a_ia_ja_i = a_k$ is in $R_0$.
-
-Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$, which is a nice conjugacy group defined in \cref{def:nice_conj_grp}.
-The special property of $R_1$ is that every relation in $R_0$ can be recovered from $R_1$.
-Ensuring that every conjugacy relation is associating two commuting operators is the purpose of introducing $\Pg_1$. \carl{I think a reader would find that last statement unclear.}
-\hfc{Maybe we just remove it?}
-It makes the construction of a finite-dimension representation of $\Gamma$ from
+\begin{definition}	
+\label{def:g0}
+	Let the set $S_0$ be 
+	\begin{align*}
+		S_0 = \{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5,
+	\end{align*}
+	and the set $R_0$ be the union of 
+	\begin{align*}
+	&R_{base} = \{s^2 = e | s \in S\},\\
+	&R_{u} = \{ u_3 = u_2o_1u_2 \quad u_4 = u_2o_2u_2 \quad 
+	u_5 = u_1u_3u_1 \quad o_2 = u_1u_4u_1 \quad u_5 = o_1 o_r o_1\},
+	\end{align*}
+	and 
+	\begin{align*}
+	R_o = 
+	\begin{cases} 
+	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1 \quad o_{2+2j} = o_2o_{1+2j}o_2\} \quad \text{ if $r$ is even },\\
+	\{o_3 = o_2o_1o_2\} \cup \bigcup_{j=1}^{(r-3)/2}\{
+	 o_{2+2j} =o_1o_{1+2j}o_1 \quad o_{3+2j} = o_2o_{2j+2}o_2 \}\quad\text{ if $r$ is odd }.
+	\end{cases}
+	\end{align*}
+	The group $\Pg_0$ is a group with presentation $\ip{R_0:S_0}$.
+\end{definition}
+The special generators of $\Pg_0$ are $o_1, o_2, u_1$ and $u_2$ because the product $o_1o_2$ behaves similarly as $o$
+and the product $u_1u_2$ behaves similarly as $u$.
+Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$,
+as proved in the next proposition.
+\begin{proposition}
+    \label{prop:g0}
+	The group $\Pg$ is embedded in $\Pg_0$.
+	Furthermore, the generators of $\Pg_0$ satisfy the relation 
+	\begin{align}
+	    \label{eq:uo_comm}
+	    &(u_1u_2) o_2 (u_2u_1) = o_2 \\ 
+	    \label{eq:uo_rel}
+		&(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
+	\end{align}
+	for any $ j \in \N$.
+\end{proposition}
+\begin{proof}
+    We prove \cref{eq:uo_comm} first. It is easy to see that
+    \begin{align}
+        u_1 (u_2o_2u_2) u_1 = u_1u_4u_1 =o_2.
+    \end{align}
+
+    Next, we prove that $\Pg$ is embedded in $\Pg_0$ by prove the $j = 1$ case of \cref{eq:uo_rel}.
+    The proof of Proposition $33$ of Ref.~\cite{slofstra2017} gives the recipe about
+    how to construct a finite-dimensional representation of $\Pg_0$ from a 
+    finite-dimensional representation of $\Pg$, so Lemma $15$ of Ref.~\cite{slofstra2017}
+    proves that a homomorphism $\phi: \Pg \rightarrow \Pg_0$ such that $\phi(u) = u_1u_2$ and 
+    $\phi(o) = o_1o_2$ is injective.
+
+	We prove \cref{eq:uo_rel} by induction.
+	The base case follows the direct calculation given below
+	\begin{align*} 
+		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
+	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
+	=& u_5 o_2\\
+	=& o_1o_ro_1 o_2.
+	\end{align*}
+	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above, which 
+	proves the $j=1$ case.
+
+	Now assume the statement is true for $j = n$, then for $j = n+1$
+	\begin{align*}
+		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
+		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
+		 =& (o_1o_2)^{r^{n+1}},
+	\end{align*}
+	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$, and
+	from the second line to the third line, we applied the $j=1$ case. Hence, the statement is true.
+\end{proof}
+Note that our representation $\Psi_0$ of $\Pg_0$ is different from the representation
+constructed in the proof of Proposition $33$ of Ref.~\cite{slofstra2017}.
+We give the formal definition of $\Psi_0$ (\cref{def:rep_g0}) in \cref{sec:rep_gamma}.
+
+To better characterize all the conjugacy
+relations of $\Pg_0$ and simplify the form of $\Pg_0$, 
+we relabel $u_i$ and $o_i$'s as $a_i$'s such that
+\begin{align}
+	a_j := 
+	\begin{cases}
+	 o_j \text{ for } j = 1,2 \\
+	 u_{j-2} \text{ for } j = 3\dots 7 \\
+	 o_{j-5} \text{ for } j = 8 \dots r+5.
+	\end{cases}
+\end{align}
+Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
+\begin{align}
+\label{eq:cr}
+	C(r) = \{ (i,j,k) |  (a_ia_ja_i = a_k) \in R_0 \}.
+\end{align}
+The size of $C(r)$ is $r+3$. 
+Hence, another presentation of the group $\Pg_0$ is
+\begin{align*}
+    \Pg_0 = \ip{ \{a_i\}_{i=1}^{r+5} : \{a_i^2 =e \}_{i=1}^{r+5} \cup \{ a_ia_ja_i = a_k \vert (i,j,k) \in C(r)\}},
+\end{align*}
+and we will construct $\Pg_1$ based on this presentation of $\Pg_0$.
+
+%---------------------------------
+\subsection{The group $\Pg_1$}
+\label{sec:g1}
+%---------------------------------
+The group $\Pg_1$ is a nice conjugacy group (\cref{def:nice_conj_grp}).
+We embed $\Pg_0$ into $\Pg_1$ to
+make the construction of a finite-dimension representation of $\Gamma$ from
 a finite-dimension representation of $\Pg_1$ easier.
-Specifically, in this step, we introduce generators $a_i, b_i, c_i, d_i \in S_1$
-for each generator $a_i \in S_0$.
-There is also a special generator $f_0 \in S_1$ such that
-\begin{align*}
-    a_i = b_ic_i = f_0d_i. 
-\end{align*}
-The relation $a_i = b_ic_i$ guarantees that $b_i$ commutes
-with $c_i$.
-The generators $b_i$ and $c_i$ are also related by a conjugacy relation
-\begin{align*}
-    c_i = f_0 b_i f_0. 
-\end{align*}
-For each $(i,j,k) \in C(r)$, 
-$S_1$ contains an auxiliary generator $h_{jk}$, and
-$R_1$ 
-contains a conjugacy relation 
-\begin{align*}
-    d_ib_jd_i = c_k,
-\end{align*}
-and a linear relation
-\begin{align*}
-    h_{jk}b_jc_k = e.
-\end{align*}
-The introduction of $h_{jk}$ helps us to deduce that 
+\begin{definition}
+\label{def:g1}
+Define the set $S_1$ to be
+\begin{align*}
+	S_1 = \{a_i, b_i, c_i, d_i\}_{i=1}^{r+5} \cup \{ f_0 \} \cup \{h_{jk}\}_{(i,j,k) \in C(r)},
+\end{align*}
+and the set $R_1$ to be
+\begin{align*}
+	R_1 = &\{ s^2 = e \vert s \in S_1\}\\ 
+	&\cup 
+	\{a_i = b_ic_i = f_0d_i, \quad f_0b_if_0 =c_i\}_{i= 1}^{r+5} \\ 
+	&\cup
+	\{h_{jk}b_j c_k = e, \quad d_ib_jd_i = c_k\}_{(i,j,k) \in C(r)}.
+\end{align*}
+The group $\Pg_1$ is a group with the presentation $\ip{S_1 : R_1}$.
+\end{definition}
+Note that the group $\Pg_1$ is the same as the group $K$ used in the proof of Lemma $29$ of Ref.~\cite{slofstra2017}.
+For each $1 \leq i \leq r+5$, the relation $a_i = b_ic_i$ guarantees that $b_i$ commutes with $c_i$.
+For each $(i,j,k) \in C(r)$, the linear relation $h_{jk} b_j c_k = e$ guarantees that
 $b_j$ commutes with $c_k$.
-Hence, every conjugacy relation in $R_1$ is either of the form
-$f_0b_if_0 = c_i$ for $1 \leq i \leq r+5$, or
-$d_ib_jd_i = c_k$ for $(i,j,k) \in C(r)$.
-From the conjugacy relations in $R_1$, it can be proven that
-\begin{align*}
-    d_ic_jd_i = b_k \text{ for each } (i,j,k) \in C(r).
-\end{align*}
-Then we can expand $a_ia_ja_i$ by first substituting in $a_i = f_0 d_i$ and $a_j = b_jc_j$ and then repeatedly substituting in the conjugacy relations in $R_1$ and 
-the conjugacy relations deduced above, so we can get
-\begin{align*}
-    a_ia_ja_i = f_0 d_i b_jc_j f_0 d_i
+
+The relation between $\Pg_0$ and $\Pg_1$ is summarized in the propositions below, which 
+is a specific case of Lemma $29$ of \cite{slofstra2017}.
+\begin{proposition}
+    \label{prop:g0g1}
+	The group $\Pg_0$ is embedded in $\Pg_1$. 
+\end{proposition}
+\begin{proof}
+    We prove this proposition by showing that generators $a_i$'s in $S_1$
+    satisfy the relation $a_i a_j a_i = a_k$ for all $(i,j,k) \in C(r)$.
+    This means the homomorphism $\phi: \Pg_0 \rightarrow \Pg_1$ that maps $a_i$
+    to $a_i$ is homomorphism from $\Pg_0$ to $\Pg_1$.
+
+	We first show that $d_i c_j d_i = b_k$, which is because
+	\begin{align*}
+		d_i c_j d_i = d_i (f_0 b_j f_0) d_i = f_0 (d_i b_j d_i) f_0 = f_0 c_k f_0 = b_k.
+	\end{align*}
+	Then, we can prove that 
+	\begin{align*}
+		a_i a_j a_i = f_0 d_i b_j c_j f_0 d_i 
 		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
 		= (f_0 c_k f_0)(f_0 b_k f_0) 
-		= b_k c_k = a_k.
-\end{align*}
+		= b_k c_k = a_k,
+	\end{align*}
+	where we use the fact that $f_0$ commutes with $d_i$.
 
@@
     \begin{align*}
-    &\Psi_1(a_i) = \1_{\C^2} \x \Psi_0(a_i).
-\end{align*}
-For more details of $\Psi_1$, we refer to \cref{sec:rep_gamma}.
-Hence, a homomorphism $\phi: \Pg_0 \rightarrow \Pg_1$ that 
-maps $a_i$ to $a_i$ is an embedding of $\Pg_0$ into $\Pg_1$
-by Lemma $15$ of Ref.~\cite{slofstra2017}.
-
-In the last step, we can construct $\Gamma:= \ip{S:R}$ with $S_1 \subset S$, in a way such that
-$\Gamma$ only has linear relations, and the linear relations can be combined
+        &\Psi_1(a_i) = \1_{\C^2} \x \Psi_0(a_i)
+    \end{align*}
+    as proved in Lemma $29$ of Ref.~\cite{slofstra2017}.
+    Then, the injectivity of $\phi$ follows Lemma $15$ of Ref.~\cite{slofstra2017}.
+\end{proof}
+The consequence of this proposition is that $\Pg$ can be embedded in $\Pg_1$.
+We give the formal definition of the represention $\Psi_1$ of $\Pg_1$ 
+(\cref{def:rep_g1}) in \cref{sec:rep_gamma}.
+
+%-------------------------------------
+\subsection{The group $\Gamma$}
+\label{sec:gamma}
+%-------------------------------------
+The group $\Gamma$ is a solution group,
+so all the generators of $\Gamma$ are of order-$2$
+and all the relations are linear relations.
+Moreover, the linear relations can be combined
 to recover the conjugacy relations in $R_1$.
-We demonstrate how relation $f_0 b_1 f_0 = c_1$ is embedded in
-$6$ linear relations of $R$ as an example. 
-We introduce auxiliary generators $f_1, f_2$ and $\{p_{1,j}\}_{j=1}^5$ such that they satisfy the linear relations:
-\begin{align*}
-    &f_0 f_1 f_2 = e && b_1 f_2 p_{1,1} = e && p_{1,1} p_{1,2} p_{1,3} = e\\
-	&f_0 p_{1,3} p_{1,4} = e && c_1 p_{1,4} p_{1,5} = e \quad f_1 p_{1,2} p_{1,5} = e.
-\end{align*}
-Then, we expand $f_0b_1f_0$ by substituting in the equations above and
-get
-\begin{align*}
-    f_0b_1f_0 = (f_1f_2)(f_2p_{1,1})(p_{1,3}p_{1,4}) =
-    f_1 p_{1,2}p_{1,4} = p_{1,5}p_{1,4} = c_1.
-\end{align*}
-The other conjugacy relations of $\Pg_1$ are embedded in linear relations analogously.
-
-A representation of $\Gamma$ can also be built from
-a representation $\Psi_1$ of $\Pg_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$
-that was constructed above.
-\carl{At this point the reader may be losing track of the precise meaning of what you're saying.
-Perhaps you could simply say, ``A representation of $\Gamma$ can also be built from the
-representation $\Psi_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$ that was constructed above.''}
-\hfc{Fixed, but I worry about the symbol $\circlearrowleft$.}
-We denote the representation of $\Gamma$ by $\Psi$ and
-it is defined on $\C^2 \x \C^2 \x \calH$ such that
-\begin{align*}
-    \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
-    s \in S_1.
-\end{align*}
-In particular, it means that for each $a_i \in S_0$
-\begin{align*}
-    \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
-\end{align*}
-Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
-maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
-by Lemma $15$ of Ref.~\cite{slofstra2017}.
-
-%---------------------------------------------------
-\subsection{Formal definitions}
-\label{sec:gamma_def}
-%---------------------------------------------------
-We define the solution group of the linear system game $\LS(r)$ first, following the steps described in the previous subsection.
-Then we define the game $\LS(r)$.
 \begin{definition}
@@
 
-From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
-we associate a variable $x(s)$ to each generator $s \in S$.
-Then each linear relation in $R$ can be translated to a linear equation.
-For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
-$f_1g_1m_2 = J$ is translated to the equation
-$x(f_1) + x(g_1) + x(m_2) = 1$. 
-The complete list of the equations is given in \cref{def:lsg_eq}.
-\begin{definition}
-\label{def:lsg}
-The linear system game $\LS(r)$ consists of
-\begin{align*}
-    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
-    & \calY^{\LS} = \{ x(s) : s \in S \},
-\end{align*}
-where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
-and $\mr := 14r + 62$ is the number of equations.  
-\carl{Since you are defining Alice's inputs to be subsets of S, why don't you just define Bob's inputs to be elements of S? Also, again you need to account that
-$J$ is an element of $S$.}
-\hfc{I think setting $\calY = S$ will cause confusion.
-You can see the forms of the equations in \cref{def:lsg_eq}.
-If I set the question set to be $S$, the reader will confuse the 
-linear equations with linear relation.
-I have moved $J$ out of $S$.}
-Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
-The answer sets are 
-\begin{align*}
-    \calA^{\LS} = (\Z_2)^{I_i} && \calB^{\LS} = \Z_2,
-\end{align*}
-because $|I_i| = 3$ for all $i$.
-The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
-\begin{align*}
-    \pi^{\LS}(I_i, x(s)) = 
-    \begin{cases}
-        1/N(r) & \text{ if } s \in I_i \\
-        0 & \text{otherwise,}
-    \end{cases}
-\end{align*}
-where $N(r) := 157r + 685$ is the total number of valid question pairs.
-We define $X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \}$, which is the set of all the valid answers of equation $i$.
-Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
-the score function is
-\begin{align*}
-    V^{\LS}_{I_i, x(s)}(\ba, b) = 
-    \begin{cases}
-        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
-        0 \text{, otherwise}.
-    \end{cases}
-\end{align*}
-\end{definition}
-\carl{This definition does not seem consistent.  You are using $a$ both as a function on $\{ 1, 2, 3 \}$ and as a function on $S$.}
-\hfc{Fixed.}
-The construction of $\LS(r)$ proves the following theorem.
-\begin{theorem}
-	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
-	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
-\end{theorem}
-\hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
-number of equation and variable pairs is $N(r)$ is of order $\Theta(r)$.}
-
-\hf{The ideal strategy of $\LS(r)$ is based on
-the representation $\Psi$ of $\Gamma$ defined in \cref{def:rep_gamma}
-of \cref{sec:rep_gamma}.
-We discuss the ideal strategy in in \cref{sec:tests}.
-Here we only highlight what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$, along
-with the important properties of the representation of these four generators,
-since they are the key generators of $\Gamma$.
-}
-
-The representation $\Psi$ is defined on the Hilbert space
+In the next proposition, we prove that the group $\Pg_1$ is embedded in $\Gamma$.
+\begin{proposition}
+    \label{prop:g1gamma}
+	The group $\Pg_1$ can be embedded in $\Gamma$.
+	The generators of $\Gamma$ also satisfy the relations: 
+	\begin{align}
+	    \label{eq:mg1} &f_0 g_0 f_0 g_0 = J,\\
+	    \label{eq:mg2} &f_2 g_2 f_2 g_2 = J.
+	\end{align}
+\end{proposition}
+\begin{proof}
+    To prove the first claim, we show that the generators
+    $b_i$, $c_i$, $d_i$ satisfy the relations
+    $d_ib_jd_i = c_k$ for each $\bc = (i,j,k) \in C(r)$.
+    \begin{align*}
+        d_ib_jd_i =& (k_{\bc 1} f_2)(f_2 k_{\bc 2})(k_{\bc 4} k_{\bc 5})\\ 
+        =& k_{\bc 1}(k_{\bc 2}k_{\bc 4})k_{\bc 5} \\
+        =& (k_{\bc 1} k_{\bc 3}) k_{\bc 5} \\
+        =& k_{\bc 6} k_{\bc 5} \\
+        =& c_k.
+    \end{align*}
+    The derivation of $f_0 b_i f_0 = c_i$ is similar for $1 \leq i \leq r+5$, so we omit it here.
+    Hence, a map $\phi:\Pg_1 \rightarrow \Gamma$ that maps $s$
+    to $s$ for each $s \in S_1$ is a homomorphism between $Pg_1$ and 
+    $Gamma$. 
+    A representation of $\Gamma$ can be constructed from a representation 
+    of $\Pg_1$ as shown in the proof of Proposition $27$ of Ref.~\cite{slofstra2017},
+    so Lemma $15$ of Ref.~\cite{slofstra2017} proves the homomorphism $\phi$
+    is injective.
+
+    The second claim follows a similar derivation
+    using linear relations in $R_{MS}$, so we omit it here.
+\end{proof}
+Since $\Pg$ is embedded in $\Pg_1$, we can conclude that
+$\Pg$ is embedded in $\Gamma$ as well.
+
+The representation $\Psi$ of $\Gamma$ is defined on the Hilbert space
 $W_2 \x W_2 \x W_{d-1}$,
 where $W_k$ denotes a Hilbert space of
-dimension $k$.  We denote the
+dimension $k$. 
+The formal definition of $\Gamma$ is defined in \cref{def:rep_gamma}
+in \cref{sec:rep_gamma}.
+We denote the
 standard basis of $W_k$ by $\{\ket{x_j}\}_{j=1}^{k}$.
@@
 \end{align*}
-Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
-modulo $d$ implicitly,
+Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, 
+where the subscript $r^j$ is taken modulo $d$ implicitly,
 because another form of $O$ is 
@@
     \label{eq:O}
-    \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}.
+    O = \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}.
 \end{align}
@@
 We denote the identity operator for the subspace $W_k$ by $\1_{W_k}$.
-The representations of $a_1, a_2, a_3$ and
-$a_4$ are 
+The representations of $a_1, a_2, a_3$ and $a_4$ are 
 \begin{align}
@@
 The operators $U$ and $O$ satisfy the relation $UOU\ct = O^r$.
+
+% A representation of $\Gamma$ can also be built from
+% a representation $\Psi_1$ of $\Pg_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$
+% that was constructed above.
+% We denote the representation of $\Gamma$ by $\Psi$ and
+% it is defined on $\C^2 \x \C^2 \x \calH$ such that
+% \begin{align*}
+%     \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
+%     s \in S_1.
+% \end{align*}
+% In particular, it means that for each $a_i \in S_0$
+% \begin{align*}
+%     \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
+% \end{align*}
+% Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
+% maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
+% by Lemma $15$ of Ref.~\cite{slofstra2017}.
+
+%---------------------------------------------------
+\subsection{Formal definitions}
+\label{sec:gamma_def}
+%---------------------------------------------------
+We define the solution group of the linear system game $\LS(r)$ first, following the steps described in the previous subsection.
+Then we define the game $\LS(r)$.
+
+From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
+we associate a variable $x(s)$ to each generator $s \in S$.
+Then each linear relation in $R$ can be translated to a linear equation.
+For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
+$f_1g_1m_2 = J$ is translated to the equation
+$x(f_1) + x(g_1) + x(m_2) = 1$. 
+The complete list of the equations is given in \cref{def:lsg_eq}.
+\begin{definition}
+\label{def:lsg}
+The linear system game $\LS(r)$ consists of
+\begin{align*}
+    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
+    & \calY^{\LS} = \{ x(s) : s \in S \},
+\end{align*}
+where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
+and $\mr := 14r + 62$ is the number of equations.  
+\carl{Since you are defining Alice's inputs to be subsets of S, why don't you just define Bob's inputs to be elements of S? Also, again you need to account that
+$J$ is an element of $S$.}
+\hfc{I think setting $\calY = S$ will cause confusion.
+You can see the forms of the equations in \cref{def:lsg_eq}.
+If I set the question set to be $S$, the reader will confuse the 
+linear equations with linear relation.
+I have moved $J$ out of $S$.}
+Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
+The answer sets are 
+\begin{align*}
+    \calA^{\LS} = (\Z_2)^{I_i} && \calB^{\LS} = \Z_2.
+\end{align*}
+The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
+\begin{align*}
+    \pi^{\LS}(I_i, x(s)) = 
+    \begin{cases}
+        1/N(r) & \text{ if } s \in I_i \\
+        0 & \text{otherwise,}
+    \end{cases}
+\end{align*}
+where $N(r) := 157r + 685$ is the total number of valid question pairs.
+We define $X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \}$, which is the set of all the valid answers of equation $i$.
+Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
+the score function is
+\begin{align*}
+    V^{\LS}_{I_i, x(s)}(\ba, b) = 
+    \begin{cases}
+        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
+        0 \text{, otherwise}.
+    \end{cases}
+\end{align*}
+\end{definition}
+
+The construction of $\LS(r)$ proves the following theorem.
+\begin{theorem}
+	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
+	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
+\end{theorem}
+\hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
+number of equation and variable pairs is $N(r)$ is of order $\Theta(r)$.}
+
+\hf{The ideal strategy of $\LS(r)$ is based on
+the representation $\Psi$ of $\Gamma$ defined in \cref{def:rep_gamma}
+of \cref{sec:rep_gamma}.
+We discuss the ideal strategy in in \cref{sec:tests}.
+Here we only highlight what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$, along
+with the important properties of the representation of these four generators,
+since they are the key generators of $\Gamma$.
+}
 
@@
 %------------------------------------------------------------------------------------------
-\carl{[Regarding the title of this subsection: Technically, you are only assuming that the correlation approximately wins $LS ( r )$.]}
-\hfc{Fixed.}
-
-In the first half of this subsection, we use $(I_i,x(s))$ to denote the question pair so that Alice gets equation label $I_i$ and Bob gets a variable label $x(s)$ for some $s \in S$. 
-\carl{[This last sentence is kind of vague.  If you're recalling notation from a previous subsection, you can just say that.]}
+\hf{In this subsection, we study the implications of a strategy that can win $\LS(r)$ with probability close to $1$. We prove a series of 
+propositions, which lead us to \cref{prop:lct_adv}.
+\Cref{prop:lct_adv} is a key step of the self-testing proof in \cref{sec:self-test}.}
+
+Recall that in $\LS(r)$ the question pair is denoted by $(I_i,x(s))$ where $I_i$ 
+labels an equation and $x(s)$ is a variable for some $s \in I_i$. 
 For simplicity, we denote 
@@
 \begin{align*}
-	\bra{\psi} M_i(s) N(s) \ket{\psi} &= 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{ij} -1 \\
-	&\appd{O(r \ep)} 2\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{is} - 1 = 1.
+	\bra{\psi} M_i(s) N(s) \ket{\psi} &= 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{ij} -1.
+\end{align*}
+Using the fact that $\bS$ approximates the winning correlation of $\LS(r)$, 
+we can get that
+\begin{align*}
+	\bra{\psi} M_i(s) N(s) \ket{\psi} \appd{O(r \ep)} 2\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{is} - 1 = 1.
 \end{align*}
 \carl{[The previous sentence \& equation do not make sense to me.]}
+\hfc{Fixed.}
 Since $M_i(s)$ and $N(s)$ are binary observables, we know that
@@
 \end{proposition}
-Recall that the group $\Pg_1$ (\cref{def:g1}) is embedded in $\Gamma$.
-\carl{[You need to tell the reader where they can find a full definition of $\Pg_1$.
-(Always do so when you reintroduce a mathematical object.)]}
+\hf{Recall that the group $\Pg_1$ (\cref{def:g1}) is embedded in $\Gamma$.  
+For details of the embedding, we refer to \cref{sec:embedding}.}
 Following the embedding procedure, we can prove the next proposition.
@@
 we can prove the following proposition.
-\begin{proposition}
+\begin{lemma}
 \label{prop:lct_adv}
@@
 for all $l \geq 1$.
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 so that it is easier to embed $\Pg$ into a solution group.
-\begin{definition}	
-\label{def:g0}
-	Let the set $S_0$ be 
-	\begin{align*}
-		S_0 = \{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5,
-	\end{align*}
-	and the set $R_0$ be the union of 
-	\begin{align*}
-	&R_{base} = \{s^2 = e | s \in S\},\\
-	&R_{u} = \{ u_3 = u_2o_1u_2 \quad u_4 = u_2o_2u_2 \quad 
-	u_5 = u_1u_3u_1 \quad o_2 = u_1u_4u_1 \quad u_5 = o_1 o_r o_1\},
-	\end{align*}
-	and 
-	\begin{align*}
-	R_o = 
-	\begin{cases} 
-	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1 \quad o_{2+2j} = o_2o_{1+2j}o_2\} \quad \text{ if $r$ is even },\\
-	\{o_3 = o_2o_1o_2\} \cup \bigcup_{j=1}^{(r-3)/2}\{
-	 o_{2+2j} =o_1o_{1+2j}o_1 \quad o_{3+2j} = o_2o_{2j+2}o_2 \}\quad\text{ if $r$ is odd }.
-	\end{cases}
-	\end{align*}
-	The group $\Pg_0$ is a group with presentation $\ip{R_0:S_0}$.
-\end{definition}
-\begin{proposition}
-    \label{prop:g0}
-	The group $\Pg$ is embedded in $\Pg_0$.
-	Furthermore, the generators of $\Pg_0$ satisfy the relation 
-	\begin{align}
-	    \label{eq:uo_comm}
-	    &(u_1u_2) o_2 (u_2u_1) = o_2 \\ 
-	    \label{eq:uo_rel}
-		&(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
-	\end{align}
-	for any $ j \in \N$.
-\end{proposition}
-\begin{proof}
-    We prove \cref{eq:uo_comm} first. It is easy to see that
-    \begin{align}
-        u_1 (u_2o_2u_2) u_1 = u_1u_4u_1 =o_2.
-    \end{align}
-
-    Next, we prove that $\Pg$ is embedded in $\Pg_0$ by prove the $j = 1$ case of \cref{eq:uo_rel}.
-    After it is proven, a homomorphism $\phi: \Pg \rightarrow \Pg_0$ such that $\phi(u) = u_1u_2$ and $\phi(o) = o_1o_2$ is injective by Proposition $33$
-    and Lemma $15$ of Ref.~\cite{slofstra2017}.
-
-	We prove \cref{eq:uo_rel} by induction.
-	The base case follows the direct calculation given below
-	\begin{align*} 
-		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
-	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
-	=& u_5 o_2\\
-	=& o_1o_ro_1 o_2.
-	\end{align*}
-	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above, which 
-	proves the $j=1$ case.
-
-	Now assume the statement is true for $j = n$, then for $j = n+1$
-	\begin{align*}
-		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
-		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
-		 =& (o_1o_2)^{r^{n+1}},
-	\end{align*}
-	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$, and
-	from the second line to the third line, we applied the $j=1$ case. Hence, the statement is true.
-\end{proof}
-To better characterize all the conjugacy
-relations of $\Pg_0$ and simplify the form of $\Pg_0$, 
-we relabel $u_i$ and $o_i$'s
-as $a_i$'s such that
-\begin{align}
-	a_j := 
-	\begin{cases}
-	 o_j \text{ for } j = 1,2 \\
-	 u_{j-2} \text{ for } j = 3\dots 7 \\
-	 o_{j-5} \text{ for } j = 8 \dots r+5.
-	\end{cases}
-\end{align}
-Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
-\begin{align}
-\label{eq:cr}
-	C(r) = \{ (i,j,k) |  (a_ia_ja_i = a_k) \in R_0 \}.
-\end{align}
-The size of $C(r)$ is $r+3$. 
-A presentation of the group $\Pg_0$ is
-\begin{align*}
-    \Pg_0 = \ip{ \{a_i\}_{i=1}^{r+5} : \{a_i^2 =e \}_{i=1}^{r+5} \cup \{ a_ia_ja_i = a_k \vert (i,j,k) \in C(r)\}}.
-\end{align*}
 
 Next we define the group $\Pg_1$.
-\begin{definition}
-\label{def:g1}
-Define the set $S_1$ to be
-\begin{align*}
-	S_1 = \{a_i, b_i, c_i, d_i\}_{i=1}^{r+5} \cup \{ f_0 \} \cup \{h_{jk}\}_{(i,j,k) \in C(r)},
-\end{align*}
-and the set $R_1$ to be
-\begin{align*}
-	R_1 = &\{ s^2 = e \vert s \in S_1\}\\ 
-	&\cup 
-	\{a_i = b_ic_i = f_0d_i, \quad f_0b_if_0 =c_i\}_{i= 1}^{r+5} \\ 
-	&\cup
-	\{h_{jk}b_j c_k = e, \quad d_ib_jd_i = c_k\}_{(i,j,k) \in C(r)}.
-\end{align*}
-The group $\Pg_1$ is a group with the presentation $\ip{S_1 : R_1}$.
-\end{definition}
-Note that the group $\Pg_1$ is the same as the group $K$ used in the proof of Lemma $29$ of Ref.~\cite{slofstra2017}.
-
-The relation between $\Pg_0$ and $\Pg_1$ is summarized in the propositions below, which was first proved in Lemma $29$ of \cite{slofstra2017}.
-\begin{proposition}
-    \label{prop:g0g1}
-	The group $\Pg_0$ is embedded in $\Pg_1$. 
-\end{proposition}
-\begin{proof}
-    We prove this proposition by showing that generators $a_i$'s in $S_1$
-    satisfy the relation $a_i a_j a_i = a_k$ for all $(i,j,k) \in C(r)$.
-    This means the homomorphism $\phi: \Pg_0 \rightarrow \Pg_1$ that maps $a_i$
-    to $a_i$ is homomorphism from $\Pg_0$ to $\Pg_1$. 
-    The injectivity of $\phi$ follows Lemma $29$ and Lemma $15$ of Ref.~\cite{slofstra2017}.
-
-	We first show that $d_i c_j d_i = b_k$, which is because
-	\begin{align*}
-		d_i c_j d_i = d_i (f_0 b_j f_0) d_i = f_0 (d_i b_j d_i) f_0 = f_0 c_k f_0 = b_k.
-	\end{align*}
-	Then, we can prove that 
-	\begin{align*}
-		a_i a_j a_i = f_0 d_i b_j c_j f_0 d_i 
-		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
-		= (f_0 c_k f_0)(f_0 b_k f_0) 
-		= b_k c_k = a_k,
-	\end{align*}
-	where we use the fact that $f_0$ commutes with $d_i$.
-\end{proof}
-The consequence of this proposition is that $\Pg$ can be embedded in $\Pg_1$.
 
 Recall the definition of $\Gamma$ in \cref{def:gamma}. We prove a property of it.
-\begin{proposition}
-    \label{prop:g1gamma}
-	The group $\Pg_1$ can be embedded in $\Gamma$.
-	The generators of $\Gamma$ also satisfy the relations: 
-	\begin{align}
-	    \label{eq:mg1} &f_0 g_0 f_0 g_0 = J,\\
-	    \label{eq:mg2} &f_2 g_2 f_2 g_2 = J.
-	\end{align}
-\end{proposition}
-\begin{proof}
-    To prove the first claim, we show that the generators
-    $b_i$, $c_i$, $d_i$ satisfy the relations
-    $d_ib_jd_i = c_k$ for each $\bc = (i,j,k) \in C(r)$.
-    \begin{align*}
-        d_ib_jd_i =& (k_{\bc 1} f_2)(f_2 k_{\bc 2})(k_{\bc 4} k_{\bc 5})\\ 
-        =& k_{\bc 1}(k_{\bc 2}k_{\bc 4})k_{\bc 5} \\
-        =& (k_{\bc 1} k_{\bc 3}) k_{\bc 5} \\
-        =& k_{\bc 6} k_{\bc 5} \\
-        =& c_k.
-    \end{align*}
-    The derivation of $f_0 b_i f_0 = c_i$ is similar for $1 \leq i \leq r+5$, so we omit it here.
-    A map $\phi:\Pg_1 \rightarrow \Gamma$ that maps $s$
-    to $s$ for each $s \in S_1$ is a homomorphism between $Pg_1$ and 
-    $Gamma$. It is also injective by Proposition $27$ and Lemma $15$ of 
-    Ref.~\cite{slofstra2017}.
-
-    The second claim follows a similar derivation, so we omit it here too.
-\end{proof}
-Since $\Pg$ is embedded in $\Pg_1$, we can conclude that
-$\Pg$ is embedded in $\Gamma$ as well.
+
 %========================================

### 2019-09-14 Draft/draft.tex
QIP version

@@
 \usepackage{amsmath,amssymb,amsfonts,amsthm,amstext}
+\usepackage{bbm}
 
@@
 \DeclareMathOperator{\hook}{hook}
-\DeclareMathOperator{\E}{\mathbb{E}}
+\DeclareMathOperator*{\E}{\mathbb{E}}
 \DeclareMathOperator{\supp}{supp}
@@
 \newcommand{\pauliz}{\sigma_z}
+\newcommand{\tO}{\tilde{O}}
 \newcommand{\tP}{\tilde{P}}
@@
 \newcommand{\bc}{\pmb{c}}
-\newcommand{\bS}{\mathrm{S}}
+\newcommand{\bS}{\mathbbmtt{S}}
 
@@
 \author[1]{Honghao Fu}
-\author[1,2]{Carl Miller}
 
@@
 \affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
-\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
+%\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
 \maketitle
@@
 \begin{abstract}
-	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
-	$\Theta(r^2)$ 
-	that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
-	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
-	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
-	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
+	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
+	that can robustly self-test a maximally entangled state of dimension $4d-4$,
+	where $r$ is the smallest multiplicative generator of $\Zd$.
+	The construction of the correlation uses the embedding procedure
+	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$ Cambridge University Press, $2019$).
+	Since there are 
+	infinitely many prime numbers whose smallest multiplicative generator
+	is at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
 	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
-	with unbounded local dimension.
+	with unbounded local dimensions.
 \end{abstract}
@@
 %========================================
-Self-testing is a unique phenomenon of quantum mechanics.
-It is also powerful because only classical interactions are required.
-It has many applications in quantum
-delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
+The certification of a quantum device is an important building block
+for many quantum information processing tasks, especially
+when the devices are provided by some untrusted vendor.
+We would like such certification to be done based solely on
+the observed measurement statistics and with the only assumption that
+any local device cannot communicate their own
+inputs to the other local devices. 
+The measurement statistics are referred to as correlations.
+
+It has been shown that certain quantum correlations require the distant parties to share
+a particular entangled state up to some local isometry. 
+This phenomenon is referred to as self-testing.  
+If we can further prove that, when the observed correlation deviates 
+from the ideal one to some extent, 
+the shared state is close to the ideal state up to some local isometry,
+then we say the self-test is robust.
+
+Self-testing is powerful because only classical interactions are performed.
+Hence, it allows a classical party to delegate quantum computations to some untrusted service provider
+and verify that the computations are performed
+honestly and correctly \cite{ruv2013,coladan2017verifier}.
+It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
 \cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
-
-The case of self-testing $2$-dimensional EPR pair, which is defined by
+Since the setting of interactive proof systems is similar to a self-test, self-testing arguments also help to prove
+lower bounds of the computational power of entanglement-assisted
+multiprover interactive proof systems \cite{fitzsimons2019, neexp}.
+
+The case of robust self-testing of the EPR pair, 
 \begin{align*}
@@
 is fully understood.
-The techniques for robustly self-testing $\ket{EPR}$ is 
-first introduced in Ref.~\cite{mckague2012}, then improved in Ref.~\cite{bamps2015}. 
-Ref.~\cite{yang2013} proved an generalized swap-isometry
-that can be used to robustly self-test large dimensional maxially entangled states.
-Its ideas are realized later in Ref.~\cite{coladan2017all}, 
-which proved that all pure bipartite entangled state 
-can be self-tested.
-The authors constructed a family of correlations such
-that each partially or maximally entangled state of any local dimension has
+The techniques for this case are 
+first introduced in \cite{mckague2012}, then improved in \cite{bamps2015}. 
+Robust self-testing of partially entangled qubits is proved later in
+\cite{yang2013}, which also proposed an generalized swap-isometry
+that can be used to robustly self-test large dimensional maximally entangled states.
+Robust self-testings of tensor product of maximally and partially entangled qubits 
+are proved in \cite{coladan2016parallel,natarajan2017,lowdegree},
+with the last one being the one with the smallest input and output alphabets.
+Self-testing of all pure bipartite entangled states is proved in \cite{coladan2017all}.
+The authors in \cite{coladan2017all} constructed a family of correlations such
+that an entangled state of any local dimension has
 a self-testing correlation in this family.
@@
 To generate a correlation in the family, Alice and Bob
-have constant number of measurement settings but each 
-measurement setting has the same number of outcomes as
-the local dimension of the entangled state to be self-tested. 
-In other words, their correlation is of size $\Theta(d^2)$,
+use constant-sized input alphabets but $\Theta(d)$-sized output alphabets, 
 where $d$ is the local dimension of the entangled state. 
 This is the only result about self-testing the general $d$-dimensional entangled state so far.
-However, proving the robustness of the family of correlations remains an open problem. 
-Without robustness, we cannot infer anything about a quantum strategy if
-the produced correlation deviates from the ideal correlation, no matter how small the 
-deviation is.
-
-A natural question to ask is whether maximally entangled states with large local dimension
-can be robustly self-tested with constant-sized correlations. 
-In this paper, we give an affirmative answer to this question by proving the following theorem.
+However, proving the robustness of this family of correlations remains an open problem.
+
+Our work aims at answering two open questions.
+The first one is whether maximally entangled states with large local dimension
+can be self-tested with constant-sized input and output alphabets, 
+which are independent of the local dimension of the self-tested state.
+For comparisons, all the correlations used in the results listed above
+have either input or output alphabets with sizes dependent on the
+local dimension of the entangled state.
+The second one is how to robustly self-test maximally entangled states
+with large local dimension and no tensor product structure. 
+We give an affirmative answers to the first question and
+make significant progress in answering the second question
+by proving the following theorem.
 \begin{theorem}[Informal]
@@
 The set $D$ is, specifically, the set of all 
-odd prime numbers whose smallest primitive root is either $2$, $3$, or $5$.  
-It has been shown that this set has infinitely many elements \cite{murty1988}.
-To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r)$ 
-for each $d \in D$ whose smallest primitive root is $r$.
+odd prime numbers whose smallest primitive root 
+is either $2$, $3$, or $5$, 
+We say that $r$ is a primitive root of $d$ if $r$ is the 
+multiplicative generator of the group $\Zd$.
+It has been shown that $D$ has infinitely many elements \cite{murty1988}.
+
+To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
+input and constant-sized output alphabets
+for each odd prime number $d$ whose smallest primitive root is $r$.
 This correlation is denoted by $\fC(d,r)$.
-Note that although the size of $\fC(d,r)$ does not depend on $d$, the entries of $\fC(d,r)$ do.
-Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
-that if some quantum strategy can approximate $\fC(d,r)$, then
-the generalized swap isometry \cite{yang2013}
-can produce the desired maximally entangled states when applied to the unknown state used in the strategy.
+Note that although the size of the input or output alphabet of $\fC(d,r)$ does not depend on $d$, 
+the distributions in $\fC(d,r)$ do. 
+Once we prove $\fC(d,r)$ can robustly self-test a maximally entangled
+state of dimension $4(d-1)$, we apply it to all $d \in D$
+and prove \cref{thm:inf}.
 %Then the self-testing property of this correlation is 
@@
 %\end{theorem}
-\carl{The paper \cite{bamps2015} says that the earlier paper \cite{yang2013} has ``flaws.'' Check what those flaws are, and make sure that they won't put a shadow on anything that you're discussing when you cite \cite{yang2013}.}
-\hfc{The flaws are in the self-testing proof, not in the 
-proof about the generalized isometry.}
-
-The correlation $\fC(d,r)$ contains the ideal correlation of a specially-designed binary linear system game.
+
+The correlation $\fC(d,r)$ contains a winning correlation of a specially-designed binary linear system game.
 In a general linear system game, Alice is given a random equation 
 from a linear system and she
-should give an assignment of the equation.
+should give an assignment to each variable of the equation.
 Bob is asked to assign a value to a random variable of that equation.
@@
 \end{align*}
-Using two copies of the maximally entangled state
-\begin{align*}
-    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
-\end{align*}
-the Magic square game can be won
-with certainty.
-It has been shown that if a strategy that can win this game almost perfectly, the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
+Using two copies of $\ket{EPR}$
+the Magic square game can be won with certainty.
+It has been shown that if a strategy that can win this game almost perfectly, 
+the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
 so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
 The key observation that leads to the self-testing proof is that 
-a winning strategy must contain observables $X$ and $Z$ that 
+a winning strategy must contain binary observables $X$ and $Z$ that 
 satisfy the anti-commutation relation 
@@
 Intuitively, we can think of the Magic Square game as a way to enforce the
-anti-commutation relation.
+anti-commutation relation \cite{coladan2017}.
 
@@
 \end{align*}
-for some integer $r$,
-in the sense that the winning strategy contains binary observables
+for unitaries $U$ and $O$, and some integer $r$.
+It implies that the winning strategy contains binary observables
 $M_1, M_2, M_3, M_4$ on Alice's side and 
@@
 \end{align*}
-This relation implies the eigenvalue of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root
-is $r$. It also implies that $U$ is a permutation of the eigenbasis of $O$.
+This relation implies the eigenvalues of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
+It also implies that $U$ is a permutation of the eigenbasis of $O$.
 Winning this linear system game implies that Alice and Bob share a state
@@
 \end{align*}
-These two relations are important for the self-testing argument
-because
-the relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
-is spanned by tensor products of states in the eigenbasis of $O$;
-and $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
+These two relations are important for the self-testing argument.
+The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
+is spanned by tensor products of states in the eigenbasis of $O$.
+The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
 under the permutation induced by $U$. 
 At this point, the eigenvalues of $O$ are unknown, so
-further restricting the eigenvalues of $O$ requires another test, 
+certifying the eigenvalues of $O$ requires another test, 
 which will be introduced later.
@@
 and the answer sets are of size $\Theta(1)$.
-Restricting $r \leq 5$ in our theorem implies that our linear system 
+Restricting $r \leq 5$ as in \cref{thm:inf} implies that our linear system 
 game only uses constant-sized question sets and constant-sized answer sets.
-\carl{A reader may get lost at the last sentence -- you're jumping into the material too quickly without enough explanation.}
-\hfc{Rewritten.}
+
 % The number of variables and the number of equations of the linear system game depend linearly on $r$,
@@
 
-The remaining question is how to certify a particular eigenvalue of $O$, so we
+The remaining question is how to certify eigenvalues of $O$, so we
 design a nonlocal test called the extended weighted CHSH test.
@@
 The difference between a nonlocal game and a nonlocal test will be discussed later.
-It is designed based on the $\alpha$-weighted CHSH inequality, which is defined by
+The combination of a linear system game with 
+a nonlocal test in the construction of $\fC(d,r)$ 
+is a new way to use a linear system game for robust self-testing.
+It distinguishes our approach from all the previous ones.
+
+The extended weighted CHSH test is designed based on the $\alpha$-weighted CHSH inequality, 
 \begin{align*}
@@
 \begin{align*}
-    M_1 = \pauliz && M_2 = \paulix,
+    \tM_1 = \pauliz && \tM_2 = \paulix,
 \end{align*}
@@
 \begin{align*}
-    N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
+    \tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && \tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
 \end{align*}
 We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
-state $\ket{\psi}$ and the observables $M_1, M_2$ and $N_1, N_2$.
-Then we noticed that 
-\begin{align*}
-    N_1N_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
+state $\ket{\psi}$ and the observables $\tM_1, \tM_2$ and $\tN_1, \tN_2$ in \cref{sec:ext_chsh}.
+Then we notice that 
+\begin{align*}
+    \tN_1\tN_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
 \end{align*}
 has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.
-Hence, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
+
+Therefore, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
 for some odd prime $d$ whose primitive root is $r$,
 and ask Alice and Bob
-to reuse the observables $M_1, M_2$ and $N_1, N_2$，then we can certify that
+to reuse the observables $M_1, M_2$ and $N_1, N_2$ defined in $\LS(r)$. Then we can certify that
 the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
@@
 and the eigenspaces of all the eigenvalues have the same cardinality.
-At this point, we has the explicit structure of $O$, so we 
+
+At this point, we have the explicit structure of $O$, so we 
 can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
 to prove the correlation $\fC(r, d)$ can robustly self-test 
-a maximally entangled state of dimension $4(d-1)$.
-
-\carl{This paragraph (also) will need more context.}
-\hfc{Rewritten.}
-
-Our contributions are four-fold.
+a maximally entangled state of dimension $4(d-1)$,
+\begin{align*}
+    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
+    \ket{EPR}^{\x 2}.
+\end{align*}
+
+In the proof, we demonstrate a new way to apply the generalized swap-isometry
+proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
+dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.
+
+Our contributions are:
 \begin{enumerate}
-    \item We identify the constant-sized question and answer sets that can be used to robustly self-test
-    maximally entangled states with unbounded dimensions. Before our work, the most efficient way
-    was to use $O(\log d)$-sized question and answer sets to robustly self-test
+\item We identify a family of correlations with constant-sized input and output alphabets that can be used to robustly self-test
+maximally entangled states with unbounded local dimensions. Before our work, the most efficient way 
+was to use $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
 the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
-    \item Our self-testing proof demonstrate a new way to apply the generalized swap-isometry
-    proposed in Ref.~\cite{yang2013} to robustly self-test a maximally entangled state of large lcoal
-    dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.
-    We believe it can be applied to prove the family of correlations proposed in Ref.~\cite{coladan2017all}
-    are also robust.
-    \item We demonstrate how to enforce relations between operators of large but fixed dimension in a 
-    binary linear system game. Before our work, only the anti-commutation relation between $2$-dimensional
-    Pauli operators can be enforced in a binary linear system game.
-    \item Our result gives us deeper understanding of the set of quantum correlations.
-    In previous works that proved the non-closeness of the set of quantum correlations
-    \cite{slofstra2017}, 
+
+\item Our result gives us deeper understandings of the set of quantum correlations.
+In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
 lower bounds of the entanglement required to achieve certain correlations are identified.
-    Our work discovers a large family of correlations where we know exactly the amount of entanglement
+We discover a large family of correlations such that we know exactly the entangled state
 required to achieve each of the correlations in this family. 
@@
 an extended weighted CHSH test, we introduce the linear system game
-in \cref{sec:lsg} and the self-testing properties of the extended weighted CHSH inequality in \cref{sec:chsh}. 
+in \cref{sec:lsg} and the extended weighted CHSH test in \cref{sec:ext_chsh}. 
 Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
@@
 %-----------------------------------
-The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we \hf{self-test} is denoted by
+The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we self-test is denoted by
 \begin{align}
@@
 The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
-The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
-\hf{the EPR pair is denoted by} 
+The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$.
+
+In the qubit case, the EPR pair is denoted by 
 \begin{align}
@@
 \end{align}
-and the Pauli operators are given by
+and the Pauli operators are denoted by
 \begin{align}
@@
 For example, $O_A$ is an operator on Alice's side and $\ket{0}_{B}$ is a state on Bob's side. 
-The only exception is for projectors used in a quantum strategy defined below, where the subscript 
+The only exception is when we label projectors used in a quantum strategy defined below. In this case, the subscript 
 is the input and the superscript is the output. For example, $M_x^a$ is Alice's projector for input $x$ and output $a$.
-Operators defined by the projectors follow the same convention, for example, $M_x := M_x^0 - M_x^1$.
+Operators defined by the projectors follow the same convention, for example, $M_x := M_x^0 - M_x^1$ is 
+a binary observable.
 If we add tilde to an operator, then this operator is fully characterized and belongs to some ideal strategy.
@@
 In other words,
-$r$ is a generator of $\Zd$.
+$r$ is a multiplicative generator of $\Zd$.
 
@@
 We introduce them below.
-For more contexts, please refer to Ref.~\cite{dummit2004}.
-
-\hf{
+For more contexts, please refer to \cite{dummit2004}.
+
 Let $S$ be a set of letters. We denote by $\mathcal{F}(S)$ the \emph{free group generated by $S$}, 
@@
 The group law is given by concatenation and cancellation.
-For a more formal treatment, we refer to Section $6.3$ of Ref.~\cite{dummit2004}.}
+For a more formal treatment, we refer to Section $6.3$ of \cite{dummit2004}.
 
@@
 \in R$.
-\hf{ There are two types of relations that we will be working with.
-} 
-Considering \hf{a subset of generators} $\{ s_j \}_{j=1}^n \subset S$ \hf{such that $s_{j_1} \neq s_{j_2}$ if $j_1 \neq j_2$},
+There are two types of relations that we will be working with.
+Considering a subset of generators $\{ s_j \}_{j=1}^n \subset S$ such that $s_{j_1} \neq s_{j_2}$ if $j_1 \neq j_2$,
 the relations of the form $\Pi_{j=1}^n s_j  = e$, where $e$ is the identity element, are called 
@@
 $s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.
+
 There are two special types of groups that we will work with in \cref{sec:lsg}. We give the definitions below.
@@
 A conjugacy group is a special case of what Slofstra defined as 
-a linear-plus-conjugacy group (Definition $26$ of Ref.~\cite{slofstra2017}). The difference is that a conjugacy group does not have linear relations. The next definition follows the 
+a linear-plus-conjugacy group (Definition $26$ of \cite{slofstra2017}). 
+The difference is that a conjugacy group does not have linear relations. 
+The next definition follows the 
 definition of a nice linear-plus-conjugacy group (Definition $28$ of \cite{slofstra2017}).
@@
 \end{definition}
-\carl{Nice work with the last two definitions -- they are prettty clean.
-I wonder if you could make the last definition even cleaner by simply asserting the relations $s_j s_k = s_k s_j$, and leaving out the generators $s_{jk}$?}
-\hfc{If we treat the commutation relations as conjugacy relations, then the final solution will be more complicated.}
 The relation $s_{jk} s_js_k = e$ implies that $s_j$ commutes with $s_k$
@@
 \end{align*}
+
 Next we give the definition of a group representation. 
 \begin{definition}
-    A representation of $G$ on the finite Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
+    A representation of a group $G$ on the finite Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
 \end{definition}
-The last concept of group theory that we need is group embedding.
+The last concept of group theory that we need is a group embedding.
 \begin{definition}[Group embedding]
@@
 to give an answer for a randomly chosen question. 
-\hf{We denote Alice's question set by $\calX$ and her family of answer sets by $\{\calA_x\}_x$
+We denote Alice's question set by $\calX$ and her family of answer sets by $\{\calA_x\}_x$
 for each $x \in \calX$. Similarly,
-Bob's question set is denoted by $\calY$ and his family of answer sets denoted by $\{\calB_y\}_y$ for each $y \in \calY$. 
-Note that when $\calA_x = \calA$ for each $x \in \calX$, we simply say the output alphabet is $\calA$, and we follow this convention on Bob's side too.
-The nonlocal game also
-comes with a functions $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
-and a family of functions $\{ V_{(x,y)} : \calA_x \times \calB_y \rightarrow \R \}_{x,y}$ for each $(x,y) \in \calX \times \calY$, which is 
+Bob's question set is denoted by $\calY$ and 
+his family of answer sets is denoted by $\{\calB_y\}_y$ for each $y \in \calY$. 
+Note that when $\calA_x = \calA$ for each $x \in \calX$, we simply say the output alphabet is $\calA$, 
+and we follow this convention on Bob's side too.
+The probability distribution over the questions of
+a nonlocal game 
+is given by a functions $\pi: \calX \times \calY \rightarrow [0,1]$,
+A nonlocal game also comes with a family of functions $\{ V_{(x,y)} : \calA_x \times \calB_y \rightarrow \R \}_{x,y}$ for each $(x,y) \in \calX \times \calY$, which is 
 the family of scoring functions.
-Note that when $\calA_x = \calA$ for all $x$ and $\calB_y = \calB$ for all $y$, we write the score function as 
+Note that when $\calA_x = \calA$ for all $x$ and $\calB_y = \calB$ for all $y$, we write the scoring function as 
 $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$.
-}
-
-\hf{We also define A nonlocal test 
+
+We also define a nonlocal test 
 to be a tuple $(\calX, \calY, \{\calA_x\}_{x \in \calX}, \{\calB_y\}_{y \in \calY}, \pi)$, where
 $\calX, \calY, \{\calA_x\}_{x}, \{\calB_y\}_{y}$ and $\pi$ are as defined for a nonlocal game.
-Hence, a nonlocal test doesn't have scoring functions.
-}
+Hence, a nonlocal test does not have scoring functions.
 
@@
 Note that the tensor product structure indicates that the
-two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.
-For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
-\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
+two parties cannot communicate with each other, 
+which is the reason why we say such task is nonlocal.
+For simplicity we omit the tensor product symbol between operators 
+acting on different Hilbert spaces in the rest of the work. 
+If $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
+\calH_B \rightarrow \calH_B$, 
+then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
 \begin{definition}
@@
 \end{definition}
+The size of a correlation is the sum of the sizes of the conditional probability distributions in the correlation.
+
 A particular type of nonlocal games that we are interested in is called binary linear system games.
 \begin{definition}[Binary linear system game]
- Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ (meaning that $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
+ Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ (meaning that $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
  $c$ is a length-$n$ vector with entries in $\Z_2$). 
@@
 
-A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
+A widely-used example of a linear system game is the Magic Square game introduced in \cite{magic_square}, which 
 have equations
@@
 \end{align*}
-\hf{Note that the equations above are taken modulo $2$.
-We follow this convention in the rest of our work.}
-For the formulation of a general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.
+Note that the equations above are taken modulo $2$.
+We follow this convention in the rest of our work.
+For the formulation of a general linear system games over $\Z_d$, we refer to Section $3.1$ of \cite{coladan2017}.
 
@@
 		\item $M_{ij}^2 = \1$ for every $i,j$, and
-		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every \carl{$i,l,k$ such that} $H(i,l) = H(i,k) =1$;
+		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every $i,l,k$ such that $H(i,l) = H(i,k) =1$;
 	\end{enumerate} 
@@
 \end{definition}
-Note that a measurement strategy of a binary linear system game can be converted to a binary observable strategy. Let a measurement strategy be 
-$(\{\{M_i^{\ba}\}_{\ba \in X_i}\}_{i=1}^m, \{\{N_j^b\}_{b=0}^1\}_{j=1}^n,\\ \ket{\psi})$, where $X_i$ is some answer set of equation $i$.
+Note that a measurement strategy of a binary linear system game can be converted to a binary observable strategy. 
+Let a measurement strategy be 
+$(\{\{M_i^{\ba}\}_{\ba \in X_i}\}_{i=1}^m, \{\{N_j^b\}_{b=0}^1\}_{j=1}^n, \ket{\psi})$, 
+where $X_i$ is the answer set of equation $i$.
 The corresponding binary observable
@@
 for $1\leq i \leq m$ and $1 \leq j \leq n$. 
-\hf{
-Hence, in the rest of the work, we focus on binary observable strategies,
-when discussing Alice's strategy of some linear system game.
+Hence, in the rest of the work, we focus on binary observable strategies of linear system games.
 Specifically, we assume that Alice has a binary observable for each variable
-in each equation ,
+in each equation,
 so when she is asked the assignment of a particular variable, she simply
-measures according to the corresponding observable of that variable in some equation.}
+measures according to the corresponding observable of that variable.
 
@@
 
-A \hf{perfect} binary observable strategy for the linear system game associated with $Hx = c$, which always wins the game, can be constructed from
+A perfect binary observable strategy for the linear system game associated with $Hx = c$ can be constructed from
 a finite-dimensional representation of a finitely presentable group
@@
 Then a perfect strategy for 
-the linear system game ($Hx = c$) is given by 
+the linear system game ($Hx = c$) has
 \begin{enumerate}
@@
 %-------------------------------------------------------------------------------
-\hf{The weighted CHSH inequality a variation of the CHSH inequality \cite{chsh}. 
-We formulate it as a nonlocal game.}
-The input sets and output sets of Alice and Bob are
+The weighted CHSH inequality a variation of the CHSH inequality \cite{chsh}. 
+We formulate it as a nonlocal game.
+The input alphabets and output alphabets of Alice and Bob are
 $\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
-The scoring function for the $\alpha$-weighted CHSH test, for $|\alpha|\geq 1$, is defined by
+The scoring function for the $\alpha$-weighted CHSH test, when $|\alpha|\geq 1$, is defined by
 \begin{align}
@@
 The input distribution is $\pi(x,y) = 1/4$ for all $(x,y) \in \calX \times \calY$.
+
 Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
@@
 	\label{def:ideal}
-	Define $\mu = \arctan(1/\alpha)$.
+	Define $\mu := \arctan(1/\alpha)$.
 	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\I_\alpha^{\max}$, 
-	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
+	consists of the joint state $\ket{EPR}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
 	$\tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $\tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
 \end{definition}
-An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
-value $\I_\alpha$ close to $\I_\alpha^{\max}$, then the strategy is close to the ideal 
-strategy up to some local isometry, 
-which is a phenomenon referred as a robust self-test.
-We give the formal statement of this self-testing property of $\I_\alpha$ in \cref{sec:chsh}.
-\hf{In \cref{sec:full_test} we design
-a nonlocal test called the extended weighted CHSH test based on the weighted CHSH inequality.}
+An interesting observation of the weighted CHSH inequality is that it admits robust self-testing of the ideal strategy given
+above. 
+We give the formal statement of this robust self-testing property of $\I_\alpha$ in \cref{sec:chsh}.
+In \cref{sec:full_test} we design
+a nonlocal test called the extended weighted CHSH test based on 
+the ideal correlation that maximally violates the weighted CHSH inequality.
 
@@
 		U\ket{u} \appd{\ep_1} a \ket{u} &&
-		V\ket{v} \appd{\ep_2} b \ket{v}, 
-	\end{align*}
-	for some $a \neq b \in \C$ such that $\norm{a} = \norm{b} = 1$. Then,
+		U\ket{v} \appd{\ep_2} b \ket{v}, 
+	\end{align*}
+	for some $a \neq b \in \C$ and $\norm{a} = \norm{b} = 1$. Then,
 	\begin{align*}
@@
 	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$,
-	$\norm{\ket{v}} \appd{\ep_2} 1$, and $\braket{u}{v} \geq 1 - \ep_3$.
+	$\norm{\ket{v}} \appd{\ep_2} 1$, and $\braket{u}{v} \appd{\ep_3} 1$.
 	Then
@@
 	\begin{align*}
-		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C.
-	\end{align*}
+		U\ket{u} \appd{\ep} a\ket{u},
+	\end{align*}
+	for $a \in \C$ and $\norm{a} = 1$.
 	Then,
 	\begin{align*}
-		U^n \ket{u} \appd{n\ep} a^n \ket{u} \text{ for all } n \geq 1.
-	\end{align*}
+		U^n \ket{u} \appd{n\ep} a^n \ket{u}
+	\end{align*}
+	for all $n \geq 1$.
 \end{proposition}
@@
 	We can prove it by induction. 
-	For $k=1$, the statement is satisfied.
+	The $k=1$ case follows the given condition.
 	Assume it holds for $k = n-1$ and consider $k = n$, then we have
@@
 	\end{align*}
-	where we used the fact that $\norm{U} = 1$ and $\norm{a} \leq 1$.
+	where we used the fact that $\norm{U} = 1$.
 \end{proof}
-
+\begin{lemma}[Substitution Lemma]
+    \label{lm:sub}
+    Let $\calH_A$ and $\calH_B$ be two Hilbert spaces, and
+    $\ket{\psi} \in \calH_A \x \calH_B$.
+    Suppose there exist unitaries 
+    $\{V\} \cup \{V_i\}_{i=1}^k \cup \{ M_i \}_{i=1}^n$ on $\calH_A)$ and
+    $\{ N_i \}_{i=1}^n$ on $\calH_B$ such that
+    \begin{align*}
+        &M_i \ket{\psi} \appd{\ep_1} N_i \ket{\psi}
+    \end{align*}
+    for $1 \leq i \leq n$, and 
+    \begin{align*}
+        &V \ket{\psi} \appd{\ep_2} \Pi_{i=1}^k V_i \ket{\psi}.
+    \end{align*}
+    Then,
+    \begin{align*}
+        V\Pi_{i=1}^n M_i \ket{\psi} 
+        \appd{(2n\ep_1 + \ep_2} \left(\Pi_{i=1}^k V_i\right) 
+        \left(\Pi_{i=1}^n M_i \right)\ket{\psi}.
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    We prove this lemma by induction on $n$.
+    The $n = 0$ case follows the condition that $V \ket{\psi} \appd{\ep_2} \Pi_{i=1}^k V_i \ket{\psi}$.
+
+    Assume the conclusion holds for $n = m$.
+    Consider the case $n = m+1$, then
+    \begin{align*}
+        V\Pi_{i=1}^{m+1} M_i \ket{\psi} 
+        &= V \left(\Pi_{i=1}^{m} M_i\right) M_{m+1} \ket{\psi} \\
+        &\appd{\ep_1} V \left(\Pi_{i=1}^{m} M_i\right) N_{m+1} \ket{\psi} \\
+        &= N_{m+1} V \left(\Pi_{i=1}^{m} M_i\right) \ket{\psi} \\
+        &\appd{2m\ep_1+\ep_2} N_{m+1}\left(\Pi_{i=1}^k V_i\right) 
+        \left(\Pi_{i=1}^m M_i \right)\ket{\psi} \\
+        &=\left(\Pi_{i=1}^k V_i\right) 
+        \left(\Pi_{i=1}^m M_i \right) N_{m+1} \ket{\psi} \\
+        &\appd{\ep_1} \left(\Pi_{i=1}^k V_i\right) 
+        \left(\Pi_{i=1}^{m+1} M_i \right) \ket{\psi}.
+    \end{align*}
+    Adding the error terms in the derivation above together gives us that
+    \begin{align*}
+        V\Pi_{i=1}^{m+1} M_i \ket{\psi} 
+        \appd{(2m+2)\ep_1+\ep_2} \left(\Pi_{i=1}^k V_i\right) 
+        \left(\Pi_{i=1}^{m+1} M_i \right) \ket{\psi}.
+    \end{align*}
+    By the principle of inductive proof, the proof is complete.
+\end{proof}
 %===============================================
@@
 %===============================================
-In this section, we introduce a binary linear system game which is a component of the full test.
+In this section, we introduce a binary linear system game that is a component of the full test.
 This game is designed to enforce relations that should be satisfied by 
@@
 The inspiration comes from 
-Slofstra's seminal work~\cite{slofstra2017}, in which he
+Slofstra's seminal work \cite{slofstra2017}, in which he
 embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
@@
 \end{align}
-for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
+for some $r \in \N$, into the solution group, $\Gamma$, of a binary linear system game, $\LS(r)$.
 The steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed 
-in the proofs of Proposition~$33$, Lemma~$29$ and Proposition $27$ of Ref.~\cite{slofstra2017}, 
+in the proofs of Proposition~$33$, Lemma~$29$ and Proposition $27$ of \cite{slofstra2017}, 
 so the group $\Pg$ (\cref{eq:pgroup}) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}),
@@
 The purposes of introducing each intermediate
-group are explained along the definition.
+group are explained along the definitions.
+In \cref{sec:lsr_def}, we construct $\LS(r)$ from $\Gamma$ and give the 
+formal definition of $\LS( r )$.
+
 Note that, we defer the full definitions of the representations of $\Pg_0$, $\Pg_1$ and $\Gamma$
@@
 Instead, We only highlight a few operators from a finite-dimensional representation of $\Gamma$.
-The representation will be used later to build the ideal strategy.
-In \cref{sec:gamma_def}, we construct $\LS(r)$ from $\Gamma$ and give the 
-formal definition of $\LS( r )$.
+The representation of $\Gamma$ will be used later to build the ideal strategy of the full test.
 
@@
 generators are of order-$2$, because
-it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single generator. On the other hand, 
-a homomorphism from $\Pg_0$ to a solution group can be easier to find.
+it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single binary generator. 
+On the other hand, a homomorphism from $\Pg_0$ to a solution group can be easier to find because all the generators of $\Pg_0$ are binary.
 \begin{definition}	
@@
 \end{definition}
-The special generators of $\Pg_0$ are $o_1, o_2, u_1$ and $u_2$ because the product $o_1o_2$ behaves similarly as $o$
+The special generators of $\Pg_0$ are $o_1, o_2, u_1$ and $u_2$ because the product $o_1o_2$ behaves similarly as $o$,
 and the product $u_1u_2$ behaves similarly as $u$.
@@
 	The group $\Pg$ is embedded in $\Pg_0$.
-	Furthermore, the generators of $\Pg_0$ satisfy the relation 
+	Furthermore, the generators of $\Pg_0$ satisfy the relations 
 	\begin{align}
@@
 
-    Next, we prove that $\Pg$ is embedded in $\Pg_0$ by prove the $j = 1$ case of \cref{eq:uo_rel}.
-    The proof of Proposition $33$ of Ref.~\cite{slofstra2017} gives the recipe about
-    how to construct a finite-dimensional representation of $\Pg_0$ from a 
-    finite-dimensional representation of $\Pg$, so Lemma $15$ of Ref.~\cite{slofstra2017}
+    Next, The proof that $\Pg$ is embedded in $\Pg_0$ is based on
+    the $j = 1$ case of \cref{eq:uo_rel}.
+    Once it is proved, we can use the recipe given in
+    the proof of Proposition $33$ of \cite{slofstra2017} 
+    to construct a finite-dimensional representation of $\Pg_0$ from a 
+    finite-dimensional representation of $\Pg$. 
+    Then Lemma $15$ of \cite{slofstra2017}
     proves that a homomorphism $\phi: \Pg \rightarrow \Pg_0$ such that $\phi(u) = u_1u_2$ and 
@@
 
-	Now assume the statement is true for $j = n$, then for $j = n+1$
+	Assume the statement is true for $j = n$, then for $j = n+1$
 	\begin{align*}
@@
 	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$, and
-	from the second line to the third line, we applied the $j=1$ case. Hence, the statement is true.
+	from the second line to the third line, we apply the $j=1$ case
+	$r^n$ times. Hence, the statement is true.
 \end{proof}
 Note that our representation $\Psi_0$ of $\Pg_0$ is different from the representation
-constructed in the proof of Proposition $33$ of Ref.~\cite{slofstra2017}.
+constructed in the proof of Proposition $33$ of \cite{slofstra2017}.
 We give the formal definition of $\Psi_0$ (\cref{def:rep_g0}) in \cref{sec:rep_gamma}.
@@
 To better characterize all the conjugacy
-relations of $\Pg_0$ and simplify the form of $\Pg_0$, 
-we relabel $u_i$ and $o_i$'s as $a_i$'s such that
+relations of $\Pg_0$ and simplify the presentation of $\Pg_0$, 
+we relabel $u_i$ and $o_i$'s as $a_i$'s in such a way that
 \begin{align}
@@
 	\begin{cases}
-	 o_j \text{ for } j = 1,2 \\
-	 u_{j-2} \text{ for } j = 3\dots 7 \\
-	 o_{j-5} \text{ for } j = 8 \dots r+5.
+	 o_j &\text{ for } j = 1,2 \\
+	 u_{j-2} &\text{ for } j = 3\dots 7 \\
+	 o_{j-5} &\text{ for } j = 8 \dots r+5.
 	\end{cases}
@@
 \end{definition}
-Note that the group $\Pg_1$ is the same as the group $K$ used in the proof of Lemma $29$ of Ref.~\cite{slofstra2017}.
+Note that the group $\Pg_1$ is the same as the group $K$ used in the proof of Lemma $29$ of \cite{slofstra2017}.
 For each $1 \leq i \leq r+5$, the relation $a_i = b_ic_i$ guarantees that $b_i$ commutes with $c_i$.
@@
 
-The relation between $\Pg_0$ and $\Pg_1$ is summarized in the propositions below, which 
-is a specific case of Lemma $29$ of \cite{slofstra2017}.
+The relation between $\Pg_0$ and $\Pg_1$ is summarized in the propositions below.
 \begin{proposition}
@@
     \end{align*}
-    as proved in Lemma $29$ of Ref.~\cite{slofstra2017}.
-    Then, the injectivity of $\phi$ follows Lemma $15$ of Ref.~\cite{slofstra2017}.
+    as proved in Lemma $29$ of \cite{slofstra2017}.
+    Then, the injectivity of $\phi$ follows Lemma $15$ of \cite{slofstra2017}.
 \end{proof}
-The consequence of this proposition is that $\Pg$ can be embedded in $\Pg_1$.
-We give the formal definition of the represention $\Psi_1$ of $\Pg_1$ 
+The consequence of this proposition is that $\Pg$ is embedded in $\Pg_1$.
+We give the formal definition of the representation $\Psi_1$ of $\Pg_1$ 
 (\cref{def:rep_g1}) in \cref{sec:rep_gamma}.
@@
 and the set $R$ to be the union of the following
-set of linear relations:
+sets of linear relations:
 \begin{itemize}
@@
 $
-\item $R_J = \{ J s J s = e \vert s \in S\}$,
+\item $R_J = \{ J s J s = e \vert s \in S\} \cup \{J^2 = e\}$,
 \item $R_{base} = \{ s^2 = e \vert s \in S\}$.
 \end{itemize}
-\hf{The group $\Gamma$ is a group with the presentation
-$\ip{S \cup \{J\} : R}$.}
+The group $\Gamma$ is a group with the presentation
+$\ip{S \cup \{J\} : R}$.
 \end{definition}
@@
     \label{prop:g1gamma}
-	The group $\Pg_1$ can be embedded in $\Gamma$.
+	The group $\Pg_1$ is embedded in $\Gamma$.
 	The generators of $\Gamma$ also satisfy the relations: 
@@
     A representation of $\Gamma$ can be constructed from a representation 
-    of $\Pg_1$ as shown in the proof of Proposition $27$ of Ref.~\cite{slofstra2017},
-    so Lemma $15$ of Ref.~\cite{slofstra2017} proves the homomorphism $\phi$
-    is injective.
-
-    The second claim follows a similar derivation
-    using linear relations in $R_{MS}$, so we omit it here.
+    of $\Pg_1$ as shown in the proof of Proposition $27$ of \cite{slofstra2017},
+    so Lemma $15$ of \cite{slofstra2017} proves that
+    the homomorphism $\phi$ is injective.
+
+    \Cref{eq:mg1} can be proved by
+    \begin{align*}
+        &f_0 g_0 f_0 g_0 \\
+        = &(f_1 f_2) (f_2 m_1)  (f_1 f_2) (f_2 m_1)\\
+        = &f_1 m_1 f_1 m_1 \\
+        = &f_1 (g_0 f_2) f_1 (m_0 m_2) \\
+        = &f_1 g_0 (f_2 f_1) (f_0 g_2) m_2 \\
+        = &f_1 g_0 g_2 m_2 \\
+        = &f_1 g_1 m_2 \\
+        = &J.
+    \end{align*}
+    \Cref{eq:mg2} can be proved analogously.
 \end{proof}
@@
 
+The formal definition of a representation of $\Gamma$ is given in \cref{def:rep_gamma}. 
+We highlight a few important operators here.
 The representation $\Psi$ of $\Gamma$ is defined on the Hilbert space
@@
 where $W_k$ denotes a Hilbert space of
-dimension $k$. 
-The formal definition of $\Gamma$ is defined in \cref{def:rep_gamma}
-in \cref{sec:rep_gamma}.
-We denote the
-standard basis of $W_k$ by $\{\ket{x_j}\}_{j=1}^{k}$.
-We define an operator $O$ on $W_{d-1}$ as
-\begin{align*}
-    O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}.
+dimension $k$,
+\begin{align}
+    \label{eq:basis}
+    W_k = \spn\{ \ket{x_j} \}_{j=1}^k.
+\end{align}
+We denote the standard basis of $W_k$ by $\{\ket{x_j}\}_{j=1}^{k}$.
+We denote the identity operator for the subspace $W_k$ by $\1_{W_k}$.
+
+We define an operator $\tO$ on $W_{d-1}$ as
+\begin{align*}
+    \tO = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}.
 \end{align*}
@@
 where the subscript $r^j$ is taken modulo $d$ implicitly,
-because another form of $O$ is 
+because another form of $\tO$ is 
 \begin{align}
     \label{eq:O}
-    O = \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}.
+    \tO = \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}.
 \end{align}
 We use the second form of the basis when it is convenient.
-The other basis of $W_{d-1}$ that we use is $\{ \ket{u_j} \}_{j=0}^{d-2}$ given by
+The other basis of $W_{d-1}$ that we use is $\{ \ket{u_j} \}_{j=0}^{d-2}$ defined by
 \begin{align*}
@@
 \end{align*}
-We denote the identity operator for the subspace $W_k$ by $\1_{W_k}$.
-The representations of $a_1, a_2, a_3$ and $a_4$ are 
+The basis $\{\ket{u_j}\}$ is the eigen-basis of operator $\tU$ defined by
+\begin{align*}
+    \tU = \sum_{j=0}^{d-2} \omega_{d-1}^j \ketbra{u_j}{u_j}.
+\end{align*}
+Note that in the standard basis, $\tU$ is
+\begin{align}
+    \label{eq:U}
+    \tU = \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}}.
+\end{align}
+The unitaries $\tU$ and $\tO$ are special because 
+they satisfy the relation $\tU \tO \tU\ct = \tO^r$.
+
+Here we only present what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$,
+since they are the key generators of $\Gamma$.
 \begin{align}
@@
     \label{eq:u1} \Psi(a_3) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ 
-    &+ \sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right) \Big]
+    &+ \sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{u_{d-1-k}}{u_k}\right) \Big]
     \end{aligned}
@@
 \end{equation}
-
 The tensor structure of the representations come from the construction of $\Psi$.
-These operators are important because they give representations of generators 
-$u$ and $o$ of $\Pg$ as $\Psi(a_1a_2) = \1_{W_2} \x \1_{W_2} \x O$
-and $\Psi(a_3a_4) = \1_{W_2} \x \1_{W_2} \x U$ where $O$ is defined in \cref{eq:O} and
-\begin{align}
-    \label{eq:u1u2}
-    U = \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}}.
-\end{align}
-The operators $U$ and $O$ satisfy the relation $UOU\ct = O^r$.
+These operators are important because $\Psi(a_1a_2) = \1_{W_2} \x \1_{W_2} \x \tO$
+and $\Psi(a_3a_4) = \1_{W_2} \x \1_{W_2} \x \tU$ where $\tO$ is defined in \cref{eq:O} and
+$\tU$ is defined in \cref{eq:U}.
+The unitaries $\Psi(a_1a_2)$ and $\Psi(a_3a_4)$ satisfy the following
+equation
+\begin{align*}
+    \Psi(a_3a_4) \Psi(a_1a_2) \Psi(a_4a_3) = \Psi(a_1a_2)^r,
+\end{align*}
+as $\tU \tO \tU\ct = \tO^r$.
 
@@
 %---------------------------------------------------
-\subsection{Formal definitions}
-\label{sec:gamma_def}
+\subsection{The game $\LS(r)$}
+\label{sec:lsr_def}
 %---------------------------------------------------
-We define the solution group of the linear system game $\LS(r)$ first, following the steps described in the previous subsection.
-Then we define the game $\LS(r)$.
-
 From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
@@
 Then each linear relation in $R$ can be translated to a linear equation.
-For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
+For example, the linear relation $f_0f_1f_2 = e$ is translated 
+to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
 $f_1g_1m_2 = J$ is translated to the equation
@@
 and $\mr := 14r + 62$ is the number of equations.  
-\carl{Since you are defining Alice's inputs to be subsets of S, why don't you just define Bob's inputs to be elements of S? Also, again you need to account that
-$J$ is an element of $S$.}
-\hfc{I think setting $\calY = S$ will cause confusion.
-You can see the forms of the equations in \cref{def:lsg_eq}.
-If I set the question set to be $S$, the reader will confuse the 
-linear equations with linear relation.
-I have moved $J$ out of $S$.}
 Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
-The answer sets are 
-\begin{align*}
-    \calA^{\LS} = (\Z_2)^{I_i} && \calB^{\LS} = \Z_2.
+Alice answer sets are 
+\begin{align*}
+    \calA^{\LS}_{I_i} = (\Z_2)^{I_i}
+\end{align*}
+for $1 \leq i \leq \mr$.
+Bob's answer set is
+\begin{align*}
+    \calB^{\LS} = \Z_2.
 \end{align*}
@@
 where $N(r) := 157r + 685$ is the total number of valid question pairs.
-We define $X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \}$, which is the set of all the valid answers of equation $i$.
+We define 
+\begin{align*}
+    X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \},
+\end{align*}
+which is the set of all the valid answers of equation $i$.
 Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
@@
 \end{theorem}
-\hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
-number of equation and variable pairs is $N(r)$ is of order $\Theta(r)$.}
-
-\hf{The ideal strategy of $\LS(r)$ is based on
-the representation $\Psi$ of $\Gamma$ defined in \cref{def:rep_gamma}
-of \cref{sec:rep_gamma}.
-We discuss the ideal strategy in in \cref{sec:tests}.
-Here we only highlight what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$, along
-with the important properties of the representation of these four generators,
-since they are the key generators of $\Gamma$.
-}
+As indicated in \cref{def:lsg}, the total
+number of question pairs is $N(r) = 157r + 685 = \Theta(r)$.
+
+The ideal strategy of $\LS(r)$ is based on
+the representation $\Psi$ of $\Gamma$ defined in \cref{def:rep_gamma}.
+We discuss the ideal strategy of $\LS(r)$ in \cref{sec:tests}
+when we introduce the ideal strategy of the full test.
 
@@
 In this section, we introduce the extended weighted CHSH test,
-which is going to be a component of the full test of \cref{sec:full_test}.
+which is going to be a component of the full test introduced in \cref{sec:full_test}.
 The ideal correlation for this test contains the ideal correlation that 
@@
 the ideal correlation of the extended weighted CHSH test easier,
-we fill the background of the self-testing property of the
+we fill in the background of the robust self-testing property of the
 general weighted CHSH inequality, $\I_\alpha$, first.
@@
 %----------------------------------------------------
-In this section, we show how the weighted CHSH inequality can be used to self-test $\ket{EPR}$ and Pauli operators robustly.
-Intuitively, robust self-testing means that if some quantum strategy achieves a value $\I_\alpha$ that is close to $\I_\alpha^{\max}$,
-then the shared state must be close to $\ket{EPR}$ and their observables are close to the rotated Pauli operators 
-defined in \cref{def:ideal},
-up to some local isometry.
-The formal statement is given in the theorem below. Since the proof uses the same techniques as in Ref.~\cite{bamps2015},
-we defer the proof till \cref{sec:selftest}, and we only list the key relations used in the proof because they will be reused in \cref{sec:main}.
+In this section, we discuss how the weighted CHSH inequality can be used to robustly self-test $\ket{EPR}$ and Pauli operators defined in \cref{def:ideal}.
+
+% Intuitively, robust self-testing means that if some quantum strategy achieves a value $\I_\alpha$ that is close to $\I_\alpha^{\max}$,
+% then the shared state must be close to $\ket{EPR}$ and their observables are close to the rotated Pauli operators 
+% defined in \cref{def:ideal},
+% up to some local isometry.
+The formal statement is given in the theorem below. Since the proof uses the same techniques as in \cite{bamps2015},
+we defer the proof till \cref{sec:w_chsh_proof}, and we only list the key relations that will be reused in \cref{sec:main} here.
 \begin{theorem}
@@
 	\begin{align*}
-		\| \Phi( M_x \x N_y \ket{\psi}) -\ket{junk} \x (\tM_x \x \tN_y) \ket{EPR}  \| = O(\frac{1}{\cos^2(\mu)\sin^{1/2}(\mu)}+
+		\| \Phi( M_x \x N_y \ket{\psi}) -\ket{junk} \x (\tM_x \x \tN_y) \ket{EPR}^{\x 2}  \| = O(\frac{1}{\cos^2(\mu)\sin^{1/2}(\mu)}+
 		\frac{1}{\sin(\mu)^{3/2}})) \sqrt{\epsilon}
@@
 \end{theorem}
-We follow the convention used in Ref.~\cite{bamps2015},
+We follow the convention used in \cite{bamps2015},
 which defines
@@
 \end{align*}
-Note that in \cref{sec:main}, we take $\mu = \pi/d$, so
-when we derive the error terms below, we only consider $\mu$ 
-that is close to $0$.
-The key relations that will be reuse are
-\begin{align}
-	\label{eq:za-zb}& Z_A\ket{\psi} \appd{O( \sqrt{\mu} \se)} Z_B\ket{\psi},\\
-	\label{eq:xa-xb}&X_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B \ket{\psi}, \\
-	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B(\1-Z_A) \ket{\psi},\\
-	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} Z_B(\1-X_A) \ket{\psi},\\
-	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} -X_AZ_A \ket{\psi},\\
-	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{O(\frac{\se}{\mu^{3/2}})} -X_BZ_B \ket{\psi},
-\end{align}
-where \cref{eq:zaxaxbzb} can be derived from \cref{eq:za-zb}, \cref{eq:xa-xb} and \cref{eq:zaxa}.
+The key relations that will be reused are
+\begin{align}
+% 	\label{eq:za-zb}& Z_A\ket{\psi} \appd{O( \sqrt{\mu} \se)} Z_B\ket{\psi},\\
+% 	\label{eq:xa-xb}&X_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B \ket{\psi}, \\
+% 	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B(\1-Z_A) \ket{\psi},\\
+% 	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} Z_B(\1-X_A) \ket{\psi},\\
+% 	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} -X_AZ_A \ket{\psi},\\
+% 	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{O(\frac{\se}{\mu^{3/2}})} -X_BZ_B \ket{\psi},
+\label{eq:za-zb}& Z_A\ket{\psi} \appd{\frac{\sqrt{s\epsilon}}{c}} Z_B\ket{\psi},\\
+	\label{eq:xa-xb}&X_A\ket{\psi} \appd{\frac{\sqrt{\epsilon}}{\sqrt{s}}} X_B \ket{\psi}, \\
+	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{\frac{c+1}{c\sqrt{s}} \se} X_B(\1-Z_A) \ket{\psi},\\
+	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{ \frac{s+1}{c\sqrt{s}} \se} Z_B(\1-X_A) \ket{\psi},\\
+	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{\frac{1+c+s}{c\sqrt{s}} \se} -X_AZ_A \ket{\psi},\\
+	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{\frac{2s^2+cs+c+s}{cs\sqrt{s}} \sqrt{\epsilon}} -X_BZ_B \ket{\psi}.
+\end{align}
+We keep the exact error terms so that some
+of the substitution steps in \cref{sec:main} are 
+easier to follow.
 
@@
 %-------------------------------------------
+In this subsection, we first give the definition of the 
+extended weighted CHSH test, then we discuss the ideal strategy of it.
+We defer the ideal correlation of this test til \cref{sec:cor}
+as it will be presented as a part of the ideal correlation of the full test.
 \begin{definition}
@@
     \end{align*}
-    The probability distribution over the question pairs is uniform.
+    The probability distribution over all the question pairs 
+    $(x,y) \in \calX^{\EXT} \times \calY^{\EXT}$ is uniform.
 \end{definition}
@@
 
-Recall the Hilbert space $W_{d-1}$ defined in \cref{sec:gamma_def}. 
+Recall the Hilbert space $W_{d-1}$ defined in \cref{eq:basis}. 
 To make the shared state and the observables of the ideal strategy have
-simpler forms, we introduce the third basis of $W_{d-1}$: $\{ \ket{j} \}_{j=1}^{d-1}$, \hf{which is defined by}
+simpler forms, we introduce the third basis of $W_{d-1}$: $\{ \ket{j} \}_{j=1}^{d-1}$, which is defined by
 \begin{align*}
@@
 
-We define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$.
+To introduce the projectors, 
+we first define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$.
 The corresponding projective measurements are $\Pi_V$ and $\Pi_{V^\perp}$. Note that $V$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$.
@@
 This is the reason behind naming this test the extended weighted CHSH test.
-It is also the reason behind having Alice and Bob agreeing on the subspace $V$ 
-by using the other three questions.
+It is also the reason behind having Alice and Bob agreeing on the subspace $V$.
 Before introducing the measurements, 
-we define some basis states of $V$
+we need to define some basis states of $V$
 \begin{align*}
@@
 
-We will present the ideal correlation of the extended weighted CHSH test
-in \cref{sec:cor} as part of the full correlation.
+% We will present the ideal correlation of the extended weighted CHSH test
+% in \cref{sec:cor} as part of the full correlation.
 
@@
 
-The first component of the full test is $\LS(r)$ defined in
-\cref{def:lsg}.
+The first component of the full test is $\LS(r)$ (\cref{def:lsg}).
 The ideal strategy of $\LS(r)$ follows the representation $\Psi$ of $\Gamma$ (\cref{def:rep_gamma}).
-Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}. 
+Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{eq:basis}. 
 In the ideal strategy Alice and Bob share the state 
@@
 The third component is a commutation game.
-Our commutation game is the based on the commutation test used in Ref.~\cite{coladan2017verifier}.
+Our commutation game is based on the commutation test used in \cite{coladan2017verifier}.
 The goal of the commutation game is to make sure that some
-of Alice's binary observables for the other two tests 
-commute with each other when acting on the shared state,
-so we reuse questions and answers from the two other tests.
+of Alice's binary observables for $\LS(r)$ 
+commute with her observable for the extended weighted CHSH test,
+when acting on the shared state.
+So we reuse questions and answers from the two other components
+of the full test.
 
@@
 \begin{align*}
-    \calX^{\COMM} = \{\nr+1, \nr+2, f_0, f_2, g_0, g_2\}.
+    \calX^{\COMM} = \{\nr+1, \nr+2, x(f_0), x(f_2), x(g_0), x(g_2)\}.
 \end{align*}
@@
 common question.
-We remark that if Alice's question is to assign a value to some variable of $\LS(r)$,
-the label of a equation that contains this variable is given 
-to Alice and the referee checks the bit corresponding to this
-variable in Alice's answer. This is equivalent to asking 
-Alice to measure an observable for the variable.
-
-We defer the ideal strategy for this test till next subsection because the ideal
-strategy to pass the two tests above can pass this test as well.
+% We remark that if Alice's question is to assign a value to some variable of $\LS(r)$,
+% the label of a equation that contains this variable is given 
+% to Alice and the referee checks the bit corresponding to this
+% variable in Alice's answer. This is equivalent to asking 
+% Alice to measure an observable for the variable.
+
+We defer the ideal strategy for this test till the next subsection because the ideal
+strategy for the other two tests above can win this game as well.
 
@@
 Define answer sets $\calA_x^{\EXT'}$ for each $x \in \calX^{\EXT'}$
-by setting 
+by 
 \begin{align*}
@@
     \begin{cases}
-    \Z_2^3 &\text{ if } x \in \calX^{\LS} \\
+    \calA_x^{\LS} &\text{ if } x \in \calX^{\LS} \\
     \calA_x^{\EXT'} &\text{ if } x \in \calX^{\EXT'} \\
@@
 \end{align*}
-Define $N$ to be the total number of question pairs with nonzero probability 
-of the three components of the full test.
+Define 
+\begin{align*}
+    N :=  N(r) + 25 + 16 = 157r + 726.
+\end{align*}
 The question distribution of the full test, $\pi: \calX \times \calY \rightarrow \R$ is defined by
@@
     \frac{1}{N} & \text{ if } (x,y) \in \calX^{\EXT'} \times \calY^{\EXT'}\\
-    \frac{1}{N} & \text{ if } (x,y) \in \calX^{\COMM} \times \calY^{\COMM} \text{ and } \pi^{\COMM}(x,y) > 0 \\
+    \frac{1}{N} & \text{ if } (x,y) \in \calX^{\COMM} \times \calY^{\COMM} 
+    \text{ and } \pi^{\COMM}(x,y) > 0 \\
     0 & \text{ otherwise}.
@@
 the extended weighted CHSH test.
-Recall the subspace $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}.
+Recall the subspace $W_{d-1}$ and $W_2$ defined in \cref{eq:basis}.
 The shared state of the ideal strategy is
@@
 \begin{align*}
-    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_1) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_1^0|_V - \tP_1^1|_V) \\
-    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_2) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_2^0|_V - \tP_2^1|_V),
+    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_1) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_1^0 - \tP_1^1) \\
+    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_2) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_2^0 - \tP_2^1),
 \end{align*}
@@
 
-Alice's projectors for the other questions of $\calX^{\EXT'}$ are
+Recall the ideal projectors $\tP_x^a$ and $\tQ_y^b$ for the extended 
+weighted CHSH test defined in \cref{sec:ext_w_chsh}.
+Alice's projectors for the question $x \in \{0, \nr+1, \nr+2\}$ of $\calX^{\EXT'}$ are
 \begin{align*}
@@
 for each $a \in \calA^{\EXT'}_x$.
-Bob's projectors for the other questions of $\calY^{\EXT'}$ are 
+Bob's projectors for the question $y \in \{0, \nr+1, \nr+2\}$ of $\calY^{\EXT'}$ are 
 \begin{align*}
@@
     Define $S' = \{f_0, f_1, f_2, g_0, g_1, g_2, m_0, m_1, m_2\} \subset S$. Notice that for each $s \in S'$, both $\tM(s)$ and $\tN(s)$ act
-    trivially on $W_{d-1}$, so we omit the verification that 
+    trivially on $W_{d-1}$, so we omit the verification about 
     $\tM(s)\tN(s) \ket{\tpsi} = \ket{\tpsi}$ for each $s \in S'$
@@
 	Next, we notice that each $s \in S$ can be expressed as the 
-	product of a sequence of generators in $S'$ and $a_1, a_2, a_3, a_4$, so
+	product of a sequence of generators in $S'$ and $a_1, a_2, a_3, a_4$
+	following the relations in $R$, so
 	to prove \cref{eq:mn_preserve}, it suffices to prove that it 
@@
     \end{align*}
-    Then using \cref{eq:u2} we can deduce that $\Psi_0(a_4)$ acts on $\ket{x_{r^j}}$ by
-    \begin{align*}
-        \Psi_0(a_4) \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} \tM(a_4) \left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
+    Then using the expression of $\Psi_0(a_4)$ from \cref{def:rep_g0},
+    we can deduce that
+    \begin{align*}
+        \Psi_0(a_4) \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} \Psi_0(a_4) \left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
         \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
@@
     \end{align*}
+    Note that the expression of $\Psi_0(a_4)$ can also be found in
+    \cref{eq:u2}, as $\Psi(a_4) = \1_{W_2} \x \1_{W_2} \x \Psi_0(a_4)$.
     Consequently, we can show that $\Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ 
@@
     \begin{align*}
-        \Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \Psi_0(a_4)\x  \Psi_0(a_4) \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
-        = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\tpsi}^{\EXT},
+        \Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} &= \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \Psi_0(a_4)\x  \Psi_0(a_4) \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} \\
+        &= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}}\\ &=\ket{\tpsi}^{\EXT},
     \end{align*}
@@
 To help readers to understand the proofs in \cref{sec:main} better, 
-parts of the full correlation is given in the tables below.
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{|c|c||c|c|}
-\hline
-\multicolumn{2}{|c|}{} &
-\multicolumn{2}{|c|}{$x=0$}\\
-\cline{3-4}
-\multicolumn{2}{|c|}{} &$a = 0$ & $a = 2$ \\
-\hline
-\hline
-\multirow{2}{*}{$y = 0$} & $b = 0$ & $2/(d-1)$ & $0$ \\
-\cline{2-4}
-&$b=2$ & $0$ & $(d-3)/(d-1)$ \\
-\hline
-\end{tabular}
-\caption{The correlation for $x=y=0$.}
-\end{center}
-\end{table}
+parts of the full correlation are given in the tables below.
 
@@
 \hline
-\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
-& $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
+\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{20}{00}$ 
+& $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{20}{10}$ \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
-&  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
+&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{20}{00}$ 
+&  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{20}{10}$  \\
 \hline
-\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
-$ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
+\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{20}{01}$ & 
+$ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{2 0}{11}$  \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
-$ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
+&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{20}{01}$ &  
+$ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{20}{11}$ \\
 \hline
@@
 \end{center}
-\caption{The correlation for $x \in \{n+1, n+2\}$ and $y \in \{1,2\}$.}
+\caption{The correlation for $x \in \{\nr+1, \nr+2\}$ and $y \in \{1,2\}$.}
 \label{tb:chsh}
 \end{table}
-We don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ for all possible $x$,$y$ 
+We don't explicitly calculate the conditional probabilities of the form $\pr{20}{xy}$ when $x \in \{\nr+1, \nr+2\}$ and $y \in \{1, 2\}$ 
 because they are irrelevant.
 Note that when $x \in \{1,2\}$ and $y \in \{\nr+1, \nr+2\}$, the correlation table is 
-the transpose of Table~\ref{tb:chsh}, so we omit it here.
+very similar to Table~\ref{tb:chsh}, so we omit it here.
 
@@
 \end{center}
-\caption{The correlation for $x ,y\in\{\nr+1,\nr+2, \ast\} $.}
+\caption{The correlation for $x ,y\in\{0, \nr+1,\nr+2\} $.}
 \end{table}
@@
 \end{center}
-\caption{The correlation for the commutation test between $f_0$ and $\nr+1$.}
+\caption{The correlation for the commutation test for questions $x(f_0)$ and $\nr+1$.}
 \label{tbl:comm}
 \end{table}
-The correlation table for the other seven commutation games are similar.
+The correlation tables for the other seven pairs
+of questions are similar.
 
@@
 correlation $\fC(d,r)$ approximately and 
-prove that the shared state of $\bS$ must be close to the state $\ket{EPR}^{\x 2} \x \ket{\EPR{d-1}}$
+prove that the shared state of $\bS$ must be close to the state $\ket{\tpsi}$
 up to some local isometry.
@@
 \begin{definition}
-	For a correlation $\tilde{C} = (\tpr{ab}{xy})$,
+    Let $\calX, \calY$ be input alphabets,
+    $\{\calA_x\}_{x \in \calX}, \{\calB_y\}_{y \in \calY}$
+    be families of output alphabets.
+	For a correlation $\tilde{C} = (\tpr{ab}{xy})$
+	with $(a,b) \in \calA_x \times \calB_y$ and $(x,y) \in \calX \times \calY$,
+	and a distribution $\pi$ over all the $(x,y) \in \calX \times \calY$,
 	we say a quantum strategy $\bS = (\ket{\psi}, \{M_x^a\}, \{N_y^b\})$
-	is an $\ep$-approximate quantum strategy of $\tilde{C}$, 
+	is an $\ep$-approximate quantum strategy of $\tilde{C}$
+	with respect to the distribution $\pi$, 
 	if it produces the correlation
@@
 	\label{eq:expect}
-	E_{(x,y)} \sum_{ab} \abs{\pr{ab}{xy} - \tpr{ab}{xy}} \leq \ep.
+	\E_{(x,y) \sim \pi} \left[\sum_{ab} \abs{\pr{ab}{xy} - \tpr{ab}{xy}}\right] \leq \ep.
 	\end{align}
 \end{definition}
-In our full test, the probability distribution over all the question pairs $(x,y)$ is uniform.  \carl{[You need to address that in the definition itself (otherwise it's not a complete definition).]}
-\hfc{I think I did define the question distribution in \cref{def:full_test}. }
+In our full test, the probability distribution over question pairs is $\pi$ given in 
+\cref{def:full_test}.
+In the rest of this section, when we say some strategy can approximate
+$\fC(d,r)$, we mean that the approximation is with respect to 
+this distribution $\pi$.
+
 The number of all the possible question pairs is 
@@
 
-In the next three subsections, we analyze the implication of an approximate strategy for the 
-three components introduced in \cref{sec:full_test}.
+In the next three subsections, we analyze the implication of an approximate strategy 
+for the correlations of the 
+three components introduced in \cref{sec:tests}.
 
@@
 %------------------------------------------------------------------------------------------
-\hf{In this subsection, we study the implications of a strategy that can win $\LS(r)$ with probability close to $1$. We prove a series of 
+In this subsection, we study the implications of a strategy that can win $\LS(r)$ with probability close to $1$. We prove a series of 
 propositions, which lead us to \cref{prop:lct_adv}.
-\Cref{prop:lct_adv} is a key step of the self-testing proof in \cref{sec:self-test}.}
+\Cref{prop:lct_adv} is a key step of the self-testing proof in \cref{sec:self-test}.
 
@@
 labels an equation and $x(s)$ is a variable for some $s \in I_i$. 
-For simplicity, we denote 
+We denote 
 Alice's observable for variable $x(s)$ in equation $i$ by $M_i(s)$ and
@@
 	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	\hf{Define $M(s) := M_i(s)$ where 
+	Define $M(s) := M_i(s)$ where 
 	$i$ is the smallest among all $i$'s
-	such that $x(s) \in I_i$.}
+	such that $x(s) \in I_i$.
 	Then, 
@@
 		&M(s) N(s) \ket{\psi} \appd{O(\sr\se)} \ket{\psi} \\
-		&\Pi_{s \in I_i} M(s) \ket{\psi} \appd{O(\sr\se)}(-1)^{c(i)} \ket{\psi}.
-	\end{align}
+		&\Pi_{s \in I_i} M(s) \ket{\psi} \appd{O(\sr\se)}(-1)^{c(i)} \ket{\psi},
+	\end{align}
+	for all $s \in S$.
 \end{proposition}
-\carl{[This proposition doesn't seem well-phrased --- it doesn't seem useful  to simply claim the existence of binary observables $M ( s )$ without specifying how they are related to the strategy $S$.]}
-\hfc{How about now?}
 
 \begin{proof}
-The condition that $(\tpr{\ba b}{i s})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
-\begin{align*}
-\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{is} = 1
+The condition that $(\tpr{\ba b}{I_i s})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
+\begin{align*}
+\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{I_i s} = 1
 \end{align*}
 for all $i = 1 \dots \mr$.
-It has been shown in Ref.~\cite{slofstra2017} that 
-\begin{align*}
-	\bra{\psi} M_i(s) N(s) \ket{\psi} &= 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{ij} -1.
-\end{align*}
+We also know that the shared state $\ket{\psi}$ and observables $M_i(s)$
+and $N(s)$ of $\bS$ satisfy the relation
+\begin{align*}
+	\bra{\psi} M_i(s) N(s) \ket{\psi} &= 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{I_i s} -1,
+\end{align*}
+as proved in \cite{slofstra2017}.
 Using the fact that $\bS$ approximates the winning correlation of $\LS(r)$, 
-we can get that
+we can further see that
 \begin{align*}
@@
 \end{align*}
-\carl{[The previous sentence \& equation do not make sense to me.]}
-\hfc{Fixed.}
-Since $M_i(s)$ and $N(s)$ are binary observables, we know that
+Since $M_i(s)$ and $N(s)$ are binary observables, the equation above
+implies that
 \begin{align*}
@@
 \end{align*}
-for all $1 \leq i \leq \mr$ and $s \in S$.
-We define $M(s) := M_{i}(s)$ for the smallest $i$ such that $ s \in I_i$, then 
+for each $1 \leq i \leq \mr$ and generator $s$ of
+$\Gamma$.
+Recall that $M(s) := M_{i}(s)$ for the smallest $i$ such that $ s \in I_i$.
+Therefore, 
 \begin{align*}
@@
 	&\norm{ M_{i}(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M(s_3) \ket{\psi}}\\
-	\leq & \norm{M_{i}(s_1)M_{i}(s_2)M_{i}(s_3)\ket{\psi} - M(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi}}+
-	\norm{M(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M_{i}(s_3) \ket{\psi}} +\\
-	&\norm{M(s_1)M(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M(s_3) \ket{\psi}}\\
-	\leq &3O(\sr\se) = O(\sr\se).
-\end{align*}
+	\leq & \norm{M_{i}(s_1)M_{i}(s_2)M_{i}(s_3)\ket{\psi} - M(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi}}\\
+	&+ \norm{M(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M_{i}(s_3) \ket{\psi}} \\
+	&+\norm{M(s_1)M(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M(s_3) \ket{\psi}}\\
+	\leq &3O(\sr\se) = O(\sr\se),
+\end{align*}
+where we bound each term in line $2,3$ and $4$ by \cref{lm:sub}.
 Hence we can conclude that 
@@
 
-To make the following derivations easier, we introduce the following terminology.
+To make the following derivations easier to understand, 
+we introduce a new terminology.
 \begin{definition}
@@
     be two sequences of $S$.
-    Define a relation $r$, \hf{whose equation form} is $\Pi_{i=1}^n s_i = \Pi_{j=1}^m s'_j$.
+    Define a relation $r$, whose equation form is $\Pi_{i=1}^n s_i = \Pi_{j=1}^m s'_j$.
     We say operators $\{M(s) : s \in S\}$ $\ep$-approximately satisfy the relation
@@
     \end{align*}
-\carl{[Technically, the word ``relation'' refers to an element of the free group, not to an equation between elements of the free group, so you need to write this in a way that accounts for that.
-It's a minor issue but worth addressing.]}
-\hfc{How about this way?}
 \end{definition}
-In other words, \cref{prop:lct_base} is equivalent to the following proposition.
+Using the new terminology, \cref{prop:lct_base} can be rephrased 
+as the following proposition.
 \begin{proposition}
@@
 	Then the observables $\{ M(s) \}_{s \in S}$ and
-	$\{N(s)\}_{s \in S}$ $O(\sr \se)$-approximately satisfy
-	each relation $r \in R$ on the shared state $\ket{\psi}$, 
-	where $S$ and $R$ are defined in the definition of $\Gamma$ 
-	(\cref{def:gamma}).	
+	$\{N(s)\}_{s \in S}$ defined in \cref{prop:lct_base}, 
+	$O(\sr \se)$-approximately satisfy
+	each relation $t \in R$ on the shared state $\ket{\psi}$, 
+	where $S$ is the generator set of
+	$\Gamma$ and
+	and $R$ is the relation set of $\Gamma$.	
 \end{proposition}
-\hf{Recall that the group $\Pg_1$ (\cref{def:g1}) is embedded in $\Gamma$.  
-For details of the embedding, we refer to \cref{sec:embedding}.}
+Recall that the group $\Pg_1$ (\cref{def:g1}) is embedded in $\Gamma$,
+as proved in \cref{prop:g1gamma}. 
 Following the embedding procedure, we can prove the next proposition.
@@
 \cref{prop:lct_group}, $O(\sr\se)$-approximately satisfy
-	each relation $r \in R_1$ on $\ket{\psi}$, 
+	each relation $t \in R_1$ on $\ket{\psi}$, 
 	where $S_1$ is the generator set of $\Pg_1$
@@
 
-\carl{[I don't think it's helpful
-to the reader to phrase this result in terms of $\Pg_1$, given that you never wrote out $\Pg_1$ in the main text.
-I think you should write this in such a way that a reader who hasn't read the appendix can follow what you're doing.
-(One possibility is to just prove the relations that you need, step by step, and then just add comments referring to how what you are doing parallels your proofs in the appendix.]}
-\hfc{We need all the relations from $\Pg_1$ (\cref{def:g1}) to recover relations of $\Pg_0$ (\cref{def:g0})
-so it is not possible to write out each one of them. 
-What I am doing is proving one of them and comment that the rest of them require the same argument.
-On the other hand, I don't think it is important for the reader to know the relations of $\Pg_1$
-or $\Pg_0$. The only relation that will feature in the self-test proof is the relation $UOU\ct = O^r$.}
-
 \begin{proof}
-    First, we prove 
+    We prove 
     \begin{align}
@@
     to demonstrate the techniques.
-    From the fact that Alice's observables $O(r\se)$-approximately satisfy the linear equations, we can get that
+    From the fact that Alice's observables $O(\sr\se)$-approximately
+    satisfy the linear relations of $\Gamma$, we can get that
     \begin{align*}
@@
     \end{align*}
-    Then we show how to expand $M(f_0)M(b_1)M(f_0)\ket{\psi}$
-    with the three equations above. The trick is to flip some 
-    operators to Bob's side using the relation $M(s) \ket{\psi} \appd{O(\sr \se)} N(s)\ket{\psi}$.
+    Then we expand $M(f_0)M(b_1)M(f_0)\ket{\psi}$
+    using the three equations above and \cref{lm:sub},
     \begin{align*}
         M(f_0)M(b_1)M(f_0) \ket{\psi} 
-        &\appd{O(\sr \se)}M(f_0)M(b_1)M(p_{1,3})M(p_{1,4}) \ket{\psi} \\
-        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})M(f_0)M(f_2)M(p_{1,1}) \ket{\psi} \\
-        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)M(f_0) \ket{\psi} \\
-        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)M(f_1)M(f_2) \ket{\psi} \\
-        & \appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)N(f_2)N(f_1) \ket{\psi} \\
-        &= N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_1) \ket{\psi} \\
-        & \appd{O(\sr \se)} M(f_1)M(p_{1,1})M(p_{1,3})M(p_{1,4}) \ket{\psi}
-    \end{align*}
-    In the rest of the proof, we skip the steps of flipping observables from Alice to Bob's side and then flip back.
+        &\appd{O(\sr \se)}M(f_1)M(f_2)M(b_1)M(f_0) \ket{\psi} \\
+        &\appd{O(\sr \se)} M(f_1)M(f_2)M(f_2)M(p_{1,1})M(f_0) \ket{\psi} \\
+        & = M(f_1)M(p_{1,1})M(f_0) \ket{\psi} \\
+        & \appd{O(\sr \se)} M(f_1)M(p_{1,1})M(p_{1,3})M(p_{1,4}) \ket{\psi}.
+    \end{align*}
+    In the rest of the proof, we skip steps of applying \cref{lm:sub}.
+    Next, we can simplify $M(f_0)M(b_1)M(f_0) \ket{\psi}$ as
     \begin{align*}
@@
     $M(c_1)M(p_{1,4})M(p_{1,5})\ket{\psi} \appd{O(\sr \se)} \ket{\psi}$.
-    The proof for the other relations are similar.
+
+    The derivation of other relations in $R_1$ from relations in $R$
+    involves the same number of substitutions and uses similar techniques, so we omit it here.
 \end{proof}
-Note that essentially the proof above follows the proof of 
-\cref{prop:g1gamma}. Then we can follow the proof of \cref{prop:g0g1}
+Essentially the proof above follows the proof of 
+\cref{prop:g1gamma},
+so we can follow the proof of \cref{prop:g0g1}
 to prove the next proposition.
@@
 \cref{prop:lct_group}, $O(\sr \se)$-approximately satisfy
-	each relation $r \in R_0$ on the shared state $\ket{\psi}$, 
+	each relation $t \in R_0$ on the shared state $\ket{\psi}$, 
 	where $S_0$ is the generator set of $\Pg_0$
@@
 the proof of \cref{prop:g0},
-we can prove the following proposition.
+we can prove the next lemma.
 \begin{lemma}
@@
 $O(r^{3/2} \se)$-approximately satisfy the relation 
-$(a_3a_4)(a_1a_2)(a_4a_3) = (a_1a_2)^r$ on the shared state $\ket{\psi}$.
+\begin{align}
+    \label{eq:a1a2r}
+    (a_3a_4)(a_1a_2)(a_4a_3) = (a_1a_2)^r
+\end{align}
+on the shared state $\ket{\psi}$.
 The derivation follows the proof of \cref{prop:g0}.
 The $O(r^{3/2}\se)$ approximation error comes from the fact that 
-the derivation has $\Theta(r)$ steps, where each step substitutes in
-a different relation of $R_0$, 
-so we have
+the derivation of \cref{eq:a1a2r} has $\Theta(r)$ substitution steps, where each substitutes uses
+a different relation of $R_0$. 
+So we have
 \begin{align}
@@
 \end{align*}
-where from the second to the last line we repeat the process of applying \cref{eq:ls_comm_rel} 
+where from the second last to the last line we repeat the process of applying \cref{eq:ls_comm_rel} 
 and the relation $(M(a_1)M(a_2))^r \ket{\psi} \appd{O(r^{3/2}\se)} (N(a_1)N(a_2))^r \ket{\psi}$, $r^n$ times.
-In summary, we have 
+In short, we have 
 \begin{align}
@@
 
-If we define $O_A := M(a_1)M(a_2)$ and $U_A := M(a_3)M(a_4)$, then
-the conclusion of \cref{prop:lct_adv} can be rewritten as 
+We define 
+\begin{align}
+    \label{eq:uaoa} & O_A := M(a_1)M(a_2) && U_A := M(a_3)M(a_4) \\
+    \label{eq:ubob} & O_B := N(a_1)N(a_2) && U_B := N(a_3)N(a_4).
+\end{align}
+The conclusion of \cref{prop:lct_adv} can be rewritten as 
 \begin{align*}
@@
 \end{align*}
-On Bob's side, we also define $O_B = N(a_1)N(a_2)$ and $U_B = N(a_3)N(a_4)$, 
-and the similar relation holds.
-
-The other relations that are embedded in $\Gamma$ are 
+On Bob's side, the similar relation holds.
+
+The other key relations that are embedded in $\Gamma$ are 
 $f_0g_0 = Jg_0f_0$ and $f_2g_2 = Jg_2 f_2$.
@@
 \end{proposition}
-Recall all the relations in \cref{eq:mg1,eq:mg2} are embedded in the
-six Magic Square relations $R_{MS}$ of $\Gamma$ (\cref{def:gamma}), 
-so this proposition can be proved with the same techniques used in the proof of \cref{prop:lct_group}.
+Following the substitution steps to prove \cref{eq:mg1} and \cref{eq:mg2} in the proof of \cref{prop:g1gamma},
+this proposition can be proved with the same techniques used in the proof of \cref{prop:lct_group}.
+
 %------------------------------------------------------------------------------------------
-\subsection{Implication of approximating the extended weighted CHSH test}
+\subsection{Implication of the extended weighted CHSH test}
 \label{sec:imp_chsh}
@@
 used in the self-testing proof in \cref{sec:self-test}.
-Note that in the following proofs, the observables $M_1$ and $M_2$ are
-equivalent to $M(a_1)$ and $M(a_2)$ respectively, because questions $1$ 
-and $2$ are equivalent to questions $x(a_1)$ and $x(a_2)$ in the full test.
+
+We will work with a strategy $\bS$ that can approximate
+$\fC(d,r)$, which contains
+the ideal correlation of the extended weighted CHSH test.
+About the notation,
+for $(x,y) \in \calX^{\EXT} \times \calY^{\EXT}$ and $(a,b) \in \calA_x^{\EXT} times \calB_y^{\EXT}$, 
+Alice and Bob's projectors are denoted 
+by $M_x^a$ and $N_y^b$,
+as illustrated in \cref{sec:prelim}.
+Since the two answers for question $1$ and $2$ are $0$ and $1$, 
+we denote Alice and Bob's binary observables for these two questions
+by $M_1, M_2$ and $N_1, N_2$ respectively.
+Note that the observables $M_1 \equiv M(a_1)$ and $M_2 \equiv M(a_2)$,
+where $M(a_1)$ and $M(a_2)$ are used in $\LS(r)$,
+because questions $1$ and $2$ are equivalent to questions $x(a_1)$ and $x(a_2)$ in the full test.  
 Similarly, on Bob's side, we have $N_1 \equiv N(a_1)$ and $N_2 \equiv N(a_2)$.
 For simplicity, in this subsection, we
-use $M_1, M_2$ and $N_1, N_2$.
+use $M_1, M_2$ and $N_1, N_2$ only.
+
 \begin{proposition}
@@
 Recall that the implication of $\bS$ being an $\ep$-approximate strategy is that 
-$\pr{ab}{xy} \appd{O(r \ep)} \tpr{ab}{xy}$ for all question 
-pair $(x,y)$ and associating answer pair $(a,b)$.
+$\pr{ab}{xy} \appd{O(r \ep)} \tpr{ab}{xy}$ for each question 
+pair $(x,y)$ and its associating answer pair $(a,b)$.
 From the correlation, we can observe that
@@
 \end{align*}
-which implies that 
+The equations above imply that 
 \begin{align*}
@@
 	\end{align}
-	Then $\bS$ induces two $O(d \sr \se)$-approximate strategies of the ideal correlation that achieves $\I_{\cot(-\pi/d)}^{\max}$, which are
+	Then,
 	\begin{align}
@@
 	\end{align}
+	are two $O(d \sr \se)$-approximate strategies of the ideal correlation that achieves $\I_{\cot(-\pi/d)}^{\max}$.
 \end{proposition}
-
+Note that here we only consider $\ep$ small enough such that 
+$\norm{M_0^0\ket{\psi}} > 0$.
 \begin{proof}
-To prove that $\bS_1$ achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, we need to examine terms of the form
-$\bra{\psi} M_0^0 M_{x}^a N_y^b M_0^0\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0,1$,
-which relate to $\bra{\psi} M_x^a N_y^b \ket{\psi}$ as follows,
+We first prove that $\bS_1$ is an 
+$O(d \sr \se)$-approximate strategies of $\I_{\cot(-\pi/d)}^{\max}$.
+This step requires examining the terms of the form
+$\bra{\psi} M_0^0 M_{x}^a N_y^b M_0^0\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0,1$.
+We find that these terms relate to $\bra{\psi} M_x^a N_y^b \ket{\psi}$ by
 \begin{align*}
@@
 $M_x^0 M_x^2 = 0$ for the relevant values of $(x,y,a,b)$.
-This means that if Alice and Bob share state $M_0^0 \ket{\psi}/\norm{M_0^0 \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$,
-they get conditional probability
+
+To demonstrate the effect of this relation, we use an example.
+If Alice and Bob share state $M_0^0 \ket{\psi}/\norm{M_0^0 \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$,
+then
 \begin{align*}
@@
 	\appd{O(d r \ep)}
-	\frac{\cos^2(-\pi/2d)}{2}.
-\end{align*} 
-because
+	\frac{\cos^2(-\pi/2d)}{2},
+\end{align*} 
+where the first error term is derived from
 \begin{align*}
@@
 \end{proof}
-Based on \cref{prop:chsh_base,prop:s1s2}, we identify a special component of $\ket{\psi}$, whose special properties are summarized
-in the proposition below. In the next lemma, we prove that this special component can be used to approximate $\ket{\psi}$. 
+
+Based on \cref{prop:chsh_base,prop:s1s2}, we identify a special sub-normalized state $\ket{\psi_1}$, 
+\begin{align}
+    \label{eq:psi1}
+	\ket{\psi_1} =1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi}.
+\end{align}
+The special properties of $\ket{\psi_1}$ are summarized
+in the propositions below. 
+Based on the properties of $\ket{\psi_1}$, we will prove that $\ket{\psi_1}$ can be used to approximate $\ket{\psi}$
+in \cref{lm:decomp_psi}.
 \begin{proposition}
-    \label{prop:psi1}
-	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.
-	Then, the state
-	\begin{align}
-		&\ket{\psi_1} =1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi}.
-		%&\ket{\psi_2} = 1/2(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)  \ket{\psi} \\
-		%&\ket{\psi_4} =1/2(N_{\nr+1}^1 + iN_{\nr+2}N_{\nr+1}^1 -iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}
-	\end{align}
-	satisfies the following properties
+    \label{prop:psi1_norm}
+	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $\ket{\psi_1}$ be as defined in
+	\cref{eq:psi1}.
+	Then, 
 	\begin{align}
@@
 	 %\label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
-	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(\sr\se)} 1/(d-1),\\
-	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\qr \qe/\sd)} \omega_d\ket{\psi_1} 
-	 && N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_1} \\
-	 \label{eq:psi1_eig2} &M_1M_2 \ket{\psi_1} \appd{O(\sd\qr \qe)} \omega_d^{-1} \ket{\psi_1}
-	 && M_2M_1 \ket{\psi_1} \appd{O(\sd\qr \qe)} \omega_d \ket{\psi_1}.
+	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(\sr\se)} 1/(d-1).
 	\end{align}
 \end{proposition}
-In this proof, we use the notation $c := \cos(\pi/d)$ and $s := \sin(\pi/d)$.
 \begin{proof}
-    \textbf{To prove \cref{eq:psi1_norm}}, 
-	we start by expanding the inner product
+	We start by expanding the inner product
 	\begin{align*}
@@
 	Similarly, we have $\bra{\psi}M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{ O(\sr \se)} 0$.
-	Hence, we get 
+	Hence, from the ideal correlation, we get 
 	\begin{align}
@@
 	\end{align}
+\end{proof}
+\begin{proposition}
+    \label{prop:psi1_eig1}
+	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $\ket{\psi_1}$ be as defined in
+	\cref{eq:psi1}.
+	Then,
+	\begin{align}
+	    \label{eq:psi1_eig1} 
+	    &N_1N_2 \ket{\psi_1} \appd{O(\qr \qe/\sd)} \omega_d\ket{\psi_1}.
+	    %&N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_1}.
+	\end{align}
+\end{proposition}
+The idea of this proof is to apply the general results in \cref{sec:chsh}
+to the strategy $\bS_1$,
+so in the first half of the proof, we can derive how $N_1$ and $N_2$
+act on the state $M_{\nr+1}^0 \ket{\psi}$ and $M_{\nr+1}^1 \ket{\psi}$.
+In the second half, we combine $M_{\nr+1}^0 \ket{\psi}$ and $M_{\nr+1}^1 \ket{\psi}$ in a way and show that it is an eigenvector of $N_1N_2$.
+It turns out that this combination of $M_{\nr+1}^0 \ket{\psi}$ and $M_{\nr+1}^1 \ket{\psi}$
+is closely related to $\ket{\psi_1}$.
+We show all the calculations to make the proof easier to read. 
+\begin{proof}
+	Following the convention in \cref{sec:chsh}, we define
+	\begin{align*}
+		& c := \cos(\frac{\pi}{d}) && s := \sin(\frac{\pi}{d}) \\
+		&Z_A  := M_{\nr+1} && X_A := M_{\nr+2} \\
+		&Z_B := \frac{N_1+N_2}{2c} && X_B := \frac{N_1-N_2}{-2s}.
+	\end{align*}
+%	Note that $Z_A$ should be defined by $M_{\nr+1}^0 - M_{\nr+1}^1 + M_{\nr+1}^\perp$,
+%	but $M_{\nr+1}^\perp$ is almost orthogonal to $M_\ast^0$, so we omit the $M_{\nr+1}^\perp$ term here.
+%	In the definition of $X_A$, we omit $M_{\nr+2}^\perp$ too.
+	In the first step, we will show how $(N_1 + N_2)/2c$, or $Z_B$,
+	acts on $M_{\nr+1}^0\ket{\psi}$ and 
+	$M_{\nr+1}^1 \ket{\psi}$.
+	Recall that \cref{thm:selftest} applies
+	to all approximating strategies pf $\I_{-\cot(\pi/d)}^{\max}$, so
+	we can substitute appropriate operators
+	and the shared state into
+    \cref{eq:za-zb} to see that
+	\begin{align*}
+		\norm{Z_B M_0^0 \ket{\psi} - Z_AM_0^0 \ket{\psi}} \leq 
+		\sqrt{s}\norm{M_0^0 \ket{\psi}} O(\sd \qr \qe)
+		= O(\qr \qe/ \sd ).
+	\end{align*}
+	Since $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$,
+	the equation above can be rewritten as 
+	\begin{align*}
+		Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \appd{O(\qr \qe / \sd )} (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi},
+	\end{align*}
+	where we use the fact that $Z_A = M_{\nr+1}^0 - M_{\nr+1}^1$.
+	Using the fact $M_{\nr+1}^0 M_{\nr+1}^1 = 0$, we can 
+	further deduce that
+	\begin{align*}
+		O(\sr \se /d) \geq &\norm{Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}}^2\\
+		=&\norm{ Z_BM_{\nr+1}^0 \ket{\psi} - M_{\nr+1}^0\ket{\psi}}^2 + \norm{ Z_BM_{\nr+1}^1 \ket{\psi} + M_{\nr+1}^1\ket{\psi}}^2,
+	\end{align*}
+	which immediately gives us that 
+	\begin{align}
+	    \label{eq:n1+n20}
+		&\frac{N_1+N_2}{2c} M_{\nr+1}^0\ket{\psi} \appd{O( \qr \qe /\sd)} M_{\nr+1}^0 \ket{\psi},\\
+		\label{eq:n1+n21}
+		&\frac{N_1+N_2}{2c} M_{\nr+1}^1\ket{\psi} \appd{O( \qr \qe /\sd)} -M_{\nr+1}^1 \ket{\psi}.
+	\end{align}
+
+	Next, we study how $X_B = (N_1-N_2)/(-2s)$ acts on 
+	$M_{\nr+1}^0\ket{\psi}$ and $M_{\nr+1}^1 \ket{\psi}$.
+	Substituting the appropriate operators and the shared state into \cref{eq:zaxb,eq:xazb}, we get
+	\begin{align*}
+		\frac{N_1-N_2}{-2s} M_{\nr+1}^0M_0^0 \ket{\psi} 
+		\appd{(\norm{M_0^0\ket{\psi}}/\sqrt{s})\;O(\sd \qr \qe)}M_{\nr+2} M_{\nr+1}^1M_0^0\ket{\psi}\\
+		\frac{N_1 -N_2}{-2s} M_{\nr+1}^1M_0^0 \ket{\psi}  
+		\appd{(\norm{M_0^0 \ket{\psi}}/\sqrt{s})\;O(\sd \qr \qe)}M_{\nr+2} M_{\nr+1}^0 M_0^0 \ket{\psi}.
+	\end{align*}
+	Using the facts that $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$
+	and $O(\sd \qr \qe)$ dominates $O(\sr \se)$, we can
+	simplify the equations above to get
+	\begin{align}
+		\label{eq:n1-n20}
+		&(N_1-N_2) M_{\nr+1}^0 \ket{\psi} \appd{O(\qr\qe/\sd )} -2sM_{\nr+2} M_{\nr+1}^1 \ket{\psi},\\
+		\label{eq:n1-n21}
+		&(N_1-N_2) M_{\nr+1}^1 \ket{\psi}\appd{O(\qr\qe/\sd )} -2sM_{\nr+2} M_{\nr+1}^0 \ket{\psi}.
+	\end{align}
+
+	In summary, we can rearrange terms in \cref{eq:n1+n20,eq:n1+n21,eq:n1-n20,eq:n1-n21} to get
+        \begin{align*}
+        		&N_1M_{\nr+1}^0 \ket{\psi} \appd{O(\qr \qe/ \sd)} cM_{\nr+1}^0\ket{\psi} - sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
+        		&N_1M_{\nr+1}^1 \ket{\psi} \appd{O(\qr \qe/ \sd)} -cM_{\nr+1}^1\ket{\psi} - sM_{\nr+2}M_{\nr+1}^0\ket{\psi},\\
+        		&N_2M_{\nr+1}^0 \ket{\psi} \appd{O( \qr \qe /\sd)} cM_{\nr+1}^0\ket{\psi} + sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
+        		&N_2M_{\nr+1}^1 \ket{\psi} \appd{O(\qr \qe/ \sd )} -cM_{\nr+1}^1\ket{\psi} + sM_{\nr+2}M_{\nr+1}^0\ket{\psi}.
+        \end{align*}
+        Then we can expand $N_1N_2 M_{\nr+1}^0\ket{\psi}$ by first substitute in
+        the approximate expression of $N_2 M_{\nr+1}^0\ket{\psi}$ and repeatedly
+        substitute in the four equations above
+        to get that
+        \begin{align*}
+        		&\quad N_1N_2 M_{\nr+1}^0 \ket{\psi} \\
+		        &\appd{O(\qr \qe/\sd)} (c N_1M_{\nr+1}^0 +sM_{\nr+2}N_1M_{\nr+1}^1)\ket{\psi}\\
+        		&\appd{O( \qr \qe/\sd)}(c^2M_{\nr+1}^0- csM_{\nr+2}M_{\nr+1}^1 -csM_{\nr+2}M_{\nr+1}^1 -s^2 M_{\nr+2}^2 M_{\nr+1}^0)\ket{\psi}\\
+        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^0 - \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.
+        \end{align*}
+        Following similar steps, we can get that
+        \begin{align*}
+            &\quad N_1N_2 M_{\nr+1}^1 \ket{\psi} \\
+		    &\appd{O( \qr \qe/\sd)} (-c N_1M_{\nr+1}^1 +sM_{\nr+2}N_1M_{\nr+1}^0)\ket{\psi}\\
+        		&\appd{O(\qr \qe/\sd)}(c^2M_{\nr+1}^1+ csM_{\nr+2}M_{\nr+1}^0 +csM_{\nr+2}M_{\nr+1}^0 -s^2 M_{\nr+2}^2 M_{\nr+1}^1)\ket{\psi}\\
+        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^1 + \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^0)\ket{\psi}.
+        \end{align*}
+        Multiplying $M_{\nr+2}$ to 
+        the approximate expression of $N_1N_2 M_{\nr+1}^1 \ket{\psi}$,
+        we can get that
+        \begin{align*}
+        N_1N_2 M_{\nr+2}M_{\nr+1}^1 \ket{\psi}\appd{O(\qr \qe/\sd)} 
+		\sin(\frac{2\pi}{d}) M_{\nr+1}^0\ket{\psi} + \cos(\frac{2\pi}{d})M_{\nr+2}M_{\nr+1}^1\ket{\psi},
+        \end{align*}
+        where we use the fact that 
+        \begin{align*}
+            (M_{\nr+2})^2 M_{\nr+1}^0 \ket{\psi} 
+            &= (M_{\nr+2}^0 + M_{\nr+2}^1)M_{\nr+1}^0 \ket{\psi}\\
+            &\appd{O(\sr \se)}N_{\nr+1}^0 M_0^0 \ket{\psi}\\
+            &\appd{O(\sr \se)}N_{\nr+1}^0 (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \\
+            &\appd{O(\sr \se)}(M_{\nr+1}^0+M_{\nr+1}^1)M_{\nr+1}^0\ket{\psi} \\
+            &= M_{\nr+1}^0 \ket{\psi}.
+        \end{align*}
+    Combining the approximate
+    expressions of $N_1N_2M_{\nr+1}^0\ket{\psi}$
+    and $N_1N_2 M_{\nr+2} M_{\nr+1}^0\ket{\psi}$ gives us that
+	\begin{align}
+		\label{eq:omegad}
+		&N_1N_2 (M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi} 
+		\appd{O(\qr \qe/\sd)}\omega_d(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
+	\end{align}
+
+	In the last step, we prove $\ket{\psi_1}$ can be 
+	approximated by
+	\begin{align*}
+	\ket{\psi_1} \appd{O(\sr \se)} 1/2(\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
+	\end{align*}
+	The central step of proving the approximation above is
+	to prove $(M_{\nr+2})^2M_{\nr+1}^0 \ket{\psi} 
+	\appd{O(\sr \se)} M_{\nr+1}^0 \ket{\psi}$,
+	which is proved in the previous paragraph.
+	So we multiply \cref{eq:omegad} on both sides by $1/2(\1 - iM_{\nr+2})$ and get
+	\begin{align}
+		N_1N_2 \ket{\psi_1} \appd{O(\qr \qe/\sd)} \omega_d\ket{\psi_1}.
+	\end{align}
+
+% 	With similar calculations, we can get that 
+% 	\begin{align}
+% 	    N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_1}.
+% 	\end{align}
+\end{proof}
+\begin{proposition}
+    \label{prop:psi1_eig2}
+	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $\ket{\psi_1}$ be as defined in
+	\cref{eq:psi1}.
+	Then,
+	\begin{align}
+    \label{eq:psi1_eig2} 
+    &M_1M_2 \ket{\psi_1} \appd{O(\sd\qr \qe)} \omega_d^{-1} \ket{\psi_1}.
+	 %&& M_2M_1 \ket{\psi_1} \appd{O(\sd\qr \qe)} \omega_d \ket{\psi_1}.
+	\end{align}
+\end{proposition}
+This proof is similar to the proof of \cref{prop:psi1_eig1} but with one extra step. 
+We first prove that there exists a state $\ket{\psi_2}$ that is
+close to $\ket{\psi_1}$, 
+then we show $\ket{\psi_2}$ is close to an eigenstate of $M_1M_2$. 
+In the last step, we show that
+$\ket{\psi_1}$ is also close to an eigenstate of $M_1M_2$.
+\begin{proof}
 %	Using the fact that for $0 < x < 1$, $\sqrt{1+x} = 1 + 1/2 x - O(x^2)$ and $\sqrt{1-x} = 1- 1/2x - O(x^2)$,
@@
 %	\end{align}	
-
-	\textbf{To prove \cref{eq:psi1_eig1}},
-	we need to dive deeper into the implication of the fact that $\bS_1$ achieves $\I_{\cot(-\pi/d)}^{\max}$ approximately.
-	Define
-	\begin{align}
-		&Z_A  := M_{\nr+1} && X_A := M_{\nr+2} \\
-		&Z_B := \frac{N_1+N_2}{2c} && X_B := \frac{N_1-N_2}{-2s}.
-	\end{align}
-%	Note that $Z_A$ should be defined by $M_{\nr+1}^0 - M_{\nr+1}^1 + M_{\nr+1}^\perp$,
-%	but $M_{\nr+1}^\perp$ is almost orthogonal to $M_\ast^0$, so we omit the $M_{\nr+1}^\perp$ term here.
-%	In the definition of $X_A$, we omit $M_{\nr+2}^\perp$ too.
-	Recall \cref{eq:za-zb}, which states that
-	\begin{align*}
-		\norm{Z_B M_0^0 \ket{\psi} - M_{\nr+1}M_\ast^0 \ket{\psi}} \leq 
-		\sqrt{s}\norm{M_0^0 \ket{\psi}} O(\sd \qr \qe)
-		= O(\qr \qe/ \sd ).
-	\end{align*}
-	Since $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$,
-	the equation above can be rewritten as 
-	\begin{align*}
-		Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \appd{O(\qr \qe / \sd )} (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}.
-	\end{align*}
-	On the other hand, using the fact $M_{\nr+1}^0 M_{\nr+1}^1 = 0$, we can get that
-	\begin{align*}
-		O(\sr \se /d) \geq &\norm{Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}}^2\\
-		=&\norm{ Z_BM_{\nr+1}^0 \ket{\psi} - M_{\nr+1}^0\ket{\psi}}^2 + \norm{ Z_BM_{\nr+1}^1 \ket{\psi} + M_{\nr+1}^1\ket{\psi}}^2,
-	\end{align*}
-	which immediately gives us that 
-	\begin{align}
-		&\frac{N_1+N_2}{2c} M_{\nr+1}^0\ket{\psi} \appd{O( \qr \qe /\sd)} M_{\nr+1}^0 \ket{\psi},\\
-		&\frac{N_1+N_2}{2c} M_{\nr+1}^1\ket{\psi} \appd{O( \qr \qe /\sd)} -M_{\nr+1}^1 \ket{\psi}.
-	\end{align}
-		Substituting the appropriate operators and states into \cref{eq:zaxb,eq:xazb}, we get
-	\begin{align*}
-		\frac{N_1-N_2}{-2s} M_{\nr+1}^0M_0^0 \ket{\psi} 
-		\appd{\norm{M_0^0\ket{\psi}}/\sqrt{s} O(\sd \qr \qe)}M_{\nr+2} M_{\nr+1}^1M_0^0\ket{\psi}\\
-		\frac{N_1 -N_2}{-2s} M_{\nr+1}^1M_\ast^0 \ket{\psi}  
-		\appd{\norm{M_0^0 \ket{\psi}}/\sqrt{s}O(\sd \qr \qe)}M_{\nr+2} M_{\nr+1}^0 M_0^0 \ket{\psi}.
-	\end{align*}
-	Using the facts that $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$
-	and $O(\sd \qr \qe)$ dominates $O(\sr \se)$, we know
-	\begin{align}
-		(N_1-N_2) M_{\nr+1}^0 \ket{\psi} \appd{O(\qr\qe/\sd )} -2sM_{\nr+2} M_{\nr+1}^1 \ket{\psi},\\
-		(N_1-N_2) M_{\nr+1}^1 \ket{\psi}\appd{O(\qr\qe/\sd )} -2sM_{\nr+2} M_{\nr+1}^0 \ket{\psi}.
-	\end{align}
-	In summary, we have shown that 
-        \begin{align*}
-        		&N_1M_{\nr+1}^0 \ket{\psi} \appd{O(\qr \qe/ \sd)} cM_{\nr+1}^0\ket{\psi} - sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
-        		&N_1M_{\nr+1}^1 \ket{\psi} \appd{O(\qr \qe/ \sd)} -cM_{\nr+1}^1\ket{\psi} - sM_{\nr+2}M_{\nr+1}^0\ket{\psi},\\
-        		&N_2M_{\nr+1}^0 \ket{\psi} \appd{O( \qr \qe /\sd)} cM_{\nr+1}^0\ket{\psi} + sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
-        		&N_2M_{\nr+1}^1 \ket{\psi} \appd{O(\qr \qe/ \sd )} -cM_{\nr+1}^1\ket{\psi} + sM_{\nr+2}M_{\nr+1}^0\ket{\psi}.
-        \end{align*}
-        Then we can calculate that 
-        \begin{align*}
-        		&\quad N_1N_2 M_{\nr+1}^0 \ket{\psi} \\
-		        &\appd{O(\qr \qe/\sd)} (c N_1M_{\nr+1}^0 +sM_{\nr+2}N_1M_{\nr+1}^1)\ket{\psi}\\
-        		&\appd{O( \qr \qe/\sd)}(c^2M_{\nr+1}^0- csM_{\nr+2}M_{\nr+1}^1 -csM_{\nr+2}M_{\nr+1}^1 -s^2 M_{\nr+2}^2 M_{\nr+1}^0)\ket{\psi}\\
-        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^0 - \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.
-        \end{align*}
-        and 
-        \begin{align*}
-            &\quad N_1N_2 M_{\nr+1}^1 \ket{\psi} \\
-		    &\appd{O( \qr \qe/\sd)} (-c N_1M_{\nr+1}^1 +sM_{\nr+2}N_1M_{\nr+1}^0)\ket{\psi}\\
-        		&\appd{O(\qr \qe/\sd)}(c^2M_{\nr+1}^1+ csM_{\nr+2}M_{\nr+1}^0 +csM_{\nr+2}M_{\nr+1}^0 -s^2 M_{\nr+2}^2 M_{\nr+1}^1)\ket{\psi}\\
-        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^1 + \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^0)\ket{\psi},
-        \end{align*}
-        or equivalently,
-        \begin{align*}
-        		N_1N_2 M_{\nr+2}M_{\nr+1}^1 \ket{\psi}\appd{O(\qr \qe/\sd)} 
-		\sin(\frac{2\pi}{d}) M_{\nr+1}^0\ket{\psi} + \cos(\frac{2\pi}{d})M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
-        \end{align*}
-        Combining the two results above we know
-	\begin{align}
-		\label{eq:omegad}
-		&N_1N_2 (M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi} 
-		\appd{O(\qr \qe/\sd)}\omega_d(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
-	\end{align}
-	Multiplying both sides by $1/2(\1 - iM_{\nr+2})$, we get
-	\begin{align}
-		N_1N_2 \ket{\psi_1} \appd{O(\qr \qe/\sd)} \omega_d\ket{\psi_1}.
-	\end{align}
-	Note that here we use another form of $\ket{\psi_1}$ which is 
-	\begin{align*}
-	\ket{\psi_1} = 1/2(\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
-	\end{align*}
-	With similar calculations, we can get that 
-	\begin{align}
-	    N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_1}.
-	\end{align}
-
-	\textbf{To prove \cref{eq:psi1_eig2}}, we introduce an approximation of $\ket{\psi_1}$, which is 
-	\begin{align}
+    In this proof, we still use the notation $c := \cos(\pi/d)$ and $s := \sin(\pi/d)$. 
+	We first introduce an approximation of $\ket{\psi_1}$,  
+	\begin{align}
+	    \label{eq:psi2}
 	    &\ket{\psi_2} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi},
 	\end{align}
-	and we will first show that 
+	and we will show that 
 	\begin{align}
@@
 
-	To prove \cref{eq:psi1_eq}, 
-	we first recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \se)} N_{\nr+1}^0 \ket{\psi}$ 
+	To prove \cref{eq:psi1_eq}, we compare each term of $\ket{\psi_1}$
+	with $\ket{\psi_2}$.
+	Recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \se)} N_{\nr+1}^0 \ket{\psi}$ 
 	and $M_{\nr+1}^1 \ket{\psi} \appd{O(\sr \se)} N_{\nr+1}^1 \ket{\psi}$ from \cref{prop:chsh_base},
-	so it suffices to show
+	then 
+	\begin{align*}
+	    \ket{\psi_2} - &\ket{\psi_1} \\
+	    &\appd{O(\sr \se)}
+	    (- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}
+	    - (M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}.
+	\end{align*}
+	Therefore, proving \cref{eq:psi1_eq} 
+	is reduced to proving
 	$(M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}$ is close to $(- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}$,
@@
 %	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
-	At this point, we can use the anti-commutation relation (\cref{eq:zaxa}) induced by $\bS_1$  and conclude that 
-	\begin{align*}
-		M_{\nr+1}M_{\nr+2} M_\ast^0 \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^0\ket{\psi}}}}{c\sqrt{s}}O(\sd\qr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^0 \ket{\psi}.
-	\end{align*}
-	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \qr \qe)$.
+	At this point, we can 
+	substitute appropriate operators and the shared 
+	state of $\bS_1$ into 
+	the anti-commutation relation (\cref{eq:zaxa})
+	and see that 
+	\begin{align*}
+		M_{\nr+1}M_{\nr+2} M_0^0 \ket{\psi} \appd{\frac{\norm{M_0^0\ket{\psi}}}{c\sqrt{s}}O(\sd\qr\qe)} -M_{\nr+1}M_{\nr+2} M_0^0 \ket{\psi}.
+	\end{align*}
+	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the error term above is of order $O(\sd \qr \qe)$.
 	Then we can show that 
 	\begin{align*}
-		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \\
+		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1+M_{\nr+1}^2)\ket{\psi} \\
 			&\appd{O(\sr\se)} M_{\nr+2}M_{\nr+1} M_0^0 \ket{\psi} \\
@@
 	Next, we show that $M_1M_2 \ket{\psi_2}\appd{O(\qr \qe/\sd)} \omega_d^{-1} \ket{\psi_2}$, which gives
-	us \cref{eq:psi1_eig2} after substituting in\cref{eq:psi1_eq}.
-	From the strategy $\bS_2$, we can deduce that 
+	us \cref{eq:psi1_eig2} after substituting in \cref{eq:psi1_eq}.
+	With similar derivation as in the proof of \cref{prop:psi1_eig1}, we can apply results from \cref{sec:chsh}
+	to the strategy $\bS_2$ to get that
 	\begin{align}
@@
 	\end{align}
-	With similar calculation as in the previous case, we can get 
-	\begin{align*}
+	So we can further deduce that 
+	\begin{align}
+	\label{eq:psi2_base}
 		M_1M_2 (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi} \appd{O(\qr \qe/\sd)} 
 		\omega_d^{-1} (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1)\ket{\psi} .
-	\end{align*}
-	Multiplying both sides of the equation above by $1/2(\1+iN_{\nr+2})$ we get
-	\begin{align}
-		M_1M_2 \ket{\psi_2} \appd{O(\qr \qe/\sd)} \omega_d^{-1}\ket{\psi_2},
-	\end{align}
-	where we use the fact that $\ket{\psi_2} = 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$
-	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \qr\qe)} \ket{\psi_2}$ gives us that 
+	\end{align}
+	It can be shown that $\ket{\psi_2} \appd{O(\sr \se)} 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$. 
+	Proving this approximation of $\ket{\psi_1}$
+	uses the same techniques as in the proof of \cref{prop:psi1_eig1}, so we omit it here.
+
+	We multiply both sides of \cref{eq:psi2_base} by $1/2(\1+iN_{\nr+2})$ and get that
+	\begin{align}
+		M_1M_2 \ket{\psi_2} \appd{O(\qr \qe/\sd)} \omega_d^{-1}\ket{\psi_2}.
+	\end{align}
+	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \qr\qe)} \ket{\psi_2}$ implies that 
 	\begin{align}
@@
 	\end{align}
-	With similar derivation we can get that 
-	\begin{align}
-	    M_2M_1 \ket{\psi_1} \appd{O(\sd \qr \qe)} \omega_d\ket{\psi_1}.
-	\end{align}
+% 	With similar derivation we can get that 
+% 	\begin{align}
+% 	    M_2M_1 \ket{\psi_1} \appd{O(\sd \qr \qe)} \omega_d\ket{\psi_1}.
+% 	\end{align}
 \end{proof}
@@
 \end{align*}
-Intuitively, it means that $\ket{\psi}$ is invariant under the permutation induced by $U_A\ct U_B\ct$.
+Intuitively, it means that $\ket{\psi}$ is invariant under the permutation induced by $U_A\ct \x U_B\ct$.
 We use this observation in the proof of the following lemma.
@@
 $\ket{\psi'} := \sum_{j=1}^{(d-1)} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}$
-with $\log_r j$ being the discrete log.
+with $\log_r j$ being the discrete log and
+$\ket{\psi_1}$ as defined in \cref{eq:psi1}.
 Then,
@@
 \begin{proof}
-	We first prove that $\norm{\ket{\psi'}}^2 \appd{O(d r^d \qe)} 1$.
+% 	We first prove that $\norm{\ket{\psi'}}^2 \appd{O(d r^d \qe)} 1$.
+	The proof takes two steps. In the first step, 
+	we show that the norm of $\ket{\psi'}$ is close to $1$.
+	In the second step, 
+	we show that $\braket{\psi}{\psi'}$ is close to $1$.
+
+	Expanding $\braket{\psi'}{\psi'}$, we get
+	\begin{align*}
+	    \braket{\psi'}{\psi'} 
+	    = \sum_{j=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j}  \ket{\psi_1}
+	    + \sum_{j\neq j'} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j'}  \ket{\psi_1}.
+	\end{align*}
 	Observe that 
@@
 		\bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j}  \ket{\psi_1} =
-		\braket{\psi_1}{\psi_1} \appd{O(\sr\se)} \frac{1}{d-1}.
-	\end{align*}
+		\braket{\psi_1}{\psi_1} \appd{O(\sr\se)} \frac{1}{d-1},
+	\end{align*}
+	so we need to show when $j \neq j'$, the inner product 
+	$\bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j'}  \ket{\psi_1}$
+	is close to $0$.
 	Using the relation $O_B(U_B\ct)^j \ket{\psi} \appd{O(r^{j+1/2} \se)} (U_B\ct)^j O_B^{r^j}\ket{\psi}$ and \cref{eq:psi1_eig1}, we can deduce that 
@@
 	where we use the fact that $\norm{1 - \omega_d^{r^{j'}-r^j}} = O(1/d)$.
-	We can calculate the norm of $\ket{\psi'}$ as 
+	Therefore, we can calculate the norm of $\ket{\psi'}$ 
 	\begin{align*}
@@
 		& \appd{O(\sr\se)} \frac{1}{2} \left(\bra{\psi}(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}  - i \bra{\psi}N_{\nr+2}M_{\nr+1} \ket{\psi} \right)\\
-		& \appd{O(r^2 \ep)} \frac{1}{2} \frac{2}{d-1} = \frac{1}{d-1},
-	\end{align*}
-	where the last approximation comes from the correlation.
+		& \appd{O(r \ep)} \frac{1}{2} \frac{2}{d-1} = \frac{1}{d-1},
+	\end{align*}
+	where the approximation of $\bra{\psi}N_{\nr+2}M_{\nr+1} \ket{\psi}$ comes from the correlation.
 	Hence, we know $\braket{\psi}{\psi'} \appd{O(d^2 \sr \se)} 1$.
-	In the end, we apply \cref{prop:close_vec} to get
+
+	In the end, we combine $\braket{\psi}{\psi'} \appd{O(d^2 \sr \se)} 1$ and $\norm{\ket{\psi'}}^2 \appd{O(d r^d \qe)} 1$,
+	and apply \cref{prop:close_vec} to conclude
 	\begin{align*}
@@
 %-------------------------------------------------------------------------------------------
-The commutation games are introduced to certify the operators used in $\LS(r)$ commute with 
+The commutation game is introduced to certify some observables used in $\LS(r)$ commute with 
 the operators for the extended weighted CHSH test. For the details of the general commutation test, 
@@
 
-The implication of winning the commutation games is summarized in the following proposition.
+The implication of winning the commutation game is summarized in the following proposition.
 \begin{proposition}
@@
 	\begin{align}
-		&M_{\nr+1}^0 M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+1}^0 \ket{\psi}, &&
-		M_{\nr+1}^1 M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+1}^1 \ket{\psi}, \\
+		&M_{\nr+1}^0 M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+1}^0 \ket{\psi},\\ 
+		&M_{\nr+1}^1 M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+1}^1 \ket{\psi}, \\
 		\label{eq:com_nr2} &M_{\nr+2} M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+2} \ket{\psi},
@@
 \end{proposition}
-Note that the $M(s)$'s for $s = f_0, f_2,g_0,g_2$ tested in the commutation test are used for
-equations of the Magic Square game in $\LS(r)$,
-which will be used to construct the isometry in the next subsection.
+Note that the $M(s)$'s for $s = f_0, f_2,g_0,g_2$ tested in the commutation game are measured for the Magic Square equations in $\LS(r)$.
+They will be used to construct the isometry in the next subsection.
 \begin{proof}
@@
 	For the other relations, we prove $M_{\nr+1}^0M(f_0) \ket{\psi} \appd{O(\sr \se)} M(f_0)M_{\nr+1}^0 \ket{\psi}$ to demonstrate 
-	the techniques involved. We denote Bob's projectors by $\{ N_{(\nr+1, f_0)}^{b_1 b_2} \}$ where $b_1 \in \{0, 1, 2\}$ and
-	$b_2 \in \{0,1\}$. From the correlation, we can get that 
+	the techniques involved.
+
+	We denote Bob's projectors by $\{ N_{(\nr+1, f_0)}^{b_1 b_2} \}$ where $b_1 \in \Z_3$ and
+	$b_2 \in \Z_2$. From the correlation in \cref{tbl:comm}, 
+	we can get that 
 	\begin{align*}
@@
 		& \appd{O(\sr \se)} (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) M_{r+6} \ket{\psi} \\
-		&= M_{r+6}  (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) \ket{\psi} \\
-		& \appd{O(\sr\se)} M_{r+6}M(f_0)^0 \ket{\psi}.
+		&= M(f_0)  (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) \ket{\psi} \\
+		& \appd{O(\sr\se)} M(f_0)M_{\nr+1}^0 \ket{\psi}.
 	\end{align*}
@@
 %-----------------------------------------------
-With the previous propositions and lemmas, we can prove the self-testing theorem.
+Based on the propositions and lemmas proved so far, we can prove the self-testing theorem.
 \begin{theorem}
 	\label{thm:self-test}
-	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$.
+	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
 	Then there exists an isometry   
-	$\Phi_A \x \Phi_B = (\Phi_{A,2} \x \Phi_{B,2})(\Phi_{A,1}\x\Phi_{B,2})$ and a state $\ket{junk}$
-	such that $\norm{\ket{junk}}^2 \appd{O(dr\se)} 1$ and 
-	\begin{align}
-		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
-		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+	$\Phi_A \x \Phi_B = (\Phi_{A,2} \x \Phi_{B,2})(\Phi_{A,1}\x\Phi_{B,1})$ and a state $\ket{junk}$
+	such that $\norm{\ket{junk}} \appd{O(\sd \qr \qe)} 1$ and 
+	\begin{align}
+		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
+		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d^{5/2}r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
-		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d^{5/2} r^{d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d r^{d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_{j r^{-1}}}_{B'}.
@@
 It implies that,
-for any odd prime number $d$ with primitive root $r$, 
-there exists a correlation of size $\Theta(r^2)$ that can robustly self-test the maximally
+for any odd prime number $d$ whose primitive root is $r$, 
+there exists a correlation of size $\Theta(r)$ that can robustly self-test the maximally
 entangled state of local dimension $4(d-1)$.
-Moreover, there are infinitely many prime numbers
-whose primitive roots are in the set $\{2,3,5\}$ \cite{murty1988},
-Hence, our main result is the following theorem.
+Since there are infinitely many prime numbers
+whose smallest primitive roots are in the set $\{2,3,5\}$ \cite{murty1988},
+we can apply \cref{thm:self-test} to the set $D$
+of all such odd prime
+numbers and prove the following theorem.
 \begin{theorem}
@@
 
-The isometry used in the proof of \cref{thm:self-test} has two steps. 
+Before proving \cref{thm:self-test}, we introduce the isometry 
+$\Phi_A \x \Phi_B$, which has two steps. 
 We denote the isometry used in the first step and the second step by $\Phi_{A,1} \x \Phi_{B,1}$ and 
@@
 in the two figures below.
-In the first step, 
-we use $U_A, O_A$ and $U_B$, $O_B$ to distill a copy of $\ket{\EPR{d-1}}$.
-In the second step. we use the observables $M_{r+6},M_{r+8}, M_{r+9}, M_{r+11}$ and 
-$N_{r+6}, N_{r+8}, N_{r+9}, N_{r+11}$ to distill two copies of $\ket{\EPR{2}}$.
-Intuitively, $M_{r+6}$ acts as $\1 \x \paulix$; $M_{r+8}$ acts as $\paulix \x \1 $;
-$M_{r+9}$ acts as $\1 \x \pauliz$ and $M_{r+11}$ acts as $\pauliz \x \1$; and similarly on Bob's side.
+
+To construct the isometry $\Phi_{A,1} \x \Phi_{B,1}$, 
+we use $U_A, O_A$ and $U_B$, $O_B$ defined in \cref{eq:uaoa,eq:ubob} 
+to produce a copy of $\ket{\EPR{d-1}}$.
+
+To construct the isometry $\Phi_{A,2} \x \Phi_{B,2}$. we use the observables $M(f_0),M(f_2), M(g_0), M(g_2)$ and 
+$N(f_0), N(f_2), N(g_0), N(g_2)$ to produce two copies of $\ket{EPR}$.
+Intuitively, $M(f_0)$ acts as $\1 \x \paulix$; $M(f_2)$ acts as $\paulix \x \1 $;
+$M(g_0)$ acts as $\1 \x \pauliz$ and $M(g_2)$ acts as $\pauliz \x \1$; and similarly on Bob's side.
 
@@
 
-The first isometry has the following steps:
+The isometry $\Phi_{A,1} \x \Phi_{B,1}$ has the following steps:
 \begin{enumerate}
@@
 \end{enumerate}
-
+Note that $\ket{x_0}$ is orthogonal to $W_{d-1}$, so
+$\spn\{ x_j \}_{j=0}^{d-1}$ has dimension $d$.
 \begin{figure}[H]
@@
         \node[phase] (phase11) at (2,0) {} edge [-] (op11);
-	\node[operator] (op23) at (2,-2) {$M_{r+11}$} edge [-] (q3);
-	\node[operator] (op24) at (2, -3) {$N_{r+11}$} edge[-] (q4);
+	\node[operator] (op23) at (2,-2) {$M(g_2)$} edge [-] (q3);
+	\node[operator] (op24) at (2, -3) {$N(g_2)$} edge[-] (q4);
         \node[phase] (phase16) at (2,-5) {} edge [-] (op16);
@@
         \node[phase] (phase12) at (3.5,-1) {} edge [-] (op12);
-	\node[operator] (op33) at (3.5,-2) {$M_{r+9}$} edge [-] (op23);
-	\node[operator] (op34) at (3.5, -3) {$N_{r+9}$} edge[-] (op24);
+	\node[operator] (op33) at (3.5,-2) {$M(g_0)$} edge [-] (op23);
+	\node[operator] (op34) at (3.5, -3) {$N(g_0)$} edge[-] (op24);
         \node[phase] (phase15) at (3.5,-4) {} edge [-] (op15);
@@
         \node[phase] (phase51) at (5.5,0) {} edge [-] (op41);
-	\node[operator] (op53) at (5.5,-2) {$M_{r+8}$} edge [-] (op33);
-	\node[operator] (op54) at (5.5, -3) {$N_{r+8}$} edge[-] (op34);
+	\node[operator] (op53) at (5.5,-2) {$M(f_2)$} edge [-] (op33);
+	\node[operator] (op54) at (5.5, -3) {$N(f_2)$} edge[-] (op34);
         \node[phase] (phase56) at (5.5,-5) {} edge [-] (op46);
@@
         \node[phase] (phase62) at (7,-1) {} edge [-] (op42);
-	\node[operator] (op63) at (7,-2) {$M_{r+6}$} edge [-] (op53);
-	\node[operator] (op64) at (7, -3) {$N_{r+6}$} edge[-] (op54);
+	\node[operator] (op63) at (7,-2) {$M(f_0)$} edge [-] (op53);
+	\node[operator] (op64) at (7, -3) {$N(f_0)$} edge[-] (op54);
         \node[phase] (phase65) at (7,-4) {} edge [-] (op45);
@@
         \draw[decorate,decoration={brace},thick,] (9.5,-1.1) to
-    	node[midway,right] (bracket2) {$\ket{\EPR{2}}^{\x 2}$}
+    	node[midway,right] (bracket2) {$\ket{EPR}^{\x 2}$}
     	(9.5,-3.9);
@@
 \end{figure}
-
 The second isometry is the standard isometry used in the self-testing result of the Magic Square game \cite{wu2016}.
@@
 \begin{align}
-	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/2} r^{d+1/2} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
+	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d r^{d} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
 \end{align}
@@
 \label{eq:phi2_result}
-\Phi_{A,2} \x \Phi_{B,2} (\sqrt{d-1}\ket{\psi_1}) \appd{O(r\se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2}.
+\Phi_{A,2} \x \Phi_{B,2} (\sqrt{d-1}\ket{\psi_1}) \appd{O(\sr\se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2}.
 \end{align}
@@
 	&\quad\Phi_{A,2} \x \Phi_{B,2}( \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi})) \\
-	&\appd{O(d^{5/2} \sr \ep^{1/8})} \Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \x\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
-	&\appd{O(r\se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
-\end{align*}
-where we use the fact that $\Phi_{A,2}\x \Phi_{B,2}$ only acts on the state $\ket{\psi_1}$.
+	&\appd{O(d r^d \ep^{1/8})} \left[\Phi_{A,2} \x \Phi_{B,2}
+	(\sqrt{d-1} \ket{\psi_1})\right] \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
+	&\appd{O(\sr\se)} \ket{junk} \x \ket{EPR}^{\x 2} \x\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
+\end{align*}
+where we use the fact that $\Phi_{A,2}\x \Phi_{B,2}$ only 
+acts nontrivially on the state $\ket{\psi_1}$.
+The state $\sqrt{d-1} \ket{\psi_1}$ is the state
+$\ket{reuse}$ in the two figures.
 
@@
 		\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(d^{5/2} r^{d} \sr \qe)}&\frac{1}{d} \sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}\omega_d^{(k_2-k_1)j}\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\appd{O(\sd r^{d} \qe)}&\frac{1}{d} \sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}\omega_d^{(k_2-k_1)j}\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
 		\xrightarrow[]{QFT_d^{-1}} &\frac{1}{d^2}\sum_{l_1,l_2 = 0}^{d-1}\sum_{k_1,k_2 = 0}^{d-1}\sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} 
@@
 \begin{align}
-	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/2} r^{d+1/2} \ep^{1/8})} \sqrt{d-1} \ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
-\end{align}
-where we use the fact that $O(d^{5/2} r^{d+1/2} \ep^{1/8})$ dominates both $O(d r^{d/2+1/4} \ep^{1/8})$ and 
-$O(d^{5/2} r^{d+1/2} \qe)$.
-Since $\norm{\ket{\psi_1}}^2 \appd{O(r \se)} 1/(d-1)$, we know $ \sqrt{d-1} \norm{\ket{\psi_1}} \appd{O(\sd \sr\qe)} 1$.
+	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d r^{d} \ep^{1/8})} \left(\sqrt{d-1} \ket{\psi_1}\right) \x \left(\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\right),
+\end{align}
+where we use the fact that $O(d r^{d} \ep^{1/8})$ dominates both $O(d r^{d/2+1/4} \ep^{1/8})$ and 
+$O(\sd r^{d} \qe)$.
+The relation $ \sqrt{d-1} \norm{\ket{\psi_1}} \appd{O(\sd \qr\qe)} 1$ is derived from the fact that
+$\norm{\ket{\psi_1}}^2 \appd{O(\sr \se)} 1/(d-1)$.
 
@@
 recall that
-$\ket{\psi_1} 
-	=\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}.
-$
+\begin{align*}
+    \ket{\psi_1} =\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}.
+\end{align*}
 The other observation that we need is that 
@@
 \end{align*}
-For simplicity we define $M^{\ba} := M(f_0)^{a(4)}M(f_2)^{a(3)}M(g_0)^{a(2)}M(g_2)^{a(1)}$ and
-$N^{\bb} := N(f_0)^{b(4)}N(f_2)^{b(3)}N(g_0)^{b(2)}N(g_2)^{b(1)} $.
-We would like to show that 
+For simplicity we define 
+\begin{align*}
+    &M^{\ba} := M(f_0)^{a(4)}M(f_2)^{a(3)}M(g_0)^{a(2)}M(g_2)^{a(1)} \\
+    &N^{\bb} := N(f_0)^{b(4)}N(f_2)^{b(3)}N(g_0)^{b(2)}N(g_2)^{b(1)}.
+\end{align*}
+Our goal is to use \cref{prop:rel_comm} to show that 
 \begin{align}
 \label{eq:mua_comm}
-M^{\ba} \ket{\psi_1} \appd{O(r\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)
+M^{\ba} \ket{\psi_1} \appd{O(\sr\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)
 M^{\ba} \ket{\psi},
@@
 for all $\ba \in \{0,1\}^4$,
-%which implies that 
-%\begin{align*}
-%	\Phi_{A,2} \x &\Phi_{B,2} (\ket{\psi_1}) \appd{O(r\se)} \\
-%	&\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)(\Phi_{A,2} \x \Phi_{B,2}(\ket{\psi}))
-%\end{align*}
-%because $N^{\ub}$ commutes with $\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$
-%for all $\ub \in \{0,1\}^4$.
-which can be justified by \cref{prop:rel_comm}.
+
 We show how to apply \cref{prop:rel_comm} to commute $M(g_2)^{a(1)}$ through 
-$\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$ and then similar process can be repeated for $M(g_0)^{a(2)}, M(f_2)^{a(3)}$ and $M(f_0)^{a(4)}$,
+$\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 \\- iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$ and then similar process can be repeated for $M(g_0)^{a(2)}, M(f_2)^{a(3)}$ and $M(f_0)^{a(4)}$ using
+\cref{lm:sub},
 \begin{align*}
@@
 	&\appd{O(\sr\se)} \frac{1}{2}[ (M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} -i M(g_2)^{a(1)} M_{\nr+2}N_{\nr+1}] \ket{\psi} \\
-	&\appd{O(\sr\se)} \frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M(g_2)^{a(1)} N_{\nr+1}] \ket{\psi} \\
+	&\appd{O(\sr\se)} \frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iN_{\nr+1} M_{\nr+2}M(g_2)^{a(1)} ] \ket{\psi} \\
 	&\appd{O(\sr\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M(g_2)^{a(1)} M_{\nr+1}] \ket{\psi} \\
-	&\appd{O(\sr\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M_{\nr+1}M(g_2)^{a(1)} ] \ket{\psi}.
+	&\appd{O(\sr\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M_{\nr+1}M(g_2)^{a(1)} ] \ket{\psi}\\
+	&= \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)M(g_2)^{a(1)}\ket{\psi}.
 \end{align*}
@@
 \begin{align}
-	\Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \appd{O(\sd \sr \se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2},
+	\Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \appd{O(\sd \sr \se)} \ket{junk} \x \ket{EPR}^{\x 2},
 \end{align} 
@@
 If the initial state is $O_A\ket{\psi}$, we first use the fact that 
-$ \Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi}) \appd{O(d^{5/4} r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi'})$, 
+$ \Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi}) \appd{O(d r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi'})$, 
 and then we calculate $\Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi'})$ as
@@
 		\sum_{j=1}^{d-1} O_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1}\ket{x_0}_{A'}\ket{x_0}_{B'}\\
-		\appd{O(\sd r^{d+1/2} \ep^{1/4})}&\sum_{j=1}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} \ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
+		\appd{O(\sd r^d \ep^{1/4})}&\sum_{j=1}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} \ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
 		\xrightarrow[]{QFT_d} &\frac{1}{d}\sum_{j=1}^{d-1} \sum_{k_1,k_2 = 0}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} 
@@
 		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(d^{5/2} r^{d+1/2}  \ep^{1/4})}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}
+		\appd{O(d r^{d}  \ep^{1/4})}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}
 		\omega_d^{-j}\omega_d^{(k_2-k_1)j}\ket{\psi_1}
@@
 If the initial state is $U_A\ket{\psi}$, we first use the fact that 
-$ \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi}) \appd{O(d^{5/4}r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi'})$, 
+$ \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi}) \appd{O(d r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi'})$, 
 and then we calculate $\Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi'})$.
@@
 		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(d^{5/2} r^{d+1/2} \qe)}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}
+		\appd{O(d r^{d} \qe)}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}
 		\omega_d^{k_2j-k_1jr^{-1}}\ket{\psi_1}
@@
 
+\section*{Acknowledgment}
+The author is deeply grateful to his PhD advisor, Carl Miller, for the enlightening discussions with him, his patient guidance and useful critiques through this
+project. His original idea about 
+combining a linear system game with a Bell inequality and characterizing prime numbers
+by their primitive roots are invaluable to
+this work. He also helped the author with the design
+of the extended weighted CHSH test
+and the editing of the draft.
+
 \bibliographystyle{alphaurl}
@@
 %===========================================
-\section{Embedding $\Pg$ into $\Gamma$}
-\label{sec:embedding}
+% \section{Embedding $\Pg$ into $\Gamma$}
+% \label{sec:embedding}
 %===========================================
-This section supports \cref{sec:embed_idea} by giving the definitions
-of $\Pg_0$ and $\Pg_1$.
-We also prove some properties of the generators of $\Pg_0$, $\Pg_1$ and 
-$\Gamma$ along the way.
-
-Recall that the goal of introducing $\Pg_0$ is to embed
-$\Pg$ in a group with only order-$2$ generators,
-so that it is easier to embed $\Pg$ into a solution group.
-
-Next we define the group $\Pg_1$.
-
-Recall the definition of $\Gamma$ in \cref{def:gamma}. We prove a property of it.
+% This section supports \cref{sec:embed_idea} by giving the definitions
+% of $\Pg_0$ and $\Pg_1$.
+% We also prove some properties of the generators of $\Pg_0$, $\Pg_1$ and 
+% $\Gamma$ along the way.
+
+% Recall that the goal of introducing $\Pg_0$ is to embed
+% $\Pg$ in a group with only order-$2$ generators,
+% so that it is easier to embed $\Pg$ into a solution group.
+
+% Next we define the group $\Pg_1$.
+
+% Recall the definition of $\Gamma$ in \cref{def:gamma}. We prove a property of it.
 
@@
     The linear system of $\LS(r)$ has 
-    variables $x(s)$ for each $s \in S \setminus \{J\}$, and equations:
+    variables $x(s)$ for each $s \in S$, and equations:
     \begin{itemize}
@@
 In this section we give the full description of a representation of $\Gamma$,
+$\Psi$,
 which is built upon representations 
-of $\Pg_0$ and $\Pg_1$. We need the representation of $\Gamma$ to construct the
-ideal strategy of $\LS(r)$.
-
-Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}, which are the carrier spaces
+of $\Pg_0$ and $\Pg_1$. We need the representation $\Psi$ of $\Gamma$ 
+to construct the ideal strategy of $\LS(r)$.
+
+Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{eq:basis}, 
+which are the carrier spaces
 of the representations given below,
@@
 can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the defining 
-conjugacy relations of $\Pg_0$.
+conjugacy relations in $\Pg_0$.
 \end{definition}
@@
 \begin{align*}
-	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
-	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
-\end{align*}
-which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
-$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$. 
+	&\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} =
+	\tO \\
+	&\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}} = \tU,
+\end{align*}
+where $\tO$ and $\tU$ are defined in \cref{eq:O,eq:U}.
 We can also check that the representation $\Psi_0$ satisfies the relations
-that $\Psi_0(a_3a_4) \Psi_0(a_2) \Psi_0(a_4a_3) = \Psi_0(a_2)$ by observing that
-	\begin{align*}
-		\Psi_0(a_3)\Psi_0(a_4)= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
-	\end{align*}
-	so we can conclude  
+that $\Psi_0(a_3a_4) \Psi_0(a_2) \Psi_0(a_4a_3) = \Psi_0(a_2)$ by first observing that
+	\begin{align*}
+		\Psi_0(a_3)\Psi_0(a_4)= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}}.
+	\end{align*}
+Then we can calculate  
 	\begin{align*}
@@
 
-Following the proof of Lemma $29$ of Ref.~\cite{slofstra2017}, we construct a representation of $\Pg_1$.
+Next, following the proof of Lemma $29$ of \cite{slofstra2017}, we construct a representation of $\Pg_1$.
 \begin{definition}
@@
 	&\Psi_1(a_i) = \1_{W_2} \x \Psi_0(a_i) \\
-	&\Psi_1(b_i) = \ketbra{x_1}{x_1} \x \Psi_1(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
-	&\Psi_1(c_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(a_i) \\
+	&\Psi_1(b_i) = \ketbra{x_1}{x_1} \x \Psi_0(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
+	&\Psi_1(c_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_0(a_i) \\
 	&\Psi_1(d_i) =  X_{W_2} \x \Psi_0(a_i);
@@
 \begin{align*}
-	\Psi_1(h_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(a_j) + \ketbra{x_2}{x_2} \x \Psi_1(a_k).
+	\Psi_1(h_{jk}) = \ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \Psi_0(a_k).
 \end{align*}
@@
 
-Finally, we follow the proof of Proposition $27$ of Ref.~\cite{slofstra2017} to construct the 
-representation of $\Gamma$.
+Finally, we follow the proof of Proposition $27$ of \cite{slofstra2017} to construct the 
+representation $\Psi$ of $\Gamma$.
 \begin{definition}
@@
 The validation of $\Psi_1$ and $\Psi$ were done in the proofs of 
-Lemma $29$ and Proposition $27$ in Ref.~\cite{slofstra2017}.
+Lemma $29$ and Proposition $27$ in \cite{slofstra2017}.
 %========================================
 \section{The proof of \cref{thm:selftest} }
-\label{sec:selftest}
+\label{sec:w_chsh_proof}
 %========================================
-This proof follows the same line of argument in Appendix A of Ref.~\cite{bamps2015}.
+This proof follows the same line of argument in Appendix A of \cite{bamps2015}.
 We first find two sum-of-square decompositions of $2\sqrt{\alpha^2+1} \1 - \I_\alpha$,
@@
 \end{align} 
-With the notation $c:= \cos(\mu)$, $s := \sin(\mu)$ and 
-\begin{align*}
-	&Z_A = M_1 && X_A = M_2\\
-	&Z_B = \frac{N_1+N_2}{2c} && X_B = \frac{N_1-N_2}{2s},
-\end{align*}
-the two SOS decompositions that we use are
+With the notation $c:= \cos(\mu)$, $s := \sin(\mu)$, 
+we define
+\begin{align*}
+	&Z_A := M_1 && X_A := M_2\\
+	&Z_B := \frac{N_1+N_2}{2c} && X_B := \frac{N_1-N_2}{2s}.
+\end{align*}
+The two SOS decompositions that we use are
 \begin{align}
@@
 \end{align}
-The verification is omitted here. From the SOS decomposition, we establish \cref{eq:za-zb,eq:xa-xb,eq:xazb,eq:zaxb,eq:zaxa,eq:zaxaxbzb}.
-We define
+The verification is omitted here. From the SOS decomposition, we can prove \cref{eq:za-zb,eq:xa-xb,eq:xazb,eq:zaxb,eq:zaxa,eq:zaxaxbzb}.
+
+We first define
 \begin{align*}
@@
 \begin{align}
-\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2
+\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2.
 \end{align}
@@
 $\ip{\bar{\I}_\alpha} \leq \epsilon$ implies that
-$\bra{\psi} S_i^2 \ket{\psi} \leq \ep$, and equivalently, $\norm{S_i \ket{\psi}} \leq \se$ for $i = 1,2,3,4$.
+\begin{align*}
+    \bra{\psi} S_i^2 \ket{\psi} \leq \ep,
+\end{align*}
+and equivalently,
+\begin{align*}
+   \norm{S_i \ket{\psi}} \leq \se 
+\end{align*}
+for $i = 1,2,3,4$.
 From the definitions of $S_i$'s, we can get that 
 \begin{align}
-	&\norm{(X_AZ_B+X_BZ_A)\ket{\psi}} \leq \frac{1}{c\sqrt{s}} \se\\
-	&\norm{(Z_A-Z_B)\ket{\psi}} \leq \frac{\sqrt{s}}{c} \se\\
-	&\norm{(X_A-X_B)\ket{\psi}} \leq \frac{1}{\sqrt{s}} \se.
-\end{align}
-The first and the second inequality give us that 
-\begin{align}
+	\label{eq:base1} &\norm{(X_AZ_B+X_BZ_A)\ket{\psi}} \leq \frac{1}{c\sqrt{s}} \se\\
+	\label{eq:base2} &\norm{(Z_A-Z_B)\ket{\psi}} \leq \frac{\sqrt{s}}{c} \se\\
+	\label{eq:base3} &\norm{(X_A-X_B)\ket{\psi}} \leq \frac{1}{\sqrt{s}} \se,
+\end{align}
+which proves \cref{eq:za-zb,eq:xa-xb}.
+\Cref{eq:base1,eq:base2} give us that 
+\begin{align*}
 	\norm{ [Z_A(\1+X_B) - (\1-X_A)Z_B] \ket{\psi} } 
 	\leq \norm{(X_AZ_B+X_BZ_A)\ket{\psi}} + \norm{(Z_A-Z_B)\ket{\psi}}
-	\leq \frac{s+1}{c\sqrt{s}} \se.
-\end{align}
-Similarly, the first and the third inequality give us that 
-\begin{align}
-	\norm{[X_A(\1+Z_B) - X_B(\1-Z_A)] \ket{\psi}} \leq \frac{c+1}{c\sqrt{s}} \se.
-\end{align}
+	\leq \frac{s+1}{c\sqrt{s}} \se,
+\end{align*}
+which proves \cref{eq:xazb}.
+Similarly, \cref{eq:base1,eq:base3} give us that 
+\begin{align*}
+	\norm{[X_A(\1+Z_B) - X_B(\1-Z_A)] \ket{\psi}} \leq \frac{c+1}{c\sqrt{s}} \se,
+\end{align*}
+which proves \cref{eq:zaxb}.
 Since $Z_AX_A +X_A Z_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}$, we can deduce that
-\begin{align}
-	\norm{ (Z_A X_A+X_AZ_A)\ket{\psi}} \leq \frac{1+c+s}{c\sqrt{s}} \se.
-\end{align}
+\begin{align*}
+	\norm{ (Z_A X_A+X_AZ_A)\ket{\psi}} \leq \frac{1+c+s}{c\sqrt{s}} \se,
+\end{align*}
+as in \cref{eq:zaxa}.
 To prove \cref{eq:zaxaxbzb}, we switch to the approximate relation form and derive that 
@@
 
-Now we introduce the isometries $\Phi_A$ and $\Phi_B$ mentioned in the statement of the theorem.
-They are the same as the ones used in Ref.~\cite{bamps2015}.
+Now we introduce the isometries $\Phi_A$ and $\Phi_B$ mentioned in the theorem.
+They are the same as the ones used in \cite{bamps2015}.
 To construct $\Phi_A$ and $\Phi_B$ we need to regularize $Z_B$ and $X_B$ to make sure the corresponding operations 
 are unitary in the isometries. We define $Z_B^\ast$ to be the operator obtained from $Z_B$ by changing all the $0$-eigenvalues
-to $1$ and 
+to $1$, then we define
 \begin{align*}
@@
 \end{figure}
-To bound $e_{xy} := \norm{ (\Phi_A\x\Phi_B) (\tA_x \x \tB_y) \ket{\tpsi} - \ket{junk} \x (A_x\x B_y) \ket{\EPR{2}}}$,
-there are some intermediate steps. Since the derivations are the same as in Ref.~\cite{bamps2015}, 
+To bound $e_{xy} := \norm{ (\Phi_A\x\Phi_B) (\tM_x \x \tN_y) \ket{\tpsi} - \ket{junk} \x (M_x\x N_y) \ket{\EPR{2}}}$,
+there are some intermediate steps. Since the derivations are the same as in \cite{bamps2015}, 
 we only record the key relations here.
@@
 \begin{align}
-	\forall x,y \in \{0,1,2\}, e_{xy} \in O((\frac{1}{c^2s^{1/2}} + \frac{1}{s^{3/2}})\sqrt{\epsilon}).
+ e_{xy} \in O((\frac{1}{c^2s^{1/2}} + \frac{1}{s^{3/2}})\sqrt{\epsilon})
+ \quad\quad 
+ \forall x,y \in \{0,1,2\}.
 \end{align}
 \end{proof}
-
 \end{document}

### 2019-09-14 Draft/ext_abstract.tex
QIP version

--- 2019-08-12 Draft/draft.tex
@@
 
-\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}
 \newtheorem{lemma}[theorem]{Lemma}
@@
 %%%%%%%%%%%%%%%%
-
+\vspace{-8ex}
+\date{}
 \begin{document}
@@
 
-\author[1]{Honghao Fu}
-\author[1,2]{Carl Miller}
-
-\renewcommand\Affilfont{\itshape\small}
-
-\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
-\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
+\author{Honghao Fu}
+
 \maketitle
 
-\begin{abstract}
-	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
-	$\Theta(r^2)$ 
-	that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
-	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
-	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
-	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
-	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
-	with unbounded local dimension.
-\end{abstract}
-%========================================
-\section{Introduction}
-\label{sec:intro}
-%========================================
-Self-testing is a unique phenomenon of quantum mechanics.
-It is also powerful because only classical interactions are required.
-It has many applications in quantum
-delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
+The certification of a quantum device is an important building block
+for many quantum information processing tasks, especially
+when the devices are provided by some untrusted vendor.
+We would like such certification to be done based solely on
+the observed measurement statistics with the only assumption being that
+any local device cannot communicate their own
+inputs to the other local devices. 
+The measurement statistics are referred to as correlations.
+
+It has been shown that certain quantum correlations require the distant parties to share
+a particular entangled state up to some local isometry. 
+This phenomenon is referred to as self-testing.  
+If we can further prove that, when the observed correlation deviates from 
+the ideal correlation to some extent, 
+the shared state is close to the ideal state up to some local isometry,
+then we say the self-test is robust.
+
+Self-testing is powerful because only classical interactions are performed.
+Hence, it allows a classical party to delegate quantum computation tasks to some untrusted service provider
+and verify that the computations are performed
+honestly and correctly \cite{ruv2013,coladan2017verifier}.
+It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
 \cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
-
-The case of self-testing $2$-dimensional EPR pair, which is defined by
-\begin{align*}
-    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
-\end{align*}
-is fully understood.
-The techniques for robustly self-testing $\ket{EPR}$ is 
-first introduced in Ref.~\cite{mckague2012}, then improved in Ref.~\cite{bamps2015}. 
-Ref.~\cite{yang2013} proved an generalized swap-isometry
-that can be used to robustly self-test large dimensional maxially entangled states.
-Its ideas are realized later in Ref.~\cite{coladan2017all}, 
-which proved that all pure bipartite entangled state 
-can be self-tested.
-The authors constructed a family of correlations such
-that each partially or maximally entangled state of any local dimension has
-a self-testing correlation in this family.
+Since the setting of interactive proof systems is similar to a self-test, self-testing arguments also help to prove
+lower bounds of the computational power of entanglement-assisted
+multiprover interactive proof systems \cite{fitzsimons2019, neexp}.
+
+Robust self-testing of the EPR pair, 
+$\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11})$,
+is first proved in \cite{mckague2012}, then 
+the techniques are improved in \cite{bamps2015}.
+Robust self-testing of partially entangled qubits is later proved in
+\cite{yang2013}.
+Robust self-testing results of tensor product of maximally and partially entangled qubits 
+are proved in \cite{coladan2016parallel,natarajan2017,lowdegree},
+with the last one being the one with the smallest input and output alphabet.
+For general bipartite entangled quantum states, \cite{coladan2017all} proves that there exists a family of correlations such that
+each bipartite entangled state can be self-tested by a correlation in this family.
+% The authors constructed a family of correlations such
+% that each partially or maximally entangled state of any local dimension has
+% a self-testing correlation in this family.
 % One can also self-test many copies of the $2$-dimensional EPR
@@
 % Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
-To generate a correlation in the family, Alice and Bob
-have constant number of measurement settings but each 
-measurement setting has the same number of outcomes as
-the local dimension of the entangled state to be self-tested. 
-In other words, their correlation is of size $\Theta(d^2)$,
-where $d$ is the local dimension of the entangled state.
-This is the only result about self-testing the general $d$-dimensional entangled state so far.
-However, proving the robustness of the family of correlations remains an open problem. 
-Without robustness, we cannot infer anything about a quantum strategy if
-the produced correlation deviates from the ideal correlation, no matter how small the 
-deviation is.
-
-A natural question to ask is whether maximally entangled states with large local dimension
-can be robustly self-tested with constant-sized correlations. 
-In this paper, we give an affirmative answer to this question by proving the following theorem.
+
+There are two open questions about self-testing that we aim at answering.
+The first one is whether maximally entangled states with large local dimension
+can be self-tested with constant-sized input and output alphabets. 
+For comparisons,
+all the self-testing correlations used in the results listed above have 
+output alphabets with size depending on $d$
+when they try to self-test an entangled state of local dimension $d$.
+The second one is how to robustly self-test maximally entangled states
+with local dimension $d > 2$ and $d \neq 2^n$ for any $n$.
+For example, the authors of \cite{coladan2017all} left proving their
+family of self-testing correlations robust as an open problem.
+
+We give an affirmative answer to the first question
+and make significant progress in answering the 
+second question
+by proving the following theorem.  
 \begin{theorem}[Informal]
@@
 	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
-	with constant-sized question and answer alphabets.
+	with constant-sized input and output alphabets.
 \end{theorem}
-The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.
-
+Formal statements of this theorem can be found in Theorem $6.16$ and $6.17$
+of the attached report.
+% The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.
+
+\textbf{Sketch of the proof}.
 The set $D$ is, specifically, the set of all 
-odd prime numbers whose smallest primitive root is either $2$, $3$, or $5$.  
-It has been shown that this set has infinitely many elements \cite{murty1988}.
-To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r)$ 
+odd prime numbers whose smallest primitive root 
+is either $2$, $3$, or $5$, 
+We say that $r$ is a primitive root of $d$ if $r$ is a 
+multiplicative generator of the group $\Zd$.
+It has been shown that $D$ has infinitely many elements \cite{murty1988}.
+
+To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
+input and constant-sized output alphabets
 for each $d \in D$ whose smallest primitive root is $r$.
 This correlation is denoted by $\fC(d,r)$.
-Note that although the size of $\fC(d,r)$ does not depend on $d$, the entries of $\fC(d,r)$ do.
-Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
-that if some quantum strategy can approximate $\fC(d,r)$, then
-the generalized swap isometry \cite{yang2013}
-can produce the desired maximally entangled states when applied to the unknown state used in the strategy.
+Note that although the size of the input or output alphabet of $\fC(d,r)$ does not depend on $d$, 
+the distributions in $\fC(d,r)$ do. 
+Details of $\fC(d,r)$ can be found in Section $5$ of the attached report.
+% Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
+% that if some quantum strategy can approximate $\fC(d,r)$, then
+% the generalized swap isometry \cite{yang2013},
+% \hf{which only involves local operations,} 
+% can produce a state that is close to the desired maximally entangled state, when applied to the unknown state used in the strategy.  
 %Then the self-testing property of this correlation is 
@@
 %\end{theorem}
-\carl{The paper \cite{bamps2015} says that the earlier paper \cite{yang2013} has ``flaws.'' Check what those flaws are, and make sure that they won't put a shadow on anything that you're discussing when you cite \cite{yang2013}.}
-\hfc{The flaws are in the self-testing proof, not in the 
-proof about the generalized isometry.}
-
-The correlation $\fC(d,r)$ contains the ideal correlation of a specially-designed binary linear system game.
-In a general linear system game, Alice is given a random equation 
-from a linear system and she
-should give an assignment of the equation.
+
+The correlation $\fC(d,r)$ contains a winning correlation of a specially-designed binary linear system game.  
+In a general binary linear system game, Alice is asked for an assignment of a random equation 
+of a linear system.
 Bob is asked to assign a value to a random variable of that equation.
+The assignment to each variable is binary. 
 They win the game if Alice's assignment satisfies the equation and Bob's
 assignment to the variable matches Alice's assignment.
-A widely-used and thoroughly-studied example of a linear system game is
-the Magic Square game \cite{magic_square}.
-In this game, the linear system is
-\begin{align*}
-    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
-    x_7 + x_8 + x_9 = 0 \\
-    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
-    x_3 + x_6 + x_9 = 0.
-\end{align*}
-Using two copies of the maximally entangled state
-\begin{align*}
-    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
-\end{align*}
-the Magic square game can be won
-with certainty.
-It has been shown that if a strategy that can win this game almost perfectly, the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
-so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
-The key observation that leads to the self-testing proof is that 
-a winning strategy must contain observables $X$ and $Z$ that 
-satisfy the anti-commutation relation 
-\begin{align*}
-    X Z = - Z X.
-\end{align*}
-Intuitively, we can think of the Magic Square game as a way to enforce the
-anti-commutation relation.
-
-Our linear system game is designed to enforce the relation 
-\begin{align*}
-    U O U\ct = O^r,
-\end{align*}
-for some integer $r$,
-in the sense that the winning strategy contains binary observables
-$M_1, M_2, M_3, M_4$ on Alice's side and 
-$N_1, N_2, N_3, N_4$ on Bob's side such that 
-\begin{align*}
-    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2.
-\end{align*}
-This relation implies the eigenvalue of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root
-is $r$. It also implies that $U$ is a permutation of the eigenbasis of $O$.
-Winning this linear system game implies that Alice and Bob share a state
-$\ket{\psi}$ such that
-\begin{align*}
-    O \x O \ket{\psi} = \ket{\psi}, && 
-    U \x U \ket{\psi} = \ket{\psi}.
-\end{align*}
-These two relations are important for the self-testing argument
-because
-the relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
-is spanned by tensor products of states in the eigenbasis of $O$;
-and $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
-under the permutation induced by $U$. 
-At this point, the eigenvalues of $O$ are unknown, so
-further restricting the eigenvalues of $O$ requires another test, 
-which will be introduced later.
+Intuitively, binary linear system games are designed to enforce certain
+relations between observables possessed by Alice and Bob.
+For example. the Magic Square game \cite{magic_square} forces
+Alice and Bob to have binary observables $X$ and $Z$ such that $XZ = -ZX$ \cite{wu2016, coladan2017}.
+
+In his seminal work \cite{slofstra2017}, Slofstra proved that 
+there exists a binary linear system game that cannot be won by any finite-dimensional quantum strategy but a limit of 
+finite-dimensional strategy can win it perfectly,
+which implies that the set of quantum correlations generated by
+finite-dimensional strategies is not closed.
+In the proof, he proposed and validated a new way 
+to design binary linear system games to enforce conjugacy relations of the
+form $X Y X\ct = Z$ for unitaries $X, Y$ and $Z$.
+Following Slofstra's work, we design our binary linear system game, $\LS(r)$,
+to enforce the relation $U O U\ct = O^r$ for some unitaries $U$ and $O$.
+By enforcing this relation we mean that, 
+if some quantum strategy with shared state $\ket{\psi}$
+wins this game with probability $1 - \ep$,
+then one can identify unitaries $U_A, O_A$ on Alice's side and
+$U_B, O_B$ on Bob's side as products of their binary observables, such that 
+\begin{align}
+\label{eq:induct}
+	 U_A O_A U_A\ct \ket{\psi} \appd{O(r \se)}  O_A^{r} \ket{\psi}.
+\end{align}
+The analogous relation holds on Bob's side too.
+The construction of $\LS(r)$ is given in Section $3$ and
+the proof of \cref{eq:induct} is given in Section $6.1$ of the attached report.
 
 The special feature of our linear system game is that the sizes
-of the question sets for Alice and Bob are of order $\Theta(r)$,
-and the answer sets are of size $\Theta(1)$.
-Restricting $r \leq 5$ in our theorem implies that our linear system 
-game only uses constant-sized question sets and constant-sized answer sets.
-\carl{A reader may get lost at the last sentence -- you're jumping into the material too quickly without enough explanation.}
-\hfc{Rewritten.}
+of the input alphabets for Alice and Bob are of order $\Theta(r)$,
+and the output alphabets are of size $\Theta(1)$.
+Restricting $r \leq 5$ as in \cref{thm:inf} implies that our linear system 
+game only uses constant-sized input and output alphabets.
+
 % The number of variables and the number of equations of the linear system game depend linearly on $r$,
@@
 
-The remaining question is how to certify a particular eigenvalue of $O$, so we
-design a nonlocal test called the extended weighted CHSH test.
-% Before going to the answer,
-% we remark that 
-% the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
-% whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
-% linear system games are binary. 
-% The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
-% We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
-% The fact that Alice and Bob only have binary observables make it easier for us 
-% to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
-The difference between a nonlocal game and a nonlocal test will be discussed later.
-It is designed based on the $\alpha$-weighted CHSH inequality, which is defined by
+\Cref{eq:induct} is not sufficient for self-testing, so
+$\fC(d,r)$ also contains an extension of the optimal correlation 
+that achieves the maximal violation of the $\cot(-\frac{\pi}{d})$-weighted CHSH inequaltiy \cite{pal2010}
 \begin{align*}
-    \I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
+    \I_{\cot(-\pi/d)} = \cot(-\frac{\pi}{d})(\ip{M_1N_1} + \ip{M_1N_2}) + \ip{M_2N_1} - \ip{M_2N_2}.
 \end{align*}
-where $M_x$ and $N_y$ for $x,y \in \{1, 2\}$ are some binary observables.
-Define $\mu = \arctan(1/\alpha)$,
-\begin{align*}
-    \pauliz = \ketbra{0}{0} - \ketbra{1}{1} && \paulix = \ketbra{0}{1} + \ketbra{1}{0},
-\end{align*}
-which are the Pauli-Z and Pauli-X operators.
-This inequality is maximally violated when the shared state is $\ket{EPR}$,
-Alice's binary observables are
-\begin{align*}
-    M_1 = \pauliz && M_2 = \paulix,
-\end{align*}
-and Bob's binary observables are
-\begin{align*}
-    N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
-\end{align*}
-We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
-state $\ket{\psi}$ and the observables $M_1, M_2$ and $N_1, N_2$.
-Then we noticed that 
-\begin{align*}
-    N_1N_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
-\end{align*}
-has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.
-Hence, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
-for some odd prime $d$ whose primitive root is $r$,
-and ask Alice and Bob
-to reuse the observables $M_1, M_2$ and $N_1, N_2$，then we can certify that
-the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
-Combining this observation with the fact that $O$ satisfy the relation $UOU\ct = O^r$,
-we can conclude that all the eigenvalues of $O$ are $\{ e^{ij 2\pi /d} \}_{j=1}^{d-1}$,
-and the eigenspaces of all the eigenvalues have the same cardinality.
-At this point, we has the explicit structure of $O$, so we 
-can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
-to prove the correlation $\fC(r, d)$ can robustly self-test 
-a maximally entangled state of dimension $4(d-1)$.
-
-\carl{This paragraph (also) will need more context.}
-\hfc{Rewritten.}
-
-Our contributions are four-fold.
-\begin{enumerate}
-    \item We identify the constant-sized question and answer sets that can be used to robustly self-test
-    maximally entangled states with unbounded dimensions. Before our work, the most efficient way
-    was to use $O(\log d)$-sized question and answer sets to robustly self-test
-    the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
-    \item Our self-testing proof demonstrate a new way to apply the generalized swap-isometry
-    proposed in Ref.~\cite{yang2013} to robustly self-test a maximally entangled state of large lcoal
-    dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.
-    We believe it can be applied to prove the family of correlations proposed in Ref.~\cite{coladan2017all}
-    are also robust.
-    \item We demonstrate how to enforce relations between operators of large but fixed dimension in a 
-    binary linear system game. Before our work, only the anti-commutation relation between $2$-dimensional
-    Pauli operators can be enforced in a binary linear system game.
-    \item Our result gives us deeper understanding of the set of quantum correlations.
-    In previous works that proved the non-closeness of the set of quantum correlations
-    \cite{slofstra2017}, 
-    lower bounds of the entanglement required to achieve certain correlations are identified.
-    Our work discovers a large family of correlations where we know exactly the amount of entanglement
-    required to achieve each of the correlations in this family. 
-\end{enumerate}
-
-\textbf{Structure of the paper}.
-We start with notations and background information in \cref{sec:prelim}.
-Since the correlation we designed can win a special linear system game and satisfy
-an extended weighted CHSH test, we introduce the linear system game
-in \cref{sec:lsg} and the self-testing properties of the extended weighted CHSH inequality in \cref{sec:chsh}. 
-Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
-In the end, we give the robust self-testing proof in \cref{sec:main}.
-
-%========================================
-\section{Preliminaries and notations}
-\label{sec:prelim}
-%========================================
-%-----------------------------------
-\subsection{Notations and mathematical background}
-%-----------------------------------
-The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we \hf{self-test} is denoted by
+In Section $4$, we prove that $\I_{\cot(-\pi/d)}$ can be used to robustly
+self-test $\ket{EPR}$ and rotated Pauli operators.
+% The extended correlation has input alphabets $\{0,1,2, \nr+1, \nr+2\}$ for Alice and Bob, where $\nr$ is the number of variables of
+% the linear system game introduced above,
+% and output alphabets with size $3$.
+% If some strategy with shared state $\ket{\psi}$ can produce a correlation that is within
+% expected trace distance $\ep$ from this correlation, 
+% we first identify a special sub-normalized state $\ket{\psi_1} = 1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi}$, such that
+% \begin{align*}
+%     &O_A \ket{\psi_1} \appd{O(\sd \qe)} \omega_d^{-1} \ket{\psi_1}, \\
+%     &O_B \ket{\psi_1} \appd{O( \qe/\sd)} \omega_d\ket{\psi_1}.
+% \end{align*}
+By investigating this extended correlation, we find a sub-normalized state
+$\ket{\psi_1}$ such that,
+if some strategy with shared state $\ket{\psi}$ can produce a correlation that is within
+expected trace distance $\ep$ from $\fC(d,r)$, then
 \begin{align}
-\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
+    \label{eq:decomp}
+    \ket{\psi} \appd{O( r^{d/2} \ep^{1/8})}
+    \sum_{j=1}^{(d-1)} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1},
 \end{align}
-The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
-The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
-\hf{the EPR pair is denoted by} 
-\begin{align}
-	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
-\end{align}
-and the Pauli operators are given by
-\begin{align}
-	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
-\end{align}
-Note that we only work with finite Hilbert spaces in our work.
-
-For quantum states and operators on different Hilbert spaces, we use subscripts to label them.
-For example, $O_A$ is an operator on Alice's side and $\ket{0}_{B}$ is a state on Bob's side. 
-The only exception is for projectors used in a quantum strategy defined below, where the subscript 
-is the input and the superscript is the output. For example, $M_x^a$ is Alice's projector for input $x$ and output $a$.
-Operators defined by the projectors follow the same convention, for example, $M_x := M_x^0 - M_x^1$.
-If we add tilde to an operator, then this operator is fully characterized and belongs to some ideal strategy.
-Otherwise, the operator is general and the only assumption is that it is finite-dimensional.
-
-We use the following notation for the closeness between quantum states.
-\begin{align}
-	\ket{u} \appd{\epsilon} \ket{v} \iff \norm{\ket{u} - \ket{v}} \leq \epsilon. 
-\end{align}
-Similarly, for numbers $a,b \in \C$, the closeness is denoted by
-$a \appd{\epsilon} b \iff \cnorm{a-b} \leq \epsilon$.
-
-We use some basic number theory in our work. 
-\begin{definition}
-A primitive root of a prime number
-$d$ is an integer $r$ such that $r$ has multiplicative order $d-1$
-in the ring of integers modulo $d$, $\mathbb{Z}_d$.
-\end{definition}
-In other words,
-$r$ is a generator of $\Zd$.
-
-We also need some basic notions of group presentation and group
-representation, so 
-We introduce them below.
-For more contexts, please refer to Ref.~\cite{dummit2004}.
-
-\hf{
-Let $S$ be a set of letters. We denote by $\mathcal{F}(S)$ the \emph{free group generated by $S$}, 
-which consists of all finite words made from $\set{s, s^{−1}| s \in S}$ such that no $ss^{−1}$ or $s^{−1}s$ appears as a substring for any $s$,
-where $s^{-1}$ denotes the inverse of $s$. 
-The group law is given by concatenation and cancellation.
-For a more formal treatment, we refer to Section $6.3$ of Ref.~\cite{dummit2004}.}
-
-\begin{definition}[Group presentation]
-    Given a set $S$, let $\mathcal{F}(S)$ be the free group generated by $S$ and $R$ be a subset of $\mathcal{F}(S)$.
-    Then $\ip{S:R}$ denotes the quotient of $\mathcal{F}(S)$
-    by the normal subgroup generated by $R$.
-    If the group $G$ is isomorphic to $\ip{S:R}$,
-    then we say $G$ 
-    has a presentation $\ip{S:R}$. 
-\end{definition}
-If both sets $S$ and $R$ are finite, then we say the group $G = \ip{S:R}$ is \emph{finitely-presentable}.
-The elements of $S$ are the \emph{generators} and the elements
-of $R$ are the \emph{relations}.
-When we refer to an equation
-of the form $a = b$ with $a, b \in \mathcal{F} ( S )$ as a ``relation,'' 
-it is understood 
-that we mean the element $ab^{-1} 
-\in R$.
-\hf{ There are two types of relations that we will be working with.
-} 
-Considering \hf{a subset of generators} $\{ s_j \}_{j=1}^n \subset S$ \hf{such that $s_{j_1} \neq s_{j_2}$ if $j_1 \neq j_2$},
-the relations of the form $\Pi_{j=1}^n s_j  = e$, where $e$ is the identity element, are called 
-\emph{linear relations};
-and the relations of the form
-$s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.   
-There are two special types of groups that we will work with in \cref{sec:lsg}. We give the definitions below.
-\begin{definition}
-    \label{def:spe_conj_grp}
-    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
-    Let
-    \begin{align*}
-        \Gamma = \ip{\{s_i\}_{i \in [n]}  :
-        \{s_i^2=e\}_{i\in [n]} \cup 
-        \{ s_i s_j s_i = s_k\}_{(i,j,k)\in C}}.
-    \end{align*}
-    We say a group is a conjugacy group if it has a presentation of this form. 
-\end{definition}
-A conjugacy group is a special case of what Slofstra defined as 
-a linear-plus-conjugacy group (Definition $26$ of Ref.~\cite{slofstra2017}). The difference is that a conjugacy group does not have linear relations. The next definition follows the 
-definition of a nice linear-plus-conjugacy group (Definition $28$ of \cite{slofstra2017}).
-\begin{definition}
-    \label{def:nice_conj_grp}
-    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
-    Let 
-    \begin{align*}
-        \Gamma = \ip{\{s_i\}_{i \in [n]} \cup \{s_{jk}\}_{(i,j,k)\in C} :
-        \{s_i^2=e\}_{i\in [n]} \cup 
-        \{s_{jk}^2 = e, s_is_js_i = s_k, s_{jk}s_js_k = e\}_{(i,j,k)\in C}}.
-    \end{align*}
-    We say a group is a nice conjugacy group if it has a presentation of this form. 
-\end{definition}
-\carl{Nice work with the last two definitions -- they are prettty clean.
-I wonder if you could make the last definition even cleaner by simply asserting the relations $s_j s_k = s_k s_j$, and leaving out the generators $s_{jk}$?}
-\hfc{If we treat the commutation relations as conjugacy relations, then the final solution will be more complicated.}
-The relation $s_{jk} s_js_k = e$ implies that $s_j$ commutes with $s_k$
-because
-\begin{align*}
-    [s_j, s_k] = s_js_ks_js_k = s_{jk}^2 = e.
-\end{align*}
-Next we give the definition of a group representation. 
-\begin{definition}
-    A representation of $G$ on the finite Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
-\end{definition}
-The last concept of group theory that we need is group embedding.
-\begin{definition}[Group embedding]
-    An embedding of $G$ into $K$ is an injective group homomorphism: $\phi: G \rightarrow K$.
-\end{definition}
-%-----------------------------------------
-\subsection{Nonlocal games}
-%-----------------------------------------
-In a nonlocal game, there are two players, Alice and Bob and each of them is requested
-to give an answer for a randomly chosen question. 
-\hf{We denote Alice's question set by $\calX$ and her family of answer sets by $\{\calA_x\}_x$
-for each $x \in \calX$. Similarly,
-Bob's question set is denoted by $\calY$ and his family of answer sets denoted by $\{\calB_y\}_y$ for each $y \in \calY$. 
-Note that when $\calA_x = \calA$ for each $x \in \calX$, we simply say the output alphabet is $\calA$, and we follow this convention on Bob's side too.
-The nonlocal game also
-comes with a functions $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
-and a family of functions $\{ V_{(x,y)} : \calA_x \times \calB_y \rightarrow \R \}_{x,y}$ for each $(x,y) \in \calX \times \calY$, which is 
-the family of scoring functions.
-Note that when $\calA_x = \calA$ for all $x$ and $\calB_y = \calB$ for all $y$, we write the score function as 
-$V: \calA \times \calB \times \calX \times \calY \rightarrow \R$.
-}
-
-\hf{We also define A nonlocal test 
-to be a tuple $(\calX, \calY, \{\calA_x\}_{x \in \calX}, \{\calB_y\}_{y \in \calY}, \pi)$, where
-$\calX, \calY, \{\calA_x\}_{x}, \{\calB_y\}_{y}$ and $\pi$ are as defined for a nonlocal game.
-Hence, a nonlocal test doesn't have scoring functions.
-}
-
-A quantum strategy of a nonlocal game or a nonlocal test presented in terms of projective measurements
-consists of projective measurements $\{\{M_x^a\}_{a \in \calA_x} \}_{x \in \calX}$ on Alice's side, 
-$\{\{N_y^b\}_{b \in \calB_y} \}_{y \in \calY}$ on Bob's side, and a shared state $\ket{\psi}$. 
-By projective measurements, we mean that  
-$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
-Then Alice and Bob's quantum strategy produces the conditional probability distribution
-\begin{align}
-	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
-\end{align}
-for each $(x,y) \in \calX \times \calY$ and $(a,b) \in \calA_x \times \calB_y$.
-Note that the tensor product structure indicates that the
-two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.
-For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
-\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
-\begin{definition}
-	Given input alphabets: $\calX$ and $\calY$, and families of output
-	alphabets: $\{\calA_x\}_{x \in \calX}$ and $\{\calB_y\}_{y \in \calY}$, a correlation is a family of conditional probability distributions
-	$\{\pr{ab}{xy}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
-\end{definition}
-A particular type of nonlocal games that we are interested in is called binary linear system games.
-\begin{definition}[Binary linear system game]
- Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ (meaning that $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
- $c$ is a length-$n$ vector with entries in $\Z_2$). 
- The associated linear system game involves two
- players Alice and Bob. 
- The input and output alphabets are 
- \begin{align*}
-     \calX = \{I_i\}_{i=1}^m && &\calY = \{1 \dots n\} \\
-     \calA_{I_i} = (\Z_2)^{I_i} && &\calB = \Z_2,
- \end{align*}
- where $I_i = \{j : H(i,j) = 1\}$.
- When Alice and Bob answer with $\ba$ and $b$ for questions $I_i$ and
- $j$ respectively,
- the scoring functions are defined by
- \begin{align}
- 	V_{(I_i,j)}(\ba, b) =
-	\begin{cases}
-		1, \quad \text{if } \sum_{k \in I_i} H(i,k) a(k) \equiv c(i) \pmod 2 \text{ and } a(j) = b \\
-		0,  \quad \text{otherwise.}
-	\end{cases}
-\end{align}
-\end{definition}
-
-A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
-have equations
-\begin{align*}
-    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
-    x_7 + x_8 + x_9 = 0 \\
-    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
-    x_3 + x_6 + x_9 = 0.
-\end{align*}
-\hf{Note that the equations above are taken modulo $2$.
-We follow this convention in the rest of our work.}
-For the formulation of a general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.
-
-% \hf{In our work, a binary linear system game is conducted in a slightly different way.
-% Instead of always getting an equation number, Alice gets an equation number or 
-% a pair of equation number and variable number with equal probability. In the later case,
-% she just needs to give assignment to the particular variable.
-% By conducting a binary linear system game in this way,
-% we force Alice and Bob to share
-% a quantum strategy in terms of binary observables.}
-% \carl{Is this modification necessary?}
-\begin{definition}[Binary observable strategy of a linear system game]
-\label{def:q_strat}
-A quantum strategy presented in terms of binary observables for the binary linear system game $Hx = c$ consists of 
-\begin{enumerate}
-	\item a pair of finite-dimensional Hilbert spaces $\calH_A$ and $\calH_B$; 
-	\item a collection of binary observables $N_j$, $1 \leq j \leq n$, on $\calH_B$
-	such that $N_j^2 = \1$ for every $1 \leq j \leq n$; 
-	\item a collection of binary observables $M_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
-	on $\calH_A$ such that 
-	\begin{enumerate}
-		\item $M_{ij}^2 = \1$ for every $i,j$, and
-		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every \carl{$i,l,k$ such that} $H(i,l) = H(i,k) =1$;
-	\end{enumerate} 
-	and
-	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
-\end{enumerate}
-\end{definition}
-Note that a measurement strategy of a binary linear system game can be converted to a binary observable strategy. Let a measurement strategy be 
-$(\{\{M_i^{\ba}\}_{\ba \in X_i}\}_{i=1}^m, \{\{N_j^b\}_{b=0}^1\}_{j=1}^n,\\ \ket{\psi})$, where $X_i$ is some answer set of equation $i$.
-The corresponding binary observable
-strategy consists of, $\ket{\psi}$, $N_j := N_j^0 - N_j^1$ and
-\begin{align*}
-    M_{ij} := \sum_{\ba: a(j)=0} M_i^{\ba} - \sum_{\ba: a(j) =1}
-    M_i^{\ba}
-\end{align*}
-for $1\leq i \leq m$ and $1 \leq j \leq n$. 
-\hf{
-Hence, in the rest of the work, we focus on binary observable strategies,
-when discussing Alice's strategy of some linear system game.
-Specifically, we assume that Alice has a binary observable for each variable
-in each equation ,
-so when she is asked the assignment of a particular variable, she simply
-measures according to the corresponding observable of that variable in some equation.}
-
-% Note that any quantum strategy presented in terms of binary observables can be 
-% converted to a quantum strategy presented in terms of projective measurement by looking into
-% the spectral decompositions of the observables. 
-% More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
-% implies that they share a common eigenspace. The collection of eigenvalues associated with one eigenstate is the assignment
-% to the whole equation when this eigenstate is measured in a projective measurement strategy \cite{cleve2014}.
-
-A \hf{perfect} binary observable strategy for the linear system game associated with $Hx = c$, which always wins the game, can be constructed from
-a finite-dimensional representation of a finitely presentable group
-over $\Z_2$, called the solution group. 
-\begin{definition}[Solution group of a linear system game]
-	\label{def:presentation}
-	Let $Hx = c$ be an $m \times n$ linear system. The solution group of this system
-	is the group
-	\begin{align*}
-		\Gamma(H,c) := \ip{
-		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
-				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
-				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
-				}.
-	\end{align*}
-\end{definition}
-The relation $J^2 = x_i^2 = e$ means that all the generators are of order $2$.
-Let $\Psi$ be a finite-dimensional representation of $\Gamma(H, c)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$. 
-Then a perfect strategy for 
-the linear system game ($Hx = c$) is given by 
-\begin{enumerate}
-	\item $M_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
-	\item $N_j = \Psi(x_j)\tp$ for all $1 \leq j \leq n$, 
-	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
-\end{enumerate}
-
-%-------------------------------------------------------------------------------
-\subsection{The weighted CHSH inequality \cite{acin2012}.}
-%-------------------------------------------------------------------------------
-\hf{The weighted CHSH inequality a variation of the CHSH inequality \cite{chsh}. 
-We formulate it as a nonlocal game.}
-The input sets and output sets of Alice and Bob are
-$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
-The scoring function for the $\alpha$-weighted CHSH test, for $|\alpha|\geq 1$, is defined by
-\begin{align}
-	V(a,b,x,y)_{\alpha-CHSH} = 
-	\begin{cases}
-		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
-		(-1)^{a + b}, \quad \text{if } x = 2,\; y = 1 \\
-		(-1)^{1 + a + b}, \quad \text{if } x = y = 2.
-	\end{cases}
-\end{align}
-The input distribution is $\pi(x,y) = 1/4$ for all $(x,y) \in \calX \times \calY$.
-Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
-We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
-The weighted CHSH inequality states that 
-\begin{align}
-	\label{eq:chsh_op}
-	\I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
-\end{align}
-where $\ip{M_x N_y} := \bra{\psi} M_x N_y \ket{\psi}$ is the expectation value of the observables. 
-The weighted CHSH inequality is true 
-if Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
-However, if they share an entangled state $\ket{\psi}$, the value of $\I_\alpha$ can be as large as
-$ \I_\alpha^{\max} = 2\sqrt{1+\alpha^2}$ \cite{acin2012}.
-\begin{definition}[Ideal strategy to achieve $\I_\alpha^{\max}$ \cite{acin2012}]
-	\label{def:ideal}
-	Define $\mu = \arctan(1/\alpha)$.
-	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\I_\alpha^{\max}$, 
-	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
-	$\tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $\tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
-\end{definition}
-An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
-value $\I_\alpha$ close to $\I_\alpha^{\max}$, then the strategy is close to the ideal 
-strategy up to some local isometry, 
-which is a phenomenon referred as a robust self-test.
-We give the formal statement of this self-testing property of $\I_\alpha$ in \cref{sec:chsh}.
-\hf{In \cref{sec:full_test} we design
-a nonlocal test called the extended weighted CHSH test based on the weighted CHSH inequality.}
-
-%-----------------------------------------------------------
-\subsection{Approximation tools}
-%-----------------------------------------------------------
-In the rest of the paper, we use the following approximation results implicitly and explicitly.
-\begin{proposition}
-	\label{prop:inner_pd}
-	Let $\ket{v}$ and $\ket{v'}$ be vectors such that the relation $\ket{v} \appd{\epsilon} \ket{v'}$ holds.
-	Then for any unit vector $\ket{u}$,
-	\begin{align*}
-		 \braket{v}{u} \appd{\ep} \braket{v'}{u}.
-	\end{align*}	
-\end{proposition}
-\begin{proof}
-	We can write $\ket{v'} = \ket{v} + \ket{v''}$, where $\norm{\ket{v''}} \leq \epsilon$,
-	then
-	\begin{align*}
-	\norm{ \braket{v}{u} - \braket{v'}{u} } = \norm{\braket{v''}{u}} \leq \norm{\ket{u}}\norm{\ket{v''}} \leq \epsilon.
-	\end{align*}
-\end{proof}
-\begin{proposition}
-	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with norm less than equal to $1$
-	such that 
-	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$.
-	Then, 
-	\begin{align*}
-		\braket{u_1}{u_2} \appd{\ep_1+ \ep_2} \braket{v_1}{v_2}.
-	\end{align*}
-\end{proposition}
-\begin{proof}
-	By direct calculation we have
-	\begin{align*}
-		\norm{ \braket{u_1}{u_2} - \braket{v_1}{v_2}} \leq &\norm{\braket{u_1}{u_2} - \braket{v_1}{u_2}}
-		+ \norm{\braket{v_1}{u_2} - \braket{v_1}{v_2}} \\
-		\leq & \ep_1 + \ep_2,
-	\end{align*}
-	where we used \cref{prop:inner_pd}.
-\end{proof}
-\begin{proposition}
-\label{prop:orthog}
-	Let $U$ be a unitary matrix and $\ket{u}$ and $\ket{v}$ be two vectors
-	such that
-	\begin{align*}
-		U\ket{u} \appd{\ep_1} a \ket{u} &&
-		V\ket{v} \appd{\ep_2} b \ket{v}, 
-	\end{align*}
-	for some $a \neq b \in \C$ such that $\norm{a} = \norm{b} = 1$. Then,
-	\begin{align*}
-		\norm{\braket{u}{v}} \leq \max(\norm{\ket{u}}, \norm{\ket{v}})\frac{\ep_1+\ep_2}{\norm{1-a^{-1}b}} + \frac{\ep_1\ep_2}{\norm{1-a^{-1}b}}.
-	\end{align*}
-\end{proposition}
-\begin{proof}
-	We write $U\ket{u} = a\ket{u} + \ket{u'}$ such that $\norm{\ket{u'}} \leq \ep_1$.
-	Similarly, we write $U\ket{v} = b\ket{v} + \ket{v'}$ such that $\norm{\ket{v'}} \leq \ep_2$.
-	Then,
-	\begin{align*}
-		\braket{u}{v} =& \braket{Uu}{Uv} \\
-		=& (a^{-1}\bra{u}+\bra{u'})(b\ket{v}+\ket{v'})\\
-		=& a^{-1}b \braket{u}{v} + a^{-1}\braket{u}{v'}
-		+ b \braket{u'}{v} + \braket{u'}{v'},
-	\end{align*}
-	which implies that 
-	\begin{align*}
-		\norm{\braket{v}{u}} &= \frac{\norm{a^{-1}\braket{u}{v'} +  b\braket{u'}{v}+ \braket{u'}{v'}}}{\norm{1 - a^{-1}b}} \\
-		&\leq \frac{\norm{a}\norm{\ket{v}}\norm{\ket{u'}}+
-		\norm{b}\norm{\ket{u}}\norm{\ket{v'}} + 
-		\norm{\ket{u'}}\norm{\ket{v'}}}{\norm{1 - a^{-1}b}} \\
-		&\leq \max(\norm{\ket{u}}, \norm{\ket{v}})\frac{\ep_1+\ep_2}{\norm{1-a^{-1}b}}
-		+ \frac{\ep_1\ep_2}{\norm{1-a^{-1}b}}.
-	\end{align*}
-\end{proof}
-\begin{proposition}
-\label{prop:close_vec}
-	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$,
-	$\norm{\ket{v}} \appd{\ep_2} 1$, and $\braket{u}{v} \geq 1 - \ep_3$.
-	Then
-	\begin{align*}
-		\ket{u} \appd{O(\sqrt{\ep_1+\ep_2+\ep_3})} \ket{v}.
-	\end{align*}
-\end{proposition}
-\begin{proof}
-	Direct calculation gives us that
-	\begin{align*}
-		\norm{\ket{u} - \ket{v}}^2 &= \norm{\ket{u}}^2 + \norm{\ket{v}}^2 - 2\braket{u}{v} \\
-		&\leq (1+\ep_1)^2 + (1+\ep_2)^2 - 2(1 - \ep_3)\\
-		&= 2(\ep_1+\ep_2+\ep_3)+ \ep_1^2 + \ep_2^2\\
-		& = O(\ep_1+\ep_2+\ep_3).
-	\end{align*}
-\end{proof}
-\begin{proposition}
-	Let $\ket{u}$ be a vector with norm less than or equal to $1$ such that for a unitary $U$,
-	\begin{align*}
-		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C.
-	\end{align*}
-	Then,
-	\begin{align*}
-		U^n \ket{u} \appd{n\ep} a^n \ket{u} \text{ for all } n \geq 1.
-	\end{align*}
-\end{proposition}
-\begin{proof}
-	We can prove it by induction. 
-	For $k=1$, the statement is satisfied.
-	Assume it holds for $k = n-1$ and consider $k = n$, then we have
-	\begin{align*}
-		&\norm{U^n \ket{u} - a^n\ket{u}} \\
-		\leq &\norm{U} \norm{U^{n-1} \ket{\psi} - a^{n-1}\ket{\psi}} + \norm{a^{n-1}}
-		\norm{U\ket{\psi} - a \ket{\psi}}\\
-		\leq &(n-1)\ep + \ep = n \ep,
-	\end{align*}
-	where we used the fact that $\norm{U} = 1$ and $\norm{a} \leq 1$.
-\end{proof}
-
-%===============================================
-\section{The binary linear system game $\LS(r)$}
-\label{sec:lsg}
-%===============================================
-In this section, we introduce a binary linear system game which is a component of the full test.
-This game is designed to enforce relations that should be satisfied by 
-Alice and Bob's observables.
-
-The inspiration comes from 
-Slofstra's seminal work~\cite{slofstra2017}, in which he
-embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
-into the solution group of a binary linear system game.  
-We generalize the relation $xyx^{-1} = y^2$ and embed the 
-following group
-\begin{align}
-    \Pg = \ip{u,o:uou^{-1} = o^r},
-\label{eq:pgroup}
-\end{align}
-for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
-The steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed 
-in the proofs of Proposition~$33$, Lemma~$29$ and Proposition $27$ of Ref.~\cite{slofstra2017}, 
-so the group $\Pg$ (\cref{eq:pgroup}) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}),
-and we obtain a chain of embeddings:
-\begin{align}
-\Pg \hookrightarrow \Pg_0 \hookrightarrow \Pg_1 \hookrightarrow \Gamma.
-\end{align}
-
-This section is structured as follows.
-In \cref{sec:g0}, we define the group $\Pg_0$ and prove that $\Pg$ is embedded in $\Pg_0$.
-In \cref{sec:g1}, we define the group $\Pg_1$ and prove that $\Pg_0$ is embedded in $\Pg_1$.
-\Cref{sec:gamma} contains the definition of the group $\Gamma$ and the proof that $\Pg_1$
-is embedded in $\Gamma$.
-The purposes of introducing each intermediate
-group are explained along the definition.
-Note that, we defer the full definitions of the representations of $\Pg_0$, $\Pg_1$ and $\Gamma$
-until \cref{sec:rep_gamma}. 
-Instead, We only highlight a few operators from a finite-dimensional representation of $\Gamma$.
-The representation will be used later to build the ideal strategy.
-In \cref{sec:gamma_def}, we construct $\LS(r)$ from $\Gamma$ and give the 
-formal definition of $\LS( r )$.
-
-%----------------------------------------
-\subsection{The group $\Pg_0$}
-\label{sec:g0}
-%----------------------------------------
-
-The group $\Pg_0$ is a conjugacy group (\cref{def:spe_conj_grp}), and is defined below.
-The purpose of this step is to embed $\Pg$ into a group where all the
-generators are of order-$2$, because
-it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single generator. On the other hand, 
-a homomorphism from $\Pg_0$ to a solution group can be easier to find.
-\begin{definition}	
-\label{def:g0}
-	Let the set $S_0$ be 
-	\begin{align*}
-		S_0 = \{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5,
-	\end{align*}
-	and the set $R_0$ be the union of 
-	\begin{align*}
-	&R_{base} = \{s^2 = e | s \in S\},\\
-	&R_{u} = \{ u_3 = u_2o_1u_2 \quad u_4 = u_2o_2u_2 \quad 
-	u_5 = u_1u_3u_1 \quad o_2 = u_1u_4u_1 \quad u_5 = o_1 o_r o_1\},
-	\end{align*}
-	and 
-	\begin{align*}
-	R_o = 
-	\begin{cases} 
-	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1 \quad o_{2+2j} = o_2o_{1+2j}o_2\} \quad \text{ if $r$ is even },\\
-	\{o_3 = o_2o_1o_2\} \cup \bigcup_{j=1}^{(r-3)/2}\{
-	 o_{2+2j} =o_1o_{1+2j}o_1 \quad o_{3+2j} = o_2o_{2j+2}o_2 \}\quad\text{ if $r$ is odd }.
-	\end{cases}
-	\end{align*}
-	The group $\Pg_0$ is a group with presentation $\ip{R_0:S_0}$.
-\end{definition}
-The special generators of $\Pg_0$ are $o_1, o_2, u_1$ and $u_2$ because the product $o_1o_2$ behaves similarly as $o$
-and the product $u_1u_2$ behaves similarly as $u$.
-Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$,
-as proved in the next proposition.
-\begin{proposition}
-    \label{prop:g0}
-	The group $\Pg$ is embedded in $\Pg_0$.
-	Furthermore, the generators of $\Pg_0$ satisfy the relation 
-	\begin{align}
-	    \label{eq:uo_comm}
-	    &(u_1u_2) o_2 (u_2u_1) = o_2 \\ 
-	    \label{eq:uo_rel}
-		&(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
-	\end{align}
-	for any $ j \in \N$.
-\end{proposition}
-\begin{proof}
-    We prove \cref{eq:uo_comm} first. It is easy to see that
-    \begin{align}
-        u_1 (u_2o_2u_2) u_1 = u_1u_4u_1 =o_2.
-    \end{align}
-
-    Next, we prove that $\Pg$ is embedded in $\Pg_0$ by prove the $j = 1$ case of \cref{eq:uo_rel}.
-    The proof of Proposition $33$ of Ref.~\cite{slofstra2017} gives the recipe about
-    how to construct a finite-dimensional representation of $\Pg_0$ from a 
-    finite-dimensional representation of $\Pg$, so Lemma $15$ of Ref.~\cite{slofstra2017}
-    proves that a homomorphism $\phi: \Pg \rightarrow \Pg_0$ such that $\phi(u) = u_1u_2$ and 
-    $\phi(o) = o_1o_2$ is injective.
-
-	We prove \cref{eq:uo_rel} by induction.
-	The base case follows the direct calculation given below
-	\begin{align*} 
-		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
-	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
-	=& u_5 o_2\\
-	=& o_1o_ro_1 o_2.
-	\end{align*}
-	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above, which 
-	proves the $j=1$ case.
-
-	Now assume the statement is true for $j = n$, then for $j = n+1$
-	\begin{align*}
-		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
-		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
-		 =& (o_1o_2)^{r^{n+1}},
-	\end{align*}
-	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$, and
-	from the second line to the third line, we applied the $j=1$ case. Hence, the statement is true.
-\end{proof}
-Note that our representation $\Psi_0$ of $\Pg_0$ is different from the representation
-constructed in the proof of Proposition $33$ of Ref.~\cite{slofstra2017}.
-We give the formal definition of $\Psi_0$ (\cref{def:rep_g0}) in \cref{sec:rep_gamma}.
-
-To better characterize all the conjugacy
-relations of $\Pg_0$ and simplify the form of $\Pg_0$, 
-we relabel $u_i$ and $o_i$'s as $a_i$'s such that
-\begin{align}
-	a_j := 
-	\begin{cases}
-	 o_j \text{ for } j = 1,2 \\
-	 u_{j-2} \text{ for } j = 3\dots 7 \\
-	 o_{j-5} \text{ for } j = 8 \dots r+5.
-	\end{cases}
-\end{align}
-Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
-\begin{align}
-\label{eq:cr}
-	C(r) = \{ (i,j,k) |  (a_ia_ja_i = a_k) \in R_0 \}.
-\end{align}
-The size of $C(r)$ is $r+3$. 
-Hence, another presentation of the group $\Pg_0$ is
-\begin{align*}
-    \Pg_0 = \ip{ \{a_i\}_{i=1}^{r+5} : \{a_i^2 =e \}_{i=1}^{r+5} \cup \{ a_ia_ja_i = a_k \vert (i,j,k) \in C(r)\}},
-\end{align*}
-and we will construct $\Pg_1$ based on this presentation of $\Pg_0$.
-
-%---------------------------------
-\subsection{The group $\Pg_1$}
-\label{sec:g1}
-%---------------------------------
-The group $\Pg_1$ is a nice conjugacy group (\cref{def:nice_conj_grp}).
-We embed $\Pg_0$ into $\Pg_1$ to
-make the construction of a finite-dimension representation of $\Gamma$ from
-a finite-dimension representation of $\Pg_1$ easier.
-\begin{definition}
-\label{def:g1}
-Define the set $S_1$ to be
-\begin{align*}
-	S_1 = \{a_i, b_i, c_i, d_i\}_{i=1}^{r+5} \cup \{ f_0 \} \cup \{h_{jk}\}_{(i,j,k) \in C(r)},
-\end{align*}
-and the set $R_1$ to be
-\begin{align*}
-	R_1 = &\{ s^2 = e \vert s \in S_1\}\\ 
-	&\cup 
-	\{a_i = b_ic_i = f_0d_i, \quad f_0b_if_0 =c_i\}_{i= 1}^{r+5} \\ 
-	&\cup
-	\{h_{jk}b_j c_k = e, \quad d_ib_jd_i = c_k\}_{(i,j,k) \in C(r)}.
-\end{align*}
-The group $\Pg_1$ is a group with the presentation $\ip{S_1 : R_1}$.
-\end{definition}
-Note that the group $\Pg_1$ is the same as the group $K$ used in the proof of Lemma $29$ of Ref.~\cite{slofstra2017}.
-For each $1 \leq i \leq r+5$, the relation $a_i = b_ic_i$ guarantees that $b_i$ commutes with $c_i$.
-For each $(i,j,k) \in C(r)$, the linear relation $h_{jk} b_j c_k = e$ guarantees that
-$b_j$ commutes with $c_k$.
-
-The relation between $\Pg_0$ and $\Pg_1$ is summarized in the propositions below, which 
-is a specific case of Lemma $29$ of \cite{slofstra2017}.
-\begin{proposition}
-    \label{prop:g0g1}
-	The group $\Pg_0$ is embedded in $\Pg_1$. 
-\end{proposition}
-\begin{proof}
-    We prove this proposition by showing that generators $a_i$'s in $S_1$
-    satisfy the relation $a_i a_j a_i = a_k$ for all $(i,j,k) \in C(r)$.
-    This means the homomorphism $\phi: \Pg_0 \rightarrow \Pg_1$ that maps $a_i$
-    to $a_i$ is homomorphism from $\Pg_0$ to $\Pg_1$.
-
-	We first show that $d_i c_j d_i = b_k$, which is because
-	\begin{align*}
-		d_i c_j d_i = d_i (f_0 b_j f_0) d_i = f_0 (d_i b_j d_i) f_0 = f_0 c_k f_0 = b_k.
-	\end{align*}
-	Then, we can prove that 
-	\begin{align*}
-		a_i a_j a_i = f_0 d_i b_j c_j f_0 d_i 
-		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
-		= (f_0 c_k f_0)(f_0 b_k f_0) 
-		= b_k c_k = a_k,
-	\end{align*}
-	where we use the fact that $f_0$ commutes with $d_i$.
-
-	A representation of $\Pg_1$ can also be built upon a representation of $\Pg_0$.
-    Suppose $\Psi_0$ is a representation of $\Pg_0$ on some Hilbert space $\calH$, then 
-    a representation of $\Pg_1$, $\Psi_1$, on the Hilbert space $\C^2 \x \calH$ can
-    be constructed such that
-    \begin{align*}
-        &\Psi_1(a_i) = \1_{\C^2} \x \Psi_0(a_i)
-    \end{align*}
-    as proved in Lemma $29$ of Ref.~\cite{slofstra2017}.
-    Then, the injectivity of $\phi$ follows Lemma $15$ of Ref.~\cite{slofstra2017}.
-\end{proof}
-The consequence of this proposition is that $\Pg$ can be embedded in $\Pg_1$.
-We give the formal definition of the represention $\Psi_1$ of $\Pg_1$ 
-(\cref{def:rep_g1}) in \cref{sec:rep_gamma}.
-
-%-------------------------------------
-\subsection{The group $\Gamma$}
-\label{sec:gamma}
-%-------------------------------------
-The group $\Gamma$ is a solution group,
-so all the generators of $\Gamma$ are of order-$2$
-and all the relations are linear relations.
-Moreover, the linear relations can be combined
-to recover the conjugacy relations in $R_1$.
-\begin{definition}
-\label{def:gamma}
-Define the set $S$ to be 
-\begin{align*}
-	S = \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
-	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
-\end{align*}
-and the set $R$ to be the union of the following
-set of linear relations:
-\begin{itemize}
-\item for each $i = 1 \dots r+5$:
-\begin{align*}
-	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
-	%&g_2 a_i w_i = e \\
-	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
-	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
-\end{align*}
-\item for each $ \bc = (i,j,k) \in C(r)$:
-\begin{align*}
-	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
-	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
-	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
-\end{align*}
-\item 
-$
-	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
-	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
-$
-\item $R_J = \{ J s J s = e \vert s \in S\}$,
-\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
-\end{itemize}
-\hf{The group $\Gamma$ is a group with the presentation
-$\ip{S \cup \{J\} : R}$.}
-\end{definition}
-
-In the next proposition, we prove that the group $\Pg_1$ is embedded in $\Gamma$.
-\begin{proposition}
-    \label{prop:g1gamma}
-	The group $\Pg_1$ can be embedded in $\Gamma$.
-	The generators of $\Gamma$ also satisfy the relations: 
-	\begin{align}
-	    \label{eq:mg1} &f_0 g_0 f_0 g_0 = J,\\
-	    \label{eq:mg2} &f_2 g_2 f_2 g_2 = J.
-	\end{align}
-\end{proposition}
-\begin{proof}
-    To prove the first claim, we show that the generators
-    $b_i$, $c_i$, $d_i$ satisfy the relations
-    $d_ib_jd_i = c_k$ for each $\bc = (i,j,k) \in C(r)$.
-    \begin{align*}
-        d_ib_jd_i =& (k_{\bc 1} f_2)(f_2 k_{\bc 2})(k_{\bc 4} k_{\bc 5})\\ 
-        =& k_{\bc 1}(k_{\bc 2}k_{\bc 4})k_{\bc 5} \\
-        =& (k_{\bc 1} k_{\bc 3}) k_{\bc 5} \\
-        =& k_{\bc 6} k_{\bc 5} \\
-        =& c_k.
-    \end{align*}
-    The derivation of $f_0 b_i f_0 = c_i$ is similar for $1 \leq i \leq r+5$, so we omit it here.
-    Hence, a map $\phi:\Pg_1 \rightarrow \Gamma$ that maps $s$
-    to $s$ for each $s \in S_1$ is a homomorphism between $Pg_1$ and 
-    $Gamma$. 
-    A representation of $\Gamma$ can be constructed from a representation 
-    of $\Pg_1$ as shown in the proof of Proposition $27$ of Ref.~\cite{slofstra2017},
-    so Lemma $15$ of Ref.~\cite{slofstra2017} proves the homomorphism $\phi$
-    is injective.
-
-    The second claim follows a similar derivation
-    using linear relations in $R_{MS}$, so we omit it here.
-\end{proof}
-Since $\Pg$ is embedded in $\Pg_1$, we can conclude that
-$\Pg$ is embedded in $\Gamma$ as well.
-
-The representation $\Psi$ of $\Gamma$ is defined on the Hilbert space
-$W_2 \x W_2 \x W_{d-1}$,
-where $W_k$ denotes a Hilbert space of
-dimension $k$. 
-The formal definition of $\Gamma$ is defined in \cref{def:rep_gamma}
-in \cref{sec:rep_gamma}.
-We denote the
-standard basis of $W_k$ by $\{\ket{x_j}\}_{j=1}^{k}$.
-We define an operator $O$ on $W_{d-1}$ as
-\begin{align*}
-    O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}.
-\end{align*}
-Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, 
-where the subscript $r^j$ is taken modulo $d$ implicitly,
-because another form of $O$ is 
-\begin{align}
-    \label{eq:O}
-    O = \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}.
-\end{align}
-We use the second form of the basis when it is convenient.
-The other basis of $W_{d-1}$ that we use is $\{ \ket{u_j} \}_{j=0}^{d-2}$ given by
-\begin{align*}
-	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
-\end{align*}
-We denote the identity operator for the subspace $W_k$ by $\1_{W_k}$.
-The representations of $a_1, a_2, a_3$ and $a_4$ are 
-\begin{align}
-    \label{eq:o1} \Psi(a_1) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}}\right) \\
-    \label{eq:o2} \Psi(a_2) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}} \right).
-\end{align}
-\begin{equation}
-    \begin{aligned}
-    \label{eq:u1} \Psi(a_3) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ 
-    &+ \sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right) \Big]
-    \end{aligned}
-\end{equation}
-\begin{equation}
-    \begin{aligned}
-    \label{eq:u2}\Psi(a_4) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\
-	& + \sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right)\Big].
-    \end{aligned}
-\end{equation}
-
-The tensor structure of the representations come from the construction of $\Psi$.
-These operators are important because they give representations of generators 
-$u$ and $o$ of $\Pg$ as $\Psi(a_1a_2) = \1_{W_2} \x \1_{W_2} \x O$
-and $\Psi(a_3a_4) = \1_{W_2} \x \1_{W_2} \x U$ where $O$ is defined in \cref{eq:O} and
-\begin{align}
-    \label{eq:u1u2}
-    U = \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}}.
-\end{align}
-The operators $U$ and $O$ satisfy the relation $UOU\ct = O^r$.
-
-% A representation of $\Gamma$ can also be built from
-% a representation $\Psi_1$ of $\Pg_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$
-% that was constructed above.
-% We denote the representation of $\Gamma$ by $\Psi$ and
-% it is defined on $\C^2 \x \C^2 \x \calH$ such that
-% \begin{align*}
-%     \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
-%     s \in S_1.
-% \end{align*}
-% In particular, it means that for each $a_i \in S_0$
-% \begin{align*}
-%     \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
-% \end{align*}
-% Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
-% maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
-% by Lemma $15$ of Ref.~\cite{slofstra2017}.
-
-%---------------------------------------------------
-\subsection{Formal definitions}
-\label{sec:gamma_def}
-%---------------------------------------------------
-We define the solution group of the linear system game $\LS(r)$ first, following the steps described in the previous subsection.
-Then we define the game $\LS(r)$.
-
-From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
-we associate a variable $x(s)$ to each generator $s \in S$.
-Then each linear relation in $R$ can be translated to a linear equation.
-For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
-$f_1g_1m_2 = J$ is translated to the equation
-$x(f_1) + x(g_1) + x(m_2) = 1$. 
-The complete list of the equations is given in \cref{def:lsg_eq}.
-\begin{definition}
-\label{def:lsg}
-The linear system game $\LS(r)$ consists of
-\begin{align*}
-    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
-    & \calY^{\LS} = \{ x(s) : s \in S \},
-\end{align*}
-where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
-and $\mr := 14r + 62$ is the number of equations.  
-\carl{Since you are defining Alice's inputs to be subsets of S, why don't you just define Bob's inputs to be elements of S? Also, again you need to account that
-$J$ is an element of $S$.}
-\hfc{I think setting $\calY = S$ will cause confusion.
-You can see the forms of the equations in \cref{def:lsg_eq}.
-If I set the question set to be $S$, the reader will confuse the 
-linear equations with linear relation.
-I have moved $J$ out of $S$.}
-Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
-The answer sets are 
-\begin{align*}
-    \calA^{\LS} = (\Z_2)^{I_i} && \calB^{\LS} = \Z_2.
-\end{align*}
-The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
-\begin{align*}
-    \pi^{\LS}(I_i, x(s)) = 
-    \begin{cases}
-        1/N(r) & \text{ if } s \in I_i \\
-        0 & \text{otherwise,}
-    \end{cases}
-\end{align*}
-where $N(r) := 157r + 685$ is the total number of valid question pairs.
-We define $X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \}$, which is the set of all the valid answers of equation $i$.
-Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
-the score function is
-\begin{align*}
-    V^{\LS}_{I_i, x(s)}(\ba, b) = 
-    \begin{cases}
-        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
-        0 \text{, otherwise}.
-    \end{cases}
-\end{align*}
-\end{definition}
-
-The construction of $\LS(r)$ proves the following theorem.
-\begin{theorem}
-	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
-	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
-\end{theorem}
-\hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
-number of equation and variable pairs is $N(r)$ is of order $\Theta(r)$.}
-
-\hf{The ideal strategy of $\LS(r)$ is based on
-the representation $\Psi$ of $\Gamma$ defined in \cref{def:rep_gamma}
-of \cref{sec:rep_gamma}.
-We discuss the ideal strategy in in \cref{sec:tests}.
-Here we only highlight what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$, along
-with the important properties of the representation of these four generators,
-since they are the key generators of $\Gamma$.
-}
-
-% \begin{proposition}
-% 	In the group $\Gamma(\LS(r))$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
-% 	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
-% \end{proposition}
-% \begin{proof}
-% 	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
-% 	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
-% 	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
-% 	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
-% \end{proof}
-
-%====================================================
-\section{Extending the weighted CHSH inequality $\I_\alpha$ into a nonlocal test}
-\label{sec:ext_chsh}
-%====================================================
-In this section, we introduce the extended weighted CHSH test,
-which is going to be a component of the full test of \cref{sec:full_test}.
-The ideal correlation for this test contains the ideal correlation that 
-achieves $\I_{-\cot(\pi/d)}^{\max}$. 
-To make the study of the implication of a strategy that realize 
-the ideal correlation of the extended weighted CHSH test easier,
-we fill the background of the self-testing property of the
-general weighted CHSH inequality, $\I_\alpha$, first.
-
-%----------------------------------------------------
-\subsection{Robust self-testing of $\ket{EPR}$ \textit{via} $\I_\alpha$}
-\label{sec:chsh}
-%----------------------------------------------------
-In this section, we show how the weighted CHSH inequality can be used to self-test $\ket{EPR}$ and Pauli operators robustly.
-Intuitively, robust self-testing means that if some quantum strategy achieves a value $\I_\alpha$ that is close to $\I_\alpha^{\max}$,
-then the shared state must be close to $\ket{EPR}$ and their observables are close to the rotated Pauli operators 
-defined in \cref{def:ideal},
-up to some local isometry.
-The formal statement is given in the theorem below. Since the proof uses the same techniques as in Ref.~\cite{bamps2015},
-we defer the proof till \cref{sec:selftest}, and we only list the key relations used in the proof because they will be reused in \cref{sec:main}.
-\begin{theorem}
-\label{thm:selftest}
-    Define $\mu := \arctan(1/\alpha)$.
-	If a quantum strategy $(\ket{\psi}, \{M_x:=M_x^0-M_x^1\}_{x=1,2}, \{N_y :=N_y^0-N_y^1\}_{y = 1,2} )$ achieves that
-	$\I_\alpha \geq \I_\alpha^{\max} - \epsilon$
-	for some $\epsilon > 0$, then
-	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{junk}$  such that
-	\begin{align*}
-		\| \Phi( M_x \x N_y \ket{\psi}) -\ket{junk} \x (\tM_x \x \tN_y) \ket{EPR}  \| = O(\frac{1}{\cos^2(\mu)\sin^{1/2}(\mu)}+
-		\frac{1}{\sin(\mu)^{3/2}})) \sqrt{\epsilon}
-	\end{align*}
-	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $\tM_x, \tN_y$ are 
-	defined in \cref{def:ideal}.  
-\end{theorem}
-We follow the convention used in Ref.~\cite{bamps2015},
-which defines
-\begin{align*}
-	&Z_A := M_1 && X_A := M_2\\
-	&Z_B := \frac{N_1+N_2}{2\cos{\mu}} && X_B := \frac{N_1-N_2}{2\sin{\mu}}.
-\end{align*}
-Note that in \cref{sec:main}, we take $\mu = \pi/d$, so
-when we derive the error terms below, we only consider $\mu$ 
-that is close to $0$.
-The key relations that will be reuse are
-\begin{align}
-	\label{eq:za-zb}& Z_A\ket{\psi} \appd{O( \sqrt{\mu} \se)} Z_B\ket{\psi},\\
-	\label{eq:xa-xb}&X_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B \ket{\psi}, \\
-	\label{eq:xazb}&X_A(\1+Z_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} X_B(\1-Z_A) \ket{\psi},\\
-	\label{eq:zaxb}&Z_A(\1+X_B)\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} Z_B(\1-X_A) \ket{\psi},\\
-	\label{eq:zaxa}&Z_AX_A\ket{\psi} \appd{O(\frac{\se}{\sqrt{\mu}})} -X_AZ_A \ket{\psi},\\
-	\label{eq:zaxaxbzb}&X_AZ_A \ket{\psi} \appd{O(\frac{\se}{\mu^{3/2}})} -X_BZ_B \ket{\psi},
-\end{align}
-where \cref{eq:zaxaxbzb} can be derived from \cref{eq:za-zb}, \cref{eq:xa-xb} and \cref{eq:zaxa}.
-
-%-------------------------------------------
-\subsection{The extended weighted CHSH test}
-\label{sec:ext_w_chsh}
-%-------------------------------------------
-\begin{definition}
-    \label{def:ext_w_chsh}
-    In the extended weighted CHSH test, the input alphabets and output alphabets for Alice and Bob are
-    \begin{align*}
-        &\calX^{\EXT} = \calY^{\EXT} = \{0, 1, 2, \nr+1, \nr+2\}, \\
-        &\calA_z^{\EXT} = \calB_z^{\EXT} =
-        \begin{cases}
-            \{0,2\} &\text{ if } z = 0, \\
-            \{0,1\} &\text{ if } z \in \{1, 2\} \\
-            \{0,1,2\} &\text{ if } z \in \{\nr+1, \nr+2\}. 
-        \end{cases}
-    \end{align*}
-    The probability distribution over the question pairs is uniform.
-\end{definition}
-The reason why this test is called the extended weighted CHSH test will be clear 
-after we introduce the ideal strategy.
-
-Recall the Hilbert space $W_{d-1}$ defined in \cref{sec:gamma_def}. 
-To make the shared state and the observables of the ideal strategy have
-simpler forms, we introduce the third basis of $W_{d-1}$: $\{ \ket{j} \}_{j=1}^{d-1}$, \hf{which is defined by}
-\begin{align*}
-    &\ket{j} = -\frac{1}{\sqrt{2}}(\ket{x_j} + e^{-ij\pi/d}\ket{x_{d-j}}) \\
-    &\ket{d-j} = \frac{i}{\sqrt{2}}(\ket{x_j} - e^{-ij\pi/d}\ket{x_{d-j}})
-	%\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), \\
-	%\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j})
-\end{align*}
-for $1 \leq j \leq \frac{d-1}{2}$.
-The shared state of the ideal strategy is 
-\begin{equation}
-    \label{eq:tpsi}
-    \begin{aligned}
-        \ket{\tpsi}^{\EXT}
-         =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j}),
-    \end{aligned}
-\end{equation}
-where the superscript $\EXT$ stresses the fact this state is for the extended weighted CHSH test.
-Note that in the standard basis of $W_{d-1}$,
-\begin{align*}
-    \ket{\tpsi}^{\EXT} = \frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}.
-\end{align*}
-
-We define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$.
-The corresponding projective measurements are $\Pi_V$ and $\Pi_{V^\perp}$. Note that $V$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$.
-
-First of all, the ideal strategy ensures that when 
-Alice and Bob get the same question from the set $\{0,\nr+1,\nr+2\}$, they always give the same answer.
-Alice's and Bob's measurements for questions $0, \nr+1$ and $\nr+2$ are
-\begin{align*}
-	&\tP_0^0 = \tQ_0^0 = \Pi_V && \tP_0^2 = \tQ_0^2 = \Pi_{V^\perp} \\
-	&\tP_{\nr+1}^0 = \tQ_{\nr+1}^0 = \ketbra{1}{1} &&
-	\tP_{\nr+1}^1 = \tQ_{\nr+1}^1 = \ketbra{d-1}{d-1} \\
-	&\tP_{\nr+2}^0 = \tQ_{\nr+2}^0 = \ketbra{1_{\times}}{1_{\times}} && \tP_{\nr+2}^1 = \tQ_{\nr+2}^1 = \ketbra{(d-1)_{\times}}{(d-1)_{\times}} \\
-	&\tP_{\nr+1}^2 = \tQ_{\nr+1}^2 = \Pi_{V^\perp} &&
-	 \tP_{\nr+2}^2 = \tQ_{\nr+2}^2 = \Pi_{V^\perp},
-\end{align*}
-where
-\begin{align*}
-    \ket{1_{\times}} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
-	&&\ket{(d-1)_{\times}} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
-\end{align*}
-Intuitively, these questions force Alice and Bob to agree on the subspace $V$ and
-on the basis of $V$ that they will measure.
-
-The ideal strategy also ensures that 
-when Alice gets $x \in \{1,2\}$ and Bob gets $y \in \{\nr+1, \nr+2\}$, 
-their answers $a,b \in \{0,1\}$ should maximize $\I_{\cot(-\pi/d)}$ with Alice and Bob's roles flipped;
-and when Alice gets $x \in \{\nr+1,\nr+2\}$ and Bob gets $y \in \{1, 2\}$,
-their answers $a,b \in \{0,1\}$ should maximize $\I_{\cot(-\pi/d)}$.
-This is the reason behind naming this test the extended weighted CHSH test.
-It is also the reason behind having Alice and Bob agreeing on the subspace $V$ 
-by using the other three questions.
-Before introducing the measurements, 
-we define some basis states of $V$
-\begin{align*}
-	&\ket{1_+} = \cos(-\frac{\pi}{2d})\ket{1} + \sin(-\frac{\pi}{2d})\ket{d-1}
-	&&\ket{(d-1)_+} = \sin(-\frac{\pi}{2d})\ket{1} - \cos(-\frac{\pi}{2d})\ket{d-1}\\
-	&\ket{1_-} = \cos(-\frac{\pi}{2d})\ket{1} - \sin(-\frac{\pi}{2d})\ket{d-1}
-	&&\ket{(d-1)_-} = \sin(-\frac{\pi}{2d})\ket{1} + \cos(-\frac{\pi}{2d})\ket{d-1},
-\end{align*}
-so that $\{\ket{1_+}, \ket{(d-1)}_+\}$ and $\{\ket{1_-}, \ket{(d-1)_-}\}$ are two basis
-of $V$.
-When Alice and Bob gets question $1$ or $2$, what they measure on $V$ are
-\begin{align*}
-	&\tP_1^0 = \tQ_1^0 =  \ketbra{1_+}{1_+} && \tP_1^1 = \tQ_1^1 =  \ketbra{(d-1)_+}{(d-1)_+}\\
-	&\tP_2^0 = \tQ_2^0 =  \ketbra{1_-}{1_-} && \tP_1^1 = \tQ_1^1 =  \ketbra{(d-1)_-}{(d-1)_-}.
-\end{align*}
-Notice that their measurements on $V$ follow the measurements to achieve $\I_{\cot(-\pi/d)}^{\max}$.
-What they measure on $V^\perp$ is irrelevant for this test. 
-%Later we will see that their measurements on $V^\perp$ are determined by their observables for variables $x(a_1)$ and $x(a_2)$ of $\LS(r)$.
-
-We will present the ideal correlation of the extended weighted CHSH test
-in \cref{sec:cor} as part of the full correlation.
-
-%==========================
-\section{The full test}
-\label{sec:full_test}
-%==========================
-The full test consists of the linear system game $\LS(r)$,
-the extended weighted CHSH test and a commutation game. We explain how the games and test are conducted and
-introduce the ideal strategy for each of them in \cref{sec:tests}. 
-Then we explain how they are combined in the full test and present the ideal strategy for the full test in \cref{sec:ideal_strat}.
-The full correlation, denoted by $\fC(r,d)$, is generated by the ideal strategy and presented in \cref{sec:cor}.
-
-%----------------------------
-\subsection{The components of the full test}
-\label{sec:tests}
-%----------------------------
-
-The first component of the full test is $\LS(r)$ defined in
-\cref{def:lsg}.
-The ideal strategy of $\LS(r)$ follows the representation $\Psi$ of $\Gamma$ (\cref{def:rep_gamma}).
-Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}. 
-In the ideal strategy Alice and Bob share the state 
-\begin{align}
-    \label{eq:ideal_st_ls}
-        \ket{\tpsi}^{\LS} = \frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right).
-\end{align}
-Alice and Bob's observables for each variable $x(s)$ are
-defined by
-\begin{align*}
-    \tM(s) = \tN(s) = \Psi(s) 
-\end{align*}
-for each $s \in S$.
-
-The second component is the extended weighted CHSH test, introduced in \cref{sec:ext_w_chsh}.
-
-% Note that when the referee wants to ask Alice $x(a_1)$ or $x(a_2)$, which also labels a variable of $\LS(r)$, 
-% the referee gives Alice an equation label $i$ such that  
-% the equation $i$ contains the variable $x(a_1)$ or $x(a_2)$. 
-% For simplicity we omit the equation label in the alphabet $\calX$, and
-% later we will show that the equation label can be made implicit.
-% Only some of the question pairs of $\calX \times \calY$ are given to Alice and Bob.
-% Alice and Bob's ideal behaviour to pass this test is summarized 
-% below:
-% \carl{[Does the phrase ``ideal behavior'' have a formal definition?
-This seems to be another case where are you are writing in a way that is sort of formal, and sort of just a sketch -- that's not a good way to write.
-Do one or the other.]}
-% \begin{enumerate}
-% 	\item if $x = y = \ast$, Alice and Bob should answer with $a = b \in \{0, \perp\}$;
-% 	\item if $x = y \in \{x_{\nr+1}, x_{\nr+2}\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
-% 	\item if $x \in \{x(a_1),x(a_2)\}$ and $y \in \{x_{\nr+1}, x_{\nr+2}\}$, 
-% 		\begin{enumerate}
-% 		\item if they answer with $a,b \in \{0,1\}$, then
-% 	they should maximize $\I_{\cot(-\pi/d)}$ with Alice and Bob's roles flipped, 
-% 		\item if Bob answers with $\perp$, then Alice's answer doesn't matter;
-% 		\end{enumerate}
-% 	\item if $x \in \{x_{\nr+1}, x_{\nr+2}\}$ and $y \in \{x(a_1),x(a_2)\}$,
-% 	\begin{enumerate} 
-% 		\item if they answer with $a,b \in \{0,1\}$, then
-% 		they should maximize $\I_{\cot(-\pi/d)}$, 
-% 		\item if Alice answers with $\perp$, then Bob's answer doesn't matter;
-% 	\end{enumerate}
-% 	\item $x \in \{x_{\nr+1},x_{\nr+2}\}, y = \ast$ 
-% 		\begin{enumerate}
-% 		\item if Bob answers with $0$, Alice should answer with $\{0.1\}$ but not $\perp$, 
-% 		\item if Bob answers with $\perp$ Alice should answer with $\perp$ too;
-% 		\end{enumerate}
-% 	\item $x = \ast, y \in \{x_{\nr+1}, x_{\nr+2}\}$
-% 	\begin{enumerate}
-% 		\item if Alice answers with $0$, Bob should answer with $\{0.1\}$ but not $\perp$, 
-% 		\item if Alice answers $\perp$, Bob should answer $\perp$ too.
-% 	\end{enumerate}
-% \end{enumerate}
-% Only the question pairs mentioned in the list above are given to Alice and Bob.
-
-The third component is a commutation game.
-Our commutation game is the based on the commutation test used in Ref.~\cite{coladan2017verifier}.
-The goal of the commutation game is to make sure that some
-of Alice's binary observables for the other two tests 
-commute with each other when acting on the shared state,
-so we reuse questions and answers from the two other tests.
-
-Bob's input set consists of eight question pairs
-\begin{align*}
-    \calY^{\COMM} = \{(\nr+1, x(s)), (\nr+2, x(s)): s = f_0, f_2, g_0, g_2 \},
-\end{align*}
-and
-Alice's input set is 
-\begin{align*}
-    \calX^{\COMM} = \{\nr+1, \nr+2, f_0, f_2, g_0, g_2\}.
-\end{align*}
-The answer sets are 
-\begin{align*}
-    &\calA^{\COMM}_x = 
-    \begin{cases}
-    \Z_3 &\text{ if } x \in \{\nr+1, \nr+2\} \\
-    \Z_2 &\text{otherwise.}
-    \end{cases}
-    \\
-    &\calB^{\COMM} = \Z_3 \times \Z_2.
-\end{align*}
-The probability distribution is
-\begin{align*}
-    \pi^{\COMM}(x,(y_1,y_2)) =
-    \begin{cases}
-        1/16 &\text{ if } x = y_1 \text{ or } x = y_2 \\
-        0   &\text{ otherwise}.
-    \end{cases}
-\end{align*}
-The scoring function is
-\begin{align*}
-    V^{\COMM}(a, (b_1,b_2), x, (y_1,y_2)) = 
-    \begin{cases}
-    1 &\text{ if } x = y_1 \text{ and } a = b_1 \\
-    1 &\text{ if } x = y_2 \text{ and } a = b_2 \\
-    0 &\text{ otherwise}.
-    \end{cases}
-\end{align*}
-The probability distribution makes sure that Alice gets one of
-the two questions that Bob gets.
-To win this game, Alice and Bob should agree on the answer to the
-common question.
-We remark that if Alice's question is to assign a value to some variable of $\LS(r)$,
-the label of a equation that contains this variable is given 
-to Alice and the referee checks the bit corresponding to this
-variable in Alice's answer. This is equivalent to asking 
-Alice to measure an observable for the variable.
-
-We defer the ideal strategy for this test till next subsection because the ideal
-strategy to pass the two tests above can pass this test as well.
-
-% What we conclude is slightly different from the original claim
-% in Ref.~\cite{coladan2017verifier}.
-% Instead of just proving the binary observables commute,
-% we prove that the projective measurements
-% for question $\nr+1$ commute with the binary observables for question
-% $x(s)$ with $s = f_0, f_2, g_0, g_2$ 
-% by examining the probability distribution generated by the ideal strategy.  \carl{I don't think there's enough context for this paragraph.  It may be best to leave it out.}
-
-% In the full test, the three tests are conducted with equal probability.
-% The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first and then $\fC(d,r)$.
-%------------------------------------------------
-\subsection{The full test and the ideal strategy}
-\label{sec:ideal_strat}
-%-----------------------------------------------
-\begin{definition}[The full test]
-\label{def:full_test}
-Define 
-\begin{align*}
-    \calX^{\EXT'} = \calY^{\EXT'} = \{0, x(a_1), x(a_2), \nr+1, \nr+2\}.
-\end{align*}
-The question sets of the full test are
-\begin{align*}
-    \calX = \calX^{\LS} \cup \calX^{\EXT'} \cup \calX^{\COMM} \\
-    \calY = \calY^{\LS} \cup \calY^{\EXT'} \cup \calY^{\COMM},
-\end{align*}
-Define answer sets $\calA_x^{\EXT'}$ for each $x \in \calX^{\EXT'}$
-by setting 
-\begin{align*}
-    &\calA_{x(a_1)}^{\EXT'} =\calA_{1}^{\EXT} \\
-    &\calA_{x(a_2)}^{\EXT'} =\calA_{2}^{\EXT} \\
-    &\calA_{x}^{\EXT'} = \calA_{x}^{\EXT} 
-    \quad \text{ for } x \neq x(a_1), x(a_2)
-\end{align*}
-The answer sets $\calB_y^{\EXT'}$ are defined analogously.
-The answer sets of the full test are
-\begin{align*}
-    \calA_x = 
-    \begin{cases}
-    \Z_2^3 &\text{ if } x \in \calX^{\LS} \\
-    \calA_x^{\EXT'} &\text{ if } x \in \calX^{\EXT'} \\
-    \calA_x^{\COMM} & \text{ if } x \in \calX^{\COMM},
-    \end{cases}
-    &&
-    \calB_y = 
-    \begin{cases}
-    \Z_2 &\text{ if } y \in \calY^{\LS} \\
-    \calB_y^{\EXT'} &\text{ if } y \in \calY^{\EXT'} \\
-    \calB_y^{\COMM} & \text{ if } y \in \calY^{\COMM}.
-    \end{cases}
-\end{align*}
-Define $N$ to be the total number of question pairs with nonzero probability 
-of the three components of the full test.
-The question distribution of the full test, $\pi: \calX \times \calY \rightarrow \R$ is defined by
-\begin{align*}
-    \pi(x,y) = \begin{cases}
-    \frac{1}{N} & \text{ if } (x,y) \in \calX^{\LS} \times \calY^{\LS}
-    \text{ and } \pi^{\LS}(x,y) > 0 \\
-    \frac{1}{N} & \text{ if } (x,y) \in \calX^{\EXT'} \times \calY^{\EXT'}\\
-    \frac{1}{N} & \text{ if } (x,y) \in \calX^{\COMM} \times \calY^{\COMM} \text{ and } \pi^{\COMM}(x,y) > 0 \\
-    0 & \text{ otherwise}.
-    \end{cases}
-\end{align*}
-\end{definition}
-Note that $\calX^{\EXT'}$ is obtained from $\calX^{\EXT}$ by replacing 
-$1$ by $x(a_1)$ and $2$ by $x(a_2)$, and similarly for $\calY^{\EXT'}$.
-The answer sets $\calA_x^{\EXT'}$ are constructed from $\calA_x^{\EXT}$
-in a similar way.
-
-The ideal strategy for the full test is an extension of the ideal strategy of $\LS(r)$ to make it able to produce the ideal correlation of 
-the extended weighted CHSH test.
-Recall the subspace $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}.
-The shared state of the ideal strategy is
-\begin{align*}
-    \ket{\tpsi} = \ket{\tpsi}^{\LS} = \frac{1}{2}(\ket{x_1}\ket{x_1} + 
-    \ket{x_2}\ket{x_2})^{\x 2} \x \ket{\tpsi}^{\EXT}.
-\end{align*}
-Alice and Bob's observables for each variable in the linear system of 
-$\LS(r)$ are 
-\begin{align*}
-    \tM(s) = \tN(s) = \Psi(s) 
-\end{align*}
-for each $s \in S$ and $\Psi$ is defined in \cref{def:rep_gamma}.
-When Alice get $I_i \in \calX^{\LS}$, she measures her half of the shared
-state according to $\tM(s)$ for each $s \in I_i$.
-
-Alice's and Bob's observables for question $x(a_1)$ and $x(a_2)$ of $\calX^{\EXT'}$ and $\calY^{\EXT'}$ are
-\begin{align*}
-    \tM(a_j) = \tN(a_j) = \Psi(a_j) 
-\end{align*}
-for $j= 1,2$.
-They can reproduce the ideal correlation because
-\begin{align*}
-    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_1) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_1^0|_V - \tP_1^1|_V) \\
-    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_2) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_2^0|_V - \tP_2^1|_V),
-\end{align*}
-and similarly on Bob's side.
-In other words, the observables $\tM(a_j)$ and $\tN(a_j)$ are 
-measuring the same state on the subspace $V$ as $\tP_j$ and $\tQ_j$
-for $j = 1,2$.
-
-Alice's projectors for the other questions of $\calX^{\EXT'}$ are
-\begin{align*}
-    \tM_x^a = \1_{W_2} \x \1_{W_2} \x \tP_x^a
-\end{align*}
-for each $a \in \calA^{\EXT'}_x$.
-Bob's projectors for the other questions of $\calY^{\EXT'}$ are 
-\begin{align*}
-    \tN_y^b = \1_{W_2} \x \1_{W_2} \x \tQ_y^b
-\end{align*}
-for each $b \in \calB^{\EXT'}_y$.
-
-Alice's measurements for $x \in \calX^{\COMM}$ is the same as her
-measurements for the other two tests.
-When Bob gets question $(y_1, y_2) \in \calY^{\COMM}$, he measures 
-according to $\tN_{y_1}^b$ first and then $\tN(y_2)$ because $\tN_{y_1}^b$
-commutes with $\tN(y_2)$ for all $b$ by construction.
-This ensures that the ideal strategy can win the commutation game.
-
-An important property of the ideal strategy for it to win $\LS(r)$ is summarized in the 
-following proposition.
-\begin{proposition}
-The observables $\tM(s)$, $\tN(s)$
-and the shared state $\ket{\tpsi}$ defined above
-satisfy the relations
-\begin{align}
-	\label{eq:mn_preserve} &\tM(s) \tN(s) \ket{\tpsi} = \ket{\tpsi},
-\end{align}
-for each $s \in S$.
-\end{proposition}
-\begin{proof}
-    Define $S' = \{f_0, f_1, f_2, g_0, g_1, g_2, m_0, m_1, m_2\} \subset S$. Notice that for each $s \in S'$, both $\tM(s)$ and $\tN(s)$ act
-    trivially on $W_{d-1}$, so we omit the verification that 
-    $\tM(s)\tN(s) \ket{\tpsi} = \ket{\tpsi}$ for each $s \in S'$
-
-	Next, we notice that each $s \in S$ can be expressed as the 
-	product of a sequence of generators in $S'$ and $a_1, a_2, a_3, a_4$, so
-	to prove \cref{eq:mn_preserve}, it suffices to prove that it 
-	holds true for $s = a_1, a_2, a_3, a_4$. 
-	Recall that $\tM(a_j) = \tN(a_j) = \1_{W_2} \x \1_{W_2} \x Psi_0(a_j)$
-	in \cref{def:rep_gamma},
-	where $\Psi_0$ is defined in \cref{def:rep_g0},
-	and $\ket{\tpsi} = \frac{1}{2} (\ket{x_1}\ket{x_1}+\ket{x_2}\ket{x_2})^{\x 2} \x \ket{\tpsi}^{\EXT}$.
-	Hence, the problem is further reduced to proving
-	\begin{align*}
-	    \Psi_0(a_j) \x \Psi_0(a_j) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}.
-	\end{align*}
-	for $1 \leq j \leq 4$.
-
-	Using \cref{eq:o1,eq:o2}, it is straightforward to see that $\Psi_0(a_j)\x \Psi_0(a_j) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ for $j = 1,2$.
-	Before checking the two cases $j=3$ and $j=4$, we can use \cref{eq:u1u2} to derive that
-	\begin{align*}
-		\Psi_0(a_3 a_4) \x\Psi_0(a_3 a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}.
-	\end{align*}
-	The eigenvectors of $\Psi_0(a_3 a_4)$ are $\ket{u_k}$,
-	for $0 \leq k \leq d-2$,
-	and $\ket{u_k}$ are defined by
-    \begin{align*}
-        \ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
-    \end{align*}
-    Hence we can express $\ket{x_{r^j}}$ in terms of $\ket{u_k}$ as 
-    \begin{align*}
-        \ket{x_{r^j}} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
-    \end{align*}
-    Then using \cref{eq:u2} we can deduce that $\Psi_0(a_4)$ acts on $\ket{x_{r^j}}$ by
-    \begin{align*}
-        \Psi_0(a_4) \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} \tM(a_4) \left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
-        \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
-        =&\frac{1}{\sqrt{d-1}} \left(\ket{u_0} + (-1)^j\ket{u_{(d-1)/2}}  + 
-        \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_{d-1-k}} + \omega_{d-1}^{jk} \ket{u_{k}})\right) \\
-        =& \ket{x_{r^{d-1-j}}}.
-    \end{align*}
-    Consequently, we can show that $\Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ 
-    because
-    \begin{align*}
-        \Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \Psi_0(a_4)\x  \Psi_0(a_4) \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
-        = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\tpsi}^{\EXT},
-    \end{align*}
-	Combining it with the fact that $\Psi_0(a_3 a_4) \x \Psi_0(a_3 a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$, we can conclude that
-	$\Psi_0(a_3) \x \Psi_0(a_3) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$.
-\end{proof}
-
-%---------------------------------------------------
-\subsection{The correlation $\fC(d,r)$}
-\label{sec:cor}
-%---------------------------------------------------
-The full correlation is generated by the ideal strategy presented in the previous subsection.
-We denote the full correlation by $\fC(d,r) = \{( \tpr{ab}{xy} )_{a,b}\}_{x,y}$.
-To help readers to understand the proofs in \cref{sec:main} better, 
-parts of the full correlation is given in the tables below.
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{|c|c||c|c|}
-\hline
-\multicolumn{2}{|c|}{} &
-\multicolumn{2}{|c|}{$x=0$}\\
-\cline{3-4}
-\multicolumn{2}{|c|}{} &$a = 0$ & $a = 2$ \\
-\hline
-\hline
-\multirow{2}{*}{$y = 0$} & $b = 0$ & $2/(d-1)$ & $0$ \\
-\cline{2-4}
-&$b=2$ & $0$ & $(d-3)/(d-1)$ \\
-\hline
-\end{tabular}
-\caption{The correlation for $x=y=0$.}
-\end{center}
-\end{table}
-
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{|c|c||c|c|c|c|c|c|}
-\hline
-\multicolumn{2}{|c|}{} &
-\multicolumn{3}{|c|}{$x=\nr+1$}&
-\multicolumn{3}{|c|}{$x=\nr+2$} \\
-\cline{3-8}
-\multicolumn{2}{|c|}{} &
-$a = 0$ & $a=1$ & $a=2$ &
-$a = 0$ & $a=1$ & $a=2$\\
-\hline
-\hline
-\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
-& $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
-\cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
-&  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
-\hline
-\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
-$ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
-\cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
-$ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
-\hline
-\end{tabular}
-\end{center}
-\caption{The correlation for $x \in \{n+1, n+2\}$ and $y \in \{1,2\}$.}
-\label{tb:chsh}
-\end{table}
-We don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ for all possible $x$,$y$ 
-because they are irrelevant.
-Note that when $x \in \{1,2\}$ and $y \in \{\nr+1, \nr+2\}$, the correlation table is 
-the transpose of Table~\ref{tb:chsh}, so we omit it here.
-
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{|c|c||c|c|c|c|c|c|c|c|}
-\hline
-\multicolumn{2}{|c|}{} &
-\multicolumn{3}{|c|}{$x=\nr+1$}&
-\multicolumn{3}{|c|}{$x=\nr+2$}&
-\multicolumn{2}{|c|}{$x=0$}\\
-\cline{3-10}
-\multicolumn{2}{|c|}{} &
-$a = 0$ & $a=1$ & $a=2$ &
-$a = 0$ & $a=1$ & $a=2$ &
-$a = 0$ & $a =2 $\\
-\hline
-\hline
-\multirow{3}{*}{$y = \nr+1$} & $b=0$ & $\frac{1}{d-1}$ & $0$ & 0 
-& $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ & 0 & $\frac{1}{d-1}$ & 0 \\
-\cline{2-10}
-&$b=1$ & 0 & $\frac{1}{d-1}$ & $0$ 
-&  $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ & 0 &$\frac{1}{d-1}$ & 0 \\
-\cline{2-10}
-&$b=2$ & 0 & 0 & $\frac{d-3}{d-1}$ 
-&  0 & 0 &  $\frac{d-3}{d-1} $ &0 & $\frac{d-3}{d-1}$ \\
-\hline
-\multirow{3}{*}{$y = \nr+2$} & $b=0$ & $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ & 0 
-& $\frac{1}{d-1}$ & $0$ & 0 & $\frac{1}{d-1}$ & 0 \\
-\cline{2-10}
-&$b=1$ & $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ & $0$ 
-&  0 & $\frac{1}{d-1}$ & $0$ &$\frac{1}{d-1}$ & 0 \\
-\cline{2-10}
-&$b=2$ & 0 & 0 & \small $\frac{d-3}{d-1}$ 
-&  0 & 0 & \small $\frac{d-3}{d-1} $ &0 &\small $\frac{d-3}{d-1}$ \\
-\hline
-\multirow{2}{*}{$y = 0$} & $b=0$ & $\frac{1}{d-1}$ & $\frac{1}{d-1}$ & 0 
-& $\frac{1}{d-1}$ & $\frac{1}{d-1}$ & 0 & $\frac{2}{d-1}$ & 0 \\
-\cline{2-10}
-&$b=2$ & 0 & 0 & $\frac{d-3}{d-1}$ 
-&  0 & 0 & \small $\frac{d-3}{d-1} $ &0 & \small $\frac{d-3}{d-1}$ \\
-\hline
-\end{tabular}
-\end{center}
-\caption{The correlation for $x ,y\in\{\nr+1,\nr+2, \ast\} $.}
-\end{table}
-
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{|c|c||c|c|c|c|c|c|}
-\hline
-\multicolumn{2}{|c|}{} &
-\multicolumn{6}{|c|}{$y=(\nr+1, f_0)$}\\
-\cline{3-8}
-\multicolumn{2}{|c|}{} &
-$b = (0,0)$ & $b=(0,1)$ & 
-$b = (1,0)$ & $b=(1,1)$ &
-$b = (2,0)$ & $b=(2,1)$   \\
-\hline
-\hline
-\multirow{3}{*}{$x = \nr+1$} & $a=0$ & $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ &  $0$
-& $0$ & $0$ & $0$  \\
-\cline{2-8}
-&$a=1$ & $0$ & $0 $ & $\frac{1}{2d-2}$ 
-&  $\frac{1}{2d-2}$ & $0$ & $0$  \\
-\cline{2-8}
-&$a=2$ & 0 & 0 & $0$ 
-&  0 & $\frac{d-3}{2d-2}$ & $\frac{d-3}{2d-2} $  \\
-\hline
-\multirow{2}{*}{$x = f_0$} & $a=0$ & $\frac{1}{2d-2}$ & $0$ & $\frac{1}{2d-2}$ 
-& $0$ & $\frac{d-3}{2d-2}$ & 0  \\
-\cline{2-8}
-&$a=1$ & $0$ & $\frac{1}{2d-2}$ & $0$ 
-&  $\frac{1}{2d-2}$ & $0$ & $\frac{d-3}{2d-2}$  \\
-\hline
-\end{tabular}
-\end{center}
-\caption{The correlation for the commutation test between $f_0$ and $\nr+1$.}
-\label{tbl:comm}
-\end{table}
-The correlation table for the other seven commutation games are similar.
-
-%=====================================
-\section{Robust self-testing with $\fC(d,r)$}
-\label{sec:main}
-%=====================================
-In this section, we examine the properties of a strategy $\bS$ that can reproduce the
-correlation $\fC(d,r)$ approximately and 
-prove that the shared state of $\bS$ must be close to the state $\ket{EPR}^{\x 2} \x \ket{\EPR{d-1}}$
-up to some local isometry.
-
-We first give the definition of an approximate strategy of a fixed correlation.
-\begin{definition}
-	For a correlation $\tilde{C} = (\tpr{ab}{xy})$,
-	we say a quantum strategy $\bS = (\ket{\psi}, \{M_x^a\}, \{N_y^b\})$
-	is an $\ep$-approximate quantum strategy of $\tilde{C}$, 
-	if it produces the correlation
-	$( \pr{ab}{xy} = \bra{\psi} M_x^a N_y^b \ket{\psi} )$ such that
-	\begin{align}
-	\label{eq:expect}
-	E_{(x,y)} \sum_{ab} \abs{\pr{ab}{xy} - \tpr{ab}{xy}} \leq \ep.
-	\end{align}
-\end{definition}
-In our full test, the probability distribution over all the question pairs $(x,y)$ is uniform.  \carl{[You need to address that in the definition itself (otherwise it's not a complete definition).]}
-\hfc{I think I did define the question distribution in \cref{def:full_test}. }
-The number of all the possible question pairs is 
-$N = \Theta(r)$.
-Considering that
-the number of possible output pairs is constant for each question pair $(x,y)$, 
-the approximate condition in \cref{eq:expect} directly implies that, if $\bS$ is an $\ep$-approximate strategy
-of $\fC(d,r)$, then
-\begin{align*}
-    \pr{ab}{xy} \appd{O(r\ep)} \tpr{ab}{xy},
-\end{align*}
-for all valid $(a,b,x,y)$ of the full test.
-
-In the next three subsections, we analyze the implication of an approximate strategy for the 
-three components introduced in \cref{sec:full_test}.
-
-%------------------------------------------------------------------------------------------
-\subsection{Implication of approximately winning $\LS(r)$}
-\label{sec:imp_lct}
-%------------------------------------------------------------------------------------------
-\hf{In this subsection, we study the implications of a strategy that can win $\LS(r)$ with probability close to $1$. We prove a series of 
-propositions, which lead us to \cref{prop:lct_adv}.
-\Cref{prop:lct_adv} is a key step of the self-testing proof in \cref{sec:self-test}.}
-
-Recall that in $\LS(r)$ the question pair is denoted by $(I_i,x(s))$ where $I_i$ 
-labels an equation and $x(s)$ is a variable for some $s \in I_i$. 
-For simplicity, we denote 
-Alice's observable for variable $x(s)$ in equation $i$ by $M_i(s)$ and
-Bob's observable for variable $x(s)$ by $N(s)$.
-
-The first implication of an approximate winning strategy is given in the proposition below.
-\begin{proposition}
-	\label{prop:lct_base}
-	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	\hf{Define $M(s) := M_i(s)$ where 
-	$i$ is the smallest among all $i$'s
-	such that $x(s) \in I_i$.}
-	Then, 
-	\begin{align}
-		&M(s) N(s) \ket{\psi} \appd{O(\sr\se)} \ket{\psi} \\
-		&\Pi_{s \in I_i} M(s) \ket{\psi} \appd{O(\sr\se)}(-1)^{c(i)} \ket{\psi}.
-	\end{align}
-\end{proposition}
-\carl{[This proposition doesn't seem well-phrased --- it doesn't seem useful  to simply claim the existence of binary observables $M ( s )$ without specifying how they are related to the strategy $S$.]}
-\hfc{How about now?}
-
-\begin{proof}
-The condition that $(\tpr{\ba b}{i s})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
-\begin{align*}
-\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{is} = 1
-\end{align*}
-for all $i = 1 \dots \mr$.
-It has been shown in Ref.~\cite{slofstra2017} that 
-\begin{align*}
-	\bra{\psi} M_i(s) N(s) \ket{\psi} &= 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{ij} -1.
-\end{align*}
-Using the fact that $\bS$ approximates the winning correlation of $\LS(r)$, 
-we can get that
-\begin{align*}
-	\bra{\psi} M_i(s) N(s) \ket{\psi} \appd{O(r \ep)} 2\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{is} - 1 = 1.
-\end{align*}
-\carl{[The previous sentence \& equation do not make sense to me.]}
-\hfc{Fixed.}
-Since $M_i(s)$ and $N(s)$ are binary observables, we know that
-\begin{align*}
-    \norm{M_i(s)\ket{\psi} - N(s)\ket{\psi}}^2 
-    = 2 - 2 \bra{\psi}M_i(s)N(s) \ket{\psi} 
-    \leq 2 - 2(1 - O(r\ep)) = O(r\ep),
-\end{align*}
-or equivalently,
-\begin{align*}
-	M_{i}(s) \ket{\psi} \appd{O(\sr\se)} N(s) \ket{\psi},
-\end{align*}
-for all $1 \leq i \leq \mr$ and $s \in S$.
-We define $M(s) := M_{i}(s)$ for the smallest $i$ such that $ s \in I_i$, then 
-\begin{align*}
-	M(s) N(s) \ket{\psi} & = M_{i}(s)N(s)\ket{\psi} \\
-	    & = N(s) M_{i}(s) \ket{\psi} \\
-	    &\appd{O(\sr\se)} N(s)^2 \ket{\psi} \\
-	    &= \ket{\psi}
-\end{align*}
-for all $s \in S$.
-
-The fact that $\bS$ is an $\ep$-approximate strategy also tells us that
-Alice gives satisfying assignment for each equation with probability $1 - O(r\ep)$,
-or equivalently,
-\begin{align*}
-	\Pi_{s \in I_i} M_{i}(s) \ket{\psi} \appd{O(\sr\se)} (-1)^{c(i)} \ket{\psi}
-\end{align*}
-for $1 \leq i \leq \mr$.
-If we replace each $M_{i}(s)$ with $M(s)$ in the equation above, we demonstrate the effect on a
-general case that $I_i = \{s_1, s_2, s_3\}$,
-\begin{align*}
-	&\norm{ M_{i}(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M(s_3) \ket{\psi}}\\
-	\leq & \norm{M_{i}(s_1)M_{i}(s_2)M_{i}(s_3)\ket{\psi} - M(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi}}+
-	\norm{M(s_1)M_{i}(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M_{i}(s_3) \ket{\psi}} +\\
-	&\norm{M(s_1)M(s_2)M_{i}(s_3) \ket{\psi} - M(s_1)M(s_2)M(s_3) \ket{\psi}}\\
-	\leq &3O(\sr\se) = O(\sr\se).
-\end{align*}
-Hence we can conclude that 
-\begin{align*}
-	\Pi_{s \in I_i} M(s) \ket{\psi} \appd{O(\sr\se)} (-1)^{c(i)}\ket{\psi}
-\end{align*}
-for $1 \leq i \leq \mr$.
-Note that with the same technique, we can prove that 
-\begin{align*}
-	\Pi_{s \in I_i} N(s) \ket{\psi} \appd{O(\sr\se)} (-1)^{c(i)}\ket{\psi}  
-\end{align*}
-for $1 \leq i \leq \mr$.
-\end{proof}
-
-To make the following derivations easier, we introduce the following terminology.
-\begin{definition}
-    Let $S$ be a set of generators, and $\{s_i\}_{i=1}^n$ and $\{s'_j\}_{j=1}^m$
-    be two sequences of $S$.
-    Define a relation $r$, \hf{whose equation form} is $\Pi_{i=1}^n s_i = \Pi_{j=1}^m s'_j$.
-    We say operators $\{M(s) : s \in S\}$ $\ep$-approximately satisfy the relation
-    $r$ on the state $\ket{\psi}$ if 
-    \begin{align*}
-        \Pi_{i=1}^n M(s_i)\ket{\psi} \appd{\ep} \Pi_{j=1}^m M(s'_j) \ket{\psi}. 
-    \end{align*}
-\carl{[Technically, the word ``relation'' refers to an element of the free group, not to an equation between elements of the free group, so you need to write this in a way that accounts for that.
-It's a minor issue but worth addressing.]}
-\hfc{How about this way?}
-\end{definition}
-In other words, \cref{prop:lct_base} is equivalent to the following proposition.
-\begin{proposition}
-    \label{prop:lct_group}
-    Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	Then the observables $\{ M(s) \}_{s \in S}$ and
-	$\{N(s)\}_{s \in S}$ $O(\sr \se)$-approximately satisfy
-	each relation $r \in R$ on the shared state $\ket{\psi}$, 
-	where $S$ and $R$ are defined in the definition of $\Gamma$ 
-	(\cref{def:gamma}).	
-\end{proposition}
-\hf{Recall that the group $\Pg_1$ (\cref{def:g1}) is embedded in $\Gamma$.  
-For details of the embedding, we refer to \cref{sec:embedding}.}
-Following the embedding procedure, we can prove the next proposition.
-\begin{proposition}
-    \label{prop:lct_pg1}
-    Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	Then the observables $\{ M(s) \}_{s \in S_1}$ and
-	$\{N(s)\}_{s \in S_1}$, defined in 
-\cref{prop:lct_group}, $O(\sr\se)$-approximately satisfy
-	each relation $r \in R_1$ on $\ket{\psi}$, 
-	where $S_1$ is the generator set of $\Pg_1$
-    and $R_1$ is the relation set of $\Pg_1$.	
-\end{proposition}
-
-\carl{[I don't think it's helpful
-to the reader to phrase this result in terms of $\Pg_1$, given that you never wrote out $\Pg_1$ in the main text.
-I think you should write this in such a way that a reader who hasn't read the appendix can follow what you're doing.
-(One possibility is to just prove the relations that you need, step by step, and then just add comments referring to how what you are doing parallels your proofs in the appendix.]}
-\hfc{We need all the relations from $\Pg_1$ (\cref{def:g1}) to recover relations of $\Pg_0$ (\cref{def:g0})
-so it is not possible to write out each one of them. 
-What I am doing is proving one of them and comment that the rest of them require the same argument.
-On the other hand, I don't think it is important for the reader to know the relations of $\Pg_1$
-or $\Pg_0$. The only relation that will feature in the self-test proof is the relation $UOU\ct = O^r$.}
-
-\begin{proof}
-    First, we prove 
-    \begin{align}
-        \label{eq:f0b1}
-        M(f_0)M(b_1)M(f_0) \ket{\psi} \appd{O(\sr\se)} M(c_1)\ket{\psi}
-    \end{align}
-    to demonstrate the techniques.
-    From the fact that Alice's observables $O(r\se)$-approximately satisfy the linear equations, we can get that
-    \begin{align*}
-        &M(f_0) \ket{\psi} \appd{O(\sr \se)} M(f_1)M(f_2)\ket{\psi} \\
-        &M(b_1) \ket{\psi} \appd{O(\sr \se)} M(f_2)M(p_{1,1}) \ket{\psi}\\
-        &M(f_0) \ket{\psi} \appd{O(\sr \se)} M(p_{1,3})M(p_{1,4}) \ket{\psi}
-    \end{align*}
-    Then we show how to expand $M(f_0)M(b_1)M(f_0)\ket{\psi}$
-    with the three equations above. The trick is to flip some 
-    operators to Bob's side using the relation $M(s) \ket{\psi} \appd{O(\sr \se)} N(s)\ket{\psi}$.
-    \begin{align*}
-        M(f_0)M(b_1)M(f_0) \ket{\psi} 
-        &\appd{O(\sr \se)}M(f_0)M(b_1)M(p_{1,3})M(p_{1,4}) \ket{\psi} \\
-        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})M(f_0)M(f_2)M(p_{1,1}) \ket{\psi} \\
-        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)M(f_0) \ket{\psi} \\
-        &\appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)M(f_1)M(f_2) \ket{\psi} \\
-        & \appd{O(\sr \se)} N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_2)N(f_2)N(f_1) \ket{\psi} \\
-        &= N(p_{1,4})N(p_{1,3})N(p_{1,1})N(f_1) \ket{\psi} \\
-        & \appd{O(\sr \se)} M(f_1)M(p_{1,1})M(p_{1,3})M(p_{1,4}) \ket{\psi}
-    \end{align*}
-    In the rest of the proof, we skip the steps of flipping observables from Alice to Bob's side and then flip back.
-    \begin{align*}
-        M(f_0)M(b_1)M(f_0) \ket{\psi}
-        &\appd{O(\sr \se)} M(f_1)M(p_{1,1})M(p_{1,3})M(p_{1,4}) \ket{\psi}\\
-        &\appd{O(\sr \se)} M(f_1)M(p_{1,2})M(p_{1,4})\ket{\psi} \\
-        &\appd{O(\sr \se)} M(p_{1,5})M(p_{1,4})\ket{\psi} \\
-        & \appd{O(\sr \se)} M(c_1) \ket{\psi},
-    \end{align*}
-    where from the second line to the third line, we used
-    the relation $M(p_{1,1})M(p_{1,2})M(p_{1,3})\ket{\psi} \appd{O(\sr \se)} \ket{\psi}$, and from the third line to the
-    fourth line, we used the relation 
-    $M(c_1)M(p_{1,4})M(p_{1,5})\ket{\psi} \appd{O(\sr \se)} \ket{\psi}$.
-    The proof for the other relations are similar.
-\end{proof}
-Note that essentially the proof above follows the proof of 
-\cref{prop:g1gamma}. Then we can follow the proof of \cref{prop:g0g1}
-to prove the next proposition.
-\begin{proposition}
-    \label{prop:lct_pg0}
-    Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	Then the observables $\{ M(s) \}_{s \in S_0}$ and 
-	$\{N(s)\}_{s \in S_0}$, defined in 
-\cref{prop:lct_group}, $O(\sr \se)$-approximately satisfy
-	each relation $r \in R_0$ on the shared state $\ket{\psi}$, 
-	where $S_0$ is the generator set of $\Pg_0$
-    and $R_0$ is the relation set of $\Pg_0$.	
-\end{proposition}
-Following the steps of the embedding of $(a_3a_4)^l a_1a_2(a_4a_3)^l = (a_1a_2)^{r^l}$ into $\Gamma$ presented in
-the proof of \cref{prop:g0},
-we can prove the following proposition.
-\begin{lemma}
-\label{prop:lct_adv}
-Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $\{M(s), N(s)\}_{s \in S}$ be the observables defined in 
-\cref{prop:lct_group}. 
-Then,
-\begin{align}
-	&M(a_1)M(a_2) (M(a_4)M(a_3))^l \ket{\psi}\appd{O(r^{l+1/2} \se)} (M(a_4)M(a_3))^l (M(a_1)M(a_2))^{r^l} \ket{\psi}, \\
-	&N(a_1)N(a_2) (N(a_4)N(a_3))^l \ket{\psi}\appd{O(r^{l+1/2} \se)} (N(a_4)N(a_3))^l (N(a_1)N(a_2))^{r^l} \ket{\psi}, 
-\end{align}
-for all $l \geq 1$.
-\end{lemma}
-\begin{proof}
-Proving the $l=1$ case is essentially proving that observables 
-$\{M(a_i)\}_{i=1}^4$ and $\{N(a_i)\}_{i=1}^4$
-$O(r^{3/2} \se)$-approximately satisfy the relation 
-$(a_3a_4)(a_1a_2)(a_4a_3) = (a_1a_2)^r$ on the shared state $\ket{\psi}$.
-The derivation follows the proof of \cref{prop:g0}.
-The $O(r^{3/2}\se)$ approximation error comes from the fact that 
-the derivation has $\Theta(r)$ steps, where each step substitutes in
-a different relation of $R_0$, 
-so we have
-\begin{align}
-	\label{eq:ls_comm_rel}
-	M(a_1)M(a_2) (M(a_4)M(a_3)) \ket{\psi} \appd{O(r^{3/2}\se)} (M(a_4)M(a_3))(M(a_1)M(a_2))^r \ket{\psi}.
-\end{align}
-Assume the statement is true for $l = n$ and consider the case that $l = n+1$,
-\begin{align*}
-	M(a_1)M(a_2) (M(a_4)M(a_3))^{n+1} \ket{\psi}  &\appd{O(\sr \se)} (N(a_3)N(a_4)) M(a_1)M(a_2)(M(a_4)M(a_3))^n \ket{\psi} \\
-	&\appd{O(r^{n+1/2}\se)} (N(a_3)N(a_4)) (M(a_4)M(a_3))^n (M(a_1)M(a_2))^{r^n} \ket{\psi}\\
-	&\appd{O(\sr \se)} (M(a_4)M(a_3))^n (M(a_1)M(a_2))^{r^n} (M(a_4)M(a_3)) \ket{\psi} \\
-	& \appd{O(r^{n+3/2} \se)} (M(a_4)M(a_3))^{n+1} (M(a_1)M(a_2))^{r^{n+1}} \ket{\psi},
-\end{align*}
-where from the second to the last line we repeat the process of applying \cref{eq:ls_comm_rel} 
-and the relation $(M(a_1)M(a_2))^r \ket{\psi} \appd{O(r^{3/2}\se)} (N(a_1)N(a_2))^r \ket{\psi}$, $r^n$ times.
-In summary, we have 
-\begin{align}
-	M(a_1)M(a_2)(M(a_4)M(a_3))^{n+1} \ket{\psi} \appd{O(r^{n+3/2} \se)} (M(a_4)M(a_3)^{n+1} (M(a_1)M(a_2))^{r^{n+1}}\ket{\psi}.
-\end{align}
-By the principal of induction, the proof is complete.
-The proof for Bob's observables $\{ N(s) \}_{s \in S}$ is analogous.
-\end{proof}
-%An informal justification of the corollary is the following calculation
-%\begin{align}
-%	M_1M_2(M_4M_3)^k \ket{\psi} &\appd{O((k-1)r\se)} (N_3N_4)^{k-1} M_1M_2(M_4M_3) \ket{\psi} \\
-%	&\appd{O(r\se)} (N_3N_4)^{k-1}(M_4M_3) (M_1M_2)^r \ket{\psi} \\
-%	&\appd{O(r\se)} (N_4N_4)^{k-2} (M_4M_3) (M_1M_2)^{r} (M_4M_3) \ket{\psi}\\
-%	&\appd{O(r^2 \se)} (N_4N_3)^{k-2} (M_4M_3)^2 (M_1M_2)^{r^2} \ket{\psi} \\
-%	& \ldots (k-2  \text{ more such swaps} ) \ldots \\
-%	&\appd{O(r^{k-1}\se)} (M_4M_3)^{k} (M_1M_2)^{r^{k}}\ket{\psi}.
-%\end{align}
-%The total distance introduced by the whole procedure above is
-%\begin{align}
-%	\sum_{j=0}^{k-1} O(r^j \se) = O(r^k \se).
-%\end{align}
-
-If we define $O_A := M(a_1)M(a_2)$ and $U_A := M(a_3)M(a_4)$, then
-the conclusion of \cref{prop:lct_adv} can be rewritten as 
-\begin{align*}
-	 O_A (U_A\ct)^n \ket{\psi} \appd{O(r^{n+1/2} \se)} (U_A\ct)^n O_A^{r^n} \ket{\psi}.
-\end{align*}
-On Bob's side, we also define $O_B = N(a_1)N(a_2)$ and $U_B = N(a_3)N(a_4)$, 
-and the similar relation holds.
-
-The other relations that are embedded in $\Gamma$ are 
-$f_0g_0 = Jg_0f_0$ and $f_2g_2 = Jg_2 f_2$.
-We summarize the implications in the following proposition.
-\begin{proposition}
-	\label{prop:lct_comm}
-	Let $\bS$, $\{M(s), N(s)\}_{s \in S}$ be the strategy and observables defined in \cref{prop:lct_group}.
-	Then,
-	\begin{align}
-		&M(f_0)M(g_0) \ket{\psi} \appd{O(\sr \se)} -M(g_0)M(f_0) \ket{\psi} \\
-		&M(f_2)M(g_2) \ket{\psi} \appd{O(\sr \se)} -M(g_2)M(f_2) \ket{\psi}.
-	\end{align}
-\end{proposition}
-Recall all the relations in \cref{eq:mg1,eq:mg2} are embedded in the
-six Magic Square relations $R_{MS}$ of $\Gamma$ (\cref{def:gamma}), 
-so this proposition can be proved with the same techniques used in the proof of \cref{prop:lct_group}.
-%------------------------------------------------------------------------------------------
-\subsection{Implication of approximating the extended weighted CHSH test}
-\label{sec:imp_chsh}
-%------------------------------------------------------------------------------------------
-In this subsection, we prove a series of propositions and lemmas 
-derived from the fact that some strategy can approximate the ideal correlation of the extended weighted CHSH test,
-which lead to a key result that will be
-used in the self-testing proof in \cref{sec:self-test}.
-Note that in the following proofs, the observables $M_1$ and $M_2$ are
-equivalent to $M(a_1)$ and $M(a_2)$ respectively, because questions $1$ 
-and $2$ are equivalent to questions $x(a_1)$ and $x(a_2)$ in the full test.
-Similarly, on Bob's side, we have $N_1 \equiv N(a_1)$ and $N_2 \equiv N(a_2)$.
-For simplicity, in this subsection, we
-use $M_1, M_2$ and $N_1, N_2$.
-\begin{proposition}
-\label{prop:chsh_base}
-Let $\bS$ be an $\ep$-approximate quantum strategy of $\fC(d,r)$.
-Then the strategy $\bS$ satisfies the following relations
-\begin{align*}
-	  M_0^0 N_0^0 \ket{\psi}
-	  &\appd{O( \sr \se)}M_0^0 \ket{\psi}\\
-	  &\appd{O( \sr \se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi}\\
-	  &\appd{O( \sr \se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
-	  &\appd{O( \sr \se)} N_0^0 \ket{\psi}\\
-	  &\appd{O( \sr \se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi}\\
-	  &\appd{O( \sr \se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
-	M_0^2 N_0^2\ket{\psi}&\appd{O( \sr \se)} M_0^2 \ket{\psi}\\
-	&\appd{O( \sr \se)} M_{\nr+1}^2 \ket{\psi}\\
-	&\appd{O( \sr \se)} M_{\nr+2}^2 \ket{\psi}\\
-	&\appd{O( \sr \se)} N_0^2 \ket{\psi}\\
-	&\appd{O( \sr \se)} N_{\nr+1}^2 \ket{\psi}\\
-	&\appd{O( \sr \se)} N_{\nr+2}^2 \ket{\psi},
-\end{align*}
-and
-\begin{align*}
-&M_{\nr+1}^0 \ket{\psi} \appd{O( \sr \se)} N_{\nr+1}^0 \ket{\psi} && M_{\nr+1}^1\ket{\psi} \appd{O( \sr \se)} N_{\nr+1}^1 \ket{\psi}\\
-&M_{\nr+2}^0 \ket{\psi} \appd{O( \sr \se)} N_{\nr+2}^0 \ket{\psi} && M_{\nr+2}^1\ket{\psi} \appd{O( \sr \se)} N_{\nr+2}^1 \ket{\psi}.
-\end{align*}
-\end{proposition}
-
-\begin{proof} 
-We prove $(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(\sr \se)} N_0^0 \ket{\psi}$ as an example.
-The rest of the relations follow the same line of argument.
-
-Recall that the implication of $\bS$ being an $\ep$-approximate strategy is that 
-$\pr{ab}{xy} \appd{O(r \ep)} \tpr{ab}{xy}$ for all question 
-pair $(x,y)$ and associating answer pair $(a,b)$.
-From the correlation, we can observe that
-\begin{align*}
- &\bra{\psi} (M_{\nr+1}^0+M_{\nr+1}^1)N_0^0 \ket{\psi} \\
- = &\pr{0,0}{\nr+1,0} + \pr{1,0}{\nr+1,0}\\
- \geq &\frac{2}{d-1} - O(r \ep).
-\end{align*}
-On the other hand, the correlation also tells us that 
-\begin{align*}
-	&\bra{\psi} N_0^0 \ket{\psi} = \pb{0}{0} \appd{O(r\ep)} \frac{2}{d-1}\\
- &\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} 
- = \pa{0}{\nr+1} + \pa{1}{\nr+1}
- \appd{O(r\ep)} \frac{2}{d-1},
-\end{align*}
-which implies that 
-\begin{align*}
-	&\norm{(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - N_0^0 \ket{\psi}}^2 \\
-	= &\bra{\psi} N_0^0 \ket{\psi}+\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} - 2\bra{\psi}N_0^0(M_{\nr+1}^0 + M_{\nr+1}^1)N_0^0 \ket{\psi}\\
-	= &O(r \ep),
-\end{align*}
-where we used the fact that $(M_{\nr+1}^0 + M_{\nr+1}^1)^2 = M_{\nr+1}^0 + M_{\nr+1}^1$.
-Hence we can conclude that $(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \appd{O(\sr \se)} N_0^0\ket{\psi}$.
-%From the correlation, we know that 
-%\begin{align}
-%	\bra{\psi} M_\ast^\perp N_\ast^\perp \ket{\psi} = \frac{d-3}{d-1} - O(r^2 \ep).
-%\end{align}
-%In the mean time, we also have 
-%$\norm{M_\ast^\perp \ket{\psi}}^2 \appd{O(r^2\ep)} \norm{N_\ast^\perp\ket{\psi}}^2 \appd{O(r^2\ep)} (d-3)/(d-1)$.
-%The two facts above imply that 
-%\begin{align}
-%	\norm{M_\ast^\perp \ket{\psi} - N_\ast^\perp \ket{\psi}}^2 = \norm{M_\ast^\perp \ket{\psi}}^2 + \norm{N_\ast^\perp \ket{\psi}}^2
-%	- 2 \bra{\psi} M_\ast^\perp N_\ast^\perp \ket{\psi}  = O(r^2 \ep),
-%\end{align}
-%or equivalently,
-%\begin{align}
-%	M_\ast^\perp \ket{\psi} \appd{O(r\se)} N_\ast^\perp \ket{\psi}.
-%\end{align}
-\end{proof}
-
-\begin{proposition}
-	\label{prop:s1s2}
-	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$. We define
-	\begin{align}
-		&M_{\nr+1} = M_{\nr+1}^0 - M_{\nr+1}^1  && 
-		M_{\nr+2} = M_{\nr+2}^0 - M_{\nr+2}^1,\\
-		&N_{\nr+1} = N_{\nr+1}^0 - N_{\nr+1}^1  && 
-		N_{\nr+2} = N_{\nr+2}^0 - N_{\nr+2}^1.
-	\end{align}
-	Then $\bS$ induces two $O(d \sr \se)$-approximate strategies of the ideal correlation that achieves $\I_{\cot(-\pi/d)}^{\max}$, which are
-	\begin{align}
-		\bS_1 = \left(M_{\nr+1}, M_{\nr+2}, N_1, N_2, \frac{M_0^0\ket{\psi}}{\norm{M_0^0\ket{\psi}}}\right),\\
-		\bS_2 = \left(N_{\nr+1}, N_{\nr+2}, M_1, M_2, \frac{M_0^0\ket{\psi}}{\norm{M_0^0\ket{\psi}}}\right).
-	\end{align}
-\end{proposition}
-
-\begin{proof}
-To prove that $\bS_1$ achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, we need to examine terms of the form
-$\bra{\psi} M_0^0 M_{x}^a N_y^b M_0^0\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0,1$,
-which relate to $\bra{\psi} M_x^a N_y^b \ket{\psi}$ as follows,
-\begin{align*}
-	   \bra{\psi} M_{x}^aN_y^b \ket{\psi} 
-	&= \bra{\psi}(M_0^0 + M_0^2) M_x^a N_y^b (M_0^0 + M_0^2)\ket{\psi} \\
-	&=  \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_0^2\ket{\psi}\\
-	&\quad\quad+\bra{\psi}M_0^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^2 M_x^aN_y^b M_0^2\ket{\psi}\\
-	&\appd{O(\sr\se)}  \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_x^2\ket{\psi} \\
-	&\quad \quad +\bra{\psi}M_x^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_x^2 M_x^aN_y^b M_x^2\ket{\psi}\\
-	&=\bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi},
-\end{align*}
-where we use the facts that $M_0^2 \ket{\psi} \appd{O(\sr \se)} M_x^2 \ket{\psi}$ and that 
-$M_x^0 M_x^2 = 0$ for the relevant values of $(x,y,a,b)$.
-This means that if Alice and Bob share state $M_0^0 \ket{\psi}/\norm{M_0^0 \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$,
-they get conditional probability
-\begin{align*}
-	\frac{\bra{\psi}M_0^0 M_{\nr+1}^0N_1^0 M_0^0\ket{\psi}}{\bra{\psi} M_0^0 \ket{\psi}}  
-	\appd{O(d \sr \se)} \frac{\bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi}}{\bra{\psi} M_0^0 \ket{\psi}}
-	\appd{O(d r \ep)}
-	\frac{\cos^2(-\pi/2d)}{2}.
-\end{align*} 
-because
-\begin{align*}
-	\frac{ \norm{\bra{\psi}M_0^0 M_{\nr+1}^0N_1^0 M_0^0\ket{\psi} -  \bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi}}}
-	{\bra{\psi} M_0^0 \ket{\psi}} \leq \frac{O(\sr\se)}{\frac{2}{d-1} - O(r \ep)} = O(d \sr \se).
-\end{align*}
-The rest of the conditional probabilities produced by $\bS_1$ can be derived in the same way.
-Using the fact that $O(d \sr \se)$ dominates $O(d r \ep)$,
-we can prove that $\bS_1$ is an $O(d \sr\se)$-approximate strategy of the ideal correlation that achieves $\I_{\cot(-\pi/d)}^{\max}$.
-The proof for $\bS_2$ is analogous so we omit it here.
-\end{proof}
-Based on \cref{prop:chsh_base,prop:s1s2}, we identify a special component of $\ket{\psi}$, whose special properties are summarized
-in the proposition below. In the next lemma, we prove that this special component can be used to approximate $\ket{\psi}$. 
-\begin{proposition}
-    \label{prop:psi1}
-	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.
-	Then, the state
-	\begin{align}
-		&\ket{\psi_1} =1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi}.
-		%&\ket{\psi_2} = 1/2(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)  \ket{\psi} \\
-		%&\ket{\psi_4} =1/2(N_{\nr+1}^1 + iN_{\nr+2}N_{\nr+1}^1 -iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}
-	\end{align}
-	satisfies the following properties
-	\begin{align}
-	 %\text{ and } \ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_4}, \\
-	 %\label{eq:psi1_sum} &M_\ast^0 \ket{\psi} \appd{O( r\se)} \ket{\psi_1}+\ket{\psi_2}, \\
-	 %\label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
-	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(\sr\se)} 1/(d-1),\\
-	 \label{eq:psi1_eig1} &N_1N_2 \ket{\psi_1} \appd{O(\qr \qe/\sd)} \omega_d\ket{\psi_1} 
-	 && N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_1} \\
-	 \label{eq:psi1_eig2} &M_1M_2 \ket{\psi_1} \appd{O(\sd\qr \qe)} \omega_d^{-1} \ket{\psi_1}
-	 && M_2M_1 \ket{\psi_1} \appd{O(\sd\qr \qe)} \omega_d \ket{\psi_1}.
-	\end{align}
-\end{proposition}
-In this proof, we use the notation $c := \cos(\pi/d)$ and $s := \sin(\pi/d)$.
-\begin{proof}
-    \textbf{To prove \cref{eq:psi1_norm}}, 
-	we start by expanding the inner product
-	\begin{align*}
-		&\braket{\psi_1}{\psi_1} \\
-		=&1/4\bra{\psi}(M_{\nr+1}^0 - iM_{\nr+1}^1M_{\nr+2} + iM_{\nr+1}^0M_{\nr+2} +M_{\nr+1}^1)\\
-		&(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 -iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi}\\
-		=&1/2\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1-iM_{\nr+1}^1M_{\nr+2}M_{\nr+1}^0+iM_{\nr+1}^0M_{\nr+2}M_{\nr+1}^1\ket{\psi}
-	\end{align*}
-	Here we apply the trick to flip $M_{\nr+1}^1$ and $M_{\nr+1}^0$ to Bob's side and get 
-	\begin{align*}
-		\bra{\psi}M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^0\ket{\psi} 
-		&\appd{O(\sr\se)} \bra{\psi}N_{\nr+1}^1M_{\nr+2}N_{\nr+1}^0\ket{\psi} \\
-		&= \bra{\psi}N_{\nr+1}^1N_{\nr+1}^0M_{\nr+2}\ket{\psi} = 0.
-	\end{align*}
-	Similarly, we have $\bra{\psi}M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{ O(\sr \se)} 0$.
-	Hence, we get 
-	\begin{align}
-		\braket{\psi_1}{\psi_1} \appd{O(\sr\se)} 1/2\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1\ket{\psi} \appd{O(r\ep)} 
-		 \frac{1}{d-1}.
-	\end{align}
-%	Using the fact that for $0 < x < 1$, $\sqrt{1+x} = 1 + 1/2 x - O(x^2)$ and $\sqrt{1-x} = 1- 1/2x - O(x^2)$,
-%	we have
-%	\begin{align}
-%		1-\frac{(d-1)r^2 \ep}{2} \leq \sqrt{d-1} \norm{\ket{\psi_1}} \leq 1 + \frac{(d-1)r^2 \ep}{2},
-%	\end{align}
-%	and we conclude that 
-%	\begin{align}
-%		\norm{\ket{\psi_1}} \appd{O(\sd r^2 \ep)} \frac{1}{\sqrt{d-1}}.
-%	\end{align}
-
-	\textbf{To prove \cref{eq:psi1_eig1}},
-	we need to dive deeper into the implication of the fact that $\bS_1$ achieves $\I_{\cot(-\pi/d)}^{\max}$ approximately.
-	Define
-	\begin{align}
-		&Z_A  := M_{\nr+1} && X_A := M_{\nr+2} \\
-		&Z_B := \frac{N_1+N_2}{2c} && X_B := \frac{N_1-N_2}{-2s}.
-	\end{align}
-%	Note that $Z_A$ should be defined by $M_{\nr+1}^0 - M_{\nr+1}^1 + M_{\nr+1}^\perp$,
-%	but $M_{\nr+1}^\perp$ is almost orthogonal to $M_\ast^0$, so we omit the $M_{\nr+1}^\perp$ term here.
-%	In the definition of $X_A$, we omit $M_{\nr+2}^\perp$ too.
-	Recall \cref{eq:za-zb}, which states that
-	\begin{align*}
-		\norm{Z_B M_0^0 \ket{\psi} - M_{\nr+1}M_\ast^0 \ket{\psi}} \leq 
-		\sqrt{s}\norm{M_0^0 \ket{\psi}} O(\sd \qr \qe)
-		= O(\qr \qe/ \sd ).
-	\end{align*}
-	Since $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$,
-	the equation above can be rewritten as 
-	\begin{align*}
-		Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \appd{O(\qr \qe / \sd )} (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}.
-	\end{align*}
-	On the other hand, using the fact $M_{\nr+1}^0 M_{\nr+1}^1 = 0$, we can get that
-	\begin{align*}
-		O(\sr \se /d) \geq &\norm{Z_B (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - (M_{\nr+1}^0 - M_{\nr+1}^1) \ket{\psi}}^2\\
-		=&\norm{ Z_BM_{\nr+1}^0 \ket{\psi} - M_{\nr+1}^0\ket{\psi}}^2 + \norm{ Z_BM_{\nr+1}^1 \ket{\psi} + M_{\nr+1}^1\ket{\psi}}^2,
-	\end{align*}
-	which immediately gives us that 
-	\begin{align}
-		&\frac{N_1+N_2}{2c} M_{\nr+1}^0\ket{\psi} \appd{O( \qr \qe /\sd)} M_{\nr+1}^0 \ket{\psi},\\
-		&\frac{N_1+N_2}{2c} M_{\nr+1}^1\ket{\psi} \appd{O( \qr \qe /\sd)} -M_{\nr+1}^1 \ket{\psi}.
-	\end{align}
-		Substituting the appropriate operators and states into \cref{eq:zaxb,eq:xazb}, we get
-	\begin{align*}
-		\frac{N_1-N_2}{-2s} M_{\nr+1}^0M_0^0 \ket{\psi} 
-		\appd{\norm{M_0^0\ket{\psi}}/\sqrt{s} O(\sd \qr \qe)}M_{\nr+2} M_{\nr+1}^1M_0^0\ket{\psi}\\
-		\frac{N_1 -N_2}{-2s} M_{\nr+1}^1M_\ast^0 \ket{\psi}  
-		\appd{\norm{M_0^0 \ket{\psi}}/\sqrt{s}O(\sd \qr \qe)}M_{\nr+2} M_{\nr+1}^0 M_0^0 \ket{\psi}.
-	\end{align*}
-	Using the facts that $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}$
-	and $O(\sd \qr \qe)$ dominates $O(\sr \se)$, we know
-	\begin{align}
-		(N_1-N_2) M_{\nr+1}^0 \ket{\psi} \appd{O(\qr\qe/\sd )} -2sM_{\nr+2} M_{\nr+1}^1 \ket{\psi},\\
-		(N_1-N_2) M_{\nr+1}^1 \ket{\psi}\appd{O(\qr\qe/\sd )} -2sM_{\nr+2} M_{\nr+1}^0 \ket{\psi}.
-	\end{align}
-	In summary, we have shown that 
-        \begin{align*}
-        		&N_1M_{\nr+1}^0 \ket{\psi} \appd{O(\qr \qe/ \sd)} cM_{\nr+1}^0\ket{\psi} - sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
-        		&N_1M_{\nr+1}^1 \ket{\psi} \appd{O(\qr \qe/ \sd)} -cM_{\nr+1}^1\ket{\psi} - sM_{\nr+2}M_{\nr+1}^0\ket{\psi},\\
-        		&N_2M_{\nr+1}^0 \ket{\psi} \appd{O( \qr \qe /\sd)} cM_{\nr+1}^0\ket{\psi} + sM_{\nr+2}M_{\nr+1}^1\ket{\psi},\\
-        		&N_2M_{\nr+1}^1 \ket{\psi} \appd{O(\qr \qe/ \sd )} -cM_{\nr+1}^1\ket{\psi} + sM_{\nr+2}M_{\nr+1}^0\ket{\psi}.
-        \end{align*}
-        Then we can calculate that 
-        \begin{align*}
-        		&\quad N_1N_2 M_{\nr+1}^0 \ket{\psi} \\
-		        &\appd{O(\qr \qe/\sd)} (c N_1M_{\nr+1}^0 +sM_{\nr+2}N_1M_{\nr+1}^1)\ket{\psi}\\
-        		&\appd{O( \qr \qe/\sd)}(c^2M_{\nr+1}^0- csM_{\nr+2}M_{\nr+1}^1 -csM_{\nr+2}M_{\nr+1}^1 -s^2 M_{\nr+2}^2 M_{\nr+1}^0)\ket{\psi}\\
-        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^0 - \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.
-        \end{align*}
-        and 
-        \begin{align*}
-            &\quad N_1N_2 M_{\nr+1}^1 \ket{\psi} \\
-		    &\appd{O( \qr \qe/\sd)} (-c N_1M_{\nr+1}^1 +sM_{\nr+2}N_1M_{\nr+1}^0)\ket{\psi}\\
-        		&\appd{O(\qr \qe/\sd)}(c^2M_{\nr+1}^1+ csM_{\nr+2}M_{\nr+1}^0 +csM_{\nr+2}M_{\nr+1}^0 -s^2 M_{\nr+2}^2 M_{\nr+1}^1)\ket{\psi}\\
-        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^1 + \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^0)\ket{\psi},
-        \end{align*}
-        or equivalently,
-        \begin{align*}
-        		N_1N_2 M_{\nr+2}M_{\nr+1}^1 \ket{\psi}\appd{O(\qr \qe/\sd)} 
-		\sin(\frac{2\pi}{d}) M_{\nr+1}^0\ket{\psi} + \cos(\frac{2\pi}{d})M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
-        \end{align*}
-        Combining the two results above we know
-	\begin{align}
-		\label{eq:omegad}
-		&N_1N_2 (M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi} 
-		\appd{O(\qr \qe/\sd)}\omega_d(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
-	\end{align}
-	Multiplying both sides by $1/2(\1 - iM_{\nr+2})$, we get
-	\begin{align}
-		N_1N_2 \ket{\psi_1} \appd{O(\qr \qe/\sd)} \omega_d\ket{\psi_1}.
-	\end{align}
-	Note that here we use another form of $\ket{\psi_1}$ which is 
-	\begin{align*}
-	\ket{\psi_1} = 1/2(\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) \ket{\psi}.
-	\end{align*}
-	With similar calculations, we can get that 
-	\begin{align}
-	    N_2N_1 \ket{\psi_1} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_1}.
-	\end{align}
-
-	\textbf{To prove \cref{eq:psi1_eig2}}, we introduce an approximation of $\ket{\psi_1}$, which is 
-	\begin{align}
-	    &\ket{\psi_2} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi},
-	\end{align}
-	and we will first show that 
-	\begin{align}
-	    \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \qr\qe)} \ket{\psi_2}.
-	\end{align}
-
-	To prove \cref{eq:psi1_eq}, 
-	we first recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \se)} N_{\nr+1}^0 \ket{\psi}$ 
-	and $M_{\nr+1}^1 \ket{\psi} \appd{O(\sr \se)} N_{\nr+1}^1 \ket{\psi}$ from \cref{prop:chsh_base},
-	so it suffices to show
-	$(M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}$ is close to $(- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}$,
-%	or equivalently,
-%	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
-	At this point, we can use the anti-commutation relation (\cref{eq:zaxa}) induced by $\bS_1$  and conclude that 
-	\begin{align*}
-		M_{\nr+1}M_{\nr+2} M_\ast^0 \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^0\ket{\psi}}}}{c\sqrt{s}}O(\sd\qr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^0 \ket{\psi}.
-	\end{align*}
-	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \qr \qe)$.
-	Then we can show that 
-	\begin{align*}
-		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \\
-			&\appd{O(\sr\se)} M_{\nr+2}M_{\nr+1} M_0^0 \ket{\psi} \\
-			&\appd{O(\sd \qr \qe)} -M_{\nr+1}M_{\nr+2} M_0^0 \ket{\psi}\\
-			&\appd{O(\sr \se)} -M_{\nr+1}M_{\nr+2} \ket{\psi} \\
-			&\appd{O(\sr \se)} -M_{\nr+1} N_{\nr+2} \ket{\psi} \\
-			&\appd{O(\sr \se)} -N_{\nr+2} N_{\nr+1} \ket{\psi},
-	\end{align*}
-	where we use the fact that $M_0^0 \ket{\psi} \appd{O(\sr \se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(\sr \se)}
-	(M_{\nr+2}^0+M_{\nr+2}^1) \ket{\psi}$.
-
-	Next, we show that $M_1M_2 \ket{\psi_2}\appd{O(\qr \qe/\sd)} \omega_d^{-1} \ket{\psi_2}$, which gives
-	us \cref{eq:psi1_eig2} after substituting in\cref{eq:psi1_eq}.
-	From the strategy $\bS_2$, we can deduce that 
-	\begin{align}
-		&(M_1+M_2) N_{\nr+1}^0 \ket{\psi} \appd{O(\qr \qe/\sd)} 2c N_{\nr+1}^0 \ket{\psi}.\\
-		&(M_1+M_2) N_{\nr+1}^1 \ket{\psi}  \appd{O(\qr \qe/\sd)} -2cN_{\nr+1}^1 \ket{\psi},\\
-		&(M_1-M_2) N_{\nr+1}^0\ket{\psi} \appd{O(\qr\qe/\sd)}-2sN_{\nr+2} N_{\nr+1}^1\ket{\psi}\\
-		&(M_1-M_2)N_{\nr+1}^1 \ket{\psi} \appd{O(\qr\qe/\sd)} -2sN_{\nr+2} N_{\nr+1}^0 \ket{\psi}.
-	\end{align}
-	With similar calculation as in the previous case, we can get 
-	\begin{align*}
-		M_1M_2 (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi} \appd{O(\qr \qe/\sd)} 
-		\omega_d^{-1} (N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1)\ket{\psi} .
-	\end{align*}
-	Multiplying both sides of the equation above by $1/2(\1+iN_{\nr+2})$ we get
-	\begin{align}
-		M_1M_2 \ket{\psi_2} \appd{O(\qr \qe/\sd)} \omega_d^{-1}\ket{\psi_2},
-	\end{align}
-	where we use the fact that $\ket{\psi_2} = 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$
-	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \qr\qe)} \ket{\psi_2}$ gives us that 
-	\begin{align}
-		M_1M_2 \ket{\psi_1} \appd{O(\sd \qr \qe)} \omega_d^{-1}\ket{\psi_1}.
-	\end{align}
-	With similar derivation we can get that 
-	\begin{align}
-	    M_2M_1 \ket{\psi_1} \appd{O(\sd \qr \qe)} \omega_d\ket{\psi_1}.
-	\end{align}
-\end{proof}
-%Note that it can be shown that 
-%\begin{align}
-%	&\ket{\psi_1} =  (\1 - iA_{n+2})(\1 + i \frac{B_1 - B_2}{-2\sin(\pi/d)})A_{n+1}^0 \ket{\psi}\\
-%	&\ket{\psi_2} =  (\1 - iA_{n+2})(\1 + i \frac{B_1 - B_2}{-2\sin(\pi/d)})A_{n+1}^1 \ket{\psi}.
-%\end{align}
-Next lemma is the major result of this subsection, which gives us a decomposition of $\ket{\psi}$.
-Before proving the next lemma, we make one important observation.
-Recall that \cref{prop:lct_base} establishes that there exist observables $\{M(s), N(s)\}$ such that 
-$M(s)N(s) \ket{\psi} \appd{O(\sr\se)} \ket{\psi}$ for $s \in S$.
-Then we can deduce that 
-\begin{align*}
-	M(a_4)M(a_3) \x N(a_4)N(a_3) \ket{\psi} \appd{O(\sr\se)} M(a_4) \x N(a_4) \ket{\psi} \appd{O(\sr\se)} \ket{\psi},
-\end{align*}
-or equivalently,
-\begin{align*}
-	U_A\ct \x U_B\ct \ket{\psi} \appd{O(\sr\se)} \ket{\psi}.
-\end{align*}
-Intuitively, it means that $\ket{\psi}$ is invariant under the permutation induced by $U_A\ct U_B\ct$.
-We use this observation in the proof of the following lemma.
-\begin{lemma}
-\label{lm:decomp_psi}
-Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$ and 
-define 
-$\ket{\psi'} := \sum_{j=1}^{(d-1)} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}$
-with $\log_r j$ being the discrete log.
-Then,
-\begin{align}
-	&\ket{\psi} \appd{O(d r^{d/2} \ep^{1/8})} \ket{\psi'}.
-\end{align}
-\end{lemma}
-\begin{proof}
-	We first prove that $\norm{\ket{\psi'}}^2 \appd{O(d r^d \qe)} 1$.
-	Observe that 
-	\begin{align*}
-		\bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j}  \ket{\psi_1} =
-		\braket{\psi_1}{\psi_1} \appd{O(\sr\se)} \frac{1}{d-1}.
-	\end{align*}
-	Using the relation $O_B(U_B\ct)^j \ket{\psi} \appd{O(r^{j+1/2} \se)} (U_B\ct)^j O_B^{r^j}\ket{\psi}$ and \cref{eq:psi1_eig1}, we can deduce that 
-	\begin{align*}
-	    O_B (U_B\ct)^j \ket{\psi_1} &= \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1)  O_B (U_B\ct)^j \ket{\psi}\\
-	   & \appd{O(r^{j+1/2} \se)} \frac{1}{2} (\1 - iM_{\nr+2})(M_{\nr+1}^0 + i M_{\nr+2}M_{\nr+1}^1) (U_B\ct)^j 
-	   O_B^{r^j} \ket{\psi} \\
-	   & = (U_B\ct)^j O_B^{r^j} \ket{\psi_1} \\
-	   & \appd{O(r^{j+1/4} \qe/ \sd)} \omega_d^{r^j} (U_B\ct)^j\ket{\psi_1}
-	\end{align*}
-	In short, we have shown that 
-    \begin{align}
-        \label{eq:B_omega}
-        O_B (U_B\ct)^j \ket{\psi_1} \appd{O(r^{j} \qe/ \sd )} \omega_d^{r^j}  (U_B\ct)^j \ket{\psi_1},
-    \end{align}
-    where we drop the insignificant error term $r^{1/4}$.
-	%Using the relation $O_A(U_A\ct)^j \ket{\psi} \appd{O(r^j \se)} (U_A\ct)^j O_A^{r^j}\ket{\psi}$ and $\ket{\psi_1} \appd{O(\sd \sr \qe)} \ket{\psi_2}$ defined in the proof of \cref{prop:psi1},
-    %we can see that 
-    %\begin{align*}
-            % 	O_A (U_A\ct)^j \ket{\psi_1} &\appd{O(\sd \sr \qe)} O_A(U_A\ct)^j \ket{\psi_2} \\
-            % 	& = 1/2 (\1 + i N_{\nr+2})(N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1) O_A (U_A\ct)^j \ket{\psi} \\
-            % 	& \appd{O(r^j \se)} 1/2  (\1 + i N_{\nr+2})(N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1)  (U_A\ct)^j O_A^{r^j} \ket{\psi} \\
-            % 	& = (U_A\ct)^j O_A^{r^j} \ket{\psi_2} \\
-            % 	& \appd{O(r^j \sr \qe/\sd)} \omega_d^{-r^j}(U_A\ct)^j \ket{\psi_2} \\
-            % 	& \appd{O(\sd \sr\qe)} \omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
-    %\end{align*}
-    %In short, we have shown that 
-    With similar derivation, we can also get
-    \begin{align}
-    \label{eq:A_omega}
-        O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
-    \end{align}
-	Hence for $j \neq j'$, $(U_A\ct U_B\ct)^{j} \ket{\psi_1}$ and $(U_A\ct U_B\ct)^{ j'} \ket{\psi_1}$ are close to eigenvectors
-	of the unitary $O_B$ with different eigenvalues.
-	Applying \cref{prop:orthog} to \cref{eq:B_omega} gives us that  
-	\begin{align*}
-		\bra{\psi_1} (U_AU_B)^{j} (U_A\ct U_B\ct)^{ j'} \ket{\psi_1} \appd{O( (r^j + r^{j'}) \qe)} 0,
-	\end{align*}
-	where we use the fact that $\norm{1 - \omega_d^{r^{j'}-r^j}} = O(1/d)$.
-	We can calculate the norm of $\ket{\psi'}$ as 
-	\begin{align*}
-		\braket{\psi'}{\psi'} &=\sum_{j,j'=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j'} \ket{\psi_1}\\
-		&\appd{O(dr^{d} \qe)} \sum_{j=1}^{d-1} \bra{\psi_1} (U_AU_B)^{\log_r j} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}\\
-		&\appd{O(dr\se)} (d-1) \frac{1}{d-1} = 1.
-	\end{align*}
-
-	Next we calculate $\braket{\psi}{\psi'}$ which is
-	\begin{align*}
-		\braket{\psi}{\psi'} = \sum_{j=1}^{d-1} \bra{\psi} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1}
-		 \appd{O(d^2\sr\se)} (d-1) \braket{\psi}{\psi_1}.
-	\end{align*}
-	The problem is reduced to calculate $\braket{\psi}{\psi_1}$, which is
-	\begin{align*}
-		\braket{\psi}{\psi_1} &= \frac{1}{2} \bra{\psi} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi}\\
-		& = \frac{1}{2} \left(\bra{\psi}(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - i \bra{\psi}M_{\nr+2}M_{\nr+1} \ket{\psi} \right)\\
-		& \appd{O(\sr\se)} \frac{1}{2} \left(\bra{\psi}(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}  - i \bra{\psi}N_{\nr+2}M_{\nr+1} \ket{\psi} \right)\\
-		& \appd{O(r^2 \ep)} \frac{1}{2} \frac{2}{d-1} = \frac{1}{d-1},
-	\end{align*}
-	where the last approximation comes from the correlation.
-	Hence, we know $\braket{\psi}{\psi'} \appd{O(d^2 \sr \se)} 1$.
-	In the end, we apply \cref{prop:close_vec} to get
-	\begin{align*}
-		\ket{\psi} \appd{O(d r^{d/2} \ep^{1/8})} \ket{\psi'}.
-	\end{align*}
-\end{proof}
-
-%------------------------------------------------------------------------------------------
-\subsection{Implications of passing the commutation games}
-\label{sec:imp_comm}
-%-------------------------------------------------------------------------------------------
-The commutation games are introduced to certify the operators used in $\LS(r)$ commute with 
-the operators for the extended weighted CHSH test. For the details of the general commutation test, 
-we refer to Appendix~A.$2$ of \cite{coladan2017verifier}. 
-We use similar techniques in our proof but our proof also bases on the correlation given in \cref{tbl:comm}.
-
-The implication of winning the commutation games is summarized in the following proposition.
-\begin{proposition}
-	\label{prop:rel_comm}
-	Let $\bS$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	Then, 
-	\begin{align}
-		&M_{\nr+1}^0 M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+1}^0 \ket{\psi}, &&
-		M_{\nr+1}^1 M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+1}^1 \ket{\psi}, \\
-		\label{eq:com_nr2} &M_{\nr+2} M(s) \ket{\psi} \appd{O(\sr \se)} M(s) M_{\nr+2} \ket{\psi},
-	\end{align}
-	for $s = f_0, f_2,g_0,g_2$.
-\end{proposition}
-Note that the $M(s)$'s for $s = f_0, f_2,g_0,g_2$ tested in the commutation test are used for
-equations of the Magic Square game in $\LS(r)$,
-which will be used to construct the isometry in the next subsection.
-\begin{proof}
-	Proving \cref{eq:com_nr2} is an application of Lemma~$28$ of \cite{coladan2017verifier} with $\se$ replaced by $O(\sr \se)$.
-
-	For the other relations, we prove $M_{\nr+1}^0M(f_0) \ket{\psi} \appd{O(\sr \se)} M(f_0)M_{\nr+1}^0 \ket{\psi}$ to demonstrate 
-	the techniques involved. We denote Bob's projectors by $\{ N_{(\nr+1, f_0)}^{b_1 b_2} \}$ where $b_1 \in \{0, 1, 2\}$ and
-	$b_2 \in \{0,1\}$. From the correlation, we can get that 
-	\begin{align*}
-		&M_{\nr+1}^0 \ket{\psi} \appd{O(\sr \se)} 
-		(N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) \ket{\psi} \\
-		&M(f_0) \ket{\psi} \appd{O(\sr \se)} 
-		(\sum_{b_1, b_2} (-1)^{b_2} N_{(\nr+1, f_0)}^{b_1b_2})\ket{\psi}.
-	\end{align*}
-	Then we can show that
-	\begin{align*}
-		M_{\nr+1}^0 M(f_0) \ket{\psi} &\appd{O(\sr \se)} M_{\nr+1}^0 (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1,f_0)}^{b_1b_2})\ket{\psi}\\
-		&\appd{O(\sr\se)}(\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, f_0)}^{b_1b_2}) 
-		(N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) \ket{\psi} \\
-		&= (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) (\sum_{b_1, b_2} (-1)^{b_2}N_{(\nr+1, f_0)}^{b_1b_2})  \ket{\psi} \\
-		& \appd{O(\sr \se)} (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) M_{r+6} \ket{\psi} \\
-		&= M_{r+6}  (N_{(\nr+1, f_0)}^{00} + N_{(\nr+1, f_0)}^{01}) \ket{\psi} \\
-		& \appd{O(\sr\se)} M_{r+6}M(f_0)^0 \ket{\psi}.
-	\end{align*}
-\end{proof}
-%-----------------------------------------------
-\subsection{Robust self-testing}
-\label{sec:self-test}
-%-----------------------------------------------
-With the previous propositions and lemmas, we can prove the self-testing theorem.
-\begin{theorem}
-	\label{thm:self-test}
-	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$.
-	Then there exists an isometry   
-	$\Phi_A \x \Phi_B = (\Phi_{A,2} \x \Phi_{B,2})(\Phi_{A,1}\x\Phi_{B,2})$ and a state $\ket{junk}$
-	such that $\norm{\ket{junk}}^2 \appd{O(dr\se)} 1$ and 
-	\begin{align}
-		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
-		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
-		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d^{5/2}r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
-		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
-		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d^{5/2} r^{d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
-		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
-		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_{j r^{-1}}}_{B'}.
-	\end{align}
-\end{theorem}
-Before proving \cref{thm:self-test}, we state the consequence of it.
-It implies that,
-for any odd prime number $d$ with primitive root $r$, 
-there exists a correlation of size $\Theta(r^2)$ that can robustly self-test the maximally
-entangled state of local dimension $4(d-1)$.
-Moreover, there are infinitely many prime numbers
-whose primitive roots are in the set $\{2,3,5\}$ \cite{murty1988},
-Hence, our main result is the following theorem.
-\begin{theorem}
-	\label{thm:infty}
-	There exists an infinity-sized set $D$ of prime numbers such that 
-	for each $d \in D$, there exists
-	a constant-sized correlation that can self-test the maximally entangled state
-	of local dimension $4(d-1)$.
-\end{theorem}
-
-The isometry used in the proof of \cref{thm:self-test} has two steps. 
-We denote the isometry used in the first step and the second step by $\Phi_{A,1} \x \Phi_{B,1}$ and 
-$\Phi_{A,2} \x \Phi_{B,2}$ respectively, which are illustrated 
-in the two figures below.
-In the first step, 
-we use $U_A, O_A$ and $U_B$, $O_B$ to distill a copy of $\ket{\EPR{d-1}}$.
-In the second step. we use the observables $M_{r+6},M_{r+8}, M_{r+9}, M_{r+11}$ and 
-$N_{r+6}, N_{r+8}, N_{r+9}, N_{r+11}$ to distill two copies of $\ket{\EPR{2}}$.
-Intuitively, $M_{r+6}$ acts as $\1 \x \paulix$; $M_{r+8}$ acts as $\paulix \x \1 $;
-$M_{r+9}$ acts as $\1 \x \pauliz$ and $M_{r+11}$ acts as $\pauliz \x \1$; and similarly on Bob's side.
-
+where $\log_r j $ is the discrete log.
+This decomposition of $\ket{\psi}$ is the key observation that enables the application of the generalized swap-isometry.  
+\Cref{eq:decomp} is 
+proved in Section $6.2$ of the attached report, which uses \cref{eq:induct}.
+
+The combination of a linear system game with 
+additional correlations in the construction of $\fC(d,r)$ 
+is a new way to use linear system games for robust self-testing.
+It distinguishes our approach from all the previous ones.
+
+Our robust self-testing proof applies two
+local isometries $\Phi_{A,1} \x \Phi_{B,1}$ and
+$\Phi_{A,2} \x \Phi_{B,2}$ sequentially to the state $\ket{\psi}$, where $\Phi_{A,1} \x \Phi_{B,1}$ is 
+illustrated in the figure below and 
+$\Phi_{A,2} \x \Phi_{B,2}$ is the standard qubit swap-isometry used 
+in the robust self-testing proof of the Magic Square game \cite{wu2016}.
 \begin{figure}[H]
@@
         % Qubits
-        \node at (0,0) (q1) {$\ket{x_0}$};
+        \node at (0,0) (q1) {$\ket{0}$};
         \node at (0,-1) (q2) {};
         \node at (0,-2) (q3) {};
-        \node at (0,-3) (q4) {$\ket{x_0}$};
+        \node at (0,-3) (q4) {$\ket{0}$};
         %
@@
         \draw[decorate,decoration={brace},thick] (5,-1) to
-    	node[midway,right] (bracket) {$\ket{reuse}$}
+    	node[midway,right] (bracket) {$\ket{\psi_1}$}
     	(5,-2);
@@
         \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
-    	node[midway,right] (bracket2) {$\sum_{j=1}^{d-1}\ket{x_j}\ket{x_{d-j}}$}
+    	node[midway,right] (bracket2) {$\sum_{j=1}^{d-1}\ket{j}\ket{d-j}$}
     	(6.5,-2.5);
@@
 \end{figure}
-
-The first isometry has the following steps:
-\begin{enumerate}
-	\item Append control register $\ket{x_0}_{A'}$ on Alice's side and $\ket{x_0}_{B'}$ on Bob's side;
-	\item Apply Quantum Fourier Transform ($QFT_d$) to Alice and Bob's control registers;
-	\item Apply Controlled-$O_{A/B}$ operations (i.e. if the control register is in state $\ket{x_k}_{A'/ B'}$, apply
-	$O_{A/B}^k$.);
-	\item Apply inverse Quantum Fourier Transform ($QFT_d^{-1}$) to the control registers;
-	\item Apply Controlled-$U_{A/B}$ operations (i.e. If Alice's control register is in state $\ket{x_j}$, she applies
-	$U_A^{\log_r (d-j)}$. If Bob's control register is in state $\ket{x_j}$, he applies $(U_B)^{\log_r j}$).
-\end{enumerate}
-
-\begin{figure}[H]
-\center
-        \begin{tikzpicture}[thick]
-        %
-        % `operator' will only be used by Hadamard (H) gates here.
-        % `phase' is used for controlled phase gates (dots).
-        % `surround' is used for the background box.
-        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
-        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
-        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
-        %
-        % Bracket
-        \draw[decorate,decoration={brace,mirror},thick] (0,-2) to
-    	node[midway,left] (bracket1) {$\ket{reuse}$}
-    	(0,-3);
-        % Qubits
-        \node at (0,0) (q1) {$\ket{0}$};
-        \node at (0,-1) (q2) {$\ket{0}$};
-        \node at (0,-2) (q3) {};
-        \node at (0,-3) (q4) {};
-        \node at (0,-4) (q5) {$\ket{0}$};
-        \node at (0,-5) (q6) {$\ket{0}$};
-        %
-        % Column 1
-        \node[operator] (op11) at (1,0) {$H$} edge [-] (q1);
-        \node[operator] (op12) at (1,-1) {$H$} edge [-] (q2);
-         \node[operator] (op15) at (1,-4) {$H$} edge [-] (q5);
-        \node[operator] (op16) at (1,-5) {$H$} edge [-] (q6);
-        %
-        % Column 3
-        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
-	\node[operator] (op23) at (2,-2) {$M_{r+11}$} edge [-] (q3);
-	\node[operator] (op24) at (2, -3) {$N_{r+11}$} edge[-] (q4);
-        \node[phase] (phase16) at (2,-5) {} edge [-] (op16);
-        \draw[-] (phase11) -- (op23);
-        \draw[-] (phase16) -- (op24);
-        %
-        % Column 4
-        \node[phase] (phase12) at (3.5,-1) {} edge [-] (op12);
-	\node[operator] (op33) at (3.5,-2) {$M_{r+9}$} edge [-] (op23);
-	\node[operator] (op34) at (3.5, -3) {$N_{r+9}$} edge[-] (op24);
-        \node[phase] (phase15) at (3.5,-4) {} edge [-] (op15);
-        \draw[-] (phase12) -- (op33);
-        \draw[-] (phase15) -- (op34);
-        %
-         % Column 5
-        \node[operator] (op41) at (4.5,0) {$H$} edge [-] (phase11);
-        \node[operator] (op42) at (4.5,-1) {$H$} edge [-] (phase12);
-         \node[operator] (op45) at (4.5,-4) {$H$} edge [-] (phase15);
-        \node[operator] (op46) at (4.5,-5) {$H$} edge [-] (phase16);
-        %
-        % Column 6
-        \node[phase] (phase51) at (5.5,0) {} edge [-] (op41);
-	\node[operator] (op53) at (5.5,-2) {$M_{r+8}$} edge [-] (op33);
-	\node[operator] (op54) at (5.5, -3) {$N_{r+8}$} edge[-] (op34);
-        \node[phase] (phase56) at (5.5,-5) {} edge [-] (op46);
-        \draw[-] (phase51) -- (op53);
-        \draw[-] (phase56) -- (op54);
-        %
-        % Column 7
-        \node[phase] (phase62) at (7,-1) {} edge [-] (op42);
-	\node[operator] (op63) at (7,-2) {$M_{r+6}$} edge [-] (op53);
-	\node[operator] (op64) at (7, -3) {$N_{r+6}$} edge[-] (op54);
-        \node[phase] (phase65) at (7,-4) {} edge [-] (op45);
-        \draw[-] (phase62) -- (op63);
-        \draw[-] (phase65) -- (op64);
-        %
-        % Bracket
-        \node(end3) at (8, -2) {} edge [-] (op63);
-        \node(end4) at (8, -3) {} edge [-] (op64);
-        \draw[decorate,decoration={brace},thick] (8.2,-2) to
-    	node[midway,right] (bracket) {$\ket{junk}$}
-    	(8.2,-3);
-        %
-        % Column 7
-        \node (end1) at (9.5,-1) {} edge [-] (phase51);
-        \node(end2) at (9.5, -1.5) {} edge [-] (phase62);
-       \node(end5) at (9.5, -3.5) {} edge [-] (phase65);
-        \node (end6) at (9.5,-4) {} edge [-] (phase56);
-        % Dashed line
-        \draw[loosely dotted] (0,-2.5) -- (7.8,-2.5);
-        \draw[solid] (end1) -- (9.3, -1);
-        % Bracket
-        \draw[decorate,decoration={brace},thick,] (9.5,-1.1) to
-    	node[midway,right] (bracket2) {$\ket{\EPR{2}}^{\x 2}$}
-    	(9.5,-3.9);
-        %
-        % Background Box
-        \begin{pgfonlayer}{background} 
-        \node[surround] (background) [fit = (q1) (op16) (bracket1)(bracket2)] {};
-        \end{pgfonlayer}
-        %
-        \end{tikzpicture}
-	\caption{The isometries $\Phi_{A,2} \x \Phi_{B,2}$.}
-\end{figure}
-
-The second isometry is the standard isometry used in the self-testing result of the Magic Square game \cite{wu2016}.
-The only thing to note is that the state $\ket{reuse}$, which is on the same Hilbert space as $\ket{\psi}$ and produced by $\Phi_{A,1} \x \Phi_{B,1}$, is the input state to $\Phi_{A,2} \x \Phi_{B,2}$.
-In this sense, our isometry is a $2$-step sequential procedure.
-
-%We first list the key relations needed for $\Phi_{A,1} \x \Phi_{B,1}$ to work.
-%\begin{align}
-%	&\ket{\psi} \appd{O(d^{5/4} r^{d/2} r^{1/4} \ep^{1/8})}\ket{\psi'} = \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1},\\
-%	&O_A(U_A\ct)^{\log_r j} \ket{\psi_1} \appd{O(\sd r^j \sr \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}\\
-%	&O_B(U_A\ct)^{\log_r j} \ket{\psi_1} \appd{O(\sd r^j \sr \qe)}\omega_d^{r^j}  (U_A\ct)^j \ket{\psi_1}.
-%\end{align}
-%The second isometry just requires properties of the Magic Square game, especially, the commutation relations in \cref{prop:lct_comm}.
-
-\begin{proof}[Proof of \cref{thm:self-test}]
-The proof takes two steps. 
-We first show that 
-\begin{align}
-	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/2} r^{d+1/2} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
-\end{align}
-Then we show that there exists a state $\ket{junk}$ such that  
-\begin{align}
-\label{eq:phi2_result}
-\Phi_{A,2} \x \Phi_{B,2} (\sqrt{d-1}\ket{\psi_1}) \appd{O(r\se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2}.
-\end{align}
-Combining the two equations above we get that 
+Note that $QFT_d$ denotes the generalized Quantum Fourier Transform.
+With the help of \cref{eq:decomp}, we can prove that
 \begin{align*}
-	&\quad\Phi_{A,2} \x \Phi_{B,2}( \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi})) \\
-	&\appd{O(d^{5/2} \sr \ep^{1/8})} \Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \x\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
-	&\appd{O(r\se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
+    \Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d r^{d} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{j}\ket{d-j}.
 \end{align*}
-where we use the fact that $\Phi_{A,2}\x \Phi_{B,2}$ only acts on the state $\ket{\psi_1}$.
-
-\Cref{lm:decomp_psi} implies that $ \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi}) \appd{O(d r^{d/2 +1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi'})$,  
-so we focus on how the isometry evolves $\ket{\psi'}$.
-The evolution is summarized below.
+This is the first application of the generalized swap-isometry \cite{yang2013} to a robust self-testing proof.  
+Applying the second isometry to the state $\sqrt{d-1}\ket{\psi_1}$ gives us that
 \begin{align*}
-		& \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
-		\xrightarrow[]{QFT_d}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}  \ket{\psi_1}\ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\xrightarrow[]{\text{Controlled-}O_{A/B}}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} O_A^{k_1}(U_A\ct)^{\log_r j} O_B^{k_2}(U_B\ct)^{\log_r j}
-		\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(d^{5/2} r^{d} \sr \qe)}&\frac{1}{d} \sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}\omega_d^{(k_2-k_1)j}\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\xrightarrow[]{QFT_d^{-1}} &\frac{1}{d^2}\sum_{l_1,l_2 = 0}^{d-1}\sum_{k_1,k_2 = 0}^{d-1}\sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} 
-		\omega_d^{k_1(d-j-l_1)}\omega_d^{k_2(j-l_2)}\ket{\psi_1} \ket{x_{l_1}}_{A'}\ket{x_{l_2}}_{B'}\\
-		= &\sum_{j=1}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
-		\xrightarrow[]{\text{Controlled-}U_{A/B}}& \sum_{j=1}^{d-1} U_A^{\log_r j} (U_A\ct)^{\log_r j} U_B^{\log_r j} (U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
-		=&\ket{\psi_1} \x \sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
+    \Phi_{A,2}\x\Phi_{B,2}(\sqrt{d-1}\ket{\psi})
+    \appd{O(\sr \se)} \ket{junk} \x 
+    \ket{EPR}^{\x 2}.
 \end{align*}
-When we analyze the effect of the controlled-$O_{A/B}$, we applied \cref{eq:A_omega,eq:B_omega} repeatedly.
-In summary, we have shown that
-\begin{align}
-	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/2} r^{d+1/2} \ep^{1/8})} \sqrt{d-1} \ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'},
-\end{align}
-where we use the fact that $O(d^{5/2} r^{d+1/2} \ep^{1/8})$ dominates both $O(d r^{d/2+1/4} \ep^{1/8})$ and 
-$O(d^{5/2} r^{d+1/2} \qe)$.
-Since $\norm{\ket{\psi_1}}^2 \appd{O(r \se)} 1/(d-1)$, we know $ \sqrt{d-1} \norm{\ket{\psi_1}} \appd{O(\sd \sr\qe)} 1$.
-
-To prove \cref{eq:phi2_result}, we first
-recall that 
-$\ket{\psi_1} 
-	=\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi}.
-$
-The other observation that we need is that 
-\begin{align*}
-	&\Phi_{A,2} \x \Phi_{B,2} (\ket{\psi_1})  \\
-	= &\frac{1}{16} \sum_{\ba, \bb \in\{0,1\}^4}
-	M(f_0)^{a(4)}N(f_0)^{b(4)}M(f_2)^{a(3)}N(f_2)^{b(3)}M(g_0)^{a(2)}N(g_0)^{b(2)}M(g_2)^{a(1)}N(g_2)^{b(1)}
-	\ket{\psi_1} \ket{\ba}_{A''} \ket{\bb}_{B''}
-\end{align*}
-For simplicity we define $M^{\ba} := M(f_0)^{a(4)}M(f_2)^{a(3)}M(g_0)^{a(2)}M(g_2)^{a(1)}$ and
-$N^{\bb} := N(f_0)^{b(4)}N(f_2)^{b(3)}N(g_0)^{b(2)}N(g_2)^{b(1)} $.
-We would like to show that 
-\begin{align}
-\label{eq:mua_comm}
-M^{\ba} \ket{\psi_1} \appd{O(r\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)
-M^{\ba} \ket{\psi},
-\end{align}
-for all $\ba \in \{0,1\}^4$,
-%which implies that 
-%\begin{align*}
-%	\Phi_{A,2} \x &\Phi_{B,2} (\ket{\psi_1}) \appd{O(r\se)} \\
-%	&\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)(\Phi_{A,2} \x \Phi_{B,2}(\ket{\psi}))
-%\end{align*}
-%because $N^{\ub}$ commutes with $\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$
-%for all $\ub \in \{0,1\}^4$.
-which can be justified by \cref{prop:rel_comm}.
-We show how to apply \cref{prop:rel_comm} to commute $M(g_2)^{a(1)}$ through 
-$\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)$ and then similar process can be repeated for $M(g_0)^{a(2)}, M(f_2)^{a(3)}$ and $M(f_0)^{a(4)}$,
-\begin{align*}
-	&\quad M(g_2)^{a(1)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} \\
-	&\appd{O(\sr\se)} \frac{1}{2}[ (M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} -i M(g_2)^{a(1)} M_{\nr+2}N_{\nr+1}] \ket{\psi} \\
-	&\appd{O(\sr\se)} \frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M(g_2)^{a(1)} N_{\nr+1}] \ket{\psi} \\
-	&\appd{O(\sr\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M(g_2)^{a(1)} M_{\nr+1}] \ket{\psi} \\
-	&\appd{O(\sr\se)}\frac{1}{2} [(M_{\nr+1}^0+M_{\nr+1}^1) M(g_2)^{a(1)} - iM_{\nr+2}M_{\nr+1}M(g_2)^{a(1)} ] \ket{\psi}.
-\end{align*}
-In summary, we have 
-\begin{align}
-	M^{\ba} N^{\bb} \ket{\psi_1} \appd{O(\sr\se)} \frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)M^{\ba}N^{\bb} \ket{\psi}
-\end{align}
-for all $\ba, \bb \in \{0,1\}^4$, which implies that 
-\begin{align*}
-	\Phi_{A,2} \x& \Phi_{B,2}(\ket{\psi_1}) \appd{O(\sr\se)}\\
-	 &\frac{1}{2} (M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 + M_{\nr+1}^1)(\Phi_{A,2}\x\Phi_{B,2} (\ket{\psi}).
-\end{align*}
-At this point we can apply Lemma C.$1$ of \cite{wu2016} to $\Phi_{A,2}\x\Phi_{B,2} (\ket{\psi})$ and conclude that 
-\begin{align}
-	\Phi_{A,2} \x \Phi_{B,2}(\sqrt{d-1} \ket{\psi_1}) \appd{O(\sd \sr \se)} \ket{junk} \x \ket{\EPR{2}}^{\x 2},
-\end{align} 
-for some state $\ket{junk}$ whose norm can be deduced from the norm of $\ket{\psi_1}$.
-
-In the rest of the proof, we only show how $\Phi_{A,1} \x \Phi_{B,1}$ acts on $O_A\ket{\psi}$ and $U_A\ket{\psi}$.
-
-If the initial state is $O_A\ket{\psi}$, we first use the fact that 
-$ \Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi}) \appd{O(d^{5/4} r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi'})$, 
-and then we calculate $\Phi_{A,1} \x \Phi_{B,1} (O_A\ket{\psi'})$ as
-\begin{align*}
-	O_A \ket{\psi'} \ket{x_0}_{A'}\ket{x_0}_{B'} =&  
-		\sum_{j=1}^{d-1} O_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1}\ket{x_0}_{A'}\ket{x_0}_{B'}\\
-		\appd{O(\sd r^{d+1/2} \ep^{1/4})}&\sum_{j=1}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} \ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
-		\xrightarrow[]{QFT_d} &\frac{1}{d}\sum_{j=1}^{d-1} \sum_{k_1,k_2 = 0}^{d-1}(U_A\ct U_B\ct)^{\log_r j} \omega_d^{-j} 
-		\ket{\psi_1}\ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\xrightarrow[]{\text{Controlled-}O_{A/B}}&\frac{1}{d}\sum_{j=1}^{d-1}\sum_{k_1,k_2 = 0}^{d-1} 
-		 O_A^{k_1}(U_A\ct)^{\log_r j} O_B^{k_2}(U_B\ct)^{\log_r j} \omega_d^{-j} \ket{\psi_1} 
-		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(d^{5/2} r^{d+1/2}  \ep^{1/4})}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}
-		\omega_d^{-j}\omega_d^{(k_2-k_1)j}\ket{\psi_1}
-		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\xrightarrow[]{QFT_d^{-1}}& \sum_{j=1}^{d-1}  (U_A\ct U_B\ct)^{\log_r j}  
-		\omega_d^{d-j}\ket{\psi_1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
-		\xrightarrow[]{\text{Controlled-}U_{A/B}}&   \sqrt{d-1} \ket{\psi_1} \x  
-		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
-\end{align*}
-The analysis for $\Phi_{A,1} \x\Phi_{B,1} (O_B \ket{\psi})$ is very similar.
-
-If the initial state is $U_A\ket{\psi}$, we first use the fact that 
-$ \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi}) \appd{O(d^{5/4}r^{d/2+1/4} \ep^{1/8})}  \Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi'})$, 
-and then we calculate $\Phi_{A,1} \x \Phi_{B,1} (U_A\ket{\psi'})$.
-\begin{align*}
-	U_A \ket{\psi'} \ket{x_0}_{A'}\ket{x_0}_{B'} =&  
-		\sum_{j=1}^{d-1} U_A(U_A\ct U_B\ct)^{\log_r j}\ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
-		=&\sum_{j=1}^{d-1}(U_A\ct)^{\log_r j-1}  (U_B\ct)^{\log_r j} \ket{\psi_1} \ket{x_0}_{A'}\ket{x_0}_{B'}\\
-		\xrightarrow[]{QFT_d} &\frac{1}{d}\sum_{j=1}^{d-1} \sum_{k_1,k_2 = 0}^{d-1}(U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j} \ket{\psi_1}  \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\xrightarrow[]{\text{Controlled-}O_{A/B}}&\frac{1}{d}\sum_{j=1}^{d-1}\sum_{k_1,k_2 = 0}^{d-1} 
-		 O_A^{k_1}(U_A\ct)^{\log_r j-1} O_B^{k_2}(U_B\ct)^{\log_r j} \ket{\psi_1} 
-		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(d^{5/2} r^{d+1/2} \qe)}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}
-		\omega_d^{k_2j-k_1jr^{-1}}\ket{\psi_1}
-		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\xrightarrow[]{QFT_d^{-1}}& \sum_{j=1}^{d-1}  (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}  
-		\ket{\psi_1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'}\\
-		\xrightarrow[]{\text{Controlled-}U_{A/B}}& \sqrt{d-1} \ket{\psi_1} \x  
-		\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'},
-\end{align*}
-where we use the fact that $(d-j)r^{-1} \equiv d -jr^{-1} \pmod{d}$.
-The analysis for $\Phi_{A,1} \x\Phi_{B,1} (U_B \ket{\psi})$ is very similar.
-\end{proof}
-
-%%-----------------------------------------------------------------
-%\subsection{Self-test}
-%%-----------------------------------------------------------------
-%\hl{This subsection needs to be formalized.}
-%We give a formal version of \cref{thm:pr_2} first and then prove it.
-%\begin{theorem}
-%\label{thm:selftest}
-%	If a quantum strategy using the shared state $\ket{\psi}$ achieves the ideal 2-party correlation $C(\dr{r})$ where $d$ is an odd
-%	prime number with primitive root $r \in \{2,3,5\}$, then there exist local isometries $\Phi_A$ and $\Phi_B$, and a state $\ket{junk}$ such 
-%	that $\Phi_A\x\Phi_B \ket{\psi} = \ket{\EPR{d-1}} \x \ket{junk}$.
-%\end{theorem}
-%\begin{proof}
-%Suppose Alice and Bob achieve the optimal correlation with the quantum strategy $(\ket{\psi}, \{A_x\}, \{B_y\})$
-%for all $x,y \in \calX \times \calY$ .
-%The observables $A_x$ and $B_y$ and the shared state $\ket{\psi}$ shall not be confused with the ones used in the optimal strategy.
-%By Lemma~$4.3$ of Ref.~\cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
-%of the linear system game $\LS_r$. 
-%For each variable $\{ x_i \}_{i=1}^{n_r}$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
-%The condition that they agree with assignment to variables means that 
-%\begin{align}
-%	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
-%	\text{ for } 1 \leq i \leq n_r
-%\end{align}
-%and the condition that Alice's assignments satisfy the constraint means that 
-%\begin{align}
-%	\Tr(\rho_A \Pi_{j: H(i,j) \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m_r
-%\end{align}
-%where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$. 
-%Similarly we define $\rho_B = \Tr_A(\ketbra{\psi}{\psi})$.
-%For any $\ket{v} \in \supp(\rho_A)$,
-%we have 
-%\begin{align}
-%\Pi_{j:H(i,j) \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m_r.
-%\end{align}
-%Since the relation $uxu^{-1} = x^r$, where $r$ is the primitive root of $d$, is embedded in this linear system game, we know
-%\begin{align}
-%	A_3A_4 A_1A_2 (A_3A_4)^\dagger \ket{v}= (A_1A_2)^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
-%\end{align}
-%For simplicity, we define $X_A = A_1A_2$ and $U_A=A_3A_4$ such that
-%the condition is equivalent to
-%\begin{align}
-%	\label{eq:ux_relation}
-%	U_AX_AU_A^\dagger \ket{v} = X_A^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
-%\end{align}
-%We will come back to the implication of this condition later.
-%
-%Suppose $A_{m_r+1} = A_\ast^0- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
-%$2m$-dimensional vector space and $\Pi_{V_A}$ is the projector onto it. The reason why it has dimension $2m$
-%will be clear shortly. On Bob's side, we also have $B_{n_r+1} = B_\ast^0- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
-%Recall that from the extended weighted CHSH test, we know
-%\begin{align}
-%	A_\ast^0 \ket{\psi} = B_\ast^0 \ket{\psi} = A_\ast^0 \x B_\ast^0 \ket{\psi},
-%\end{align}
-%which implies that with an appropriate change of basis, we can get $V_A = V_B$, so in the rest of the proof
-%we drop the subscript of $V$.
-%By \cref{lm:chsh_comp} and \cref{prop:2d-subspace}, we know $V$ consists of $\omega_d$-eigenvectors and $\omega_d^{-1}$ eigenvectors of 
-%$X_A$, so we can write 
-%\begin{align}
-%	\Pi_{V} = \Pi_{V_1} + \Pi_{V_{d-1}},
-%\end{align}
-%where $\Pi_{V_{1}}$ is the projector onto the $\omega_d$-eigenspace of $X_A$ and $\Pi_{V_{d-1}}$ is the projector 
-%onto the $\omega_d^{-1}$-eigenspace of $X_A$.
-%\hl{Here what we need is that $\Pi_{V_1,A} \ket{\psi} = \Pi_{V_{d-1},B} \ket{\psi} = \Pi_{V_1,A}\Pi_{V_{d-1},B}\ket{\psi}$
-%and $\Pi_{V_1,B} \ket{\psi} = \Pi_{V_{d-1},A} \ket{\psi} = \Pi_{V_1,B}\Pi_{V_{d-1},A}\ket{\psi}$.
-%This is not proved because $\Pi_{V_1}$ and $\Pi_{V_{d-1}}$ are not in the strategy.}
-%Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.
-%By \cref{eq:ux_relation} we can calculate that
-%\begin{align}
-%\label{eq:ladder}
-% X_AU_A^\dagger \ket{x_{1}} = U_A^\dagger X_A^r \ket{x_{1}} = \omega_d^r U_A^\dagger \ket{x_{1}},
-%\end{align}
-%so $U_A^\dagger \ket{x_{1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^r$.
-%By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{r^i} (U_A^\dagger)^i\ket{x_{1}}$. 
-%From the set $\{(U_A^\dagger)^i \Pi_{V_1} (U_A)^i \}_{i=0}^{d-2}$, we can identify $\Pi_{V_i}$ for $i = 1 \dots  d-1$
-%such that $\Pi_{V_i}$ is the projector onto the $\omega_d^i$-eigenspace of $X_A$,
-%\hl{Actually, we are not sure about the containment between $\supp((U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)})$ and 
-%$\supp(\Pi_{V_{d-1}})$, so we cannot say that $\Pi_{V_{d-1}} = (U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)}$.}
-%and 
-%\begin{align}
-% \cup_{i \in [d-1]+1} V_i \subset \supp(\rho_A).
-%\end{align}
-%Since unitary transformation does not change the rank of a matrix, we know $\rank(\Pi_{V_1}) = \rank(\Pi_{V_{i}}) =N$
-%for $ i =1 \dots d-1$.
-%We pick a basis for $V_1$ such that 
-%\begin{align}
-%	\Pi_{V_1} =  \sum_{j=1}^m \ketbra{x_{1,j}}{x_{1,j}},
-%\end{align}
-%then we can construct 
-%\begin{align}
-% \Pi_{V_i} = \sum_{j=1}^m \ketbra{x_{i,j}}{x_{i,j}},
-%\end{align}
-%where $\ket{x_{i,j}} = (U\ct)^{k_i} \ket{x_{1,j}}$ for $r^{k_i} \equiv i \pmod{d}$ and $1 \leq j \leq m$.
-%By \cref{eq:ux_relation} we also know that $U_A \ket{x_{i,j}} = \ket{x_{i/2,j}}$ for $i = 1,2 \dots d-1$.
-%In order to apply \cref{lm:ux_independ}, we construct $m$ subspaces $\{W_j\}_{j=1}^m$ where 
-%\begin{align}
-%	W_j = \spn( \{ \ket{x_{i,j}} \}_{i=1}^{d-1} )
-%\end{align}
-%The subspace $W_j$ is orthogonal to $W_{j'}$ for $j \neq j'$, and
-%$U_A$ and $X_A$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
-%restricted to each $W_j$.
-%Similar argument also applies to operator $X_B$ and $U_B$ on Bob's side.
-
-%With an appropriate change of basis, we 
-%assume that $\ket{\psi} = \vc(\tau)$ for some $\tau \in L(\supp(\rho_A))$
-%The consistency condition is equivalent to
-%\begin{align}
-%\label{eq:con_tau}
-%	A_i \tau B_i^\dagger = \tau.
-%\end{align}
-%Substituting $i=1,2$ into \cref{eq:con_tau}, we get 
-%\begin{align}
-%	X_A \tau X_A^\dagger = A_1A_2\tau B_2^\dagger B_1^\dagger = A_1\tau B_1^\dagger = \tau.
-%\end{align}
-%Similar argument gives us that 
-%\begin{align}
-%	U_A \tau U_A^\dagger = \tau.
-%\end{align}
-%Then we can conclude that for any $k \in \{0,1 \dots d-2\}$ and $l \in \{1,2\dots d-1\}$
-%\begin{align}
-%	U_A^kX_A^l \tau (U_A^kX_A^l)^\dagger = \tau.
-%\end{align}
-%Let $\Pi_{W_j}$ be the projector onto $W_j$. 
-%By \cref{lm:ux_independ}, $\Pi_{W_j} \tau \Pi_{W_j}$ commutes with all the $(d-1) \times (d-1)$ matrices, which means that 
-%\begin{align}
-%	\label{eq:d-1}
-%	\Pi_{W_j} \tau \Pi_{W_j}  = c_j \1_{W_j} \text{ for } j = 1\dots m.
-%\end{align}
-%In the vector form, we know
-%\begin{align}
-%	\sum_{j =1}^N \Pi_{W_j} \ket{\psi} =\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}. 
-%\end{align}
-%Recalling the fact that 
-%\begin{align}
-%\norm{ \Pi_{V_1} + \Pi_{V_{d-1}} \ket{\psi}}^2 = \norm{\Pi_{V_1} \ket{\psi}}^2 + \norm{\Pi_{V_{d-1}} \ket{\psi}}^2 = \frac{2}{d-1},
-% \end{align}
-% it means that 
-% \begin{align}
-% 	2 \sum_{j=1}^m \norm{c_j}^2 = \frac{2}{d-1}.
-% \end{align}
-% Then we can calculate the norm of $\sum_{j =1}^m \Pi_{W_j} \ket{\psi}$, which is
-% \begin{align}
-% \norm{\sum_{j =1}^m \Pi_{W_j} \ket{\psi}}^2 = \sum_{i=1}^{d-1} \sum_{j=1}^m \norm{c_j}^2 = 1 = \norm{\ket{\psi}}^2.
-% \end{align}
-% We can conclude that $\supp{\rho_A} = \cup_{i=1}^{d-1} V_i$ and 
-% \begin{align}
-% 	\ket{\psi} = \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}\ket{x_{i,j}}.
-% \end{align}
-% 
-%The last step is to construct the local isometries $\Phi_A$ and $\Phi_B$ that can produce $\ket{\EPR{d-1}}$ from $\ket{\psi}$.
-%To help understanding, we draw a diagram to demonstrate the isometry first and then show
-%how this isometry works.
-%\begin{figure}[H]
-%\center
-%        \begin{tikzpicture}[thick]
-%        %
-%        % `operator' will only be used by Hadamard (H) gates here.
-%        % `phase' is used for controlled phase gates (dots).
-%        % `surround' is used for the background box.
-%        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
-%        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
-%        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
-%        %
-%        % Bracket
-%        \draw[decorate,decoration={brace,mirror},thick] (0,-1) to
-%    	node[midway,left] (bracket1) {$\ket{\psi}$}
-%    	(0,-2);
-%        % Qubits
-%        \node at (0,0) (q1) {$\ket{0}$};
-%        \node at (0,-1) (q2) {};
-%        \node at (0,-2) (q3) {};
-%        \node at (0,-3) (q4) {$\ket{0}$};
-%        %
-%        % Column 1
-%        \node[operator] (op11) at (1,0) {$QFT_d$} edge [-] (q1);
-%        \node[operator] (op14) at (1,-3) {$QFT_d$} edge [-] (q4);
-%        %
-%        % Column 3
-%        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
-%	\node[operator] (op22) at (2,-1) {$X_A$} edge [-] (q2);
-%	\node[operator] (op23) at (2, -2) {$X_B$} edge[-] (q3);
-%        \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
-%        \draw[-] (phase11) -- (op22);
-%        \draw[-] (phase14) -- (op23);
-%        %
-%        % Column 4
-%        \node[operator] (op31) at (3,0) {$QFT_d^{-1}$} edge [-] (phase11);
-%        \node[operator] (op34) at (3,-3) {$QFT_d^{-1}$} edge [-] (phase14);
-%        %
-%        % Column 5
-%        \node[phase] (phase21) at (4,0) {} edge [-] (op31);
-%	\node[operator] (op42) at (4,-1) {$U_A$} edge [-] (op22);
-%	\node[operator] (op43) at (4, -2) {$U_B$} edge[-] (op23);
-%        \node[phase] (phase24) at (4,-3) {} edge [-] (op34);
-%        \draw[-] (phase21) -- (op42);
-%        \draw[-] (phase24) -- (op43);
-%        %
-%        % Column 6
-%        \node (end2) at (5,-1) {} edge [-] (op42);
-%        \node (end3) at (5,-2) {} edge [-] (op43);
-%        %
-%        % Bracket
-%        \draw[decorate,decoration={brace},thick] (5,-1) to
-%    	node[midway,right] (bracket) {$\ket{junk}$}
-%    	(5,-2);
-%        %
-%        % Column 7
-%        \node (end1) at (6.5,-0.5) {} edge [-] (phase21);
-%        \node (end4) at (6.5,-2.5) {} edge [-] (phase24);
-%        % Dashed line
-%        \draw[loosely dotted] (0,-1.5) -- (5,-1.5);
-%        % Bracket
-%        \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
-%    	node[midway,right] (bracket2) {$\ket{\EPR{d-1}}$}
-%    	(6.5,-2.5);
-%        %
-%        % Background Box
-%        \begin{pgfonlayer}{background} 
-%        \node[surround] (background) [fit = (q1) (op14) (bracket1)(bracket2)] {};
-%        \end{pgfonlayer}
-%        %
-%        \end{tikzpicture}
-%	\caption{The isometries $\Phi_A$ and $\Phi_B$.}
-%\end{figure}
-%The isometry maps the state $\ket{\psi}$ in the following steps:
-%\begin{enumerate}
-%	\item Append $\ket{0}_A$ on Alice's side and $\ket{0}_B$ on Bob's side as control registers, and
-%	the state becomes $\ket{\psi} \ket{0}_A \ket{0}_B$;
-%	\item Apply $QFT_d$ to the control registers, and the state becomes
-%	\begin{align}
-%		\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \ket{\psi} \ket{k_1}_A \ket{k_2}_B;
-%	\end{align}
-%	\item Apply $X_A^{k_1}$ to Alice's share of $\ket{\psi}$ and $X_B^{k_2}$ to Bob's share controlled
-%	by the control registers, and the state becomes
-%	\begin{align}
-%		&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1}X_A^{k_1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B\\
-%		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1}\ket{x_{i,j}}_A X_B^{k_2}\ket{x_{i,j}}_B
-%		\ket{k_1}_A \ket{k_2}_B\\
-%		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1i+k_2i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
-%		\ket{k_1}_A \ket{k_2}_B;
-%	\end{align}
-%	\item Apply $QFT_d^{-1}$ to the control registers, and the state becomes
-%	\begin{align}
-%		&\frac{1}{d^2} \sum_{l_1,l_2 =0}^{d-1}\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i-l_1)+k_2(i-l_2)} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
-%		\ket{l_1}_A \ket{l_2}_B\\
-%		=& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B;
-%	\end{align}
-%	\item Let $n_i$ satisfy the condition $r^{n_i} \equiv i \pmod{d}$, apply $U_A^{(i)} = U_A^{n_i}$ to Alice's share of $\ket{\psi}$ and $U_B^{(i)} = U_B^{n_i}$ to Bob's share controlled
-%	by the control registers, and the state becomes
-%	\begin{align}
-%		&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B \\
-%		=&\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i r^{-n_i} ,j}}_A \ket{x_{i r^{-n_i},j}}_B \ket{i}_A\ket{i}_B\\
-%		=& \sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i i^{-1},j}}_A \ket{x_{i i^{-1},j}}_B \ket{i}_A\ket{i}_B\\
-%		= &\left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \sum_{i=1}^{d-1} \ket{i}_A\ket{i}_B\\
-%		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
-%		\frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1}\ket{i}_A\ket{i}_B\\
-%		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \ket{\EPR{d-1}},
-%	\end{align}
-%	where in the last line we used the fact that $\norm{\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B} = 1/\sqrt{d-1}$.
-%\end{enumerate}
-%
-%If the initial state is $X_A\ket{\psi}$, the isometry maps the state as following
-%\begin{align}
-%	X_A\ket{\psi} \to &X_A\ket{\psi}\ket{0}_A\ket{0}_B\\
-%	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
-%	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A^{k_1+1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
-%	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1+k_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
-%		\ket{k_1}_A \ket{k_2}_B\\
-%	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1-l_1)i+(k_2-l_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
-%		\ket{l_1}_A \ket{l_2}_B\\
-%	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B\\
-%	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
-%	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{i}_A\ket{i}_B\\
-%	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
-%		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\omega_d^i \ket{i}_A\ket{i}_B\\
-%	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tX_A \ket{\EPR{d-1}},
-%\end{align}
-%where $\tX_A$ is the ideal $X$ operator.
-%The case of $X_B\ket{\psi}$ is similar, so we omit it here. 
-%
-%If the initial state is $U_A\ket{\psi}$, the isometry maps the state as following
-%\begin{align}
-%	U_A\ket{\psi} \to &U_A\ket{\psi}\ket{0}_A\ket{0}_B\\
-%	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} U_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
-%	= &\frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A\ket{x_{i,j}}_A\ket{x_{i,j}}_B
-%		\ket{k_1}_A \ket{k_2}_B\\
-%	= & \frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i r^{-1} ,j}}_A\ket{x_{i,j}}_B
-%		\ket{k_1}_A \ket{k_2}_B\\
-%	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1} \ket{x_{i r^{-1} ,j}}_A
-%	X_B^{k_2}\ket{x_{i,j}}_B  \ket{k_1}_A \ket{k_2}_B \\
-%	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1 i/r}\omega_d^{k_2i} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
-%		\ket{k_1}_A \ket{k_2}_B\\
-%	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i/r-l_1)}\omega_d^{(k_2(i-l_2)} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
-%		\ket{l_1}_A \ket{l_2}_B\\
-%	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j  \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B \ket{ir^{-1}}_A \ket{i}_B\\
-%	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(ir^{-1})}\ket{x_{ir^{-1},j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
-%	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{ir^{-1}}_A\ket{i}_B\\
-%	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
-%		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\ket{ir^{-1}}_A\ket{i}_B\\
-%	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tU_A \ket{\EPR{d-1}},
-%\end{align}
-%where $\tU_A$ is the ideal $U$ operator on Alice's side.
-%The derivation is similar when $U_B$ is applied, so we omit it here.
-%\end{proof}
-%The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
-%\begin{align}
-%	X \ket{x_i} = \omega_d^i \ket{x_i}.
-%\end{align}
-%The other effect of $\SVT_X$ is that we know 
-%\begin{align}
-%	\tA_\triangle^0 \rho_A \tA_\triangle^0 = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^0.
-%\end{align}
-%\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
-
-%We remark that our proof works for any odd prime number with primitive root $r$.
-%However, since there is no upper-bound of $r$ for a general prime number $d$, we 
-%cannot claim the corresponding correlation $C(d)$ is constant-sized. On the other
-%hand, since $r$ is usually much smaller than $d$, our result implies a more efficient
-%way to test EPR pairs of prime local dimension than the one proposed in Ref.~\cite{cgs2017}.
-%The size of our correlation grows linearly in $r$ whereas the Coladangelo \textit{et. al.}'s
-%method uses correlation grows linearly in $d$.
+Details about these two isometries can be found in
+Section $6.4$ of the attached report.
+
+In summary, 
+for any $d \in D$, the maximally entangled state
+of local dimension $4(d-1)$, $\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{j}\ket{d-j} \x \ket{EPR}^{\x 2}$, can be 
+robustly self-tested by the correlation $\fC(d,r)$ 
+where $r$ is the smallest primitive root of $d$.
+Since $D$ has infinitely many elements and, for each $d$, 
+its smallest primitive root is at most $5$, 
+we have proved \cref{thm:inf}.
+
+\textbf{Our contributions}:
+We identify a family of correlations with constant-sized input and output alphabets that can be used to robustly self-test
+maximally entangled states with unbounded local dimensions. Before our work, the most efficient way 
+uses $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
+the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
+
+Our result gives us deeper understandings of the set of quantum correlations.
+In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
+lower bounds of the entanglement required to achieve certain correlations are identified.
+We take a step further and discover a large family of correlations that we know exactly the entangled state
+required to achieve each of the correlations in this family.
+
+It has been shown that robust self-testing allows a versifier to encode the verification of
+a large computational problem into small questions \cite{fitzsimons2019,neexp}. One of the future applications of our result 
+is to further reduce the lengths of questions for entanglement-assisted interactive proof systems.
 
@@
 \bibliography{quantum_correlation}
-\appendix
-
-%===========================================
-\section{Embedding $\Pg$ into $\Gamma$}
-\label{sec:embedding}
-%===========================================
-This section supports \cref{sec:embed_idea} by giving the definitions
-of $\Pg_0$ and $\Pg_1$.
-We also prove some properties of the generators of $\Pg_0$, $\Pg_1$ and 
-$\Gamma$ along the way.
-
-Recall that the goal of introducing $\Pg_0$ is to embed
-$\Pg$ in a group with only order-$2$ generators,
-so that it is easier to embed $\Pg$ into a solution group.
-
-Next we define the group $\Pg_1$.
-
-Recall the definition of $\Gamma$ in \cref{def:gamma}. We prove a property of it.
-
-%========================================
-\section{The linear system of $\LS(r)$}
-\label{sec:lsg_eq}
-%========================================
-\begin{definition}
-    \label{def:lsg_eq}
-    The linear system of $\LS(r)$ has 
-    variables $x(s)$ for each $s \in S \setminus \{J\}$, and equations:
-    \begin{itemize}
-        \item for each $1 \leq i \leq r+5$:
-        \begin{align*}
-            & x(a_i) + x(b_i) + x(c_i) = 0
-            && x(a_i) + x(f_0) + x(d_i) = 0 \\
-            & x(b_i) + x(f_2) + x(p_{i,1}) = 0 
-            && x(p_{i,2}) + x(p_{i,3}) + x(p_{i,4}) = 0 
-            && x(f_0) + x(p_{i,3}) + x(p_{i,4}) = 0\\
-            & x(c_i) + x(p_{i,4})+x(p_{i,5}) = 0
-            && x(f_1) + x(p_{i,2}) + x(p_{i,3}) = 0; 
-        \end{align*}
-        \item for each $\bc = (i,j,k) \in C(r)$:
-        \begin{align*}
-            & x(h_{jk}) + x(b_j) + x(c_k) = 0 \\
-            & x(d_i) + x(q_{\bc, 1}) + x(f_2) = 0 
-            && x(b_j) + x(f_2) + x(q_{\bc, 2}) = 0 
-            && x(q_{\bc, 2}) + x(q_{\bc, 3}) + x(q_{\bc, 4}) = 0 \\
-            & x(d_i) + x(q_{\bc, 4}) + x(q_{\bc, 5}) = 0 
-            && x(c_k) + x(q_{\bc, 5}) + x(q_{\bc, 6}) = 0 
-            && x(q_{\bc, 1}) + x(q_{\bc, 3}) + x(q_{\bc, 6}) = 0;
-        \end{align*}
-        \item Magic Square equations:
-        \begin{align*}
-            &x(f_0) + x(f_1) + x(f_2) = 0 &&
-            x(g_0) + x(g_1) + x(g_2) = 0 &&
-            x(m_0) + x(m_1) + x(m_2) = 0 \\
-            &x(f_0) + x(g_2) + x(m_0) = 0 &&
-            x(f_2) + x(g_0) + x(m_1) = 0 &&
-            x(f_1) + x(g_1) + x(m_2) = 1.
-        \end{align*} 
-    \end{itemize}
-\end{definition}
-%================================================
-\section{A representation of $\Gamma$}
-\label{sec:rep_gamma}
-%================================================
-In this section we give the full description of a representation of $\Gamma$, 
-which is built upon representations 
-of $\Pg_0$ and $\Pg_1$. We need the representation of $\Gamma$ to construct the
-ideal strategy of $\LS(r)$.
-
-Recall the two Hilbert spaces $W_{d-1}$ and $W_2$ defined in \cref{sec:gamma_def}, which are the carrier spaces
-of the representations given below,
-On the Hilbert space $W_2$, we define
-\begin{align*}
-	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
-	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
-	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
-\end{align*}
-\begin{definition}
-\label{def:rep_g0}
-The representation, $\Psi_0$, of $\Pg_0$ on $W_{d-1}$ is defined by
-\begin{align*}
-	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
-	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
-	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
-	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
-	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
-	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
-\end{align*}
-The representation of the rest of the generators
-can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the defining 
-conjugacy relations of $\Pg_0$.
-\end{definition}
-We can check that
-\begin{align*}
-	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
-	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
-\end{align*}
-which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
-$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$. 
-We can also check that the representation $\Psi_0$ satisfies the relations
-that $\Psi_0(a_3a_4) \Psi_0(a_2) \Psi_0(a_4a_3) = \Psi_0(a_2)$ by observing that
-	\begin{align*}
-		\Psi_0(a_3)\Psi_0(a_4)= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
-	\end{align*}
-	so we can conclude  
-	\begin{align*}
-		&\Psi_0(a_3)\Psi_0(a_4) \Psi_0(a_2) \Psi_0(a_4) \Psi_0(a_3)\\
-		= &\sum_{j=0}^{(d-3)/2} \Psi_0(a_3)\Psi_0(a_4) (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) \Psi_0(a_4)\Psi_0(a_3)\\
-		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}}\\ 
-		=& \Psi_0(a_2).
-	\end{align*}
-
-Following the proof of Lemma $29$ of Ref.~\cite{slofstra2017}, we construct a representation of $\Pg_1$.
-\begin{definition}
-\label{def:rep_g1}
-The representation $\Psi_1$ of $\Pg_1$ on $W_2 \x W_{d-1}$ is defined by
-\begin{itemize}
-\item for $f_0$
-\begin{align*}
-	&\Psi_1(f_0) = X_{W_2} \x \1_{W_{d-1}};
-\end{align*}
-\item
-for $i = 1 \dots r+5$,
-\begin{align*}
-	&\Psi_1(a_i) = \1_{W_2} \x \Psi_0(a_i) \\
-	&\Psi_1(b_i) = \ketbra{x_1}{x_1} \x \Psi_1(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
-	&\Psi_1(c_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(a_i) \\
-	&\Psi_1(d_i) =  X_{W_2} \x \Psi_0(a_i);
-\end{align*}
-\item for $(i,j,k) \in C(r)$,
-\begin{align*}
-	\Psi_1(h_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(a_j) + \ketbra{x_2}{x_2} \x \Psi_1(a_k).
-\end{align*}
-\end{itemize}
-\end{definition}
-
-Finally, we follow the proof of Proposition $27$ of Ref.~\cite{slofstra2017} to construct the 
-representation of $\Gamma$.
-\begin{definition}
-\label{def:rep_gamma}
-The representation $\Psi$ of $\Gamma$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
-\begin{itemize}
-\item for $s \in \{a_i, b_i, c_i, d_i\}_{i=1}^{r+5}$,
-\begin{align*}
-	\Psi(s) = \1_{W_2} \x \Psi_1(s);
-\end{align*}
-\item for $f_i$, $g_i$, $m_i$ with $i = 0,1,2$ and $J$
-\begin{align*}
-    &\Psi(f_0) = \1 \x X_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi(f_1) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi(f_2) = X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi(g_0) = \1 \x Z_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi(g_1) = Z_{W_2} \x Z_{W_2} \x \1_{W_{d-1}} \\
-	&\Psi(g_2) = Z_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
-	& \Psi(m_0) = Z_{W_2} \x X_{W_2} \x \1_{W_{d-1}}\\
-	& \Psi(m_1) = X_{W_2} \x Z_{W_2} \x \1_{W_{d-1}}\\
-	& \Psi(m_2) = Y_{W_2} \x Y_{W_2} \x \1_{W_{d-1}}\\
-	& \Psi(J) = - \1_{W_2} \x \1_{W_2} \x \1_{W_{d-1}};
-\end{align*}
-\item for the generators involved in $R_i$
-with $1 \leq i \leq r+5$ :
-\begin{align*}
-	\Psi(p_{i,1}) &= X_{W_2} \x \Psi_1(b_i) \\
-	\Psi(p_{i,2}) &= \ketbra{x_1}{x_2} \x \Psi_1(b_if_0) + \ketbra{x_2}{x_1} \x \Psi_1(f_0b_i)\\
-	\Psi(p_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_if_0b_i) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
-	\Psi(p_{i,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_ic_i) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-    \Psi(p_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i);
-\end{align*}
-\item for the generators involved in $R_{\bc}$ with $\bc = (i,j,k) \in C(r)$:
-\begin{align*}
-	\Psi(q_{\bc, 1}) &= X_{W_2} \x \Psi_1(d_i) \\
-	\Psi(q_{\bc, 2}) &= X_{W_2} \x \Psi_1(b_j) \\
-	\Psi(q_{\bc, 3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
-	\Psi(q_{\bc, 4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_jd_ib_j) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
-	\Psi(q_{\bc, 5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
-	\Psi(q_{\bc, 6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k}).
-\end{align*}
-\end{itemize}
-\end{definition}
-The validation of $\Psi_1$ and $\Psi$ were done in the proofs of 
-Lemma $29$ and Proposition $27$ in Ref.~\cite{slofstra2017}.
-%========================================
-\section{The proof of \cref{thm:selftest} }
-\label{sec:selftest}
-%========================================
-This proof follows the same line of argument in Appendix A of Ref.~\cite{bamps2015}.
-We first find two sum-of-square decompositions of $2\sqrt{\alpha^2+1} \1 - \I_\alpha$,
-where $\I_\alpha$ is expressed in terms of $\{M_x\}$ and $\{N_y\}$.
-The decompositions allow us to determine some key relations between Alice and Bob's observables
-and their shared state, which will be used to draw the conclusion.
-
-\begin{proof}
-The first step is to find a sum-of-square decomposition of 
-the following Bell expression
-\begin{align}
-	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
-	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(M_1N_1+M_1N_2) -  M_2N_1 + M_2N_2.
-\end{align} 
-With the notation $c:= \cos(\mu)$, $s := \sin(\mu)$ and 
-\begin{align*}
-	&Z_A = M_1 && X_A = M_2\\
-	&Z_B = \frac{N_1+N_2}{2c} && X_B = \frac{N_1-N_2}{2s},
-\end{align*}
-the two SOS decompositions that we use are
-\begin{align}
-	\label{eq:sos1}&\bar{\I}_\alpha = \frac{s \bar{\I}_\alpha^2 + 4sc^2(Z_AX_B+X_AZ_B)^2}{4},\\
-	\label{eq:sos2}&\bar{\I}_\alpha = \frac{c^2}{s}(Z_A-Z_B)^2 + s(X_A-X_B)^2.
-\end{align}
-The verification is omitted here. From the SOS decomposition, we establish \cref{eq:za-zb,eq:xa-xb,eq:xazb,eq:zaxb,eq:zaxa,eq:zaxaxbzb}.
-We define
-\begin{align*}
-	&S_1 = \frac{\sqrt{s}}{2} \bar{\I}_\alpha, &&
-	S_2 = \sqrt{s}c(Z_AX_B+ X_AZ_B),\\
-	&S_3 = \frac{c}{\sqrt{s}}(Z_A-Z_B), &&
-	S_4 = \sqrt{s}(X_A-X_B)
-\end{align*}
-then 
-\begin{align}
-\bar{\I}_\alpha = S_1^2 + S_2^2 = S_3^2 + S_4^2
-\end{align}
-The fact that the quantum strategy $(\ket{\psi}, \{M_x\}_{x=1,2}, \{N_{y }\}_{y=1,2}$ achieves that 
-$\ip{\bar{\I}_\alpha} \leq \epsilon$ implies that
-$\bra{\psi} S_i^2 \ket{\psi} \leq \ep$, and equivalently, $\norm{S_i \ket{\psi}} \leq \se$ for $i = 1,2,3,4$.
-From the definitions of $S_i$'s, we can get that 
-\begin{align}
-	&\norm{(X_AZ_B+X_BZ_A)\ket{\psi}} \leq \frac{1}{c\sqrt{s}} \se\\
-	&\norm{(Z_A-Z_B)\ket{\psi}} \leq \frac{\sqrt{s}}{c} \se\\
-	&\norm{(X_A-X_B)\ket{\psi}} \leq \frac{1}{\sqrt{s}} \se.
-\end{align}
-The first and the second inequality give us that 
-\begin{align}
-	\norm{ [Z_A(\1+X_B) - (\1-X_A)Z_B] \ket{\psi} } 
-	\leq \norm{(X_AZ_B+X_BZ_A)\ket{\psi}} + \norm{(Z_A-Z_B)\ket{\psi}}
-	\leq \frac{s+1}{c\sqrt{s}} \se.
-\end{align}
-Similarly, the first and the third inequality give us that 
-\begin{align}
-	\norm{[X_A(\1+Z_B) - X_B(\1-Z_A)] \ket{\psi}} \leq \frac{c+1}{c\sqrt{s}} \se.
-\end{align}
-Since $Z_AX_A +X_A Z_A = \frac{S_2}{c\sqrt{s}} + \frac{\sqrt{s}\tilde{X}_AS_3}{c} + \frac{\tilde{Z}_AS_4}{\sqrt{s}}$, we can deduce that
-\begin{align}
-	\norm{ (Z_A X_A+X_AZ_A)\ket{\psi}} \leq \frac{1+c+s}{c\sqrt{s}} \se.
-\end{align}
-To prove \cref{eq:zaxaxbzb}, we switch to the approximate relation form and derive that 
-\begin{align}
-	X_AZ_A \ket{\psi} &\appd{\frac{1+c+s}{c\sqrt{s}} \se}  -Z_AX_A \ket{\psi} \\
-	&\appd{\frac{\sqrt{s}}{c} \se} -Z_AX_B \ket{\psi} \\
-	&\appd{\frac{1}{s^{3/2} }\se} -X_BZ_B\ket{\psi},
-\end{align}
-where in the last line we use the fact $\norm{X_B} \leq 1/s$.
-
-Now we introduce the isometries $\Phi_A$ and $\Phi_B$ mentioned in the statement of the theorem.
-They are the same as the ones used in Ref.~\cite{bamps2015}.
-To construct $\Phi_A$ and $\Phi_B$ we need to regularize $Z_B$ and $X_B$ to make sure the corresponding operations 
-are unitary in the isometries. We define $Z_B^\ast$ to be the operator obtained from $Z_B$ by changing all the $0$-eigenvalues
-to $1$ and 
-\begin{align*}
-Z_B' := Z_B^\ast |Z_B^\ast|^{-1},
-\end{align*}
-where $|Z_B^\ast|$ is obtained from $Z_B^\ast$ by replacing all negative eigenvalues by its absolute value.
-In a similar way, we define $X_B^\ast$ and $X_B'$.
-On Alice's side, since $Z_A$ and $X_A$ are unitaries already,
-we define
-$Z_A' := Z_A$ and $X_A' = X_A$.
-The isometries are illustrated in the figure below.
-\begin{figure}[H]
-\center
-        \begin{tikzpicture}[thick]
-        %
-        % `operator' will only be used by Hadamard (H) gates here.
-        % `phase' is used for controlled phase gates (dots).
-        % `surround' is used for the background box.
-        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
-        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
-        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
-        %
-        % Bracket
-        \draw[decorate,decoration={brace,mirror},thick] (0,-1) to
-    	node[midway,left] (bracket1) {$\ket{\tpsi}$}
-    	(0,-2);
-        % Qubits
-        \node at (0,0) (q1) {$\ket{0}$};
-        \node at (0,-1) (q2) {};
-        \node at (0,-2) (q3) {};
-        \node at (0,-3) (q4) {$\ket{0}$};
-        %
-        % Column 1
-        \node[operator] (op11) at (1,0) {H} edge [-] (q1);
-        \node[operator] (op14) at (1,-3) {H} edge [-] (q4);
-        %
-        % Column 3
-        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
-	\node[operator] (op22) at (2,-1) {$Z_A'$} edge [-] (q2);
-	\node[operator] (op23) at (2, -2) {$Z_B'$} edge[-] (q3);
-        \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
-        \draw[-] (phase11) -- (op22);
-        \draw[-] (phase14) -- (op23);
-        %
-        % Column 4
-        \node[operator] (op31) at (3,0) {H} edge [-] (phase11);
-        \node[operator] (op34) at (3,-3) {H} edge [-] (phase14);
-        %
-        % Column 5
-        \node[phase] (phase21) at (4,0) {} edge [-] (op31);
-	\node[operator] (op42) at (4,-1) {$X_A'$} edge [-] (op22);
-	\node[operator] (op43) at (4, -2) {$X_B'$} edge[-] (op23);
-        \node[phase] (phase24) at (4,-3) {} edge [-] (op34);
-        \draw[-] (phase21) -- (op42);
-        \draw[-] (phase24) -- (op43);
-        %
-        % Column 6
-        \node (end2) at (5,-1) {} edge [-] (op42);
-        \node (end3) at (5,-2) {} edge [-] (op43);
-        %
-        % Bracket
-        \draw[decorate,decoration={brace},thick] (5,-1) to
-    	node[midway,right] (bracket) {$\ket{aux}$}
-    	(5,-2);
-        %
-        % Column 7
-        \node (end1) at (6.5,-0.5) {} edge [-] (phase21);
-        \node (end4) at (6.5,-2.5) {} edge [-] (phase24);
-        % Dashed line
-        \draw[loosely dotted] (0,-1.5) -- (5,-1.5);
-        % Bracket
-        \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
-    	node[midway,right] (bracket2) {$\frac{\ket{00}+\ket{11}}{\sqrt{2}}$}
-    	(6.5,-2.5);
-        %
-        % Background Box
-        \begin{pgfonlayer}{background} 
-        \node[surround] (background) [fit = (q1) (op14) (bracket1)(bracket2)] {};
-        \end{pgfonlayer}
-        %
-        \end{tikzpicture}
-	\caption{The isometries $\Phi_A$ and $\Phi_B$.}
-\end{figure}
-To bound $e_{xy} := \norm{ (\Phi_A\x\Phi_B) (\tA_x \x \tB_y) \ket{\tpsi} - \ket{junk} \x (A_x\x B_y) \ket{\EPR{2}}}$,
-there are some intermediate steps. Since the derivations are the same as in Ref.~\cite{bamps2015}, 
-we only record the key relations here.
-\begin{align*}
-	&\norm{(Z_B' - Z_B) \ket{\tpsi}} \leq \frac{\sqrt{s}}{c} \sqrt{\epsilon},\\
-	&\norm{(Z_B' - Z_A') \ket{\tpsi}} \leq 2 \frac{\sqrt{s}}{c}\sqrt{\epsilon}, \\
-	&\norm{(X_B' - X_B) \ket{\tpsi}} \leq \frac{c+1}{s^{3/2}} \sqrt{\epsilon} := \delta_1 \sqrt{\epsilon},\\
-	&\norm{(X_B'Z_B'+ Z_B'X_B')\ket{\tpsi}} \leq [\frac{2\sqrt{s}}{c} + \frac{2}{\sqrt{s}} + 2\delta_1 + 
-	(\sqrt{2}+\frac{1}{c})(2\frac{\sqrt{s}}{c}+\frac{1+c+s}{c\sqrt{s}})]\sqrt{\epsilon}
-	:= \delta_2 \sqrt{\epsilon}.
-\end{align*}
-Then we can calculate that 
-\begin{align*}
-	&e_{00} = e_{10} = 2\delta_2 \sqrt{\epsilon}\\
-	&e_{20} = 2(\frac{1+c+s}{c\sqrt{s}} + \delta_2) \sqrt{\epsilon}\\
-	&e_{01} = e_{02} = e_{11} = e_{12} = [\sqrt{s}+s(2\frac{1+c+s}{c\sqrt{s}} + \delta_1) + 2\delta_2]\sqrt{\epsilon}\\
-	&e_{21} = e_{22} = [2\frac{1+c+s}{c\sqrt{s}} + \sqrt{s}+s(2\frac{1+c+s}{c\sqrt{s}} + \delta_1) + 2\delta_2]\sqrt{\epsilon},
-\end{align*}
-so an upper bound of the error is that
-\begin{align}
-	\forall x,y \in \{0,1,2\}, e_{xy} \in O((\frac{1}{c^2s^{1/2}} + \frac{1}{s^{3/2}})\sqrt{\epsilon}).
-\end{align}
-\end{proof}
-
 \end{document}

### 2019-09-14 Draft/ext_abstract_nc.tex
QIP version

--- 2019-09-14 Draft/ext_abstract.tex
@@
 The measurement statistics are referred to as correlations.
-
-It has been shown that certain quantum correlations require the distant parties to share
+In general, not all quantum states can be certified in this way, but some entangled states
+can. Furthermore, certain correlations require the distant parties to share
 a particular entangled state up to some local isometry. 
 This phenomenon is referred to as self-testing.  
-If we can further prove that, when the observed correlation deviates from 
-the ideal correlation to some extent, 
+If we can further prove that, when the observed correlation deviates from the ideal to some extent, 
 the shared state is close to the ideal state up to some local isometry,
@@
 \cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
-Since the setting of interactive proof systems is similar to a self-test, self-testing arguments also help to prove
+Since the setting of interactive proof system is similar to a self-test, self-testing arguments also help to prove
 lower bounds of the computational power of entanglement-assisted
@@
 \cite{yang2013}.
-Robust self-testing results of tensor product of maximally and partially entangled qubits 
+\hf{Robust self-testing results of tensor product of maximally and partially entangled qubits 
 are proved in \cite{coladan2016parallel,natarajan2017,lowdegree},
-with the last one being the one with the smallest input and output alphabet.
+with the last one being the one with the smallest input and output alphabet.}
 For general bipartite entangled quantum states, \cite{coladan2017all} proves that there exists a family of correlations such that
@@
 can be self-tested with constant-sized input and output alphabets. 
-For comparisons,
+\hf{For comparison,
 all the self-testing correlations used in the results listed above have 
 output alphabets with size depending on $d$
-when they try to self-test an entangled state of local dimension $d$.
+when they try to self-test a maximally entangled state of local dimension $d$.
+}
 The second one is how to robustly self-test maximally entangled states
 with local dimension $d > 2$ and $d \neq 2^n$ for any $n$.
-For example, the authors of \cite{coladan2017all} left proving their
-family of self-testing correlations robust as an open problem.
+\hf{For example, the authors of \cite{coladan2017all} left proving their
+family of self-testing correlations robust as an open problem.}
 
@@
 second question
-by proving the following theorem.  
-\begin{theorem}[Informal]
+by proving the following theorem.  \begin{theorem}[Informal]
 \label{thm:inf}
@@
 	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
-	with constant-sized input and output alphabets.
+	with constant-sized question and answer alphabets.
 \end{theorem}
-Formal statements of this theorem can be found in Theorem $6.16$ and $6.17$
+Formal statements of this theorem can be found in Theorem $6.14$ and $6.15$
 of the attached report.
@@
 is either $2$, $3$, or $5$, 
-We say that $r$ is a primitive root of $d$ if $r$ is a 
-multiplicative generator of the group $\Zd$.
+\hf{We say that $r$ is a primitive root of $d$ if $r$ is the 
+multiplicative generator of the group $\Zd$.}
 It has been shown that $D$ has infinitely many elements \cite{murty1988}.
@@
 Note that although the size of the input or output alphabet of $\fC(d,r)$ does not depend on $d$, 
-the distributions in $\fC(d,r)$ do. 
-Details of $\fC(d,r)$ can be found in Section $5$ of the attached report.
+\hf{the distributions in $\fC(d,r)$ do}. 
 % Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
@@
 
-The correlation $\fC(d,r)$ contains a winning correlation of a specially-designed binary linear system game.  
+The correlation $\fC(d,r)$ contains \hf{a} winning correlation of a specially-designed binary linear system game.  
 In a general binary linear system game, Alice is asked for an assignment of a random equation 
@@
 
-In his seminal work \cite{slofstra2017}, Slofstra proved that 
+In his seminal work \cite{slofstra2017}, \hf{Slofstra proved that 
 there exists a binary linear system game that cannot be won by any finite-dimensional quantum strategy but a limit of 
@@
 finite-dimensional strategies is not closed.
-In the proof, he proposed and validated a new way 
+In the proof, he proposed and validated a new way} 
 to design binary linear system games to enforce conjugacy relations of the
@@
 then one can identify unitaries $U_A, O_A$ on Alice's side and
-$U_B, O_B$ on Bob's side as products of their binary observables, such that 
+$U_B, O_B$ on Bob's side \hf{as products of their binary observables}, such that 
 \begin{align}
 \label{eq:induct}
-	 U_A O_A U_A\ct \ket{\psi} \appd{O(r \se)}  O_A^{r} \ket{\psi}.
+	 (U_A)^n O_A (U_A\ct)^n \ket{\psi} \appd{O(r^{n} \se)}  O_A^{r^n} \ket{\psi}
 \end{align}
+for all $n \geq 1$.
 The analogous relation holds on Bob's side too.
@@
 of the input alphabets for Alice and Bob are of order $\Theta(r)$,
-and the output alphabets are of size $\Theta(1)$.
+and the answer sets are of size $\Theta(1)$.
 Restricting $r \leq 5$ as in \cref{thm:inf} implies that our linear system 
@@
 
-\Cref{eq:induct} is not sufficient for self-testing, so
-$\fC(d,r)$ also contains an extension of the optimal correlation 
+The correlation $\fC(d,r)$ also contains an extension of the \hf{optimal} correlation 
 that achieves the maximal violation of the $\cot(-\frac{\pi}{d})$-weighted CHSH inequaltiy \cite{pal2010}
@@
 \end{align*}
-In Section $4$, we prove that $\I_{\cot(-\pi/d)}$ can be used to robustly
-self-test $\ket{EPR}$ and rotated Pauli operators.
 % The extended correlation has input alphabets $\{0,1,2, \nr+1, \nr+2\}$ for Alice and Bob, where $\nr$ is the number of variables of
@@
 if some strategy with shared state $\ket{\psi}$ can produce a correlation that is within
-expected trace distance $\ep$ from $\fC(d,r)$, then
+expected trace distance $\ep$ from this correlation, then
 \begin{align}
@@
 This decomposition of $\ket{\psi}$ is the key observation that enables the application of the generalized swap-isometry.  
-\Cref{eq:decomp} is 
-proved in Section $6.2$ of the attached report, which uses \cref{eq:induct}.
-
-The combination of a linear system game with 
-additional correlations in the construction of $\fC(d,r)$ 
-is a new way to use linear system games for robust self-testing.
-It distinguishes our approach from all the previous ones.
+Robust self-testing property of $\I_{\cot(-\pi/d)}$
+is proved in Section $4$ and \cref{eq:decomp} is 
+proved in Section $6.2$ of the attached report.
 
@@
         \draw[decorate,decoration={brace},thick] (5,-1) to
-    	node[midway,right] (bracket) {$\ket{\psi_1}$}
+    	node[midway,right] (bracket) {$\ket{reuse}$}
     	(5,-2);
@@
 \end{align*}
-This is the first application of the generalized swap-isometry \cite{yang2013} to a robust self-testing proof.  
+This is the first application of the generalized swap-isometry \cite{yang2013} in the robust self-testing proof.
 Applying the second isometry to the state $\sqrt{d-1}\ket{\psi_1}$ gives us that
@@
 
-In summary, 
-for any $d \in D$, the maximally entangled state
+In summary, for any $d \in D$, the maximally entangled state
 of local dimension $4(d-1)$, $\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{j}\ket{d-j} \x \ket{EPR}^{\x 2}$, can be 
@@
 
+Comparing to previous works, 
+our work is the first successful attempt to use linear system game to robustly
+self-test maximally entangled states with large local dimension and
+no tensor product structure.
+% The correlation extended from the ideal correlation that achieves $\I_{\cot(-\pi/d)}^{\max}$
+% can be seen as a test of binary observables 
+% used in the strategy of the linear system game.  
+The invention of combining a linear system game with 
+additional correlations
+distinguishes our approach from all the previous ones.
+
 \textbf{Our contributions}:
@@
 maximally entangled states with unbounded local dimensions. Before our work, the most efficient way 
-uses $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
+was to use $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
 the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
 
-Our result gives us deeper understandings of the set of quantum correlations.
+Our result gives us deeper understanding of the set of quantum correlations.
 In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
 lower bounds of the entanglement required to achieve certain correlations are identified.
-We take a step further and discover a large family of correlations that we know exactly the entangled state
+We take a step further and discover a large family of correlations that we know exactly the amount of entanglement
 required to achieve each of the correlations in this family.
-
-It has been shown that robust self-testing allows a versifier to encode the verification of
-a large computational problem into small questions \cite{fitzsimons2019,neexp}. One of the future applications of our result 
-is to further reduce the lengths of questions for entanglement-assisted interactive proof systems.
 

### 2019-09-15 Draft/draft.tex
Honghao: minor changes

@@
 	The construction of the correlation uses the embedding procedure
-	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$ Cambridge University Press, $2019$).
+	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$, ($2019$)).
 	Since there are 
-	infinitely many prime numbers whose smallest multiplicative generator
-	is at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
+	infinitely many prime numbers whose smallest multiplicative generators
+	are at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
 	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
-	with unbounded local dimensions.
+	with unbounded local dimension.
 \end{abstract}
@@
         V\Pi_{i=1}^n M_i \ket{\psi} 
-        \appd{(2n\ep_1 + \ep_2} \left(\Pi_{i=1}^k V_i\right) 
+        \appd{2n\ep_1 + \ep_2} \left(\Pi_{i=1}^k V_i\right) 
         \left(\Pi_{i=1}^n M_i \right)\ket{\psi}.
@@
 	&R_{base} = \{s^2 = e | s \in S\},\\
-	&R_{u} = \{ u_3 = u_2o_1u_2 \quad u_4 = u_2o_2u_2 \quad 
-	u_5 = u_1u_3u_1 \quad o_2 = u_1u_4u_1 \quad u_5 = o_1 o_r o_1\},
+	&R_{u} = \{ u_3 = u_2o_1u_2, \quad u_4 = u_2o_2u_2, \quad 
+	u_5 = u_1u_3u_1, \quad o_2 = u_1u_4u_1, \quad u_5 = o_1 o_r o_1\},
 	\end{align*}
@@
 	\begin{cases} 
-	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1 \quad o_{2+2j} = o_2o_{1+2j}o_2\} \quad \text{ if $r$ is even },\\
+	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1, \quad o_{2+2j} = o_2o_{1+2j}o_2\}  &\text{ if $r$ is even },\\
 	\{o_3 = o_2o_1o_2\} \cup \bigcup_{j=1}^{(r-3)/2}\{
-	 o_{2+2j} =o_1o_{1+2j}o_1 \quad o_{3+2j} = o_2o_{2j+2}o_2 \}\quad\text{ if $r$ is odd }.
+	 o_{2+2j} =o_1o_{1+2j}o_1, \quad o_{3+2j} = o_2o_{2j+2}o_2 \} &\text{ if $r$ is odd }.
 	\end{cases}
@@
 \begin{align*}
-	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
+	R_i =  \{ &a_i = b_ic_i = f_0d_i,\quad
 	%&g_2 a_i w_i = e \\
-	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
-	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
+	f_0 f_1 f_2 = e, \quad b_i f_2 p_{i,1} = e, \quad p_{i,1} p_{i,2} p_{i,3} = e,\\
+	&f_0 p_{i,3} p_{i,4} = e, \quad c_i p_{i,4} p_{i,5} =e, \quad f_1 p_{i,2} p_{i,5} = e\},
 \end{align*}
@@
 \begin{align*}
-	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
-	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
-	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
+	R_{\bc} = \{&h_{jk}b_j c_k = e, \quad
+	d_i q_{\bc,1} f_2 = e, \quad b_j f_2 q_{\bc,2} = e, \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e,\\
+	&d_i q_{\bc,4} q_{\bc,5} = e, \quad c_k q_{\bc,5} q_{\bc,6} =e, \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
 \end{align*}
@@
 $
-	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
-	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
+	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e, \quad m_0 m_1 m_2 = e, \quad
+	f_0 g_2 m_0 = e, \\ \indent f_2 g_0 m_1 = e, \quad f_1 g_1 m_2 = J\},
 $
@@
 	Using \cref{eq:o1,eq:o2}, it is straightforward to see that $\Psi_0(a_j)\x \Psi_0(a_j) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ for $j = 1,2$.
-	Before checking the two cases $j=3$ and $j=4$, we can use \cref{eq:u1u2} to derive that
+	Before checking the two cases $j=3$ and $j=4$, we can use \cref{eq:u1,eq:u2} to derive that
 	\begin{align*}
@@
 The author is deeply grateful to his PhD advisor, Carl Miller, for the enlightening discussions with him, his patient guidance and useful critiques through this
-project. His original idea about 
+project. His original ideas about 
 combining a linear system game with a Bell inequality and characterizing prime numbers

### 2019-10-29 Draft/draft.tex
Fixing introduction.

@@
 
-\author[1]{Honghao Fu}
+\author{Honghao Fu
+\footnote{\href{mailto:h7fu@umd.edu}{h7fu@umd.edu}}}
 
@@
 
-\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
+\date{}
+\affil{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA
+\break
+}
 %\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
@@
 	infinitely many prime numbers whose smallest multiplicative generators
-	are at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
+	are at most $5$ (M. Murty \textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
 	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
@@
 from the ideal one to some extent, 
-the shared state is close to the ideal state up to some local isometry,
+the shared state is still close to the ideal state up to some local isometry,
 then we say the self-test is robust.
 
-Self-testing is powerful because only classical interactions are performed.
-Hence, it allows a classical party to delegate quantum computations to some untrusted service provider
+The fact that the verifier only interacts classically with the unknown device
+makes self-testing a powerful tool 
+for applications in 
+quantum cryptography and computational
+complexity theory.
+It allows a classical party to delegate quantum computations to some untrusted service provider
 and verify that the computations are performed
@@
 It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
-\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
-Since the setting of interactive proof systems is similar to a self-test, self-testing arguments also help to prove
+\cite{mayersyao,vv2014,fu2018}.
+Since the setting of multi-prover interactive proof systems is similar to a self-test, self-testing arguments also help to prove
 lower bounds of the computational power of entanglement-assisted
@@
 Robust self-testing of partially entangled qubits is proved later in
-\cite{yang2013}, which also proposed an generalized swap-isometry
+\cite{yang2013}, the authors of which also propose an generalized swap-isometry
 that can be used to robustly self-test large dimensional maximally entangled states.
@@
 Self-testing of all pure bipartite entangled states is proved in \cite{coladan2017all}.
-The authors in \cite{coladan2017all} constructed a family of correlations such
+The authors of \cite{coladan2017all} construct a family of correlations such
 that an entangled state of any local dimension has
@@
 To generate a correlation in the family, Alice and Bob
-use constant-sized input alphabets but $\Theta(d)$-sized output alphabets, 
+use constant-sized input alphabets but size-$d$ output alphabets, 
 where $d$ is the local dimension of the entangled state. 
-This is the only result about self-testing the general $d$-dimensional entangled state so far.
-However, proving the robustness of this family of correlations remains an open problem.
-
-Our work aims at answering two open questions.
-The first one is whether maximally entangled states with large local dimension
-can be self-tested with constant-sized input and output alphabets, 
-which are independent of the local dimension of the self-tested state.
+The robustness of this family of correlations is proved in \cite{inf_sep}.
+
+Our work aims at minimizing the sizes of the input 
+and output alphabets of a correlation that can self-test
+a maximally entangled states with large local dimension.
+% that are independent of the local dimension of the self-tested state.
 For comparisons, all the correlations used in the results listed above
@@
 local dimension of the entangled state.
-The second one is how to robustly self-test maximally entangled states
-with large local dimension and no tensor product structure. 
-We give an affirmative answers to the first question and
-make significant progress in answering the second question
-by proving the following theorem.
+Our progress is summarized in the following theorem.
 \begin{theorem}[Informal]
@@
 
+\subsection{Proof overview}
+
 To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
@@
 This correlation is denoted by $\fC(d,r)$.
-Note that although the size of the input or output alphabet of $\fC(d,r)$ does not depend on $d$, 
-the distributions in $\fC(d,r)$ do. 
+Note that the sizes of the input or output alphabet of $\fC(d,r)$ is independent of $d$. 
+% the distributions in $\fC(d,r)$ do. 
 Once we prove $\fC(d,r)$ can robustly self-test a maximally entangled
@@
 
-Our linear system game is designed to enforce the relation 
-\begin{align*}
+Our linear system game, $\LS(r)$, is designed to enforce the relation 
+\begin{align}
+\label{eq:uor}
     U O U\ct = O^r,
-\end{align*}
+\end{align}
 for unitaries $U$ and $O$, and some integer $r$.
-It implies that the winning strategy contains binary observables
+The inspiration comes from Slofstra's seminal work \cite{slofstra2017},
+where he proves that 
+there exists a binary linear system game that cannot be won by 
+any finite-dimensional quantum strategy but a limit of 
+finite-dimensional strategies can win it perfectly.
+It implies that the set of quantum correlations generated by
+finite-dimensional strategies is not closed.
+In the proof, he proposes and validates a new way 
+to design binary linear system games to enforce conjugacy relations of the
+form $X Y X\ct = Z$ for unitaries $X, Y$ and $Z$.
+
+Following Slofstra's design, 
+the game $\LS(r)$ is constructed so that the sizes
+of the input alphabets for Alice and Bob are of order $\Theta(r)$,
+and the answer sets are of size $\Theta(1)$.
+Restricting $r \leq 5$ as in \cref{thm:inf} implies that 
+$\LS(r)$ only uses constant-sized input and output alphabets.
+
+The reason that we choose \cref{eq:uor} to be the relation enforced
+by $\LS(r)$ is the following.
+Winning $\LS(r)$ implies that the winning strategy contains binary observables
 $M_1, M_2, M_3, M_4$ on Alice's side and 
@@
 \begin{align*}
-    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2.
-\end{align*}
-This relation implies the eigenvalues of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
-It also implies that $U$ is a permutation of the eigenbasis of $O$.
-Winning this linear system game implies that Alice and Bob share a state
-$\ket{\psi}$ such that
-\begin{align*}
-    O \x O \ket{\psi} = \ket{\psi}, && 
-    U \x U \ket{\psi} = \ket{\psi}.
-\end{align*}
-These two relations are important for the self-testing argument.
-The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
-is spanned by tensor products of states in the eigenbasis of $O$.
-The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
-under the permutation induced by $U$. 
+    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2
+\end{align*}
+with $U$ and $O$ satisfying \cref{eq:uor}.
+Then we can deduce that the eigenvalues of $O$ must be
+of the form $\omega_d^j = e^{i 2j\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
+We can also deduce that $U$ is a permutation of the eigenbasis of $O$.
+Winning this linear system game also implies that Alice and Bob share a state
+$\ket{\psi}$ such that $\ket{\psi}$
+is spanned by tensor products of states in the eigenbasis of $O$,
+and is invariant under the permutation induced by $U$
+% \begin{align*}
+%     O \x O \ket{\psi} = \ket{\psi}, && 
+%     U \x U \ket{\psi} = \ket{\psi}.
+% \end{align*}
+% The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
+% is spanned by tensor products of states in the eigenbasis of $O$.
+% The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
+% under the permutation induced by $U$. 
 At this point, the eigenvalues of $O$ are unknown, so
-certifying the eigenvalues of $O$ requires another test, 
-which will be introduced later.
-
-The special feature of our linear system game is that the sizes
-of the question sets for Alice and Bob are of order $\Theta(r)$,
-and the answer sets are of size $\Theta(1)$.
-Restricting $r \leq 5$ as in \cref{thm:inf} implies that our linear system 
-game only uses constant-sized question sets and constant-sized answer sets.
+certifying the eigenvalues of $O$ requires another test.
 
@@
 \end{align*}
-
-In the proof, we demonstrate a new way to apply the generalized swap-isometry
+In this proof, we demonstrate a new way to apply the generalized swap-isometry
 proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
-dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.
+dimension.
 
@@
 \begin{align}
-	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
+	\pr{a,b}{x,y} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
 \end{align}
@@
 	alphabets: $\{\calA_x\}_{x \in \calX}$ and $\{\calB_y\}_{y \in \calY}$, a correlation is a family of conditional probability distributions
-	$\{\pr{ab}{xy}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
+	$\{\pr{a,b}{x,y}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
 \end{definition}
@@
 The complete list of the equations is given in \cref{def:lsg_eq}.
+The construction of $\LS(r)$ proves the following theorem.
+The definition of $\LS(r)$ follows this theorem.
+\begin{theorem}
+	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
+	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
+\end{theorem}
+
 \begin{definition}
@@
 Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
-Alice answer sets are 
+Alice's answer sets are 
 \begin{align*}
@@
 
-The construction of $\LS(r)$ proves the following theorem.
-\begin{theorem}
-	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
-	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
-\end{theorem}
-As indicated in \cref{def:lsg}, the total
+As indicated above, the total
 number of question pairs is $N(r) = 157r + 685 = \Theta(r)$.
@@
 achieves $\I_{-\cot(\pi/d)}^{\max}$. 
-To make the study of the implication of a strategy that realize 
-the ideal correlation of the extended weighted CHSH test easier,
+To ease the study of the implication of a strategy that realize 
+the ideal correlation of the extended weighted CHSH test,
 we fill in the background of the robust self-testing property of the
@@
 \end{align}
-We keep the exact error terms so that some
-of the substitution steps in \cref{sec:main} are 
-easier to follow.
+We keep the exact error terms for the substitution steps in \cref{sec:main}.
 
@@
 after we introduce the ideal strategy.
+The superscript $\EXT$ stresses the fact 
+the labeled object is for the extended weighted CHSH test.
 
 Recall the Hilbert space $W_{d-1}$ defined in \cref{eq:basis}. 
-To make the shared state and the observables of the ideal strategy have
-simpler forms, we introduce the third basis of $W_{d-1}$: $\{ \ket{j} \}_{j=1}^{d-1}$, which is defined by
-\begin{align*}
+To better characterize the shared state and the observables of the ideal strategy, we need to decompose $W_{d-1}$ into $2$-dimensional
+orthogonal subspaces.
+In order to do it, we introduce the third basis of $W_{d-1}$: $\{ \ket{j} \}_{j=1}^{d-1}$ defined by
+\begin{align}
+    \label{eq:ketj}
     &\ket{j} = -\frac{1}{\sqrt{2}}(\ket{x_j} + e^{-ij\pi/d}\ket{x_{d-j}}) \\
+    \label{eq:ketd-j}
     &\ket{d-j} = \frac{i}{\sqrt{2}}(\ket{x_j} - e^{-ij\pi/d}\ket{x_{d-j}})
@@
 	%\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j})
-\end{align*}
+\end{align}
 for $1 \leq j \leq \frac{d-1}{2}$.
+Then the $2$-dimensional subspaces are
+\begin{align}
+    \label{eq:vj}
+    V_j = \spn( \ket{j}, \ket{d-j})
+\end{align}
+for $1 \leq j \leq \frac{d-1}{2}$.
+The projector onto $V_j$ is denoted by $\Pi_{V_j}$. 
+On each subspace $V_j$, we define quantum states 
+\begin{align}
+    \ket{j_{\times}} = \frac{1}{\sqrt{2}}(\ket{j} + \ket{d-j}) &&
+    \ket{(d-j)_{\times}} = \frac{1}{\sqrt{2}}(\ket{j} - \ket{d-j})
+\end{align}
+and
+\begin{align}
+    \label{eq:ketj+}
+    &\ket{j_+} = \cos(-\frac{j\pi}{2d})\ket{j} + \sin(-\frac{j\pi}{2d})\ket{d-j}
+	&&\ket{(d-j)_+} = \sin(-\frac{j\pi}{2d})\ket{j} - \cos(-\frac{j\pi}{2d})\ket{d-j}\\
+	\label{eq:ketj-}
+	&\ket{j_-} = \cos(-\frac{j\pi}{2d})\ket{j} - \sin(-\frac{j\pi}{2d})\ket{d-j}
+	&&\ket{(d-j)_-} = \sin(-\frac{j\pi}{2d})\ket{j} + \cos(-\frac{j\pi}{2d})\ket{d-j}.
+\end{align}
+Note that $\{\ket{j_{\times}}, \ket{(d-j)_{\times}}\}$,
+$\{\ket{j_+}, \ket{(d-j)}_+\}$ and $\{\ket{j_-}, \ket{(d-j)_-}\}$ are three sets of basis states of $V_j$.
+These are the states that the ideal strategy measures.
+
 The shared state of the ideal strategy is 
@@
         \ket{\tpsi}^{\EXT}
-         =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j}),
+         =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j}).
     \end{aligned}
 \end{equation}
-where the superscript $\EXT$ stresses the fact this state is for the extended weighted CHSH test.
 Note that in the standard basis of $W_{d-1}$,
@@
 
-To introduce the projectors, 
-we first define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$.
-The corresponding projective measurements are $\Pi_V$ and $\Pi_{V^\perp}$. Note that $V$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$.
+% To introduce the projectors of the ideal strategy, we
+% define $V_1^\perp := \bigoplus_{j=2}^{(d-1)/2} V_j$
+% and denote the corresponding projector by $\Pi_{V_1}^{\perp}$.
+% we first define two subspaces of $W_{d-1}$: $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$.
+% The corresponding projective measurements are $\Pi_V$ and $\Pi_{V^\perp}$. 
+% Note that $V_1$ is the subspace on which they should maximize $\I_{\cot(-\pi/d)}$. We also need to define
 
@@
 \begin{align*}
-	&\tP_0^0 = \tQ_0^0 = \Pi_V && \tP_0^2 = \tQ_0^2 = \Pi_{V^\perp} \\
+	&\tP_0^0 = \tQ_0^0 = \Pi_{V_1} && \tP_0^2 = \tQ_0^2 = \Pi_{V_1}^\perp \\
 	&\tP_{\nr+1}^0 = \tQ_{\nr+1}^0 = \ketbra{1}{1} &&
@@
 	&\tP_{\nr+2}^0 = \tQ_{\nr+2}^0 = \ketbra{1_{\times}}{1_{\times}} && \tP_{\nr+2}^1 = \tQ_{\nr+2}^1 = \ketbra{(d-1)_{\times}}{(d-1)_{\times}} \\
-	&\tP_{\nr+1}^2 = \tQ_{\nr+1}^2 = \Pi_{V^\perp} &&
-	 \tP_{\nr+2}^2 = \tQ_{\nr+2}^2 = \Pi_{V^\perp},
+	&\tP_{\nr+1}^2 = \tQ_{\nr+1}^2 = \Pi_{V_1}^\perp &&
+	 \tP_{\nr+2}^2 = \tQ_{\nr+2}^2 = \Pi_{V_1}^\perp,
 \end{align*}
@@
 \begin{align*}
-    \ket{1_{\times}} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
-	&&\ket{(d-1)_{\times}} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
-\end{align*}
-Intuitively, these questions force Alice and Bob to agree on the subspace $V$ and
-on the basis of $V$ that they will measure.
+    \Pi_{V_1}^{\perp} = \1 - \Pi_{V_1}.
+\end{align*}
+Intuitively, these questions force Alice and Bob to agree on the subspace $V_1$ and
+on the basis of $V_1$ that they measure.
 
@@
 This is the reason behind naming this test the extended weighted CHSH test.
-It is also the reason behind having Alice and Bob agreeing on the subspace $V$.
-Before introducing the measurements, 
-we need to define some basis states of $V$
-\begin{align*}
-	&\ket{1_+} = \cos(-\frac{\pi}{2d})\ket{1} + \sin(-\frac{\pi}{2d})\ket{d-1}
-	&&\ket{(d-1)_+} = \sin(-\frac{\pi}{2d})\ket{1} - \cos(-\frac{\pi}{2d})\ket{d-1}\\
-	&\ket{1_-} = \cos(-\frac{\pi}{2d})\ket{1} - \sin(-\frac{\pi}{2d})\ket{d-1}
-	&&\ket{(d-1)_-} = \sin(-\frac{\pi}{2d})\ket{1} + \cos(-\frac{\pi}{2d})\ket{d-1},
-\end{align*}
-so that $\{\ket{1_+}, \ket{(d-1)}_+\}$ and $\{\ket{1_-}, \ket{(d-1)_-}\}$ are two basis
-of $V$.
-When Alice and Bob gets question $1$ or $2$, what they measure on $V$ are
-\begin{align*}
-	&\tP_1^0 = \tQ_1^0 =  \ketbra{1_+}{1_+} && \tP_1^1 = \tQ_1^1 =  \ketbra{(d-1)_+}{(d-1)_+}\\
-	&\tP_2^0 = \tQ_2^0 =  \ketbra{1_-}{1_-} && \tP_1^1 = \tQ_1^1 =  \ketbra{(d-1)_-}{(d-1)_-}.
-\end{align*}
-Notice that their measurements on $V$ follow the measurements to achieve $\I_{\cot(-\pi/d)}^{\max}$.
-What they measure on $V^\perp$ is irrelevant for this test. 
+It is also the reason behind having Alice and Bob agreeing on the subspace $V_1$.
+
+When Alice and Bob gets question $1$ or $2$, what they measure are
+\begin{align*}
+	&\tP_1^0 = \tQ_1^0 =  \sum_{j=1}^{(d-1)/2}\ketbra{j_+}{j_+} && \tP_1^1 = \tQ_1^1 = \sum_{j=1}^{(d-1)/2} \ketbra{(d-j)_+}{(d-j)_+}\\
+	&\tP_2^0 = \tQ_2^0 = \sum_{j=1}^{(d-1)/2} \ketbra{j_-}{j_-} && \tP_1^1 = \tQ_1^1 = \sum_{j=1}^{(d-1)/2} \ketbra{(d-j)_-}{(d-j)_-}.
+\end{align*}
+In particular, their measurements on $V_1$  
+for question $1$ and $2$,
+follow the measurements to achieve $\I_{\cot(-\pi/d)}^{\max}$.
+What they measure on the complementary of $V_1$ 
+in $W_{d-1}$
+is irrelevant for this test,
+but important for the full test introduced 
+in the next section.
 %Later we will see that their measurements on $V^\perp$ are determined by their observables for variables $x(a_1)$ and $x(a_2)$ of $\LS(r)$.
@@
 
-The ideal strategy for the full test is an extension of the ideal strategy of $\LS(r)$ to make it able to produce the ideal correlation of 
+The ideal strategy for the full test is an extension of the ideal strategy of $\LS(r)$ to make it generate the ideal correlation of 
 the extended weighted CHSH test.
@@
 \begin{align*}
-    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_1) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_1^0 - \tP_1^1) \\
-    &(\1_{W_2} \x \1_{W_2} \x \Pi_V) \tM(a_2) (\1_{W_2} \x \1_{W_2} \x \Pi_V) = \1_{W_2} \x \1_{W_2} \x (\tP_2^0 - \tP_2^1),
-\end{align*}
-and similarly on Bob's side.
-In other words, the observables $\tM(a_j)$ and $\tN(a_j)$ are 
-measuring the same state on the subspace $V$ as $\tP_j$ and $\tQ_j$
+    & \tM(a_j)  = \1_{W_2} \x \1_{W_2} \x (\tP_j^0 - \tP_j^1) \\
+    & \tN(a_j)  = \1_{W_2} \x \1_{W_2} \x (\tQ_j^0 - \tQ_j^1),
+\end{align*}
+for $j = 1,2$,
+which can be checked using \cref{eq:ketj,eq:ketd-j,eq:ketj+,eq:ketj-}.
+In particular, the observables $\tM(a_j)$ and $\tN(a_j)$ are 
+measuring the same state on the subspace $V_1$ as $\tP_j$ and $\tQ_j$
 for $j = 1,2$.
@@
 The full correlation is generated by the ideal strategy presented in the previous subsection.
-We denote the full correlation by $\fC(d,r) = \{( \tpr{ab}{xy} )_{a,b}\}_{x,y}$.
+We denote the full correlation by $\fC(d,r) = \{( \tpr{a,b}{x,y} )_{a,b}\}_{x,y}$.
 To help readers to understand the proofs in \cref{sec:main} better, 
@@
 \hline
-\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{20}{00}$ 
-& $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{20}{10}$ \\
+\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{2,0}{0,0}$ 
+& $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{2,0}{1,0}$ \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{20}{00}$ 
-&  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{20}{10}$  \\
+&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{2,0}{0,0}$ 
+&  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{2,0}{1,0}$  \\
 \hline
-\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{20}{01}$ & 
-$ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{2 0}{11}$  \\
+\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{2,0}{0,1}$ & 
+$ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{2, 0}{1,1}$  \\
 \cline{2-8}
-&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{20}{01}$ &  
-$ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{20}{11}$ \\
+&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{2,0}{0,1}$ &  
+$ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{2,0}{1,1}$ \\
 \hline
@@
 \end{table}
-We don't explicitly calculate the conditional probabilities of the form $\pr{20}{xy}$ when $x \in \{\nr+1, \nr+2\}$ and $y \in \{1, 2\}$ 
+We don't explicitly calculate the conditional probabilities of the form $\pr{2,0}{x,y}$ when $x \in \{\nr+1, \nr+2\}$ and $y \in \{1, 2\}$ 
 because they are irrelevant.
@@
 The correlation tables for the other seven pairs
-of questions are similar.
+of questions of the commutation game are similar.
 
@@
     be families of output alphabets.
-	For a correlation $\tilde{C} = (\tpr{ab}{xy})$
+	For a correlation $\tilde{C} = (\tpr{a,b}{x,y})$
 	with $(a,b) \in \calA_x \times \calB_y$ and $(x,y) \in \calX \times \calY$,
@@
 	if it produces the correlation
-	$( \pr{ab}{xy} = \bra{\psi} M_x^a N_y^b \ket{\psi} )$ such that
+	$( \pr{a,b}{x,y} = \bra{\psi} M_x^a N_y^b \ket{\psi} )$ such that
 	\begin{align}
 	\label{eq:expect}
-	\E_{(x,y) \sim \pi} \left[\sum_{ab} \abs{\pr{ab}{xy} - \tpr{ab}{xy}}\right] \leq \ep.
+	\E_{(x,y) \sim \pi} \left[\sum_{ab} \abs{\pr{a,b}{x,y} - \tpr{a,b}{x,y}}\right] \leq \ep.
 	\end{align}
@@
 \begin{align*}
-    \pr{ab}{xy} \appd{O(r\ep)} \tpr{ab}{xy},
+    \pr{a,b}{x,y} \appd{O(r\ep)} \tpr{a,b}{x,y},
 \end{align*}
@@
 \begin{proof}
-The condition that $(\tpr{\ba b}{I_i s})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
-\begin{align*}
-\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{I_i s} = 1
+The condition that $(\tpr{\ba, b}{I_i, s})$ of $\fC(d,r)$ wins the linear system game optimally is equivalent to
+\begin{align*}
+\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba, b}{I_i, s} = 1
 \end{align*}
@@
 \begin{align*}
-	\bra{\psi} M_i(s) N(s) \ket{\psi} &= 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba b}{I_i s} -1,
+	\bra{\psi} M_i(s) N(s) \ket{\psi} &= 2 \sum_{\ba,b: \ba \in X_i, a(s) = b} \pr{\ba, b}{I_i, s} -1,
 \end{align*}
@@
 \begin{align*}
-	\bra{\psi} M_i(s) N(s) \ket{\psi} \appd{O(r \ep)} 2\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba b}{is} - 1 = 1.
+	\bra{\psi} M_i(s) N(s) \ket{\psi} \appd{O(r \ep)} 2\sum_{\ba,b: \ba \in X_i, a(j) = b} \tpr{\ba, b}{I_i, s} - 1 = 1.
 \end{align*}
@@
 About the notation,
-for $(x,y) \in \calX^{\EXT} \times \calY^{\EXT}$ and $(a,b) \in \calA_x^{\EXT} times \calB_y^{\EXT}$, 
+for $(x,y) \in \calX^{\EXT} \times \calY^{\EXT}$ and $(a,b) \in \calA_x^{\EXT} \times \calB_y^{\EXT}$, 
 Alice and Bob's projectors are denoted 
@@
 as illustrated in \cref{sec:prelim}.
-Since the two answers for question $1$ and $2$ are $0$ and $1$, 
+Since the two answers for questions $1$ and $2$ are $0$ and $1$, 
 we denote Alice and Bob's binary observables for these two questions
@@
 Recall that the implication of $\bS$ being an $\ep$-approximate strategy is that 
-$\pr{ab}{xy} \appd{O(r \ep)} \tpr{ab}{xy}$ for each question 
+$\pr{a,b}{x,y} \appd{O(r \ep)} \tpr{a,b}{x,y}$ for each question 
 pair $(x,y)$ and its associating answer pair $(a,b)$.
@@
 \begin{align*}
-	   \bra{\psi} M_{x}^aN_y^b \ket{\psi} 
-	&= \bra{\psi}(M_0^0 + M_0^2) M_x^a N_y^b (M_0^0 + M_0^2)\ket{\psi} \\
-	&=  \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_0^2\ket{\psi}\\
-	&\quad\quad+\bra{\psi}M_0^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^2 M_x^aN_y^b M_0^2\ket{\psi}\\
-	&\appd{O(\sr\se)}  \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_x^2\ket{\psi} \\
-	&\quad \quad +\bra{\psi}M_x^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_x^2 M_x^aN_y^b M_x^2\ket{\psi}\\
-	&=\bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi},
+	   &\bra{\psi} M_{x}^aN_y^b \ket{\psi} \\
+	= &\bra{\psi}(M_0^0 + M_0^2) M_x^a N_y^b (M_0^0 + M_0^2)\ket{\psi} \\
+	=  &\bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_0^2\ket{\psi}
+	+\bra{\psi}M_0^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^2 M_x^aN_y^b M_0^2\ket{\psi}\\
+	\appd{O(\sr\se)} & \bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_0^0 M_x^aN_y^b M_x^2\ket{\psi} 
+	+\bra{\psi}M_x^2 M_x^aN_y^b M_0^0\ket{\psi} + \bra{\psi}M_x^2 M_x^aN_y^b M_x^2\ket{\psi}\\
+	=&\bra{\psi}M_0^0 M_x^aN_y^b M_0^0\ket{\psi},
 \end{align*}
@@
 	 %\label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
-	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(\sr\se)} 1/(d-1).
+	 \label{eq:psi1_norm} &\norm{\ket{\psi_1}}^2 \appd{O(\sr\se)} \frac{1}{d-1}.
 	\end{align}
@@
     \label{eq:A_omega}
-        O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1}.
-    \end{align}
+        O_A (U_A\ct)^j \ket{\psi_1} \appd{O(\sd r^{j} \qe)}\omega_d^{-r^j}  (U_A\ct)^j \ket{\psi_1},
+    \end{align}
+    which will be used in \cref{sec:self-test}.
 	Hence for $j \neq j'$, $(U_A\ct U_B\ct)^{j} \ket{\psi_1}$ and $(U_A\ct U_B\ct)^{ j'} \ket{\psi_1}$ are close to eigenvectors
@@
 	\begin{align}
-		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
-		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
+		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
-		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d r^{d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d^{5/2} r^{d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_{j r^{-1}}}_{B'}.
@@
 \begin{align}
-	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d r^{d} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
+	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}.
 \end{align}
@@
 	&\quad\Phi_{A,2} \x \Phi_{B,2}( \Phi_{A,1} \x \Phi_{B,1} (\ket{\psi})) \\
-	&\appd{O(d r^d \ep^{1/8})} \left[\Phi_{A,2} \x \Phi_{B,2}
+	&\appd{O(d^{5/2} r^d \ep^{1/8})} \left[\Phi_{A,2} \x \Phi_{B,2}
 	(\sqrt{d-1} \ket{\psi_1})\right] \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
@@
 		\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(\sd r^{d} \qe)}&\frac{1}{d} \sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}\omega_d^{(k_2-k_1)j}\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
+		\appd{O(d^{5/2} r^{d} \qe)}&\frac{1}{d} \sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}\omega_d^{(k_2-k_1)j}\ket{\psi_1} \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
 		\xrightarrow[]{QFT_d^{-1}} &\frac{1}{d^2}\sum_{l_1,l_2 = 0}^{d-1}\sum_{k_1,k_2 = 0}^{d-1}\sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j} 
@@
 \begin{align}
-	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d r^{d} \ep^{1/8})} \left(\sqrt{d-1} \ket{\psi_1}\right) \x \left(\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\right),
-\end{align}
-where we use the fact that $O(d r^{d} \ep^{1/8})$ dominates both $O(d r^{d/2+1/4} \ep^{1/8})$ and 
-$O(\sd r^{d} \qe)$.
+	\Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8})} \left(\sqrt{d-1} \ket{\psi_1}\right) \x \left(\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\right),
+\end{align}
+where we use the fact that $O(d^{5/2} r^{d} \ep^{1/8})$ dominates both $O(d r^{d/2+1/4} \ep^{1/8})$ and 
+$O(d^{5/2} r^{d} \qe)$.
 The relation $ \sqrt{d-1} \norm{\ket{\psi_1}} \appd{O(\sd \qr\qe)} 1$ is derived from the fact that
@@
 		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(d r^{d}  \ep^{1/4})}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}
+		\appd{O(d^{5/2} r^{d}  \ep^{1/4})}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct U_B\ct)^{\log_r j}
 		\omega_d^{-j}\omega_d^{(k_2-k_1)j}\ket{\psi_1}
@@
 		 \ket{x_{k_1}}_{A'}\ket{x_{k_2}}_{B'}\\
-		\appd{O(d r^{d} \qe)}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}
+		\appd{O(d^{5/2} r^{d} \qe)}& \frac{1}{d}\sum_{k_1,k_2 = 0}^{d-1} \sum_{j=1}^{d-1} (U_A\ct)^{\log_r j-1} (U_B\ct)^{\log_r j}
 		\omega_d^{k_2j-k_1jr^{-1}}\ket{\psi_1}

### 2019-11-05 Draft/draft.tex
Honghao: arXiv version 1

@@
 \author{Honghao Fu
-\footnote{\href{mailto:h7fu@umd.edu}{h7fu@umd.edu}}}
+\footnote{Email: \href{mailto:h7fu@umd.edu}{h7fu@umd.edu}}}
 
@@
 \date{}
-\affil{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA
-\break
+\affil{
+Joint Center for Quantum Information and Computer Science, \break
+Institute for Advanced Computer Studies and Department of Computer Science,\break 
+University of Maryland, College Park, MD 20742, USA
 }
@@
 	Since there are 
-	infinitely many prime numbers whose smallest multiplicative generators
-	are at most $5$ (M. Murty \textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
+	infinitely many prime numbers whose smallest multiplicative generator
+	is at most $5$ (M. Murty \textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
 	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
@@
 honestly and correctly \cite{ruv2013,coladan2017verifier}.
-It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
-\cite{mayersyao,vv2014,fu2018}.
+Self-testing also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
+\cite{mayersyao,fu2018}.
 Since the setting of multi-prover interactive proof systems is similar to a self-test, self-testing arguments also help to prove
@@
 	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
-	with constant-sized question and answer alphabets.
+	with constant-sized input and output alphabets.
 \end{theorem}
@@
 This correlation is denoted by $\fC(d,r)$.
-Note that the sizes of the input or output alphabet of $\fC(d,r)$ is independent of $d$. 
+Note that the size of neither the input nor the output alphabet of $\fC(d,r)$ depends on $d$. 
 % the distributions in $\fC(d,r)$ do. 
@@
 should give an assignment to each variable of the equation.
-Bob is asked to assign a value to a random variable of that equation.
+Bob is asked to assign a value to a random variable of the chosen equation.
 They win the game if Alice's assignment satisfies the equation and Bob's
@@
 \end{align*}
-Using two copies of $\ket{EPR}$
+Using two copies of $\ket{EPR}$,
 the Magic square game can be won with certainty.
-It has been shown that if a strategy that can win this game almost perfectly, 
-the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
-so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
+It has been shown that if a strategy can win this game almost perfectly, 
+the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}.
+So we say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
 The key observation that leads to the self-testing proof is that 
@@
 Following Slofstra's design, 
-the game $\LS(r)$ is constructed so that the sizes
-of the input alphabets for Alice and Bob are of order $\Theta(r)$,
-and the answer sets are of size $\Theta(1)$.
-Restricting $r \leq 5$ as in \cref{thm:inf} implies that 
-$\LS(r)$ only uses constant-sized input and output alphabets.
+the sizes of the input alphabets for Alice and Bob are of order $\Theta(r)$,
+and the answer sets are of size $\Theta(1)$ in $\LS(r)$.
+%Restricting $r \leq 5$ as in \cref{thm:inf} implies that 
+%$\LS(r)$ only uses constant-sized input and output alphabets.
 
@@
 by $\LS(r)$ is the following.
-Winning $\LS(r)$ implies that the winning strategy contains binary observables
+Winning $\LS(r)$ guarantees that the winning strategy contains binary observables
 $M_1, M_2, M_3, M_4$ on Alice's side and 
@@
 with $U$ and $O$ satisfying \cref{eq:uor}.
-Then we can deduce that the eigenvalues of $O$ must be
-of the form $\omega_d^j = e^{i 2j\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
-We can also deduce that $U$ is a permutation of the eigenbasis of $O$.
-Winning this linear system game also implies that Alice and Bob share a state
-$\ket{\psi}$ such that $\ket{\psi}$
-is spanned by tensor products of states in the eigenbasis of $O$,
-and is invariant under the permutation induced by $U$
+%Then we can deduce that the eigenvalues of $O$ must be
+%of the form $\omega_d^j = e^{i 2j\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
+Moreover, if we can certify that the unitary $O$
+has the eigenvalue $\omega_d := e^{i 2\pi /d }$
+where $r$ is a primitive root of $d$, \cref{eq:uor}
+automatically guarantees that the spectrum of $O$ contains 
+$\{ \omega_d^j \}_{j=1}^{d-1}$.
+It also guarantees that the eigenspace of each distinct eigenvalue
+has the same dimension. 
+%We can also deduce that $U$ is a permutation of the eigenbasis of $O$.
+%Winning this linear system game also guarantees that Alice and Bob share a state
+%$\ket{\psi}$ such that 
 % \begin{align*}
@@
 % \end{align*}
+%From the equations above, we can deduce that
+%$\ket{\psi}$ is spanned by tensor products of states in the eigenbasis of $O$,
+%and is invariant under the permutation induced by $U$.
+
 % The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
@@
 % under the permutation induced by $U$. 
-At this point, the eigenvalues of $O$ are unknown, so
-certifying the eigenvalues of $O$ requires another test.
+%At this point, the eigenvalues of $O$ are unknown, so
+%certifying the eigenvalues of $O$ requires another test.
 
@@
 
-The remaining question is how to certify eigenvalues of $O$, so we
-design a nonlocal test called the extended weighted CHSH test.
 % Before going to the answer,
@@
 % to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
-The difference between a nonlocal game and a nonlocal test will be discussed later.
-The combination of a linear system game with 
-a nonlocal test in the construction of $\fC(d,r)$ 
-is a new way to use a linear system game for robust self-testing.
-It distinguishes our approach from all the previous ones.
-
-The extended weighted CHSH test is designed based on the $\alpha$-weighted CHSH inequality, 
+%The difference between a nonlocal game and a nonlocal test will be discussed later.
+
+The strong guarantee of \cref{eq:uor} is built on the assumption of an eigenvalue
+of the unitary $O$, so the next problem is how to certify that $O$ has eigenvalue $\omega_d$.
+In order to solve it, we design $\fC(d,r)$ to contain 
+an extension of the optimal correlation 
+that achieves the maximal violation of the weighted
+CHSH inequality.
+The $\alpha$-weighted CHSH inequality is defined by
 \begin{align*}
@@
 
-Therefore, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
+Therefore, in the extended correlation, we set $\alpha = \cot( -\pi/d )$
 for some odd prime $d$ whose primitive root is $r$,
 and ask Alice and Bob
-to reuse the observables $M_1, M_2$ and $N_1, N_2$ defined in $\LS(r)$. Then we can certify that
-the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
-Combining this observation with the fact that $O$ satisfy the relation $UOU\ct = O^r$,
-we can conclude that all the eigenvalues of $O$ are $\{ e^{ij 2\pi /d} \}_{j=1}^{d-1}$,
-and the eigenspaces of all the eigenvalues have the same cardinality.
-
-At this point, we have the explicit structure of $O$, so we 
-can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
-to prove the correlation $\fC(r, d)$ can robustly self-test 
-a maximally entangled state of dimension $4(d-1)$,
-\begin{align*}
-    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
-    \ket{EPR}^{\x 2}.
-\end{align*}
-In this proof, we demonstrate a new way to apply the generalized swap-isometry
-proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
-dimension.
-
-Our contributions are:
-\begin{enumerate}
-\item We identify a family of correlations with constant-sized input and output alphabets that can be used to robustly self-test
-maximally entangled states with unbounded local dimensions. Before our work, the most efficient way 
-was to use $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
-the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
-
-\item Our result gives us deeper understandings of the set of quantum correlations.
-In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
-lower bounds of the entanglement required to achieve certain correlations are identified.
-We discover a large family of correlations such that we know exactly the entangled state
-required to achieve each of the correlations in this family. 
-\end{enumerate}
-
-\textbf{Structure of the paper}.
+to reuse the observables $M_1, M_2$ and $N_1, N_2$ from a winning strategy of $\LS(r)$. Then we can certify that
+the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $\omega_d$ and $\omega_d^{-1}$.
+Combining this observation with the fact that $O$ satisfy the relation \cref{eq:uor},
+we can conclude that all the eigenvalues of $O$ contains $\{ \omega_d^j \}_{j=1}^{d-1}$,
+and the eigenspaces of all such eigenvalues have the same dimension.
+
+%At this point, we have the explicit structure of $O$, so we 
+%can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
+%to prove the correlation $\fC(r, d)$ can robustly self-test 
+%a maximally entangled state of dimension $4(d-1)$,
+%\begin{align*}
+%    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
+%    \ket{EPR}^{\x 2}.
+%\end{align*}
+%In this proof, we demonstrate a new way to apply the generalized swap-isometry
+%proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
+%dimension.
+
+The full correlation $\fC(r, d)$ is produced by an ideal strategy
+that can win $\LS(r)$ perfectly and 
+can reproduce the aforementioned extended correlation perfectly.
+Combining the implications of a quantum strategy to win $\LS(r)$
+and reproduce the extended correlation, we 
+can prove that the correlation $\fC(r, d)$ can robustly self-test the state
+$\ket{\tpsi}$ defined by
+\begin{align*}
+	\ket{\tpsi} = \frac{1}{\sqrt{d-1}} \left( \sum_{j=1}^{d-1} \ket{j}\ket{d-j} \right) \x \ket{EPR}^{\x 2}.
+\end{align*}
+More precisely, we prove that if some quantum strategy using the shared state
+$\ket{\psi}$ can produce a correlation that is within trace distance
+$\ep$ to $\fC(d,r)$, then there exist an local isometry
+$\Phi_A \x \Phi_B$ and a state $\ket{junk}$ such that
+\begin{align}
+    \label{eq:distance}
+    \norm{\Phi_A\x\Phi_B(\ket{\psi}) - \ket{junk}\x \ket{\tpsi}} = O(d^{5/2} r^d \ep^{1/8}).
+\end{align}
+Note that the isometry $\Phi_A \x \Phi_B$ only involves local operations
+on Alice's and Bob's side.
+The isometry $\Phi_A \x \Phi_B$ captures the essence of the generalized 
+swap-isometry proposed in \cite{yang2013}, but it is constructed in a different way.
+
+As mentioned at the start of this subsection, the last step of proving \cref{thm:inf} is to apply the general self-testing result of
+$\fC(d,r)$ to the prime numbers with a primitive root $2$, $3$ or $5$.
+The theorem follows naturally from the fact that there are infinitely many such
+prime numbers \cite{murty1988}.
+
+\subsection{Structure of the paper}
 We start with notations and background information in \cref{sec:prelim}.
@@
 Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
-In the end, we give the robust self-testing proof in \cref{sec:main}.
+\Cref{sec:main} is devoted to the robust self-testing proof. We end this paper with conclusions
+in \cref{sec:conclu}.
 
@@
 %-----------------------------------
-The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we self-test is denoted by
-\begin{align}
-\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
-\end{align}
-The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
+%The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we self-test is denoted by
+%\begin{align}
+%\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
+%\end{align}
+%The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
+
+The EPR pair is denoted by 
+\begin{align}
+	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
+\end{align}
+and the Pauli operators are denoted by
+\begin{align}
+	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
+\end{align}
 The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. 
-
-In the qubit case, the EPR pair is denoted by 
-\begin{align}
-	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
-\end{align}
-and the Pauli operators are denoted by
-\begin{align}
-	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
-\end{align}
 Note that we only work with finite Hilbert spaces in our work.
@@
 \end{align*}
-
 Next we give the definition of a group representation. 
@@
 	\begin{cases}
-		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
-		(-1)^{a + b}, \quad \text{if } x = 2,\; y = 1 \\
-		(-1)^{1 + a + b}, \quad \text{if } x = y = 2.
+		\alpha (-1)^{a + b}, & \text{if } x = 1, \\
+		(-1)^{a + b},  &\text{if } x = 2,\; y = 1, \\
+		(-1)^{1 + a + b},  &\text{if } x = y = 2.
 	\end{cases}
@@
 The weighted CHSH inequality is true 
-if Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
+if Alice and Bob share some product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
 However, if they share an entangled state $\ket{\psi}$, the value of $\I_\alpha$ can be as large as
@@
     Hence, a map $\phi:\Pg_1 \rightarrow \Gamma$ that maps $s$
-    to $s$ for each $s \in S_1$ is a homomorphism between $Pg_1$ and 
-    $Gamma$. 
+    to $s$ for each $s \in S_1$ is a homomorphism between $\Pg_1$ and 
+    $\Gamma$. 
     A representation of $\Gamma$ can be constructed from a representation 
     of $\Pg_1$ as shown in the proof of Proposition $27$ of \cite{slofstra2017},
-    so Lemma $15$ of \cite{slofstra2017} proves that
-    the homomorphism $\phi$ is injective.
+    so the injectivity of homomorphism $\phi$ follows Lemma $15$ of \cite{slofstra2017}.
 
@@
 \end{align*}
-Note that in the standard basis, $\tU$ is
+Note that in the standard basis, 
 \begin{align}
@@
 The projector onto $V_j$ is denoted by $\Pi_{V_j}$. 
-On each subspace $V_j$, we define quantum states 
+On each subspace $V_j$, we define states 
 \begin{align}
@@
 \begin{align*}
-    \calX = \calX^{\LS} \cup \calX^{\EXT'} \cup \calX^{\COMM} \\
-    \calY = \calY^{\LS} \cup \calY^{\EXT'} \cup \calY^{\COMM},
+    \calX = \calX^{\LS} \cup \calX^{\EXT'} \cup \calX^{\COMM}, \\
+    \calY = \calY^{\LS} \cup \calY^{\EXT'} \cup \calY^{\COMM}.
 \end{align*}
@@
 The shared state of the ideal strategy is
-\begin{align*}
+\begin{align}
+	\label{eq:tpsi_full}
     \ket{\tpsi} = \ket{\tpsi}^{\LS} = \frac{1}{2}(\ket{x_1}\ket{x_1} + 
     \ket{x_2}\ket{x_2})^{\x 2} \x \ket{\tpsi}^{\EXT}.
-\end{align*}
+\end{align}
 Alice and Bob's observables for each variable in the linear system of 
@@
 	\begin{align*}
-	    \ket{\psi_2} - &\ket{\psi_1} \\
+	    &\ket{\psi_2} - \ket{\psi_1} \\
 	    &\appd{O(\sr \se)}
@@
 	\begin{align}
-		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}\\	
-		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\tpsi}\\	
+		&\Phi_A \x \Phi_B (O_A\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{EPR}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{d-j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (O_B\ket{\psi}) \appd{O(d^{5/2} r^{d} \ep^{1/8}))} \ket{junk} \x \ket{EPR}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \omega_d^{j}\ket{x_{d-j}}_{A'}\ket{x_j}_{B'}\\
-		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d^{5/2} r^{d}  \ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (U_A\ket{\psi}) \appd{O(d^{5/2} r^{d}  \ep^{1/8}))} \ket{junk} \x \ket{EPR}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{(d-j)r^{-1}}}_{A'}\ket{x_j}_{B'} \\
-		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{\EPR{2}}^{\x 2} \x
+		&\Phi_A \x \Phi_B (U_B\ket{\psi}) \appd{O(d^{5/2} r^{d}\ep^{1/8}))} \ket{junk} \x \ket{EPR}^{\x 2} \x
 		\frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{x_{d-j}}_{A'}\ket{x_{j r^{-1}}}_{B'}.
@@
 \end{theorem}
+The state $\ket{\tpsi}$ is defined in \cref{eq:tpsi_full}.
+
 Before proving \cref{thm:self-test}, we state the consequence of it.
@@
         \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
-    	node[midway,right] (bracket2) {$\sum_{j=1}^{d-1}\ket{x_j}\ket{x_{d-j}}$}
+    	node[midway,right] (bracket2) {$\ket{\tpsi}^{\EXT}$}
     	(6.5,-2.5);
@@
 \end{proof}
+
+%=============================
+\section{Conclusions}
+\label{sec:conclu}
+%=============================
+In summary, we identify a family of correlations with constant-sized input and output alphabets that can be used to robustly self-test
+maximally entangled states with unbounded local dimension.
+Before our work, the most efficient way 
+was to use $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
+the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
+
+Our result gives us deeper understandings of the set of quantum correlations.
+In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
+lower bounds of the entanglement required to achieve certain correlations are identified.
+We discover a large family of correlations such that we know exactly the entangled state
+required to achieve each of the correlations in this family.
 
